### 2018-12-04 paper/main.tex
INIT | add first latex template for 2018 / add sec18 origin paper tex content

%!TEX options = --shell-escape

\documentclass[bachelor]{thesis-uestc}

\title{密文重复数据删除机制的频率攻击方法}
\author{任彦璟}
\advisor{李经纬\chinesespace 副教授}
\school{计算机科学与工程学院(网络空间安全学院)}
\major{信息安全}
\studentid{2015040101018}

\begin{document}

\makecover

\begin{chineseabstract}

加密重复数据删除旨在解决大规模数据存储系统中的安全性和存储效率：它确保每个明文都由明文本身内容派生的对称密钥加密，从而为数据存储提供机密性保证，同时保留重复数据删除的存储节省效率。但是，加密重复数据删除的确定性特性也会泄漏明文的频率，从而使加密重复数据删除容易受到频率分析的影响。在本文中，我们重新审视了频率分析导致的加密重复数据删除的安全漏洞。我们认为加密重复数据删除可能更容易受到精心设计的频率分析攻击，因此攻击提供了高可信度，可确保每个推断的明文确实对应于目标密文的概率很高（即从统计角度来看，高精度） 。为此，我们提出了两种新的频率分析攻击，它们可以适应实际重复数据删除工作负载的特性，从而提高频率分析的准确性。我们根据实际情况评估针对实际存储工作负载的建议攻击，并提供有关如何带来实际损失的观察。

\chinesekeyword{加密重复数据删除, 频率分析攻击, 聚类分析}
\end{chineseabstract}

\begin{englishabstract}
Encrypted deduplication aims to address security and storage efficiency in large-scale data storage systems: it ensures that each plaintext is encrypted by a symmetric key that is derived from the content of the plaintext itself, so as to provide confidentiality guarantees for data storage while preserving the storage saving effectiveness of deduplication. However, the deterministic nature of encrypted deduplication also leaks the frequencies of plaintexts, thereby making encrypted deduplication vulnerable to frequency analysis. In this paper, we revisit the security vulnerability of encrypted deduplication due to frequency analysis. We argue that encrypted deduplication can be even more vulnerable to carefully crafted frequency analysis attacks, such that the attacks provide high confidence of ensuring that each inferred plaintext indeed corresponds to the target ciphertext with a high probability (i.e., high precision from a statistical perspective). To this end, we propose two new frequency analysis attacks that adapt the characteristics of practical deduplication workloads to increasing the severity of frequency analysis. We empirically evaluate our proposed attacks against real-world storage workloads, and provide observations on how they bring actual damages.

\englishkeyword{Encrypted deduplication, Frequency analysis attacks, Cluster analysis}
\end{englishabstract}

\thesistableofcontents

\thesischapterexordium

\section{研究工作的背景与意义}

在本节中，我们将介绍普通和加密重复数据删除方法的基础知识。
我们专注于基于块的重复数据删除，它以称为块的小型数据单元的粒度运行。图1总结了重复数据删除工作流程。具体地，存储系统首先经由一些组块过程将客户端的文件（例如，备份）分割成逻辑组块，使得每个逻辑组块由其内容的加密哈希唯一地标识，称为标签（即，指纹）。如果两个逻辑块具有相同的标记，则认为它们是相同的，而不同逻辑块具有相同标记的可能性几乎可以忽略不计[24]。存储系统仅存储相同逻辑块的副本作为物理块，并且每个相同的逻辑块通过小尺寸引用引用相同的物理块。
基于块的重复数据删除比整个文件重复数据删除更精细，因此通常具有更高的存储效率。我们可以进一步选择固定大小或可变大小的块来进行重复数据删除。固定大小的分块将数据分区为等大小（逻辑）块，而可变大小的分块（也称为内容定义的分块）通常以内容相关的方式指定块边界（例如，通过Rabin指纹[54]）和分区将数据文件转换为可变大小的块。固定大小的分块简单而快速，而可变大小的分块在内容转换时保持存储效率，因为即使文件添加或删除了一些内容，大多数块仍然保持不变。可变大小的分块通常用在备份系统中（例如，[46]，[66]），但固定大小的分块显示对某些工作负载（例如，VM映像[38]）有效。我们的工作涉及固定大小和可变大小的分块方法。
加密的重复数据删除解决了外包环境（例如，云存储）中的块机密性，同时保持了重复数据删除的有效性。传统的对称加密要求多个客户端通过其（不同的）密钥加密其文件数据，从而将相同的块转换为不再能够进行重复数据删除的不同加密块。消息锁定加密（MLE）[21]规范了加密重复数据删除。基线MLE实例化基于每个明文的内容（例如，基于块的重复数据删除中的逻辑组块）导出对称密钥（称为MLE密钥），并使用MLE密钥加密明文以形成密文（例如，加密的逻辑块）。因此，MLE确保将相同的明文加密为相同的密文。最后，存储系统从每个密文中导出标签并执行重复数据删除。

MLE可以实现为不同的实例化（参见第VIII节）。最受欢迎的是融合加密（CE）[29]，它已在各种存储系统中实现（例如，[3]，[5]  -  [7]，[9]，[13]，[15] ]，[28]，[58]）。 CE的主要思想是从每个明文内容的加密散列中导出MLE密钥。注意，一些MLE实例[21]允许将相同的明文加密成不同的密文。然而，他们确保标签仍然来自明文，因此他们可以通过检查标签的相等性来执行重复数据删除。
现有的MLE实例都建立在概念确定性加密的基础上，以确保密文（或标签）确定性地从明文传递，从而保持重复数据删除的有效性，而不是传统的对称加密。虽然确定性加密提供了机密性保证，但在本文中，我们认为攻击者可以利用这种确定性来推断给定密文的原始明文。

\chapter{Introduction}
\label{sec:introduction}

Modern storage systems save storage space by removing content redundancy 
via {\em deduplication}, which stores only the data copies with unique content
among all already stored data copies.  Field studies show that deduplication
effectively saves substantial fractions of storage space for real-world
storage workloads, such as backups
\cite{zhu08,lillibridge09,wallace12,douglis17}, file system snapshots
\cite{meyer11}, and virtual machine (VM) disk images \cite{jin09}.  Cloud
storage services (e.g., Dropbox and Google Drive) also deploy deduplication to
save maintenance costs \cite{harnik10}. 
To ensure data confidentiality, clients should first encrypt their own data
before writing the data to a storage system.  It is critical that the
encryption approach preserves the original content redundancy pattern, so that
duplicate data copies can still be detected and removed from the storage
system even after encryption.

We study {\em encrypted deduplication}, which combines encryption and
deduplication in a way that each plaintext (data copy) is symmetrically
encrypted and decrypted by a key that is derived from the content of the
plaintext itself; in other words, should the plaintexts be duplicates, their
resulting ciphertexts are also duplicates and hence can be deduplicated.
Encrypted deduplication can be achieved through the formal cryptographic
primitive known as {\em message-locked encryption (MLE)} \cite{bellare13a},
whose instantiations have been extensively studied and realized in the
literature (see Section~\ref{sec:background}).  MLE builds on the notion of
{\em deterministic encryption}, which deterministically maps a plaintext to
the same ciphertext to preserve the identical content pattern.  In addition to
MLE, deterministic encryption is also found in symmetric searchable encryption
(SSE) \cite{song00} and order-revealing encryption (ORE) \cite{boldyreva09},
so as to allow efficient queries over encrypted data.

%that yields the same ciphertext for a given plaintext and key, even over
%separate executions of the encryption functions. This makes it specially
%efficient for {\em equality test}, meaning that finding an exact match
%plaintext is as easy as finding an exact match over the corresponding
%ciphertext. Thus, deterministic encryption has been applied in various
%application-specific cryptographic primitives, such as symmetric searchable
%encryption (SSE) \cite{song00}, order-revealing encryption (ORE)
%\cite{boldyreva09} and message-locked encryption (MLE) \cite{bellare13a},
%so as to enable efficient queries over encrypted data.

%the effectiveness of frequency analysis against deterministic encryption in
%the context of {\em deduplication}, which stores only data copies, called
%{\em chunks}, that have unique content among all already stored chunks. The
%deduplication technique can effectively reduce the storage space of different
%workloads (e.g., 68\% for primary data \cite{meyer09}, 83\% for backup data
%\cite{meyer09}, and 80\% for virtual machine volumes \cite{jin09}),
%and it has been deployed in various cloud storage services (e.g., Dropbox
%and Google Drive) for minimizing maintenance cost
%\cite{harnik10}. To protect information, (encrypted) deduplication
%applies deterministic encryption \cite{bellare13a} on each chunk, such
%that the redundant copies of plaintext chunks can  be removed
%efficiently.  Compared to database records \cite{naveed15} or searchable
%keywords \cite{islam12}, the chunks involved in deduplication constitute
%a huge domain (e.g., over ten millions of possible plaintext values), and
%the underlying plaintexts of some target chunks may not appear in the
%auxiliary information. In addition, a large fraction of chunks have the
%same frequencies in practical deduplication workloads \cite{li17}, and
%this fact has been shown to decrease the effectiveness of frequency
%analysis \cite{naveed15}.    Prior work \cite{li17} shows that classical
%frequency analysis can only infer a few plaintext chunks in
%deduplication.

However, because of the deterministic nature, encrypted deduplication leaks
information about the ciphertexts, such that the adversaries can analyze the
ciphertexts and infer their corresponding original plaintexts.  Specifically,
an adversary can perform {\em frequency analysis} \cite{alkadit92} on both the
ciphertexts that are observed and the plaintexts that are known a priori.
Then the adversary can infer the ciphertext-plaintext pairs, in which both the
ciphertext and the plaintext in each pair have correlated frequency patterns. 
Such inference attacks have been shown effective against database records (e.g.,
\cite{lacharite18,grubbs17,kellaris16,naveed15,bindschaedler17,durak16}) and
searchable keywords (e.g., \cite{pouliot16,zhang16b,cash15,islam12,grubbs16})
that are protected by deterministic encryption.   In particular, frequency
analysis is shown to effectively infer plaintext information from encrypted
deduplication \cite{li17}.

In this paper, we revisit the information leakage issues in encrypted
deduplication.  We argue that encrypted deduplication can actually be even
more vulnerable towards carefully crafted frequency analysis attacks.  Such
sophisticated attacks not only infer a significant fraction of
ciphertext-plaintext pairs as shown in the previous work \cite{li17}, but also
ensure that each inferred plaintext indeed corresponds to the target
ciphertext with a high probability.  From a statistical perspective, The
latter implies that the number of false positives is low, or equivalently, the
precision is high.

To this end, we propose {\em two} new frequency analysis attacks against
practical encrypted deduplication storage systems, and demonstrate their
severity using real-world storage workloads.  Both attacks build on the
characteristics of practical deduplication workloads.  While such
characteristics have been exploited to improve deduplication performance and
storage efficiency in practice, we show how to exploit them from an
adversarial perspective.  We hope that our findings help practitioners and
researchers better understand the vulnerabilities in encrypted deduplication
and motivate more research along this direction.

%They exploit the orders and frequencies of plaintexts preserved within a
%sequence of ciphertexts, in order to infer ciphertext-plaintext pairs as many
%as possible.  However, we find the prior attack  introduces a large number of
%false positives into its inference results and has low precision in
%extracting correct information. In other words, while capable of inferring a
%significant fraction of ciphertext-plaintext pairs, it cannot ensure each
%inferred plaintext is exactly mapped from the target ciphertext.

% For example, our evaluation shows although the locality-based attack can correctly infer 15.2\% of ciphertext-plaintext pairs in some case, the false positives take around 65.2\% in its inference results. In other words, the adversary has low confidence in identifying whether the inferred ciphertext-plaintext pairs are correct or not.

% In this paper, we further examine the information leakage issues in encrypted
% deduplication and argue that encrypted deduplication is in fact even more
% vulnerable towards inference attacks.  We show that in addition to exploiting
% the deterministic encryption nature, an adversary can leverage other leakage
% channels specific to the deduplication characteristics, so as to design {\em high precision} inference attacks against practical encrypted deduplication storage
% systems.  We propose {\em two} novel inference attacks that extend frequency
% analysis and demonstrate their severity against real-world storage workloads.
% We hope that our findings help practitioners and researchers better understand
% the security issues in encrypted deduplication storage and motivate more
% research along this direction.

%Note that variable-size chunking, chunk locality, and similarity are the key
%design primitives of existing deduplication systems to improve deduplication
%performance and storage savings.  We show how these primitives can be
%exploited from an adversarial perspective. 
% We show that in addition to exploiting
% the deterministic encryption nature, an adversary can leverage other leakage
% channels specific to the deduplication characteristics, so as to design {\em high precision} inference attacks against practical encrypted deduplication storage
% systems.  We propose {\em two} novel inference attacks that extend frequency
% analysis and demonstrate their severity against real-world storage workloads.

\section{Overview of New Frequency Analysis Attacks}

We summarize the main ideas of our two new frequency analysis attacks against
encrypted deduplication, namely the {\em distributed-based attack} and the
{\em clustering-based attack}. They build on different assumptions of
adversarial knowledge.

\paragraph{Distribution-based attack:}  The attack builds on the 
{\em locality} property \cite{xia11,lillibridge09,zhu08}, which states that
the ordering of data is likely preserved across various backup files, to infer
the ciphertext-plaintext pairs that are in similar positions of backup files.
In particular, it examines the relative frequency distribution based on the
co-occurrence frequencies of adjacent data, and explores the observation that a
plaintext and its corresponding ciphertext are likely to have similar relative
frequency distributions. Our evaluation shows that the distribution-based
attack reduces the number of false positives of the previously proposed
locality-based attack \cite{li17} by up to 82.4\%, while correctly inferring
up to 21.2\% ciphertext-plaintext pairs (higher than that of the
locality-based attack \cite{li17} by 6\% in the same case).

Furthermore, the distribution-based attack can exploit the leakage of the
varying sizes of plaintexts to filter more false positives.  Our evaluation
shows that it can suppress the fraction of false positives to as low as 1.7\%.

%with {\em variable-size chunking} (see Section~\ref{sec:background}), which partitions file data into smaller units of varying sizes to better remove duplicate content at finer-grained granularities. We leverage the varying sizes of plaintexts to  filter possibly flawed inference results. Our evaluation shows the distribution-based attack further suppresses the fraction of false positives as low as 1.6\%.

% An adversary can leverage the varying sizes of ciphertexts to infer the original plaintexts.  Our evaluation shows that the size-based attack correctly infers up to 31.3\% of ciphertext-plaintext pairs in a real-world dataset.

%{\bf Size-based attack:}  This attack exploits {\em variable-size chunking}
%(see Section~\ref{sec:background}), which partitions file data into smaller
%units of varying sizes to better remove duplicate content at finer-grained
%granularities. An adversary can leverage the varying sizes of ciphertexts to
%infer the original plaintexts.  Our evaluation shows that the size-based
%attack correctly infers up to 31.3\% of ciphertext-plaintext pairs in a
%real-world dataset.

% We also combines 
% This attack exploits the ordering of
% ciphertexts before deduplication and is applicable for both fixed-size and
% variable-size chunking approaches; in other words, we relax the adversarial
% knowledge about the chunk size in the size-based attack.   
% It further inspects the relative frequency distribution of the data
% and filters any potentially flawed inference results.  Our evaluation shows
% that the distribution-based attack infers up to 21.2\% of ciphertext-plaintext
% pairs in a real-world dataset, while significantly reducing the number of
% false positives compared to the prior attack \cite{li17}.

\paragraph{Clustering-based attack:}  The attack relaxes the knowledge about
the ordering pattern exploited by the distribution-based attack.  It builds on
the {\em similarity} property \cite{xia11,bhagwat09}, which states that backup
files share a large fraction of the same data (the ordering may not be
preserved), to infer the ciphertext-plaintext pairs that are clustered
in similar regions of a backup file.  Our evaluation shows that the
clustering-based attack infers up to 30.8\% of raw data content in a
real-world VM image dataset.

%group ciphertexts and plaintexts into clusters, respectively. Then, it infers
%the original contents of ciphertexts from the similar clusters of a backup
%file. 
% infer the ciphertext-plaintext pairs that are in similar
% {\em clusters} of a backup file.

\paragraph{Observations:}  We study the nature of our frequency analysis
attacks based on real-world datasets.  In general, the distribution-based
attack preserves the attack severity even when the prior knowledge of
plaintexts is loosely correlated with the ciphertexts to be attacked.  The
reason is that it uses a statistical approach to quantify the relative
frequency distribution and addresses the disturbance to frequency ranking.  This indicates a wide
exploitation of the distribution-based attack, which should be taken into
account when developing countermeasures.   Also, the distribution-based attack
is more likely to affect rarely updated large files (e.g., disk image files)
or some correlated small files (e.g., programming source files) that are stored together, while the clustering-based
attack mainly threatens the confidentiality of VM disk images.

%We summarize the main ideas of our three inference attacks against encrypted
%deduplication.  The inference attacks build on different assumptions of
%adversarial knowledge.

%In this paper, we propose new inference attacks that increase the effectiveness of frequency analysis with {\em various leakages} of practical deduplication. The key technique is based on an extensive exploitation of the characteristics of deduplication workloads, so as to {\color{blue} identify the available auxiliary information  that is highly correlated with  the underlying plaintexts of target chunks}.  We empirically evaluate our attacks based on real-world datasets, and present new observations about the dataset characteristics for which deterministic encryption is especially insecure. We also discuss possible countermeasures to mitigate the leakage channels. In the following, we summarize the main results of this paper.

%\subsection{Overview of Inference Attacks}

%We summarize the main ideas of our three inference attacks against encrypted
%deduplication.  The inference attacks build on different assumptions of
%adversarial knowledge.

%\begin{itemize}[leftmargin=*]
%\item
%{\bf Size-based attack:}  This attack exploits {\em variable-size chunking}
%(see Section~\ref{sec:background}), which partitions file data into smaller
%units of varying sizes to better remove duplicate content at finer-grained
%granularities. An adversary can leverage the varying sizes of ciphertexts to
%infer the original plaintexts.  Our evaluation shows that the size-based
%attack correctly infers up to 31.3\% of ciphertext-plaintext pairs in a
%real-world dataset. 
%\item
%{\bf Distribution-based attack:}  This attack exploits the ordering of
%ciphertexts before deduplication and is applicable for both fixed-size and
%variable-size chunking approaches; in other words, we relax the adversarial
%knowledge about the chunk size in the size-based attack. It leverages the {\em
%chunk locality} property \cite{xia11,lillibridge09,zhu08}, which states that
%the ordering of data is likely preserved across various backup files, to infer
%the ciphertext-plaintext pairs that are in similar {\em positions} of backup
%files.  It further inspects the relative frequency distribution of the data
%and filters any potentially flawed inference results.  Our evaluation shows
%that the distribution-based attack infers up to 21.2\% of ciphertext-plaintext
%pairs in a real-world dataset, while significantly reducing the number of
%false positives compared to the prior attack \cite{li17}. 
%\item
%{\bf Clustering-based attack:}  This attack further relaxes the knowledge
%about the ordering of ciphertexts in the distribution-based attack.  It
%exploits the {\em similarity} property \cite{xia11,bhagwat09}, which states
%that backup files share a large fraction of the same data (the ordering may
%not be preserved), to infer the ciphertext-plaintext pairs that are in similar
%{\em clusters} of a backup file.  Our evaluation shows that the
%clustering-based attack infers up to 18.1\% of ciphertext-plaintext pairs in a 
%real-world VM image dataset.
%\end{itemize}

%Note that variable-size chunking, chunk locality, and similarity are the key
%design primitives of existing deduplication systems to improve deduplication
%performance and storage savings.  We show how these primitives can be
%exploited from an adversarial perspective.

%%Our trace-driven evaluation shows that the distribution-based attack infers up to 21.2\% of plaintext chunks in the FSL dataset. For comparison, with the same auxiliary information, the inferred chunks by the locality-based attack \cite{li17} (that uses the same leakage of logical order) takes a fraction of 15.2\%. Another advantage of the distribution-based attack is that its effectively is less affected by the correlations between the auxiliary information and target chunks. For example, when we use some loosely correlated auxiliary information, this only degrades the coverage of inferred chunks by 1.4\%.

%%distinguish chunks by their sizes.  Specifically, we propose the {\em
%%size-based attack}, whose idea is to group all chunks by their sizes and
%%launch frequency analysis against each group of chunks of the same size.  Our
%%evaluation shows that the size-based attack correctly infers up to 31.3\% of
%%ciphertext-plaintext pairs in a real-world dataset.

%%The distribution-based attack builds on {\em chunk locality}
%%\cite{xia11,lillibridge09,zhu08}, which is the tendency for chunks in backup
%%streams to re-occur together in the same order. Specifically, if a chunk $M$
%%is surrounded by the chunks $M'$ and $M''$ in one backup, then $M$ is likely
%%to be surrounded by $M'$ and $M''$ in future backups. The rationale is that
%%backup updates  cluster together and affect a few regions of chunks, while
%%the remaining large stretch of chunks (in backup streams) remain unchanged.
%%We adapt this characteristics to frequency analysis. Our insight is that if
%%$M$ is the underlying plaintext of a ciphertext chunk $C$, then $M$ and $C$
%%are likely to have similar (relative) frequency distribution on the
%%%co-occurrences of their surrounding chunks. We propose to adjust frequency
%%ranking and filter out unreasonable inference results based on the relative
%%frequency distribution. The distribution-based attack incorporates the
%%(distribution-based) frequency ranking with locality-based loop \cite{li17}
%%to iteratively infer more chunks.

%%The distribution-based attack assumes the leakage of the logical orders of
%%chunks. Specifically, the adversary has the knowledge about the position, in
%%which each chunk appears in the file data before deduplication.

%%In addition to chunk frequencies, we consider the presence of chunk size leakage.  We propose the {\em size-based attack} to extract plaintext information of the chunks yielded by {\em variable-size chunking}, which has already been used in practical systems such as LBFS \cite{muthitacharoen01} and Deep Store \cite{you05} to address boundary-shift problem. Specifically, variable-size chunking computes the Rabin fingerprint \cite{rabin81} based on a sliding window of data content, and places a chunk boundary when the resulting fingerprint matches a specific pattern. In other words, different chunks may have different chunk sizes due to their possibly distinct content patterns. Thus, we group all available chunks by chunk size, and launch frequency analysis through the chunks that have the same size. Our trace-driven evaluation shows that the size-based attack correctly infers up to 31.3\% of plaintext chunks in the real-world FSL dataset (see Section~\ref{sec:dataset}).

%% . In other words, variable-size chunking generate chunks based on original content so as to address the problem of boundary shift. Our insight is different chunks possibly have different sizes in the setting. We can group all available chunks by their sizes, and launch attack on each chunk group, separately.  
%% about the order of each chunk in original input files.
%% that expands threat to both variable-size and fixed-size chunks.

%% Based on the necessary requirement, we propose distribution-based ranking  
% % primitive 
%% adjust the ranking of frequency analysis, and filter out unreasonable
%% inference results. The distribution-based attack     
%%to improve the effectiveness of classical frequency analysis.

%% has an inference precision of 64.7\% to infer up to 21.2\% of original FSL backup data. For comparison, with the same auxiliary knowledge, the prior locality-based attack \cite{li17} achieves the corresponding precision and rate of only 34.8\% and 15.2\%, respectively. Another advantage is that the effectiveness of the distribution-based attack is less affected by the frequency correlations between the auxiliary and target chunks. For example, when we use a less correlated auxiliary dataset, this only leads to a limited inference rate degradation of 1.4\%.

%% In addition, we observe that the distribution-based attack mainly threatens the rarely-update large-size files, and it can infer up to XXX\% of corresponding original content.

%%\paragraph{Attack using generic order:}
%%We consider to relax the required  knowledge of the distribution-based attack. We assume that the adversary learns the (generic) order information in a {\em coarse-grained unit}, in which a number of chunks appear together as a set; while the adversary cannot identify the accurate order of any chunk in each set.   
%%
%%To exploit the (relaxed) adversarial knowledge, we propose the {\em
%%clustering-based attack}, which builds on {\em similarity}
%%\cite{li17,qin17,xia11,bhagwat09}. Specifically, similarity states that two
%%sets of chunks have the same minimum cryptographic hash (i.e., {\em
%%MinHash}) over their elements if and only if they have a large
%%fraction of common chunks \cite{broder97}. Prior approaches
%%\cite{li17,qin17,xia11,bhagwat09} apply similarity to improve the storage
%%efficiency of near-exact deduplication, while we adapt it into inference
%%attack: suppose $S_{\rm a}$ and $S_{\rm t}$ are the sets of plaintext and
%%ciphertext chunks, respectively; our insight is that if the MinHash
%%derived from the underlying plaintext chunks of $S_{\rm t}$ is identical
%%with that of $S_{\rm a}$, then the plaintexts of the ciphertext chunks in
%%$S_{\rm t}$ are likely to be in $S_{\rm a}$.
%%Thus, we can use $S_{\rm a}$ as the auxiliary information, and launch frequency analysis to infer the chunks corresponding to $S_{\rm t}$.
%%
%%The effectiveness of the clustering-based attack depends on how chunks are
%%grouped in each set. We observe that the clustering-based attack is severe for
%%some special workloads, such as the virtual machine (VM) disk images that
%%store data aligned with block boundaries and are commonly chunked into
%%fixed-size chunks for deduplication \cite{jin09}. Our trace-driven evaluation
%%shows that the clustering-based attack infers up to 18.1\% plaintext chunks in
%%the experimental VM dataset.

\section{Summary of Contributions}

We summarize the main contributions of the paper. 
%
\begin{itemize}[leftmargin=*]
\item
We present two novel frequency analysis attacks against encrypted
deduplication.  In addition to exploiting the leakage of frequencies due to
the deterministic nature of encrypted deduplication, both attacks exploit the
characteristics of deduplication workloads to increase the severity of
frequency analysis.
\item
We evaluate our frequency analysis attacks with several real-world datasets,
including long-term backups \cite{sun16,FSL14}, Windows file system snapshots
\cite{meyer11}, and VM disk images \cite{li15,qin17}.  We present new
observations based on our evaluation, and further analyze the security
implications of how our frequency analysis attacks bring actual damages. 
\item 
We discuss possible countermeasures to mitigate the information leakage in
encrypted deduplication.  
\end{itemize}

The remainder of the paper proceeds as follows. 
Section~\ref{sec:background} presents the basics of encrypted deduplication.
Section~\ref{sec:threat} defines the threat model. 
Sections~\ref{sec:distribution-attack} and \ref{sec:clustering-attack}
present two new frequency analysis attacks against encrypted deduplication.
Section~\ref{sec:experiment} presents our trace-driven evaluation results.
Section~\ref{sec:countermeasure} discusses the countermeasures against
information leakage. Section~\ref{sec:related} reviews related work, and
finally, Section~\ref{sec:conclusion} concludes the paper.

%under a precision of 76.8\%.

% \begin{table}
% 	\centering
% \caption{Summary of inference attacks against encrypted deduplication}
% 	\vspace{-3pt}
% 	\small
% 	\begin{tabular}{@{}p{2.15cm}p{1.2cm}p{.3cm}p{.5cm}p{1.1cm}l@{}}
% \toprule
% \multirow{2}{*}{\bf Objectives} & \multicolumn{3}{c}{\bf Exploiting Leakages} & \multirow{2}{*}{\bf Chunking} & \multirow{2}{*}{\bf Where} \\ \cmidrule{2-4}
% 				  &   {\bf Frequency}    &   {\bf Size}    &   {\bf Order}   &                   &                   \\
% \midrule
% File Existence &       &  \checkmark  &      & Var-size                  & \cite{ritzdorf16} \\ 
% 	Chunk Recovery &  \checkmark  &  \checkmark  &      & Var-size                  & Section~\ref{sec:bucket_attack} \\ 
% 	Chunk Recovery &  \checkmark  &    &   \checkmark  & All                  & \cite{li17}, Section~\ref{sec:distribution_attack} \\ 
% 	Content Recovery &  \checkmark  &    &   Relax  & All                  & Section~\ref{sec:two_stage_attack} \\ 
%  \bottomrule
% \end{tabular} \medskip

% Note: we do not include (i) frequency analysis due to its low severity \cite{li17} and (ii) side-channel attack \cite{mulazzani11,halevi11,harnik10} as it only occurs in client-side and cross-user deduplication.
% \end{table}

\chapter{Background}
\label{sec:background}

In this section, we present the basics of both plain and encrypted
deduplication approaches. 
% We motivate why encrypted deduplication remains
% vulnerable.

\begin{figure}[t]
\centering
\includegraphics[width=.48\textwidth]{pic/dedup-view.pdf}
\caption{Overview of  deduplication workflow.}
\label{fig:dedup-view}
\end{figure}

We focus on {\em chunk-based deduplication}, which operates at the granularity
of small-size data units called {\em chunks}.  Figure~\ref{fig:dedup-view}
summarizes the deduplication workflow.  Specifically, a storage system first
partitions a file (e.g., backup) of a client into {\em logical chunks} via
some {\em chunking} procedure, such that each logical chunk is uniquely
identified by the cryptographic hash of its content called a {\em tag} (a.k.a.
fingerprint).  Two logical chunks are said to be {\em identical} if they have
the same tag, while the likelihood that distinct logical chunks have the same
tag is practically negligible \cite{black06}.  The storage system stores only
a copy of identical logical chunks as a {\em physical chunk}, and each
identical logical chunk refers to the same physical chunk via small-size
references.

Chunk-based deduplication is more fine-grained than whole-file deduplication,
and hence has higher storage efficiency in general.  We can further choose
either {\em fixed-size} or {\em variable-size} chunking for deduplication.
Fixed-size chunking partitions file data into equal-size (logical) chunks,
while variable-size chunking (a.k.a. content-defined chunking) often specifies
chunk boundaries in a content-dependent manner (e.g., via Rabin fingerprinting
\cite{rabin81}) and partitions file data into variable-size chunks.
Fixed-size chunking is simple and fast, while variable-size chunking maintains
storage efficiency in the face of content shifts since the majority of chunks
remain unchanged even the file has added or removed some content.
Variable-size chunking is often used in backup systems (e.g.,
\cite{zhu08,lillibridge09}), yet fixed-size chunking is shown to be effective
for some workloads (e.g., VM images \cite{jin09}).  Our work addresses both
fixed-size and variable-size chunking approaches.

{\em Encrypted deduplication} addresses chunk confidentiality in an
outsourcing environment (e.g., cloud storage), while preserving deduplication
effectiveness.  Traditional symmetric encryption requires that multiple
clients encrypt their file data by their (distinct) secret keys, thereby
transforming identical chunks into distinct encrypted chunks that can no
longer be deduplicated.  {\em Message-locked encryption (MLE)}
\cite{bellare13a} formalizes encrypted deduplication.  The baseline MLE
instantiation derives a symmetric key (called the {\em MLE key}) based on the
content of each {\em plaintext} (e.g., a logical chunk in chunk-based
deduplication), and encrypts the plaintext using the MLE key to form a {\em
ciphertext} (e.g., an encrypted logical chunk).  Thus, MLE ensures that
identical plaintexts are encrypted to identical ciphertexts.  Finally, the
storage system derives the tag from each ciphertext and performs
deduplication.

MLE can be realized as different instantiations (see Section~\ref{sec:related}). The
most popular one is convergent encryption (CE) \cite{douceur02}, which has
been implemented in a wide variety of storage systems (e.g., 
\cite{adya02,elephantdrive,mega,gnunet,freenet,cryptosphere,cox02,storer08,
anderson10}).  The main idea of CE is to derive the MLE key from the
cryptographic hash of the content of each plaintext.  Note that some MLE
instantiations \cite{bellare13a} allow identical plaintexts to be encrypted
into distinct ciphertexts.  Nevertheless, they ensure that the tags are still
derived from the plaintexts, so that they can perform deduplication by
checking the equality of tags.

Existing MLE instantiations all build on the notion {\em deterministic
encryption} to ensure that the ciphertexts (or the tags) are deterministically
derived from the plaintexts, so as to preserve deduplication effectiveness as
opposed to traditional symmetric encryption.  While deterministic encryption
provides confidentiality guarantees, in this paper, we argue that such a
deterministic nature can be exploited by an adversary to infer the original
plaintext from a given ciphertext.

%Today, MLE \cite{bellare13a} and its variants \cite{douceur02, bellare13a, bellare13b, li15} have been implemented in various practical systems \cite{cryptosphere,elephantdrive, mega, adya02,freenet, wilcox-ohearn08, gnunet,li15,anderson10,cox02, armknecht15, shah15, qin17}.

% from these distinct ciphertext chunks, and cannot detect whether the original content underlying these ciphertext chunks are identical.

% The server cannot detect whether the original content underlying these  ciphertext chunks are identical; otherwise it violates the security guarantee of symmetric encryption.

% For security concerns, users want their data to be encrypted before outsourcing.

% Figure~\ref{fig:dedup-view} presents an overview of {\em encrypted deduplication} \cite{bellare13a}, where multiple clients outsource data to a remote storage system that performs {\em deduplication} across  clients to save storage space. Specifically, each client first partitions file data into {\em logical chunks}, each of which is with either fixed or variable sizes. 
% Fixed-size chunking achieves high computational performance, while variable-size chunking defines chunk boundaries based on  content so as to be robust against content shift.

% Then, the client protects each chunk via encryption. However, in traditional symmetric encryption, clients use their own (distinct) secret keys for encryption, and transform the same plaintext chunks to different ciphertext chunks. The storage system cannot detect whether the original content underlying these ciphertext chunks are identical; otherwise it violates the security guarantee of symmetric encryption.

% % To save space, the storage system performs {\em deduplication} across all its users.

% Specifically, if two users upload the same message $M$, the server can detect this and store only a single copy of $M$. We focus on {\em chunk-based deduplication}, which partitions file data into fixed-size or variable-size chunks. Specifically, fixed-size chunking achieves high computational performance, while variable-size chunking defines chunk boundaries by content so as to be robust against content shift. Then, it removes duplicates in the graularity of chunk. In this paper, we use the term ``message'' and ``chunk'' interchangeably to refer to the fine-grained data unit operated by deduplication.

% Deduplication is a technique that reduces storage space by eliminating content redundancies. Figure~\ref{fig:dedup-view} presents the logical view of a deduplication-enabled storage system, which operates at the granularity of {\em chunk} and removes the chunks that have identical content with some already stored chunks. 
% Specifically, it first partitions file data into an ordered sequence of {\em logical chunks}, each of which is with either fixed or variable sizes. 
% Fixed-size chunking achieves high computational performance, while variable-size chunking defines chunk boundaries based on  content so as to be robust against content shift. Then, it only stores the chunks (called {\em physical chunks}) that have unique content, and refers other copies of a stored chunk via small-size references.

% Encrypted deduplication aims to address the chunk-level confidentiality of deduplication in an outsourcing environment (e.g., cloud storage). Consider a scenario where multiple users outsource storage to a remote third-party cloud service, which apply deduplication across its users to save storage space. For security concerns, users want their data to be encrypted before outsourcing. However, in traditional symmetric encryption, users use their own (distinct) secret keys for encryption, and  transform the same plaintext chunks to different ciphertext chunks. The server cannot detect whether the original content underlying these  ciphertext chunks are identical; otherwise it violates the security guarantee of symmetric encryption.

% {\em Message-locked encryption (MLE)} \cite{bellare13a} is a cryptographic primitive to achieve encrypted deduplication. It derives a symmetric key $K_M$ (called {\em MLE key}) based on the content of each message $M$ (e.g., $K_M$ is the cryptographic hash of $M$ \cite{douceur02}), and further uses the MLE key $K_M$ to encrypt $M$. This makes the ciphertext only depend on the plaintext, from which it is encrypted. The server can detect duplicates by checking the equality of ciphertexts (e.g., comparing their cryptographic hashes). Today, MLE \cite{bellare13a} and its variants \cite{douceur02, bellare13a, bellare13b, li15} have been implemented in various systems \cite{cryptosphere,elephantdrive, mega, adya02,freenet, wilcox-ohearn08, gnunet,li15,anderson10,cox02, armknecht15, shah15, qin17}  for encrypted deduplication.

% Consider a scenario where multiple users outsource storage to a remote third-party cloud service. To save space, the cloud server performs {\em deduplication} across all its users. Specifically, if two users upload the same message $M$, the server can detect this and store only a single copy of $M$. We focus on {\em chunk-based deduplication}, which partitions file data into fixed-size or variable-size chunks. Specifically, fixed-size chunking achieves high computational performance, while variable-size chunking defines chunk boundaries by content so as to be robust against content shift. Then, it removes duplicates in the graularity of chunk. In this paper, we use the term ``message'' and ``chunk'' interchangeably to refer to the fine-grained data unit operated by deduplication.

% that have the same fingerprint are {\em identical}, since the probability of fingerprint collision (i.e., different chunks lead to the same fingerprint) is negligible in practice \cite{black06}. A deduplication system stores only a single copy of identical chunks, while referring the other copies by small-size references.

% It performs chunking to partition input data into fixed-size or variable-size chunks. Fixed-size chunking generates all chunks that have a uniform chunk size; on the other hand, variable-size chunking, configured by the maximum, average and minimum chunk sizes, defines the boundary of each chunk (e.g., via Rabin fingerprinting \cite{rabin81}) through matching a specific content pattern. This makes it robust against content shift.

% \subsection{Leakage Channels}
% \label{sec:leakage}

% MLE applies {\em deterministic encryption}, and exposes some information, called {\em leakage}, about plaintext chunks. The fundamental leakage is {\em chunk frequency}, which is the number of times that each plaintext chunk appears in the original file data. Although the frequency leakage has been acknowledged in prior works \cite{abadi13,bellare15,ritzdorf16,li17}, it is hard to be prevented, since this breaks the one-to-one mapping between plaintext and ciphertext chunks, and leads to the degradation of deduplication performance \cite{abadi13} or storage efficiency \cite{li17} (see \S\ref{sec:countermeasure}).

% sacrifices security and exposes some information,  
% that has been . Specifically, MLE encrypts identical plaintext chunks into identical ciphertext chunks, and hence leaks  We

% Additional leakages \cite{ritzdorf16, li17} have been explored due to the careless deployment of encrypted deduplication. First, some deduplication systems \cite{xia11,lillibridge09,zhu08} aim for high performance, and operate chunks in the same order that they appear in plaintext files; this exposes the {\em logical order}, based on which one can identify the position of each chunk in input files. Second, some practitioners \cite{douceur02, wilcox-ohearn08, bellare13b} avoid storage overhead, and do not pad ciphertext chunks with any additional data; this exposes the {\em chunk size}, since the ciphertext chunks have the same number of blocks with corresponding plaintext chunks.

% The risks posed by the above leakage profiles have not been scrutinized except \cite{ritzdorf16, li17}, which build attacks to infer the plaintext contents of ciphertext chunks \cite{li17} or to guess if particular files have already been stored \cite{ritzdorf16}. On the other hand, it remains unexplored that what is the security implication of the inferred information. This paper presents a comprehensive study of the leakage of encrypted deduplication, and we seek to answer the following questions: {\em (i) how to enable primitives to infer plaintext contents in various leakage settings, and (ii) what is the concrete implication from the inferred contents?}

% \subsection{Frequency Analysis}
% \label{sec:freqanalysis}

% {\em Frequency analysis} is a well-known cryptanalysis primitive that illustrates the weakness of deterministic encryption. Suppose an adversary has access to a target set of ciphertexts (that are encrypted by deterministic encryption) and an auxiliary set of plaintexts. To launch frequency analysis, it sorts ciphertexts and plaintexts by their frequencies, respectively, and relates each ciphertext with the plaintext that has the same frequency rank. 
% Prior works have exploited different leakage profiles (e.g., access pattern \cite{kellaris16, lacharite18, islam12, zhang16b}, numeric order \cite{grubbs17, bindschaedler17, durak16}, query pattern \cite{cash15}) to examine frequency analysis in various applications (e.g., database \cite{naveed15}, keyword search \cite{grubbs16,pouliot16}). This paper shows how to strengthen the effectiveness of frequency analysis with practical leakages in deduplication.

%The locality-based attack \cite{li17} targets deduplication, and increases the coverage of inferred chunks with an additional leakage of logical order.

% strengthened the effectiveness of frequency analysis in different applications with various leakages.

% Frequency analysis has been applied in prior works \cite{grubbs17,bindschaedler17,zhang16b,grubbs16,kellaris16,pouliot16,durak16,naveed15,cash15,islam12,lacharite18} to construct inference attacks. Some attacks target structured relational data in database, by classical frequency analysis \cite{naveed15}, exploring correlations or orderings of table columns, .

% % Naveed {\em et al.} \cite{naveed15} propose $l_p$-optimization that equivalents classical frequency analysis.

%  studies the security of encrypted database, and reduces classical frequency analysis to  problem.

% on rational data

% They either

% The effectiveness of frequency analysis depends on the correlation between the auxiliary set and the target set. It performs well, only when the frequency of ciphertext is correlated with that of the corresponding plaintext. In addition, some ciphertexts (resp. plaintexts) may have the same frequencies, and form {\em ties} during sorting. How to break ties affects the result of frequency analysis.

% This paper aims to apply frequency analysis to explore the vulnerabilities of encrypted deduplication. Our focus is not to address how to obtain correlated plaintexts for inference attack. Instead, we develop strategies to break ties effectively, so as to demonstrate the severity of frequency analysis.

% comment on March 15
% Deduplication eliminates the redundant copies of identical {\em chunks} for storage efficiency. It performs chunking to partition input data into fixed-size or variable-size chunks. Fixed-size chunking generates all chunks that have a uniform chunk size; on the other hand, variable-size chunking, configured by the maximum, average and minimum chunk sizes, defines the boundary of each chunk (e.g., via Rabin fingerprinting \cite{rabin81}) through matching a specific content pattern. This makes it robust against content shift. Each chunk is identified based on the cryptographic hash (known as {\em fingerprint}) of the content of the chunk. We consider the chunks that have the same fingerprint are {\em identical}, since the probability of fingerprint collision (i.e., different chunks lead to the same fingerprint) is negligible in practice \cite{black06}. A deduplication system stores only a single copy of identical chunks, while referring the other copies by small-size references.

% Encrypted deduplication ensures all chunks are encrypted {\em before} deduplication, while the redundant copies of original chunks can still be removed. An elegant approach of resolving this tension is {\em message-locked encryption (MLE)} \cite{bellare13a}, which encrypts each chunk with a key derived from the content of the chunk. This maps identical plaintext chunks to identical ciphertext chunks that can be detected by deduplication. Today, various systems \cite{cryptosphere,elephantdrive, mega, adya02,freenet, wilcox-ohearn08, gnunet,li15,anderson10,cox02, armknecht15, shah15, qin17} (see \S\ref{sec:related}) have applied MLE \cite{bellare13a} or its variants \cite{douceur02, bellare13b, li15} for encrypted deduplication in practice.

% However, the practical encrypted deduplication systems expose some information, called {\em leakage}, about the original chunks. The fundamental leakage is {\em chunk frequency} that has been acknowledged in prior works \cite{abadi13,bellare15,ritzdorf16,li17}. Specifically, MLE encrypts identical plaintext chunks into identical ciphertext chunks, and hence leaks the number of times that each original chunk appears in the input data. We argue that it is hard to prevent the frequency leakage, since this breaks the one-to-one mapping of plaintext and ciphertext chunks and hence degrades deduplication performance \cite{abadi13} or storage efficiency \cite{li17}.

% Additional leakages \cite{ritzdorf16, li17} have been explored due to careless deployment of encrypted deduplication. First, some deduplication systems \cite{zhu08, xia11} aim for high performance, and require to operate chunks in the same order that they appear in original files; this exposes the {\em logical order}, based on which one can identify the position of each chunk in input files. Second, some practitioners \cite{douceur02, wilcox-ohearn08, bellare13b} avoid storage overhead and do not pad ciphertext chunks with any additional data; this exposes the {\em chunk size}, as the ciphertext chunks should have the {\em same} number of blocks with the original plaintext chunks.

% The risks posed by leakage have not been scrutinized except \cite{ritzdorf16, li17}, which build {\em attack primitives} to infer original plaintext chunks \cite{li17} or the existence of particular files \cite{ritzdorf16} against encrypted deduplication. It remains unexplored of how to launch practical attacks based on the inferred information. This paper presents a comprehensive study of the leakage of encrypted deduplication, and we seek to answer the following two questions: {\em (i) how to enable primitives to infer original contents in various leakage settings, and (ii) what is the concrete implication of the practical attack that builds on the inferred contents?}

% The present paper studies the leakage of SE in order to understand its practical security. We consider a range of threats including IKK’s query-identification setting, and against various approaches to building SE.

% To this end, we pose the following question: how to enable secure and lightweight rekeying, while preserving the deduplication capability?

% the work of IKK. The current literature leaves a practitioner with few concrete recommendations for configuring and deploying SE. The risk is not merely abstract; several deployments of SE may be easily broken depending on how they are used.

% Prior works

% to our best knowledge, none of schemes/systems attempt to protect the processing order of chunks. For performance reasons, some deduplication systems (e.g., DDFS \cite{zhu08} and SiLo \cite{xia11}) even require to operate chunks in the same order that they appear in the original logical files. This exposes the {\em logical order}, based on which one can identify the position of each chunk in the input file.

% In addition to the frequency leakage, practitioners configure and deploy encrypted deduplication carelessly, and possibly .

% In the following, we discuss a variety of leakages observed in the state-of-the-art encrypted deduplication schemes/systems.

% \begin{itemize}[leftmargin=10pt]
% \item \textbf{Frequency leakage:} 
% Encrypted deduplication schemes apply {\em deterministic encryption} (e.g., MLE), where identical plaintext chunks will be encrypted into identical ciphertext chunks. This leaks the {\em frequency information} (i.e., the number of times that the original chunk appears in the input data) of each chunk. The frequency leakage is fundamental to MLE, as it is hard to be prevented (otherwise, leading to significant degradation of deduplication performance \cite{abadi13} or storage efficiency \cite{li17}).

% \item \textbf{Size leakage:} 
% To mitigate storage overhead, practitioners are suggested to implement chunk encryption without padding schemes \cite{ritzdorf16}. For example, Farsite \cite{douceur02}, Tahoe-LAFS \cite{wilcox-ohearn08} and DupLESS \cite{bellare13b} apply AES in counter mode, yet they do not pad ciphertext chunks with any additional data. This leaks the {\em chunk size information} \cite{ritzdorf16}, as the ciphertext chunks should have the {\em same} number of blocks with the original plaintext chunks.  
% The leakage is more severe for variable-size chunks, whose boundaries are identified (e.g., via Rabin fingerprinting \cite{rabin81}) by matching a specific content pattern. A variable-size ciphertext chunk leaks the information that only the last a few bytes (determined by a sliding window) of its original chunk are likely to match the public content pattern. Two ciphertext chunks with distinct sizes further expose the information that they are mapped from different plaintext chunks.

% \item \textbf{Order leakage:}
% Leakage occurs in deploying encrypted deduplication carelessly. \end{itemize}

% This paper studies the leakage of encrypted deduplication. We present a family of new inference attacks that exploit the exposed information to learn the original content of encrypted chunks.

\chapter{Threat Model}
\label{sec:threat}

In this section, we formulate the threat model for our proposed frequency
analysis attacks against encrypted deduplication.

\section{Definitions}

We first provide the definitions for our threat model. We model a plain file
as an ordered list of $n$ {\em logical plaintexts} (i.e., logical chunks
before deduplication), denoted by $\mathbf{M} = \langle \hat{M}^{(1)},
\hat{M}^{(2)}, \ldots, \hat{M}^{(n)}\rangle$.  Each logical plaintext
$\hat{M}^{(i)}$ (where $1\le i\le n$) is encrypted via MLE into the
corresponding ciphertext $\hat{C}^{(i)}$, and all encrypted results of
$\mathbf{M}$ form a stream of $n$ {\em logical ciphertexts} $\mathbf{C} =
\langle \hat{C}^{(1)}, \hat{C}^{(2)}, \ldots, \hat{C}^{(n)} \rangle$.  Note
that the logical ciphertexts in $\mathbf{C}$ are also ordered to reflect the
deduplication processing sequence of an encrypted deduplication storage
system.

Identical logical plaintexts and ciphertexts may appear at different positions
of $\mathbf{M}$ and $\mathbf{C}$, respectively.  We denote a unique plaintext
as $M$ (uniquely identified by its tag), which is encrypted via MLE to the
corresponding unique ciphertext $C$.  Each $M$ (resp. $C$) corresponds to one
or multiple identical copies of $\hat{M}^{(i)}$ (resp. $\hat{C}^{(i)}$).

% of $\mathbf{M}$ is
% independently encrypted into corresponding ciphertext $C$ via MLE, and all encrypted results

% A unique plaintext (or plaintext for short) $M$ has one or more copies in $\mathbf{M}$  
% Identical plaintexts may have multiple copies in $\mathbf{M}$, and we introduce unique plaintext  
% We define a unique plaintext as the plaintext that has unique content among other plaintexts of $\mathbf{M}$    
% Let $M$ and $C$ be a
% plaintext and its corresponding ciphertext, respectively; both of them are in
% units of chunks defined by deduplication.  We model a plain file before
% deduplication as an {\em ordered} list of $n$ plaintexts, denoted by
% $\mathbf{M} = \langle M^{(1)},  M^{(2)}, \ldots, M^{(n)}\rangle$.  Identical
% plaintexts may appear at different positions of $\mathbf{M}$, say $M^{(i)} =
% M^{(j)}$ for some $1\le i \neq j\le n$.   
% % Also, each plaintext can have the
% same or different chunk sizes due to fixed-size or variable-size chunking,
% respectively, and let $|M|$ denote the size of a plaintext $M$.  
% Let $M$ and $C$ denote a
% plaintext (i.e., a logical chunk before encryption) and its corresponding
% ciphertext (i.e., a logical chunk after encryption).  We model a plain file

\section{Adversarial Goals and Assumptions}
\label{sec:assumptions}

We consider an adversary that aims to infer a set of ciphertext-plaintext
pairs, denoted by \{$(C, M)$\}, with two specific goals:
\begin{itemize}[leftmargin=*]
\item
{\bf High inference rate:} A large fraction of correct ciphertext-plaintext pairs
are inferred, among all correct ciphertext-plaintext pairs (i.e., high recall or
low false negative rates in statistical terms).
\item
{\bf High inference precision:} A large fraction of ciphertext-plaintext pairs
are correct, among all inferred ciphertext-plaintext pairs (i.e., high precision
or low false positive rates in statistical terms).
\end{itemize}

We assume that the adversary is {\em honest-but-curious}, such that it can
passively monitor the stream of ciphertexts $\mathbf{C}$ being written to the
storage system and exploit different types of leakage information from
$\mathbf{C}$ (see Section~\ref{sec:leakage}).  Given the available leakage
information, the adversary aims to infer the original plaintext of each
ciphertext in $\mathbf{C}$ via a {\em ciphertext-only} attack.  It is possible
that the adversary knows a limited subset of ciphertext-plaintext pairs to
launch a known-plaintext attack, which further strengthens attack severity
\cite{li17}.  We do not consider the known-plaintext attack in this paper.

%We treat $\mathbf{C}$ as the {\em view} by the
%adversary and model different properties of the view

We assume that the adversary does not have access to any {\em metadata} that
contains the information about how chunks are operated and stored, as we do
not apply deduplication to the metadata and hence it can be protected by
traditional symmetric encryption.  Also, we assume that the adversary does not
have {\em active} capabilities, which can be independently prevented by
existing approaches. One example is that a malicious client may claim the
ownership of unauthorized files in client-side deduplication
\cite{harnik10,halevi11,mulazzani11}; it can be addressed by
proof-of-ownership \cite{halevi11,xu13,pietro12} or server-side deduplication
\cite{harnik10,li15}.  Another example is that a malicious storage system may
modify stored data; it can be detected by remote integrity checking
\cite{juels07,ateniese07}.

% In addition, $\mathcal{A}$ does not aim to infer if
% particular files have been stored \cite{harnik10, ritzdorf16}. Instead, we
% study the security implication based on the inferred contents over different
% types of files (see \S\ref{sec:case}).. 
% Intuitively, we want to guarantee that what $\mathcal{A}$ can learn is some
% well defined leakage $\mathcal{L}$, which includes the frequency, logical
% order and/or chunk size (\S\ref{sec:leakage}). 
% Note that $\mathcal{A}$ is specific to a {\em passive} adversary with content
% inference in mind. We do not assume $\mathcal{A}$ has {\em active}
% capabilities,

\section{Leakage Channels}
\label{sec:leakage}

We consider three types of leakage channels in encrypted deduplication storage
that enable an adversary to infer information:
\begin{itemize}[leftmargin=*]
\item
{\bf Frequency:}  Due to the deterministic nature of encrypted deduplication,
the frequency of each ciphertext in $\mathbf{C}$ before deduplication (i.e., 
the number of duplicate copies) can be mapped to that of its corresponding
plaintext in $\mathbf{M}$. 
% the size of each ciphertext in
% $\mathbf{C}$ is approximately equal to that of its corresponding plaintext in
% $\mathbf{M}$. In other words, the exact number of blocks (e.g., that are of size 16 bytes) in ciphertexts   
% the exact number of blocks in the plaintext equals the number of blocks in the ciphertext
% {\bf PC: if block cipher is used, it's not necessary that the
% plaintext has the same size as its ciphertext}.
%(e.g., \cite{douceur02, wilcox-ohearn08, bellare13b}) do not pad ciphertexts
%with additional data to avoid storage overhead, 
\item
{\bf Order:}  Some storage systems (e.g., \cite{xia11,lillibridge09,zhu08})
apply deduplication to the chunks in the same order as they appear in the
original file.  Thus, the order of ciphertexts in $\mathbf{C}$ can be mapped
to that of plaintexts in $\mathbf{M}$. 
\item
{\bf Size:}  Variable-size chunking (see Section~\ref{sec:background}) leads
to different chunk sizes of the ciphertexts.  If such ciphertexts are not
padded (to avoid storage overhead \cite{ritzdorf16}), the size of a ciphertext
in $\mathbf{C}$ can be mapped to that of its corresponding plaintext in
$\mathbf{M}$.    
\end{itemize}

%We also consider other leakage channels that are specific to real-world
%deduplication storage systems. First, {\em order leakage} exposes the logical
%order of each plaintext, and it is available for the systems
%\cite{xia11,lillibridge09,zhu08} that aim for high performance and operate
%the deduplication of chunks in the same order as these chunks appear in
%original files; this implies that the logical order of ciphertext in
%$\mathbf{C}$ exactly reflects that of its corresponding plaintext. Second,
%{\em size leakage} exposes the chunk size of each plaintext, since some
%systems \cite{douceur02, wilcox-ohearn08, bellare13b} avoid storage
%overhead and do not pad ciphertexts with any additional data; this
%implies that the size of ciphertext in $\mathbf{C}$ exactly equals that
%of its corresponding plaintext.

In addition, the adversary has access to some {\em auxiliary information} that
presents the ground truth about the data characteristics correlated with
$\mathbf{M}$. Note that the availability of auxiliary information is necessary
for any inference attack \cite{kumar07,li17,grubbs17,zhang16b,kellaris16,ritzdorf16,naveed15,cash15,islam12}.
In this work, we consider the auxiliary information as an ordered list of
previously known plaintexts (e.g., old user backups or VM disk images),
denoted by $\mathbf{A}$.  Clearly, the attack severity depends on the
correlation between $\mathbf{A}$ (i.e., the previously known plaintexts) and
$\mathbf{M}$ (i.e., the plaintexts that are to be inferred).  Our focus is not
to address how an adversary can obtain auxiliary information, possibly due to
careless data release \cite{careless-release}, stolen storage devices
\cite{stolen-device}, and cloud leakage \cite{cloud-leakage}. Instead, given
such information, we investigate how the available auxiliary information,
combined with the leakage channels, bring information leakage from encrypted
deduplication.

We focus on frequency analysis \cite{alkadit92} as the attack methodology.
Classical frequency analysis sorts the unique ciphertexts in $\mathbf{C}$ and
the unique plaintexts in $\mathbf{A}$ by {\em frequency} (i.e., the number of
identical copies corresponding to each unique ciphertext or unique plaintext). 
It then relates each unique ciphertext in $\mathbf{C}$ with the unique
plaintext in $\mathbf{A}$ that has the same frequency rank. In the following
sections, we design sophisticated frequency analysis attacks against encrypted
deduplication.

% Frequency analysis is a cryptanalysis primitive to relate the ciphertexts in $\mathbf{C}$  with the plaintexts in $\mathbf{M}$. Specifically, it sorts ciphertexts and plaintexts by their frequencies in $\mathbf{C}$ and $\mathbf{A}$, respectively, and maps each ciphertext to the plaintext that has the same frequency rank. Building on the classical version of frequency analysis, we show how to exploit leakage channels to strengthen its severity against encrypted deduplication.

% infer ciphertext-plaintext pairs from $\mathbf{C}$ and $\mathbf{A}$. 
 % Specifically, the adversary

% It performs well, only when the frequency of ciphertext is correlated with that of the corresponding plaintext. 
% The more correlated to $\mathbf{M}$,

% Our focus is not to address its availability, which is due to careless data release \cite{careless-release}, stolen storage devices \cite{stolen-device}, and cloud leakage \cite{cloud-leakage}. Instead, we show how an adversary can launch inference attacks based on the available auxiliary information $\mathbf{A}$.

% Our focus is not to address how to obtain accurate auxiliary information, which we pose as future work; instead, given the available auxiliary information, we study how an adversary can design a severe attack based on frequency analysis and how we can defend against the attack
% Some available auxiliary information has been demonstrated to be necessary for inference attacks  and we consider the auxiliary information $\mathbf{M}$ as a complete user backup, file system snapshot or VM disk image in plaintext. The rationale of its availability is that the adversary can obtain the original data from  We emphasize that the auxiliary information $\mathbf{M}$ does not need to be identical with the original file of $\mathbf{C}$. In other words, $\mathbf{M}$ may not have the
% same number of chunks with $\mathbf{C}$, or its $i$-th chunk $M^{\langle i \rangle}$ may not be the plaintext of $C^{\langle i \rangle}$ or even not mapped into $\mathbf{C}$. 
% {\bf PC: give the background on frequency analysis.}

% We assume that the adversary can take advantage of some   for attacks. The auxiliary information , and it has been demonstrated for necessity in inference attacks . In this work,

% In addition, the adversary can exploit other deduplication-specific leakage channels.

% effectiveness of inference attacks. First, we consider {\em size leakage}, meaning that the adversary can derive the size of a plaintext directly based on the corresponding ciphertext: ${\sf s}(C) = |M|$, where $C$ is the encryption of $M$.

% deduplication-specific leakage channels.

% We target inference attacks against {\em backup workloads}, which refer to the copies of primary data (e.g., application states, file systems, and virtual disk images) over time. The recent technology trend \cite{douglis17} suggests to create full backups (that store the complete data of the primary source) over traditional incremental backups (that only store the changes of data since the last full backup), so as to mitigate the overhead in restoring earlier (full) backups. Thus, we focus on inferring information from different versions of full backups (or backups for short) that are created based on the same primary data source at different times.

% They can be created as either weekly full backups (that store the complete data of the primary source) or daily incremental backups (that only store the changes of data since the prior full backup). Informed by the technology trend , we focus on full backups (or {\em backups} for short). Specifically, we aim to infer information from different versions of backups that are created based on the same primary data source yet at different times.

% To launch attacks, we assume that $\mathcal{A}$ is an ``{\em honest-but-curious}'' adversary that can compromise the server hosting deduplication service, while it cannot establish a long-term presence for attack. Intuitively, we want to guarantee that what $\mathcal{A}$ can learn is some well defined leakage $\mathcal{L}$, which includes the frequency, logical order and/or chunk size (\S\ref{sec:leakage}). Formally, we define these leakage channels based on a target victim file $\mathbf{M}_{\rm t}$:

% \begin{itemize}[leftmargin=*]
% 	\item  {\bf Frequency leakage}: $\mathcal{L}_{\rm freq} = \{(C, {\sf freq}(M)): M \in \mathbf{M}_{\rm t}$ and $C = {\sf E}_{K_M}(M) \}$ is a set of chunk-frequency pairs, where $C$ is the encryption of some plaintext chunk $M$ in $\mathbf{M}_{\rm t}$, and each pair $(C, {\sf freq}(M))$ leaks the corresponding frequency of $M$.

% 	\item  {\bf Order leakage}: $\mathcal{L}_{\rm order} = \{(C, {\sf ord}(M)): M\in\mathbf{M}_{\rm t}$ and $C = {\sf E}_{K_M}(M) \}$ associates each ciphertext chunk $C$ with a set ${\sf ord}(M)$ of logical orders, at which the copies of its original chunk $M$ appear in $\mathbf{M}_{\rm t}$. Note that order leakage {\em implies} frequency leakage, since the logical orders of each chunk copy inherently includes the number of times the corresponding chunk appears.

% 	\item  {\bf Size leakage}: $\mathcal{L}_{\rm size} = \{(C, {\sf size}(M)): M \in \mathbf{M}_{\rm t}$ and $C = {\sf E}_{K_M}(M) \}$ is a set of chunk-size pairs, where each pair leaks the size of the original chunk of $C$.
% \end{itemize}

% In addition, $\mathcal{A}$ can take advantage of the {\em auxiliary information} $\mathbf{M}_{\rm a}$ that presents the ground truth about the frequency, size and order information about plaintext chunks. Some available auxiliary information is necessary for inference attacks , and we focus on validating our attacks with the auxiliary information obtained from different types of storage workloads (see \S\ref{sec:dataset}).

% Acquiring the above capabilities, $\mathcal{A}$'s primary goal is to recover the plaintext chunks in the target file $\mathbf{M}_{\rm t}$. More formally, given the leakage $\mathcal{L}$ (that can be some combination of $\mathcal{L}_{\rm freq}$, $\mathcal{L}_{\rm order}$ and $\mathcal{L}_{\rm size}$) and the auxiliary information $\mathbf{M}_{\rm a}$, $\mathcal{A}$ outputs a collection of ciphertext-plaintext chunk pairs $\mathcal{R} = \{ (C, M) \}$: $\mathcal{A}(\mathcal{L}, \mathbf{M}_{\rm a}) \rightarrow \mathcal{R}.$ Each output pair $(C, M)$ indicates $\mathcal{A}$'s guess that relates a ciphertext chunk $C$ with a plaintext chunk $M$.

% identify the ciphertext-plaintext chunk pairs about $\mathbf{M}_{\rm tar}$. More formally, given the leakage $\mathcal{L}$ (that can be some combinations of $\mathcal{L}_{\rm freq}$, $\mathcal{L}_{\rm order}$ and $\mathcal{L}_{\rm size}$), and auxiliary information $\mathbf{M}_{\rm aux}$, $\mathcal{A}$ outputs a collection of ciphertext-plaintext chunk pairs $\mathcal{R} = \{ (C, M) \}$: $\mathcal{A}(\mathcal{L}, \mathbf{M}_{\rm aux}) \rightarrow \mathcal{R}.$ Each pair $(C, M)$ indicates $\mathcal{A}$'s guess that relates a ciphertext chunk $C$ with a plaintext chunk $M$.

% a malicious server may corrupt stored chunks, yet it can be detected by integrity checking mechanisms \cite{juels07,ateniese07};

% and it is a correct inference by $\mathcal{A}$ if $C$ is the actual encryption of $M$, i.e., $(M, C) \in \mathcal{E}$.

% We measure the success of attacks in several ways. The {\em raw inference rate} is the percentage of ciphertext chunks (including duplicates) that are inferred correctly over the total number of ciphertext chunks in the target information. For example, if the adversary correctly infers a ciphertext-plaintext chunk pair $(C, M)$ and the ciphertext chunk $C$ accounts for a fraction of 10\% in the target information, then the raw inference rate will be at least 10\%.

% We assume the adversary can eavesdrop the deduplication processing (e.g., comparison operation of fingerprints) of all ciphertext chunks in a victim file (called {\em target information}); on the other hand, it cannot access related metadata that can be protected by traditional encryption \cite{li17}. 
% the same and different private sources, as well as some public source .

% Note that $\mathcal{A}$ is specific to a passive adversary with content recovery in mind. We do not abstract $\mathcal{A}$ with active capabilities, since these threats can be protected by existing approaches. For example, a malicious server may corrupt stored chunks, yet it can be detected by integrity checking mechanisms \cite{juels07,ateniese07}; a malicious client may cheat owning a particular file \cite{harnik10,halevi11,mulazzani11}, yet it can be addressed by proof of ownership \cite{halevi11} or enforcing server-side deduplication \cite{li15}.

\chapter{Distribution-based Attack}
\label{sec:distribution-attack}

The distribution-based attack exploits the order information of $\mathbf{C}$
and $\mathbf{A}$ to strengthen the effectiveness of frequency analysis.  It
then compares the relative frequency distributions of $\mathbf{C}$ and
$\mathbf{A}$ to reduce the false positive results.  We also show how to
exploit chunk size information to further improve the inference precision.

\section{Background: Locality-based Attack}
\label{sec:prior-attack}

The distribution-based attack builds on the previously proposed {\em
locality-based attack} \cite{li17}, which shows how frequency analysis causes
information leakage in backup workloads.  The locality-based attack considers
{\em full backups} (or backups for short) that are created as the complete
copies of primary data (e.g., application states, file system snapshots, and
VM disk images) on a daily or weekly basis. It aims to infer the
ciphertext-plaintext pairs across different versions of backups.  It assumes
that the auxiliary information $\mathbf{A}$ is derived from some older
backups, and its goal is to infer the plaintexts of the latest backup (i.e.,
$\mathbf{M}$).

The locality-based attack leverages the {\em locality} property
\cite{xia11,zhu08,lillibridge09}, which is a common phenomenon in practical
backup workloads. Specifically, the locality property states that neighboring
chunks tend to co-occur in the {\em same order} across different versions of
backups before deduplication. The main reason is that the updates to each
backup are often clustered in some small regions of chunks, while the
remaining large stretch of chunks appear unchanged or preserve the same order
across different versions of backups.

Based on locality, the locality-based attack exploits the order information to
discover the neighboring information of ciphertexts and plaintexts.
Specifically, for a given unique ciphertext $C$, the attack first identifies
the set of all identical copies $\{\hat{C}^{(i)}\}$.  For each
$\hat{C}^{(i)}$, it considers the left and right {\em neighbors} of
$\hat{C}^{(i)}$, i.e., $\hat{C}^{(i-1)}$ and $\hat{C}^{(i+1)}$, respectively.
It extracts the sets of left and right neighbors into the associative arrays
$\mathbf{L_C}$ and $\mathbf{R_C}$, respectively.  The associative arrays store
the mappings of each unique ciphertext $C$ and its {\em co-occurrence
frequencies} with its left and right neighbors, respectively.   Similarly, the attack also constructs the
associative arrays $\mathbf{L_A}$ and $\mathbf{R_A}$ based on the order
information of $\mathbf{A}$.

The locality-based attack then iterates frequency analysis through the
neighbors of each inferred ciphertext-plaintext pair.  It first applies
frequency analysis to infer a number (parameterized by $u$) of top-frequent
ciphertext-plaintext pairs \{$(C, M)$\} from $\mathbf{C}$ and $\mathbf{A}$.
The inferred results are likely to be {\em real} (i.e., the target ciphertext
is indeed mapped from the inferred plaintext), based on the observation that
the ranks of highly frequent chunks are stable across different versions of
backups.  For each inferred pair $(C, M)$, the attack finds their left and
right neighbors that have the most co-occurrence frequencies with $C$ and $M$,
respectively.  Due to locality, the left and right neighbors of $M$ are likely
to be the original plaintexts of the corresponding left and right neighbors of
$C$, respectively.  Thus, the attack also includes the top-frequent left
(resp. right) neighbors of $C$ and $M$ into the set of the resulting inferred
ciphertext-plaintext pairs.  Finally, the attack procedure iterates until the
neighbors of each inferred ciphertext-plaintext pair are examined.

%It applies frequency analysis to infer new ciphertext-plaintext pairs that
%have the same co-occurrence frequency rank among corresponding neighbors. The
%rationale is the order of chunks is preserved by chunk locality, and the left
%and right neighbors of $M$ are likely to be the original plaintexts of the
%corresponding neighbors of $C$. Thus, the attack further iterates the same
%frequency analysis through the neighbors of these newly inferred
%ciphertext-plaintext pairs, so as to increase attack severity.

%if $u$ is small. The rationale is the ranks of highly frequent chunks are
%stable across backups. On the other hand, a smaller $u$ degrades the coverage
%of inferred ciphertext-plaintext pairs, and we examine the impact of $u$ in
%Section~\ref{sec:experiment-distribution}.

However, the locality-based attack has a major weakness that it  introduces
a high number of false positives (i.e., incorrect ciphertext-plaintext pairs).
Since the main idea of frequency analysis is to map ciphertexts to plaintexts
with the same frequency ranks, any disturbance to frequency ranking (e.g., 
the updates across backups) can lead to incorrect ciphertext-plaintext pairs,
which can in turn comprise the inference of their neighbors.  Although the
locality-based attack is shown to effectively infer a significant fraction of
real ciphertext-plaintext pairs,  the adversary has low confidence to tell
whether each inferred ciphertext-plaintext pair is real or a false positive.

% For example, our evaluation shows although the locality-based attack can correctly infer 15.2\% of ciphertext-plaintext pairs in some case, the false positives take around 65.2\% in its inference results. In other words, the adversary has low confidence in identifying whether the inferred ciphertext-plaintext pairs are correct or not.

% Our observation is frequency analysis essentially dominates the severity of the locality-based attack, yet it is {\em sensitive to frequency ranking}. Specifically, any disturbance (e.g., due to data updates or sorting the tied chunks that have the same frequency) to the frequency rank can greatly degrade the inference accuracy. These incorrectly inferred ciphertext-plaintext chunk pairs will compromise the iterations of their neighboring chunks (see above), and hence lead to low inference rate. 
% Although the authors \cite{li17} use a parameter (e.g., $u$, see above) to limit only a small number of top-frequent chunk pairs to be returned by frequency analysis, we find that the trick is not enough for {\em severe} inference attacks that demand high inference rate and accuracy.  In our experiments, we show the trick is not enough for severity and accuracy. A lower bound, although achieves high accuracy, potentially decreases the number of inferred ciphertext-plaintext chunk pairs.

 % The adversary adds the newly inferred top-frequent chunk pairs into $\mathcal{G}$, and iterates until $\mathcal{G}$ is empty.
% We apply frequency analysis to find the most frequent ciphertext-plaintext chunk pairs from each of LC and LM, and similarly from RC and RM. In other words, we find the left and right neighboring chunks of C and M that have the most co-occurrences with C and M themselves, respectively.
% infer new ciphertext-plaintext pairs from the neighbors of $C$ and $M$. Specifically, it sorts the left and right neighbors of $C$ and $M$ based on their co-occurrence frequencies with $C$ and $M$, respectively, and infer    
% collects their left and right neighbors, and applies frequency analysis 
% applies    
% on frequency analysis as underlying primitive, and repeats it based on . Specifically,  The key idea behind the locality-based attack is to 
% the original plaintext of ciphertext   
% which  
% . Specifically, chunk locality states   
% to repeat frequency analysis.  To exploit chunk locality, the adversary first applies   
% To launch locality-based attack, the adversary first

% and iterates it based on {\em chunk locality} , which specifies neighboring chunks tend to co-occur in the same order. Specifically, the adversary first applies frequency analysis to initialize an inferred set $\mathcal{G}$ with a configurable number (parameterized by $u$) of top-frequent ciphertext-plaintext chunk pairs. These inferred pairs can be considered correct with a high probability when $u$ is not much large (see \S\ref{sec:bucket_description}). In each iteration, the adversary picks one pair $(C, M)$ out of $\mathcal{G}$, and identifies the corresponding neighboring chunks $\mathbf{L}_\mathcal{C}[C]$, $\mathbf{R}_\mathcal{C}[C]$, $\mathbf{L}_\mathcal{M}[M]$ and $\mathbf{R}_\mathcal{M}[M]$ of $C$ and $M$. It applies frequency analysis on
% $\mathbf{L}_\mathcal{C}[C]$ and $\mathcal{L}_\mathcal{M}[M]$, as well as $\mathbf{R}_\mathcal{C}[C]$ and $\mathbf{R}_\mathcal{M}[M]$, according to their co-occurrence frequencies with $C$ and $M$. The rationale is the order of chunks is preserved due to locality, and the left and right neighbors of $M$ are likely to be the original chunks of the left and right neighbors of $C$. The adversary adds the newly inferred top-frequent chunk pairs into $\mathcal{G}$, and iterates until $\mathcal{G}$ is empty.

% Recall that a ciphertext may repeat in $\mathbf{C}$, and it can be associated with more than one co-occurrences in $\mathbf{L_C}$ and $\mathbf{R_C}$, each of which stores the number of times it appears with its left and right neighbors.  
% co-occur with  left and right neighbors. 
% store the co-occurrences of left and right neighboring ciphertext in $\mathbf{C}$, respectively.   
% Specifically, for the $i$-th plaintext $M^{(i)}$ of $\mathbf{M}$, it considers the {\em left} and {\em right neighbor} of $M^{(i)}$ as  $M^{( i-1 )}$ and $M^{( i+1 )}$, which appear directly before and after $M^{( i )}$ in $\mathbf{M}$, respectively. It collects the ordering of $\mathbf{A}$ in the form of the associative arrays $\mathbf{L_A}$ and $\mathbf{R_A}$, which store the co-occurrences of neighboring plaintexts in $\mathbf{A}$.

% The attack assumes the adversary's knowledge of order information is distributional, in the form of the associative arrays $\mathbf{L}_\mathcal{C}$ and $\mathbf{R}_\mathcal{C}$, which map each ciphertext chunk $C$ to its left and right neighboring chunks and corresponding co-occurrence frequencies with $C$. Note that this can be computed exactly if the adversary knows $\mathcal{L}_o$. The adversary can also extract similar arrays $\mathbf{L}_\mathcal{M}$ and $\mathbf{R}_\mathcal{M}$ from $\mathbf{M}_a$.
% propose the  that builds on  in backup workloads.
% In this section, we present the {\em distribution-based attack}, which is applicable for {\em both} fixed-size and variable-size chunks in backup data. Specifically, the distribution-based attack targets {\em full backups} (or backups for short) that are created as the complete copies of primary data (e.g., application states, file systems, and VM images) on a daily or a weekly basis, and it aims to infer the ciphertext-plaintext pairs across different versions (e.g., $\mathbf{M}$ and $\mathbf{C}$) of backups. The distribution-based attack exploits the order information, meaning that the logical orders of plaintexts in orginal file are reflected by the sequences of corresponding ciphertexts in $\mathbf{C}$ (see Section~\ref{sec:leakage}). 
% The distribution-based attack builds on {\em chunk locality} \cite{xia11,lillibridge09,zhu08, li17}, which defines the co-occurrence of neighboring chunks in backups. We follow the notations of \cite{li17} to capture chunk locality.  Based on the neighborhood relationship, we construct the associative arrays $\mathbf{L_M}$ and $\mathbf{R_M}$ to store the co-occurrences of neighboring plaintexts. Specifically, for the plaintexts of $M$ and $M'$,  $\mathbf{L_M}[M][M']$ and $\mathbf{R_M}[M][M']$ store the number of times that $M'$ is the left and right neighbor of $M$ in $\mathbf{M}$, respectively. We also build the associative arrays $\mathbf{L_C}$ and $\mathbf{R_C}$ to store the co-occurrences of
% neighboring ciphertexts in $\mathbf{C}$.

\section{Description of Distribution-based Attack}
\label{sec:distribution-attack-description}

The distribution-based attack extends the locality-based attack \cite{li17} to
significantly remove false positives.  It leverages the locality property in
backup workloads as in the locality-based attack.  In addition, for each
unique ciphertext $C$ in $\mathbf{C}$, we measure its {\em relative frequency
distribution} based on its co-occurrence frequencies with its neighbors.
Similarly, we examine the relative frequency distribution of each unique
plaintext $M$ in $\mathbf{A}$.  Our observation is that for a real
ciphertext-plaintext pair $(C, M)$, both $C$ and $M$ should have similar
relative frequency distributions; i.e., their co-occurrence frequencies with
their respective neighbors are similar.  We treat this observation as a more
general notion of the locality property, and use it as a condition to filter
possibly incorrect ciphertext-plaintext pairs.

%Our insight is if $M$ is the original plaintext of $C$, then the relative
%frequency distributions of $M$ and $C$ are likely to be {\em similar}. The
%rationale is  $\mathbf{A}$ and $\mathbf{C}$ are mapped from the same source,
%and hence share a large stretch of unchanged chunks that preserve
%relative frequency distributions. In other words, we extend frequency
%analysis, and filter the possibly flawed ciphertext-plaintext pairs $(C,
%M)$, in which the relative frequency distributions of $C$ and $M$
%are significantly different. This is expected to improve the precision of
%inference results. 
% infer the ciphertext-plaintext pair $(C, M)$ only when $C$ and $M$ have similar relative frequency distributions. Thus, we can filter the flawed inference pairs, in which the relative frequency distributions of the ciphertext and corresponding plaintext are likely to be significantly different.

\begin{figure}[t]
\centering
\includegraphics[width=.48\textwidth]{pic/distribution-attack.pdf}
\caption{Workflow of  distribution-based attack.}
\label{fig:distribution-attack}
\end{figure}

Figure \ref{fig:distribution-attack} presents the workflow of the
distribution-based attack. We first sort the unique ciphertexts and  plaintexts by
their frequencies in $\mathbf{C}$ and $\mathbf{A}$, respectively. As in the
locality-based attack \cite{li17}, we configure the parameter $u$ and 
the underlying frequency analysis to return at most $u$ ciphertext-plaintext
pairs.  In particular, for each unique ciphertext $C_i$ of rank $i$ (where 
$1 \leq i \leq u$), we examine a number of unique plaintexts $M_{i-r}, \ldots,
M_i, \ldots, M_{i+r}$ that rank from $i-r$ to $i+r$, where $r$ is a
configurable parameter (e.g., 10 by default) that indicates the maximum range
of rank disturbance that can be addressed.

For each $C_i$ (where $1\le i\le u$) and the corresponding $M_j$ (where 
$i-r\le j\le i+r$),  we compare their relative frequency distributions by
{\em entropy}, a key concept in information theory that measures the amount of
information produced by a random source. Here, we adopt the entropy to 
{\em quantify the randomness of probability distribution} \cite{wang08}.
Specifically, we define two random variables, denoted by $X$ and $Y$, to
describe the co-occurrences of $C_i$ with its left and right neighbors,
respectively, such that the event ``$X=C$'' denotes the case that $C$ is the
left neighbor of $C_i$, and the event ``$Y=C$'' denotes the case that $C$ is
the right neighbor of $C_i$.  Thus, we compute the probabilities of both
events based on $\mathbf{L_C}$ and $\mathbf{R_C}$:   
%
\begin{eqnarray}
\Pr[X = C] = \frac{\mathbf{L_C}[C_i][C]}{\sum_{C' \in \mathbf{L_C}[C_i]} \mathbf{L_C}[C_i][C']}, \nonumber \\
\Pr[Y = C] = \frac{\mathbf{R_C}[C_i][C]}{\sum_{C' \in \mathbf{R_C}[C_i]} \mathbf{R_C}[C_i][C']}, \nonumber
\end{eqnarray}
%
where $\mathbf{L_C}[C_i]$ and $\mathbf{R_C}[C_i]$ store the left and right
neighbors of $C_i$, respectively, while $\mathbf{L_C}[C_i][C']$ and
$\mathbf{R_C}[C_i][C']$ store the co-occurrence frequencies of $C_i$ with its
left and right neighbor $C'$.  Both $X$ and $Y$ follow the relative frequency
distributions of $C_i$, and we characterize their randomness by entropies
denoted by $e(\mathbf{L_C}[C_i])$ and $e(\mathbf{R_C}[C_i])$, respectively:  
%
\begin{eqnarray}
    e(\mathbf{L_C}[C_i]) = \sum_{C \in \mathbf{L_C}[C_i]} \log_2\frac{1}{\Pr[X = C]}, \nonumber \\
    e(\mathbf{R_C}[C_i]) = \sum_{C \in \mathbf{R_C}[C_i]} \log_2\frac{1}{\Pr[Y = C]}. \nonumber
	% e_{C_i}.r = \sum_{C' \in \mathbf{R_C}[C_i]} {\sf log}_2 \frac{\mathbf{R_C}[C_i][C']}{\sum_{C'' \in \mathbf{R_C}[C_i]} \mathbf{R_C}[C_i][C'']}, 
\end{eqnarray}

Similarly, we compute the entropies $e(\mathbf{L_A}[M_j])$ and
$e(\mathbf{R_A}[M_j])$ of each $M_j$ based on $\mathbf{L_A}$ and
$\mathbf{R_A}$, respectively.  We then quantify the similarity of the relative
frequency distributions of $C_i$ and $M_j$ via the {\em Euclidean distance},
denoted by $d(C_i, M_j)$:  
% is used to measure the amount of information produced by a 
 % random source. Specifically, we compute the entropies $e_{C_i}.l$ and $e_{C_i}.r$ of $C_i$ based on the co-occurrence frequencies of $C_i$ with its left and right neighbors, respectively:  
% \begin{eqnarray}
	% e_{C_i}.l = \sum_{C' \in \mathbf{L_C}[C_i]} {\sf log}_2 \frac{\mathbf{L_C}[C_i][C']}{\sum_{C'' \in \mathbf{L_C}[C_i]} \mathbf{L_C}[C_i][C'']}, \\
	% e_{C_i}.r = \sum_{C' \in \mathbf{R_C}[C_i]} {\sf log}_2 \frac{\mathbf{R_C}[C_i][C']}{\sum_{C'' \in \mathbf{R_C}[C_i]} \mathbf{R_C}[C_i][C'']}, 
% \end{eqnarray}
% where $\mathbf{L_C}[C_i]$ and $\mathbf{R_C}[C_i]$ store the left and right neighbors of $C_i$, respectively, and $\mathbf{L_C}[C_i][C']$ and $\mathbf{R_C}[C_i][C']$ stores the co-occurrence frequencies of $C_i$ with its corresponding neighbor $C'$. Similarly, we compute the entropies $e_{M_j}.l$ and $e_{M_j}.r$ of each $M_j$ based on $\mathbf{L_M}$ and $\mathbf{R_M}$, and collectively measure the similarity of the relative frequency distributions of $C_i$ and $M_j$ via the Euclidean distance:  
\begin{eqnarray*}
	d(C_i, M_j) & = & 
	\big\{[e(\mathbf{L_C}[C_i]) - e(\mathbf{L_A}[M_j])]^2 \\
	& & + \ \ [e(\mathbf{R_C}[C_i]) - e(\mathbf{R_A}[M_j])]^2\big\}^{1/2}.
\end{eqnarray*}

Clearly, $C_i$ and $M_j$ have similar relative frequency distributions only
when the Euclidean distance $d(C_i, M_j)$ of their entropies is small.
Thus,  we identify $(C_i, M_j)$ as an inferred ciphertext-plaintext pair if
they satisfy the following requirements: 
%
\begin{itemize}[leftmargin=*]
\item {\bf R1:} $d(C_i, M_j)$ is the {\em smallest} for all $i-r \leq j \leq i+r$.
\item {\bf R2:} $d(C_i, M_j)$ is not larger than a pre-defined parameter $t$ (e.g., 1 by default).
\end{itemize}

% One special note is R1 is necessarily that some $M_j$  satisfies R1.

One special note is that the original plaintext of $C_i$ may fall outside of
the examined plaintexts $M_{i-r}, \ldots, M_{i+r}$. 
In this case, R1 is still satisfied by some $M_j$ ($i-r \leq j \leq i+r$), and we expect to filter the incorrect ciphertext-plaintext pair by R2.

% {\bf We use the requirement R2, and expect it can filter the flawed
% inference results that map $C_i$ to some $M_j$ in this case. PC: don't quite
% understand the statement???}

Then, we adopt the iteration paradigm in the prior locality-based attack \cite{li17} (see Section~\ref{sec:prior-attack}) to increase the coverage of inferred ciphertext-plaintext pairs. Specifically, for each inferred $(C_i, M_j)$, we apply the new frequency analysis scheme (see above) to infer more ciphertext-plaintext pairs through the neighbors of $C_i$ and $M_j$, and further iterate the same inference for those newly inferred pairs. We finally stop the iteration, when none of new ciphertext-plaintext pairs can be inferred.

% Like the prior attack , we then iterate with each inferred  to infer more ciphertext-plaintext pairs from their neighbors. We apply the proposed new frequency analysis scheme (see above) through the left and right neighbors of $C_i$ and $M_j$, respectively, and      
% through the neighbors of  to infer more . , and further iterate   
% {\bf PC: can we not mention $\mathcal{Q}$ in this paragraph???} Then, we operate a first-in-first-out queue $\mathcal{Q}$, and apply the same locality-based paradigm (see Section~\ref{sec:prior-attack}) like the prior attack \cite{li17}. Specifically, we initialize $\mathcal{Q}$ with all ciphertext-plaintext pairs that have already been inferred. Each time, we pick one pair $(C_i, M_j)$ out of $\mathcal{Q}$, and apply the distribution-based frequency analysis (see above) over the left and right neighbors of $C_i$ and $M_j$, respectively. We include the newly inferred ciphertext-plaintext pairs into $\mathcal{Q}$, and finally stop the iteration until $\mathcal{Q}$ is empty.

 % For each inferred pair $(C_i, M_j)$, we apply the same locality-based paradigm like the prior attack \cite{li17}. Specifically, we operate a first-in-first-out queue $\mathcal{Q}$
% To repeat the distribution-based ranking, we initialize a first-in-first-out queue $\mathcal{Q}$ with the ciphertext-plaintext pairs inferred in Step 1. Each time, we pick one pair $(C_i, M_j)$ out of $\mathcal{Q}$, and apply the distribution-based ranking over their corresponding neighbors $\mathbf{L_C}[C_i]$ and $\mathbf{L_M}[M_j]$, as well as $\mathbf{R_C}[C_i]$ and $\mathbf{R_M}[M_j]$. From each case, we infer new ciphertext-plaintext pairs, and add them into $\mathcal{Q}$ for future loops. We finally stop the loop until $\mathcal{Q}$ is empty.
 % Our rationale of R2 is , and the parameter $t$ helps filter  
 % helps filter out these flawed inference results.

\paragraph{Summary:} To summarize, the distribution-based attack provides a
more general notion of locality by considering the relative frequency
distribution during frequency analysis.  It is configured by three parameters
(i) $u$, which specifies the maximum number of ciphertext-plaintext pairs returned by frequency analysis, 
(ii) $r$, which specifies the maximum range of rank disturbance to be
considered, and (iii) $t$, which specifies the Euclidean distance threshold to
filter possibly incorrect inference results. 
The prior locality-based attack \cite{li17} can be regarded as a special case
of the distribution-based attack under the parameter configuration of $r = 0$
(i.e., without addressing any disturbance to frequency ranking) and 
$t\rightarrow\infty$ (i.e., without filtering any incorrect inference results).

 % to 
 % specify the maximum range of disturbance to frequency ranking the scheme considers to address and the maximum entropy threshold

% The locality-based attack can be regarded as a special case of the distribution-based attack under the

\section{Exploiting Size Leakage}

We propose an advanced variant of the distribution-based attack that operates with size information to further reduce false positives. Specifically, we assume that the size of each ciphertext in $\mathbf{C}$ reflects that of its original plaintext.

% The distribution-based attack addresses the precision of inference results by comparing relative frequency distributions. We argue that there is oppurtunity to further reduce the number of false positives by exploiting size leakage. Specifically, we make an additional assumption that

% The rationale is symmetric encryption (e.g., block cipher) preserves the number of blocks.

Our idea builds on the fundamental truth that if a ciphertext $C$ corresponds to a plaintext $M$, then the size of $C$ approximates that of $M$. This is because encrypted deduplication preserves the number of blocks (i.e., the basic units operated by symmetric encryption) in the content to be encrypted. We use this fact to further filter the incorrect ciphertext-plaintext pairs $(C, M)$, where the number of blocks in $C$ and $M$ are different.

% In other words, the number of blocks in each plaintext is exactly mapped to that in the corresponding ciphertext.

% Our idea is based on the fundamental truth that if $C$ is mapped from $M$, then the size of $C$ approximates that of $M$. This is because encrypted deduplication preserves the number of blocks. In other words, we can filter the candiate pair $(C_i, M_j)$, where the number of blocks of $C_i$ and $M_j$ are different.

In this work, we assume that each block is of 16 bytes, which is a typical configuration for AES. For each considered ciphertext-plaintext pair $(C_i, M_j)$, we derive the number of blocks in $C_i$ and $M_j$ as $b({C_i})$ and $b({M_j})$, respectively:
\begin{eqnarray*}
b({C_i}) = \lceil \frac{{\sf size}(C_i)}{16} \rceil, \nonumber \\
b({M_j}) = \lceil \frac{{\sf size}(M_j)}{16} \rceil, \nonumber 
\end{eqnarray*}
where ${\sf size}(C_i)$ and ${\sf size}(M_j)$ are the exact sizes of $C_i$ and $M_j$, respecitively, and $\lceil x \rceil$ returns the smallest integer greater than or equal to $x$. In addition to R1 and R2 (see Section~\ref{sec:distribution-attack-description}), we apply the following requirement to filter by size:    
\begin{itemize}[leftmargin=*]
    \item {\bf R3:} $b({C_i})$ equals $b({M_j})$.
\end{itemize}

The requirement R3 is effective to filter the incorrect ciphertext-plaintext pairs regarding variable-size chunks, where different chunks possibly have distinct sizes. However, for fixed-size chunks, it is always satisfied by the ciphertext-plaintext pairs, even they are incorret. Despite of this, we can still apply R1 and R2 to achieve high-precision attack.

% for filtering false positives in terms of only variable-size chunks, where different chunks have possibly distinct sizes. On the other hand, it is always satisfied by fixed-size chunks, and cannot improve the precision of inference results in this case. Even so, we can still apply R1 and R2 to significantly reduce the amount of false positives in the locality-based attack \cite{li17} (see Section~\ref{sec:distribution-attack-description}).

% by {\bf about 50\%} (see Section~\ref{sec:experiment-distribution}).

% percentage of false positives below 25\% .

% \paragraph{Discussion:}
% The filtering effect of R3 depends on the size distribution of  (variable-size) chunks. Since encrypted deduplication only preserves approximate size (i.e., the number of blocks), R3 cannot detect the false positive, which maps a ciphertext to some flawed plaintext that shares the same number of blocks with corresponding exact plaintext. This makes it less effective in addressing inference precision against the workloads, where the sizes of majority chunks are clustered within a small range.

% Specifically, it is less effective in reducing the number of false positives against the workloads, in which the sizes of chunks are clustered into a small range. The reason is the adversary who observes the size of a ciphertext can only deduce the number of blocks in corresponding plaintext.

% The plaintexts whose sizes are clustered are more likely to have the same number of blocks, and the adversary cannot distinguish them by size.

% The main reason is the adversary can deduce the size of the plaintext in the quantization factor of block size.   
% Due to the above facts, an adversary who can see the length of a ciphertext can readily deduce the length of the respective plaintext, except for a quantization factor of 8 or 128 respectively. The larger the quantization factor, the less resolution the attacker has regarding plaintext length information. Rupture is able to attack ciphers with even large quantization factors, yet a larger factor can make the attack slower. While the quantization factor can be made arbitrarily large when designing ciphers, the penalty being paid is in bandwidth consumed to transmit the ciphertext.
% and R3 is less effective in reducing the false positives against small-size chunks.
% only for variable-size chunks, where different chunks have possibly distinct sizes. It is naturally satisfied by fixed-size chunks, and cannot filter any false positives. In this case, this  
% In addition, the effect of R3 depends on the (average) size of chunks.

% \paragraph{Discussion:}
% The size-based attack builds on the assumption of varying sizes of chunks, and demonstrates security alert only in variable-size chunking. In other words, the size-based attack will degrade to classical frequency analysis under fixed-size chunking, in which all plaintexts or ciphertexts have a uniform size and come into a single entry of the associative array.  
% The effectiveness of the size-based attack depends on the (average) size of chunks, and it is less effective for inferring small-size chunks. For example, we have evaluated that the size-based attack infers as low as 0.32\% of ciphertext-plaintext pairs against the chunks of an average size of 2KB (for comparison, it can infer up to 31.3\% ciphertext-plaintext pairs in our experiment of 8KB-size chunks, see Section~\ref{sec:experiment-size}). This is mainly for two reasons. First, small-size chunks are likely to have limited  variance on their size, and aggregate into a few entries of the associative array; this degrades the coverage of inferred pairs (recall that the attack  returns a limited number of ciphertext-plaintext pairs for each available chunk size). Second, each entry of the associative array is likely to include a large amount of small-size chunks, among which
% there tend to exist many ties where chunks have the same frequency; 
 % this possibly introduces additional false positives into frequency analysis \cite{naveed15, li17}.

% For each $M_j$ ($i-r \leq j \leq i+r$), we compute similar entropies $e_{M_j}.l$ and $e_{M_j}.r$ for $M_j$, and collectively measure the similarity of the relative frequency distributions of $C_i$ and $M_j$ via the Euclidean distance:

% We first sort available ciphertexts and plaintexts by their frequencies in $\mathbf{C}$ and $\mathbf{M}$, respectively. Next, we consider the distribution-based ranking scheme configured by a tuple of parameters $(u, r, t)$, in order to infer at most $u$ ciphertext-plaintext pairs. Specifically, for each ciphertext $C_i$ of rank $i$ ($1 \leq i \leq u$), we examine the plaintexts $M_{i-r},\ldots,M_i,\ldots,M_{i+r}$ that rank from $i-r$ to $i+r$, where $r$ (e.g., 10 by default) indicates the maximum range of rank disturbance can be addressed by the distribution-based ranking scheme. Then, we compute the entropies $e_{C_i}.l$ and $e_{C_i}.r$ of $C_i$ based on the co-occurrences of $C_i$ with its left and right neighbors, respectively:\footnote{Alternatively, we can calculate the entropies (that depend on the associative arrays $\mathbf{L_C}$ and $\mathbf{R_C}$) in
% pre-processing, rather than computing them on the fly.} 
% \begin{eqnarray}
% 	e_{C_i}.l = \sum_{C' \in \mathbf{L_C}[C_i]} {\sf log}_2 \frac{\mathbf{L_C}[C_i][C']}{\sum_{C'' \in \mathbf{L_C}[C_i]} \mathbf{L_C}[C_i][C'']}, \\
% 	e_{C_i}.r = \sum_{C' \in \mathbf{R_C}[C_i]} {\sf log}_2 \frac{\mathbf{R_C}[C_i][C']}{\sum_{C'' \in \mathbf{R_C}[C_i]} \mathbf{R_C}[C_i][C'']}, 
% \end{eqnarray}
% where $\mathbf{L_C}[C_i]$ and $\mathbf{R_C}[C_i]$) store the left and right neighbors of $C_i$, respectively, and $\mathbf{L_C}[C_i][C']$ and $\mathbf{R_C}[C_i][C']$ stores the co-occurrences of $C_i$ with its corresponding neighbor $C'$. For each $M_j$ ($i-r \leq j \leq i+r$), we compute similar entropies $e_{M_j}.l$ and $e_{M_j}.r$ for $M_j$, and collectively measure the similarity of the relative frequency distributions of $C_i$ and $M_j$ via the Euclidean distance:  
% \begin{eqnarray}
% 	{\sf Sim}(C_i, M_j) = \sqrt{(e_{C_i}.l - e_{M_j}.l)^2 + (e_{C_i}.r - e_{M_j}.r)^2}.  
% \end{eqnarray}

%  We infer $(C_i, M_j)$ as a ciphertext-plaintext pair, if (i) ${\sf Sim}(C_i, M_j)$ is the {\em smallest} among all examined plaintexts, and (ii) ${\sf Sim}(C_i, M_j)$ is not larger than the parameter $t$ (e.g., 1 by default). Our rationale is that the original plaintext of $C_i$ may fall outside of $M_{i-r}, \ldots, M_{i+r}$ (e.g., the range of rank disturbance is greater than $r$), and the pre-defined upper bound $t$ helps filter out these flawed inference results.

% Our insight is that if $M$ is the underlying plaintext of $C$, then the relative frequency distributions of $C$ and $M$ are likely to be {\em similar}. The rationale is that $\mathbf{M}$ and $\mathbf{C}$ are from the same primary data (at different time), and hence share a large stretch of unchanged chunks due to chunk locality. Thus, we can adjust the ranking of classical frequency analysis by taking relative frequency distribution into consideration. Specifically, for each ciphertext $C_i$ of rank $i$ and plaintext $M_j$ of rank $j$, we compare their relative frequency distributions, say by the {\em entropies} on the co-occurrences of their neighbors. If they have similar entropy values, we say their relative frequency distributions are similar, and we call $(C_i, M_j)$ as an inferred ciphertext-plaintext pair, even though $C_i$ and $M_j$ have different ranks (i.e., $i \neq j$).

% Thus, we can operate frequency analysis while taking relative frequency distribution into consideration, in order to filter out the inference results, in which the relative frequency distributions of the ciphertext and plaintext are significantly different. 
% Specifically, for each  plaintext $M$, we consider its {\em relative frequency distribution} that is counted by the co-occurrences of $M$ with its neighboring plaintexts (recall that $M$ may have duplicate copies and hence multiple neighbors in $\mathbf{M}$). We also count the relative frequency distribution of each ciphertext $C$.  
 % Thus, we can adjust the ranking of classical frequency analysis by taking relative frequency distribution into consideration. Specifically, for each ciphertext $C_i$ of rank $i$ and plaintext $M_j$ of rank $j$, we compare their relative frequency distributions, say by the {\em entropies} on the co-occurrences of their neighbors. If they have similar entropy values, we say their relative frequency distributions are similar, and we call $(C_i, M_j)$ as an inferred ciphertext-plaintext pair, even though $C_i$ and $M_j$ have different ranks (i.e., $i \neq j$). 
% The key idea of our attack is to inspect the distribution of , so as to filter out potentially flawed inference results.
% t further inspects the relative frequency distribution of the data and filters any potentially flawed inference results.
% We propose to extend chunk locality, and examine the frequency .

% Inspired by chunk locality (see \S\ref{sec:locality}), we move one step further to examine the co-occurrence of neighboring chunks.
% Specifically, for each chunk, we consider its {\em relative frequency distribution} that is counted by the number of co-occurrences with its neighbors (recall that a chunk may have duplicate copies and hence multiple neighboring chunks). Our insight is that identical chunks likely have {\em similar} relative frequency distributions across backups. The rationale is updates to backups appear in few clustered regions of chunks, while the remaining majority regions of chunks preserve their co-occurrence relationships.

% Chunk locality states that neighboring chunks tend to co-occur under the same order across backups. For example, if a plaintext $M$ is surrounded by the plaintexts $M'$ and $M''$ in one backup, then $M$ is also likely to be surrounded by $M'$ and $M''$ in the following backups. Prior works \cite{xia11,lillibridge09,zhu08} have exploited chunk locality to improve performance, while we adapt it into addressing the false positives in frequency analysis. Specifically, classical frequency analysis is sensitive to frequency ranking, and any disturbances (e.g., due to data updates across backups or ranking the ciphertexts/plaintexts that have identical frequency) to the frequency ranking can introduce a significant amount of flawed inference results.  
   % In the following, we show how to build on chunk locality to construct an inference attack with low false positives. We first elaborate the key designs of the distribution-based attack, and then present the attack details step by step.

% {\bf say drawback of classical frequency analysis}

% Take {\em backups}, the complete copies of some primary data (e.g., application states, file systems, and VM images), as an example, if a plaintext $M$ is surrounded by the plaintexts $M'$ and $M''$ in one backup, then $M$ is also likely to be surrounded by $M'$ and $M''$ in the following backup from the same primary data. Prior works \cite{xia11,lillibridge09,zhu08} have exploited chunk locality to improve performance, while we adapt it into addressing the false positives of inference attack.

% Figure \ref{fig:distribution-attack} shows an overview of the distribution-based attack. Given the input of $\mathbf{M}$ and $\mathbf{C}$, it builds on the {\em distribution-based ranking} to reduce the number of false positives in classical frequency analysis. Specifically, for each  plaintext $M$, we consider its {\em relative frequency distribution} that is counted by the co-occurrences of $M$ with its neighboring plaintexts (recall that $M$ may have duplicate copies and hence multiple neighbors in $\mathbf{M}$). We also count the relative frequency distribution of each ciphertext $C$.  
% Our insight is that if $M$ is the underlying plaintext of $C$, then the relative frequency distributions of $C$ and $M$ are likely to be {\em similar}. The rationale is that $\mathbf{M}$ and $\mathbf{C}$ are from the same primary data (at different time), and hence share a large stretch of unchanged chunks due to chunk locality. Thus, we can adjust the ranking of classical frequency analysis by taking relative frequency distribution into consideration. Specifically, for each ciphertext $C_i$ of rank $i$ and plaintext $M_j$ of rank $j$, we compare their relative frequency distributions, say by the {\em entropies} on the co-occurrences of their neighbors. If they have similar entropy values, we say their relative frequency distributions are similar, and we call $(C_i, M_j)$ as an inferred ciphertext-plaintext pair, even though $C_i$ and $M_j$ have different ranks (i.e., $i \neq j$).

% For each inferred ciphertext-plaintext pair $(C_i, M_j)$, we repeat the same inference (see above) through their neighbors. Specifically, we collect the left and right neighbors of $C_i$,  as well as of $M_j$, respectively, and apply the distribution-based ranking over their corresponding neighbors, in order to infer new ciphertext-plaintext pairs. The rationale is that chunk locality preserves orders, and the left and right neighbors of $M_j$ are likely to be the underlying plaintexts of the left and right neighbors of $C_i$, respectively. We further repeat the inference through the neighbors of these newly inferred ciphertext-plaintext pairs, so as to increase the coverage of inferred pairs.

% Then, we describe the details of the distribution-based attack.

% The distribution-based ranking proceeds as follows. We first rank available ciphertexts and plaintexts by their frequencies in $\mathbf{C}$ and $\mathbf{M}$, respectively. 
% Thus, we can adjust the ranking of classical frequency analysis by taking the relative frequency distribution of each plaintext and ciphertext into account. In other words, suppose $C_i$ and $M_j$ are the $i$-th and $j$-th top frequent ciphertext and plaintext, respectively.  
% This allows to infer the ciphertext-plaintext pair like $(C_i, M_j)$ 
% To perform distribution-based ranking,

% Thus, we          
% Thus, we first establish the frequency-only ranking like classical frequency analysis (see \S\ref{sec:freqanalysis}), and then adjust the ranking by taking into account the relative frequency distributions of chunks. Roughly, we break rank disturbances and infer the ciphertext-plaintext chunks pairs
% $(C_i, M_j)$, where $C_i$ and $M_j$ have similar relative frequency distribution yet possibly different ranks (e.g., $i \neq j$). We refer the Step 1 of the attack for detailed requirements of $C_i$ and $M_j$.

% We propose a new (frequency-based) ranking primitive, named {\em distribution-based ranking}, to address the ties incurred in classcial frequency analysis (see \S\ref{sec:freqanalysis}). Specifically, for each chunk, we consider its {\em relative frequency distribution} that is counted by the co-occurrences with its neighbors (recall that a chunk may have duplicate copies and hence multiple neighbors). Our insight is that the relative frequency distribution of the same chunk must be similar across backups. The reason is chunk locality implies that the majority stretches of chunks are unchanged. Thus, we first establish the frequency-only ranking like classical frequency analysis (see \S\ref{sec:freqanalysis}), and then adjust the ranking by taking into account the relative frequency distributions of chunks. Roughly, we break rank disturbances and infer the ciphertext-plaintext chunks pairs
% $(C_i, M_j)$, where $C_i$ and $M_j$ have similar relative frequency distribution yet possibly different ranks (e.g., $i \neq j$). We refer the Step 1 of the attack for detailed requirements of $C_i$ and $M_j$.  
% We elaborate the details below.

% \paragraph{Step 1 (Distribution-based ranking):}
% We first sort available ciphertexts and plaintexts by their frequencies in $\mathbf{C}$ and $\mathbf{M}$, respectively. Next, we consider the distribution-based ranking scheme configured by a tuple of parameters $(u, r, t)$, in order to infer at most $u$ ciphertext-plaintext pairs. Specifically, for each ciphertext $C_i$ of rank $i$ ($1 \leq i \leq u$), we examine the plaintexts $M_{i-r},\ldots,M_i,\ldots,M_{i+r}$ that rank from $i-r$ to $i+r$, where $r$ (e.g., 10 by default) indicates the maximum range of rank disturbance can be addressed by the distribution-based ranking scheme. Then, we compute the entropies $e_{C_i}.l$ and $e_{C_i}.r$ of $C_i$ based on the co-occurrences of $C_i$ with its left and right neighbors, respectively:\footnote{Alternatively, we can calculate the entropies (that depend on the associative arrays $\mathbf{L_C}$ and $\mathbf{R_C}$) in
% pre-processing, rather than computing them on the fly.} 
% \begin{eqnarray}
% 	e_{C_i}.l = \sum_{C' \in \mathbf{L_C}[C_i]} {\sf log}_2 \frac{\mathbf{L_C}[C_i][C']}{\sum_{C'' \in \mathbf{L_C}[C_i]} \mathbf{L_C}[C_i][C'']}, \\
% 	e_{C_i}.r = \sum_{C' \in \mathbf{R_C}[C_i]} {\sf log}_2 \frac{\mathbf{R_C}[C_i][C']}{\sum_{C'' \in \mathbf{R_C}[C_i]} \mathbf{R_C}[C_i][C'']}, 
% \end{eqnarray}
% where $\mathbf{L_C}[C_i]$ and $\mathbf{R_C}[C_i]$) store the left and right neighbors of $C_i$, respectively, and $\mathbf{L_C}[C_i][C']$ and $\mathbf{R_C}[C_i][C']$ stores the co-occurrences of $C_i$ with its corresponding neighbor $C'$. For each $M_j$ ($i-r \leq j \leq i+r$), we compute similar entropies $e_{M_j}.l$ and $e_{M_j}.r$ for $M_j$, and collectively measure the similarity of the relative frequency distributions of $C_i$ and $M_j$ via the Euclidean distance:  
% \begin{eqnarray}
% 	{\sf Sim}(C_i, M_j) = \sqrt{(e_{C_i}.l - e_{M_j}.l)^2 + (e_{C_i}.r - e_{M_j}.r)^2}.  
% \end{eqnarray}

%  We infer $(C_i, M_j)$ as a ciphertext-plaintext pair, if (i) ${\sf Sim}(C_i, M_j)$ is the {\em smallest} among all examined plaintexts, and (ii) ${\sf Sim}(C_i, M_j)$ is not larger than the parameter $t$ (e.g., 1 by default). Our rationale is that the original plaintext of $C_i$ may fall outside of $M_{i-r}, \ldots, M_{i+r}$ (e.g., the range of rank disturbance is greater than $r$), and the pre-defined upper bound $t$ helps filter out these flawed inference results.

% We  apply classical frequency analysis to establish the (frequency-only) ranking on the plaintext chunks in $\mathbf{M}_{\rm a}$, as well as on the ciphertext chunks in $\mathcal{L}_{\rm order}$. Like the size-based attack (see \S\ref{sec:size-attack-description}), we configure the parameter $u$ that indicates the {\em maximum} number of most frequent chunk pairs to be inferred by our distribution-based ranking scheme.  
% Then,  For $C_i$ and each $M_j$ $(i-r \leq j \leq i+r)$, we compare their relative frequency distributions, say by the {\em entropies} of neighboring chunks. Specifically, we compute the entropies $e_{M_j}.l$ and $e_{M_j}.r$ based on the co-occurrences of $M_j$ and its left and right neighbors, respectively:    
% (recall that we can access the co-occurrences of $M_j$ and its neighbors from $\mathbf{L}_{\rm a}$ and $\mathbf{R}_{\rm a}$).

% For example, if a chunk $M$ is surrounded by the chunks $M'$ and $M''$ in one backup, then $M$ is also likely to be surrounded by $M'$ and $M''$ in the following backups. The rationale is that the changes of backups often affect a few chunks, while the remaining chunks repeat in the same order.

% The distribution-based attack builds on {\em chunk locality}  that is defined based on the neighborhood of chunks. Specifically, given a logical chunk $M^{\langle i \rangle}$, we define its {\em left} (resp. {\em right}) {\em neighbor} as the logical chunk $M^{\langle i-1 \rangle}$ (resp. $M^{\langle i+1 \rangle}$) that appears directly before (resp. after) $M^{\langle i \rangle}$.

% To capture chunk locality, we build the associative arrays $\mathbf{L}_{\rm a}$ and $\mathbf{R}_{\rm a}$, which store the co-occurrences of neighboring  chunks in the auxiliary information $\mathbf{M}_{\rm a}$. Specifically, for two neighboring chunks $M$ and $M'$, $\mathbf{L}_{\rm a}[M][M']$ (resp. $\mathbf{R}_{\rm a}[M][M']$) stores the number of times that $M'$ is the left (resp. right) neighbor of $M$. For the ciphertext chunks, we also extract $\mathbf{L}_{\rm t}$ and $\mathbf{R}_{\rm t}$ to store the co-occurrences of their original chunks (recall that we can access the orders of original chunks by $\mathcal{L}_{\rm order}$).

% even they have different frequency ranks of $i$ and $j$ (see Step 1 for detailed requirements on .    
% This allows us to address rank disturbances and infer the

% We propose the {\em distribution-based ranking}, which exploits the co-occurrences of neighboring chunks to address the rank disturbances (e.g., due to data updates or breaking ties) of classical frequency analysis (\S\ref{sec:freqanalysis}). Specifically, for each chunk,

% the distribution-based ranking through their neighboring chunks. Specifically, we establish the distribution-based ranking on the left and right neighbors of $C_i$ and $M_j$, and infer more ciphertext-plaintext chunk pairs. The rationale is that the neighbors of $M_j$ are likely to be the neighbors of the original chunk of $C_i$, since chunk locality implies that the orders of chunks are preserved. We iterate the similar inference through the neighbors of those newly inferred chunk pairs, so as to increase attack severity.

% Thus, we can infer more ciphertext-plaintext chunk pairs and increase attack severity based on the iterative inferences.

% In this work,  a tuple $(u, r, t)$ of parameters.
% the co-occurrences of neighboring chunks are likely to be preserved across backups.

% (recall that we can access the logical orders of original chunks from $\mathcal{L}_{\rm order}$). 
% Based on the data structures, we first propose a new frequency analysis primitive, the {\em distribution-based ranking}, to address the rank disturbances of classical frequency analysis (\S\ref{sec:freqanalysis}). Then, we explain how to exploit chunk locality to repeat the inference primitive for high severity.   
% introduce a building block,  of the attack, followed by how to repeat the inference for high severity.      
% \paragraph{Distribution-based ranking:}
% Frequency analysis is sensitive to frequency ranking, and any disturbances (e.g., due to data updates or breaking ties) to the ranks can greatly degrade its inference accuracy. Inspired by chunk locality, we propose to examine the  
% updates to backups commonly appear in few clustered regions of chunks, while the remaining majority  chunks preserve their co-occurrence relationships.

% \paragraph{Step 2 (Repeat distribution-based ranking through neighbors):}
% To repeat the distribution-based ranking, we initialize a first-in-first-out queue $\mathcal{Q}$ with the ciphertext-plaintext pairs inferred in Step 1. Each time, we pick one pair $(C_i, M_j)$ out of $\mathcal{Q}$, and apply the distribution-based ranking over their corresponding neighbors $\mathbf{L_C}[C_i]$ and $\mathbf{L_M}[M_j]$, as well as $\mathbf{R_C}[C_i]$ and $\mathbf{R_M}[M_j]$. From each case, we infer new ciphertext-plaintext pairs, and add them into $\mathcal{Q}$ for future loops. We finally stop the loop until $\mathcal{Q}$ is empty.

% For each inferred chunk pair $(C_i, M_j)$, we build the {\em locality-based loop} \cite{li17} to repeat inferences through their neighboring chunks. Specifically, we collect the set of left $\mathbf{L}_{\rm t}[C_i] = \{C': \mathbf{L}_{\rm t}[C_i][C'] > 0 \}$ and right $\mathbf{R}_{\rm t}[C_i] = \{C': \mathbf{R}_{\rm t}[C_i][C'] > 0 \}$ neighbors of $C_i$, as well as the left $\mathbf{L}_{\rm a}[M_j]$ and right $\mathbf{R}_{\rm a}[M_j]$ neighbors of $M_j$. Then, we establish the distribution-based ranking over the chunks in $\mathbf{L}_{\rm t}[C_i]$ and $\mathbf{L}_{\rm a}[M_j]$, as well as in $\mathbf{R}_{\rm t}[C_i]$ and $\mathbf{R}_{\rm a}[M_j]$, respectively, so as to infer more ciphertext-plaintext chunk pairs. The rationale is that the chunks in $\mathbf{L}_{\rm a}[M_j]$ (resp. $\mathbf{R}_{\rm a}[M_j]$) are likely to be the underlying
% plaintexts of the ciphertext chunks in $\mathbf{L}_{\rm t}[C_i]$ (resp. $\mathbf{R}_{\rm t}[C_i]$), since chunk locality implies that the orders of chunks are preserved. We further iterate the similar inference through the neighbors of those newly inferred chunk pairs, so as to increase attack severity.     
 % In other words, we infer the ciphertext-plaintext chunk pairs, say $(C, M)$, from the neighbors of $C_i$ and $M_j$, such that (i) $C$ and $M$ have the most co-occurrences with $C_i$ and $M_j$, respectively and (ii) the relative frequency distributions of $C$ and $M$ are highly similar. We add the newly inferred  chunk pairs into $\mathcal{Q}$, and finally stop the loop until $\mathcal{Q}$ is empty.

% A special note is that we only examine the possible plaintext chunks that rank from $i$ to $i+r$ (rather than $i-r$ to $i+r$) for the distribution-based ranking in the loop. Our rationale is that chunks may have low co-occurrences after a number of loops, and most of them are likely to have similar relative frequency distribution with $C_i$. We start examination from rank $i$ to avoid relating the plaintext chunk that has a large rank difference from $i$.

% and all inferred chunk pairs have been iterated.

% and identify their neighbor sets $\mathbf{L}_{\rm t}[C_i], \mathbf{R}_{\rm t}[C_i], \mathbf{L}_{\rm a}[M_j]$ and $\mathbf{R}_{\rm a}[M_j]$. We invoke the distribution-based ranking on $\mathbf{L}_{\rm t}[C_i]$ and $\mathbf{L}_{\rm a}[M_j]$, as well as on $\mathbf{R}_{\rm t}[C_i]$ and $\mathbf{R}_{\rm a}[M_j]$, and add the newly inferred ciphertext-plaintext chunk pairs into $\mathcal{Q}$.

% Specifically, the adversary first applies frequency analysis to initialize an inferred set $\mathcal{G}$ with a configurable number (parameterized by $u$) of top-frequent ciphertext-plaintext chunk pairs. These inferred pairs can be considered correct with a high probability when $u$ is not much large (see \S\ref{sec:bucket_description}). In each iteration, the adversary picks one pair $(C, M)$ out of $\mathcal{G}$, and identifies the corresponding neighboring chunks $\mathbf{L}_\mathcal{C}[C]$, $\mathbf{R}_\mathcal{C}[C]$, $\mathbf{L}_\mathcal{M}[M]$ and $\mathbf{R}_\mathcal{M}[M]$ of $C$ and $M$. It applies frequency analysis on $\mathbf{L}_\mathcal{C}[C]$ and $\mathcal{L}_\mathcal{M}[M]$, as well as $\mathbf{R}_\mathcal{C}[C]$ and $\mathbf{R}_\mathcal{M}[M]$, according to their co-occurrence frequencies with $C$ and $M$. The rationale is the order of chunks is preserved due to locality, and the left and right neighbors of $M$ are likely to be the original chunks of the left and right neighbors of $C$. The adversary adds the newly inferred top-frequent chunk pairs into $\mathcal{G}$, and iterates until $\mathcal{G}$ is empty.  
% from $\mathbf{L}_{\rm t}$ and $\mathbf{R}_{\rm t}$.   
% since a chunk may have duplicate copies and hence multiple neighbors, we :w
% can compute the entropies $\mathbf{E}_{\rm tar}[C_i].l$ and $\mathbf{E}_{\rm tar}[C_i].r$, as well as $\mathbf{E}_{\rm aux}[M_j].l$ and $\mathbf{E}_{\rm aux}[M_j].r$, based on the co-occurrences of the neighbors of $C_i$ and $M_j$. Thus, we can collectively measure the similarity of relative frequency distributions via Euclidean distance: 
% Note that our ranking approach combines the co-occurrence relationship of neighboring chunks to address the rank disturbance of frequency-only ranking. It does not require each inferred pair $(C_i, M_j)$ must have the same rank, i.e., $j$ does not need to equal $i$.  In \S\ref{}, we will experimentally justify its advantage in distribution-based attack (\S\ref{sec:distribution-description}).   
% Based on chunk locality, we

% \subsection{Discussion}
% \label{sec:distribution-discussion}

% \noindent {\bf Generalization of prior attack:} 
% The recent {\em locality-based attack} \cite{li17} builds on chunk locality as our work, in order to improve the severity of frequency analysis against encrypted deduplication. The main difference is the prior attack \cite{li17} uses classical frequency analysis as the inference primitive (used in both Step 1 and Step 2 in Section~\ref{sec:distribution-attack-description}), rather than applying the distribution-based ranking to filter out flawed inference results. In fact, it \cite{li17} can be regarded as a special case of the distribution-based attack under the parameter configuration of $r = 0$ (i.e., cannot address rank disturbances) and $t = \infty$ (i.e., cannot filter out any flawed inference results).

% \paragraph{Fine-grained ordering knowledge:}
% For each ciphertext, the distribution-based attack assumes that its deduplication processing sequence reflects the logical order of corresponding plaintext, so that the adversary can identify the neighboring ciphertexts for attack. The assumption holds in a variety of real-world storage systems \cite{xia11,lillibridge09,zhu08} that preserve orders in deduplication, yet it can be addressed by scrambling the orders of ciphertexts. 
% % This breaks their neighborhood relationships, and hence prevents the attack.

% (see \S\ref{sec:countermeasure}

% To launch the distribution-based attack, the adversary must have the order information of ciphertexts. In other words, for each ciphertext, the attack  
% Although the assumption is plausible in a variety ,  
% the orders of ciphertexts reflect the  
% knows the logical order of underlying plaintexts in priori.

% The distribution-based attack has some limitations. First, the attack assumes that the adversary has full knowledge of neighboring chunks. Although it is plausible for some deduplicaton systems \cite{xia11,lillibridge09,zhu08}, we can address the assumption by simply swapping the orders of chunks (see \S\ref{sec:countermeasure}). Second, the attack depends on the prevalence of locality in workloads, and it may perform poor in the low-locality workloads.

% In Section~\ref{sec:experiment-distribution}, we will experimentally show that our new attack 
% can significantly reducing the number of false positives.

% it is reasonable to replace the frequency-only ranking (in classical frequency analysis) by our generalized distribution-based ranking. The reason is the inference precision of classical frequency analysis is strongly susceptible to rank disturbances. 
 % Any incorrectly inferred ciphertext-plaintext chunk pairs will compromise the following inference loops over their neighbors, and  affect inference rate. In \S\ref{sec:experiment-distribution}, we experimentally examine the improvement of our distribution-based attack over the prior locality-based attack \cite{li17}.
 % , which builds on classical frequency analysis as the underlying primitive.    
% repeat inferences .     
% Like the , the  builds on the same characteristics of  to demonstrate the security vulnerability of encrypted deduplication.
% Recently, Li {\em et al.}  , which builds on chunk locality as the distribution-based attack. The difference is the   
% repeats classical frequency analysis through neighbors of each inferred ciphertext-plaintext pair.

% This limits the adaptability of the distribution-based attack. %for the low-locality workloads (\S\ref{sec:clustering-attack}).
%, in which the data chunks arrive in the server under random order or from disparate clients.

% % We first review the {\em locality-based attack} \cite{li17} 
% % that combines frequency and order information to infer plaintext content in encrypted deduplication. Then, we present {\em distribution-based attack} that augments the locality-based attack with high inference accuracy. 
% % Note that we do not explicitly exploit size information in these attacks, since they are adapt to fixed-size chunking setting.

% \subsection{Prior Work: Locality-based Attack}
% \label{sec:locality-attack}
% The locality-based attack \cite{li17} targets backup workloads. It models a prior backup as $\mathbf{M}_{\rm aux}$, and aims to recover the original chunks of a later backup (known as $\mathbf{M}_{\rm tar}$). It builds on {\em chunk locality} \cite{xia11,zhu08}, which specifies that neighboring chunks tend to co-occur again in the same order. The attack defines the {\em left (resp. right) neighbor} of a chunk $M$ is the chunk that appears directly before (resp. after) $M$ in logical order. It derives a key insight that if $M$ is the original chunk of a ciphertext chunk $C$, then the neighbors of $M$ are likely to be the original chunks of the corresponding neighbors of $C$.

% To represent neighboring relations, the attack assumes that the adversary's knowledge of order information is in the form of the associative arrays $\mathbf{L}_{\rm tar}$ and $\mathbf{R}_{\rm tar}$. Specifically, $\mathbf{L}_{\rm tar}[C]$ (resp. $\mathbf{R}_{\rm tar}[C]$) maps a ciphertext chunk $C$ to its left (resp. right) neighbors and the corresponding co-occurrences with $C$. Note that this can be computed exactly if the adversary knows $\mathcal{L}_{\rm order}$. In addition, the attack extracts similar arrays $\mathbf{L}_{\rm aux}$ and $\mathbf{R}_{\rm aux}$  from $\mathbf{M}_{\rm aux}$.

% % which map each ciphertext chunk $C$ to its left and right neighboring chunks and corresponding co-occurrence frequencies with $C$.

% To launch attack, the adversary iterates frequency analysis to infer the neighbors of each known ciphertext-plaintext chunk pair. Specifically, it first initializes an inferred set $\mathcal{G}$ with a configurable number (e.g., $u$) of top-frequent chunk pairs. In each iteration, it picks one pair $(C, M)$ out of $\mathcal{G}$, and applies frequency analysis on their neighbors $\mathbf{L}_{\rm tar}[C]$ and $\mathbf{L}_{\rm aux}[M]$, as well as $\mathbf{R}_{\rm tar}[C]$ and $\mathbf{R}_{\rm aux}[M]$, and further adds the newly inferred top-frequent chunk pairs into $\mathcal{G}$. The adversary iterates the above procedure until $\mathcal{G}$ is empty.

%  % and identifies the corresponding neighboring chunks $\mathbf{L}_\mathcal{C}[C]$, $\mathbf{R}_\mathcal{C}[C]$, $\mathbf{L}_\mathcal{M}[M]$ and $\mathbf{R}_\mathcal{M}[M]$ of $C$ and $M$. It applies frequency analysis on $\mathbf{L}_\mathcal{C}[C]$ and $\mathcal{L}_\mathcal{M}[M]$, as well as $\mathbf{R}_\mathcal{C}[C]$ and $\mathbf{R}_\mathcal{M}[M]$, according to their co-occurrence frequencies with $C$ and $M$. The rationale is the order of chunks is preserved due to locality, and the left and right neighbors of $M$ are likely to be the original chunks of the left and right neighbors of $C$.

% % finds the corresponding sets $\mathbf{L_C}[C]$, $\mathbf{L_M}[M]$, $\mathbf{R_C}[C]$ and $\mathbf{R_M}[M]$ of neighboring chunks, and applies frequency analysis on $\mathbf{L_C}[C]$ and $\mathbf{L_M}[M]$, and similarly on $\mathbf{R_C}[C]$ and $\mathbf{R_M}[M]$.

% % initializes  (e.g., by frequency analysis). The rationale is the frequency ranks of these top-frequent chunks are stable across backups, and hence the inferred pairs are correct with a high probability.

% % More formally, the adversary knows the following information: $\mathbf{F}_\mathcal{C} = \{ (C, {\sf cnt}(M)) : C \in \mathcal{C} \wedge (M, C) \in \mathcal{E} \}$, which maps each ciphertext chunk to the frequency of its original chunk in $\mathbf{M}_t$, as well as $\mathbf{L}_\mathcal{C} = $ and $\mathbf{R}_\mathcal{C}$ which map each ciphertext chunk to its left and right neighboring chunks and their co-occurrence frequencies, respectively. The adversary also knows the similar associative arrays $\mathbf{F}_\mathcal{M}$, $\mathbf{L}_\mathcal{M}$ and $\mathbf{R}_\mathcal{M}$ about $\mathbf{M}_a$.

% Our observation is that the underlying frequency analysis is {\em sensitive to frequency ranking}. Specifically, any disturbance (e.g., due to data updates or breaking ties) to the frequency rank can greatly degrade inference accuracy. Any incorrectly inferred chunk pairs will further compromise the following iterations of their neighbors, and hence affect inference rate. The original construction \cite{li17} builds on parameter-aware frequency analysis to strengthen accuracy, yet this primitive sacrifices inference coverage as discussed in \S\ref{sec:bucket-description}.

% % Thus, the attack of \cite{li17}, while valuable for alerting the vulnerabilities of encrypted deduplication, is fairly severe in practice.

% % {\bf The authors \cite{li17} employ parameters to indicate only a small number of top-frequent chunk pairs to be returned by frequency analysis}. However, as discussed in \S\ref{sec:bucket-description}, this trick incurs new problem: a lower bound limits the coverage of inferred chunks, while a higher bound .

% We argue that there is an opportunity to increase attack severity by extensively exploiting the knowledge of order information. Our view is to build robust frequency ranking for being resistant to rank disturbance. In this way, we can properly increase frequency analysis parameter to infer more chunks, while mitigating the rank disturbance of the relatively non-top chunks to preserve accuracy. In the following two sections, we will elaborate our ranking approach (\S\ref{sec:distribution-ranking}), followed by how to build on it for inference attack (\S\ref{sec:distribution-description}).

% % augment the parameter-aware frequency analysis with {\em robust ranking}. This allows to increase the frequency analysis parameter to potentially infer more chunks, while it can mitigate the rank disturbance of relatively non-top chunks to preserve accuracy.

% % In \S\ref{sec:distribution_attack_description}, we present a simple but effective approach to establish {\em robust} frequency ranking, so as to ensure the inference accuracy of frequency analysis. We also integrate our approach with the locality-based attack for both severity and accuracy.

% \subsection{Robust Ranking}
% \label{sec:distribution-ranking}

% \subsection{Attack Description}
% \label{sec:distribution-description}
% % Our view is to build {\em robust} frequency ranking for being resistant to disturbance. In the following, we first propose a robust ranking approach for frequency analysis. Then, we present the {\em distribution-based attack} that augments the prior locality-based attack \cite{li17} with robust frequency ranking for high severity.

% We now proceed the {\em distribution-based attack}, which replaces the frequency-only ranking of the locality-based attack \cite{li17} by our robust ranking scheme (\S\ref{sec:distribution-ranking}). Algorithm \ref{alg:distribution-attack} shows the attack details. It takes input the frequency analysis parameter $u$, (expected) rank disturbance range $r$, distance threshold $t$, order leakage $\mathcal{L}_{\rm order}$ and auxiliary information $\mathbf{M}_{\rm aux}$ as input, and outputs the result set $\mathcal{R}$ of all inferred ciphertext-plaintext chunk pairs.

% Like the locality-based attack (\S\ref{sec:locality-attack}), {\sc Distribution-Attack} extracts $\mathbf{F}_{\rm tar}, \mathbf{L}_{\rm tar}$ and $\mathbf{R}_{\rm tar}$, as well as $\mathbf{F}_{\rm aux}, \mathbf{L}_{\rm aux}$ and $\mathbf{R}_{\rm aux}$, from $\mathcal{L}_{\rm tar}$ and $\mathbf{M}_{\rm aux}$, respectively (Line~3-4), where $\mathbf{F}_{\rm tar}$ and $\mathbf{F}_{\rm aux}$ keeps the frequency of each chunk (recall $\mathcal{L}_{\rm order}$ inherently includes the leakage of frequency), and $\mathbf{L}_{\rm tar}, \mathbf{R}_{\rm tar}, \mathbf{L}_{\rm aux}$ and $\mathbf{R}_{\rm aux}$ store the co-occurrences of neighboring chunks (\S\ref{sec:locality-attack}). It calls the function {\sc Entropy} to extract additional data structures $\mathbf{E}_{\rm aux}$ and $\mathbf{E}_{\rm tar}$ (Line~5-6), which map each chunk to the entropies that are counted by the relative frequency distributions of its left and right neighbors. Then, it calls the function {\sc Rank} with a flag of "INIT" to initialize $\mathcal{G}$ with the ciphertext-plaintext chunk pairs returned by our robust ranking scheme (Line~7). It also copies the inferred chunk pairs to $\mathcal{R}$ (Line~8).

% For the iteration of each chunk pair $(C, M)$ of $\mathcal{G}$, {\sc Distribution-Attack} also calls {\sc Rank} to build robust ranks on its neighboring chunks $\mathbf{L}_{\rm tar}[C]$ and $\mathbf{L}_{\rm aux}[M]$, as well as $\mathbf{R}_{\rm tar}[C]$ and $\mathbf{R}_{\rm aux}[M]$ (Line~11-12). One special mention is that we use a flag "ITERA" to identify the {\sc Rank} instances that are called in the iteration procedure. For each ciphertext chunk $C_i$ of rank $i$, we configure these instances to examine the possible plaintext chunks whose ranks start from $i$ (rather than $i-r$). Our rationale is chunks may have low frequencies after a number of iterations, and they are more likely to have identical relative frequency distribution with $C_i$. We start examination from rank $i$ to avoid relating the plaintext chunk that has a large rank difference from $i$. {\sc Distribution-Attack} includes the newly inferred ciphertext-plaintext chunk pairs (Line~13-15) into both $\mathcal{G}$ and $\mathcal{R}$. It iterates until $\mathcal{G}$ is empty, and finally returns $\mathcal{R}$.

% % we can configure that the examination in these instances starts with the plaintext chunks whose ranks are identical with the target ciphertext chunk. For example, for the  we start to examine the relative frequency distribution of the $i$-th frequent plaintext chunk.

% % To capture relative frequency distribution, we Note that both arrays can be easily computed from the original data structures $\mathbf{L}_{\rm aux}, \mathbf{R}_{\rm aux}, \mathbf{L}_{\rm tar}$ and $\mathbf{R}_{\rm tar}$ (\S\ref{sec:locality-attack}) of the locality-based attack.

% % The distribution-based attack initializes $\mathcal{G}$ by establishing robust ranking on all chunks. Specifically, the adversary finds $u$ and $u+r$ most frequent ciphertext and plaintext chunks, respectively, and relates each $i$-th frequent ciphertext chunk $C_i$ with a possible plaintext chunk that ranks from $i-r$ to $i+r$ (see above). It returns at most $u$ ciphertext-plaintext chunk pairs and adds them into $\mathcal{G}$.

% % The distribution-based attack also applies robust ranking on the neighbors of each iterating pair $(C, M)$.

% % For the iteration of each chunk pair $(C, M)$ of $\mathcal{G}$, the adversary also builds robust ranks on its neighboring sets $\mathbf{L}_\mathcal{C}[C]$ and $\mathbf{L}_\mathcal{M}[M]$, as well as $\mathbf{R}_\mathcal{C}[C]$ and $\mathbf{R}_\mathcal{M}[M]$. To relate the $i$-th frequent ciphertext chunk $C_i$, it only examines the possible plaintext chunks that are ranked from $i$ to $i+r$ (rather than $i-r$ to $i+r$). Our rationale is the ranked chunks may have low frequency count after a number of iterations, and they are likely to have identical relative frequency distribution with $C_i$. We start examination from rank $i$ to avoid relating the plaintext chunk that has a large rank difference from $i$.

% % \paragraph{Algorithm details:}
% % The distribution-based attack builds on prior locality-based attack \cite{li17} (see \S\ref{sec:locality}), and uses the robust frequency ranking approach to infer ciphertext-plaintext chunk pairs. We modify the parameters of the locality-based attack \cite{li17}. First, we remove the parameter (i.e., $w$ in \cite{li17}) of size of $\mathcal{G}$, as we find the memory can hold all fingerprints of our experimental datasets (see \S\ref{sec:methodology}). Second, we replace another parameter (i.e., $v$ in \cite{li17}) that bounds the number of chunk pairs returned by frequency analysis in each iteration, by $r$ to indicate the possible plaintext chunks to be examined.

% % Algorithm~\ref{alg:distribution} presents the pseudo-code of the distribution-based attack, where we assume the adversary can construct the associative arrays $\mathbf{F_C}, \mathbf{L_C}$, and $\mathbf{R_C}$, as well as $\mathbf{F_M}, \mathbf{L_M}$, and $\mathbf{R_M}$ by calling $\textsc{Count}(\mathbf{C})$ and $\textsc{Count}(\mathbf{C})$, respectively. We omit the algorithm details about $\textsc{Count}$, and readers may refer the function of the same name in ref. \cite{li17}. 
% % The algorithm \textsc{Distribution-attack} takes $\mathbf{C}, \mathbf{M}, u$ and $r$ as input, and outputs $\mathcal{R}$ of inferred ciphertext-plaintext chunk pairs. After initializing the associative arrays of $\mathbf{F_C}, \mathbf{L_C}$ and $\mathbf{R_C}$, it calls the function \textsc{Entropy} to obtain $\mathbf{E_C}$ which maps each ciphertext chunk to its entropies derived from the relative frequency distributions of its left and right neighbors (Line~4). Similarly, it obtains $\mathbf{E_M}$ for the plaintext chunks (Line~6). Then, it calls the \textsc{Robust-ranking} function to initialize $\mathcal{G}$ and $\mathcal{R}$ (Line~7-8). 
% % In each iteration, the algorithm picks out a pair $(C, M)$ from $\mathcal{G}$ (Line~10), and calls the function $\textsc{Robust-ranking}$ to infer ciphertext-plaintext chunk pairs $\mathcal{R}_r$ and $\mathcal{R}_l$ from the left and right neighbors of $C$ and $M$ (Line~11-12). It further adds the newly inferred pairs of $\mathcal{R}_l$ and $\mathcal{R}_r$ into $\mathcal{G}$ and $\mathcal{R}$ (Line~13-15). The iteration does not end until $\mathcal{G}$ is empty. The algorithm finally returns $\mathcal{R}$ (Line~16).

% The function \textsc{Entropy} builds the entropy array $\mathbf{E}_{\rm X}$ based on $\mathbf{L}_{\rm X}$ and $\mathbf{R}_{\rm X}$, where the X can be "tar" or "aux". For each chunk $X$, it counts the total co-occurrences $\Sigma_l$ of all left neighbors of $X$ (Line~20), and further the entropy $\mathbf{E}_{\rm X}[X].l$ of the relative frequency distribution of left neighbors (Line~21-22). Similarly, it counts the entropy $\mathbf{E}_{\rm X}[X].r$ of the relative frequency distribution of right neighbors (Line~23-25).

% The function \textsc{Rank} performs robust frequency ranking based on $\mathbf{X}_{\rm tar}$ and $\mathbf{X}_{\rm aux}$, where $\mathbf{X}_{\rm tar}$ and $\mathbf{X}_{\rm aux}$ can be $\mathbf{F}_{\rm tar}$ and $\mathbf{F}_{\rm aux}$, $\mathbf{L}_{\rm tar}[*]$ and $\mathbf{L}_{\rm aux}[*]$, or $\mathbf{R}_{\rm tar}[*]$ and $\mathbf{R}_{\rm aux}[*]$. It first sorts $\mathbf{X}_{\rm tar}$ and $\mathbf{X}_{\rm aux}$ by frequencies, respectively (Line~29-30). For each $i$-th frequent ciphertext chunk $C_i$, it identifies the range of plaintext chunks to be examined. Specifically, if the flag $f$ is INIT, it sets the starting rank $m$ as the maximum number of $1$ and $i-r$, since $i$ may be smaller than $r$ (Line~34-35); if $f$ is ITERA, it sets $m$ as $i$ (Line~36-37). Then, it finds the plaintext chunk $M$ in the examined range, such that ${\sf D}(C_i, M)$ is minimum (Line~38-42). The function adds $(C_i, M)$ into the result set $\mathcal{R}_x$ only when the distance ${\sf D}(C_i, M)$ is also smaller than the threshold $t$ (Line~43-44).

% % Note that \textsc{Robust-ranking} also returns $u$ highly frequent chunk pairs like locality-based attack \cite{li17}. Similarly, it sorts  For each top-frequent ciphertext chunk $C$ with a rank of $i$ ($1 \leq i \leq u$), it examines the cor:responding plaintext chunks that rank range from $i-r$ to $i+r$. Since $i-r$ is possibly below the first rank index, the algorithm derives the minimum rank $start$ of $1$ and $i-r$ and

% \begin{algorithm}[t]
% \caption{Distribution-based Attack}
% \label{alg:distribution-attack}
% \small
%   \SetKwFunction{Main}{\sc Distribution-Attack}
%   \SetKwProg{Pro}{procedure}{:}{}
% 	\Pro{\Main{$u, r, t, \mathcal{L}_{\rm order}, \mathbf{M}_{\rm aux}$}}{
% 		initialize $\mathcal{R} \longleftarrow \emptyset$\;

% 		extract $\mathbf{F}_{\rm tar}, \mathbf{L}_{\rm tar}$ and $\mathbf{R}_{\rm tar}$ from $\mathcal{L}_{\rm order}$\;
% 		% \tcc{$\mathbf{F}_{\rm tar}[C]$ maps $C$ to frequency of its original chunk in $\mathbf{M}_{\rm tar}$}
% 		% \tcc{$\mathbf{L}_{\rm tar}[C]$ maps ciphertext chunk $C$ to its left neighbors as well as corresponding co-occurrences with $C$}
% 		% \tcc{$\mathbf{R}_{\rm tar}[C]$ maps ciphertext chunk $C$ to its right neighbors as well as corresponding co-occurrences with $C$}

% 		extract $\mathbf{F}_{\rm aux}, \mathbf{L}_{\rm aux}$ and $\mathbf{R}_{\rm aux}$ from $\mathbf{M}_{\rm aux}$\;
% 		% \tcc{$\mathbf{F}_{\rm aux}[M]$ stores frequency of plaintext chunk $M$ in $\mathbf{M}_{\rm aux}$}
% 		% \tcc{$\mathbf{L}_{\rm aux}[M]$ maps plaintext chunk $M$ to its left neighbors and corresponding co-occurrences with $M$}
% 		% \tcc{$\mathbf{R}_{\rm aux}[M]$ maps plaintext chunk $M$ to its right neighbors and corresponding co-occurrences with $M$}

% 		$\mathbf{E}_{\rm tar} \longleftarrow \textsc{Entropy}(\mathbf{L}_{\rm tar}, \mathbf{R}_{\rm tar})$\;
% 		$\mathbf{E}_{\rm aux} \longleftarrow \textsc{Entropy}(\mathbf{L}_{\rm aux}, \mathbf{R}_{\rm aux})$\;

% 		$\mathcal{G} \longleftarrow \textsc{Rank}(u, r, t, \mathbf{F}_{\rm tar}, \mathbf{E}_{\rm tar}, \mathbf{F}_{\rm aux}, \mathbf{E}_{\rm aux}, {\rm INIT})$\;

% 		$\mathcal{R} \longleftarrow \mathcal{G}$\;
% 		\While{$\mathcal{G}$ is non-empty}{
% 			pick $(C, M)$ out of $\mathcal{G}$\;
% 			$\mathcal{R}_l \longleftarrow \textsc{Rank}(u, r, t, \mathbf{L}_{\rm tar}[C], \mathbf{E}_{\rm tar}, \mathbf{L}_{\rm aux}[M], \mathbf{E}_{\rm aux}, {\rm ITERA})$\;
% 			$\mathcal{R}_r \longleftarrow \textsc{Rank}(u, r, t, \mathbf{R}_{\rm tar}[C], \mathbf{E}_{\rm tar}, \mathbf{R}_{\rm aux}[M], \mathbf{E}_{\rm aux}, {\rm ITERA})$\;
% 			\For{each $(C, M)$ in $\mathcal{R}_l \cup \mathcal{R}_r$}{
% 				\If{$(C, *)$ is not in $\mathcal{R}$}{
% 					Add $(C, M)$ into $\mathcal{G}$ and $\mathcal{R}$\;
% 				}
% 			}
% 		}
% 		\KwRet{$\mathcal{R}$}\;
%   }

%   \SetKwFunction{Entropy}{\sc Entropy}
%   \SetKwProg{Fn}{function}{:}{}
% 	\Fn{\Entropy{$\mathbf{L}_{\rm X}, \mathbf{R}_{\rm X}$}}{
% 		\For{each chunk $X$ in $\mathbf{L}_{\rm X}$ and $\mathbf{R}_{\rm X}$}{
% 			initialize $\mathbf{E}_{\rm X}[X].l,  \mathbf{E}_{\rm X}[X].r \longleftarrow 0$\;
% 			$\Sigma_l \longleftarrow$ sum of co-occurrences of left neighbors in $\mathbf{L}_{\rm X}[X]$\;
% 			\For{each left neighbor $X_l$ in $\mathbf{L}_{\rm X}[X]$}{
% 				$\mathbf{E}_{\rm X}[X].l \longleftarrow \mathbf{E}_{\rm X}[X].l - {\sf log}_2\frac{\mathbf{L}_{\rm X}[X][X_l]}{\Sigma_l}$\;
% 			}
% 			$\Sigma_r \longleftarrow$ sum of co-occurrences of right neighbors in $\mathbf{R}_{\rm X}[X]$\;
% 			\For{each right neighbor $X_r$ in $\mathbf{R}_{\rm X}[X]$}{
% 				$\mathbf{E}_{\rm X}[X].r \longleftarrow \mathbf{E}_{\rm X}[X].r - {\sf log}_2\frac{\mathbf{R}_{\rm X}[X][X_r]}{\Sigma_r}$\;
% 			}
% 		}
% 		\KwRet{$\mathbf{E}_{\rm X}$}\;
% 	}

% 	\SetKwFunction{Ranking}{\sc Rank}
%   \SetKwProg{Fn}{function}{:}{}
% 	\Fn{\Ranking{$u, r, t, \mathbf{X}_{\rm tar}, \mathbf{E}_{\rm tar}, \mathbf{X}_{\rm aux}, \mathbf{E}_{\rm aux}, f$}}{
% 		initialize $\mathcal{R}_x \longleftarrow \emptyset$\;
% 		sort ciphertext chunks in $\mathbf{X}_{\rm tar}$ by frequencies\;
% 		sort plaintext chunks in $\mathbf{X}_{\rm aux}$ by frequencies\;
% 		\For{$i \longleftarrow 1$ to $u$}{
% 			$C_i \longleftarrow$ $i$-th frequent ciphertext chunk\;
% 			initialize $d \longleftarrow$ MAX\_DISTANCE\;
% 			\uIf{$f$ is {\rm INIT}}{
% 				$m \longleftarrow$ maximum rank of $1$ and $i-r$\;
% 			}
% 			\uElseIf{$f$ is {\rm ITERA}}{
% 				$m \longleftarrow$ $i$\;
% 			}
% 			\For{$j \longleftarrow m$ to $i+r$}{ 
% 				$M_j \longleftarrow$ $j$-th frequent plaintext chunk\;
% 				\If{${\sf D}(C_i, M_j) < d$}{
% 					$M \longleftarrow M_j$\;
% 					$d \longleftarrow {\sf D}(C_i, M_j)$\;
% 				}
% 			}
% 			\If{${\sf D}(C_i, M) < t$}{
% 				add $(C_i, M)$ into $\mathcal{R}_x$\;
% 			}
% 		}
% 		\KwRet{$\mathcal{R}_x$}\;
% 	}

% \end{algorithm}

\chapter{Clustering-based Attack}
\label{sec:clustering-attack}

% The distribution-based attack is based on the assumption that the ordering of ciphertexts in $\mathbf{C}$ reflects that of corresponding plaintexts in $\mathbf{M}$ (recall $\mathbf{M}$ is the original file of $\mathbf{C}$).

In this section, we relax the adversarial knowledge in the distribution-based attack, and propose the {\em clustering-based attack}, which does not need the fine-grained ordering of plaintexts. Instead, it exploits the {\em similarity} property to infer original data from similar {\em clusters} (i.e., some large data units aggregated by chunks), without relying on the ordering of chunks in each cluster. We first introduce similarity, and then show how to adapt this property into inference attack.

% In the following, we introduce similarity, followed by how we adapt this property to inference attack.

\section{Background: Similarity}
\label{sec:similarity}
Similarity \cite{bhagwat09} states that backup files from the same source are likely to be {\em similar} and share a large fraction of identical chunks. The similarity between backup files can be quantified by {\em Broder's theorem} \cite{broder97}. Specifically, if we treat each file as a set $S$ of chunks (i.e., ignore their orders), Broder's theorem states that if the probability that two sets of chunks share the same minimum chunk hash is high, then both sets are likely to share a large fraction of identical chunks and vice versa:  
\begin{eqnarray}
	\Pr[\min\{{\rm H}(S)\} = \min\{{\rm H}(S')\} ] = \frac{|S \cap S'|}{|S \cup S'|}, \nonumber
	\label{eq:broder}
\end{eqnarray}
where ${\rm H}(\cdot)$ is a hash function that is chosen uniformly at random from a min-wise independent family of permutations, and $\min\{{\rm H}(S)\}$ returns the minimum chunk hash of $S$. 
% For easy elaboration, we use {\em MinHash} to denote the minimum element hash of some set.

Prior works that target different aspects (e.g., performance \cite{qin17,xia11,bhagwat09}, and security \cite{li17}) of deduplication  have applied similarity to {\em preserve storage efficiency}. Specifically, they operate deduplication just on the files that share the same minimum chunk hash (i.e., similar); since similar files can have a large number of identical chunks due to Broder's theorem, such {\em near-exact} deduplication only leads to a slight degradation of storage efficiency. Different from  prior approaches \cite{qin17,xia11,bhagwat09,li17}, we apply similarity to increase the severity of frequency analysis.

% Thus, prior works   apply chunk-based deduplication across similar segments, so as to improve the effectiveness of {\em near-exact} deduplication.

% the probability that two sets (files)     
% if two sets share a large fraction of common elements (i.e., they are highly similar), then the probability that both sets share the same minimum hash element is also high.
% likely to be highly similar and share a large fraction of identical chunks. The similarity of  
% The similarity of files can be  Specifically, we treat each file as a set of chunks, and do not care the order of each chunk.   
% that are possibly under different orders yet. Previous approach (e.g., \cite{xia11,bhagwat09}) exploits this property to minimize the memory usage of deduplication.

% the similarity-based approach that is commonly used to improve deduplication performance \cite{qin17,xia11,bhagwat09}. Then, we show how to adapt the similarity property to inference attack.

% infer ciphertext-plaintext pairs that are in similar clusters, without the knowledge of the order information of each ciphertext or plaintext in the clusters. 
% consider to relax such ordering leakage. Specifically, we 90  
% We assume that the adversary learns the (generic) order information in a {\em coarse-grained unit}, in which a number of chunks appear together as a set; while the adversary cannot identify the accurate order of any chunk in each set.

% has some limitations. First, the attack assumes that the adversary has full knowledge of neighboring chunks. Although it is plausible for some deduplicaton systems \cite{xia11,lillibridge09,zhu08}, we can address the assumption by simply swapping the orders of chunks (see \S\ref{sec:countermeasure}). Second, the attack depends on the prevalence of locality in workloads, and it may perform poor in the low-locality workloads.

% Informed by the limitations (see \S\ref{sec:distribution-discussion}), we consider an attack against the {\em low-locality} workloads, where there does not exist a large stretch of repeated data across backups. We argue that such a workload is reasonable in practice. For example, if multiple users upload their data simultaneously, the chunks received by the server will be disordered and lose locality.

% Thus, there is no locality among the chunks that arrives in a window of time. 
% continuous data protection (CDP) only stores the chunks where information has changed, it destroys the locality of chunks since changes often appear in unpredictable regions. Thus, for low-locality workloads, the information perceived by the adversary no longer reflect the actual logical orders of chunks.

% To model the scenario, we consider {\em time window}, which is the basic unit of period whose actual order can be perceived by the adversary. Specifically, we assume that the network bandwidth is steady, and the server can receive a fixed amount (e.g., 4MB) of data during each time window. The adversary cannot distinguish the actual logical orders of chunks that are received within the same time window, while it can learn if two chunks are received in an identical time window.

% Formally, we use ${\sf tw}(M)$ to denote the orders of the time windows during which the chunk $M$ is received by the server, if we upload all chunks in order.

% Suppose that all chunks are uploaded under their logical orders. We use ${\sf tw}(M)$ to denote the orders of the time windows during which $M$ is received by the server (note that a chunk may appear multiple times and hence in several time windows). This is the only information about ordering that can be perceived by the adversary. Thus, we can define the leakage:

% \begin{itemize}[leftmargin=2em]
% 	\item  $\widetilde{\mathcal{L}}_{\rm order} = \{(C, {\sf tw}(M)): M \in \mathbf{M}_{\rm t} \textrm{ and } C = {\sf E}_{K_M}(M)\}$, in which each pair leaks the time window of the original chunk. Note that $\widetilde{\mathcal{L}}_{\rm order}$ no longer implies $\mathcal{L}_{\rm freq}$, since a chunk possibly appears multiple times in the same time window.     
% \end{itemize}

% In this section, we propose a new inference attack, the {\em clustering-based attack}, which can increase the severity of frequency analysis with only the coarse-grained order information like time window, i.e., $\mathcal{L} = (\mathcal{L}_{\rm freq}, \widetilde{\mathcal{L}}_{\rm order})$.

% does not need the accurate knowledge about neighboring relationships.

% In this section, we consider the leakage of {\em coarse-grained order information}.  
%    we propose a new inference attack, the {\em clustering-based attack}, which does not need the accurate knowledge about neighboring relationships. Instead, we model $\mathbf{M}_{\rm tar}$ as a collection of {\em chunk regions}, and each region includes a set of continues chunks. The adversary only knows the logical orders of regions, while the orders of chunks in each region are randomly scrambled. 
% Instead, it builds on the  in which the adversary only needs to know the logical order of coarse-grained set of continues chunks, while the orders of chunks in each set are scrambled. More formally, we define the coarse-grained order leakage $\widetilde{\mathcal{L}}_{\rm order}$, ...    
% an obfuscated version of order leakage $\widetilde{\mathcal{L}}_{\rm order}$, based on which the adversary can only know: (i) and (ii) the orders of chunks in each region have been randomized.

% does not need the accurate knowledge about neighboring relationships. Instead, we model $\mathbf{M}_{\rm tar}$ as a collection of {\em chunk regions}, and each region includes a set of continues chunks. The adversary only knows the logical orders of regions, while the orders of chunks in each region are randomly scrambled.

% A challenge of the attack is how to break ties.

% \subsection{Similarity-based Approaches}
% For example, in a NAS-based backup storage system, the identical chunks are possibly arrived in random order from different clients.

% coming from different clients are possibly arrived in random order.  
% Since two backups from the same data source are expected to be highly similar and share a large number of identical chunks

% Previous similarity-based approaches \cite{li17,qin17,xia11,bhagwat09} address deduplication performance of such workloads via the Broder's theorem.   
% Previous similarity-based approaches \cite{li17,qin17,xia11,bhagwat09} address the performance bottleneck of deduplication storage systems via Broder's theorem.     
% improves deduplication performance based on :

% Previous similarity-based approaches

% In other words, there does not exist

% in which the chunks are possibly associated with random orders. The stretch of the data, although having the same content, their chunks are associated with random orders.

% Informed by the limitations (see \S\ref{sec:distribution-discussion}), we consider an attack against the {\em low-locality} workloads, where there does not exist a large stretch of repeated data across backups. We argue that such a workload is reasonable in practice. For example, if multiple users upload their data simultaneously, the chunks received by the server will be disordered and lose locality.

\section{Description of Clustering-based Attack}
\label{sec:clustering-attack-description}

\begin{figure}
	\includegraphics[width=.48\textwidth]{pic/clustering-attack-new.pdf}
    % \caption{Workflow of clustering-based attack: MinHash denotes the minimum chunk hash of plaintext segment, $e(\mathcal{C}_\mathbf{C})$ and $e(\mathcal{C}_\mathbf{A})$ denote the entropies based on the frequency distributions in $\mathcal{C}_\mathbf{C}$ and $\mathcal{C}_\mathbf{A}$, respectively, and  $\#\mathcal{C}_\mathbf{C}$ and $\#\mathcal{C}_\mathbf{A}$ denote the total number of logical ciphertexts and plaintexts in $\mathcal{C}_\mathbf{C}$ and $\mathcal{C}_\mathbf{A}$, respectively.}
    \caption{Workflow of clustering-based attack: MinHash denotes the minimum chunk hash of a plaintext segment.}
	\label{fig:clustering-attack}
\end{figure}

We now present the clustering-based attack (Figure~\ref{fig:clustering-attack}) that builds on similarity to infer original data against encrypted deduplication.

To exploit similarity, we first introduce {\em segmentation} on a stream of chunks. Specifically, we partition $\mathbf{C}$ into a set of coarse-grained data units, called {\em ciphertext segments}. Each ciphertext segment, denoted by $S_\mathbf{C}$, comprises multiple adjacent ciphertexts in $\mathbf{C}$. In this work, we implement the {\em fixed-size} segmentation scheme to ensure that all ciphertext segments are of the same size (e.g., 4MB by default). 
For compatibility, the same fixed-size segmentation scheme also applies to the auxiliary information $\mathbf{A}$, so as to generate multiple {\em plaintext segments}, each of which is denoted by $S_\mathbf{A}$. 
Note that some variable-size segmentation schemes \cite{lillibridge09, qin17}  identify segment boundaries after the chunks whose contents match a specific pattern and thus address the boundary shift problem faced by the fixed-size segmentation scheme. 
However, we cannot use these variable-size segmentation schemes \cite{lillibridge09, qin17} in the attack. The reason is that the original contents of chunks in ciphertext segments are protected by symmetric encryption, and we cannot ensure that the boundaries for both ciphertext and plaintext segments match the same pattern. This leads to an incompatibility between ciphertext and plaintext segments, and degrades the amount of segment-level data inferred by the clustering-based attack (see the late part of this section).

% It violates compability, since we cannot

% It impossible to ensuring the boundaries for  plaintext and ciphertext segments match the same pattern.

% Even we apply the variable-size segmentation scheme directly  on the contents of ciphertexts,

% we cannot derive the same pattern for both

% Note that the order and size of each ciphertext in $\mathbf{C}$ are necessary for operating the fixed-size segmentation, while we do {\em not} need them to reflect those of corresponding plaintext;

% , so as to be robust against boundary shift of fixed-size segment.  
% we cannot apply
% that match specific content patterns,   
% which address the boundary shift of fixed-size segment, yet requiring to identify segment boundaries that match specific content patterns so as to remain robust against content shifts  
% operate more  requiring the original content patterns of ciphertexts in $\mathbf{C}$.

We propose to infer ciphertext-plaintext pairs through similar segments. Let $S_\mathbf{M}$ be the original plaintext segment of a ciphertext segment $S_\mathbf{C}$ (i.e., each plaintext in $S_\mathbf{M}$ corresponds to some ciphertext in $S_\mathbf{C}$ and vice versa). According to Broder's theorem, if $S_\mathbf{M}$ shares the same minimum chunk hash, say $h$, with some plaintext segment $S_\mathbf{A}$, then $S_\mathbf{M}$  and $S_\mathbf{A}$ tend to have a large fraction of identical plaintexts. This implies that the ciphertexts in $S_\mathbf{C}$ are likely to be mapped from the plaintexts in  $S_\mathbf{A}$. In other words, we first classify all plaintext segments of $\mathbf{A}$ by their minimum chunk hashes, and obtain multiple {\em plaintext clusters}. Each plaintext cluster, denoted by $\mathcal{C}_\mathbf{A} = \{ S_\mathbf{A} \}$, corresponds to a unique minimum chunk hash shared by its included segments. We also 
group the ciphertext segments, whose original plaintext segments have the same minimum chunk hash $h$ (i.e., similar), into an identical {\em ciphertext cluster}, denoted by $\mathcal{C}_\mathbf{C} = \{ S_\mathbf{C} \}$. Then, we infer the original data of $\mathcal{C}_\mathbf{C}$ from some $\mathcal{C}_\mathbf{A}$ that corresponds to  $h$.

% corresponding segment that is mapped to $S_\mathbf{C}$ (i.e., each plaintext in $S_\mathbf{M}$ corresponds to some ciphertext in $S_\mathbf{C}$, and visa versa). 
% Given a ciphertext segment $S_\mathbf{C}$, let

% if  in other words,  Thus, we propose to launch frequency analysis through similar segments. 
% Specifically,

% say $\mathcal{C}_\mathbf{C}$.  
% $h$ 
% We denote a plaintext cluster by , which includes multiple  plaintext segments that have the same minimum chunk hash.    
% Each plaintext cluster, denoted by  is a set of  We propose to also collect the ciphertext segments (as a {\em ciphertext cluster} denoted by $\mathcal{C}_\mathbf{C}$) whose original plaintext segments share an identical minimum chunk hash $h$, and then infer their original contents from
% some $\mathcal{C}_\mathbf{A}$ that corresponds to $h$ (i.e., the minimum chunk hash of each plaintext segment in $\mathcal{C}_\mathbf{A}$ equals $h$).

% and $h$ be the minimum chunk hash computed from $S_\mathbf{M}$.

% Our insight is if $h$ equals the minimum chunk hash of some $S_\mathbf{A}$, then the ciphertexts in $S_\mathbf{C}$  The rationale is the original segment of $S_\mathbf{C}$ has a large fraction of identical plaintexts with $S_\mathbf{A}$ due to Broder's theorem.

% In other words,

% This is expected to reduce the disturbances to frequency analysis.

% $\{S_\mathbf{C}\}$ that have an identical {\em original} minimum element hash $h$,

% composed of the segments that have the same minimum element hash.  
% However, the original data of each ciphertext segment $S_\mathbf{C}$ is protected by symmetric encryption, and it is impossible to identify the corresponding minimum chunk hash $h$ for grouping ($h$ is derived from the original plaintext segment of $S_\mathbf{C}$). The challenge is how to group similar ciphertext segments {\em without} knowing the minimum chunk hash $h$ of each $S_\mathbf{C}$.

% the original content of each ciphertext segment $S_\mathbf{C}$ is protected by symmetric encryption; this makes it impossible to identify the corresponding  $h$ for grouping (recall $h$ is derived from the original plaintext segment of $S_\mathbf{C}$). In other words, there exists a challenge of

We propose a {\em clustering} scheme to group similar ciphertext segments. A na\"{i}ve approach is to classify segments by their minimum chunk hashes, but it does not work on ciphertext segments, whose original contents are protected by symmetric encryption. We address the classification issue based on Broder's theorem.   
% operate classification by the  of each segment , but it .   
Our insight is that if two ciphertext segments have a large fraction of identical ciphertexts, then  they correspond to the same minimum chunk hash with a high probability. The reason is that deterministic encryption preserves the cardinalities of union and intersection of plaintext segments, based on which we can use Broder's theorem to learn the equivalence of their minimum chunk hashes.    
% the fraction of identical plaintexts, based on  Thus, we  apply a clustering algorithm, and aggregate similar ciphertext segments into the same cluster.

In this work, we define the {\em clustering distance} $d(S_\mathbf{C}, S_\mathbf{C}')$ of any two ciphertext segments $S_\mathbf{C}$ and $S_\mathbf{C}'$ by one minus the fraction of their identical ciphertexts:
\begin{eqnarray}
d(S_\mathbf{C}, S_\mathbf{C}') = 1 - \frac{|S_\mathbf{C} \cap S_\mathbf{C}'|}{|S_\mathbf{C} \cup S_\mathbf{C}'|}. \nonumber
\end{eqnarray}
Note that identical ciphertexts may repeat in $S_\mathbf{C}$ or $S_\mathbf{C}'$, and $|S_\mathbf{C} \cap S_\mathbf{C}'|$ and $|S_\mathbf{C} \cup S_\mathbf{C}'|$ return the number of {\em unique} ciphertexts in their  intersection and union, respectively. Clearly,  the smaller $d(S_\mathbf{C}, S_\mathbf{C}')$ is, the more likely are $S_\mathbf{C}$ and $S_\mathbf{C}'$ to correspond to the same minimum chunk hash. Then, we adopt the {\em agglomerative hierarchical clustering (AHC)} \cite{johnson67} to aggregate similar ciphertext segments based on their distance information.  
Specifically, we start with eash ciphertext segment in its own singleton cluster, and iteratively combine the two closest clusters based on the maximum distance of their ciphertext segments. We configure a parameter $k$, 
% to indicate the upper bound distance in combination, 
and stop the iterated combination when the maximum distance of ciphertext segments in the two cloest
clusters is greater than $k$.

% finally stop combination when       
% Specifically, the clustering scheme is configured by a minimum intercluster distance $d$.   
% We combine nearby segments into clusters based on the distance metric, and stop the combination when 
% the maximum distance between any segment in two clusters is less than $d$.
% the first cluster and any single data point in the second cluster.
% Based on the distance definition, 
% we implement the clustering algorithm via {\em ALGLIB} \cite{alglib}, which is a programming library for extensive data analysis. While ALGLIB supports multiple clustering algorithms, we choose the , because we  only have the distance information of  segments (rather than their coordinates). 
% Specifically, we configure a desired minimum intercluster distance $d$ (e.g., 0.8 by default) via ${\tt clusterizerseparatedbydist()}$, and generate multiple ciphertext clusters via ${\tt clusterizerrunahc()}$.

For each aggregated ciphertext cluster $\mathcal{C}_\mathbf{C}$, we relate it to some plaintext cluster $\mathcal{C}_\mathbf{A}$ with frequency analysis, while taking frequency distribution into account. This is based on the observation that identical ciphertexts (resp. plaintexts) may  repeat in the same or different ciphertext (resp. plaintext) segments and identical ciphertext (resp. plaintext) segments may also repeat in the same ciphertext (resp. plaintext) cluster. We propose to examine the frequency distribution of the logical ciphertexts or plaintexts in each cluster, and perceive that the frequency distributions for similar clusters (i.e., correspond to the same minimum chunk hash) are also likely to be similar. 
% {\bf Our rationale is changes to backups only apply on limited regions, and do not modify the spatiality of majority chunks.}

% We proceed the frequency analysis scheme as follows. First, we  sort available ciphertext and plaintext clusters by the total number of logical  ciphertexts and plaintexts they include, respectively. Then, we count the entropy of each cluster based on the frequency distribution of its logical ciphertexts or plaintexts. Like the distribution-based attack (see Section~\ref{sec:distribution-attack-description}), we configure the frequency analysis scheme with the parameters $(u, r, t)$, and infer the ciphertext cluster $\mathcal{C}_\mathbf{C}$ is similar to a plaintext cluster $\mathcal{C}_\mathbf{A}$, if they satisfy the following requirements:    
We proceed the frequency analysis scheme as follows. First, we  sort available ciphertext and plaintext clusters by the total number of logical  ciphertexts and plaintexts they include, respectively. Then, we count an associative array $\mathbf{F}$ that stores the frequency of each unique ciphertext or plaintext in  corresponding cluster. Based on $\mathbf{F}$, we compute the probability that a  ciphertext $C$ exists in a ciphertext cluster $\mathcal{C}_\mathbf{C}$ and further the   
entropy of $\mathcal{C}_\mathbf{C}$:      
% entropy of each ciphertext cluster $\mathcal{C}_\mathbf{C}$:    
\begin{eqnarray*}
    \Pr[C \in \mathcal{C}_\mathbf{C}] = \frac{\mathbf{F}[\mathcal{C}_\mathbf{C}][C]}{\sum_{C' \in \mathcal{C}_\mathbf{C}} \mathbf{F}[\mathcal{C}_\mathbf{C}][C']}, \\
    e(\mathcal{C}_\mathbf{C}) = \sum_{C \in \mathcal{C}_\mathbf{C}} \log_2 \frac{1}{\Pr[C \in \mathcal{C}_\mathbf{C}]},  
    % e(\mathcal{C}_\mathbf{M}) = \sum_{M \in \mathbf{F}[\mathcal{C}_\mathbf{M}]} \log_2 \frac{\mathbf{F}[\mathcal{C}_\mathbf{M}][M]}{a} 
\end{eqnarray*}
where   
$\mathbf{F}[\mathcal{C}_\mathbf{C}][C]$  stores the frequency of $C$ in $\mathcal{C}_\mathbf{C}$. Similarly, we  compute the entropy $e(\mathcal{C}_\mathbf{A})$ for the plaintext cluster $\mathcal{C}_\mathbf{A}$.   
Like the distribution-based attack (see Section~\ref{sec:distribution-attack-description}), we configure the frequency analysis scheme with the parameters $(u, r, t)$, and infer that the ciphertext cluster $\mathcal{C}_\mathbf{C}$ is similar to a plaintext cluster $\mathcal{C}_\mathbf{A}$, if they satisfy the following requirements:
% the entropy of each cluster based on the frequency distribution of its logical ciphertexts or plaintexts. Like the distribution-based attack (see Section~\ref{sec:distribution-attack-description}), we configure the frequency analysis scheme with the parameters $(u, r, t)$, and infer the ciphertext cluster $\mathcal{C}_\mathbf{C}$ is similar to a plaintext cluster $\mathcal{C}_\mathbf{A}$, if they satisfy the following requirements:    
\begin{itemize}[leftmargin=*]
    \item  The rank of $\mathcal{C}_\mathbf{C}$ is not larger than $u$.
    \item  The rank difference of $\mathcal{C}_\mathbf{C}$ and $\mathcal{C}_\mathbf{A}$ is not larger than $r$.  
    \item  The difference of $e(\mathcal{C}_\mathbf{C})$ and $e(\mathcal{C}_\mathbf{A})$ is the smallest and also not larger than $t$.
\end{itemize}

% Thus, the ciphertexts or plaintexts in each cluster may follow a non-uniform frequency distribution, and such frequency distributions are further correlated for the similar clusters  in different backups.  
% We expect  ciphertexts or plaintexts in most of clusters follow a non-uniform frequency distribution, and such frequency distributions are {\em correlated} for  similar clusters (i.e., correspond to the same minimum chunk hash) in different backups. 
% Our rationale is .   
% Thus, we apply a  scheme like the distribution-based frequency analysis (see Section~\ref{sec:distribution-attack-description}), in order to find similar clusters.

Then, for each pair $(\mathcal{C}_\mathbf{C}, \mathcal{C}_\mathbf{A})$ of similar clusters, we infer ciphertext-plaintext pairs in two levels. 
\begin{itemize}[leftmargin=*]
    \item {\bf Segment-level inference:}
        If $\mathcal{C}_\mathbf{C}$ and $\mathcal{C}_\mathbf{A}$ have the same number of logical chunks (i.e., ciphertexts or plaintexts), as well as an identical entropy, this implies that $\mathcal{C}_\mathbf{C}$ is exactly mapped from $\mathcal{C}_\mathbf{A}$ with a high probability. In this case, we operate attack on the coarse-grained {\em segment} level. Specifically, we first compute the entropies of each ciphertext segment $S_\mathbf{C}$ in $\mathcal{C}_\mathbf{C}$ and each plaintext segment $S_\mathbf{A}$ in $\mathcal{C}_\mathbf{A}$, based on the frequency distributions of their ciphertexts and plaintexts, respectively. 
        % (recall identical chunks may have duplicate copies in the same segment). 
         We infer that $S_\mathbf{C}$ is mapped from  $S_\mathbf{A}$, if the total numbers of logical chunks, as well as the entropies, of $S_\mathbf{C}$ and $S_\mathbf{A}$ are identical. Our evaluation shows that the segment-level inference contributes most of the correctly inferred contents in the
        clustering-based attack (see
        Section~\ref{sec:experiment-clustering}). It is also possible to further recover each plaintext in these inferred segments with additional adversarial knowledge (e.g., ordering).

    \item {\bf Chunk-level inference:}
        If $\mathcal{C}_\mathbf{C}$ and $\mathcal{C}_\mathbf{A}$ have different numbers of logical chunks or entropies, we apply frequency analysis to operate attack on the fine-grained {\em chunk} level. Specifically, we sort all unique ciphertexts and plaintexts by their frequencies in $\mathcal{C}_\mathbf{C}$ and $\mathcal{C}_\mathbf{A}$, respectively, and infer ciphertext-plaintext pairs based on frequency ranks.  
        However, we find the chunk-level inference does not perform well in our experimental dataset. The possible reason is each cluster includes a large number of logical chunks, which degrades the effectiveness of  frequency analysis. Even so, we expect the chunk-level inference can recover more ciphertext-plaintext pairs in practice, especially when the number of logical chunks in some clusters is limited.   
        % there are many tied chunks in the similar classes of the VM dataset
        % Even so, we still expect it can recover even more information in practice, especially when each cluster is of .  
\end{itemize}

% Figure~\ref{fig:clustering-attack} puts all design primitives together, and show the workflow of the clustering-based attack.

\paragraph{Summary:}
To summarize, the clustering-based attack exploits similarity, and launches frequency analysis in similar clusters to infer ciphertext-plaintext pairs. In addition to  $u$, $r$ and $t$, it is configured by the parameter $k$, which specifies the upper bound distance in combining the closest clusters.

Although possibly affected by the boundary shift of fixed-size segments, we argue that the clustering-based attack is severe against VM disk images. 
Specifically, a flat VM image file is allocated of a fixed size at the time it is created, and such size cannot be changed during its lifetime. All unused regions in a VM image are initially filled with  zero chunks, which can be further re-written for storing additional data in the image. 
% The clustering-based attack does not suffer from boundary shift in this case, since VM images do not need to insert or remove chunks. 
In Section \ref{sec:experiment-clustering}, we examine the effectiveness of the clustering-based attack against VM images.

% One limitation of the clustering-based attack is it suffers from the {\em boundary shift} of segment. Specifically, since we apply fixed-size segmentation, the insertion of one or more chunks will shift the boundaries of all segments that come after the insertion point. This changes the frequency distribution of chunks in some segments, and affects the precision of the identified similar clusters. This also leads to a reduced number of identical segments, and degrades the amount of original contents inferred by the segment-level inference. 
% % Our evaluation shows that the clustering-based attack can only infer about 1\% original content in a long-term backup dataset. 
% We argue that the clustering-based attack is still severe for {\em VM disk images}.

% After allocation, all unused regions in the image are filled by , and   
% which of {\em fixed} sizes during their lifetime.  
% . Specifically, a flat image file is allocated of a {\em fixed} size at the time it is created, and all unused regions of the image file are initially filled with {\em zero chunks}. The image file can store additional data by re-writing zero chunks   
%  Flat images are fixed-size files, with one block for each block in the guest’s disk. Initially, unused blocks are zero-filled; thus, flat disk images tend to have a lot of zero-filled blocks, particularly if they are rela- tively large to allow the guest operating system space into which to store additional data. Sparse images, unlike flat im- ages, only contain virtual disk blocks that have been written at least once. Thus, sparse images can occupy relatively lit- tle space when created, and only grow as the guest operating system uses more and more of its virtual disk. Note, how- ever, that sparse images can
% contain zero-filled blocks, since the guest operating system may write a block containing all zeros; such a block would be stored by the virtual machine in the disk image file. While there is no global standard for virtual machine disk images, specifications for one file format is available from VMware

% the clustering-based attack has low effectiveness (about 1% inference rate) against the FSL dataset.

% Even so, we argue that the clustering-based attack is severe for some workloads, which store data {\em aligned} with disk block boundaries and do not have the problem of  \cite{jin09}. In \S\ref{sec:experiment-clustering}, we will examine the effectiveness of the clustering-based attack against VM workloads,

% The main limitation of the clustering-based attack is the {\em boundary shift} of segment.  This changes the chunk distributions of some segments, and  affects the precision of identifying similar classes in Step 2. The boundary shift also decreases the effectiveness of the segment-level attack in Step 3, since it leads to fewer common segments in the auxiliary data and target data. On the other hand, we cannot address the boundary-shift problem by existing approaches (e.g., the content-defined segmentation \cite{lillibridge09}), which depend on the knowledge of the underlying content pattern of ciphertext chunks.

%% In \S\ref{sec:clustering-experiment}, we justify the barrier of the boundary shift in the clustering-based attack.       
% % between $\mathbf{M}_{\rm a}$ and $\mathbf{M}_{\rm t}$,  
%%We adapt the similarity-based approach to inference attack. Specifically, we apply segmentation, yet on ciphertext chunks, and generate the segments that include adjacent ciphertext chunks under the scrambled order in $\widetilde{\mathcal{L}}_{\rm order}$.

%If $\mathcal{C}_i$ and $\mathcal{M}_j$ have different numbers of logical chunks or entropies, we apply operate classical frequency analysis to operate attack on {\em chunk level}. This can infer more ciphertext-plaintext chunk pairs, yet degrading inference precision.

%% over $\mathcal{C}_i$ and $\mathcal{M}_j$ . 
%% for each ciphertext segment in $\mathcal{C}_i$, we find the plaintext segment that has the same  
%% Specifically, for each ciphertext segment $S_{\rm t}$ in $\mathcal{C}_i$, we find the plaintext segment $S_{\rm a}$ in $\mathcal{S}_j$ such that   
%% Then, we adopt the idea of distribution-based ranking (\S\ref{sec:distribution-attack-description}) to identify the ciphertext and plaintext classes that are identified by the same MinHash.  
%%In the following, we first propose the {\em similarity-based clustering} approach, which aims to classify ciphertext segments by their underlying MinHash. Then, we elaborate how to relate a class of ciphertext segments with that of plaintext segments. 
%%\paragraph{Similarity-based clustering:}
%%works on ciphertext segments and classify them by their underlying MinHash. Then,

% \paragraph{Step 3: (Launch attack through similar classes):} For each identified similar classes $(\mathcal{C}_i, \mathcal{M}_j)$, we launch attack for two cases. If $\mathcal{C}_i$ and $\mathcal{M}_j$ have the same number of logical chunks and entropy, our attack operates on {\em segment level}. For each ciphertext segment $S_{\rm t}$ in $\mathcal{C}_i$, we examine each available plaintext segment $S_{\rm a}$ in $\mathcal{S}_j$, and infer $(S_{\rm t}, S_{\rm a})$ as a ciphertext-plaintext segment pair if $S_{\rm a}$ has the same number of logical chunks and entropy (via Equation~\ref{eq:clustering-entropy} but computed for segment) with $S_{\rm t}$. We stop the attack at segment level in this case, because there is not enough information to further extracting chunk content; otherwise it sacrifices inference precision. We argue that the segment-level attack is severe, since each segment represents a continues region of data. The adversary can learn significant information if it successfully extracts the underlying data of some segment.

%% Through experimental analysis, the segment-level attack contributes the most component of correct inferences.     
%% has the same number of logical chunks and entropy as $S_{\rm t}$. We infer that $S_{\rm a}$ is the original segment of $S_{\rm t}$.

%If $\mathcal{C}_i$ and $\mathcal{M}_j$ have different numbers of logical chunks or entropies, we apply operate classical frequency analysis to operate attack on {\em chunk level}. This can infer more ciphertext-plaintext chunk pairs, yet degrading inference precision.

%% over $\mathcal{C}_i$ and $\mathcal{M}_j$ . 
%% for each ciphertext segment in $\mathcal{C}_i$, we find the plaintext segment that has the same  
%% Specifically, for each ciphertext segment $S_{\rm t}$ in $\mathcal{C}_i$, we find the plaintext segment $S_{\rm a}$ in $\mathcal{S}_j$ such that   
%% Then, we adopt the idea of distribution-based ranking (\S\ref{sec:distribution-attack-description}) to identify the ciphertext and plaintext classes that are identified by the same MinHash.  
%%In the following, we first propose the {\em similarity-based clustering} approach, which aims to classify ciphertext segments by their underlying MinHash. Then, we elaborate how to relate a class of ciphertext segments with that of plaintext segments. 
%%\paragraph{Similarity-based clustering:}
%%works on ciphertext segments and classify them by their underlying MinHash. Then,

% Based on the configuration parameters of $u$, $r$ and $t$ (see \S\ref{sec:distribution-attack-description}), we pick the ciphertext class $\mathcal{C}_i$ that has the $i$-th most number of logical chunks ($1 \leq i \leq u$), and examine each plaintext class $\mathcal{M}_j$ that ranks from $i-r$ to $i+r$. We identify that $\mathcal{C}_i$ and $\mathcal{M}_j$ have the same MinHash, if the difference of their entropies is (i) minimum across all $i-r \leq j \leq i+r$ and (ii) smaller than $t$.

% while the rest data preserve the same characteristics.   
% Due to backup redundancies, .   . 
% Our rationale is that the chunk distributions in similar classes are likely to be correlated due to deterministic encryption.

%We build on the idea of the distribution-based ranking (see \S\ref{sec:distribution-attack-description}) to identify the ciphertext and plaintext classes that correspond to the same MinHash. Specifically, for each ciphertext class with an underlying MinHash of $h$, our aim is to find the plaintext class identified by the same MinHash of $h$. Note that we cannot measure relative frequency distributions for ranking, since we do not have enough knowledge about neighboring chunks. Instead, we count the entropy of a class by the {\em occurrences of different chunks} in the class. Specifically, for a plaintext class $\mathcal{M}$, we compute its entropy:  \begin{eqnarray}
%        e_{\mathcal{M}} = \sum_{M \in \mathcal{M}} {\sf log}_2 \frac{{\sf cnt}_\mathcal{M}(M)}{|\mathcal{M}|},
%        \label{eq:clustering-entropy}
%\end{eqnarray}
%where $|\mathcal{M}|$ is the total number of logical chunks in $\mathcal{M}$ and ${\sf cnt}_\mathcal{M}(M)$ returns the number of copies of the chunk $M$ in $\mathcal{M}$. We derive similar entropy $e_\mathcal{C}$ for a ciphertext class $\mathcal{C}$, and consider $\mathcal{M}$ and $\mathcal{C}$ are {\em similar classes} (i.e., having the same MinHash), if the difference of their entropies is minimum. Our rationale is that the chunk distributions in similar classes are likely to be correlated due to deterministic encryption.

%In more details, we first sort the available ciphertext and plaintext classes separately by the number of logical chunks they include. Based on the configuration parameters of $u$, $r$ and $t$ (see \S\ref{sec:distribution-attack-description}), we pick the ciphertext class $\mathcal{C}_i$ that has the $i$-th most number of logical chunks ($1 \leq i \leq u$), and examine each plaintext class $\mathcal{M}_j$ that ranks from $i-r$ to $i+r$. We identify that $\mathcal{C}_i$ and $\mathcal{M}_j$ have the same MinHash, if the difference of their entropies is (i) minimum across all $i-r \leq j \leq i+r$ and (ii) smaller than $t$.

%% However, it is hard to classify ciphertext segments, since there still exists a challenge on identifying the underlying MinHash of ciphertext segments. Recall that  
%% By our assumption (\S\ref{sec:clustering-attack}), all ciphertext segments must have the same size. Thus, to be compatible, we also partition the original stream of plaintext chunks $\mathbf{M}_{\rm a}$ into fixed-size {\em plaintext segments}, each of which comprises a sequence of plaintext chunks.

%% We adapt the similarity-based approach to inference attack. Specifically, to capture the notion of similarity,  
%% for inferring ciphertext-plaintext chunk pairs through similar segments. Specifically, we

% We proceed our similarity-based clustering scheme as follows. It defines the {\em clustering distance} of The smaller the distance ${\sf Dist}(S_{\rm t}, S_{\rm t}')$ is, the more likely are $S_{\rm t}$ and $S_{\rm t}'$ to have the same underlying MinHash. Then, it uses the agglomerative hierarchical clustering algorithm (via the function  in ) for clustering, and generates the ciphertext classes based on a desired minimum intercluster distance of $d$ (via the function  in ALGLIB \cite{alglib}). By default, we configure $d$ by 0.8.

% we can apply Broder's theorem  on ciphertexts due to the deterministic nature of encryption.  
% This is because encryption preserves the deduplication capability of elements.
% . Thus, we can compute the overlaps between any two ciphertext segments, and cluster them into several {\em ciphertext classes}, such that each cluster includes the ciphertext segments that possibly have the same underlying MinHash.

%We propose the {\em similarity-based clustering} approach, which aims to classify the ciphertext segments by their underlying MinHash while not compromising confidentiality. The key insight is that if two ciphertext segments have a large fraction of common (ciphertext) chunks, then they are likely to have the same underlying MinHash (due to Equation (\ref{eq:broder})). Thus, we can compute the overlaps between any two ciphertext segments, and cluster them into several {\em ciphertext classes}, such that each cluster includes the ciphertext segments that possibly have the same underlying MinHash.

% identify  This raises a challenge on how to group   
% the minimum element hash $h$  
% it is impossible to the original plaintext and identify the minimum element hash corresponding to a ciphertext segment.  
% recover its original plaintext segment and extract the minimum element hash.    
% the original plaintexts of the ciphertext segment, and further learn the      
% The challenge is  Since each ciphertext segment is mapped by symmetric encryption, it is impossible to learn their original content and identify the minimum element hash from corresponding plaintexts.
% Since each ciphertext in $S_\mathbf{C}$ is mapped by symmetric encryption, it is impossible to learn their original plaintexts or identify the minimum element hash (based on these plaintexts). In other words, the main challenge  
% which chunk leads to the minimum element hash, and further the exact hash value. In other words, there exists a challenge on collecting similar $\{ S_\mathbf{C} \}$ (i.e., they share the same original minimum element hash) and map them to $\mathcal{C}_\mathbf{A}$.

%Thus, instead of inferring ciphertext-plaintext pairs (from $\mathbf{C}$ and $\mathbf{A}$) directly,

%One challenge behind the clustering-based attack is how to identify the original minimum element hash $h$ of each $S_\mathbf{C}$. Since

%The clustering-based attack proceeds as follows. First, we

%We classify plaintext segments into a set of {\em plaintext classes} by their MinHash. On the other hand, we cannot perform similar classification over ciphertext segments, since their underlying contents are protected by symmetric encryption (see \S\ref{sec:threat}).

%% , each of which includes the plaintext segments that have the same MinHash. 
%% it is impossible to access or compare the underlying contents of ciphertext chunks for classification, since their original contents are protected by symmetric encryption

%% split the original space () of frequency analysis into multiple subspaces, and
%% eliminates     
%% identify the minimum element hash of each $S_\mathbf{C}$, and then apply frequency analysis with some $S_\mathbf{A}$ that shares the same minimum element hash. This      
%% This inspires us to    
% % $S_\mathbf{M}$ has a large fraction of overlaps with the original plaintexts of $S_{\rm t}$    
%% Our insight is  if the {\em underlying MinHash} (that is computed from the plaintext of each ciphertext chunk element) of a ciphertext segment $S_{\rm t}$ is identified the same as that of some plaintext segment $S_{\rm a}$, then the chunks in $S_{\rm a}$ are likely to be the original plaintexts of the ciphertexts in $S_{\rm t}$. The rationale is that $S_{\rm a}$ has a large fraction of overlaps with the original plaintexts of $S_{\rm t}$  (due to Equation~(\ref{eq:broder})). In other words, we collect all ciphertext segments that have a common underlying MinHash (see Step 1), say $h$, and infer their original chunks from the plaintext segments that have the same MinHash of $h$ (see Step 2 and Step 3). By repeating the inference for each available MinHash, we can avoid some of ties incurred by classical frequency analysis, since the tied chunks may have different frequencies for the same MinHash.    
%% Similarly, we apply fixed-size segmentation to generate each segment $S_\mathbf{A}$ that consists of plaintexts of $\mathbf{A}$.
%% knowledge of the underlying content pattern of ciphertext chunks. 
%% that we need the order of each ciphertext in $\mathbf{C}$ for segmentation, while not requiring such order reflects that of corresponding plaintext. 
%% We use  and  that is generated from $\mathbf{C}$ and that is mapped from, respectively.
%% generated from $\mathbf{C}$ and its corresponding plaintext, respectively.
%% denote a segment from $\mathbf{C}$ by  
%% Note that we need the ordering of $\mathbf{C}$ to ensure each segment includes the continue content, while not requiring such ordering reflects that of corresponding plaintext.  
%% {\em fixed-size} data units,   
%%In this work, we implement fixed-size segmentation scheme to generate ciphertext segments. More sophisticated segmentation schemes (e.g., variable-size segmentation \cite{lillibridge09, qin17}) can be applied to address content shifting, yet they depend on the knowledge of the underlying content pattern of ciphertext chunks. For clustering, we define the distance of two ciphertext segments $S_{\rm tar}$ and $S_{\rm tar}'$ by one minus their Jaccard similarity coefficient:
%%
%% Given $\mathbf{C}$, we partition   
%% The clustering-based attack builds on {\em similarity-based approach} \cite{li17,qin17,xia11,bhagwat09}. Specifically, the similarity-based approach groups multiple adjacent chunks into a coarse-grained unit called {\em segment}, and considers that two segments are {\em similar} if they have the same minimum hash value (i.e., {\em MinHash}) over their chunk elements. By Broder's theorem \cite{broder97}, the probability that two segments $S$ and $S'$ are similar is the same as their Jaccard similarity coefficient: 
%% \subsection{Attack Description}
%% {\color{blue}
%% {\bf --- not good enough ---}
%% To capture similarity in inference attack, we partition the auxiliary stream $\mathbf{M}_{\rm a}$ of plaintext chunks into {\em plaintext segments}, which comprises sequences of plaintext chunks. Correspondingly, we construct {\em ciphertext segments}, each of which is composed of the ciphertext chunks whose original plaintexts are in the same plaintext segment. For compatibility, we ensure that both  plaintext and ciphertext segments have the same size.   
%% {\bf --- not good enough ---}
%% }
%% (recall that we can access the time windows of original chunks from $\widetilde{\mathcal{L}}_{\rm order}$). 
%% We propose to launch inference attack through similar segments.

%\begin{figure}
%	\includegraphics[width=.48\textwidth]{pic/clustering-attack.pdf}
%	\caption{Overview of the clustering-based attack.}
%	\label{fig:clustering-attack}
%\end{figure}

%Figure~\ref{fig:clustering-attack} highlights the main steps of the clustering-based attack. We elaborate the details as follows.

%\paragraph{Step 2: (Identify similar classes):}
%We build on the idea of the distribution-based ranking (see \S\ref{sec:distribution-attack-description}) to identify the ciphertext and plaintext classes that correspond to the same MinHash. Specifically, for each ciphertext class with an underlying MinHash of $h$, our aim is to find the plaintext class identified by the same MinHash of $h$. Note that we cannot measure relative frequency distributions for ranking, since we do not have enough knowledge about neighboring chunks. Instead, we count the entropy of a class by the {\em occurrences of different chunks} in the class. Specifically, for a plaintext class $\mathcal{M}$, we compute its entropy:  \begin{eqnarray}
%        e_{\mathcal{M}} = \sum_{M \in \mathcal{M}} {\sf log}_2 \frac{{\sf cnt}_\mathcal{M}(M)}{|\mathcal{M}|},
%        \label{eq:clustering-entropy}
%\end{eqnarray}
%where $|\mathcal{M}|$ is the total number of logical chunks in $\mathcal{M}$ and ${\sf cnt}_\mathcal{M}(M)$ returns the number of copies of the chunk $M$ in $\mathcal{M}$. We derive similar entropy $e_\mathcal{C}$ for a ciphertext class $\mathcal{C}$, and consider $\mathcal{M}$ and $\mathcal{C}$ are {\em similar classes} (i.e., having the same MinHash), if the difference of their entropies is minimum. Our rationale is that the chunk distributions in similar classes are likely to be correlated due to deterministic encryption.

%In more details, we first sort the available ciphertext and plaintext classes separately by the number of logical chunks they include. Based on the configuration parameters of $u$, $r$ and $t$ (see \S\ref{sec:distribution-attack-description}), we pick the ciphertext class $\mathcal{C}_i$ that has the $i$-th most number of logical chunks ($1 \leq i \leq u$), and examine each plaintext class $\mathcal{M}_j$ that ranks from $i-r$ to $i+r$. We identify that $\mathcal{C}_i$ and $\mathcal{M}_j$ have the same MinHash, if the difference of their entropies is (i) minimum across all $i-r \leq j \leq i+r$ and (ii) smaller than $t$.

%% However, it is hard to classify ciphertext segments, since there still exists a challenge on identifying the underlying MinHash of ciphertext segments. Recall that  
%% By our assumption (\S\ref{sec:clustering-attack}), all ciphertext segments must have the same size. Thus, to be compatible, we also partition the original stream of plaintext chunks $\mathbf{M}_{\rm a}$ into fixed-size {\em plaintext segments}, each of which comprises a sequence of plaintext chunks.

%% We adapt the similarity-based approach to inference attack. Specifically, to capture the notion of similarity,  
%% for inferring ciphertext-plaintext chunk pairs through similar segments. Specifically, we

%\paragraph{Step 3: (Launch attack through similar classes):} For each identified similar classes $(\mathcal{C}_i, \mathcal{M}_j)$, we launch attack for two cases. If $\mathcal{C}_i$ and $\mathcal{M}_j$ have the same number of logical chunks and entropy, our attack operates on {\em segment level}. For each ciphertext segment $S_{\rm t}$ in $\mathcal{C}_i$, we examine each available plaintext segment $S_{\rm a}$ in $\mathcal{S}_j$, and infer $(S_{\rm t}, S_{\rm a})$ as a ciphertext-plaintext segment pair if $S_{\rm a}$ has the same number of logical chunks and entropy (via Equation~\ref{eq:clustering-entropy} but computed for segment) with $S_{\rm t}$. We stop the attack at segment level in this case, because there is not enough information to further extracting chunk content; otherwise it sacrifices inference precision. We argue that the segment-level attack is severe, since each segment represents a continues region of data. The adversary can learn significant information if it successfully extracts the underlying data of some segment.

%% Through experimental analysis, the segment-level attack contributes the most component of correct inferences.     
%% has the same number of logical chunks and entropy as $S_{\rm t}$. We infer that $S_{\rm a}$ is the original segment of $S_{\rm t}$.

%If $\mathcal{C}_i$ and $\mathcal{M}_j$ have different numbers of logical chunks or entropies, we apply operate classical frequency analysis to operate attack on {\em chunk level}. This can infer more ciphertext-plaintext chunk pairs, yet degrading inference precision.

%% over $\mathcal{C}_i$ and $\mathcal{M}_j$ . 
%% for each ciphertext segment in $\mathcal{C}_i$, we find the plaintext segment that has the same  
%% Specifically, for each ciphertext segment $S_{\rm t}$ in $\mathcal{C}_i$, we find the plaintext segment $S_{\rm a}$ in $\mathcal{S}_j$ such that   
%% Then, we adopt the idea of distribution-based ranking (\S\ref{sec:distribution-attack-description}) to identify the ciphertext and plaintext classes that are identified by the same MinHash.  
%%In the following, we first propose the {\em similarity-based clustering} approach, which aims to classify ciphertext segments by their underlying MinHash. Then, we elaborate how to relate a class of ciphertext segments with that of plaintext segments. 
%%\paragraph{Similarity-based clustering:}
%%works on ciphertext segments and classify them by their underlying MinHash. Then,

%\subsection{Discussion}
%\label{sec:clustering-attack-discussion}

%The main limitation of the clustering-based attack is the {\em boundary shift} of segment. The insertion of one or more chunks will shift the boundaries of all segments that come after the insertion point. This changes the chunk distributions of some segments, and  affects the precision of identifying similar classes in Step 2. The boundary shift also decreases the effectiveness of the segment-level attack in Step 3, since it leads to fewer common segments in the auxiliary data and target data. On the other hand, we cannot address the boundary-shift problem by existing approaches (e.g., the content-defined segmentation \cite{lillibridge09}), which depend on the knowledge of the underlying content pattern of ciphertext chunks.

%Even so, we argue that the clustering-based attack is severe for the virtual machine (VM) images, which store data {\em aligned} with disk block boundaries  \cite{jin09}. In \S\ref{sec:experiment-clustering}, we will examine the effectiveness of the clustering-based attack against VM workloads.

%% In \S\ref{sec:clustering-experiment}, we justify the barrier of the boundary shift in the clustering-based attack.       
% % between $\mathbf{M}_{\rm a}$ and $\mathbf{M}_{\rm t}$,  
%%We adapt the similarity-based approach to inference attack. Specifically, we apply segmentation, yet on ciphertext chunks, and generate the segments that include adjacent ciphertext chunks under the scrambled order in $\widetilde{\mathcal{L}}_{\rm order}$.

%%In this work, we implement fixed-size segmentation scheme to generate ciphertext segments. More sophisticated segmentation schemes (e.g., variable-size segmentation \cite{lillibridge09, qin17}) can be applied to address content shifting, yet they depend on the knowledge of the underlying content pattern of ciphertext chunks. For clustering, we define the distance of two ciphertext segments $S_{\rm tar}$ and $S_{\rm tar}'$ by one minus their Jaccard similarity coefficient:
%%$${\sf Sim}(S_{\rm tar}, S_{\rm tar}') = 1 - \frac{|S_{\rm tar} \cap S_{\rm tar}'|}{|S_{\rm tar} \cup S_{\rm tar}'|}.$$
%%The smaller ${\sf Sim}(S_{\rm tar}, S_{\rm tar}')$ is, the more likely that they have the same underlying MinHash. Then, we use agglomerative hierarchical clustering algorithm (via the function {\tt clusterizerrunahc} in ALGLIB \cite{alglib}) to generate the slices.

%%% For any two ciphertext segments $S_{\rm tar}$ and $S_{\rm tar}'$, we define their similarity distance by one minus their Jaccard similarity coefficient:
%%% $${\sf Sim}(S_{\rm tar}, S_{\rm tar}') = 1 - \frac{|S_{\rm tar} \cap S_{\rm tar}'|}{|S_{\rm tar} \cup S_{\rm tar}'|}.$$

%%In addition, we partition $\mathbf{M}_{\rm aux}$ to form plaintext segments, each of which is a region of logically adjacent chunks in $\mathbf{M}_{\rm aux}$. For compatibility, we require that the plaintext segment has the same (fixed) size with ciphertext segment. Then, we classify plaintext segments by their MinHash (note that we have full access to the MinHash of each plaintext segment), and obtain several plaintext slices.

%%To launch attack, we apply frequency analysis to the ciphertext and plaintext slices that are identified by the same MinHash. This is for two reasons. First, tied chunks may have different frequencies in some slices, and these ties can be break. Second, the original chunks are likely to be in the

%%each of which includes the segments that have the same MinHash (note that we have fully access to the MinHash of each plaintext segment).

%%Like prior works \cite{li17,qin17,xia11,bhagwat09}, we

%%Specifically, we  We also generate ciphertext segments, which include adjacent ciphertext chunks yet under the scrambled order in $\widetilde{\mathcal{L}}_{\rm order}$.

%%The clustering-based attack uses {\em ``divide-and-conquer''} strategy to improve the inference accuracy of tied chunks. At a high level, it partitions $\mathbf{M}_{\rm aux}$ into {\em plaintext slices}, and each slice includes a number of plaintext chunks. It generates similar {\em ciphertext slices} from $\widetilde{\mathcal{L}}_{\rm order}$, and pairs each ciphertext slice with some plaintext slice of $\mathbf{M}_{\rm aux}$. It finally applies frequency analysis to infer original chunks from each slice pair. The rationale is that tied chunks may have different frequencies in some slices.

%%% To generate slices, we build on the {\em similarity-based approach} \cite{li17,qin17,xia11,bhagwat09}. Specifically, it defines a coarse-grained unit called {\em segment}, which comprises multiple adjacent chunks. Two segments are said {\em similar}, if they have the same minimum hash (i.e., MinHash) over their chunk elements. By Broder's theorem \cite{broder97}, the probability that two segments $S_i, S_j$ are similar is the same as their Jaccard similarity coefficient: 
%%% $${\sf Pr}[{\sf MinHash}(S_i) = {\sf MinHash}(S_j)] = \frac{|S_i \cap S_j|}{|S_i \cup S_j|},$$
%%% where ${\sf MinHash}(S)$ is the minimum hash of chunk element in $S$. Thus, prior works \cite{li17,qin17,xia11,bhagwat09} can apply the similarity-based approach to improve the effectiveness of near-exact deduplication.

%%To form a plaintext slice, we collect all

%%===

%%Specifically, we add the segments that have the same MinHash into an identical slice, and pair a ciphertext slice with a plaintext slice if they have the same chunk. Thus,

%%each slice includes the segments that have the same MinHash. Since

%%the original chunk of ciphertext chunk is likely to be in

%%Our insight is that if two ciphertext segments have a large fraction of common chunks, they are likely to have the same underlying MinHash.

%%By Broder's theorem, similar segments are likely to have a large fraction of common chunks.

%%Our insight is to generate slices

%%A plaintext segment is a region of logically adjacent chunks in $\mathbf{M}_{\rm aux}$, while a ciphertext segment includes several adjacent ciphertext chunks defined in the scrambled order in $\widetilde{\mathcal{L}}_{\rm order}$. We measure the {\em similarity} of two segments (e.g., $S_i$ and $S_j$) by their Jaccard similarity coefficient (e.g., $|S_i \cap S_j|/|S_i \cup S_j|$).

%%Our insight is to generate the slices that include all segments identified by the same MinHash.

%%We propose a new inference attack, the {\em clustering-based attack}, which uses {\em ``divide-and-conquer''} strategy to improve the severity of frequency analysis.

%%The clustering-based attack builds on

%%The key technique underlying the attack is {\em similarity-based approach} to generate slices.

%%To generate slices, the clustering-based attack uses a {\em similarity-based approach}, which builds on a coarse-grained unit, called {\em segment}, of chunks. A plaintext segment is a region of logically adjacent chunks in $\mathbf{M}_{\rm aux}$. We also extract ciphertext segments, which include adjacent ciphertext chunks defined in the scrambled order in $\widetilde{\mathcal{L}}_{\rm order}$.

%%It can  based

%%We generate a plaintext segment as a region of  On the other hand, we form ciphertext segments directly based on the scrambled order of each ciphertext chunk.

%%Specifically,

%%   which can infer original chunk content with coarse-grained order information.

%%In the following, we present the attack details step by step.

%%% We propose the {\em clustering-based attack}. At a high level, it partitions $\mathbf{M}_{\rm aux}$ into {\em plaintext slices}, which include a number of plaintext chunks. It generates similar {\em ciphertext slices} from $\widetilde{\mathcal{L}}_{\rm order}$, and pairs each ciphertext slice with some plaintext slice of $\mathbf{M}_{\rm aux}$. It finally applies frequency analysis to infer original chunks from each ciphertext-plaintext slice pair. In the following, we present the attack step by step.

%%\paragraph{Step 1: Group chunks into segments.}
%%The clustering-based attack defines a coarse-grained unit, called {\em segment}, of chunks. We generate a plaintext segment as a region of logically adjacent chunks in $\mathbf{M}_{\rm aux}$. On the other hand, we form ciphertext segments directly based on the scrambled order of each ciphertext chunk.

%%By segmentation, we expect we can limit order scrambling within each segment.

%%Note that since we cannot identify the underlying content of ciphertext chunks, our segmentation scheme is with a fixed size rather than content based.

%%it can only form ciphertext segment based on the scrambled orders of ciphertext chunks. Even so, we expect the order scrambling can be located within each segment.

%%By segmentation, we expect the order

%%For $\mathbf{M}_{\rm aux}$, a (plaintext) segment includes a fixed-size region of logically adjacent chunks. On the other hand, we cannot identify the accurate order of each ciphertext chunk. Thus, we elaborate segment as based on the scrambled orders in $\widetilde{\mathcal{L}}_{\rm order}$.

%%\paragraph{Step 2: Classify plaintext segments by MinHash.}

%%\paragraph{Step 3: Cluster ciphertext segments by similarity.}

%%% The rationale is that tied chunks may have different frequencies in some slices.

%%The clustering-based attack builds on a {\em similarity-based approach} to generate slices of chunks. First, it groups chunks into a coarse-grained unit, called {\em segment}.

%%After segmentation, we expect the order scrambling only appears within each segment.

%%\paragraph{Step 3: Slice pairing.}

%%\paragraph{Step 4: Chunk inference.}

%%We start with a na\"{i}ve slicing approach. Specifically, we partition $\mathbf{M}_{\rm aux}$ into fixed-size regions of

%%To realize slicing, we propose a  
%%generates plaintext and ciphertext slices from $\mathbf{M}_{\rm aux}$ and $\widetilde{\mathcal{L}}_{\rm order}$, respectively. Each slice includes a number of plaintext or ciphertext chunks.

%%To generate slices, the attack builds on the similarity characteristics of workloads.

%%The attack apply to pair ciphertext-plaintext slices,

%%First, the adversary

%%We start with a na\"ive frequency analysis.

%%builds on similarity.

%%\paragraph{Similarity-based clustering:}

%%\paragraph{Distribution-based pairing:}

%%At a high level, the clustering-based attack partitions $\mathbf{M}_{\rm aux}$ into {\em plaintext slices}, and each slice includes a number of plaintext chunks. It also generates ciphertext slices from $\widetilde{\mathcal{L}}_{\rm order}$, and pairs each ciphertext slice with some plaintext slice of $\mathbf{M}_{\rm aux}$. Then, it applies frequency analysis on all paired ciphertext-plaintext slices to infer chunks.

%%The similarity-based clustering builds on Broder's theorem, which states that the probability that the two sets $S_1$ and $S_2$ have the same minimum hash element is the same as their Jaccard similarity coefficient.

%%\subsection{Attack Description}

%%Our idea is to group all chunks

%%We first overview how the clustering-based attack works.  First, the adversary partitions $\mathbf{M}_{\rm aux}$ into {\em plaintext slices}, and each slice includes a number of plaintext chunks. It also generates ciphertext slices from $\widetilde{\mathcal{L}}_{\rm order}$. Then, the adversary pairs each ciphertext slice with some plaintext slice, and applies frequency analysis on all paired slices to infer chunks. This mitigates the chunk tiles in some extent, since the globally tied chunks may not have the same frequency in all paired slices.

%%at high level. Generally, the clustering-based attack builds on the  It partitions

%%The clustering-based attack builds on the  strategy. Specifically, it cuts $\mathbf{M}_{\rm aux}$ into several {\em plaintext slices}, and each slice includes a number of plaintext chunks.

%%A naive slicing solution is to

%%Based on the auxiliary information, it

%%Instead of attacking with $\mathbf{M}_{\rm aux}$ and $\widetilde{\mathcal{L}}_{\rm order}$ in their entirety, it divides the adversarial knowledge into plaintext and ciphertext slices, and uses frequency analysis to identify the ciphertext-plaintext chunks in each slice.

%%Specifically, it first generates plaintext slices $\mathbf{M}_{\rm aux}$. Each slice includes a number of continuous chunks.

%%\paragraph{Attack details:}

%%\subsection{Discussion}

%%%in which the known chunk orders are {\em permuted} from the original order of corresponding chunks.

%%%We first re-define our model to adapt the setting of the two-stage attack.

%%%   which requires {\em minimum} knowledge about order information. Specifically, in the two-stage attack, the  instead, it just need to access

%%%can work with

%%%only needs {\em minimum} knowledge about order information. Specifically, it can build on

%%%We suppose that the target victim file $\mathbf{M}_{\rm tar}$ includes $n$ chunks (including duplicates), and $\pi$ is a permutation by randomizing the logical orders of every $k$ chunks.

%%%over their order set $\{1,\ldots,n\}$.

%%%%We define $\widetilde{\mathcal{L}}_{\rm order} = \{(C, \pi({\sf ord}(M))): (M, *) \in \mathbf{M}_{\rm tar} \wedge C = \mathcal{E}_K(M)\}$.

%%%{\bf TO DO}
%%%% suppose the target victim file includes $n$ logical chunks, and $\pi$ is a permutation on the set $\{1,\ldots,n\}$. }

%%%\paragraph{Attack Overview:}

%%%\subsection{Attack Overview}

%%%The two-stage attack follows the {\em divide and conquer} principle. Figure \ref{fig:overview} outlines the overview of the two-stage attack.

%%\subsection{Similarity-based Clustering}

%%\subsection{Attack Description}

%%\subsection{Attack Example}

\chapter{Experiments}
\label{sec:experiment}

In this section, we present the trace-driven evaluation results to demonstrate
the severity of our proposed frequency analysis attacks against encrypted
deduplication.

\section{Methodology}
\label{sec:dataset}

\begin{table}[!t]
    \caption{Characteristics of experimental datasets.}
\small
\label{tab:dataset}
\renewcommand{\arraystretch}{1.2}
\vspace{-3pt}
\centering
\begin{tabular}{|c|c|c|c|}
\hline
 \multirow{2}{*}{\bf Dataset} & \multirow{2}{*}{\bf Category} & \multicolumn{2}{c|}{\bf Characteristics in Each Snapshot} \\
\cline{3-4}
    & &  \#Logical (Million) & \#Unique (Million) \\
\hline
    \multirow{6}{*}{FSL} & User004  & 1.0-1.3 & 0.7-0.9\\
 \cline{2-4}
              & User007 &  3.5-5.2 & 2.3-3.6 \\
 \cline{2-4}
              & User012 &  25.0-26.4 & 8.9-9.7 \\
\cline{2-4}
              & User013 &  1.8-5.7 & 1.2-4.2 \\
\cline{2-4}
              & User015 &  13.4-20.5 & 9.0-11.0 \\
\cline{2-4}
              & User028 &  6.0-10.3 & 3.5-6.8 \\
\hline
\hline
    \multirow{4}{*}{MS} & Win7  & 61.6-61.8 & 61.1-61.3\\
\cline{2-4}
              & Serv-03 & 10.6-10.7 & 8.4-8.5\\
\cline{2-4}
              & Serv-08 & $\sim$6.5 & $\sim$3.8 \\
\cline{2-4}
              & Vista-B &  $\sim$7.6 & $\sim$2.0\\
\cline{2-4}
              & Vista-U &  $\sim$21.0 & $\sim$10.4 \\
\hline
\hline

    \multirow{6}{*}{VM} & User1  &  \multirow{6}{*}{2.6} & $\sim$0.9 \\
\cline{2-2}
\cline{4-4}
              & User2 &  & 1.1-1.3 \\
\cline{2-2}
\cline{4-4}
              & User3 &  & 0.9-1.1 \\
\cline{2-2}
\cline{4-4}
              & User4 &  & $\sim$0.9 \\
\cline{2-2}
\cline{4-4}
              & User5 &  & 0.9-1.0 \\
\cline{2-2}
\cline{4-4}
              & User6 &  & 0.9-1.1 \\
\hline
\end{tabular}
\medskip

\raggedright
    The notations \#Logical and \#Unique denote the total number of logical and unique chunks in each experimental snapshot, respectively. 
    % All VM images have a fixed size of 10GB and hence the same number of logical chunks.
\end{table}

%\begin{table}[!t]
%\small
%\caption{Experimental datasets.}
%\label{tab:dataset}
%\renewcommand{\arraystretch}{1.2}
%\vspace{-3pt}
%\centering
%\begin{tabular}{|c|c|c|}
%\hline
%{\bf Dataset} & {\bf Category} & {\bf Approximate Logical Size} \\
%\hline
%\hline
%%\multirow{2}{*}{FSL} & Physical  & 431.9GB  & 659.3GB & 584.3GB \\
%	\multirow{6}{*}{FSL} & User004  & 10GB/backup $\times$ 14 backups \\
%\cline{2-3}
%			  & User007 & 39GB/backup $\times$ 14 backups \\
%\cline{2-3}
%			  & User012 & 244GB/backup $\times$ 14 backups \\
%\cline{2-3}
%			  & User013 & 22GB/backup $\times$ 14 backups\\
%\cline{2-3}
%			  & User015 & 158GB/backup $\times$ 14 backups\\
%\cline{2-3}
%			  & User028 & 77GB/backup $\times$ 14 backups\\
%\hline
%\hline
%\multirow{4}{*}{MS} & WIN7  & 425GB/snapshot $\times$ 4 snapshots \\
%\cline{2-3}
%			  & Serv-03 & 78GB/snapshot $\times$ 4 snapshots \\
%\cline{2-3}
%			  & Serv-08 & 48GB/snapshot $\times$ 4 snapshots \\
%\cline{2-3}
%			  & Vista-B & 55GB/snapshot $\times$ 4 snapshots \\
%\cline{2-3}
%			  & Vista-U & 159GB/snapshot $\times$ 4 snapshots \\

%\hline
%\hline

%\multirow{6}{*}{VM} & User1  & 25GB/backup $\times$ 13 backups \\
%\cline{2-3}
%			  & User2 & 28GB/backup $\times$ 13 backups \\
%\cline{2-3}
%			  & User3 & 26GB/backup $\times$ 13 backups \\
%\cline{2-3}
%			  & User4 & 25GB/backup $\times$ 13 backups\\
%\cline{2-3}
%			  & User5 & 25GB/backup $\times$ 13 backups\\
%\cline{2-3}
%			  & User6 & 27GB/backup $\times$ 13 backups\\

%% \multicolumn{2}{|c|}{\bf Storage saving} & 98.6\% & 98.3\% \\
%\hline
%\end{tabular}
%\end{table}
We evaluate our attacks using the following real-world datasets, whose
characteristics are summarized in Table~\ref{tab:dataset}. 
% Table~\ref{tab:dataset} summarizes the characteristics of the experimental datasets used in our experiments. 
% We evaluate our attacks using the following datasets. 
% investigate the security implications of the leakages (see \S\ref{sec:background}) by means of simulated attacks,

\begin{itemize}[leftmargin=*]
\item 
\textbf{FSL:} This dataset is collected by the File systems and
        Storage Lab (FSL) at Stony Brook University \cite{sun16,FSL14,sun18}. We focus on
the {\em fslhomes} snapshots, each of which includes an ordered list of 48-bit
chunk hashes that are produced by variable-size chunking under an average size
of 8KB, as well as the corresponding metadata information (e.g., chunk size,
file name extension, etc). We pick the snapshots from January 22 to May 21 in
2013, and select six users (i.e., User004, User007, User012, User013, User015,
and User028) that have the complete daily snapshots over the whole duration.
We collect these snapshots on a weekly basis, and hence form 14 weekly full
backups for each user.  
\item 
\textbf{MS:} This dataset is collected by Microsoft
\cite{meyer11} and publicized on SNIA \cite{ms}. The original dataset contains
the Windows file system snapshots that span from September 5 to October 31,
2009. Each snapshot is represented by the 40-bit chunk hashes under different
average sizes obtained from Rabin fingerprinting \cite{rabin81}.  We focus on
the snapshots that have been installed with the operating systems in the
following categories: Windows 7 (Win7), Microsoft Windows Server 2003
(Serv-03), Microsoft Windows Server 2008 (Serv-08), Microsoft Windows Vista
Business Edition (Vista-B), and Microsoft Windows Vista Ultimate Edition
(Vista-U). In each category, we pick four snapshots, each of which is
configured with the average chunk size of 8KB.   
\item 
\textbf{VM:} This dataset is collected from a university programming course in
Spring 2014. The original dataset includes a number of VM image snapshots for
the students enrolled in the course, and each snapshot has a fixed size of
10GB and is represented by the ordered list of SHA-1 hashes of 4KB fixed-size
chunks. We focus on 6 users (i.e., User1-User6) and extract their snapshots
into 13 weekly backups.  
%Prior studies \cite{qin17, li15} have used some variants of the dataset for
%different evaluation purposes, and we aim to validate the severity of the
%clustering-based attack against VM disk images.   
\end{itemize}

Our datasets do not contain actual content, so we mimic the adversarial
knowledge based on chunk hashes. Specifically, we use the ordered lists of
chunk hashes in some snapshots as the auxiliary information $\mathbf{A}$ and
the ground truth $\mathbf{M}$, respectively. To simulate encryption, we apply
an additional hash function over each original chunk hash (that represents a
plaintext) in $\mathbf{M}$, and truncate the result into an agreed number of
bits specific to the used dataset. The truncated result mimics a ciphertext in
$\mathbf{C}$. For each inferred ciphertext-plaintext pair $(C, M)$, we verify
its correctness by applying the same simulated encryption on $M$ and comparing
the result with $C$. Note that the clustering-based attack can operate at the
segment level, and infer the ciphertext-plaintext segment pair $(S_\mathbf{C},
S_\mathbf{A})$.  In this case, we check $(S_\mathbf{C}, S_\mathbf{A})$ by
examining each ciphertext in $S_\mathbf{C}$ is exactly mapped from each
plaintext in $S_\mathbf{A}$.

% , although we cannot recover each chunk in the real attack.   
% We count the leakage (see \S\ref{sec:threat}) of each ciphertext chunk, and use it for our inference attacks.  
% MD5 on each hash (that represents a plaintext) in $\mathbf{M}$, and truncate the resulting hash into an agreed number of bits (e.g., 48-bit for FSL, 40-bit for MS, and 160-bit for VM).

We measure the severity of the attacks by the inference rate and the inference
precision (see Section~\ref{sec:threat}).

\section{Results of Distribution-based Attack}
\label{sec:experiment-distribution}

\begin{figure*}[t]
    \centering
    \begin{tabular}{p{.31\textwidth}p{.31\textwidth}p{.31\textwidth}}
        \multicolumn{3}{c}{\includegraphics[width=.7\textwidth]{pic/legend-fsl-line.pdf}} \smallskip \\
        \includegraphics[width=.3\textwidth]{pic/distribution-impact-u.pdf} &
        \includegraphics[width=.3\textwidth]{pic/distribution-impact-r.pdf} &
	    \includegraphics[width=.3\textwidth]{pic/distribution-impact-t.pdf} \medskip \\
        {\footnotesize 
        \centering
        (a) Impact of $u$: $r$ = 0; $t \rightarrow \infty$
        } &
        {\footnotesize
        (b) Impact of $r$: $u$ = 128 for User004, User013 and User015, and $u$ = 256 for User007, User012 and User028; $t \rightarrow \infty$
        } &
        {\footnotesize
        (c) Impact of $t$: $u$ = 128 for User004, User013 and User015, and $u$ = 256 for User007, User012 and User028; $r$ = 10
        } \\
    \end{tabular}
    \caption{Experiment 1 (Impact of parameters): impact of $(u, r, t)$ in distribution-based attack.}
    \label{fig:distribution-impact}
\end{figure*}

\paragraph{Experiment 1 (Impact of parameters):}
We evaluate the impact of the parameters $(u, r, t)$ in the distribution-based
attack. We drive our evaluation using the FSL dataset, and use the 12th weekly
backup of each user as the auxiliary information to infer original plaintexts
in corresponding 14th weekly backup.  We configure $t \rightarrow \infty$ and $r$ = 0 to
evaluate the impact of $u$ (in this case, the distribution-based attack
reduces to the locality-based attack \cite{li17}). Our rationale is to avoid
the disturbances by other parameters.

Figure~\ref{fig:distribution-impact}(a) shows the impact of $u$,
when we vary $u$ from 2 to 512. Regarding inference rate, we have the same
observation as the prior work \cite{li17}. Specifically, the inference rates
first increase with $u$, since the attack can infer more ciphertext-plaintext
pairs. After hitting the maximum values (e.g., 13.9\% for User004, 13.6\% for
User007, 1.4\% for User012, 0.5\% for User013, 0.7\% for User015, and 6.1\%
for User028), they decrease.  The reason is that the underlying frequency
analysis introduces a large number of false positives that compromise the
inferences over corresponding neighbors.

The prior work \cite{li17} does not report the inference precision about the
attack. We observe that the inference precisions for all users are at a
fairly low level (e.g., less than 40\%), except the case of $u = 2$ for
User028 that does not introduce any false positives. On the other hand, the
inference rate in the special case is about 0.0001\%, meaning that the attack
only infers a few ciphertext-plaintext pairs. In addition, as $u$ increases,
the inference precisions decrease slightly. For example, when $u$ increases
from 2 to 512, the inference precision of User004 drops from 30.7\% to 12.8\%.

{\bf Observation (1) --} {\em A relatively larger $u$ increases the inference
rate, yet it decreases the inference precision (i.e., more false positives are
introduced). }

Informed by the impact of $u$, we set $u$ at 128 for User004, User013 and
User015, and at 256 for User007, User012 and User028, respectively, in order
to evaluate the impact of $r$ and $t$. 
% {\bf Note that the configuration
% exceeds the best one that leads to the highest inference rate. PC: I don't
% quite understand???} 
Our rationale is to increase the coverage of inferred ciphertext-plaintext
pairs, while we use $r$ and $t$ to filter possibly false positives.

We first configure $t \rightarrow \infty$ and evaluate the impact of $r$. Figure~\ref{fig:distribution-impact}(b) shows the results. We observe that the
inference rates of majority users increase with $r$. For example, when we vary
$r$ from 0 to 16, the inference rates grow from 9.5\% to 16.0\%, from 10.0\%
to 13.0\%, from 0.5\% to 0.7\%, and from 4.7\% to 5.6\% for User004, User007,
User013, and User028, respectively. The reason is that the distribution-based
attack addresses disturbances to frequency ranking, and infer more correct
ciphertext-plaintext  pairs. On the other hand, the inference rates decrease
slightly from 1.3\% to 0.8\% and from 0.6\% to 0.4\% for User012 and User015,
respectively. The reason is that they examine a large range of plaintexts and
may introduce more false positives. In addition, the inference precisions for
all users are  at a low level (e.g., less than 45\%), and have similar
tendencies with corresponding inference rates.

{\bf Observation (2) --} {\em A larger $r$ provides more opportunities of
identifying correct ciphertext-plaintext pairs, yet it also increases the
probability of having false positives.}

Then, we fix $r$ = 10 and evaluate the impact of $t$. 
Figure~\ref{fig:distribution-impact}(c) shows the results. When $t$ is small
(e.g., less than 0.5), we observe that the attack misjudges and filters a
significant number of ciphertext-plaintext pairs, even they are correct. This
introduces {\em false negatives} that reduce the inference rate. As $t$
increases, the number of false negatives decreases.  When $t$ = 1.5, the
inference rates hit the maximum values at 21.2\%, 18.2\%, 10.4\%, 1.2\%,
1.2\%, and 13.5\% for User004, User007, User012, User013, User015, and
User028, respectively. When $t$ further increases to 2, the corresponding
inference rates drop to 20.5\%, 17.1\%, 8.3\%, 1.2\%, 1.0\%, and 11.2\%,
respectively. The reason is that if $t$ is too large, it cannot filter false
positives effectively. For the same reason, the inference precisions for all
users decrease with $t$.  
% The inference rates first  increase with $t$, since the number of false negatives (i.e., misjudge some correctly inferred ciphertext-plaintext pairs in filtering) are reduced.

% implies that the distribution-based attack  returns more incorrect ciphertext-plaintext chunk pairs, which affects attack severity.

{\bf Observation (3) --} {\em A smaller $t$ filters a large fraction of false
positives, yet it introduces more false negatives.}

\paragraph{Experiment 2 (Comparison with prior attack):}
We compare the severity of the distribution-based attack with that of the
locality-based attack \cite{li17}. In addition to using the FSL dataset like
Experiment~1, we include the MS dataset for cross-dataset validation.
Specifically, for each MS category, we choose two snapshots at a time, use one
to infer the other, and evaluate the average inference rate and precision.

We consider the following attack instances for comparison. 
%
\begin{itemize}[leftmargin=*]
\item 
$\tt Baseline$: We re-implement the locality-based attack based on the
parameter configuration suggested in \cite{li17}. Specifically, it infers 5
most frequent ciphertext-plaintext pairs in the first invocation (i.e., to
initialize a set of ciphertext-plaintext pairs for iteration) of frequency
analysis, and 30 in each following invocation (i.e., to iteratively infer ciphertext-plaintext pairs from 
 neighbors).  
\item 
$\tt Distribution$ and $\tt Distribution^S$: We consider two attack instances
of the distribution-based attack, denoted by $\tt Distribution^S$ and ${\tt
Distribution}$, which operate with and without size information,
        respectively (i.e., the superscript $\tt S$ indicates that the attack instance operates with size information). 
        We configure $\tt Distribution^S$ and ${\tt Distribution}$
under the same configuration of  ${\tt Baseline}$. In addition, we choose
$r$ and $t$ in both  $\tt Distribution^S$ and ${\tt Distribution}$ in the following way: for the FSL dataset, we fix $r$ = 10 for
all users, and individually set $t$ = 1.5, 1.2, 1, 1, 0.7, and 0.9 for
User004, User007, User012, User013, User015, and User028, respectively; for
the MS dataset, we also fix $r$ = 10 for all categories, and set $t$ = 2 for
Win7 and Serv-08, and $t$ = 1.6 for Vista-U, Serv-03, and Vista-B, respectively.
This is informed by our tests for optimal configurations of the datasets.   
\item 
$\tt Distribution$-$\tt o$ and $\tt Distribution^S$-$\tt o$:
We consider two additional distribution-based attack instances, denoted by $\tt Distribution$-$\tt o$
and $\tt Distribution^S$-$\tt o$, which apply the same configurations for $r$ and $t$ as with $\tt Distribution$ and $\tt
Distribution^S$, and further use larger $u$ to increase the
coverage of inferred ciphertext-plaintext pairs.  
        Specifically, we configure $u$ in $\tt Distribution$-$\tt o$
and $\tt Distribution^S$-$\tt o$ in the following way:  
        for the FSL
dataset, we apply the same configuration of $u$ in Experiment~1; for the MS
dataset, we set $u$ = 128 for Win7, and $u$ = 30 for Serv-03, Serv-08,
Vista-B, and Vista-U. 
        % Our rationale is to increase
% the inference rate, while we expect  this only leads to a slight
% degradation of the inference precision since the distribution-based attack
% filters a large fraction of false positives. 
\end{itemize}

\begin{figure*}[t]
    \centering
    \begin{tabular}{c@{\hskip 2em}c}
        \multicolumn{2}{c}{\includegraphics[width=.7\textwidth]{pic/legend-fsl-bar.pdf}} \smallskip \\
        \includegraphics[height=2.1in]{pic/distribution-comparison-fsl.pdf} &
        \includegraphics[height=2.1in]{pic/distribution-comparison-ms.pdf} \medskip \\
        {\footnotesize 
        (a) FSL dataset 
        } &
        {\footnotesize
        (b) MS dataset 
        } \\
    \end{tabular}
    \caption{Experiment 2 (Comparison with prior attack): comparison of attack severity for distribution-based attack and locality-based attack.}
    \label{fig:distribution-comparison}
\end{figure*}

% \begin{itemize}[leftmargin=*]
	% \item {\em Distribution-I:} We configure our proposed distribution-based attack with the {\em same} configuration of the baseline above. Informed by Experiment 3, we further choose the distribution-based ranking parameters in the following way: for the FSL dataset, we fix $r$ = 10 for all users, and individually set $t$ = 1.5, 1.2, 1, 1, 0.7, and 0.9 for User004, User007, User012, User013, User015, and User028; for the MS dataset, we fix $r$ = 10 for all categories, and configure $t$ as 2 for Win7 and Serv-08 and as 1.6 for Vista-U, Serv-03, and Vista-B, respectively.

	% \item {\em Distribution-II:} We configure our proposed distribution-based attack with the same ranking configuration of distribution-I, while building on a larger $u$ to infer more chunk pairs. The rationale is to increase inference rate, while we expect the inference precision is degraded slightly as the attack can filter out unreasonable inferences. Specifically, for the FSL dataset, we set $u$ = 128 for User004, User013 and User015, and $u$ = 256 for User007, User012 and User028, respectively; for the MS dataset, we set $u$ = 128 for Win7, and $u$ = 30 for Serv-03, Serv-08, Vista-B, and Vista-U, respectively.
% \end{itemize}

Figure~\ref{fig:distribution-comparison}(a) shows the
comparison results of the FSL dataset. We observe that different instances of
the distribution-based attack outperform the locality-based attack in almost
all cases. For example, regarding User028, the lowest inference rate of the
distribution-based attack is 11.4\%, with the precision of 84.1\% (due to $\tt
Distribution$), while the corresponding inference rate and precision of
$\tt Baseline$ are only 1.2\% and 1.7\%, respectively; this implies that the distribution-based attack reduces the number of false postives by 82.4\% in this case.

{\bf Observation (4) --} {\em The distribution-based attack significantly
increases the inference precision, while achieving a higher inference rate than
the locality-based attack.}

$\tt Distribution^S$ and $\tt Distribution^S$-$\tt o$ have higher inference
precisions than $\tt Distribution$ and $\tt Distribution$-$\tt o$,
respectively, since they further filter false positives by size information.
For example, for User004, $\tt Distribution^S$ and $\tt Distribution^S$-$\tt o$  reduce the fraction of false positives in  $\tt Distribution$ and $\tt Distribution$-$\tt o$ from 35.2\% to 1.7\% and from 35.3\% to 2.2\%, respectively. However, in the same case,    
 we observe that the inference rates of $\tt Distribution$ and $\tt Distribution$-$\tt o$ are 20.0\% and 21.2\%, slightly higher than those of  
$\tt Distribution^S$ and
$\tt Distribution^S$-$\tt o$ by 2.0\% and
0.4\%, respectively. The reason is that $\tt Distribution$ and $\tt
Distribution$-$\tt o$ infer a small number of correct results from the
neighbors of incorrect ciphertext-plaintext pairs. In other words,  although
$(C, M)$ is an incorrect ciphertext-plaintext pair, the neighbors of $C$ may
correspond to those of $M$ with a small probability. Even in this case, all distribution-based attack instances are more severe than the locality-based attack instance. Specifically, the inference rate of $\tt Baseline$ is only 15.2\%, lower than those of the best and the worst distribution-based attack instances by 6.0\% and 2.8\%, respectively.

% For the same reason, $\tt Baseline$ has higher inference rate than $\tt Distribution^S$ in User013.

{\bf Observation (5) --} {\em Filtering incorrect inference results improves
the inference precision, yet it degrades the coverage of inferred
ciphertext-plaintext pairs and possibly decreases the inference rate.
}

We further observe that although $\tt Distribution$-$\tt o$ and $\tt
Distribution^S$-$\tt o$ build on larger $u$, their inference rates are just
slightly higher than those of $\tt Distribution$ and $\tt Distribution^S$ by
0.4\% and 0.9\%, respectively. The reason is that the distribution-based
attack iterates inference just through neighbors, and has a bounded coverage
of inferred ciphertext-plaintext pairs. The further increase of $u$ only adds
a small number of new correct  ciphertext-plaintext pairs into results.

Figure~\ref{fig:distribution-comparison}(b) shows the
results of the MS dataset. Both locality-based and distribution-based attacks
have high inference rates and precisions in most MS categories (except Win7).
The possible reason is that MS snapshots are highly correlated (e.g., the
variance of the total number of chunks is small, as shown in
Table~\ref{tab:dataset}).  We observe that the distribution-based attack still
outperforms the locality-based attack. For example, in Vista-U, the inference
rates and precisions of all inferences of the distribution-based attack are
above 24.1\% and 96.4\%, while those of $\tt Baseline$ are 21.7\% and 87.1\%,
respectively.

Note that both  distribution-based and  locality-based attacks have low
inference rates (e.g., less than 0.01\%) in the Win7 category. The reason is
 that Win7 includes a large fraction (e.g., more than 98.8\%, as shown in
Table~\ref{tab:dataset}) of unique chunks, which cannot be correctly
inferred by the frequency analysis attacks.

% We do not include Win7  in the comparison, since all attack instances have low effectiveness. We observe all attacks have higher severity than those in the FSL dataset.

\begin{figure*}[t]
     \centering
    \centering
    \begin{tabular}{c@{\hskip 2em}c}
        \multicolumn{2}{c}{\includegraphics[width=.25\textwidth]{pic/legend-effectiveness.pdf}} \smallskip \\
        \includegraphics[height=2.2in]{pic/distribution-effectiveness-wo-size.pdf} &
	\includegraphics[height=2.2in]{pic/distribution-effectiveness-w-size.pdf} \medskip \\
        {\footnotesize 
        (a) Distribution-based attack without size information  
        } &
        {\footnotesize
        (b) Distribution-based attack with size information 
        } \\
    \end{tabular}
	\caption{Experiment 3 (Attack effectiveness): severity of distribution-based attack in FSL dataset.}
	\label{fig:experiment-distribution-effectiveness}
\end{figure*}

\paragraph{Experiment 3 (Attack effectiveness):} We consider a long-term
backup scenario and examine the effectiveness of the distribution-based attack
with the FSL dataset. Specifically, we choose the $i$th FSL weekly backup of
each user as the auxiliary information to infer original plaintexts in the corresponding $(i+w)$th FSL
weekly backup. Clearly, the smaller $w$ is, the higher correlation between the
auxiliary information and the target backup will be.  We configure the two  
distribution-based attack instances $\tt Distribution$-$\tt o$ and $\tt Distribution^S$-$\tt o$
like Experiment~2, and evaluate their inference rates and inference precisions that
are averaged for all available $i$ for each user.

Figure~\ref{fig:experiment-distribution-effectiveness}(a) shows the results. The
distribution-based attack has varying inference rate and precision  across
users. For example, in the favorable case like User004, it achieves the
highest inference rates of 24.8\%, 24.5\%, and 24.0\% with the precisions of
67.3\%, 67.0\%, and 66.5\% for $w$ = 1, 2, and 3, respectively; in the
non-favorable case like User015, the inference rate of the distribution-based
attack is only around 0.3\%. The possible reason is that the backup data from
User015 has low chunk locality.

In addition, we observe that the correlation (i.e., $w$) of the auxiliary
information has low impact on the effectiveness of the distribution-based
attack.  For example, when $w$ increases from 1 to 3, it only leads to limited
degradations on inference rate (e.g., less than 1.4\%) and precision (e.g.,
less than 5.6\%). The reason is that the distribution-based attack addresses
disturbances to frequency ranking and preserves attack effectiveness.

{\bf Observation (6) --} {\em The distribution-based attack can limit the
degradation of attack effectiveness in the presence of loosely correlated
auxiliary information.}

% We also use the instance in Experiment 2 to evaluate the effectiveness of the distribution-based attack that operates with
 % size information. 
 Figure~\ref{fig:experiment-distribution-effectiveness}(b) shows the results of $\tt Distribution^S$-$\tt o$. We observe that it has similar inference rate with $\tt Distribution$-$\tt o$,  
 while achieving much higher precision. For example, the average inference precision of all users are 93.1\%, 92.8\%, and 92.4\% for $w$ = 1, 2, and 3, respectively.

% Figure~\ref{fig:experiment-distribution-severity-ms} shows the attack results of the MS dataset. The distribution-based attack achieves high severity. For example, it can infer 24.0\% of unique chunks in Vista-U with a precision of 96.2\%.

% Although there is l

\section{Results of Clustering-based Attack}
\label{sec:experiment-clustering}

\paragraph{Experiment 4 (Impact of parameter):} We first evaluate the impact
of the parameter $k$, which defines the upper bound distance
in combining the closest clusters.  We use both the FSL and the VM datasets to
study how $k$ affects the underlying clustering scheme in the attack.
Specifically, we apply segmentation on the last backup of each considered FSL
and VM user, respectively, and generate the segments that have a fixed size of
4MB.

The clustering scheme aims to aggregate similar ciphertext segments into the
same cluster, without compromising the confidentiality of chunks in each
ciphertext segment.  To quantify its effect, we compare the results of
clustering with those of a {\em real} classification approach, which directly
classifies segments by their minimum chunk hash.  Suppose we generate $m$ real
classes of segments by classification, and $\widetilde{m}$ clusters by the
clustering scheme, respectively.  We consider {\em clustering closeness},
evaluated by $\frac{{\sf abs}(m-\widetilde{m})}{m}$ (where 
${\sf abs}(m-\widetilde{m})$ returns the absolute value of $m-\widetilde{m}$),
which quantifies how the  number of clusters approximates that of real
classes. In addition, let $\hat{m}$ be the number of clusters, in which all
segments are similar (i.e., have the same minimum chunk hash). We also
consider {\em clustering correctness}, evaluated by
$\frac{\hat{m}}{\widetilde{m}}$, which quantifies how precisely the clustering
scheme groups similar segments.

Figure~7(a) shows the results of the FSL dataset, where we
consider four FSL users (e.g., User004, User007, User015 and User028) for
saving evaluation time. The clustering closeness first increases with $k$,
since the number (i.e., $\widetilde{m}$) of clusters decreases and
approximates $m$. When $k$ increases further, the number of clusters drops
away from $m$, and leads to the increase of clustering closeness.  In
addition, we observe that the clustering correctness gradually decreases with
$k$, because some of non-similar segments (i.e., their minimum chunk hashes are
different) are aggregated into the same cluster. Both results suggest that we
can configure an appropriate $k$ to balance the closeness and correctness of
clustering. For example, when we set $k$ = 0.65 for User015, the corresponding
closeness and correctness are 1.0\% and 94.2\%, respectively. This implies
that the results of the clustering scheme  highly approximates
those of real classification.

{\bf Observation (7) --} {\em By configuring an appropriate $k$ for
clustering, we  approximate the results of  classifying segments, without the knowledge of  minimum chunk hash in each
segment.}

Figure~7(b) shows the results of the VM dataset. We observe
that the clustering closeness and correctness of all VM users have  similar
tendencies with those of FSL users. When we configure $k$ = 0.8, the average
clustering closeness of all VM users is only 3.0\%, while the corresponding
clustering correctness is as high as 93.1\%.

\begin{figure*}[t]
\centering
    \begin{tabular}{cc@{\hspace{0.3in}}p{.32\textwidth}}
    \includegraphics[width=.3\textwidth]{pic/clustering-impact-d-fsl.pdf} &
    \includegraphics[width=.3\textwidth]{pic/clustering-impact-d-vm.pdf} & 
    \includegraphics[width=.3\textwidth]{pic/clustering-effectiveness.pdf} \medskip \\
{\footnotesize 
        (a) FSL dataset } 
&
{\footnotesize 
        (a) VM dataset } 
        &  ~~~ \medskip \\
        \multicolumn{2}{p{.64\textwidth}}{
            \footnotesize Fig.~7\quad Experiment 4 (Impact of parameter): impact of $k$ in the clustering scheme; for clustering closeness, the smaller the better; for clustering correctness, the larger the better. } &
        % \multicolumn{2}{c}{\footnotesize Fig.~6\quad Experiment 4 (Impact of parameter): show impact of $d$ with clustering closeness and correctness; for clustering closeness, the smaller the better; for clustering correctness, the larger the better.} &
        {\footnotesize
Fig.~8\quad Experiment 5 (Attack effectiveness):  severity of clustering-based attack in VM dataset.
        }
\end{tabular}
    \hspace{-1in}
\end{figure*}

% \begin{figure}
% 	\includegraphics[width=.48\textwidth]{pic/clustering-impact-d.pdf}
% 	\caption{Experiment 6 (Impact of parameter).}
% 	\label{fig:experiment-clustering-impact}
% \end{figure}

\begin{table*}[!t]
\small
    \caption{Experiment 6 (Security implications)}
\renewcommand{\arraystretch}{1.2}
\vspace{-3pt}
 \begin{minipage}[t]{0.7\textwidth}
\centering
        (a) Distribution-based attacks \medskip \\
\begin{tabular}{|c|c|c|c|c|c|}
\hline

    \multirow{2}{*}{\bf Type} & \multirow{2}{*}{\bf Extension Name} & \multirow{2}{*}{\bf \centering Range of File Size}  & \multicolumn{2}{c|}{\bf Raw Inference Rate} \\ \cline{4-5} 
    & & &  $\sf Distribution$-$\sf o$ & $\sf Distribution^S$-$\sf o$ \\ \hline
\hline
    Office & doc(x), ppt(x), xls(x) & 10KB-1MB   & 4.9\% & 5.3\%\\
\hline
    Picture & jpg, png &10-100KB  & 7.7\% & 6.7\% \\
\hline
    Source & c, h, cpp, java, py & 10-20KB   & 17.1\% & 15.0\%\\
% \hline
	% Library & .a, .dll, .so \\
% \hline
	% Compression & .bz2, .gz, tar, rar, zip, 7z \\
\hline
    Database & db, po & 20-700KB   & 2.6\% & 2.4\%\\
\hline
    Disk & vmdk, img & 200MB-1GB  & 15.8\% & 16.7\%\\
\hline
\end{tabular}
\label{tab:file}
 \end{minipage}
\hfill
    \begin{minipage}[t]{0.3\textwidth}
    \centering
        (b) Clustering-based attack \medskip \\
    \begin{tabular}{|c|c|}
    \hline
        {\bf Users} & {\bf Raw Inference Rate} \\
    \hline
    \hline
        1 & 13.2\% \\ 
    \hline
        2 & 22.4\% \\ 
    \hline
        3 & 25.7\% \\ 
    \hline
        4 & 28.4\% \\ 
    \hline
        5 & 18.5\% \\ 
    \hline
        6 & 30.8\% \\ 
    \hline
    \end{tabular}
\label{tab:user}
    \end{minipage}

\end{table*}

\paragraph{Experiment 5 (Attack effectiveness):} We now study the
effectiveness of the clustering-based attack. Due to the boundary shift of
fixed-size segment, it has low effectiveness
(about 1\% inference rate in our test) against the FSL dataset.  Thus, we use
the VM dataset to examine its severity. To configure the attack, we set $k$ =
0.8 for clustering, and $(u, r, t)$ = (5000, 100, 0.5) for relating ciphertext
clusters to corresponding plaintext clusters.

In our micro-benchmarking, we find that the chunk-level inference in the
clustering-based attack only infers thousands of chunks correctly, which
contributes to a negligible inference rate (e.g., less than 0.01\%).  
% The
% reason is that each cluster includes a large number of chunks, and frequency
% analysis is ineffective in this case. 
Thus, we focus on the
segment-level inference, which presents the bottom line of severity in the
clustering-based attack. To be consistent with the chunk-level measurements, we count inference rate and precision based
on the unique chunks in each correctly inferred segment.

We use the same evaluation methodology of Experiment~3, and report the results
in Figure~8. Specifically, the x-axis describes the index $i$ (where 1 $\leq i \leq$
12) of the VM backup that is used as the auxiliary information for attack,
while the y-axis presents the average inference rate or precision of all VM
users against the $(i+w)$th backup (where $w$ = 1, 2, and 3). We observe that both the inference rate and the inference
precision fluctuate significantly. For example, when using the 3rd backup as
the auxiliary information, the attack achieves the highest inference rates at
18.1\%, 17.1\% and 16.3\%, with the precisions of 76.8\%, 75.0\% and 73.0\%
for $w$ = 1, 2, and 3, respectively. 
On the other hand, when using the 7th
backup as the auxiliary information, the corresponding inference rates and
precisions drop down to 9.6\% and 65.9\%, 6.8\% and 71.2\%, and 6.9\% and
75.6\%, respectively. The reason is that the VM users have heavy updates after
the 7th week, and this reduces the correlation  of adjacent backups. 
On
average, for $w$ = 1, 2 and 3, the clustering-based attack infers 15.8\%,
14.0\%, and 12.6\% ciphertext-plaintext pairs, with the precisions of 71.1\%,
69.1\%, and 68.9\%, respectively. 
% This demonstrates high severity against
% the VM disk images.

\section{Results of Security Implications}
\label{sec:case}
We thus far have examined the severity of inference attacks by quantifying the
correctly inferred ciphertext-plaintext pairs.  However, it remains an open
issue that what are the security implications informed by these results and
how the frequency analysis attacks bring actual damage. In the following
experiment, we evaluate the security implications of our attacks based on the
{\em raw inference rate}, defined as the percentage of raw data content
affected by correctly inferred chunks.

\paragraph{Experiment 6 (Security implications):}
We first consider the distribution-based attack, and evaluate its raw
inference rate against {\em different types} of files. We drive the evaluation
using the FSL dataset, since only the FSL dataset includes file metadata (that
includes the extension names of files) in plaintext. Specifically, we focus on
five types of files that have specific extension names (see
Table~\ref{tab:file}(a)): office files ({\em Office}), picture files 
({\em Picture}), programming source files ({\em Source}), database files 
({\em Database}), and disk image files ({\em Disk}). These files occupy more
than 60\% of raw content of FSL snapshots.

We apply the methodology of Experiment~2, and evaluate the raw inference
rates of $\sf Distribution^S$-$\sf o$ and $\sf Distribution$-$\sf o$. 
Table~\ref{tab:file}(a) shows the results. Both attack instances have high raw
inference rates against {\em Disk} (e.g., 15.8\% for 
$\sf Distribution$-$\sf o$ and 16.7\% for $\sf Distribution^S$-$\sf o$),
because each disk file includes a large number of rarely updated chunks that
form high locality within the same file. Interestingly, we observe that 
{\em Source}, although each file is of a small size, also incurs high raw
inference rates by the distribution-based attacks (e.g., 17.1\% for 
$\sf Distribution$-$\sf o$ and 15.0\% for $\sf Distribution^S$-$\sf o$). The
reason is that programming source files are often stored together in file system
(e.g., the source files that belong to the same project locate in an identical
directory) and form a large stretch of correlated chunks, which present high
locality across files. For small and scattered files (e.g., {\em Office}, 
{\em Picture}, and {\em Database}), the distribution-based attacks have
relative low raw inference rates.

{\bf Observation (8) --} {\em The severity of the distribution-based attack depends on the update frequencies, sizes, and spatiality of target files. }

We examine the security implication of the clustering-based attack using the
VM dataset. Specifically, we use the 11th  backup of each VM user  to infer original content in corresponding 13th VM
backup. Since the VM dataset does not contain any metadata, we count the raw
inference rate based on the  whole data content in each VM snapshot.
Note that we filter all zero chunks in the count of raw inference rate,
because they occupy a large fraction in VM disk images \cite{jin09}.

% switch to the clustering-based attack, and infer the content of the last (i.e., the 13th) VM backup based on the corresponding 11th backup. Since the VM dataset does not contain metadata, we evaluate the raw inference rate across different users. Specifically, like Experiment 7, we only consider segment-level attack for high precision, and count the raw inference rate based on the correctly inferred segments. Note that since VM images commonly contain a large fraction of zero chunks ,  we filter out the zero segments in our inferred raw content.

We use the same configuration of Experiment~5, and evaluate raw inference rate
based on segment-level inference.  Table~\ref{tab:user}(b) shows the results
for different users.  We observe that the clustering-based attack achieves high
severity against the VM dataset. For example, it infers up to 30.8\% raw
content of User6's VM backup. On average, the raw inference rate of all users
is as high as 23.2\%.  
% a relatively high raw inference rate.  On average, the raw inference rate is 23.2\% for all users.

{\bf Observation (9) --} {\em The clustering-based attack threatens the
confidentiality of VM disk images. }

\chapter{Countermeasure Discussion}
\label{sec:countermeasure}

In this section, we discuss the advantages and disadvantages of possible countermeasures against the leakage channels exploited in this paper. Note that the countermeasures against size leakage are not enough for preventing our attacks, in which the size information is just optional.

\paragraph{Against frequency leakage:}
MinHash encryption \cite{qin17, li17} encrypts each plaintext with a key derived from the minimum chunk hash over a set of its adjacent chunks, and possibly maps identical plaintexts into  different ciphertexts. The rationale for defense is that MinHash encryption changes frequencies, and disturbs frequency ranking. 
 Note that MinHash encryption also prevents the frequency analysis attacks in this paper, because  we target deterministic encryption (e.g., MLE \cite{bellare13a}), while MinHash encryption is non-deterministic and changes the  frequency distribution of chunks. The disadvantage is that MinHash encryption degrades the storage saving by deduplication, since it breaks the one-to-one mapping between plaintexts and ciphertexts. In addition, MinHash encryption is not an active countermeasure, since its randomness essentially depends on the minimum chunk hashes in the target workloads.

% (rather than the chunk itself \cite{bellare13a}) over its adjacent chunks, so that some identical plaintext chunks can be encrypted into different ciphertext chunks. The rationale of defense is MinHash encryption {\em changes the frequencies of chunks} and leads to rank disturbances in classical frequency analysis. In addition, the nature of MinHash encryption is {\em non-deterministic}, and prevents the distribution-based ranking (see \S\ref{sec:distribution-attack-description}) that targets deterministic encryption. On the other hand, MinHash encryption is not an {\em active} countermeasure, since its defense effectiveness is dominated by workload characteristics (i.e., depending on the diversity of MinHash). It also degrades deduplication effectiveness due to breaking the one-to-one mapping between plaintexts and ciphertexts.

A recent work \cite{zuo18} suggests intentionally adding duplicate chunks to prevent traffic analysis against client-side deduplication. The approach \cite{zuo18} can be applied to address the frequency analysis attacks, since it changes the frequencies of chunks. Compared with MinHash encryption, the countermeasure \cite{zuo18} does not degrade storage efficiency, since only duplicate chunks are added. On the other hand, it  requires the priori knowledge that if particular chunks are duplicate, and only suits the client-side deduplication, which possibly introduces additional leakage channels (see Section~\ref{sec:related}).

Several extended MLE instantiations build on strong cryptographic primitives to defend against the frequency leakage of encrypted deduplication, such as randomized encryption that supports equality testing \cite{abadi13}, hybrid encryption \cite{stanek14}, and interactions with fully homomorphic encryption \cite{bellare15}. They provide provable security, yet how they can be implemented and deployed in practice remains unexplored.

% yet how they are implemented and deployed in practice remains unexplored. 
% some random encryption schemes \cite{stanek14,bellare15,abadi13,lacharite18a}  address the frequency leakage of deterministic encryption. Other than the practical approaches \cite{qin17, li17, zuo18}, they provide provable security, yet building on computationally expensive primitives. 
% % (see Section~\ref{sec:related}).

% are proposed to address frequency leakage from cryptography aspect, yet they are not readily implemented in practice .

% Some studies \cite{stanek14,abadi13,bellare15} aim to achieve stronger security than the more practical schemes focused above. Stanek {\em et al.} \cite{stanek14} design a hybrid encryption scheme where unpopular messages are protected by semantically secure encryption for high security guarantee, while popular messages are protected by CE to enable deduplication. On the other hand, the scheme \cite{stanek14} builds on public-key primitive which is inefficient for encrypting large-size messages. Abadi {\em et al.} \cite{abadi13} construct two schemes for the messages whose distributions are publicly available. Their first scheme generates  random tags and ciphertexts to prevent frequency leakage, yet incurring expensive {\em equality test} for checking duplicates. Their second scheme produces deterministic ciphertexts, and exposes the frequencies of corresponding plaintexts. Interactive MLE \cite{bellare15} introduces interactions into encrypted deduplication, and strengthens the security of both correlated and parameter-dependent messages, yet it is impractical for the use of fully homomorphic encryption. On the contrary to these theoretical contributions \cite{stanek14, abadi13, bellare15}, this paper focuses on the applied aspect, and investigates the security vulnerabilities in practical deduplication.

\paragraph{Against order leakage:}
A simple countermeasure is to disturb the deduplication processing sequence of chunks. For example, we can operate an additional order-scrambling process on the stream of plaintexts before encryption, so as to hide the actual logical order of each plaintext. This prevents the distribution-based attack, because the adversary cannot identify neighboring information correctly. On the other hand, it is not always effective against the clustering-based attack. If scrambling  operates on just a small basis (e.g., the orders of plaintexts in each segment are scrambled), the clustering-based attack still works. 
The disadvantage of the order-scrambling countermeasure is that it breaks chunk locality and leads to performance drop in large-scale deduplication \cite{xia11,zhu08,lillibridge09}.

% On the other hand, if we operate scrambling        
% {\em scrambling}, which intentionally disturbs the deduplication processing sequence of chunks. 
% operates the stream  before deduplication and disturbs the order of each plaintext. 
% disturbs the orders of plaintexts before deduplication 
% to scramble the orders of plaintexts. Specifically, the scrambling approach , and randomly changes the order of each plaintext.   
% A countermeasure is to scramble the orders of chunks, so as to prevent adversary from learning the actual order of each chunk. One note is the scrambling countermeasure should be applied by taking similarity into account; otherwise, the adversary can exploit the property for inference attack (see \S\ref{sec:clustering-attack}). For example, applying scrambling in a small basis (e.g., within a segment) is not enough for preventing the clustering-based attack. On the other hand, large-scale scrambling breaks chunk locality completely, and leads to significant degradation of deduplication performance .

\paragraph{Against size leakage:}
As suggested by prior work \cite{ritzdorf16}, we can pad each plaintext with additional data to obfuscate the actual size of this plaintext. However, we note that the padding scheme is not straightforward, since it requires to add identical redundancies to the same plaintexts; otherwise the storage system cannot detect duplicates for deduplication. One possible solution is to build on the paradigm of MLE \cite{bellare13b,bellare13a}. We compute the cryptographic hash of each plaintext as a seed, and use it to generate variable-size pseudorandom data to be padded with the  plaintext. Like MLE, this solution comes at the expense of server-aided approach \cite{bellare13b} to defend against brute-force attack (see Section~\ref{sec:related}).

% A countermeasure is to sacrifice storage efficiency and {\em pad each chunk with additional data}, which can obfuscate the original size of this chunk. The padding scheme is not straightforward, as it is required to {\em add identical redundant data to the same chunks}; otherwise, the server cannot detect duplicates for deduplication. One possible solution is based on the spirit of MLE \cite{bellare13b,bellare13a}. 
% Specifically, we compute the cryptographic hash of each chunk as a seed, and use the seed to generate variable-size pseudorandom data to be padded with the corresponding chunk. Like MLE, this solution comes at the expense of server-aided approach \cite{bellare13b} to defend against brute-force attack (see \S\ref{sec:related}).

  Instead of variable-size chunking, we can use fixed-size chunking to 
 generate equal-size chunks for deduplication. Since all chunks have the same size, the adversary cannot exploit size information to differentiate them.  Although fixed-size chunking suffers from boundary shift, it achieves almost the same storage saving of deduplication as variable-size chunking in VM disk images \cite{jin09}. Thus, we suggest applying fixed-size chunking in its favorable workloads to prevent size leakage.

  % make the leaked size information hard to be exploited for inference attack. It suffers from the shift of chunk boundaries and is less effective for majority workloads, while prior work \cite{jin09} shows fixed-size chunking achieves almost the same storage efficiency as variable-size chunking for VM disk images.

% , although does not address size leakage explicitly, can make the available size information hard to be exploited for inference attack. On the other hand, it sacrifices deduplication effectiveness in most of storage workloads due to the shift of chunk boundaries.

\chapter{Related Work}
\label{sec:related}

\noindent
{\bf MLE instantiations:}  
Recall from Section~\ref{sec:background} that MLE \cite{bellare13a} formalizes the
cryptographic foundation of encrypted deduplication.  The first published MLE
instantiation is convergent encryption (CE) \cite{douceur02}, which uses the
cryptographic hash of a plaintext and its corresponding ciphertext as the
MLE key and the tag, respectively.  Other CE variants include: hash convergent
encryption (HCE) \cite{bellare13a}, which derives the tag from the plaintext
while still using the hash of the plaintext as the MLE key; random convergent
encryption (RCE) \cite{bellare13a}, which encrypts a plaintext with a fresh
random key to form a non-deterministic ciphertext, protects the random key by
the MLE key derived from the hash of the plaintext, and attaches a
deterministic tag derived from the plaintext for duplicate checks; and
convergent dispersal (CD) \cite{li15}, which extends CE to secret sharing by
using the cryptographic hash of a plaintext as the random seed of a secret
sharing algorithm.  Since all the above instantiations derive MLE keys and/or
tags from the plaintexts {\em only}, they are vulnerable to the offline
brute-force attack \cite{bellare13b} if the plaintext is {\em predictable}
(i.e., the number of all possible plaintexts is limited) , as an adversary can
exhaustively derive the MLE keys and tags from all possible plaintexts and
check if any plaintext is encrypted to a target ciphertext (in CE, HCE, and
CD) or mapped to a target tag (in RCE).  The brute-force attack has been
demonstrated to learn file information \cite{ce_attack}.

%Suppose an adversary learns  that the underlying message of a target
%ciphertext is drawn from a publicly available set. To recover the underlying
%message, the adversary tries each possible message from the public set,
%derives corresponding MLE key, and uses the derived key to decrypt the
%target ciphertext. If the decryption result equals the tried message, the
%adversary can deduce the underlying message.

% {\em HCE1} and {\em HCE2} \cite{bellare13a} derive tag from client side, and
% upload it along with ciphertext for deduplication. They offer better
% performance for the storage system, which can simply read the tag from
% uploads rather than computing it by hashing a possibly long ciphertext.
% {\em Random convergent encryption (RCE)} \cite{bellare13a} encrypts a
% message with a fresh random key, and protects the random key with the  MLE
% key of the message. RCE is more efficient, since it can combine both
% encryption and key generation into a single concerted pass over the message
% \cite{bellare13a}. On the other hand, RCE needs to attach a deterministic
% tag to the random ciphertext for checking duplicates. In addition to
% improving performance, {\em convergent dispersal} \cite{li15} replaces the
% random input of secret sharing by the cryptographic hash of message, so as
% to  augment CE with fault-tolerate storage.

% CE has been implemented in a wide variety of storage systems \cite{adya02, elephantdrive, mega, gnunet, freenet, cryptosphere, cox02, storer08, anderson10}.

% compute the tag $T = {\sf H}({\sf H}(M))$ as a double hash over plaintext message, and require to upload $T$ along with ciphertext for efficient deduplication. 
% A special note is RCE needs to places an appropriate tag along with ciphertext for deduplication, since its ciphertext is random. 
% Like HCE1 and HCE2, RCE , and 
% the message encryption and MLE key derivation of RCE can be combined into a single concerted pass over the possibly long message.

To protect against the offline brute-force attack, DupLESS \cite{bellare13b}
implements server-aided MLE by managing MLE keys in a standalone key server,
which ensures that each MLE key cannot be derived from a message offline.
DupLESS employs two mechanisms to achieve robust MLE key management: (i)
oblivious key generation, in which a client always obtains a deterministic MLE
key for a message from the key server without revealing the message content to
the key server, and (ii) rate limiting, which limits the key generation
requests from the client and prevents the online brute-force attack.  Other
studies extend server-aided MLE to address various aspects, such as reliable
key management \cite{duan14}, transparent pricing \cite{armknecht15},
peer-to-peer key management \cite{liu15}, and rekeying \cite{qin17}.  However,
server-aided MLE still builds on deterministic encryption.  To our
knowledge, existing MLE instantiations (based on either CE or server-aided
MLE) are all vulnerable to the inference attacks studied in this paper.

%In addition, existing MLE instantiations lack active protection against the
%size 
%vulnerabilities explored in this paper, since they generate deterministic
%ciphertexts or tags for deduplication. In addition, they lack active
%protection against the size and order leakages, which can be exploited to
%increase the severity of frequency analysis.

%SS \cite{bellare13b}, follow-up studies (see \cite{shin17} for a complete
%survey) address additional issues, including . Liu {\em et al.} \cite{liu15}
%propose to encrypt each message with a random key, and share the key among
%the clients that have the same message. This prevents brute-force attack due
%to the use of random keys, while mitigating security dependence on a global
%secret.

% All above MLE instantiations transform identical message to the same ciphertext or tag, and hence incur the frequency leakage. They also lack of active protection against the size and order leakages. 
% via password-based key exchange. This addresses , and also prevents brute-force attack. 
% Liu {\em et al.} \cite{liu15} propose to share encryption keys via a password-based key exchange protocol, so as to mitigate the dependence of the key manager. All above works apply deterministic encryption and are susceptible to frequency leakage. They also lack of active protection against the size and order leakages.

\paragraph{Attacks against (encrypted) deduplication:} In addition to the
offline brute-force attack, previous studies consider various attacks against
deduplication storage, and such attacks generally apply to encrypted
deduplication as well.  For example, the side-channel attack
\cite{harnik10,halevi11} enables adversaries to exploit the deduplication
pattern to infer the content of uploaded files from target users or gain
unauthorized access in client-side deduplication; it is shown that the
side-channel attack (and other related attacks) was successfully launched
against Dropbox in 2010 \cite{mulazzani11}.  The duplicate-faking attack
\cite{bellare13a} compromises message integrity via inconsistent tags.
Ritzdorf {\em et al.} \cite{ritzdorf16} exploit the leakage of the chunk size
to infer the existence of files.  The locality-based attack \cite{li17}
exploits frequency analysis to infer ciphertext-plaintext pairs.  Our
work follows the line of work on inference attacks \cite{ritzdorf16,li17}, yet
provides a more in-depth study of inference attacks against encrypted
deduplication via various types of leakage.

%Our distribution-based attack inherently implies the prior attack \cite{li17}
%(see \S\ref{sec:distribution-attack-description}). We also propose the
%clustering-based attack that does not need the knowledge of fine-grained
%chunk orders.  
\paragraph{Defense mechanisms:} 
Section~\ref{sec:countermeasure} discusses the countermeasures agasint the frequency, order and size leakage of encrypted deduplication. 
Additional defense mechanisms are designed to protect against other types of attacks.  
% Several countermeasures are designed to defend
% against the attacks on encrypted deduplication.  
As mentioned above,
server-aided MLE \cite{bellare13b} can defend against the offline brute-force
attack. Server-side deduplication \cite{li15,harnik10,armknecht17} and
proof-of-ownership \cite{xu13,pietro12,halevi11} can defend against the
side-channel attack.  Server-side tag generation \cite{douceur02,bellare13b}
and guarded decryption \cite{bellare13a} can defend against the
duplicate-checking attack.

% MinHash encryption \cite{qin17} disturbs the
% frequency ranking of ciphertexts and is shown to defend against the frequency
% analysis based on the locality-based attack via trace analysis.  Several
% extended MLE instantiations build on strong cryptographic primitives to defend
% against the inference attacks, such as randomized encryption that supports
% equality testing \cite{abadi13}, hybrid encryption \cite{stanek14}, and
% interactions with fully homomorphic encryption \cite{bellare15}, yet how they
% are implemented and deployed in practice remains unexplored.

\paragraph{Inference attacks:}  Several inference attacks have been proposed
against encrypted databases
\cite{grubbs17,bindschaedler17,kellaris16,durak16,naveed15,lacharite18} and 
keyword search \cite{zhang16b,grubbs16,pouliot16,cash15,islam12}.  They all
exploit the deterministic encryption nature to identify different types of
leakage.  Our work differs from them by specifically focusing on frequency analysis against encrypted
deduplication.

%construct inference attacks against encrypted databases. Naveed {\em et al.}
%\cite{naveed15} propose attacks to recover the plaintext records of {\em
%CryptDB} \cite{popa11a}. Kellaris {\em et al.} \cite{kellaris16} and
%Lacharite {\em et al.} \cite{lacharite18} analyze the volumes of the data
%returned by range queries, and present generic reconstruction attacks on
%database entries. Grubbs {\em et al.} \cite{grubbs16}, Bindschaedler {\em
%et al.} \cite{bindschaedler17}, and Durak {\em et al.} \cite{durak16}
%show how to recover the plaintexts from the database column encrypted by
%order-revealing encryption. 
%
%target keyword search. Islam {\em et al.} \cite{islam12} exploit the leakage of access pattern, and recover the plaintext keywords associated with files. Cash {\em et al.} \cite{cash15} and Pouliot \cite{pouliot16} examine the security of searchable encryption under different leakage profiles. Zhang {\em et al.} \cite{zhang16b} propose file-injection attacks to recover searchable keywords. Grubbs \cite{grubbs16} build attacks against {\em Mylar} \cite{popa14} that is a practical system with keyword search enabled.    This paper differs from the above works \cite{grubbs17,bindschaedler17,kellaris16,durak16,naveed15,lacharite18,zhang16b,grubbs16,pouliot16,cash15,islam12} by launching inference attacks against encrypted deduplication.

%Other studies \cite{zhang16b,grubbs16,pouliot16,cash15,islam12} target keyword search. Islam {\em et al.} \cite{islam12} exploit the leakage of access pattern, and recover the plaintext keywords associated with files. Cash {\em et al.} \cite{cash15} and Pouliot \cite{pouliot16} examine the security of searchable encryption under different leakage profiles. Zhang {\em et al.} \cite{zhang16b} propose file-injection attacks to recover searchable keywords. Grubbs \cite{grubbs16} build attacks against {\em Mylar} \cite{popa14} that is a practical system with keyword search enabled.    This paper differs from the above works \cite{grubbs17,bindschaedler17,kellaris16,durak16,naveed15,lacharite18,zhang16b,grubbs16,pouliot16,cash15,islam12} by launching inference attacks against encrypted deduplication.

%Client-side deduplication leaks the side channel information that if
%particular messages have already been stored. Harnik {\em et al.}
%\cite{harnik10} and Halevi {\em et al.} \cite{halevi11} show how to exploit
%the side channel leakage for different purposes, including creating covert
%channels between clients and gaining access to unauthorized information.

%Some studies \cite{stanek14,abadi13,bellare15} aim to achieve stronger security than the more practical schemes focused above. Stanek {\em et al.} \cite{stanek14} design a hybrid encryption scheme where unpopular messages are protected by semantically secure encryption for high security guarantee, while popular messages are protected by CE to enable deduplication. On the other hand, the scheme \cite{stanek14} builds on public-key primitive which is inefficient for encrypting large-size messages. Abadi {\em et al.} \cite{abadi13} construct two schemes for the messages whose distributions are publicly available. Their first scheme generates  random tags and ciphertexts to prevent frequency leakage, yet incurring expensive {\em equality test} for checking duplicates. Their second scheme produces deterministic ciphertexts, and exposes the frequencies of corresponding plaintexts. Interactive MLE \cite{bellare15} introduces interactions into encrypted deduplication, and strengthens the security of both correlated and parameter-dependent messages, yet it is impractical for the use of fully homomorphic encryption. On the contrary to these theoretical contributions \cite{stanek14, abadi13, bellare15}, this paper focuses on the applied aspect, and investigates the security vulnerabilities in practical deduplication.

% {\em Duplicate-faking attack} \cite{bellare13a} compromises the integrity of data by inconsistent tags. Specifically, an adversary can attach a maliciously-generated ciphertext to a faking tag $T$, so that the following legitimate messages that have the same tag of $T$ will be removed by deduplication. It can be addressed by server-side tag generation \cite{douceur02, bellare13b} or guarded decryption \cite{bellare13a}.

% or introducing a random threshold to control client-side or server-side deduplication \cite{,harnik10}.

% Our second attack augments the prior work \cite{li17} with distribution-based ranking and achieves high inference rate and accuracy. We   
%Some studies \cite{bosman16,gruss15,xiao13} investigate the side channels of memory deduplication, and this paper differs from them in considering deduplication in outsourced storage (e.g., cloud storage).

% \paragraph{Property-revealing encryption:}
% Encrypted deduplication leaks the underlying equality of plaintext chunks for detecting duplicates. A generalized {\em property-revealing encryption} \cite{bindschaedler17} has been studied for securing database storage \cite{curtmola06,bellare07,bellare09,boldyreva09,boldyreva11,popa11}. This paper differs from these works as it targets unstructured workloads.

% both theory \cite{curtmola06,bellare07,bellare09,boldyreva09,boldyreva11} and practice \cite{popa11}.

% illustrate the weakness of searchable encryption.

% present reconstruction attacks by analyzing ;

% \cite{grubbs17,bindschaedler17,zhang16b,grubbs16,kellaris16,pouliot16,durak16,naveed15,cash15,islam12,lacharite18}  Regarding databases,    Regarding keyword search, ; further

% under different leakage settings;

% classical frequency analysis against cryptdb.

% -specific cryptographic primitives of deterministic encryption.

% applications.

% structured relational data or

% based on frequency analysis.

% % Frequency analysis has been applied in prior works \cite{grubbs17,bindschaedler17,zhang16b,grubbs16,kellaris16,pouliot16,durak16,naveed15,cash15,islam12,lacharite18} to construct inference attacks. Some attacks target , by classical frequency analysis \cite{naveed15}, exploring correlations or orderings of table columns, .

% while these approaches either target structured relational data \cite{grubbs17,bindschaedler17,kellaris16,durak16,naveed15,lacharite18} or aim to recover keywords of files \cite{zhang16b,grubbs16,pouliot16,cash15,islam12}, and cannot be applied to infer a huge number of chunks.  
% % Traditional MLE (e.g., CE) builds on a {\em public} function (e.g., the hash function) to derive encryption keys, and it is susceptible to brute-force attack \cite{bellare13a} that can be used to . The weakness can be addressed by server-aided MLE \cite{bellare13b}.  
%  % posted by the side-channel leakage in client-side and cross-user deduplication. 
%  % This paper differs from these attacks in considering an adversary from the server side.

\chapter{Conclusion}
\label{sec:conclusion}

Encrypted deduplication applies deterministic encryption, and leaks the frequencies of plaintexts. This paper revisits the security vulnerability  due to frequency analysis, and demonstrates that encrypted deduplication is even more vulnerable towards inference attacks. We propose two new frequency analysis attacks, both of which  achieve high inference rate and high inference precision, while under different assumptions of adversarial knowledge. We empirically evaluate our attacks with three real-world datasets, present a variety of new observations about their natures, and further analyze how they bring actual damages. We also discuss the advantages and disadvantages of possible countermeasures to advise practitioners for securely implementing and deploying encrypted deduplication storage systems.

% types of files are especially insecure under these attacks.    
% We propose two new inference attacks, which augment the prior attack \cite{li17} with high precision inference and relaxed adversarial knowledge, respectively.   
% While prior work \cite{li17} has illustrated the vulnerability  via frequency analysis, this paper presents an in-depth study on the security of encrypted deduplication, and       
 We pose three directions for future work. First, we consider a complete old backup as the auxiliary information, and do not study how to launch attack if the adversary only has partial knowledge about the old backup. Possibly, we can still apply the frequency analysis attacks to extract characteristics from the available partial backup, and infer ciphertext-plaintext pairs by comparing the characteristics with those in the target backup. One direction is can we design advanced inference attacks, which  perform better than directly applying our attacks in this partial knowledge case?

 % The attack effectiveness depends on how the information in the partial backup correlates with the target backup.       
 Second, we adjust the parameters of the frequency analysis attacks based on their effectiveness, which can only be learnt after the attacks have happened. We do not study how to derive the optimal parameters from auxiliary information beforehand. Future work may do better.

 % We believe the parameter configurations depend on the characteristics of workloads, but do not see how to derive them efficiently.

 % the frequency analysis attacks are parameter sensitive. We adjust parameters based on the attack effectiveness (that can only be measured after the attack happens), and do not study how to identify the optimal parameter configuration  beforehand. We believe the parameter configurations depend on the characteristics of workloads, but do not see how to derive them efficiently. Future work may do better.

 % our proposed attacks are parameter sensitive. In evaluation, we adjust the parameters based on attack results, and report the security vulnerability of encrypted deduplication under some {\em specific} parameter settings of our attacks. We do not  study how to identify the optimal parameter setting of attack without the knowledge of attack results. We begin to consider that the attack configurations possibly depend on the characteristics of target workloads, but do not see how to derive them. Future work may do better.

% help practitioners and researchers better understand the security issues in encrypted deduplication storage and motivate more research along this direction.
% While 
% of encrypted deduplication
% Although it is vulnerable to frequency analysis, prior work \cite{li17} shows that classical frequency analysis can only infer a few original chunks in practice. This paper considers to increase the effectiveness of frequency analysis with additional leakages. Specifically, we present three new inference attacks by exploiting the size and order leakages that have been witnessed in deduplication systems \cite{xia11,lillibridge09,zhu08,douceur02, wilcox-ohearn08, bellare13b}. We evaluate the effectiveness of  our attacks with real-world datasets, and show that they can infer significant amount of original data under different types of workloads. We also discuss possible countermeasures to address the leakage channels exploited by our attacks. We pose the following future works.

Third, we do not implement  attack prototypes against real-world encrypted deduplication storage systems. Another direction is to deploy our attack design and 
report the vulnerability of encrypted deduplication in practice.

% - Our attacks are parameter sensitive. One direction is to explore the relationship between configuration and workload characteristics.

% - There seems a tradeoff between size-based attack and distribution-based attack. Throughout our experiment, size-based attack operates big chunks better, since they have more variances on chunk size. The distribution-based attack is expected to operate small chunks better, because there exists more chunk locality between small chunks.

% - To defend our attacks, one approach is to obfuscate the chunk distributions. A recent work suggests to add redundant chunks to mix up network traffic. It works for changing chunk distribution, but depends on knowing if a chunk is duplicate before deduplication.

% - This paper aims to report the vulnerabilities of encrypted deduplication, while not target on implementing a real attack against practical encrypted deduplication systems. Another direction is deploy our attack design in practice to alert the vulerabilities of encrypted deduplication.

\thesisacknowledgement

\thesisloadbibliography[nocite]{reference}

%
% Uncomment following codes to load bibliography database with native
% \bibliography command.
%
% \nocite{*}
% \bibliographystyle{thesis-uestc}
% \bibliography{reference}
%

\thesisappendix

%\thesisloadachievement{publications}

%\thesistranslationoriginal
%\section{}
%
%
%\thesistranslationchinese
%
%\section{}

\end{document}

### 2018-12-12 paper/introduction.tex
ING | writing introduction over

\section{研究工作的背景与意义}
\subsection{研究背景}

随着信息技术产业的高速发展，数字信息量呈爆炸式增长。Gartner研究表明\citing{gartner2015} ，仅2015年的移动数据流量就较2014年增长59\%；并且，这一增长率将持至2018年末，移动数据流量水平达1.73亿TB。数据的快速增长导致企业面临的存储和管理成本越来越高\citing{敖莉2010重复数据删除技术}。另一方面，在存储系统所保存的数据中，高达60\%的数据都是冗余的，随着时间的推移，这些冗余数据的比例将进一步上升\citing{mcknight2006digital}。近年来，存储系统中数据高冗余的特点得到越来越多研究人员的关注，利用该特点来节省存储容量是一个热门研究课题。

数据重删技术（data deduplication）是指通过识别数据流中的冗余，只传输或存储唯一数据（unique data），而使用指向已存储数据的指针替换重复副本， 以达到节省带宽或存储空间的目的\citing{2012重复数据删除关键技术研究进展}。由于能够有效地降低存储开销，数据重删技术非常适合为管理日益增长的海量数据节省成本。在工业界，EMC Data Domain\citing{EMCDataDomain}和Avamar\citing{Avamar}、Veritas的NetBackup Appliances\citing{veritas} 以及Commvault的开放数据平台\citing{CommVault} 都是比较知名的数据重删应用产品；此外，各大云存储厂商（例如 Dropbox、Google Drive、Bitcasa、Moza等）也纷纷将数据重删技术应用于各自的云服务产品中，以提升经济效益\citing{harnik2010side}。

如图\ref{fig:数据重删系统的存储模式}所示，在支持数据重删的存储系统（统称为数据重删系统）中，重删后的任何数据块都被一个或多个文件引用，而文件则以指向这些数据块的指针的集合形式存储。这种文件共用数据块的存储模式强调了数据块的敏感性，因为一个数据块的泄漏可能扩散影响到共用这个数据块的所有文件。如何保护重删后的数据的隐私，成为信息安全领域的一个研究热点。

\begin{figure}[!htb]
    \small
    \centering
    \includegraphics[width=14cm]{DedupSystemStorageMode}
    \caption{数据重删系统的存储模式} 
    \label{fig:数据重删系统的存储模式}
\end{figure}

为了保护数据隐私，加密重复数据删除（encrypted deduplication）增加了一层作用于逻辑数据块的加密操作。如图\ref{fig:加密重复数据删除系统逻辑视图}所示，该加密层基于数据内容来产生加密密钥\citing{bellare2013message}（例如将数据块的散列值作为密钥\citing{douceur2002reclaiming}），从而将相同的明文数据块加密为相同的密文数据块。系统计算每个密文数据块的散列值(称为指纹，fingerprint)，查询指纹索引（fingerprint index）确定该数据块是否已经存储，最后保存仅具有唯一指纹的密文数据块。需要指出的是，部分加密重复数据删除方案\citing{bellare2013message}采用随机加密算法，但基于明文数据块产生指纹，因此仍然可以通过检查指纹来识别重复数据。

\begin{figure}[!htb]
    \small
    \centering
    \includegraphics[width=14cm]{EncryptDedupSystemLogic}
    \caption{加密重复数据删除系统逻辑视图}
    \label{fig:加密重复数据删除系统逻辑视图}
\end{figure}

除了指纹索引以外，加密重复数据删除系统须存储额外的元数据（metadata），包括:
\begin{enumerate}
    \item 文件元数据记录了文件内逻辑数据块与相应物理数据块的映射关系，用于重构完整文件。
    \item 密钥元数据记录了文件内逻辑数据块的解密密钥，用于恢复相应的明文内容，由于密钥元数据包含密钥信息，需由文件属主的主密钥（master key）加密后以密文形式存储。
\end{enumerate}

\subsection{问题和动机}

\textbf{数据块频率泄漏问题}

%TODO:数据块信息引用
由于基于数据块内容产生密钥，加密重复数据删除泄漏了数据块的频率信息，即如果一个明文数据块出现了n次，则它对应的密文数据块也将出现n次。另一方面，真实数据集中数据块的出现频率往往呈非均匀分布，本文调研了FSL和VM备份数据集(数据集信息见§3.2)的数据块频率分布特征，发现三种数据集有超过97\%的数据块的频率低于100次，而至多只有0.04\%的数据块的频率高于10,000次（图\ref{fig:两种真实数据集的数据块频率分布}），这种非均匀的分布特点使攻击者可以利用频率来确定相应数据块。

基于以上原因，认为加密重复数据删除可能受到频率分析\citing{naveed2015inference}的威胁，拟通过本课题，深入研究频率分析攻击对加密重复数据删除安全性的影响，以及提高频率分析攻击效果的方法。

\begin{figure}[!htb]
    \small
    \centering
    \includegraphics[width=8cm]{两种真实数据集的数据块频率分布.png} %{FSLandVMfrequencyDis.eps} %{两种真实数据集的数据块频率分布.png}
    \caption{两种真实数据集的数据块频率分布} 
    \label{fig:两种真实数据集的数据块频率分布}
\end{figure}

\subsection{研究意义}

本课题研究将填补频率分析攻击研究空白，对理解加密重复数据删除的实际安全性，并降低其在非适合场景下的误用风险具有重要作用。

尽管加密重复数据删除的频率泄漏已是学术界公认的安全问题，但针对性的频率分析攻击研究仍为空白(即利用频率泄漏来获取隐私数据仍是一个开放性问题)，致使部分厂商盲目地将加密重复数据删除技术应用于商业产品\citing{MEGA,ElephantDrive}和开源系统\citing{Cryptosphere,Freenet,GNUP2P,Tahoe-LAFS}中。本项目将研究加密重复数据删除技术在频率分析攻击下的实际安全性，以指导其在适合场景下被正确使用。

\section{国内外研究历史与现状}

\subsection{加密重复数据删除}
\label{sec:加密重复数据删除}
在传统对称加密方式下，每个用户具有不同的密钥，不同用户之间的相同明文会被加密为不同密文，难以执行(密文)重复数据删除操作。

消息锁定加密（message-locked encryption，MLE）确立了加密重复数据删除的密码学基础\citing{bellare2013message}:基于数据内容产生密钥(称为 MLE 密钥)，从而将相同明文加密为相同密文。最流行的MLE实例是收敛加密（convergent encryption，CE）\citing{douceur2002reclaiming}，它使用明文的散列值作为MLE密钥，并基于密文散列值计算指纹，以识别重复数据（如图\ref{fig:加密重复数据删除系统逻辑视图}）。基于CE的加密重复数据删除方案还包括:

\begin{enumerate}
    \item 散列收敛加密（hash convergent encryption，HCE）\citing{douceur2002reclaiming}与CE具有相同的MLE密钥产生规则，但基于明文散列值计算指纹。
    \item 随机收敛加密（random convergent encryption，RCE）\citing{douceur2002reclaiming}使用随机密钥加密以产生非确定的密文，同时也基于明文散列值来进行重复检查。
    \item 收敛扩散（convergent dispersal，CD）\citing{li2016cdstore}使用明文散列值作为秘密共享（secret sharing）的输入种子，在兼容重复数据删除的基础上 提高了密文存储的可靠性。
\end{enumerate}

上述MLE实例基于明文产生MLE密钥（CE、HCE和CD）或指纹（HCE和RCE），如果明文是可预测的(即所有可能的明文的数量有限)，这些方案易于受到离线暴力破解攻击\citing{bellare2013message,keelveedhi2013dupless}。为了抵御该攻击，DupLESS\citing{keelveedhi2013dupless}基于第三方密钥服务器实现了服务器辅助 MLE（server-aided MLE），确保无法从离线明文派生出相应的MLE密钥。以服务器辅助MLE为基础，现有研究进一步解决了加密重复数据删除的故障容错\citing{li2015cdstore,duan2014distributed}、透明价格模型\citing{armknecht2015transparent}、点对点密钥管理\citing{liu2015secure}、层次密钥管理\citing{zhou2015secdep}等问题。围绕MLE扩展功能的一系列研究包括:兼容加密重复数据删除的数据完整性审计协议\citing{li2016secure}；支持动态访问控制的加密重复数据删除系统REED\citing{li2016rekeying,qin2017design}。

无论是MLE还是服务器辅助MLE，均须为相同的明文产生相同的密文（CE、HCE、CD和DupLESS）或指纹（HCE和RCE），泄漏了数据的出现频率。一些理论研究\citing{abadi2013message,stanek2014secure,bellare2015interactive}基于零知识证明、全同态加密、双线性对运算等底层密码技术实现了随机加密，但这些方案存在计算复杂性高、依赖多轮信息交互等问题，难以应用到系统实践中。本文关注可实际应用的加密重复数据删除系统/方案的频率泄漏问题，研究其安全性影响和防御对策。

\subsection{频率分析攻击}
\label{sec:传统频率分析攻击}

频率分析\citing{katz1996handbook}是一种针对确定性加密（deterministic encryption）的密码分析技术，被应用于破解匿名查询日志\citing{kumar2007anonymizing}、破坏关键词隐私\citing{cash2015leakage,grubbs2016breaking,islam2012access,pouliot2016shadow,zhang2016all}、重构密文数据库记录\citing{naveed2015inference,bindschaedler2018tao,durak2016else,grubbs2017leakage,kellaris2016generic,lacharite2018improved} 等实际攻击。本项目研究针对数据块的频率分析攻击，与现有攻击目标（查询日志条目、关键词、数据库记录等）相比，数据块数量极其庞大（呈千万级），并且大量数据块具有相同频率，致使当前的频率分析攻击算法难以适用。

面向加密重复数据删除，已有工作\citing{li2017information}提出了基于数据块局部性（chunk locality）\citing{zhu2008avoiding,lillibridge2009sparse,xia2011silo}的频率分析攻击。本课题的部分技术路线（\cref{sec:技术路线}）就是在该工作\citing{li2017information}的基础上提出来的，并进一步研究频率分析攻击的准确率和依赖条件，以及面向真实系统的攻击原型。除了频率分析和暴力破解（\cref{sec:加密重复数据删除}）之外，加密重复数据删除还可能遭受边信道攻击\citing{harnik2010side,halevi2011proofs,mulazzani2011dark}、副本伪造攻击\citing{bellare2013message}、基于数据块长度的攻击\citing{ritzdorf2016information}等威胁，但这些攻击可通过所有权证明\citing{halevi2011proofs}、守卫解密(guarded decryption)\citing{bellare2013message}、固定长度分块等措施进行防御，而本文所研究的频率分析攻击超出了现有保护措施的防御范畴。

\section{课题的研究内容、研究目标、以及拟解决的关键问题}
\subsection{研究内容}

\subsubsection*{加密重复数据删除的频率分析攻击}

在传统频率分析模式下，攻击者能够访问明文逻辑数据块集合M和密文逻辑数据块集合$C$（$M$和$C$包含重复的明文和密文数据块）。攻击者根据出现频率分别对$M$和$C$中的数据块进行排序，然后将$C$中的密文数据块映射为$M$中与其具有相同排名的明文数据块。但是，传统频率分析在加密重复数据删除中难以形成有效的攻击，主要原因是：$M$和$C$的原始内容可能存在差异(例如$M$和$C$来源于同一个文件系统在不同时间点的备份镜像)，将打乱数据块频率排序的对应关系；并且，在频率排序过程中可能存在大量明文和密文数据块具有相同的频率，频率分析难以排序这些数据块来形成正确的对应关系。

为了提高传统频率分析的攻击效果，首先研究基于数据特征的新型频率分析攻击技术。然后，分别从抵抗频率排序干扰和降低攻击发生条件两方面改进攻击技术。最后，实现针对真实系统的频率分析攻击原型，并分析该攻击对各类数据安全性的影响。

\subsection{研究目标}

针对以上研究内容，预期实现如下研究目标: 
\begin{enumerate}
    \item 在理论上，构造针对加密重复数据删除的频率分析攻击，揭示实践中的安全隐患。
    \item 在技术上，以理论研究为支撑，设计并实现针对加密重复数据删除系统/方案的频率分析攻击工具，并在真实系统中进行理论验证和攻击效果测试。 
\end{enumerate}

\subsection{拟解决的关键问题}

本课题致力于解决传统频率分析攻击方法在针对加密重复数据删除方案/系统进行攻击时难以解决的如下问题：

\begin{enumerate}
    \item 明密文数据块的的原始内容可能存在差异(例如一组明密文集合分别来源于同一个文件系统在不同时间点的备份镜像)，将打乱数据块频率排序的对应关系。
    \item 在频率排序过程中可能存在大量明文和密文数据块具有相同的频率，基本频率分析攻击难以排序这些数据块来形成正确的对应关系。
\end{enumerate}

\section{拟采取的研究方案}
\label{sec:技术路线}

如图\ref{fig:技术路线图}所示，在支撑研究（基于数据块局部性的频率分析攻击方案\citing{li2017information}）的基础上，根据相对频率分布特性，设计抗排序干扰的攻击方法；在数据相似性的基础上，设计低依赖条件的攻击方法。最终设计出针对加密重复数据删除方案/系统的新型频率分析攻击方法及对应的原型软件工具。

\begin{figure}[!htb]
    \small
    \centering
    \includegraphics[width=15cm]{TechnicalRoute.eps}
    \caption{技术路线图} 
    \label{fig:技术路线图}
\end{figure}

\subsection{支撑研究}

基于数据块局部性的频率分析攻击方案（locality-based attack）\citing{li2017information}作为支撑研究，该方案主要用于破译加密数据备份，即已知的明文数据块集合$M$和目标密文数据块集合$C$源于同一个系统在两个不同时间点的备份镜像。攻击利用了数据块的局部性特征：在不同备份之间，绝大多数数据块保持了相同的局部顺序；例如，每天备份工作项目的进度快照，若一天内的改动较小，则在两次备份之间未被改动的大部分数据块之间的相对顺序保持不变。因此，得出一个关键推论：如果明文数据块M是密文数据块$C$的原始明文，那么M左边和右边相邻的明文数据块有较大可能也是$C$左边和右边相邻密文数据块的原始明文。

\begin{figure}[!htb]
    \small
    \centering
    \includegraphics[width=14cm]{BaseFrequencyAttack}
    \caption{基于数据块局部性的频率分析攻击} 
    \label{fig:基于数据块局部性的频率分析攻击}
\end{figure}

基于此，攻击流程如图\ref{fig:基于数据块局部性的频率分析攻击}所示：首先，对$C$和$M$应用传统频率分析（\cref{sec:传统频率分析攻击}），将获得的若干组高频明密文对加入推测结果集合 $G$；然后，每次从$G$中选取一组明密文对$(M,C)$，分别对其左右相邻的明文和密文数据块集合$L_M[M]$和$L_C[C]$，以及$R_M[M]$和$R_C[C]$实施频率分析，并将获得的高频明密文对也加入$G$；继续对$G$中的明密文对进行基于相邻数据块的频率分析，直至所有明密文对都被处理。

为了验证攻击效果，定义推测率为正确推测出原始明文的(不同)密文数据块个数与$C$中(不同)密文数据块总个数的比率。在基于真实数据集的实验验证中，攻击方案能够达到17.8\%推测率，远远高于传统频率分析方法的0.0001\%推测率。

\subsection{技术突破}

\subsubsection{基于分布的频率分析攻击方法}

\par 基于分布的频率分析攻击利用密文和明文的相对顺序信息来增强频率分析的有效性。该攻击方法建立在数据块局部性\citing{xia2011silo,lillibridge2009sparse,zhu2008avoiding}的基础上。通过以下三个关键特性构造出基于分布的频率分析攻击方法。

\begin{itemize}
    \item 数据块局部性指出数据的原始排序可能会在各种备份文件中得以保留，因此可以用于在备份文件中推断出类似的与位置相关的密文-明文对。
    \item 相邻数据的共现频率的相对频率分布可以通过分析得到。
    \item 明文及其相应的密文具有相似的相对频率分布的特性。
\end{itemize}

\subsubsection{基于聚类的频率分析攻击方法}

在基于分布的频率分析攻击方法的基础上，通过引入相似性\citing{bhagwat2009extreme}这一属性来消除基于分布的频率分析攻击方法对明文数据的细粒度顺序信息的需求。基于此提出基于聚类的频率分析攻击方法。

\section{可行性分析}

\subsection{研究方法可行}

本课题通过引入加密重复数据删除方案/系统的相关特性来设计新型频率分析攻击方法，针对性提高频率分析攻击方法的有效性。该研究问题具有很高的实际价值且在面向加密重复数据删除的攻击中，已有工作提出了基于数据块局部性（chunk locality）\citing{zhu2008avoiding,lillibridge2009sparse,xia2011silo}的频率分析攻击\citing{li2017information}，在此基础上改进攻击方案具有明确的可行性。

\subsection{研究条件可行}

前期基于数据块局部性的频率分析攻击方案给出了本课题研究两种新型频率分析攻击方法的基本理论和工具基础。在原有方案上改进即可用于本课题研究。研究者在本科阶段深入钻研了CDStore、REED、SDFS等加密重复数据删除系统，以及前期基于数据块局部性的频率分析攻击方案的理论和工具实现。这些经验可以帮助设计新型频率分析方法以及其在真实系统中的实践。

\section{本文特色与创新之处}

本文的特色与创新之处有以下几点：

\begin{enumerate}
    \item 本文针对加密重复数据删除提出了两种新型的频率分析攻击方法。除了利用由于加密重复数据删除具有确定性导致的频率泄漏之外，两种攻击都利用重复数据删除工作负载的特性来增加频率分析攻击的有效性。
    \item 本文使用多个真实数据集（包括长期备份\citing{sun2016long,FSL14}，Windows文件系统快照\citing{meyer2012study}和VM磁盘映像\citing{li2016cdstore,qin2017design}）以及开源重复数据删除系统SDFS\citing{SDFS}、Destor\citing{Destor}，评估两种新型频率分析攻击方法和基本频率分析攻击方法的实际效果。本文通过评估频率攻击方法的攻击结果，进一步分析本频率分析攻击方法对实际加密重复数据删除带来的安全性影响。
    \item 本文讨论了减少加密重复数据删除中信息泄漏的可能方案。
\end{enumerate}

### 2018-12-12 paper/main.tex
ING | writing introduction over

@@
 \documentclass[bachelor]{thesis-uestc}
+%----文内引用符号
+\usepackage[utf8]{inputenc}
+\usepackage{cleveref}
+\crefname{section}{§}{§§}
+%----------
 
@@
 
-\section{研究工作的背景与意义}
+\input{introduction}
 
-在本节中，我们将介绍普通和加密重复数据删除方法的基础知识。
-我们专注于基于块的重复数据删除，它以称为块的小型数据单元的粒度运行。图1总结了重复数据删除工作流程。具体地，存储系统首先经由一些组块过程将客户端的文件（例如，备份）分割成逻辑组块，使得每个逻辑组块由其内容的加密哈希唯一地标识，称为标签（即，指纹）。如果两个逻辑块具有相同的标记，则认为它们是相同的，而不同逻辑块具有相同标记的可能性几乎可以忽略不计[24]。存储系统仅存储相同逻辑块的副本作为物理块，并且每个相同的逻辑块通过小尺寸引用引用相同的物理块。
-基于块的重复数据删除比整个文件重复数据删除更精细，因此通常具有更高的存储效率。我们可以进一步选择固定大小或可变大小的块来进行重复数据删除。固定大小的分块将数据分区为等大小（逻辑）块，而可变大小的分块（也称为内容定义的分块）通常以内容相关的方式指定块边界（例如，通过Rabin指纹[54]）和分区将数据文件转换为可变大小的块。固定大小的分块简单而快速，而可变大小的分块在内容转换时保持存储效率，因为即使文件添加或删除了一些内容，大多数块仍然保持不变。可变大小的分块通常用在备份系统中（例如，[46]，[66]），但固定大小的分块显示对某些工作负载（例如，VM映像[38]）有效。我们的工作涉及固定大小和可变大小的分块方法。
-加密的重复数据删除解决了外包环境（例如，云存储）中的块机密性，同时保持了重复数据删除的有效性。传统的对称加密要求多个客户端通过其（不同的）密钥加密其文件数据，从而将相同的块转换为不再能够进行重复数据删除的不同加密块。消息锁定加密（MLE）[21]规范了加密重复数据删除。基线MLE实例化基于每个明文的内容（例如，基于块的重复数据删除中的逻辑组块）导出对称密钥（称为MLE密钥），并使用MLE密钥加密明文以形成密文（例如，加密的逻辑块）。因此，MLE确保将相同的明文加密为相同的密文。最后，存储系统从每个密文中导出标签并执行重复数据删除。
+%\thesisacknowledgement
 
-MLE可以实现为不同的实例化（参见第VIII节）。最受欢迎的是融合加密（CE）[29]，它已在各种存储系统中实现（例如，[3]，[5]  -  [7]，[9]，[13]，[15] ]，[28]，[58]）。 CE的主要思想是从每个明文内容的加密散列中导出MLE密钥。注意，一些MLE实例[21]允许将相同的明文加密成不同的密文。然而，他们确保标签仍然来自明文，因此他们可以通过检查标签的相等性来执行重复数据删除。
-现有的MLE实例都建立在概念确定性加密的基础上，以确保密文（或标签）确定性地从明文传递，从而保持重复数据删除的有效性，而不是传统的对称加密。虽然确定性加密提供了机密性保证，但在本文中，我们认为攻击者可以利用这种确定性来推断给定密文的原始明文。
-
-\chapter{Introduction}
-\label{sec:introduction}
-
-Modern storage systems save storage space by removing content redundancy 
-via {\em deduplication}, which stores only the data copies with unique content
-among all already stored data copies.  Field studies show that deduplication
-effectively saves substantial fractions of storage space for real-world
-storage workloads, such as backups
-\cite{zhu08,lillibridge09,wallace12,douglis17}, file system snapshots
-\cite{meyer11}, and virtual machine (VM) disk images \cite{jin09}.  Cloud
-storage services (e.g., Dropbox and Google Drive) also deploy deduplication to
-save maintenance costs \cite{harnik10}. 
-To ensure data confidentiality, clients should first encrypt their own data
-before writing the data to a storage system.  It is critical that the
-encryption approach preserves the original content redundancy pattern, so that
-duplicate data copies can still be detected and removed from the storage
-system even after encryption.
-
-We study {\em encrypted deduplication}, which combines encryption and
-deduplication in a way that each plaintext (data copy) is symmetrically
-encrypted and decrypted by a key that is derived from the content of the
-plaintext itself; in other words, should the plaintexts be duplicates, their
-resulting ciphertexts are also duplicates and hence can be deduplicated.
-Encrypted deduplication can be achieved through the formal cryptographic
-primitive known as {\em message-locked encryption (MLE)} \cite{bellare13a},
-whose instantiations have been extensively studied and realized in the
-literature (see Section~\ref{sec:background}).  MLE builds on the notion of
-{\em deterministic encryption}, which deterministically maps a plaintext to
-the same ciphertext to preserve the identical content pattern.  In addition to
-MLE, deterministic encryption is also found in symmetric searchable encryption
-(SSE) \cite{song00} and order-revealing encryption (ORE) \cite{boldyreva09},
-so as to allow efficient queries over encrypted data.
-
-%that yields the same ciphertext for a given plaintext and key, even over
-%separate executions of the encryption functions. This makes it specially
-%efficient for {\em equality test}, meaning that finding an exact match
-%plaintext is as easy as finding an exact match over the corresponding
-%ciphertext. Thus, deterministic encryption has been applied in various
-%application-specific cryptographic primitives, such as symmetric searchable
-%encryption (SSE) \cite{song00}, order-revealing encryption (ORE)
-%\cite{boldyreva09} and message-locked encryption (MLE) \cite{bellare13a},
-%so as to enable efficient queries over encrypted data.
-
-%the effectiveness of frequency analysis against deterministic encryption in
-%the context of {\em deduplication}, which stores only data copies, called
-%{\em chunks}, that have unique content among all already stored chunks. The
-%deduplication technique can effectively reduce the storage space of different
-%workloads (e.g., 68\% for primary data \cite{meyer09}, 83\% for backup data
-%\cite{meyer09}, and 80\% for virtual machine volumes \cite{jin09}),
-%and it has been deployed in various cloud storage services (e.g., Dropbox
-%and Google Drive) for minimizing maintenance cost
-%\cite{harnik10}. To protect information, (encrypted) deduplication
-%applies deterministic encryption \cite{bellare13a} on each chunk, such
-%that the redundant copies of plaintext chunks can  be removed
-%efficiently.  Compared to database records \cite{naveed15} or searchable
-%keywords \cite{islam12}, the chunks involved in deduplication constitute
-%a huge domain (e.g., over ten millions of possible plaintext values), and
-%the underlying plaintexts of some target chunks may not appear in the
-%auxiliary information. In addition, a large fraction of chunks have the
-%same frequencies in practical deduplication workloads \cite{li17}, and
-%this fact has been shown to decrease the effectiveness of frequency
-%analysis \cite{naveed15}.    Prior work \cite{li17} shows that classical
-%frequency analysis can only infer a few plaintext chunks in
-%deduplication.
-
-However, because of the deterministic nature, encrypted deduplication leaks
-information about the ciphertexts, such that the adversaries can analyze the
-ciphertexts and infer their corresponding original plaintexts.  Specifically,
-an adversary can perform {\em frequency analysis} \cite{alkadit92} on both the
-ciphertexts that are observed and the plaintexts that are known a priori.
-Then the adversary can infer the ciphertext-plaintext pairs, in which both the
-ciphertext and the plaintext in each pair have correlated frequency patterns. 
-Such inference attacks have been shown effective against database records (e.g.,
-\cite{lacharite18,grubbs17,kellaris16,naveed15,bindschaedler17,durak16}) and
-searchable keywords (e.g., \cite{pouliot16,zhang16b,cash15,islam12,grubbs16})
-that are protected by deterministic encryption.   In particular, frequency
-analysis is shown to effectively infer plaintext information from encrypted
-deduplication \cite{li17}.
-
-In this paper, we revisit the information leakage issues in encrypted
-deduplication.  We argue that encrypted deduplication can actually be even
-more vulnerable towards carefully crafted frequency analysis attacks.  Such
-sophisticated attacks not only infer a significant fraction of
-ciphertext-plaintext pairs as shown in the previous work \cite{li17}, but also
-ensure that each inferred plaintext indeed corresponds to the target
-ciphertext with a high probability.  From a statistical perspective, The
-latter implies that the number of false positives is low, or equivalently, the
-precision is high.
-
-To this end, we propose {\em two} new frequency analysis attacks against
-practical encrypted deduplication storage systems, and demonstrate their
-severity using real-world storage workloads.  Both attacks build on the
-characteristics of practical deduplication workloads.  While such
-characteristics have been exploited to improve deduplication performance and
-storage efficiency in practice, we show how to exploit them from an
-adversarial perspective.  We hope that our findings help practitioners and
-researchers better understand the vulnerabilities in encrypted deduplication
-and motivate more research along this direction.
-
-%They exploit the orders and frequencies of plaintexts preserved within a
-%sequence of ciphertexts, in order to infer ciphertext-plaintext pairs as many
-%as possible.  However, we find the prior attack  introduces a large number of
-%false positives into its inference results and has low precision in
-%extracting correct information. In other words, while capable of inferring a
-%significant fraction of ciphertext-plaintext pairs, it cannot ensure each
-%inferred plaintext is exactly mapped from the target ciphertext.
-
-% For example, our evaluation shows although the locality-based attack can correctly infer 15.2\% of ciphertext-plaintext pairs in some case, the false positives take around 65.2\% in its inference results.
-In other words, the adversary has low confidence in identifying whether the inferred ciphertext-plaintext pairs are correct or not.
-
-% In this paper, we further examine the information leakage issues in encrypted
-% deduplication and argue that encrypted deduplication is in fact even more
-% vulnerable towards inference attacks.  We show that in addition to exploiting
-% the deterministic encryption nature, an adversary can leverage other leakage
-% channels specific to the deduplication characteristics, so as to design {\em high precision} inference attacks against practical encrypted deduplication storage
-% systems.  We propose {\em two} novel inference attacks that extend frequency
-% analysis and demonstrate their severity against real-world storage workloads.
-% We hope that our findings help practitioners and researchers better understand
-% the security issues in encrypted deduplication storage and motivate more
-% research along this direction.
-
-%Note that variable-size chunking, chunk locality, and similarity are the key
-%design primitives of existing deduplication systems to improve deduplication
-%performance and storage savings.  We show how these primitives can be
-%exploited from an adversarial perspective. 
-% We show that in addition to exploiting
-% the deterministic encryption nature, an adversary can leverage other leakage
-% channels specific to the deduplication characteristics, so as to design {\em high precision} inference attacks against practical encrypted deduplication storage
-% systems.  We propose {\em two} novel inference attacks that extend frequency
-% analysis and demonstrate their severity against real-world storage workloads.
-
-\section{Overview of New Frequency Analysis Attacks}
-
-We summarize the main ideas of our two new frequency analysis attacks against
-encrypted deduplication, namely the {\em distributed-based attack} and the
-{\em clustering-based attack}. They build on different assumptions of
-adversarial knowledge.
-
-\paragraph{Distribution-based attack:}  The attack builds on the 
-{\em locality} property \cite{xia11,lillibridge09,zhu08}, which states that
-the ordering of data is likely preserved across various backup files, to infer
-the ciphertext-plaintext pairs that are in similar positions of backup files.
-In particular, it examines the relative frequency distribution based on the
-co-occurrence frequencies of adjacent data, and explores the observation that a
-plaintext and its corresponding ciphertext are likely to have similar relative
-frequency distributions. Our evaluation shows that the distribution-based
-attack reduces the number of false positives of the previously proposed
-locality-based attack \cite{li17} by up to 82.4\%, while correctly inferring
-up to 21.2\% ciphertext-plaintext pairs (higher than that of the
-locality-based attack \cite{li17} by 6\% in the same case).
-
-Furthermore, the distribution-based attack can exploit the leakage of the
-varying sizes of plaintexts to filter more false positives.  Our evaluation
-shows that it can suppress the fraction of false positives to as low as 1.7\%.
-
-%with {\em variable-size chunking} (see Section~\ref{sec:background}), which partitions file data into smaller units of varying sizes to better remove duplicate content at finer-grained granularities.
-We leverage the varying sizes of plaintexts to  filter possibly flawed inference results.
-Our evaluation shows the distribution-based attack further suppresses the fraction of false positives as low as 1.6\%.
-
-% An adversary can leverage the varying sizes of ciphertexts to infer the original plaintexts.
-Our evaluation shows that the size-based attack correctly infers up to 31.3\% of ciphertext-plaintext pairs in a real-world dataset.
-
-%{\bf Size-based attack:}  This attack exploits {\em variable-size chunking}
-%(see Section~\ref{sec:background}), which partitions file data into smaller
-%units of varying sizes to better remove duplicate content at finer-grained
-%granularities. An adversary can leverage the varying sizes of ciphertexts to
-%infer the original plaintexts.  Our evaluation shows that the size-based
-%attack correctly infers up to 31.3\% of ciphertext-plaintext pairs in a
-%real-world dataset.
-
-% We also combines 
-% This attack exploits the ordering of
-% ciphertexts before deduplication and is applicable for both fixed-size and
-% variable-size chunking approaches; in other words, we relax the adversarial
-% knowledge about the chunk size in the size-based attack.   
-% It further inspects the relative frequency distribution of the data
-% and filters any potentially flawed inference results.  Our evaluation shows
-% that the distribution-based attack infers up to 21.2\% of ciphertext-plaintext
-% pairs in a real-world dataset, while significantly reducing the number of
-% false positives compared to the prior attack \cite{li17}.
-
-\paragraph{Clustering-based attack:}  The attack relaxes the knowledge about
-the ordering pattern exploited by the distribution-based attack.  It builds on
-the {\em similarity} property \cite{xia11,bhagwat09}, which states that backup
-files share a large fraction of the same data (the ordering may not be
-preserved), to infer the ciphertext-plaintext pairs that are clustered
-in similar regions of a backup file.  Our evaluation shows that the
-clustering-based attack infers up to 30.8\% of raw data content in a
-real-world VM image dataset.
-
-%group ciphertexts and plaintexts into clusters, respectively. Then, it infers
-%the original contents of ciphertexts from the similar clusters of a backup
-%file. 
-% infer the ciphertext-plaintext pairs that are in similar
-% {\em clusters} of a backup file.
-
-\paragraph{Observations:}  We study the nature of our frequency analysis
-attacks based on real-world datasets.  In general, the distribution-based
-attack preserves the attack severity even when the prior knowledge of
-plaintexts is loosely correlated with the ciphertexts to be attacked.  The
-reason is that it uses a statistical approach to quantify the relative
-frequency distribution and addresses the disturbance to frequency ranking.  This indicates a wide
-exploitation of the distribution-based attack, which should be taken into
-account when developing countermeasures.   Also, the distribution-based attack
-is more likely to affect rarely updated large files (e.g., disk image files)
-or some correlated small files (e.g., programming source files) that are stored together, while the clustering-based
-attack mainly threatens the confidentiality of VM disk images.
-
-%We summarize the main ideas of our three inference attacks against encrypted
-%deduplication.  The inference attacks build on different assumptions of
-%adversarial knowledge.
-
-%In this paper, we propose new inference attacks that increase the effectiveness of frequency analysis with {\em various leakages} of practical deduplication.
-The key technique is based on an extensive exploitation of the characteristics of deduplication workloads, so as to {\color{blue} identify the available auxiliary information  that is highly correlated with  the underlying plaintexts of target chunks}.
-We empirically evaluate our attacks based on real-world datasets, and present new observations about the dataset characteristics for which deterministic encryption is especially insecure.
-We also discuss possible countermeasures to mitigate the leakage channels.
-In the following, we summarize the main results of this paper.
-
-%\subsection{Overview of Inference Attacks}
-
-%We summarize the main ideas of our three inference attacks against encrypted
-%deduplication.  The inference attacks build on different assumptions of
-%adversarial knowledge.
-
-%\begin{itemize}[leftmargin=*]
-%\item
-%{\bf Size-based attack:}  This attack exploits {\em variable-size chunking}
-%(see Section~\ref{sec:background}), which partitions file data into smaller
-%units of varying sizes to better remove duplicate content at finer-grained
-%granularities. An adversary can leverage the varying sizes of ciphertexts to
-%infer the original plaintexts.  Our evaluation shows that the size-based
-%attack correctly infers up to 31.3\% of ciphertext-plaintext pairs in a
-%real-world dataset. 
-%\item
-%{\bf Distribution-based attack:}  This attack exploits the ordering of
-%ciphertexts before deduplication and is applicable for both fixed-size and
-%variable-size chunking approaches; in other words, we relax the adversarial
-%knowledge about the chunk size in the size-based attack. It leverages the {\em
-%chunk locality} property \cite{xia11,lillibridge09,zhu08}, which states that
-%the ordering of data is likely preserved across various backup files, to infer
-%the ciphertext-plaintext pairs that are in similar {\em positions} of backup
-%files.  It further inspects the relative frequency distribution of the data
-%and filters any potentially flawed inference results.  Our evaluation shows
-%that the distribution-based attack infers up to 21.2\% of ciphertext-plaintext
-%pairs in a real-world dataset, while significantly reducing the number of
-%false positives compared to the prior attack \cite{li17}. 
-%\item
-%{\bf Clustering-based attack:}  This attack further relaxes the knowledge
-%about the ordering of ciphertexts in the distribution-based attack.  It
-%exploits the {\em similarity} property \cite{xia11,bhagwat09}, which states
-%that backup files share a large fraction of the same data (the ordering may
-%not be preserved), to infer the ciphertext-plaintext pairs that are in similar
-%{\em clusters} of a backup file.  Our evaluation shows that the
-%clustering-based attack infers up to 18.1\% of ciphertext-plaintext pairs in a 
-%real-world VM image dataset.
-%\end{itemize}
-
-%Note that variable-size chunking, chunk locality, and similarity are the key
-%design primitives of existing deduplication systems to improve deduplication
-%performance and storage savings.  We show how these primitives can be
-%exploited from an adversarial perspective.
-
-%%Our trace-driven evaluation shows that the distribution-based attack infers up to 21.2\% of plaintext chunks in the FSL dataset.
-For comparison, with the same auxiliary information, the inferred chunks by the locality-based attack \cite{li17} (that uses the same leakage of logical order) takes a fraction of 15.2\%.
-Another advantage of the distribution-based attack is that its effectively is less affected by the correlations between the auxiliary information and target chunks.
-For example, when we use some loosely correlated auxiliary information, this only degrades the coverage of inferred chunks by 1.4\%.
-
-%%distinguish chunks by their sizes.  Specifically, we propose the {\em
-%%size-based attack}, whose idea is to group all chunks by their sizes and
-%%launch frequency analysis against each group of chunks of the same size.  Our
-%%evaluation shows that the size-based attack correctly infers up to 31.3\% of
-%%ciphertext-plaintext pairs in a real-world dataset.
-
-%%The distribution-based attack builds on {\em chunk locality}
-%%\cite{xia11,lillibridge09,zhu08}, which is the tendency for chunks in backup
-%%streams to re-occur together in the same order. Specifically, if a chunk $M$
-%%is surrounded by the chunks $M'$ and $M''$ in one backup, then $M$ is likely
-%%to be surrounded by $M'$ and $M''$ in future backups. The rationale is that
-%%backup updates  cluster together and affect a few regions of chunks, while
-%%the remaining large stretch of chunks (in backup streams) remain unchanged.
-%%We adapt this characteristics to frequency analysis. Our insight is that if
-%%$M$ is the underlying plaintext of a ciphertext chunk $C$, then $M$ and $C$
-%%are likely to have similar (relative) frequency distribution on the
-%%%co-occurrences of their surrounding chunks. We propose to adjust frequency
-%%ranking and filter out unreasonable inference results based on the relative
-%%frequency distribution. The distribution-based attack incorporates the
-%%(distribution-based) frequency ranking with locality-based loop \cite{li17}
-%%to iteratively infer more chunks.
-
-%%The distribution-based attack assumes the leakage of the logical orders of
-%%chunks. Specifically, the adversary has the knowledge about the position, in
-%%which each chunk appears in the file data before deduplication.
-
-%%In addition to chunk frequencies, we consider the presence of chunk size leakage.
-We propose the {\em size-based attack} to extract plaintext information of the chunks yielded by {\em variable-size chunking}, which has already been used in practical systems such as LBFS \cite{muthitacharoen01} and Deep Store \cite{you05} to address boundary-shift problem.
-Specifically, variable-size chunking computes the Rabin fingerprint \cite{rabin81} based on a sliding window of data content, and places a chunk boundary when the resulting fingerprint matches a specific pattern.
-In other words, different chunks may have different chunk sizes due to their possibly distinct content patterns.
-Thus, we group all available chunks by chunk size, and launch frequency analysis through the chunks that have the same size.
-Our trace-driven evaluation shows that the size-based attack correctly infers up to 31.3\% of plaintext chunks in the real-world FSL dataset (see Section~\ref{sec:dataset}).
-
-%% .
-In other words, variable-size chunking generate chunks based on original content so as to address the problem of boundary shift.
-Our insight is different chunks possibly have different sizes in the setting.
-We can group all available chunks by their sizes, and launch attack on each chunk group, separately.
-%% about the order of each chunk in original input files.
-%% that expands threat to both variable-size and fixed-size chunks.
-
-%% Based on the necessary requirement, we propose distribution-based ranking  
-% % primitive 
-%% adjust the ranking of frequency analysis, and filter out unreasonable
-%% inference results. The distribution-based attack     
-%%to improve the effectiveness of classical frequency analysis.
-
-%% has an inference precision of 64.7\% to infer up to 21.2\% of original FSL backup data.
-For comparison, with the same auxiliary knowledge, the prior locality-based attack \cite{li17} achieves the corresponding precision and rate of only 34.8\% and 15.2\%, respectively.
-Another advantage is that the effectiveness of the distribution-based attack is less affected by the frequency correlations between the auxiliary and target chunks.
-For example, when we use a less correlated auxiliary dataset, this only leads to a limited inference rate degradation of 1.4\%.
-
-%% In addition, we observe that the distribution-based attack mainly threatens the rarely-update large-size files, and it can infer up to XXX\% of corresponding original content.
-
-%%\paragraph{Attack using generic order:}
-%%We consider to relax the required  knowledge of the distribution-based attack.
-We assume that the adversary learns the (generic) order information in a {\em coarse-grained unit}, in which a number of chunks appear together as a set; while the adversary cannot identify the accurate order of any chunk in each set.
-%%
-%%To exploit the (relaxed) adversarial knowledge, we propose the {\em
-%%clustering-based attack}, which builds on {\em similarity}
-%%\cite{li17,qin17,xia11,bhagwat09}. Specifically, similarity states that two
-%%sets of chunks have the same minimum cryptographic hash (i.e., {\em
-%%MinHash}) over their elements if and only if they have a large
-%%fraction of common chunks \cite{broder97}. Prior approaches
-%%\cite{li17,qin17,xia11,bhagwat09} apply similarity to improve the storage
-%%efficiency of near-exact deduplication, while we adapt it into inference
-%%attack: suppose $S_{\rm a}$ and $S_{\rm t}$ are the sets of plaintext and
-%%ciphertext chunks, respectively; our insight is that if the MinHash
-%%derived from the underlying plaintext chunks of $S_{\rm t}$ is identical
-%%with that of $S_{\rm a}$, then the plaintexts of the ciphertext chunks in
-%%$S_{\rm t}$ are likely to be in $S_{\rm a}$.
-%%Thus, we can use $S_{\rm a}$ as the auxiliary information, and launch frequency analysis to infer the chunks corresponding to $S_{\rm t}$.
-%%
-%%The effectiveness of the clustering-based attack depends on how chunks are
-%%grouped in each set. We observe that the clustering-based attack is severe for
-%%some special workloads, such as the virtual machine (VM) disk images that
-%%store data aligned with block boundaries and are commonly chunked into
-%%fixed-size chunks for deduplication \cite{jin09}. Our trace-driven evaluation
-%%shows that the clustering-based attack infers up to 18.1\% plaintext chunks in
-%%the experimental VM dataset.
-
-\section{Summary of Contributions}
-
-We summarize the main contributions of the paper. 
-%
-\begin{itemize}[leftmargin=*]
-\item
-We present two novel frequency analysis attacks against encrypted
-deduplication.  In addition to exploiting the leakage of frequencies due to
-the deterministic nature of encrypted deduplication, both attacks exploit the
-characteristics of deduplication workloads to increase the severity of
-frequency analysis.
-\item
-We evaluate our frequency analysis attacks with several real-world datasets,
-including long-term backups \cite{sun16,FSL14}, Windows file system snapshots
-\cite{meyer11}, and VM disk images \cite{li15,qin17}.  We present new
-observations based on our evaluation, and further analyze the security
-implications of how our frequency analysis attacks bring actual damages. 
-\item 
-We discuss possible countermeasures to mitigate the information leakage in
-encrypted deduplication.  
-\end{itemize}
-
-The remainder of the paper proceeds as follows. 
-Section~\ref{sec:background} presents the basics of encrypted deduplication.
-Section~\ref{sec:threat} defines the threat model. 
-Sections~\ref{sec:distribution-attack} and \ref{sec:clustering-attack}
-present two new frequency analysis attacks against encrypted deduplication.
-Section~\ref{sec:experiment} presents our trace-driven evaluation results.
-Section~\ref{sec:countermeasure} discusses the countermeasures against
-information leakage. Section~\ref{sec:related} reviews related work, and
-finally, Section~\ref{sec:conclusion} concludes the paper.
-
-%under a precision of 76.8\%.
-
-% \begin{table}
-% 	\centering
-% \caption{Summary of inference attacks against encrypted deduplication}
-% 	\vspace{-3pt}
-% 	\small
-% 	\begin{tabular}{@{}p{2.15cm}p{1.2cm}p{.3cm}p{.5cm}p{1.1cm}l@{}}
-% \toprule
-% \multirow{2}{*}{\bf Objectives} & \multicolumn{3}{c}{\bf Exploiting Leakages} & \multirow{2}{*}{\bf Chunking} & \multirow{2}{*}{\bf Where} \\ \cmidrule{2-4}
-% 				  &   {\bf Frequency}    &   {\bf Size}    &   {\bf Order}   &                   &                   \\
-% \midrule
-% File Existence &       &  \checkmark  &      & Var-size                  & \cite{ritzdorf16} \\ 
-% 	Chunk Recovery &  \checkmark  &  \checkmark  &      & Var-size                  & Section~\ref{sec:bucket_attack} \\ 
-% 	Chunk Recovery &  \checkmark  &    &   \checkmark  & All                  & \cite{li17}, Section~\ref{sec:distribution_attack} \\ 
-% 	Content Recovery &  \checkmark  &    &   Relax  & All                  & Section~\ref{sec:two_stage_attack} \\ 
-%  \bottomrule
-% \end{tabular} \medskip
-
-% Note: we do not include (i) frequency analysis due to its low severity \cite{li17} and (ii) side-channel attack \cite{mulazzani11,halevi11,harnik10} as it only occurs in client-side and cross-user deduplication.
-% \end{table}
-
-\chapter{Background}
-\label{sec:background}
-
-In this section, we present the basics of both plain and encrypted
-deduplication approaches. 
-% We motivate why encrypted deduplication remains
-% vulnerable.
-
-\begin{figure}[t]
-\centering
-\includegraphics[width=.48\textwidth]{pic/dedup-view.pdf}
-\caption{Overview of  deduplication workflow.}
-\label{fig:dedup-view}
-\end{figure}
-
-We focus on {\em chunk-based deduplication}, which operates at the granularity
-of small-size data units called {\em chunks}.  Figure~\ref{fig:dedup-view}
-summarizes the deduplication workflow.  Specifically, a storage system first
-partitions a file (e.g., backup) of a client into {\em logical chunks} via
-some {\em chunking} procedure, such that each logical chunk is uniquely
-identified by the cryptographic hash of its content called a {\em tag} (a.k.a.
-fingerprint).  Two logical chunks are said to be {\em identical} if they have
-the same tag, while the likelihood that distinct logical chunks have the same
-tag is practically negligible \cite{black06}.  The storage system stores only
-a copy of identical logical chunks as a {\em physical chunk}, and each
-identical logical chunk refers to the same physical chunk via small-size
-references.
-
-Chunk-based deduplication is more fine-grained than whole-file deduplication,
-and hence has higher storage efficiency in general.  We can further choose
-either {\em fixed-size} or {\em variable-size} chunking for deduplication.
-Fixed-size chunking partitions file data into equal-size (logical) chunks,
-while variable-size chunking (a.k.a. content-defined chunking) often specifies
-chunk boundaries in a content-dependent manner (e.g., via Rabin fingerprinting
-\cite{rabin81}) and partitions file data into variable-size chunks.
-Fixed-size chunking is simple and fast, while variable-size chunking maintains
-storage efficiency in the face of content shifts since the majority of chunks
-remain unchanged even the file has added or removed some content.
-Variable-size chunking is often used in backup systems (e.g.,
-\cite{zhu08,lillibridge09}), yet fixed-size chunking is shown to be effective
-for some workloads (e.g., VM images \cite{jin09}).  Our work addresses both
-fixed-size and variable-size chunking approaches.
-
-{\em Encrypted deduplication} addresses chunk confidentiality in an
-outsourcing environment (e.g., cloud storage), while preserving deduplication
-effectiveness.  Traditional symmetric encryption requires that multiple
-clients encrypt their file data by their (distinct) secret keys, thereby
-transforming identical chunks into distinct encrypted chunks that can no
-longer be deduplicated.  {\em Message-locked encryption (MLE)}
-\cite{bellare13a} formalizes encrypted deduplication.  The baseline MLE
-instantiation derives a symmetric key (called the {\em MLE key}) based on the
-content of each {\em plaintext} (e.g., a logical chunk in chunk-based
-deduplication), and encrypts the plaintext using the MLE key to form a {\em
-ciphertext} (e.g., an encrypted logical chunk).  Thus, MLE ensures that
-identical plaintexts are encrypted to identical ciphertexts.  Finally, the
-storage system derives the tag from each ciphertext and performs
-deduplication.
-
-MLE can be realized as different instantiations (see Section~\ref{sec:related}). The
-most popular one is convergent encryption (CE) \cite{douceur02}, which has
-been implemented in a wide variety of storage systems (e.g., 
-\cite{adya02,elephantdrive,mega,gnunet,freenet,cryptosphere,cox02,storer08,
-anderson10}).  The main idea of CE is to derive the MLE key from the
-cryptographic hash of the content of each plaintext.  Note that some MLE
-instantiations \cite{bellare13a} allow identical plaintexts to be encrypted
-into distinct ciphertexts.  Nevertheless, they ensure that the tags are still
-derived from the plaintexts, so that they can perform deduplication by
-checking the equality of tags.
-
-Existing MLE instantiations all build on the notion {\em deterministic
-encryption} to ensure that the ciphertexts (or the tags) are deterministically
-derived from the plaintexts, so as to preserve deduplication effectiveness as
-opposed to traditional symmetric encryption.  While deterministic encryption
-provides confidentiality guarantees, in this paper, we argue that such a
-deterministic nature can be exploited by an adversary to infer the original
-plaintext from a given ciphertext.
-
-%Today, MLE \cite{bellare13a} and its variants \cite{douceur02, bellare13a, bellare13b, li15} have been implemented in various practical systems \cite{cryptosphere,elephantdrive, mega, adya02,freenet, wilcox-ohearn08, gnunet,li15,anderson10,cox02, armknecht15, shah15, qin17}.
-
-% from these distinct ciphertext chunks, and cannot detect whether the original content underlying these ciphertext chunks are identical.
-
-% The server cannot detect whether the original content underlying these  ciphertext chunks are identical; otherwise it violates the security guarantee of symmetric encryption.
-
-% For security concerns, users want their data to be encrypted before outsourcing.
-
-% Figure~\ref{fig:dedup-view} presents an overview of {\em encrypted deduplication} \cite{bellare13a}, where multiple clients outsource data to a remote storage system that performs {\em deduplication} across  clients to save storage space.
-Specifically, each client first partitions file data into {\em logical chunks}, each of which is with either fixed or variable sizes.
-% Fixed-size chunking achieves high computational performance, while variable-size chunking defines chunk boundaries based on  content so as to be robust against content shift.
-
-% Then, the client protects each chunk via encryption.
-However, in traditional symmetric encryption, clients use their own (distinct) secret keys for encryption, and transform the same plaintext chunks to different ciphertext chunks.
-The storage system cannot detect whether the original content underlying these ciphertext chunks are identical; otherwise it violates the security guarantee of symmetric encryption.
-
-% % To save space, the storage system performs {\em deduplication} across all its users.
-
-% Specifically, if two users upload the same message $M$, the server can detect this and store only a single copy of $M$.
-We focus on {\em chunk-based deduplication}, which partitions file data into fixed-size or variable-size chunks.
-Specifically, fixed-size chunking achieves high computational performance, while variable-size chunking defines chunk boundaries by content so as to be robust against content shift.
-Then, it removes duplicates in the graularity of chunk.
-In this paper, we use the term ``message'' and ``chunk'' interchangeably to refer to the fine-grained data unit operated by deduplication.
-
-% Deduplication is a technique that reduces storage space by eliminating content redundancies.
-Figure~\ref{fig:dedup-view} presents the logical view of a deduplication-enabled storage system, which operates at the granularity of {\em chunk} and removes the chunks that have identical content with some already stored chunks.
-% Specifically, it first partitions file data into an ordered sequence of {\em logical chunks}, each of which is with either fixed or variable sizes. 
-% Fixed-size chunking achieves high computational performance, while variable-size chunking defines chunk boundaries based on  content so as to be robust against content shift.
-Then, it only stores the chunks (called {\em physical chunks}) that have unique content, and refers other copies of a stored chunk via small-size references.
-
-% Encrypted deduplication aims to address the chunk-level confidentiality of deduplication in an outsourcing environment (e.g., cloud storage).
-Consider a scenario where multiple users outsource storage to a remote third-party cloud service, which apply deduplication across its users to save storage space.
-For security concerns, users want their data to be encrypted before outsourcing.
-However, in traditional symmetric encryption, users use their own (distinct) secret keys for encryption, and  transform the same plaintext chunks to different ciphertext chunks.
-The server cannot detect whether the original content underlying these  ciphertext chunks are identical; otherwise it violates the security guarantee of symmetric encryption.
-
-% {\em Message-locked encryption (MLE)} \cite{bellare13a} is a cryptographic primitive to achieve encrypted deduplication.
-It derives a symmetric key $K_M$ (called {\em MLE key}) based on the content of each message $M$ (e.g., $K_M$ is the cryptographic hash of $M$ \cite{douceur02}), and further uses the MLE key $K_M$ to encrypt $M$.
-This makes the ciphertext only depend on the plaintext, from which it is encrypted.
-The server can detect duplicates by checking the equality of ciphertexts (e.g., comparing their cryptographic hashes).
-Today, MLE \cite{bellare13a} and its variants \cite{douceur02, bellare13a, bellare13b, li15} have been implemented in various systems \cite{cryptosphere,elephantdrive, mega, adya02,freenet, wilcox-ohearn08, gnunet,li15,anderson10,cox02, armknecht15, shah15, qin17}  for encrypted deduplication.
-
-% Consider a scenario where multiple users outsource storage to a remote third-party cloud service.
-To save space, the cloud server performs {\em deduplication} across all its users.
-Specifically, if two users upload the same message $M$, the server can detect this and store only a single copy of $M$.
-We focus on {\em chunk-based deduplication}, which partitions file data into fixed-size or variable-size chunks.
-Specifically, fixed-size chunking achieves high computational performance, while variable-size chunking defines chunk boundaries by content so as to be robust against content shift.
-Then, it removes duplicates in the graularity of chunk.
-In this paper, we use the term ``message'' and ``chunk'' interchangeably to refer to the fine-grained data unit operated by deduplication.
-
-% that have the same fingerprint are {\em identical}, since the probability of fingerprint collision (i.e., different chunks lead to the same fingerprint) is negligible in practice \cite{black06}.
-A deduplication system stores only a single copy of identical chunks, while referring the other copies by small-size references.
-
-% It performs chunking to partition input data into fixed-size or variable-size chunks.
-Fixed-size chunking generates all chunks that have a uniform chunk size; on the other hand, variable-size chunking, configured by the maximum, average and minimum chunk sizes, defines the boundary of each chunk (e.g., via Rabin fingerprinting \cite{rabin81}) through matching a specific content pattern.
-This makes it robust against content shift.
-
-% \subsection{Leakage Channels}
-% \label{sec:leakage}
-
-% MLE applies {\em deterministic encryption}, and exposes some information, called {\em leakage}, about plaintext chunks.
-The fundamental leakage is {\em chunk frequency}, which is the number of times that each plaintext chunk appears in the original file data.
-Although the frequency leakage has been acknowledged in prior works \cite{abadi13,bellare15,ritzdorf16,li17}, it is hard to be prevented, since this breaks the one-to-one mapping between plaintext and ciphertext chunks, and leads to the degradation of deduplication performance \cite{abadi13} or storage efficiency \cite{li17} (see \S\ref{sec:countermeasure}).
-
-% sacrifices security and exposes some information,  
-% that has been . Specifically, MLE encrypts identical plaintext chunks into identical ciphertext chunks, and hence leaks  We
-
-% Additional leakages \cite{ritzdorf16, li17} have been explored due to the careless deployment of encrypted deduplication.
-First, some deduplication systems \cite{xia11,lillibridge09,zhu08} aim for high performance, and operate chunks in the same order that they appear in plaintext files; this exposes the {\em logical order}, based on which one can identify the position of each chunk in input files.
-Second, some practitioners \cite{douceur02, wilcox-ohearn08, bellare13b} avoid storage overhead, and do not pad ciphertext chunks with any additional data; this exposes the {\em chunk size}, since the ciphertext chunks have the same number of blocks with corresponding plaintext chunks.
-
-% The risks posed by the above leakage profiles have not been scrutinized except \cite{ritzdorf16, li17}, which build attacks to infer the plaintext contents of ciphertext chunks \cite{li17} or to guess if particular files have already been stored \cite{ritzdorf16}.
-On the other hand, it remains unexplored that what is the security implication of the inferred information.
-This paper presents a comprehensive study of the leakage of encrypted deduplication, and we seek to answer the following questions: {\em (i) how to enable primitives to infer plaintext contents in various leakage settings, and (ii) what is the concrete implication from the inferred contents?}
-
-% \subsection{Frequency Analysis}
-% \label{sec:freqanalysis}
-
-% {\em Frequency analysis} is a well-known cryptanalysis primitive that illustrates the weakness of deterministic encryption.
-Suppose an adversary has access to a target set of ciphertexts (that are encrypted by deterministic encryption) and an auxiliary set of plaintexts.
-To launch frequency analysis, it sorts ciphertexts and plaintexts by their frequencies, respectively, and relates each ciphertext with the plaintext that has the same frequency rank.
-% Prior works have exploited different leakage profiles (e.g., access pattern \cite{kellaris16, lacharite18, islam12, zhang16b}, numeric order \cite{grubbs17, bindschaedler17, durak16}, query pattern \cite{cash15}) to examine frequency analysis in various applications (e.g., database \cite{naveed15}, keyword search \cite{grubbs16,pouliot16}).
-This paper shows how to strengthen the effectiveness of frequency analysis with practical leakages in deduplication.
-
-%The locality-based attack \cite{li17} targets deduplication, and increases the coverage of inferred chunks with an additional leakage of logical order.
-
-% strengthened the effectiveness of frequency analysis in different applications with various leakages.
-
-% Frequency analysis has been applied in prior works \cite{grubbs17,bindschaedler17,zhang16b,grubbs16,kellaris16,pouliot16,durak16,naveed15,cash15,islam12,lacharite18} to construct inference attacks.
-Some attacks target structured relational data in database, by classical frequency analysis \cite{naveed15}, exploring correlations or orderings of table columns, .
-
-% % Naveed {\em et al.} \cite{naveed15} propose $l_p$-optimization that equivalents classical frequency analysis.
-
-%  studies the security of encrypted database, and reduces classical frequency analysis to  problem.
-
-% on rational data
-
-% They either
-
-% The effectiveness of frequency analysis depends on the correlation between the auxiliary set and the target set.
-It performs well, only when the frequency of ciphertext is correlated with that of the corresponding plaintext.
-In addition, some ciphertexts (resp.
-plaintexts) may have the same frequencies, and form {\em ties} during sorting.
-How to break ties affects the result of frequency analysis.
-
-% This paper aims to apply frequency analysis to explore the vulnerabilities of encrypted deduplication.
-Our focus is not to address how to obtain correlated plaintexts for inference attack.
-Instead, we develop strategies to break ties effectively, so as to demonstrate the severity of frequency analysis.
-
-% comment on March 15
-% Deduplication eliminates the redundant copies of identical {\em chunks} for storage efficiency.
-It performs chunking to partition input data into fixed-size or variable-size chunks.
-Fixed-size chunking generates all chunks that have a uniform chunk size; on the other hand, variable-size chunking, configured by the maximum, average and minimum chunk sizes, defines the boundary of each chunk (e.g., via Rabin fingerprinting \cite{rabin81}) through matching a specific content pattern.
-This makes it robust against content shift.
-Each chunk is identified based on the cryptographic hash (known as {\em fingerprint}) of the content of the chunk.
-We consider the chunks that have the same fingerprint are {\em identical}, since the probability of fingerprint collision (i.e., different chunks lead to the same fingerprint) is negligible in practice \cite{black06}.
-A deduplication system stores only a single copy of identical chunks, while referring the other copies by small-size references.
-
-% Encrypted deduplication ensures all chunks are encrypted {\em before} deduplication, while the redundant copies of original chunks can still be removed.
-An elegant approach of resolving this tension is {\em message-locked encryption (MLE)} \cite{bellare13a}, which encrypts each chunk with a key derived from the content of the chunk.
-This maps identical plaintext chunks to identical ciphertext chunks that can be detected by deduplication.
-Today, various systems \cite{cryptosphere,elephantdrive, mega, adya02,freenet, wilcox-ohearn08, gnunet,li15,anderson10,cox02, armknecht15, shah15, qin17} (see \S\ref{sec:related}) have applied MLE \cite{bellare13a} or its variants \cite{douceur02, bellare13b, li15} for encrypted deduplication in practice.
-
-% However, the practical encrypted deduplication systems expose some information, called {\em leakage}, about the original chunks.
-The fundamental leakage is {\em chunk frequency} that has been acknowledged in prior works \cite{abadi13,bellare15,ritzdorf16,li17}.
-Specifically, MLE encrypts identical plaintext chunks into identical ciphertext chunks, and hence leaks the number of times that each original chunk appears in the input data.
-We argue that it is hard to prevent the frequency leakage, since this breaks the one-to-one mapping of plaintext and ciphertext chunks and hence degrades deduplication performance \cite{abadi13} or storage efficiency \cite{li17}.
-
-% Additional leakages \cite{ritzdorf16, li17} have been explored due to careless deployment of encrypted deduplication.
-First, some deduplication systems \cite{zhu08, xia11} aim for high performance, and require to operate chunks in the same order that they appear in original files; this exposes the {\em logical order}, based on which one can identify the position of each chunk in input files.
-Second, some practitioners \cite{douceur02, wilcox-ohearn08, bellare13b} avoid storage overhead and do not pad ciphertext chunks with any additional data; this exposes the {\em chunk size}, as the ciphertext chunks should have the {\em same} number of blocks with the original plaintext chunks.
-
-% The risks posed by leakage have not been scrutinized except \cite{ritzdorf16, li17}, which build {\em attack primitives} to infer original plaintext chunks \cite{li17} or the existence of particular files \cite{ritzdorf16} against encrypted deduplication.
-It remains unexplored of how to launch practical attacks based on the inferred information.
-This paper presents a comprehensive study of the leakage of encrypted deduplication, and we seek to answer the following two questions: {\em (i) how to enable primitives to infer original contents in various leakage settings, and (ii) what is the concrete implication of the practical attack that builds on the inferred contents?}
-
-% The present paper studies the leakage of SE in order to understand its practical security.
-We consider a range of threats including IKK’s query-identification setting, and against various approaches to building SE.
-
-% To this end, we pose the following question: how to enable secure and lightweight rekeying, while preserving the deduplication capability?
-
-% the work of IKK.
-The current literature leaves a practitioner with few concrete recommendations for configuring and deploying SE.
-The risk is not merely abstract; several deployments of SE may be easily broken depending on how they are used.
-
-% Prior works
-
-% to our best knowledge, none of schemes/systems attempt to protect the processing order of chunks.
-For performance reasons, some deduplication systems (e.g., DDFS \cite{zhu08} and SiLo \cite{xia11}) even require to operate chunks in the same order that they appear in the original logical files.
-This exposes the {\em logical order}, based on which one can identify the position of each chunk in the input file.
-
-% In addition to the frequency leakage, practitioners configure and deploy encrypted deduplication carelessly, and possibly .
-
-% In the following, we discuss a variety of leakages observed in the state-of-the-art encrypted deduplication schemes/systems.
-
-% \begin{itemize}[leftmargin=10pt]
-% \item \textbf{Frequency leakage:} 
-% Encrypted deduplication schemes apply {\em deterministic encryption} (e.g., MLE), where identical plaintext chunks will be encrypted into identical ciphertext chunks.
-This leaks the {\em frequency information} (i.e., the number of times that the original chunk appears in the input data) of each chunk.
-The frequency leakage is fundamental to MLE, as it is hard to be prevented (otherwise, leading to significant degradation of deduplication performance \cite{abadi13} or storage efficiency \cite{li17}).
-
-% \item \textbf{Size leakage:} 
-% To mitigate storage overhead, practitioners are suggested to implement chunk encryption without padding schemes \cite{ritzdorf16}.
-For example, Farsite \cite{douceur02}, Tahoe-LAFS \cite{wilcox-ohearn08} and DupLESS \cite{bellare13b} apply AES in counter mode, yet they do not pad ciphertext chunks with any additional data.
-This leaks the {\em chunk size information} \cite{ritzdorf16}, as the ciphertext chunks should have the {\em same} number of blocks with the original plaintext chunks.
-% The leakage is more severe for variable-size chunks, whose boundaries are identified (e.g., via Rabin fingerprinting \cite{rabin81}) by matching a specific content pattern.
-A variable-size ciphertext chunk leaks the information that only the last a few bytes (determined by a sliding window) of its original chunk are likely to match the public content pattern.
-Two ciphertext chunks with distinct sizes further expose the information that they are mapped from different plaintext chunks.
-
-% \item \textbf{Order leakage:}
-% Leakage occurs in deploying encrypted deduplication carelessly. \end{itemize}
-
-% This paper studies the leakage of encrypted deduplication. We present a family of new inference attacks that exploit the exposed information to learn the original content of encrypted chunks.
-
-\chapter{Threat Model}
-\label{sec:threat}
-
-In this section, we formulate the threat model for our proposed frequency
-analysis attacks against encrypted deduplication.
-
-\section{Definitions}
-
-We first provide the definitions for our threat model. We model a plain file
-as an ordered list of $n$ {\em logical plaintexts} (i.e., logical chunks
-before deduplication), denoted by $\mathbf{M} = \langle \hat{M}^{(1)},
-\hat{M}^{(2)}, \ldots, \hat{M}^{(n)}\rangle$.  Each logical plaintext
-$\hat{M}^{(i)}$ (where $1\le i\le n$) is encrypted via MLE into the
-corresponding ciphertext $\hat{C}^{(i)}$, and all encrypted results of
-$\mathbf{M}$ form a stream of $n$ {\em logical ciphertexts} $\mathbf{C} =
-\langle \hat{C}^{(1)}, \hat{C}^{(2)}, \ldots, \hat{C}^{(n)} \rangle$.  Note
-that the logical ciphertexts in $\mathbf{C}$ are also ordered to reflect the
-deduplication processing sequence of an encrypted deduplication storage
-system.
-
-Identical logical plaintexts and ciphertexts may appear at different positions
-of $\mathbf{M}$ and $\mathbf{C}$, respectively.  We denote a unique plaintext
-as $M$ (uniquely identified by its tag), which is encrypted via MLE to the
-corresponding unique ciphertext $C$.  Each $M$ (resp. $C$) corresponds to one
-or multiple identical copies of $\hat{M}^{(i)}$ (resp. $\hat{C}^{(i)}$).
-
-% of $\mathbf{M}$ is
-% independently encrypted into corresponding ciphertext $C$ via MLE, and all encrypted results
-
-% A unique plaintext (or plaintext for short) $M$ has one or more copies in $\mathbf{M}$  
-% Identical plaintexts may have multiple copies in $\mathbf{M}$, and we introduce unique plaintext  
-% We define a unique plaintext as the plaintext that has unique content among other plaintexts of $\mathbf{M}$    
-% Let $M$ and $C$ be a
-% plaintext and its corresponding ciphertext, respectively; both of them are in
-% units of chunks defined by deduplication.  We model a plain file before
-% deduplication as an {\em ordered} list of $n$ plaintexts, denoted by
-% $\mathbf{M} = \langle M^{(1)},  M^{(2)}, \ldots, M^{(n)}\rangle$.  Identical
-% plaintexts may appear at different positions of $\mathbf{M}$, say $M^{(i)} =
-% M^{(j)}$ for some $1\le i \neq j\le n$.   
-% % Also, each plaintext can have the
-% same or different chunk sizes due to fixed-size or variable-size chunking,
-% respectively, and let $|M|$ denote the size of a plaintext $M$.  
-% Let $M$ and $C$ denote a
-% plaintext (i.e., a logical chunk before encryption) and its corresponding
-% ciphertext (i.e., a logical chunk after encryption).  We model a plain file
-
-\section{Adversarial Goals and Assumptions}
-\label{sec:assumptions}
-
-We consider an adversary that aims to infer a set of ciphertext-plaintext
-pairs, denoted by \{$(C, M)$\}, with two specific goals:
-\begin{itemize}[leftmargin=*]
-\item
-{\bf High inference rate:} A large fraction of correct ciphertext-plaintext pairs
-are inferred, among all correct ciphertext-plaintext pairs (i.e., high recall or
-low false negative rates in statistical terms).
-\item
-{\bf High inference precision:} A large fraction of ciphertext-plaintext pairs
-are correct, among all inferred ciphertext-plaintext pairs (i.e., high precision
-or low false positive rates in statistical terms).
-\end{itemize}
-
-We assume that the adversary is {\em honest-but-curious}, such that it can
-passively monitor the stream of ciphertexts $\mathbf{C}$ being written to the
-storage system and exploit different types of leakage information from
-$\mathbf{C}$ (see Section~\ref{sec:leakage}).  Given the available leakage
-information, the adversary aims to infer the original plaintext of each
-ciphertext in $\mathbf{C}$ via a {\em ciphertext-only} attack.  It is possible
-that the adversary knows a limited subset of ciphertext-plaintext pairs to
-launch a known-plaintext attack, which further strengthens attack severity
-\cite{li17}.  We do not consider the known-plaintext attack in this paper.
-
-%We treat $\mathbf{C}$ as the {\em view} by the
-%adversary and model different properties of the view
-
-We assume that the adversary does not have access to any {\em metadata} that
-contains the information about how chunks are operated and stored, as we do
-not apply deduplication to the metadata and hence it can be protected by
-traditional symmetric encryption.  Also, we assume that the adversary does not
-have {\em active} capabilities, which can be independently prevented by
-existing approaches. One example is that a malicious client may claim the
-ownership of unauthorized files in client-side deduplication
-\cite{harnik10,halevi11,mulazzani11}; it can be addressed by
-proof-of-ownership \cite{halevi11,xu13,pietro12} or server-side deduplication
-\cite{harnik10,li15}.  Another example is that a malicious storage system may
-modify stored data; it can be detected by remote integrity checking
-\cite{juels07,ateniese07}.
-
-% In addition, $\mathcal{A}$ does not aim to infer if
-% particular files have been stored \cite{harnik10, ritzdorf16}. Instead, we
-% study the security implication based on the inferred contents over different
-% types of files (see \S\ref{sec:case}).. 
-% Intuitively, we want to guarantee that what $\mathcal{A}$ can learn is some
-% well defined leakage $\mathcal{L}$, which includes the frequency, logical
-% order and/or chunk size (\S\ref{sec:leakage}). 
-% Note that $\mathcal{A}$ is specific to a {\em passive} adversary with content
-% inference in mind. We do not assume $\mathcal{A}$ has {\em active}
-% capabilities,
-
-\section{Leakage Channels}
-\label{sec:leakage}
-
-We consider three types of leakage channels in encrypted deduplication storage
-that enable an adversary to infer information:
-\begin{itemize}[leftmargin=*]
-\item
-{\bf Frequency:}  Due to the deterministic nature of encrypted deduplication,
-the frequency of each ciphertext in $\mathbf{C}$ before deduplication (i.e., 
-the number of duplicate copies) can be mapped to that of its corresponding
-plaintext in $\mathbf{M}$. 
-% the size of each ciphertext in
-% $\mathbf{C}$ is approximately equal to that of its corresponding plaintext in
-% $\mathbf{M}$. In other words, the exact number of blocks (e.g., that are of size 16 bytes) in ciphertexts   
-% the exact number of blocks in the plaintext equals the number of blocks in the ciphertext
-% {\bf PC: if block cipher is used, it's not necessary that the
-% plaintext has the same size as its ciphertext}.
-%(e.g., \cite{douceur02, wilcox-ohearn08, bellare13b}) do not pad ciphertexts
-%with additional data to avoid storage overhead, 
-\item
-{\bf Order:}  Some storage systems (e.g., \cite{xia11,lillibridge09,zhu08})
-apply deduplication to the chunks in the same order as they appear in the
-original file.  Thus, the order of ciphertexts in $\mathbf{C}$ can be mapped
-to that of plaintexts in $\mathbf{M}$. 
-\item
-{\bf Size:}  Variable-size chunking (see Section~\ref{sec:background}) leads
-to different chunk sizes of the ciphertexts.  If such ciphertexts are not
-padded (to avoid storage overhead \cite{ritzdorf16}), the size of a ciphertext
-in $\mathbf{C}$ can be mapped to that of its corresponding plaintext in
-$\mathbf{M}$.    
-\end{itemize}
-
-%We also consider other leakage channels that are specific to real-world
-%deduplication storage systems. First, {\em order leakage} exposes the logical
-%order of each plaintext, and it is available for the systems
-%\cite{xia11,lillibridge09,zhu08} that aim for high performance and operate
-%the deduplication of chunks in the same order as these chunks appear in
-%original files; this implies that the logical order of ciphertext in
-%$\mathbf{C}$ exactly reflects that of its corresponding plaintext. Second,
-%{\em size leakage} exposes the chunk size of each plaintext, since some
-%systems \cite{douceur02, wilcox-ohearn08, bellare13b} avoid storage
-%overhead and do not pad ciphertexts with any additional data; this
-%implies that the size of ciphertext in $\mathbf{C}$ exactly equals that
-%of its corresponding plaintext.
-
-In addition, the adversary has access to some {\em auxiliary information} that
-presents the ground truth about the data characteristics correlated with
-$\mathbf{M}$. Note that the availability of auxiliary information is necessary
-for any inference attack \cite{kumar07,li17,grubbs17,zhang16b,kellaris16,ritzdorf16,naveed15,cash15,islam12}.
-In this work, we consider the auxiliary information as an ordered list of
-previously known plaintexts (e.g., old user backups or VM disk images),
-denoted by $\mathbf{A}$.  Clearly, the attack severity depends on the
-correlation between $\mathbf{A}$ (i.e., the previously known plaintexts) and
-$\mathbf{M}$ (i.e., the plaintexts that are to be inferred).  Our focus is not
-to address how an adversary can obtain auxiliary information, possibly due to
-careless data release \cite{careless-release}, stolen storage devices
-\cite{stolen-device}, and cloud leakage \cite{cloud-leakage}. Instead, given
-such information, we investigate how the available auxiliary information,
-combined with the leakage channels, bring information leakage from encrypted
-deduplication.
-
-We focus on frequency analysis \cite{alkadit92} as the attack methodology.
-Classical frequency analysis sorts the unique ciphertexts in $\mathbf{C}$ and
-the unique plaintexts in $\mathbf{A}$ by {\em frequency} (i.e., the number of
-identical copies corresponding to each unique ciphertext or unique plaintext). 
-It then relates each unique ciphertext in $\mathbf{C}$ with the unique
-plaintext in $\mathbf{A}$ that has the same frequency rank. In the following
-sections, we design sophisticated frequency analysis attacks against encrypted
-deduplication.
-
-% Frequency analysis is a cryptanalysis primitive to relate the ciphertexts in $\mathbf{C}$  with the plaintexts in $\mathbf{M}$.
-Specifically, it sorts ciphertexts and plaintexts by their frequencies in $\mathbf{C}$ and $\mathbf{A}$, respectively, and maps each ciphertext to the plaintext that has the same frequency rank.
-Building on the classical version of frequency analysis, we show how to exploit leakage channels to strengthen its severity against encrypted deduplication.
-
-% infer ciphertext-plaintext pairs from $\mathbf{C}$ and $\mathbf{A}$. 
- % Specifically, the adversary
-
-% It performs well, only when the frequency of ciphertext is correlated with that of the corresponding plaintext. 
-% The more correlated to $\mathbf{M}$,
-
-% Our focus is not to address its availability, which is due to careless data release \cite{careless-release}, stolen storage devices \cite{stolen-device}, and cloud leakage \cite{cloud-leakage}.
-Instead, we show how an adversary can launch inference attacks based on the available auxiliary information $\mathbf{A}$.
-
-% Our focus is not to address how to obtain accurate auxiliary information, which we pose as future work; instead, given the available auxiliary information, we study how an adversary can design a severe attack based on frequency analysis and how we can defend against the attack
-% Some available auxiliary information has been demonstrated to be necessary for inference attacks  and we consider the auxiliary information $\mathbf{M}$ as a complete user backup, file system snapshot or VM disk image in plaintext.
-The rationale of its availability is that the adversary can obtain the original data from  We emphasize that the auxiliary information $\mathbf{M}$ does not need to be identical with the original file of $\mathbf{C}$.
-In other words, $\mathbf{M}$ may not have the
-% same number of chunks with $\mathbf{C}$, or its $i$-th chunk $M^{\langle i \rangle}$ may not be the plaintext of $C^{\langle i \rangle}$ or even not mapped into $\mathbf{C}$. 
-% {\bf PC: give the background on frequency analysis.}
-
-% We assume that the adversary can take advantage of some   for attacks. The auxiliary information , and it has been demonstrated for necessity in inference attacks . In this work,
-
-% In addition, the adversary can exploit other deduplication-specific leakage channels.
-
-% effectiveness of inference attacks.
-First, we consider {\em size leakage}, meaning that the adversary can derive the size of a plaintext directly based on the corresponding ciphertext: ${\sf s}(C) = |M|$, where $C$ is the encryption of $M$.
-
-% deduplication-specific leakage channels.
-
-% We target inference attacks against {\em backup workloads}, which refer to the copies of primary data (e.g., application states, file systems, and virtual disk images) over time.
-The recent technology trend \cite{douglis17} suggests to create full backups (that store the complete data of the primary source) over traditional incremental backups (that only store the changes of data since the last full backup), so as to mitigate the overhead in restoring earlier (full) backups.
-Thus, we focus on inferring information from different versions of full backups (or backups for short) that are created based on the same primary data source at different times.
-
-% They can be created as either weekly full backups (that store the complete data of the primary source) or daily incremental backups (that only store the changes of data since the prior full backup).
-Informed by the technology trend , we focus on full backups (or {\em backups} for short).
-Specifically, we aim to infer information from different versions of backups that are created based on the same primary data source yet at different times.
-
-% To launch attacks, we assume that $\mathcal{A}$ is an ``{\em honest-but-curious}'' adversary that can compromise the server hosting deduplication service, while it cannot establish a long-term presence for attack.
-Intuitively, we want to guarantee that what $\mathcal{A}$ can learn is some well defined leakage $\mathcal{L}$, which includes the frequency, logical order and/or chunk size (\S\ref{sec:leakage}).
-Formally, we define these leakage channels based on a target victim file $\mathbf{M}_{\rm t}$:
-
-% \begin{itemize}[leftmargin=*]
-% 	\item  {\bf Frequency leakage}: $\mathcal{L}_{\rm freq} = \{(C, {\sf freq}(M)): M \in \mathbf{M}_{\rm t}$ and $C = {\sf E}_{K_M}(M) \}$ is a set of chunk-frequency pairs, where $C$ is the encryption of some plaintext chunk $M$ in $\mathbf{M}_{\rm t}$, and each pair $(C, {\sf freq}(M))$ leaks the corresponding frequency of $M$.
-
-% 	\item  {\bf Order leakage}: $\mathcal{L}_{\rm order} = \{(C, {\sf ord}(M)): M\in\mathbf{M}_{\rm t}$ and $C = {\sf E}_{K_M}(M) \}$ associates each ciphertext chunk $C$ with a set ${\sf ord}(M)$ of logical orders, at which the copies of its original chunk $M$ appear in $\mathbf{M}_{\rm t}$.
-Note that order leakage {\em implies} frequency leakage, since the logical orders of each chunk copy inherently includes the number of times the corresponding chunk appears.
-
-% 	\item  {\bf Size leakage}: $\mathcal{L}_{\rm size} = \{(C, {\sf size}(M)): M \in \mathbf{M}_{\rm t}$ and $C = {\sf E}_{K_M}(M) \}$ is a set of chunk-size pairs, where each pair leaks the size of the original chunk of $C$.
-% \end{itemize}
-
-% In addition, $\mathcal{A}$ can take advantage of the {\em auxiliary information} $\mathbf{M}_{\rm a}$ that presents the ground truth about the frequency, size and order information about plaintext chunks.
-Some available auxiliary information is necessary for inference attacks , and we focus on validating our attacks with the auxiliary information obtained from different types of storage workloads (see \S\ref{sec:dataset}).
-
-% Acquiring the above capabilities, $\mathcal{A}$'s primary goal is to recover the plaintext chunks in the target file $\mathbf{M}_{\rm t}$.
-More formally, given the leakage $\mathcal{L}$ (that can be some combination of $\mathcal{L}_{\rm freq}$, $\mathcal{L}_{\rm order}$ and $\mathcal{L}_{\rm size}$) and the auxiliary information $\mathbf{M}_{\rm a}$, $\mathcal{A}$ outputs a collection of ciphertext-plaintext chunk pairs $\mathcal{R} = \{ (C, M) \}$: $\mathcal{A}(\mathcal{L}, \mathbf{M}_{\rm a}) \rightarrow \mathcal{R}.$ Each output pair $(C, M)$ indicates $\mathcal{A}$'s guess that relates a ciphertext chunk $C$ with a plaintext chunk $M$.
-
-% identify the ciphertext-plaintext chunk pairs about $\mathbf{M}_{\rm tar}$.
-More formally, given the leakage $\mathcal{L}$ (that can be some combinations of $\mathcal{L}_{\rm freq}$, $\mathcal{L}_{\rm order}$ and $\mathcal{L}_{\rm size}$), and auxiliary information $\mathbf{M}_{\rm aux}$, $\mathcal{A}$ outputs a collection of ciphertext-plaintext chunk pairs $\mathcal{R} = \{ (C, M) \}$: $\mathcal{A}(\mathcal{L}, \mathbf{M}_{\rm aux}) \rightarrow \mathcal{R}.$ Each pair $(C, M)$ indicates $\mathcal{A}$'s guess that relates a ciphertext chunk $C$ with a plaintext chunk $M$.
-
-% a malicious server may corrupt stored chunks, yet it can be detected by integrity checking mechanisms \cite{juels07,ateniese07};
-
-% and it is a correct inference by $\mathcal{A}$ if $C$ is the actual encryption of $M$, i.e., $(M, C) \in \mathcal{E}$.
-
-% We measure the success of attacks in several ways.
-The {\em raw inference rate} is the percentage of ciphertext chunks (including duplicates) that are inferred correctly over the total number of ciphertext chunks in the target information.
-For example, if the adversary correctly infers a ciphertext-plaintext chunk pair $(C, M)$ and the ciphertext chunk $C$ accounts for a fraction of 10\% in the target information, then the raw inference rate will be at least 10\%.
-
-% We assume the adversary can eavesdrop the deduplication processing (e.g., comparison operation of fingerprints) of all ciphertext chunks in a victim file (called {\em target information}); on the other hand, it cannot access related metadata that can be protected by traditional encryption \cite{li17}.
-% the same and different private sources, as well as some public source .
-
-% Note that $\mathcal{A}$ is specific to a passive adversary with content recovery in mind.
-We do not abstract $\mathcal{A}$ with active capabilities, since these threats can be protected by existing approaches.
-For example, a malicious server may corrupt stored chunks, yet it can be detected by integrity checking mechanisms \cite{juels07,ateniese07}; a malicious client may cheat owning a particular file \cite{harnik10,halevi11,mulazzani11}, yet it can be addressed by proof of ownership \cite{halevi11} or enforcing server-side deduplication \cite{li15}.
-
-\chapter{Distribution-based Attack}
-\label{sec:distribution-attack}
-
-The distribution-based attack exploits the order information of $\mathbf{C}$
-and $\mathbf{A}$ to strengthen the effectiveness of frequency analysis.  It
-then compares the relative frequency distributions of $\mathbf{C}$ and
-$\mathbf{A}$ to reduce the false positive results.  We also show how to
-exploit chunk size information to further improve the inference precision.
-
-\section{Background: Locality-based Attack}
-\label{sec:prior-attack}
-
-The distribution-based attack builds on the previously proposed {\em
-locality-based attack} \cite{li17}, which shows how frequency analysis causes
-information leakage in backup workloads.  The locality-based attack considers
-{\em full backups} (or backups for short) that are created as the complete
-copies of primary data (e.g., application states, file system snapshots, and
-VM disk images) on a daily or weekly basis. It aims to infer the
-ciphertext-plaintext pairs across different versions of backups.  It assumes
-that the auxiliary information $\mathbf{A}$ is derived from some older
-backups, and its goal is to infer the plaintexts of the latest backup (i.e.,
-$\mathbf{M}$).
-
-The locality-based attack leverages the {\em locality} property
-\cite{xia11,zhu08,lillibridge09}, which is a common phenomenon in practical
-backup workloads. Specifically, the locality property states that neighboring
-chunks tend to co-occur in the {\em same order} across different versions of
-backups before deduplication. The main reason is that the updates to each
-backup are often clustered in some small regions of chunks, while the
-remaining large stretch of chunks appear unchanged or preserve the same order
-across different versions of backups.
-
-Based on locality, the locality-based attack exploits the order information to
-discover the neighboring information of ciphertexts and plaintexts.
-Specifically, for a given unique ciphertext $C$, the attack first identifies
-the set of all identical copies $\{\hat{C}^{(i)}\}$.  For each
-$\hat{C}^{(i)}$, it considers the left and right {\em neighbors} of
-$\hat{C}^{(i)}$, i.e., $\hat{C}^{(i-1)}$ and $\hat{C}^{(i+1)}$, respectively.
-It extracts the sets of left and right neighbors into the associative arrays
-$\mathbf{L_C}$ and $\mathbf{R_C}$, respectively.  The associative arrays store
-the mappings of each unique ciphertext $C$ and its {\em co-occurrence
-frequencies} with its left and right neighbors, respectively.   Similarly, the attack also constructs the
-associative arrays $\mathbf{L_A}$ and $\mathbf{R_A}$ based on the order
-information of $\mathbf{A}$.
-
-The locality-based attack then iterates frequency analysis through the
-neighbors of each inferred ciphertext-plaintext pair.  It first applies
-frequency analysis to infer a number (parameterized by $u$) of top-frequent
-ciphertext-plaintext pairs \{$(C, M)$\} from $\mathbf{C}$ and $\mathbf{A}$.
-The inferred results are likely to be {\em real} (i.e., the target ciphertext
-is indeed mapped from the inferred plaintext), based on the observation that
-the ranks of highly frequent chunks are stable across different versions of
-backups.  For each inferred pair $(C, M)$, the attack finds their left and
-right neighbors that have the most co-occurrence frequencies with $C$ and $M$,
-respectively.  Due to locality, the left and right neighbors of $M$ are likely
-to be the original plaintexts of the corresponding left and right neighbors of
-$C$, respectively.  Thus, the attack also includes the top-frequent left
-(resp. right) neighbors of $C$ and $M$ into the set of the resulting inferred
-ciphertext-plaintext pairs.  Finally, the attack procedure iterates until the
-neighbors of each inferred ciphertext-plaintext pair are examined.
-
-%It applies frequency analysis to infer new ciphertext-plaintext pairs that
-%have the same co-occurrence frequency rank among corresponding neighbors. The
-%rationale is the order of chunks is preserved by chunk locality, and the left
-%and right neighbors of $M$ are likely to be the original plaintexts of the
-%corresponding neighbors of $C$. Thus, the attack further iterates the same
-%frequency analysis through the neighbors of these newly inferred
-%ciphertext-plaintext pairs, so as to increase attack severity.
-
-%if $u$ is small. The rationale is the ranks of highly frequent chunks are
-%stable across backups. On the other hand, a smaller $u$ degrades the coverage
-%of inferred ciphertext-plaintext pairs, and we examine the impact of $u$ in
-%Section~\ref{sec:experiment-distribution}.
-
-However, the locality-based attack has a major weakness that it  introduces
-a high number of false positives (i.e., incorrect ciphertext-plaintext pairs).
-Since the main idea of frequency analysis is to map ciphertexts to plaintexts
-with the same frequency ranks, any disturbance to frequency ranking (e.g., 
-the updates across backups) can lead to incorrect ciphertext-plaintext pairs,
-which can in turn comprise the inference of their neighbors.  Although the
-locality-based attack is shown to effectively infer a significant fraction of
-real ciphertext-plaintext pairs,  the adversary has low confidence to tell
-whether each inferred ciphertext-plaintext pair is real or a false positive.
-
-% For example, our evaluation shows although the locality-based attack can correctly infer 15.2\% of ciphertext-plaintext pairs in some case, the false positives take around 65.2\% in its inference results.
-In other words, the adversary has low confidence in identifying whether the inferred ciphertext-plaintext pairs are correct or not.
-
-% Our observation is frequency analysis essentially dominates the severity of the locality-based attack, yet it is {\em sensitive to frequency ranking}.
-Specifically, any disturbance (e.g., due to data updates or sorting the tied chunks that have the same frequency) to the frequency rank can greatly degrade the inference accuracy.
-These incorrectly inferred ciphertext-plaintext chunk pairs will compromise the iterations of their neighboring chunks (see above), and hence lead to low inference rate.
-% Although the authors \cite{li17} use a parameter (e.g., $u$, see above) to limit only a small number of top-frequent chunk pairs to be returned by frequency analysis, we find that the trick is not enough for {\em severe} inference attacks that demand high inference rate and accuracy.
-In our experiments, we show the trick is not enough for severity and accuracy.
-A lower bound, although achieves high accuracy, potentially decreases the number of inferred ciphertext-plaintext chunk pairs.
-
- % The adversary adds the newly inferred top-frequent chunk pairs into $\mathcal{G}$, and iterates until $\mathcal{G}$ is empty.
-% We apply frequency analysis to find the most frequent ciphertext-plaintext chunk pairs from each of LC and LM, and similarly from RC and RM.
-In other words, we find the left and right neighboring chunks of C and M that have the most co-occurrences with C and M themselves, respectively.
-% infer new ciphertext-plaintext pairs from the neighbors of $C$ and $M$.
-Specifically, it sorts the left and right neighbors of $C$ and $M$ based on their co-occurrence frequencies with $C$ and $M$, respectively, and infer
-% collects their left and right neighbors, and applies frequency analysis 
-% applies    
-% on frequency analysis as underlying primitive, and repeats it based on . Specifically,  The key idea behind the locality-based attack is to 
-% the original plaintext of ciphertext   
-% which  
-% . Specifically, chunk locality states   
-% to repeat frequency analysis.  To exploit chunk locality, the adversary first applies   
-% To launch locality-based attack, the adversary first
-
-% and iterates it based on {\em chunk locality} , which specifies neighboring chunks tend to co-occur in the same order.
-Specifically, the adversary first applies frequency analysis to initialize an inferred set $\mathcal{G}$ with a configurable number (parameterized by $u$) of top-frequent ciphertext-plaintext chunk pairs.
-These inferred pairs can be considered correct with a high probability when $u$ is not much large (see \S\ref{sec:bucket_description}).
-In each iteration, the adversary picks one pair $(C, M)$ out of $\mathcal{G}$, and identifies the corresponding neighboring chunks $\mathbf{L}_\mathcal{C}[C]$, $\mathbf{R}_\mathcal{C}[C]$, $\mathbf{L}_\mathcal{M}[M]$ and $\mathbf{R}_\mathcal{M}[M]$ of $C$ and $M$.
-It applies frequency analysis on
-% $\mathbf{L}_\mathcal{C}[C]$ and $\mathcal{L}_\mathcal{M}[M]$, as well as $\mathbf{R}_\mathcal{C}[C]$ and $\mathbf{R}_\mathcal{M}[M]$, according to their co-occurrence frequencies with $C$ and $M$.
-The rationale is the order of chunks is preserved due to locality, and the left and right neighbors of $M$ are likely to be the original chunks of the left and right neighbors of $C$.
-The adversary adds the newly inferred top-frequent chunk pairs into $\mathcal{G}$, and iterates until $\mathcal{G}$ is empty.
-
-% Recall that a ciphertext may repeat in $\mathbf{C}$, and it can be associated with more than one co-occurrences in $\mathbf{L_C}$ and $\mathbf{R_C}$, each of which stores the number of times it appears with its left and right neighbors.
-% co-occur with  left and right neighbors. 
-% store the co-occurrences of left and right neighboring ciphertext in $\mathbf{C}$, respectively.   
-% Specifically, for the $i$-th plaintext $M^{(i)}$ of $\mathbf{M}$, it considers the {\em left} and {\em right neighbor} of $M^{(i)}$ as  $M^{( i-1 )}$ and $M^{( i+1 )}$, which appear directly before and after $M^{( i )}$ in $\mathbf{M}$, respectively.
-It collects the ordering of $\mathbf{A}$ in the form of the associative arrays $\mathbf{L_A}$ and $\mathbf{R_A}$, which store the co-occurrences of neighboring plaintexts in $\mathbf{A}$.
-
-% The attack assumes the adversary's knowledge of order information is distributional, in the form of the associative arrays $\mathbf{L}_\mathcal{C}$ and $\mathbf{R}_\mathcal{C}$, which map each ciphertext chunk $C$ to its left and right neighboring chunks and corresponding co-occurrence frequencies with $C$.
-Note that this can be computed exactly if the adversary knows $\mathcal{L}_o$.
-The adversary can also extract similar arrays $\mathbf{L}_\mathcal{M}$ and $\mathbf{R}_\mathcal{M}$ from $\mathbf{M}_a$.
-% propose the  that builds on  in backup workloads.
-% In this section, we present the {\em distribution-based attack}, which is applicable for {\em both} fixed-size and variable-size chunks in backup data.
-Specifically, the distribution-based attack targets {\em full backups} (or backups for short) that are created as the complete copies of primary data (e.g., application states, file systems, and VM images) on a daily or a weekly basis, and it aims to infer the ciphertext-plaintext pairs across different versions (e.g., $\mathbf{M}$ and $\mathbf{C}$) of backups.
-The distribution-based attack exploits the order information, meaning that the logical orders of plaintexts in orginal file are reflected by the sequences of corresponding ciphertexts in $\mathbf{C}$ (see Section~\ref{sec:leakage}).
-% The distribution-based attack builds on {\em chunk locality} \cite{xia11,lillibridge09,zhu08, li17}, which defines the co-occurrence of neighboring chunks in backups.
-We follow the notations of \cite{li17} to capture chunk locality.
-Based on the neighborhood relationship, we construct the associative arrays $\mathbf{L_M}$ and $\mathbf{R_M}$ to store the co-occurrences of neighboring plaintexts.
-Specifically, for the plaintexts of $M$ and $M'$,  $\mathbf{L_M}[M][M']$ and $\mathbf{R_M}[M][M']$ store the number of times that $M'$ is the left and right neighbor of $M$ in $\mathbf{M}$, respectively.
-We also build the associative arrays $\mathbf{L_C}$ and $\mathbf{R_C}$ to store the co-occurrences of
-% neighboring ciphertexts in $\mathbf{C}$.
-
-\section{Description of Distribution-based Attack}
-\label{sec:distribution-attack-description}
-
-The distribution-based attack extends the locality-based attack \cite{li17} to
-significantly remove false positives.  It leverages the locality property in
-backup workloads as in the locality-based attack.  In addition, for each
-unique ciphertext $C$ in $\mathbf{C}$, we measure its {\em relative frequency
-distribution} based on its co-occurrence frequencies with its neighbors.
-Similarly, we examine the relative frequency distribution of each unique
-plaintext $M$ in $\mathbf{A}$.  Our observation is that for a real
-ciphertext-plaintext pair $(C, M)$, both $C$ and $M$ should have similar
-relative frequency distributions; i.e., their co-occurrence frequencies with
-their respective neighbors are similar.  We treat this observation as a more
-general notion of the locality property, and use it as a condition to filter
-possibly incorrect ciphertext-plaintext pairs.
-
-%Our insight is if $M$ is the original plaintext of $C$, then the relative
-%frequency distributions of $M$ and $C$ are likely to be {\em similar}. The
-%rationale is  $\mathbf{A}$ and $\mathbf{C}$ are mapped from the same source,
-%and hence share a large stretch of unchanged chunks that preserve
-%relative frequency distributions. In other words, we extend frequency
-%analysis, and filter the possibly flawed ciphertext-plaintext pairs $(C,
-%M)$, in which the relative frequency distributions of $C$ and $M$
-%are significantly different. This is expected to improve the precision of
-%inference results. 
-% infer the ciphertext-plaintext pair $(C, M)$ only when $C$ and $M$ have similar relative frequency distributions.
-Thus, we can filter the flawed inference pairs, in which the relative frequency distributions of the ciphertext and corresponding plaintext are likely to be significantly different.
-
-\begin{figure}[t]
-\centering
-\includegraphics[width=.48\textwidth]{pic/distribution-attack.pdf}
-\caption{Workflow of  distribution-based attack.}
-\label{fig:distribution-attack}
-\end{figure}
-
-Figure \ref{fig:distribution-attack} presents the workflow of the
-distribution-based attack. We first sort the unique ciphertexts and  plaintexts by
-their frequencies in $\mathbf{C}$ and $\mathbf{A}$, respectively. As in the
-locality-based attack \cite{li17}, we configure the parameter $u$ and 
-the underlying frequency analysis to return at most $u$ ciphertext-plaintext
-pairs.  In particular, for each unique ciphertext $C_i$ of rank $i$ (where 
-$1 \leq i \leq u$), we examine a number of unique plaintexts $M_{i-r}, \ldots,
-M_i, \ldots, M_{i+r}$ that rank from $i-r$ to $i+r$, where $r$ is a
-configurable parameter (e.g., 10 by default) that indicates the maximum range
-of rank disturbance that can be addressed.
-
-For each $C_i$ (where $1\le i\le u$) and the corresponding $M_j$ (where 
-$i-r\le j\le i+r$),  we compare their relative frequency distributions by
-{\em entropy}, a key concept in information theory that measures the amount of
-information produced by a random source. Here, we adopt the entropy to 
-{\em quantify the randomness of probability distribution} \cite{wang08}.
-Specifically, we define two random variables, denoted by $X$ and $Y$, to
-describe the co-occurrences of $C_i$ with its left and right neighbors,
-respectively, such that the event ``$X=C$'' denotes the case that $C$ is the
-left neighbor of $C_i$, and the event ``$Y=C$'' denotes the case that $C$ is
-the right neighbor of $C_i$.  Thus, we compute the probabilities of both
-events based on $\mathbf{L_C}$ and $\mathbf{R_C}$:   
-%
-\begin{eqnarray}
-\Pr[X = C] = \frac{\mathbf{L_C}[C_i][C]}{\sum_{C' \in \mathbf{L_C}[C_i]} \mathbf{L_C}[C_i][C']}, \nonumber \\
-\Pr[Y = C] = \frac{\mathbf{R_C}[C_i][C]}{\sum_{C' \in \mathbf{R_C}[C_i]} \mathbf{R_C}[C_i][C']}, \nonumber
-\end{eqnarray}
-%
-where $\mathbf{L_C}[C_i]$ and $\mathbf{R_C}[C_i]$ store the left and right
-neighbors of $C_i$, respectively, while $\mathbf{L_C}[C_i][C']$ and
-$\mathbf{R_C}[C_i][C']$ store the co-occurrence frequencies of $C_i$ with its
-left and right neighbor $C'$.  Both $X$ and $Y$ follow the relative frequency
-distributions of $C_i$, and we characterize their randomness by entropies
-denoted by $e(\mathbf{L_C}[C_i])$ and $e(\mathbf{R_C}[C_i])$, respectively:  
-%
-\begin{eqnarray}
-    e(\mathbf{L_C}[C_i]) = \sum_{C \in \mathbf{L_C}[C_i]} \log_2\frac{1}{\Pr[X = C]}, \nonumber \\
-    e(\mathbf{R_C}[C_i]) = \sum_{C \in \mathbf{R_C}[C_i]} \log_2\frac{1}{\Pr[Y = C]}. \nonumber
-	% e_{C_i}.r = \sum_{C' \in \mathbf{R_C}[C_i]} {\sf log}_2 \frac{\mathbf{R_C}[C_i][C']}{\sum_{C'' \in \mathbf{R_C}[C_i]} \mathbf{R_C}[C_i][C'']}, 
-\end{eqnarray}
-
-Similarly, we compute the entropies $e(\mathbf{L_A}[M_j])$ and
-$e(\mathbf{R_A}[M_j])$ of each $M_j$ based on $\mathbf{L_A}$ and
-$\mathbf{R_A}$, respectively.  We then quantify the similarity of the relative
-frequency distributions of $C_i$ and $M_j$ via the {\em Euclidean distance},
-denoted by $d(C_i, M_j)$:  
-% is used to measure the amount of information produced by a 
- % random source. Specifically, we compute the entropies $e_{C_i}.l$ and $e_{C_i}.r$ of $C_i$ based on the co-occurrence frequencies of $C_i$ with its left and right neighbors, respectively:  
-% \begin{eqnarray}
-	% e_{C_i}.l = \sum_{C' \in \mathbf{L_C}[C_i]} {\sf log}_2 \frac{\mathbf{L_C}[C_i][C']}{\sum_{C'' \in \mathbf{L_C}[C_i]} \mathbf{L_C}[C_i][C'']}, \\
-	% e_{C_i}.r = \sum_{C' \in \mathbf{R_C}[C_i]} {\sf log}_2 \frac{\mathbf{R_C}[C_i][C']}{\sum_{C'' \in \mathbf{R_C}[C_i]} \mathbf{R_C}[C_i][C'']}, 
-% \end{eqnarray}
-% where $\mathbf{L_C}[C_i]$ and $\mathbf{R_C}[C_i]$ store the left and right neighbors of $C_i$, respectively, and $\mathbf{L_C}[C_i][C']$ and $\mathbf{R_C}[C_i][C']$ stores the co-occurrence frequencies of $C_i$ with its corresponding neighbor $C'$.
-Similarly, we compute the entropies $e_{M_j}.l$ and $e_{M_j}.r$ of each $M_j$ based on $\mathbf{L_M}$ and $\mathbf{R_M}$, and collectively measure the similarity of the relative frequency distributions of $C_i$ and $M_j$ via the Euclidean distance:
-\begin{eqnarray*}
-	d(C_i, M_j) & = & 
-	\big\{[e(\mathbf{L_C}[C_i]) - e(\mathbf{L_A}[M_j])]^2 \\
-	& & + \ \ [e(\mathbf{R_C}[C_i]) - e(\mathbf{R_A}[M_j])]^2\big\}^{1/2}.
-\end{eqnarray*}
-
-Clearly, $C_i$ and $M_j$ have similar relative frequency distributions only
-when the Euclidean distance $d(C_i, M_j)$ of their entropies is small.
-Thus,  we identify $(C_i, M_j)$ as an inferred ciphertext-plaintext pair if
-they satisfy the following requirements: 
-%
-\begin{itemize}[leftmargin=*]
-\item {\bf R1:} $d(C_i, M_j)$ is the {\em smallest} for all $i-r \leq j \leq i+r$.
-\item {\bf R2:} $d(C_i, M_j)$ is not larger than a pre-defined parameter $t$ (e.g., 1 by default).
-\end{itemize}
-
-% One special note is R1 is necessarily that some $M_j$  satisfies R1.
-
-One special note is that the original plaintext of $C_i$ may fall outside of
-the examined plaintexts $M_{i-r}, \ldots, M_{i+r}$. 
-In this case, R1 is still satisfied by some $M_j$ ($i-r \leq j \leq i+r$), and we expect to filter the incorrect ciphertext-plaintext pair by R2.
-
-% {\bf We use the requirement R2, and expect it can filter the flawed
-% inference results that map $C_i$ to some $M_j$ in this case. PC: don't quite
-% understand the statement???}
-
-Then, we adopt the iteration paradigm in the prior locality-based attack \cite{li17} (see Section~\ref{sec:prior-attack}) to increase the coverage of inferred ciphertext-plaintext pairs.
-Specifically, for each inferred $(C_i, M_j)$, we apply the new frequency analysis scheme (see above) to infer more ciphertext-plaintext pairs through the neighbors of $C_i$ and $M_j$, and further iterate the same inference for those newly inferred pairs.
-We finally stop the iteration, when none of new ciphertext-plaintext pairs can be inferred.
-
-% Like the prior attack , we then iterate with each inferred  to infer more ciphertext-plaintext pairs from their neighbors.
-We apply the proposed new frequency analysis scheme (see above) through the left and right neighbors of $C_i$ and $M_j$, respectively, and
-% through the neighbors of  to infer more . , and further iterate   
-% {\bf PC: can we not mention $\mathcal{Q}$ in this paragraph???} Then, we operate a first-in-first-out queue $\mathcal{Q}$, and apply the same locality-based paradigm (see Section~\ref{sec:prior-attack}) like the prior attack \cite{li17}.
-Specifically, we initialize $\mathcal{Q}$ with all ciphertext-plaintext pairs that have already been inferred.
-Each time, we pick one pair $(C_i, M_j)$ out of $\mathcal{Q}$, and apply the distribution-based frequency analysis (see above) over the left and right neighbors of $C_i$ and $M_j$, respectively.
-We include the newly inferred ciphertext-plaintext pairs into $\mathcal{Q}$, and finally stop the iteration until $\mathcal{Q}$ is empty.
-
- % For each inferred pair $(C_i, M_j)$, we apply the same locality-based paradigm like the prior attack \cite{li17}. Specifically, we operate a first-in-first-out queue $\mathcal{Q}$
-% To repeat the distribution-based ranking, we initialize a first-in-first-out queue $\mathcal{Q}$ with the ciphertext-plaintext pairs inferred in Step 1.
-Each time, we pick one pair $(C_i, M_j)$ out of $\mathcal{Q}$, and apply the distribution-based ranking over their corresponding neighbors $\mathbf{L_C}[C_i]$ and $\mathbf{L_M}[M_j]$, as well as $\mathbf{R_C}[C_i]$ and $\mathbf{R_M}[M_j]$.
-From each case, we infer new ciphertext-plaintext pairs, and add them into $\mathcal{Q}$ for future loops.
-We finally stop the loop until $\mathcal{Q}$ is empty.
- % Our rationale of R2 is , and the parameter $t$ helps filter  
- % helps filter out these flawed inference results.
-
-\paragraph{Summary:} To summarize, the distribution-based attack provides a
-more general notion of locality by considering the relative frequency
-distribution during frequency analysis.  It is configured by three parameters
-(i) $u$, which specifies the maximum number of ciphertext-plaintext pairs returned by frequency analysis, 
-(ii) $r$, which specifies the maximum range of rank disturbance to be
-considered, and (iii) $t$, which specifies the Euclidean distance threshold to
-filter possibly incorrect inference results. 
-The prior locality-based attack \cite{li17} can be regarded as a special case
-of the distribution-based attack under the parameter configuration of $r = 0$
-(i.e., without addressing any disturbance to frequency ranking) and 
-$t\rightarrow\infty$ (i.e., without filtering any incorrect inference results).
-
- % to 
- % specify the maximum range of disturbance to frequency ranking the scheme considers to address and the maximum entropy threshold
-
-% The locality-based attack can be regarded as a special case of the distribution-based attack under the
-
-\section{Exploiting Size Leakage}
-
-We propose an advanced variant of the distribution-based attack that operates with size information to further reduce false positives.
-Specifically, we assume that the size of each ciphertext in $\mathbf{C}$ reflects that of its original plaintext.
-
-% The distribution-based attack addresses the precision of inference results by comparing relative frequency distributions.
-We argue that there is oppurtunity to further reduce the number of false positives by exploiting size leakage.
-Specifically, we make an additional assumption that
-
-% The rationale is symmetric encryption (e.g., block cipher) preserves the number of blocks.
-
-Our idea builds on the fundamental truth that if a ciphertext $C$ corresponds to a plaintext $M$, then the size of $C$ approximates that of $M$.
-This is because encrypted deduplication preserves the number of blocks (i.e., the basic units operated by symmetric encryption) in the content to be encrypted.
-We use this fact to further filter the incorrect ciphertext-plaintext pairs $(C, M)$, where the number of blocks in $C$ and $M$ are different.
-
-% In other words, the number of blocks in each plaintext is exactly mapped to that in the corresponding ciphertext.
-
-% Our idea is based on the fundamental truth that if $C$ is mapped from $M$, then the size of $C$ approximates that of $M$.
-This is because encrypted deduplication preserves the number of blocks.
-In other words, we can filter the candiate pair $(C_i, M_j)$, where the number of blocks of $C_i$ and $M_j$ are different.
-
-In this work, we assume that each block is of 16 bytes, which is a typical configuration for AES.
-For each considered ciphertext-plaintext pair $(C_i, M_j)$, we derive the number of blocks in $C_i$ and $M_j$ as $b({C_i})$ and $b({M_j})$, respectively:
-\begin{eqnarray*}
-b({C_i}) = \lceil \frac{{\sf size}(C_i)}{16} \rceil, \nonumber \\
-b({M_j}) = \lceil \frac{{\sf size}(M_j)}{16} \rceil, \nonumber 
-\end{eqnarray*}
-where ${\sf size}(C_i)$ and ${\sf size}(M_j)$ are the exact sizes of $C_i$ and $M_j$, respecitively, and $\lceil x \rceil$ returns the smallest integer greater than or equal to $x$.
-In addition to R1 and R2 (see Section~\ref{sec:distribution-attack-description}), we apply the following requirement to filter by size:
-\begin{itemize}[leftmargin=*]
-    \item {\bf R3:} $b({C_i})$ equals $b({M_j})$.
-\end{itemize}
-
-The requirement R3 is effective to filter the incorrect ciphertext-plaintext pairs regarding variable-size chunks, where different chunks possibly have distinct sizes.
-However, for fixed-size chunks, it is always satisfied by the ciphertext-plaintext pairs, even they are incorret.
-Despite of this, we can still apply R1 and R2 to achieve high-precision attack.
-
-% for filtering false positives in terms of only variable-size chunks, where different chunks have possibly distinct sizes.
-On the other hand, it is always satisfied by fixed-size chunks, and cannot improve the precision of inference results in this case.
-Even so, we can still apply R1 and R2 to significantly reduce the amount of false positives in the locality-based attack \cite{li17} (see Section~\ref{sec:distribution-attack-description}).
-
-% by {\bf about 50\%} (see Section~\ref{sec:experiment-distribution}).
-
-% percentage of false positives below 25\% .
-
-% \paragraph{Discussion:}
-% The filtering effect of R3 depends on the size distribution of  (variable-size) chunks.
-Since encrypted deduplication only preserves approximate size (i.e., the number of blocks), R3 cannot detect the false positive, which maps a ciphertext to some flawed plaintext that shares the same number of blocks with corresponding exact plaintext.
-This makes it less effective in addressing inference precision against the workloads, where the sizes of majority chunks are clustered within a small range.
-
-% Specifically, it is less effective in reducing the number of false positives against the workloads, in which the sizes of chunks are clustered into a small range.
-The reason is the adversary who observes the size of a ciphertext can only deduce the number of blocks in corresponding plaintext.
-
-% The plaintexts whose sizes are clustered are more likely to have the same number of blocks, and the adversary cannot distinguish them by size.
-
-% The main reason is the adversary can deduce the size of the plaintext in the quantization factor of block size.   
-% Due to the above facts, an adversary who can see the length of a ciphertext can readily deduce the length of the respective plaintext, except for a quantization factor of 8 or 128 respectively.
-The larger the quantization factor, the less resolution the attacker has regarding plaintext length information.
-Rupture is able to attack ciphers with even large quantization factors, yet a larger factor can make the attack slower.
-While the quantization factor can be made arbitrarily large when designing ciphers, the penalty being paid is in bandwidth consumed to transmit the ciphertext.
-% and R3 is less effective in reducing the false positives against small-size chunks.
-% only for variable-size chunks, where different chunks have possibly distinct sizes. It is naturally satisfied by fixed-size chunks, and cannot filter any false positives. In this case, this  
-% In addition, the effect of R3 depends on the (average) size of chunks.
-
-% \paragraph{Discussion:}
-% The size-based attack builds on the assumption of varying sizes of chunks, and demonstrates security alert only in variable-size chunking.
-In other words, the size-based attack will degrade to classical frequency analysis under fixed-size chunking, in which all plaintexts or ciphertexts have a uniform size and come into a single entry of the associative array.
-% The effectiveness of the size-based attack depends on the (average) size of chunks, and it is less effective for inferring small-size chunks.
-For example, we have evaluated that the size-based attack infers as low as 0.32\% of ciphertext-plaintext pairs against the chunks of an average size of 2KB (for comparison, it can infer up to 31.3\% ciphertext-plaintext pairs in our experiment of 8KB-size chunks, see Section~\ref{sec:experiment-size}).
-This is mainly for two reasons.
-First, small-size chunks are likely to have limited  variance on their size, and aggregate into a few entries of the associative array; this degrades the coverage of inferred pairs (recall that the attack  returns a limited number of ciphertext-plaintext pairs for each available chunk size).
-Second, each entry of the associative array is likely to include a large amount of small-size chunks, among which
-% there tend to exist many ties where chunks have the same frequency; 
- % this possibly introduces additional false positives into frequency analysis \cite{naveed15, li17}.
-
-% For each $M_j$ ($i-r \leq j \leq i+r$), we compute similar entropies $e_{M_j}.l$ and $e_{M_j}.r$ for $M_j$, and collectively measure the similarity of the relative frequency distributions of $C_i$ and $M_j$ via the Euclidean distance:
-
-% We first sort available ciphertexts and plaintexts by their frequencies in $\mathbf{C}$ and $\mathbf{M}$, respectively.
-Next, we consider the distribution-based ranking scheme configured by a tuple of parameters $(u, r, t)$, in order to infer at most $u$ ciphertext-plaintext pairs.
-Specifically, for each ciphertext $C_i$ of rank $i$ ($1 \leq i \leq u$), we examine the plaintexts $M_{i-r},\ldots,M_i,\ldots,M_{i+r}$ that rank from $i-r$ to $i+r$, where $r$ (e.g., 10 by default) indicates the maximum range of rank disturbance can be addressed by the distribution-based ranking scheme.
-Then, we compute the entropies $e_{C_i}.l$ and $e_{C_i}.r$ of $C_i$ based on the co-occurrences of $C_i$ with its left and right neighbors, respectively:\footnote{Alternatively, we can calculate the entropies (that depend on the associative arrays $\mathbf{L_C}$ and $\mathbf{R_C}$) in
-% pre-processing, rather than computing them on the fly.} 
-% \begin{eqnarray}
-% 	e_{C_i}.l = \sum_{C' \in \mathbf{L_C}[C_i]} {\sf log}_2 \frac{\mathbf{L_C}[C_i][C']}{\sum_{C'' \in \mathbf{L_C}[C_i]} \mathbf{L_C}[C_i][C'']}, \\
-% 	e_{C_i}.r = \sum_{C' \in \mathbf{R_C}[C_i]} {\sf log}_2 \frac{\mathbf{R_C}[C_i][C']}{\sum_{C'' \in \mathbf{R_C}[C_i]} \mathbf{R_C}[C_i][C'']}, 
-% \end{eqnarray}
-% where $\mathbf{L_C}[C_i]$ and $\mathbf{R_C}[C_i]$) store the left and right neighbors of $C_i$, respectively, and $\mathbf{L_C}[C_i][C']$ and $\mathbf{R_C}[C_i][C']$ stores the co-occurrences of $C_i$ with its corresponding neighbor $C'$.
-For each $M_j$ ($i-r \leq j \leq i+r$), we compute similar entropies $e_{M_j}.l$ and $e_{M_j}.r$ for $M_j$, and collectively measure the similarity of the relative frequency distributions of $C_i$ and $M_j$ via the Euclidean distance:
-% \begin{eqnarray}
-% 	{\sf Sim}(C_i, M_j) = \sqrt{(e_{C_i}.l - e_{M_j}.l)^2 + (e_{C_i}.r - e_{M_j}.r)^2}.  
-% \end{eqnarray}
-
-%  We infer $(C_i, M_j)$ as a ciphertext-plaintext pair, if (i) ${\sf Sim}(C_i, M_j)$ is the {\em smallest} among all examined plaintexts, and (ii) ${\sf Sim}(C_i, M_j)$ is not larger than the parameter $t$ (e.g., 1 by default).
-Our rationale is that the original plaintext of $C_i$ may fall outside of $M_{i-r}, \ldots, M_{i+r}$ (e.g., the range of rank disturbance is greater than $r$), and the pre-defined upper bound $t$ helps filter out these flawed inference results.
-
-% Our insight is that if $M$ is the underlying plaintext of $C$, then the relative frequency distributions of $C$ and $M$ are likely to be {\em similar}.
-The rationale is that $\mathbf{M}$ and $\mathbf{C}$ are from the same primary data (at different time), and hence share a large stretch of unchanged chunks due to chunk locality.
-Thus, we can adjust the ranking of classical frequency analysis by taking relative frequency distribution into consideration.
-Specifically, for each ciphertext $C_i$ of rank $i$ and plaintext $M_j$ of rank $j$, we compare their relative frequency distributions, say by the {\em entropies} on the co-occurrences of their neighbors.
-If they have similar entropy values, we say their relative frequency distributions are similar, and we call $(C_i, M_j)$ as an inferred ciphertext-plaintext pair, even though $C_i$ and $M_j$ have different ranks (i.e., $i \neq j$).
-
-% Thus, we can operate frequency analysis while taking relative frequency distribution into consideration, in order to filter out the inference results, in which the relative frequency distributions of the ciphertext and plaintext are significantly different.
-% Specifically, for each  plaintext $M$, we consider its {\em relative frequency distribution} that is counted by the co-occurrences of $M$ with its neighboring plaintexts (recall that $M$ may have duplicate copies and hence multiple neighbors in $\mathbf{M}$).
-We also count the relative frequency distribution of each ciphertext $C$.
- % Thus, we can adjust the ranking of classical frequency analysis by taking relative frequency distribution into consideration.
-Specifically, for each ciphertext $C_i$ of rank $i$ and plaintext $M_j$ of rank $j$, we compare their relative frequency distributions, say by the {\em entropies} on the co-occurrences of their neighbors.
-If they have similar entropy values, we say their relative frequency distributions are similar, and we call $(C_i, M_j)$ as an inferred ciphertext-plaintext pair, even though $C_i$ and $M_j$ have different ranks (i.e., $i \neq j$).
-% The key idea of our attack is to inspect the distribution of , so as to filter out potentially flawed inference results.
-% t further inspects the relative frequency distribution of the data and filters any potentially flawed inference results.
-% We propose to extend chunk locality, and examine the frequency .
-
-% Inspired by chunk locality (see \S\ref{sec:locality}), we move one step further to examine the co-occurrence of neighboring chunks.
-% Specifically, for each chunk, we consider its {\em relative frequency distribution} that is counted by the number of co-occurrences with its neighbors (recall that a chunk may have duplicate copies and hence multiple neighboring chunks).
-Our insight is that identical chunks likely have {\em similar} relative frequency distributions across backups.
-The rationale is updates to backups appear in few clustered regions of chunks, while the remaining majority regions of chunks preserve their co-occurrence relationships.
-
-% Chunk locality states that neighboring chunks tend to co-occur under the same order across backups.
-For example, if a plaintext $M$ is surrounded by the plaintexts $M'$ and $M''$ in one backup, then $M$ is also likely to be surrounded by $M'$ and $M''$ in the following backups.
-Prior works \cite{xia11,lillibridge09,zhu08} have exploited chunk locality to improve performance, while we adapt it into addressing the false positives in frequency analysis.
-Specifically, classical frequency analysis is sensitive to frequency ranking, and any disturbances (e.g., due to data updates across backups or ranking the ciphertexts/plaintexts that have identical frequency) to the frequency ranking can introduce a significant amount of flawed inference results.
-   % In the following, we show how to build on chunk locality to construct an inference attack with low false positives.
-We first elaborate the key designs of the distribution-based attack, and then present the attack details step by step.
-
-% {\bf say drawback of classical frequency analysis}
-
-% Take {\em backups}, the complete copies of some primary data (e.g., application states, file systems, and VM images), as an example, if a plaintext $M$ is surrounded by the plaintexts $M'$ and $M''$ in one backup, then $M$ is also likely to be surrounded by $M'$ and $M''$ in the following backup from the same primary data.
-Prior works \cite{xia11,lillibridge09,zhu08} have exploited chunk locality to improve performance, while we adapt it into addressing the false positives of inference attack.
-
-% Figure \ref{fig:distribution-attack} shows an overview of the distribution-based attack.
-Given the input of $\mathbf{M}$ and $\mathbf{C}$, it builds on the {\em distribution-based ranking} to reduce the number of false positives in classical frequency analysis.
-Specifically, for each  plaintext $M$, we consider its {\em relative frequency distribution} that is counted by the co-occurrences of $M$ with its neighboring plaintexts (recall that $M$ may have duplicate copies and hence multiple neighbors in $\mathbf{M}$).
-We also count the relative frequency distribution of each ciphertext $C$.
-% Our insight is that if $M$ is the underlying plaintext of $C$, then the relative frequency distributions of $C$ and $M$ are likely to be {\em similar}.
-The rationale is that $\mathbf{M}$ and $\mathbf{C}$ are from the same primary data (at different time), and hence share a large stretch of unchanged chunks due to chunk locality.
-Thus, we can adjust the ranking of classical frequency analysis by taking relative frequency distribution into consideration.
-Specifically, for each ciphertext $C_i$ of rank $i$ and plaintext $M_j$ of rank $j$, we compare their relative frequency distributions, say by the {\em entropies} on the co-occurrences of their neighbors.
-If they have similar entropy values, we say their relative frequency distributions are similar, and we call $(C_i, M_j)$ as an inferred ciphertext-plaintext pair, even though $C_i$ and $M_j$ have different ranks (i.e., $i \neq j$).
-
-% For each inferred ciphertext-plaintext pair $(C_i, M_j)$, we repeat the same inference (see above) through their neighbors.
-Specifically, we collect the left and right neighbors of $C_i$,  as well as of $M_j$, respectively, and apply the distribution-based ranking over their corresponding neighbors, in order to infer new ciphertext-plaintext pairs.
-The rationale is that chunk locality preserves orders, and the left and right neighbors of $M_j$ are likely to be the underlying plaintexts of the left and right neighbors of $C_i$, respectively.
-We further repeat the inference through the neighbors of these newly inferred ciphertext-plaintext pairs, so as to increase the coverage of inferred pairs.
-
-% Then, we describe the details of the distribution-based attack.
-
-% The distribution-based ranking proceeds as follows. We first rank available ciphertexts and plaintexts by their frequencies in $\mathbf{C}$ and $\mathbf{M}$, respectively. 
-% Thus, we can adjust the ranking of classical frequency analysis by taking the relative frequency distribution of each plaintext and ciphertext into account.
-In other words, suppose $C_i$ and $M_j$ are the $i$-th and $j$-th top frequent ciphertext and plaintext, respectively.
-% This allows to infer the ciphertext-plaintext pair like $(C_i, M_j)$ 
-% To perform distribution-based ranking,
-
-% Thus, we          
-% Thus, we first establish the frequency-only ranking like classical frequency analysis (see \S\ref{sec:freqanalysis}), and then adjust the ranking by taking into account the relative frequency distributions of chunks.
-Roughly, we break rank disturbances and infer the ciphertext-plaintext chunks pairs
-% $(C_i, M_j)$, where $C_i$ and $M_j$ have similar relative frequency distribution yet possibly different ranks (e.g., $i \neq j$).
-We refer the Step 1 of the attack for detailed requirements of $C_i$ and $M_j$.
-
-% We propose a new (frequency-based) ranking primitive, named {\em distribution-based ranking}, to address the ties incurred in classcial frequency analysis (see \S\ref{sec:freqanalysis}).
-Specifically, for each chunk, we consider its {\em relative frequency distribution} that is counted by the co-occurrences with its neighbors (recall that a chunk may have duplicate copies and hence multiple neighbors).
-Our insight is that the relative frequency distribution of the same chunk must be similar across backups.
-The reason is chunk locality implies that the majority stretches of chunks are unchanged.
-Thus, we first establish the frequency-only ranking like classical frequency analysis (see \S\ref{sec:freqanalysis}), and then adjust the ranking by taking into account the relative frequency distributions of chunks.
-Roughly, we break rank disturbances and infer the ciphertext-plaintext chunks pairs
-% $(C_i, M_j)$, where $C_i$ and $M_j$ have similar relative frequency distribution yet possibly different ranks (e.g., $i \neq j$).
-We refer the Step 1 of the attack for detailed requirements of $C_i$ and $M_j$.
-% We elaborate the details below.
-
-% \paragraph{Step 1 (Distribution-based ranking):}
-% We first sort available ciphertexts and plaintexts by their frequencies in $\mathbf{C}$ and $\mathbf{M}$, respectively.
-Next, we consider the distribution-based ranking scheme configured by a tuple of parameters $(u, r, t)$, in order to infer at most $u$ ciphertext-plaintext pairs.
-Specifically, for each ciphertext $C_i$ of rank $i$ ($1 \leq i \leq u$), we examine the plaintexts $M_{i-r},\ldots,M_i,\ldots,M_{i+r}$ that rank from $i-r$ to $i+r$, where $r$ (e.g., 10 by default) indicates the maximum range of rank disturbance can be addressed by the distribution-based ranking scheme.
-Then, we compute the entropies $e_{C_i}.l$ and $e_{C_i}.r$ of $C_i$ based on the co-occurrences of $C_i$ with its left and right neighbors, respectively:\footnote{Alternatively, we can calculate the entropies (that depend on the associative arrays $\mathbf{L_C}$ and $\mathbf{R_C}$) in
-% pre-processing, rather than computing them on the fly.} 
-% \begin{eqnarray}
-% 	e_{C_i}.l = \sum_{C' \in \mathbf{L_C}[C_i]} {\sf log}_2 \frac{\mathbf{L_C}[C_i][C']}{\sum_{C'' \in \mathbf{L_C}[C_i]} \mathbf{L_C}[C_i][C'']}, \\
-% 	e_{C_i}.r = \sum_{C' \in \mathbf{R_C}[C_i]} {\sf log}_2 \frac{\mathbf{R_C}[C_i][C']}{\sum_{C'' \in \mathbf{R_C}[C_i]} \mathbf{R_C}[C_i][C'']}, 
-% \end{eqnarray}
-% where $\mathbf{L_C}[C_i]$ and $\mathbf{R_C}[C_i]$) store the left and right neighbors of $C_i$, respectively, and $\mathbf{L_C}[C_i][C']$ and $\mathbf{R_C}[C_i][C']$ stores the co-occurrences of $C_i$ with its corresponding neighbor $C'$.
-For each $M_j$ ($i-r \leq j \leq i+r$), we compute similar entropies $e_{M_j}.l$ and $e_{M_j}.r$ for $M_j$, and collectively measure the similarity of the relative frequency distributions of $C_i$ and $M_j$ via the Euclidean distance:
-% \begin{eqnarray}
-% 	{\sf Sim}(C_i, M_j) = \sqrt{(e_{C_i}.l - e_{M_j}.l)^2 + (e_{C_i}.r - e_{M_j}.r)^2}.  
-% \end{eqnarray}
-
-%  We infer $(C_i, M_j)$ as a ciphertext-plaintext pair, if (i) ${\sf Sim}(C_i, M_j)$ is the {\em smallest} among all examined plaintexts, and (ii) ${\sf Sim}(C_i, M_j)$ is not larger than the parameter $t$ (e.g., 1 by default).
-Our rationale is that the original plaintext of $C_i$ may fall outside of $M_{i-r}, \ldots, M_{i+r}$ (e.g., the range of rank disturbance is greater than $r$), and the pre-defined upper bound $t$ helps filter out these flawed inference results.
-
-% We  apply classical frequency analysis to establish the (frequency-only) ranking on the plaintext chunks in $\mathbf{M}_{\rm a}$, as well as on the ciphertext chunks in $\mathcal{L}_{\rm order}$.
-Like the size-based attack (see \S\ref{sec:size-attack-description}), we configure the parameter $u$ that indicates the {\em maximum} number of most frequent chunk pairs to be inferred by our distribution-based ranking scheme.
-% Then,  For $C_i$ and each $M_j$ $(i-r \leq j \leq i+r)$, we compare their relative frequency distributions, say by the {\em entropies} of neighboring chunks.
-Specifically, we compute the entropies $e_{M_j}.l$ and $e_{M_j}.r$ based on the co-occurrences of $M_j$ and its left and right neighbors, respectively:
-% (recall that we can access the co-occurrences of $M_j$ and its neighbors from $\mathbf{L}_{\rm a}$ and $\mathbf{R}_{\rm a}$).
-
-% For example, if a chunk $M$ is surrounded by the chunks $M'$ and $M''$ in one backup, then $M$ is also likely to be surrounded by $M'$ and $M''$ in the following backups.
-The rationale is that the changes of backups often affect a few chunks, while the remaining chunks repeat in the same order.
-
-% The distribution-based attack builds on {\em chunk locality}  that is defined based on the neighborhood of chunks.
-Specifically, given a logical chunk $M^{\langle i \rangle}$, we define its {\em left} (resp.
-{\em right}) {\em neighbor} as the logical chunk $M^{\langle i-1 \rangle}$ (resp.
-$M^{\langle i+1 \rangle}$) that appears directly before (resp.
-after) $M^{\langle i \rangle}$.
-
-% To capture chunk locality, we build the associative arrays $\mathbf{L}_{\rm a}$ and $\mathbf{R}_{\rm a}$, which store the co-occurrences of neighboring  chunks in the auxiliary information $\mathbf{M}_{\rm a}$.
-Specifically, for two neighboring chunks $M$ and $M'$, $\mathbf{L}_{\rm a}[M][M']$ (resp.
-$\mathbf{R}_{\rm a}[M][M']$) stores the number of times that $M'$ is the left (resp.
-right) neighbor of $M$.
-For the ciphertext chunks, we also extract $\mathbf{L}_{\rm t}$ and $\mathbf{R}_{\rm t}$ to store the co-occurrences of their original chunks (recall that we can access the orders of original chunks by $\mathcal{L}_{\rm order}$).
-
-% even they have different frequency ranks of $i$ and $j$ (see Step 1 for detailed requirements on .    
-% This allows us to address rank disturbances and infer the
-
-% We propose the {\em distribution-based ranking}, which exploits the co-occurrences of neighboring chunks to address the rank disturbances (e.g., due to data updates or breaking ties) of classical frequency analysis (\S\ref{sec:freqanalysis}).
-Specifically, for each chunk,
-
-% the distribution-based ranking through their neighboring chunks.
-Specifically, we establish the distribution-based ranking on the left and right neighbors of $C_i$ and $M_j$, and infer more ciphertext-plaintext chunk pairs.
-The rationale is that the neighbors of $M_j$ are likely to be the neighbors of the original chunk of $C_i$, since chunk locality implies that the orders of chunks are preserved.
-We iterate the similar inference through the neighbors of those newly inferred chunk pairs, so as to increase attack severity.
-
-% Thus, we can infer more ciphertext-plaintext chunk pairs and increase attack severity based on the iterative inferences.
-
-% In this work,  a tuple $(u, r, t)$ of parameters.
-% the co-occurrences of neighboring chunks are likely to be preserved across backups.
-
-% (recall that we can access the logical orders of original chunks from $\mathcal{L}_{\rm order}$). 
-% Based on the data structures, we first propose a new frequency analysis primitive, the {\em distribution-based ranking}, to address the rank disturbances of classical frequency analysis (\S\ref{sec:freqanalysis}).
-Then, we explain how to exploit chunk locality to repeat the inference primitive for high severity.
-% introduce a building block,  of the attack, followed by how to repeat the inference for high severity.      
-% \paragraph{Distribution-based ranking:}
-% Frequency analysis is sensitive to frequency ranking, and any disturbances (e.g., due to data updates or breaking ties) to the ranks can greatly degrade its inference accuracy.
-Inspired by chunk locality, we propose to examine the
-% updates to backups commonly appear in few clustered regions of chunks, while the remaining majority  chunks preserve their co-occurrence relationships.
-
-% \paragraph{Step 2 (Repeat distribution-based ranking through neighbors):}
-% To repeat the distribution-based ranking, we initialize a first-in-first-out queue $\mathcal{Q}$ with the ciphertext-plaintext pairs inferred in Step 1.
-Each time, we pick one pair $(C_i, M_j)$ out of $\mathcal{Q}$, and apply the distribution-based ranking over their corresponding neighbors $\mathbf{L_C}[C_i]$ and $\mathbf{L_M}[M_j]$, as well as $\mathbf{R_C}[C_i]$ and $\mathbf{R_M}[M_j]$.
-From each case, we infer new ciphertext-plaintext pairs, and add them into $\mathcal{Q}$ for future loops.
-We finally stop the loop until $\mathcal{Q}$ is empty.
-
-% For each inferred chunk pair $(C_i, M_j)$, we build the {\em locality-based loop} \cite{li17} to repeat inferences through their neighboring chunks.
-Specifically, we collect the set of left $\mathbf{L}_{\rm t}[C_i] = \{C': \mathbf{L}_{\rm t}[C_i][C'] > 0 \}$ and right $\mathbf{R}_{\rm t}[C_i] = \{C': \mathbf{R}_{\rm t}[C_i][C'] > 0 \}$ neighbors of $C_i$, as well as the left $\mathbf{L}_{\rm a}[M_j]$ and right $\mathbf{R}_{\rm a}[M_j]$ neighbors of $M_j$.
-Then, we establish the distribution-based ranking over the chunks in $\mathbf{L}_{\rm t}[C_i]$ and $\mathbf{L}_{\rm a}[M_j]$, as well as in $\mathbf{R}_{\rm t}[C_i]$ and $\mathbf{R}_{\rm a}[M_j]$, respectively, so as to infer more ciphertext-plaintext chunk pairs.
-The rationale is that the chunks in $\mathbf{L}_{\rm a}[M_j]$ (resp.
-$\mathbf{R}_{\rm a}[M_j]$) are likely to be the underlying
-% plaintexts of the ciphertext chunks in $\mathbf{L}_{\rm t}[C_i]$ (resp.
-$\mathbf{R}_{\rm t}[C_i]$), since chunk locality implies that the orders of chunks are preserved.
-We further iterate the similar inference through the neighbors of those newly inferred chunk pairs, so as to increase attack severity.
- % In other words, we infer the ciphertext-plaintext chunk pairs, say $(C, M)$, from the neighbors of $C_i$ and $M_j$, such that (i) $C$ and $M$ have the most co-occurrences with $C_i$ and $M_j$, respectively and (ii) the relative frequency distributions of $C$ and $M$ are highly similar.
-We add the newly inferred  chunk pairs into $\mathcal{Q}$, and finally stop the loop until $\mathcal{Q}$ is empty.
-
-% A special note is that we only examine the possible plaintext chunks that rank from $i$ to $i+r$ (rather than $i-r$ to $i+r$) for the distribution-based ranking in the loop.
-Our rationale is that chunks may have low co-occurrences after a number of loops, and most of them are likely to have similar relative frequency distribution with $C_i$.
-We start examination from rank $i$ to avoid relating the plaintext chunk that has a large rank difference from $i$.
-
-% and all inferred chunk pairs have been iterated.
-
-% and identify their neighbor sets $\mathbf{L}_{\rm t}[C_i], \mathbf{R}_{\rm t}[C_i], \mathbf{L}_{\rm a}[M_j]$ and $\mathbf{R}_{\rm a}[M_j]$.
-We invoke the distribution-based ranking on $\mathbf{L}_{\rm t}[C_i]$ and $\mathbf{L}_{\rm a}[M_j]$, as well as on $\mathbf{R}_{\rm t}[C_i]$ and $\mathbf{R}_{\rm a}[M_j]$, and add the newly inferred ciphertext-plaintext chunk pairs into $\mathcal{Q}$.
-
-% Specifically, the adversary first applies frequency analysis to initialize an inferred set $\mathcal{G}$ with a configurable number (parameterized by $u$) of top-frequent ciphertext-plaintext chunk pairs.
-These inferred pairs can be considered correct with a high probability when $u$ is not much large (see \S\ref{sec:bucket_description}).
-In each iteration, the adversary picks one pair $(C, M)$ out of $\mathcal{G}$, and identifies the corresponding neighboring chunks $\mathbf{L}_\mathcal{C}[C]$, $\mathbf{R}_\mathcal{C}[C]$, $\mathbf{L}_\mathcal{M}[M]$ and $\mathbf{R}_\mathcal{M}[M]$ of $C$ and $M$.
-It applies frequency analysis on $\mathbf{L}_\mathcal{C}[C]$ and $\mathcal{L}_\mathcal{M}[M]$, as well as $\mathbf{R}_\mathcal{C}[C]$ and $\mathbf{R}_\mathcal{M}[M]$, according to their co-occurrence frequencies with $C$ and $M$.
-The rationale is the order of chunks is preserved due to locality, and the left and right neighbors of $M$ are likely to be the original chunks of the left and right neighbors of $C$.
-The adversary adds the newly inferred top-frequent chunk pairs into $\mathcal{G}$, and iterates until $\mathcal{G}$ is empty.
-% from $\mathbf{L}_{\rm t}$ and $\mathbf{R}_{\rm t}$.   
-% since a chunk may have duplicate copies and hence multiple neighbors, we :w
-% can compute the entropies $\mathbf{E}_{\rm tar}[C_i].l$ and $\mathbf{E}_{\rm tar}[C_i].r$, as well as $\mathbf{E}_{\rm aux}[M_j].l$ and $\mathbf{E}_{\rm aux}[M_j].r$, based on the co-occurrences of the neighbors of $C_i$ and $M_j$.
-Thus, we can collectively measure the similarity of relative frequency distributions via Euclidean distance:
-% Note that our ranking approach combines the co-occurrence relationship of neighboring chunks to address the rank disturbance of frequency-only ranking.
-It does not require each inferred pair $(C_i, M_j)$ must have the same rank, i.e., $j$ does not need to equal $i$.
-In \S\ref{}, we will experimentally justify its advantage in distribution-based attack (\S\ref{sec:distribution-description}).
-% Based on chunk locality, we
-
-% \subsection{Discussion}
-% \label{sec:distribution-discussion}
-
-% \noindent {\bf Generalization of prior attack:} 
-% The recent {\em locality-based attack} \cite{li17} builds on chunk locality as our work, in order to improve the severity of frequency analysis against encrypted deduplication.
-The main difference is the prior attack \cite{li17} uses classical frequency analysis as the inference primitive (used in both Step 1 and Step 2 in Section~\ref{sec:distribution-attack-description}), rather than applying the distribution-based ranking to filter out flawed inference results.
-In fact, it \cite{li17} can be regarded as a special case of the distribution-based attack under the parameter configuration of $r = 0$ (i.e., cannot address rank disturbances) and $t = \infty$ (i.e., cannot filter out any flawed inference results).
-
-% \paragraph{Fine-grained ordering knowledge:}
-% For each ciphertext, the distribution-based attack assumes that its deduplication processing sequence reflects the logical order of corresponding plaintext, so that the adversary can identify the neighboring ciphertexts for attack.
-The assumption holds in a variety of real-world storage systems \cite{xia11,lillibridge09,zhu08} that preserve orders in deduplication, yet it can be addressed by scrambling the orders of ciphertexts.
-% % This breaks their neighborhood relationships, and hence prevents the attack.
-
-% (see \S\ref{sec:countermeasure}
-
-% To launch the distribution-based attack, the adversary must have the order information of ciphertexts. In other words, for each ciphertext, the attack  
-% Although the assumption is plausible in a variety ,  
-% the orders of ciphertexts reflect the  
-% knows the logical order of underlying plaintexts in priori.
-
-% The distribution-based attack has some limitations.
-First, the attack assumes that the adversary has full knowledge of neighboring chunks.
-Although it is plausible for some deduplicaton systems \cite{xia11,lillibridge09,zhu08}, we can address the assumption by simply swapping the orders of chunks (see \S\ref{sec:countermeasure}).
-Second, the attack depends on the prevalence of locality in workloads, and it may perform poor in the low-locality workloads.
-
-% In Section~\ref{sec:experiment-distribution}, we will experimentally show that our new attack 
-% can significantly reducing the number of false positives.
-
-% it is reasonable to replace the frequency-only ranking (in classical frequency analysis) by our generalized distribution-based ranking.
-The reason is the inference precision of classical frequency analysis is strongly susceptible to rank disturbances.
- % Any incorrectly inferred ciphertext-plaintext chunk pairs will compromise the following inference loops over their neighbors, and  affect inference rate.
-In \S\ref{sec:experiment-distribution}, we experimentally examine the improvement of our distribution-based attack over the prior locality-based attack \cite{li17}.
- % , which builds on classical frequency analysis as the underlying primitive.    
-% repeat inferences .     
-% Like the , the  builds on the same characteristics of  to demonstrate the security vulnerability of encrypted deduplication.
-% Recently, Li {\em et al.}  , which builds on chunk locality as the distribution-based attack. The difference is the   
-% repeats classical frequency analysis through neighbors of each inferred ciphertext-plaintext pair.
-
-% This limits the adaptability of the distribution-based attack. %for the low-locality workloads (\S\ref{sec:clustering-attack}).
-%, in which the data chunks arrive in the server under random order or from disparate clients.
-
-% % We first review the {\em locality-based attack} \cite{li17} 
-% % that combines frequency and order information to infer plaintext content in encrypted deduplication.
-Then, we present {\em distribution-based attack} that augments the locality-based attack with high inference accuracy.
-% % Note that we do not explicitly exploit size information in these attacks, since they are adapt to fixed-size chunking setting.
-
-% \subsection{Prior Work: Locality-based Attack}
-% \label{sec:locality-attack}
-% The locality-based attack \cite{li17} targets backup workloads.
-It models a prior backup as $\mathbf{M}_{\rm aux}$, and aims to recover the original chunks of a later backup (known as $\mathbf{M}_{\rm tar}$).
-It builds on {\em chunk locality} \cite{xia11,zhu08}, which specifies that neighboring chunks tend to co-occur again in the same order.
-The attack defines the {\em left (resp.
-right) neighbor} of a chunk $M$ is the chunk that appears directly before (resp.
-after) $M$ in logical order.
-It derives a key insight that if $M$ is the original chunk of a ciphertext chunk $C$, then the neighbors of $M$ are likely to be the original chunks of the corresponding neighbors of $C$.
-
-% To represent neighboring relations, the attack assumes that the adversary's knowledge of order information is in the form of the associative arrays $\mathbf{L}_{\rm tar}$ and $\mathbf{R}_{\rm tar}$.
-Specifically, $\mathbf{L}_{\rm tar}[C]$ (resp.
-$\mathbf{R}_{\rm tar}[C]$) maps a ciphertext chunk $C$ to its left (resp.
-right) neighbors and the corresponding co-occurrences with $C$.
-Note that this can be computed exactly if the adversary knows $\mathcal{L}_{\rm order}$.
-In addition, the attack extracts similar arrays $\mathbf{L}_{\rm aux}$ and $\mathbf{R}_{\rm aux}$  from $\mathbf{M}_{\rm aux}$.
-
-% % which map each ciphertext chunk $C$ to its left and right neighboring chunks and corresponding co-occurrence frequencies with $C$.
-
-% To launch attack, the adversary iterates frequency analysis to infer the neighbors of each known ciphertext-plaintext chunk pair.
-Specifically, it first initializes an inferred set $\mathcal{G}$ with a configurable number (e.g., $u$) of top-frequent chunk pairs.
-In each iteration, it picks one pair $(C, M)$ out of $\mathcal{G}$, and applies frequency analysis on their neighbors $\mathbf{L}_{\rm tar}[C]$ and $\mathbf{L}_{\rm aux}[M]$, as well as $\mathbf{R}_{\rm tar}[C]$ and $\mathbf{R}_{\rm aux}[M]$, and further adds the newly inferred top-frequent chunk pairs into $\mathcal{G}$.
-The adversary iterates the above procedure until $\mathcal{G}$ is empty.
-
-%  % and identifies the corresponding neighboring chunks $\mathbf{L}_\mathcal{C}[C]$, $\mathbf{R}_\mathcal{C}[C]$, $\mathbf{L}_\mathcal{M}[M]$ and $\mathbf{R}_\mathcal{M}[M]$ of $C$ and $M$.
-It applies frequency analysis on $\mathbf{L}_\mathcal{C}[C]$ and $\mathcal{L}_\mathcal{M}[M]$, as well as $\mathbf{R}_\mathcal{C}[C]$ and $\mathbf{R}_\mathcal{M}[M]$, according to their co-occurrence frequencies with $C$ and $M$.
-The rationale is the order of chunks is preserved due to locality, and the left and right neighbors of $M$ are likely to be the original chunks of the left and right neighbors of $C$.
-
-% % finds the corresponding sets $\mathbf{L_C}[C]$, $\mathbf{L_M}[M]$, $\mathbf{R_C}[C]$ and $\mathbf{R_M}[M]$ of neighboring chunks, and applies frequency analysis on $\mathbf{L_C}[C]$ and $\mathbf{L_M}[M]$, and similarly on $\mathbf{R_C}[C]$ and $\mathbf{R_M}[M]$.
-
-% % initializes  (e.g., by frequency analysis).
-The rationale is the frequency ranks of these top-frequent chunks are stable across backups, and hence the inferred pairs are correct with a high probability.
-
-% % More formally, the adversary knows the following information: $\mathbf{F}_\mathcal{C} = \{ (C, {\sf cnt}(M)) : C \in \mathcal{C} \wedge (M, C) \in \mathcal{E} \}$, which maps each ciphertext chunk to the frequency of its original chunk in $\mathbf{M}_t$, as well as $\mathbf{L}_\mathcal{C} = $ and $\mathbf{R}_\mathcal{C}$ which map each ciphertext chunk to its left and right neighboring chunks and their co-occurrence frequencies, respectively.
-The adversary also knows the similar associative arrays $\mathbf{F}_\mathcal{M}$, $\mathbf{L}_\mathcal{M}$ and $\mathbf{R}_\mathcal{M}$ about $\mathbf{M}_a$.
-
-% Our observation is that the underlying frequency analysis is {\em sensitive to frequency ranking}.
-Specifically, any disturbance (e.g., due to data updates or breaking ties) to the frequency rank can greatly degrade inference accuracy.
-Any incorrectly inferred chunk pairs will further compromise the following iterations of their neighbors, and hence affect inference rate.
-The original construction \cite{li17} builds on parameter-aware frequency analysis to strengthen accuracy, yet this primitive sacrifices inference coverage as discussed in \S\ref{sec:bucket-description}.
-
-% % Thus, the attack of \cite{li17}, while valuable for alerting the vulnerabilities of encrypted deduplication, is fairly severe in practice.
-
-% % {\bf The authors \cite{li17} employ parameters to indicate only a small number of top-frequent chunk pairs to be returned by frequency analysis}.
-However, as discussed in \S\ref{sec:bucket-description}, this trick incurs new problem: a lower bound limits the coverage of inferred chunks, while a higher bound .
-
-% We argue that there is an opportunity to increase attack severity by extensively exploiting the knowledge of order information.
-Our view is to build robust frequency ranking for being resistant to rank disturbance.
-In this way, we can properly increase frequency analysis parameter to infer more chunks, while mitigating the rank disturbance of the relatively non-top chunks to preserve accuracy.
-In the following two sections, we will elaborate our ranking approach (\S\ref{sec:distribution-ranking}), followed by how to build on it for inference attack (\S\ref{sec:distribution-description}).
-
-% % augment the parameter-aware frequency analysis with {\em robust ranking}.
-This allows to increase the frequency analysis parameter to potentially infer more chunks, while it can mitigate the rank disturbance of relatively non-top chunks to preserve accuracy.
-
-% % In \S\ref{sec:distribution_attack_description}, we present a simple but effective approach to establish {\em robust} frequency ranking, so as to ensure the inference accuracy of frequency analysis.
-We also integrate our approach with the locality-based attack for both severity and accuracy.
-
-% \subsection{Robust Ranking}
-% \label{sec:distribution-ranking}
-
-% \subsection{Attack Description}
-% \label{sec:distribution-description}
-% % Our view is to build {\em robust} frequency ranking for being resistant to disturbance.
-In the following, we first propose a robust ranking approach for frequency analysis.
-Then, we present the {\em distribution-based attack} that augments the prior locality-based attack \cite{li17} with robust frequency ranking for high severity.
-
-% We now proceed the {\em distribution-based attack}, which replaces the frequency-only ranking of the locality-based attack \cite{li17} by our robust ranking scheme (\S\ref{sec:distribution-ranking}).
-Algorithm \ref{alg:distribution-attack} shows the attack details.
-It takes input the frequency analysis parameter $u$, (expected) rank disturbance range $r$, distance threshold $t$, order leakage $\mathcal{L}_{\rm order}$ and auxiliary information $\mathbf{M}_{\rm aux}$ as input, and outputs the result set $\mathcal{R}$ of all inferred ciphertext-plaintext chunk pairs.
-
-% Like the locality-based attack (\S\ref{sec:locality-attack}), {\sc Distribution-Attack} extracts $\mathbf{F}_{\rm tar}, \mathbf{L}_{\rm tar}$ and $\mathbf{R}_{\rm tar}$, as well as $\mathbf{F}_{\rm aux}, \mathbf{L}_{\rm aux}$ and $\mathbf{R}_{\rm aux}$, from $\mathcal{L}_{\rm tar}$ and $\mathbf{M}_{\rm aux}$, respectively (Line~3-4), where $\mathbf{F}_{\rm tar}$ and $\mathbf{F}_{\rm aux}$ keeps the frequency of each chunk (recall $\mathcal{L}_{\rm order}$ inherently includes the leakage of frequency), and $\mathbf{L}_{\rm tar}, \mathbf{R}_{\rm tar}, \mathbf{L}_{\rm aux}$ and $\mathbf{R}_{\rm aux}$ store the co-occurrences of neighboring chunks (\S\ref{sec:locality-attack}).
-It calls the function {\sc Entropy} to extract additional data structures $\mathbf{E}_{\rm aux}$ and $\mathbf{E}_{\rm tar}$ (Line~5-6), which map each chunk to the entropies that are counted by the relative frequency distributions of its left and right neighbors.
-Then, it calls the function {\sc Rank} with a flag of "INIT" to initialize $\mathcal{G}$ with the ciphertext-plaintext chunk pairs returned by our robust ranking scheme (Line~7).
-It also copies the inferred chunk pairs to $\mathcal{R}$ (Line~8).
-
-% For the iteration of each chunk pair $(C, M)$ of $\mathcal{G}$, {\sc Distribution-Attack} also calls {\sc Rank} to build robust ranks on its neighboring chunks $\mathbf{L}_{\rm tar}[C]$ and $\mathbf{L}_{\rm aux}[M]$, as well as $\mathbf{R}_{\rm tar}[C]$ and $\mathbf{R}_{\rm aux}[M]$ (Line~11-12).
-One special mention is that we use a flag "ITERA" to identify the {\sc Rank} instances that are called in the iteration procedure.
-For each ciphertext chunk $C_i$ of rank $i$, we configure these instances to examine the possible plaintext chunks whose ranks start from $i$ (rather than $i-r$).
-Our rationale is chunks may have low frequencies after a number of iterations, and they are more likely to have identical relative frequency distribution with $C_i$.
-We start examination from rank $i$ to avoid relating the plaintext chunk that has a large rank difference from $i$.
-{\sc Distribution-Attack} includes the newly inferred ciphertext-plaintext chunk pairs (Line~13-15) into both $\mathcal{G}$ and $\mathcal{R}$.
-It iterates until $\mathcal{G}$ is empty, and finally returns $\mathcal{R}$.
-
-% % we can configure that the examination in these instances starts with the plaintext chunks whose ranks are identical with the target ciphertext chunk.
-For example, for the  we start to examine the relative frequency distribution of the $i$-th frequent plaintext chunk.
-
-% % To capture relative frequency distribution, we Note that both arrays can be easily computed from the original data structures $\mathbf{L}_{\rm aux}, \mathbf{R}_{\rm aux}, \mathbf{L}_{\rm tar}$ and $\mathbf{R}_{\rm tar}$ (\S\ref{sec:locality-attack}) of the locality-based attack.
-
-% % The distribution-based attack initializes $\mathcal{G}$ by establishing robust ranking on all chunks.
-Specifically, the adversary finds $u$ and $u+r$ most frequent ciphertext and plaintext chunks, respectively, and relates each $i$-th frequent ciphertext chunk $C_i$ with a possible plaintext chunk that ranks from $i-r$ to $i+r$ (see above).
-It returns at most $u$ ciphertext-plaintext chunk pairs and adds them into $\mathcal{G}$.
-
-% % The distribution-based attack also applies robust ranking on the neighbors of each iterating pair $(C, M)$.
-
-% % For the iteration of each chunk pair $(C, M)$ of $\mathcal{G}$, the adversary also builds robust ranks on its neighboring sets $\mathbf{L}_\mathcal{C}[C]$ and $\mathbf{L}_\mathcal{M}[M]$, as well as $\mathbf{R}_\mathcal{C}[C]$ and $\mathbf{R}_\mathcal{M}[M]$.
-To relate the $i$-th frequent ciphertext chunk $C_i$, it only examines the possible plaintext chunks that are ranked from $i$ to $i+r$ (rather than $i-r$ to $i+r$).
-Our rationale is the ranked chunks may have low frequency count after a number of iterations, and they are likely to have identical relative frequency distribution with $C_i$.
-We start examination from rank $i$ to avoid relating the plaintext chunk that has a large rank difference from $i$.
-
-% % \paragraph{Algorithm details:}
-% % The distribution-based attack builds on prior locality-based attack \cite{li17} (see \S\ref{sec:locality}), and uses the robust frequency ranking approach to infer ciphertext-plaintext chunk pairs.
-We modify the parameters of the locality-based attack \cite{li17}.
-First, we remove the parameter (i.e., $w$ in \cite{li17}) of size of $\mathcal{G}$, as we find the memory can hold all fingerprints of our experimental datasets (see \S\ref{sec:methodology}).
-Second, we replace another parameter (i.e., $v$ in \cite{li17}) that bounds the number of chunk pairs returned by frequency analysis in each iteration, by $r$ to indicate the possible plaintext chunks to be examined.
-
-% % Algorithm~\ref{alg:distribution} presents the pseudo-code of the distribution-based attack, where we assume the adversary can construct the associative arrays $\mathbf{F_C}, \mathbf{L_C}$, and $\mathbf{R_C}$, as well as $\mathbf{F_M}, \mathbf{L_M}$, and $\mathbf{R_M}$ by calling $\textsc{Count}(\mathbf{C})$ and $\textsc{Count}(\mathbf{C})$, respectively.
-We omit the algorithm details about $\textsc{Count}$, and readers may refer the function of the same name in ref.
-\cite{li17}.
-% % The algorithm \textsc{Distribution-attack} takes $\mathbf{C}, \mathbf{M}, u$ and $r$ as input, and outputs $\mathcal{R}$ of inferred ciphertext-plaintext chunk pairs.
-After initializing the associative arrays of $\mathbf{F_C}, \mathbf{L_C}$ and $\mathbf{R_C}$, it calls the function \textsc{Entropy} to obtain $\mathbf{E_C}$ which maps each ciphertext chunk to its entropies derived from the relative frequency distributions of its left and right neighbors (Line~4).
-Similarly, it obtains $\mathbf{E_M}$ for the plaintext chunks (Line~6).
-Then, it calls the \textsc{Robust-ranking} function to initialize $\mathcal{G}$ and $\mathcal{R}$ (Line~7-8).
-% % In each iteration, the algorithm picks out a pair $(C, M)$ from $\mathcal{G}$ (Line~10), and calls the function $\textsc{Robust-ranking}$ to infer ciphertext-plaintext chunk pairs $\mathcal{R}_r$ and $\mathcal{R}_l$ from the left and right neighbors of $C$ and $M$ (Line~11-12).
-It further adds the newly inferred pairs of $\mathcal{R}_l$ and $\mathcal{R}_r$ into $\mathcal{G}$ and $\mathcal{R}$ (Line~13-15).
-The iteration does not end until $\mathcal{G}$ is empty.
-The algorithm finally returns $\mathcal{R}$ (Line~16).
-
-% The function \textsc{Entropy} builds the entropy array $\mathbf{E}_{\rm X}$ based on $\mathbf{L}_{\rm X}$ and $\mathbf{R}_{\rm X}$, where the X can be "tar" or "aux".
-For each chunk $X$, it counts the total co-occurrences $\Sigma_l$ of all left neighbors of $X$ (Line~20), and further the entropy $\mathbf{E}_{\rm X}[X].l$ of the relative frequency distribution of left neighbors (Line~21-22).
-Similarly, it counts the entropy $\mathbf{E}_{\rm X}[X].r$ of the relative frequency distribution of right neighbors (Line~23-25).
-
-% The function \textsc{Rank} performs robust frequency ranking based on $\mathbf{X}_{\rm tar}$ and $\mathbf{X}_{\rm aux}$, where $\mathbf{X}_{\rm tar}$ and $\mathbf{X}_{\rm aux}$ can be $\mathbf{F}_{\rm tar}$ and $\mathbf{F}_{\rm aux}$, $\mathbf{L}_{\rm tar}[*]$ and $\mathbf{L}_{\rm aux}[*]$, or $\mathbf{R}_{\rm tar}[*]$ and $\mathbf{R}_{\rm aux}[*]$.
-It first sorts $\mathbf{X}_{\rm tar}$ and $\mathbf{X}_{\rm aux}$ by frequencies, respectively (Line~29-30).
-For each $i$-th frequent ciphertext chunk $C_i$, it identifies the range of plaintext chunks to be examined.
-Specifically, if the flag $f$ is INIT, it sets the starting rank $m$ as the maximum number of $1$ and $i-r$, since $i$ may be smaller than $r$ (Line~34-35); if $f$ is ITERA, it sets $m$ as $i$ (Line~36-37).
-Then, it finds the plaintext chunk $M$ in the examined range, such that ${\sf D}(C_i, M)$ is minimum (Line~38-42).
-The function adds $(C_i, M)$ into the result set $\mathcal{R}_x$ only when the distance ${\sf D}(C_i, M)$ is also smaller than the threshold $t$ (Line~43-44).
-
-% % Note that \textsc{Robust-ranking} also returns $u$ highly frequent chunk pairs like locality-based attack \cite{li17}.
-Similarly, it sorts  For each top-frequent ciphertext chunk $C$ with a rank of $i$ ($1 \leq i \leq u$), it examines the cor:responding plaintext chunks that rank range from $i-r$ to $i+r$.
-Since $i-r$ is possibly below the first rank index, the algorithm derives the minimum rank $start$ of $1$ and $i-r$ and
-
-% \begin{algorithm}[t]
-% \caption{Distribution-based Attack}
-% \label{alg:distribution-attack}
-% \small
-%   \SetKwFunction{Main}{\sc Distribution-Attack}
-%   \SetKwProg{Pro}{procedure}{:}{}
-% 	\Pro{\Main{$u, r, t, \mathcal{L}_{\rm order}, \mathbf{M}_{\rm aux}$}}{
-% 		initialize $\mathcal{R} \longleftarrow \emptyset$\;
-
-% 		extract $\mathbf{F}_{\rm tar}, \mathbf{L}_{\rm tar}$ and $\mathbf{R}_{\rm tar}$ from $\mathcal{L}_{\rm order}$\;
-% 		% \tcc{$\mathbf{F}_{\rm tar}[C]$ maps $C$ to frequency of its original chunk in $\mathbf{M}_{\rm tar}$}
-% 		% \tcc{$\mathbf{L}_{\rm tar}[C]$ maps ciphertext chunk $C$ to its left neighbors as well as corresponding co-occurrences with $C$}
-% 		% \tcc{$\mathbf{R}_{\rm tar}[C]$ maps ciphertext chunk $C$ to its right neighbors as well as corresponding co-occurrences with $C$}
-
-% 		extract $\mathbf{F}_{\rm aux}, \mathbf{L}_{\rm aux}$ and $\mathbf{R}_{\rm aux}$ from $\mathbf{M}_{\rm aux}$\;
-% 		% \tcc{$\mathbf{F}_{\rm aux}[M]$ stores frequency of plaintext chunk $M$ in $\mathbf{M}_{\rm aux}$}
-% 		% \tcc{$\mathbf{L}_{\rm aux}[M]$ maps plaintext chunk $M$ to its left neighbors and corresponding co-occurrences with $M$}
-% 		% \tcc{$\mathbf{R}_{\rm aux}[M]$ maps plaintext chunk $M$ to its right neighbors and corresponding co-occurrences with $M$}
-
-% 		$\mathbf{E}_{\rm tar} \longleftarrow \textsc{Entropy}(\mathbf{L}_{\rm tar}, \mathbf{R}_{\rm tar})$\;
-% 		$\mathbf{E}_{\rm aux} \longleftarrow \textsc{Entropy}(\mathbf{L}_{\rm aux}, \mathbf{R}_{\rm aux})$\;
-
-% 		$\mathcal{G} \longleftarrow \textsc{Rank}(u, r, t, \mathbf{F}_{\rm tar}, \mathbf{E}_{\rm tar}, \mathbf{F}_{\rm aux}, \mathbf{E}_{\rm aux}, {\rm INIT})$\;
-
-% 		$\mathcal{R} \longleftarrow \mathcal{G}$\;
-% 		\While{$\mathcal{G}$ is non-empty}{
-% 			pick $(C, M)$ out of $\mathcal{G}$\;
-% 			$\mathcal{R}_l \longleftarrow \textsc{Rank}(u, r, t, \mathbf{L}_{\rm tar}[C], \mathbf{E}_{\rm tar}, \mathbf{L}_{\rm aux}[M], \mathbf{E}_{\rm aux}, {\rm ITERA})$\;
-% 			$\mathcal{R}_r \longleftarrow \textsc{Rank}(u, r, t, \mathbf{R}_{\rm tar}[C], \mathbf{E}_{\rm tar}, \mathbf{R}_{\rm aux}[M], \mathbf{E}_{\rm aux}, {\rm ITERA})$\;
-% 			\For{each $(C, M)$ in $\mathcal{R}_l \cup \mathcal{R}_r$}{
-% 				\If{$(C, *)$ is not in $\mathcal{R}$}{
-% 					Add $(C, M)$ into $\mathcal{G}$ and $\mathcal{R}$\;
-% 				}
-% 			}
-% 		}
-% 		\KwRet{$\mathcal{R}$}\;
-%   }
-
-%   \SetKwFunction{Entropy}{\sc Entropy}
-%   \SetKwProg{Fn}{function}{:}{}
-% 	\Fn{\Entropy{$\mathbf{L}_{\rm X}, \mathbf{R}_{\rm X}$}}{
-% 		\For{each chunk $X$ in $\mathbf{L}_{\rm X}$ and $\mathbf{R}_{\rm X}$}{
-% 			initialize $\mathbf{E}_{\rm X}[X].l,  \mathbf{E}_{\rm X}[X].r \longleftarrow 0$\;
-% 			$\Sigma_l \longleftarrow$ sum of co-occurrences of left neighbors in $\mathbf{L}_{\rm X}[X]$\;
-% 			\For{each left neighbor $X_l$ in $\mathbf{L}_{\rm X}[X]$}{
-% 				$\mathbf{E}_{\rm X}[X].l \longleftarrow \mathbf{E}_{\rm X}[X].l - {\sf log}_2\frac{\mathbf{L}_{\rm X}[X][X_l]}{\Sigma_l}$\;
-% 			}
-% 			$\Sigma_r \longleftarrow$ sum of co-occurrences of right neighbors in $\mathbf{R}_{\rm X}[X]$\;
-% 			\For{each right neighbor $X_r$ in $\mathbf{R}_{\rm X}[X]$}{
-% 				$\mathbf{E}_{\rm X}[X].r \longleftarrow \mathbf{E}_{\rm X}[X].r - {\sf log}_2\frac{\mathbf{R}_{\rm X}[X][X_r]}{\Sigma_r}$\;
-% 			}
-% 		}
-% 		\KwRet{$\mathbf{E}_{\rm X}$}\;
-% 	}
-
-% 	\SetKwFunction{Ranking}{\sc Rank}
-%   \SetKwProg{Fn}{function}{:}{}
-% 	\Fn{\Ranking{$u, r, t, \mathbf{X}_{\rm tar}, \mathbf{E}_{\rm tar}, \mathbf{X}_{\rm aux}, \mathbf{E}_{\rm aux}, f$}}{
-% 		initialize $\mathcal{R}_x \longleftarrow \emptyset$\;
-% 		sort ciphertext chunks in $\mathbf{X}_{\rm tar}$ by frequencies\;
-% 		sort plaintext chunks in $\mathbf{X}_{\rm aux}$ by frequencies\;
-% 		\For{$i \longleftarrow 1$ to $u$}{
-% 			$C_i \longleftarrow$ $i$-th frequent ciphertext chunk\;
-% 			initialize $d \longleftarrow$ MAX\_DISTANCE\;
-% 			\uIf{$f$ is {\rm INIT}}{
-% 				$m \longleftarrow$ maximum rank of $1$ and $i-r$\;
-% 			}
-% 			\uElseIf{$f$ is {\rm ITERA}}{
-% 				$m \longleftarrow$ $i$\;
-% 			}
-% 			\For{$j \longleftarrow m$ to $i+r$}{ 
-% 				$M_j \longleftarrow$ $j$-th frequent plaintext chunk\;
-% 				\If{${\sf D}(C_i, M_j) < d$}{
-% 					$M \longleftarrow M_j$\;
-% 					$d \longleftarrow {\sf D}(C_i, M_j)$\;
-% 				}
-% 			}
-% 			\If{${\sf D}(C_i, M) < t$}{
-% 				add $(C_i, M)$ into $\mathcal{R}_x$\;
-% 			}
-% 		}
-% 		\KwRet{$\mathcal{R}_x$}\;
-% 	}
-
-% \end{algorithm}
-
-\chapter{Clustering-based Attack}
-\label{sec:clustering-attack}
-
-% The distribution-based attack is based on the assumption that the ordering of ciphertexts in $\mathbf{C}$ reflects that of corresponding plaintexts in $\mathbf{M}$ (recall $\mathbf{M}$ is the original file of $\mathbf{C}$).
-
-In this section, we relax the adversarial knowledge in the distribution-based attack, and propose the {\em clustering-based attack}, which does not need the fine-grained ordering of plaintexts.
-Instead, it exploits the {\em similarity} property to infer original data from similar {\em clusters} (i.e., some large data units aggregated by chunks), without relying on the ordering of chunks in each cluster.
-We first introduce similarity, and then show how to adapt this property into inference attack.
-
-% In the following, we introduce similarity, followed by how we adapt this property to inference attack.
-
-\section{Background: Similarity}
-\label{sec:similarity}
-Similarity \cite{bhagwat09} states that backup files from the same source are likely to be {\em similar} and share a large fraction of identical chunks.
-The similarity between backup files can be quantified by {\em Broder's theorem} \cite{broder97}.
-Specifically, if we treat each file as a set $S$ of chunks (i.e., ignore their orders), Broder's theorem states that if the probability that two sets of chunks share the same minimum chunk hash is high, then both sets are likely to share a large fraction of identical chunks and vice versa:
-\begin{eqnarray}
-	\Pr[\min\{{\rm H}(S)\} = \min\{{\rm H}(S')\} ] = \frac{|S \cap S'|}{|S \cup S'|}, \nonumber
-	\label{eq:broder}
-\end{eqnarray}
-where ${\rm H}(\cdot)$ is a hash function that is chosen uniformly at random from a min-wise independent family of permutations, and $\min\{{\rm H}(S)\}$ returns the minimum chunk hash of $S$. 
-% For easy elaboration, we use {\em MinHash} to denote the minimum element hash of some set.
-
-Prior works that target different aspects (e.g., performance \cite{qin17,xia11,bhagwat09}, and security \cite{li17}) of deduplication  have applied similarity to {\em preserve storage efficiency}.
-Specifically, they operate deduplication just on the files that share the same minimum chunk hash (i.e., similar); since similar files can have a large number of identical chunks due to Broder's theorem, such {\em near-exact} deduplication only leads to a slight degradation of storage efficiency.
-Different from  prior approaches \cite{qin17,xia11,bhagwat09,li17}, we apply similarity to increase the severity of frequency analysis.
-
-% Thus, prior works   apply chunk-based deduplication across similar segments, so as to improve the effectiveness of {\em near-exact} deduplication.
-
-% the probability that two sets (files)     
-% if two sets share a large fraction of common elements (i.e., they are highly similar), then the probability that both sets share the same minimum hash element is also high.
-% likely to be highly similar and share a large fraction of identical chunks. The similarity of  
-% The similarity of files can be  Specifically, we treat each file as a set of chunks, and do not care the order of each chunk.   
-% that are possibly under different orders yet. Previous approach (e.g., \cite{xia11,bhagwat09}) exploits this property to minimize the memory usage of deduplication.
-
-% the similarity-based approach that is commonly used to improve deduplication performance \cite{qin17,xia11,bhagwat09}. Then, we show how to adapt the similarity property to inference attack.
-
-% infer ciphertext-plaintext pairs that are in similar clusters, without the knowledge of the order information of each ciphertext or plaintext in the clusters. 
-% consider to relax such ordering leakage. Specifically, we 90  
-% We assume that the adversary learns the (generic) order information in a {\em coarse-grained unit}, in which a number of chunks appear together as a set; while the adversary cannot identify the accurate order of any chunk in each set.
-
-% has some limitations.
-First, the attack assumes that the adversary has full knowledge of neighboring chunks.
-Although it is plausible for some deduplicaton systems \cite{xia11,lillibridge09,zhu08}, we can address the assumption by simply swapping the orders of chunks (see \S\ref{sec:countermeasure}).
-Second, the attack depends on the prevalence of locality in workloads, and it may perform poor in the low-locality workloads.
-
-% Informed by the limitations (see \S\ref{sec:distribution-discussion}), we consider an attack against the {\em low-locality} workloads, where there does not exist a large stretch of repeated data across backups.
-We argue that such a workload is reasonable in practice.
-For example, if multiple users upload their data simultaneously, the chunks received by the server will be disordered and lose locality.
-
-% Thus, there is no locality among the chunks that arrives in a window of time. 
-% continuous data protection (CDP) only stores the chunks where information has changed, it destroys the locality of chunks since changes often appear in unpredictable regions.
-Thus, for low-locality workloads, the information perceived by the adversary no longer reflect the actual logical orders of chunks.
-
-% To model the scenario, we consider {\em time window}, which is the basic unit of period whose actual order can be perceived by the adversary.
-Specifically, we assume that the network bandwidth is steady, and the server can receive a fixed amount (e.g., 4MB) of data during each time window.
-The adversary cannot distinguish the actual logical orders of chunks that are received within the same time window, while it can learn if two chunks are received in an identical time window.
-
-% Formally, we use ${\sf tw}(M)$ to denote the orders of the time windows during which the chunk $M$ is received by the server, if we upload all chunks in order.
-
-% Suppose that all chunks are uploaded under their logical orders.
-We use ${\sf tw}(M)$ to denote the orders of the time windows during which $M$ is received by the server (note that a chunk may appear multiple times and hence in several time windows).
-This is the only information about ordering that can be perceived by the adversary.
-Thus, we can define the leakage:
-
-% \begin{itemize}[leftmargin=2em]
-% 	\item  $\widetilde{\mathcal{L}}_{\rm order} = \{(C, {\sf tw}(M)): M \in \mathbf{M}_{\rm t} \textrm{ and } C = {\sf E}_{K_M}(M)\}$, in which each pair leaks the time window of the original chunk.
-Note that $\widetilde{\mathcal{L}}_{\rm order}$ no longer implies $\mathcal{L}_{\rm freq}$, since a chunk possibly appears multiple times in the same time window.
-% \end{itemize}
-
-% In this section, we propose a new inference attack, the {\em clustering-based attack}, which can increase the severity of frequency analysis with only the coarse-grained order information like time window, i.e., $\mathcal{L} = (\mathcal{L}_{\rm freq}, \widetilde{\mathcal{L}}_{\rm order})$.
-
-% does not need the accurate knowledge about neighboring relationships.
-
-% In this section, we consider the leakage of {\em coarse-grained order information}.  
-%    we propose a new inference attack, the {\em clustering-based attack}, which does not need the accurate knowledge about neighboring relationships.
-Instead, we model $\mathbf{M}_{\rm tar}$ as a collection of {\em chunk regions}, and each region includes a set of continues chunks.
-The adversary only knows the logical orders of regions, while the orders of chunks in each region are randomly scrambled.
-% Instead, it builds on the  in which the adversary only needs to know the logical order of coarse-grained set of continues chunks, while the orders of chunks in each set are scrambled.
-More formally, we define the coarse-grained order leakage $\widetilde{\mathcal{L}}_{\rm order}$, ...
-% an obfuscated version of order leakage $\widetilde{\mathcal{L}}_{\rm order}$, based on which the adversary can only know: (i) and (ii) the orders of chunks in each region have been randomized.
-
-% does not need the accurate knowledge about neighboring relationships.
-Instead, we model $\mathbf{M}_{\rm tar}$ as a collection of {\em chunk regions}, and each region includes a set of continues chunks.
-The adversary only knows the logical orders of regions, while the orders of chunks in each region are randomly scrambled.
-
-% A challenge of the attack is how to break ties.
-
-% \subsection{Similarity-based Approaches}
-% For example, in a NAS-based backup storage system, the identical chunks are possibly arrived in random order from different clients.
-
-% coming from different clients are possibly arrived in random order.  
-% Since two backups from the same data source are expected to be highly similar and share a large number of identical chunks
-
-% Previous similarity-based approaches \cite{li17,qin17,xia11,bhagwat09} address deduplication performance of such workloads via the Broder's theorem.   
-% Previous similarity-based approaches \cite{li17,qin17,xia11,bhagwat09} address the performance bottleneck of deduplication storage systems via Broder's theorem.     
-% improves deduplication performance based on :
-
-% Previous similarity-based approaches
-
-% In other words, there does not exist
-
-% in which the chunks are possibly associated with random orders. The stretch of the data, although having the same content, their chunks are associated with random orders.
-
-% Informed by the limitations (see \S\ref{sec:distribution-discussion}), we consider an attack against the {\em low-locality} workloads, where there does not exist a large stretch of repeated data across backups.
-We argue that such a workload is reasonable in practice.
-For example, if multiple users upload their data simultaneously, the chunks received by the server will be disordered and lose locality.
-
-\section{Description of Clustering-based Attack}
-\label{sec:clustering-attack-description}
-
-\begin{figure}
-	\includegraphics[width=.48\textwidth]{pic/clustering-attack-new.pdf}
-    % \caption{Workflow of clustering-based attack: MinHash denotes the minimum chunk hash of plaintext segment, $e(\mathcal{C}_\mathbf{C})$ and $e(\mathcal{C}_\mathbf{A})$ denote the entropies based on the frequency distributions in $\mathcal{C}_\mathbf{C}$ and $\mathcal{C}_\mathbf{A}$, respectively, and  $\#\mathcal{C}_\mathbf{C}$ and $\#\mathcal{C}_\mathbf{A}$ denote the total number of logical ciphertexts and plaintexts in $\mathcal{C}_\mathbf{C}$ and $\mathcal{C}_\mathbf{A}$, respectively.}
-    \caption{Workflow of clustering-based attack: MinHash denotes the minimum chunk hash of a plaintext segment.}
-	\label{fig:clustering-attack}
-\end{figure}
-
-We now present the clustering-based attack (Figure~\ref{fig:clustering-attack}) that builds on similarity to infer original data against encrypted deduplication.
-
-To exploit similarity, we first introduce {\em segmentation} on a stream of chunks.
-Specifically, we partition $\mathbf{C}$ into a set of coarse-grained data units, called {\em ciphertext segments}.
-Each ciphertext segment, denoted by $S_\mathbf{C}$, comprises multiple adjacent ciphertexts in $\mathbf{C}$.
-In this work, we implement the {\em fixed-size} segmentation scheme to ensure that all ciphertext segments are of the same size (e.g., 4MB by default).
-For compatibility, the same fixed-size segmentation scheme also applies to the auxiliary information $\mathbf{A}$, so as to generate multiple {\em plaintext segments}, each of which is denoted by $S_\mathbf{A}$.
-Note that some variable-size segmentation schemes \cite{lillibridge09, qin17}  identify segment boundaries after the chunks whose contents match a specific pattern and thus address the boundary shift problem faced by the fixed-size segmentation scheme.
-However, we cannot use these variable-size segmentation schemes \cite{lillibridge09, qin17} in the attack.
-The reason is that the original contents of chunks in ciphertext segments are protected by symmetric encryption, and we cannot ensure that the boundaries for both ciphertext and plaintext segments match the same pattern.
-This leads to an incompatibility between ciphertext and plaintext segments, and degrades the amount of segment-level data inferred by the clustering-based attack (see the late part of this section).
-
-% It violates compability, since we cannot
-
-% It impossible to ensuring the boundaries for  plaintext and ciphertext segments match the same pattern.
-
-% Even we apply the variable-size segmentation scheme directly  on the contents of ciphertexts,
-
-% we cannot derive the same pattern for both
-
-% Note that the order and size of each ciphertext in $\mathbf{C}$ are necessary for operating the fixed-size segmentation, while we do {\em not} need them to reflect those of corresponding plaintext;
-
-% , so as to be robust against boundary shift of fixed-size segment.  
-% we cannot apply
-% that match specific content patterns,   
-% which address the boundary shift of fixed-size segment, yet requiring to identify segment boundaries that match specific content patterns so as to remain robust against content shifts  
-% operate more  requiring the original content patterns of ciphertexts in $\mathbf{C}$.
-
-We propose to infer ciphertext-plaintext pairs through similar segments.
-Let $S_\mathbf{M}$ be the original plaintext segment of a ciphertext segment $S_\mathbf{C}$ (i.e., each plaintext in $S_\mathbf{M}$ corresponds to some ciphertext in $S_\mathbf{C}$ and vice versa).
-According to Broder's theorem, if $S_\mathbf{M}$ shares the same minimum chunk hash, say $h$, with some plaintext segment $S_\mathbf{A}$, then $S_\mathbf{M}$  and $S_\mathbf{A}$ tend to have a large fraction of identical plaintexts.
-This implies that the ciphertexts in $S_\mathbf{C}$ are likely to be mapped from the plaintexts in  $S_\mathbf{A}$.
-In other words, we first classify all plaintext segments of $\mathbf{A}$ by their minimum chunk hashes, and obtain multiple {\em plaintext clusters}.
-Each plaintext cluster, denoted by $\mathcal{C}_\mathbf{A} = \{ S_\mathbf{A} \}$, corresponds to a unique minimum chunk hash shared by its included segments.
-We also
-group the ciphertext segments, whose original plaintext segments have the same minimum chunk hash $h$ (i.e., similar), into an identical {\em ciphertext cluster}, denoted by $\mathcal{C}_\mathbf{C} = \{ S_\mathbf{C} \}$.
-Then, we infer the original data of $\mathcal{C}_\mathbf{C}$ from some $\mathcal{C}_\mathbf{A}$ that corresponds to  $h$.
-
-% corresponding segment that is mapped to $S_\mathbf{C}$ (i.e., each plaintext in $S_\mathbf{M}$ corresponds to some ciphertext in $S_\mathbf{C}$, and visa versa). 
-% Given a ciphertext segment $S_\mathbf{C}$, let
-
-% if  in other words,  Thus, we propose to launch frequency analysis through similar segments. 
-% Specifically,
-
-% say $\mathcal{C}_\mathbf{C}$.  
-% $h$ 
-% We denote a plaintext cluster by , which includes multiple  plaintext segments that have the same minimum chunk hash.    
-% Each plaintext cluster, denoted by  is a set of  We propose to also collect the ciphertext segments (as a {\em ciphertext cluster} denoted by $\mathcal{C}_\mathbf{C}$) whose original plaintext segments share an identical minimum chunk hash $h$, and then infer their original contents from
-% some $\mathcal{C}_\mathbf{A}$ that corresponds to $h$ (i.e., the minimum chunk hash of each plaintext segment in $\mathcal{C}_\mathbf{A}$ equals $h$).
-
-% and $h$ be the minimum chunk hash computed from $S_\mathbf{M}$.
-
-% Our insight is if $h$ equals the minimum chunk hash of some $S_\mathbf{A}$, then the ciphertexts in $S_\mathbf{C}$  The rationale is the original segment of $S_\mathbf{C}$ has a large fraction of identical plaintexts with $S_\mathbf{A}$ due to Broder's theorem.
-
-% In other words,
-
-% This is expected to reduce the disturbances to frequency analysis.
-
-% $\{S_\mathbf{C}\}$ that have an identical {\em original} minimum element hash $h$,
-
-% composed of the segments that have the same minimum element hash.  
-% However, the original data of each ciphertext segment $S_\mathbf{C}$ is protected by symmetric encryption, and it is impossible to identify the corresponding minimum chunk hash $h$ for grouping ($h$ is derived from the original plaintext segment of $S_\mathbf{C}$).
-The challenge is how to group similar ciphertext segments {\em without} knowing the minimum chunk hash $h$ of each $S_\mathbf{C}$.
-
-% the original content of each ciphertext segment $S_\mathbf{C}$ is protected by symmetric encryption; this makes it impossible to identify the corresponding  $h$ for grouping (recall $h$ is derived from the original plaintext segment of $S_\mathbf{C}$).
-In other words, there exists a challenge of
-
-We propose a {\em clustering} scheme to group similar ciphertext segments.
-A na\"{i}ve approach is to classify segments by their minimum chunk hashes, but it does not work on ciphertext segments, whose original contents are protected by symmetric encryption.
-We address the classification issue based on Broder's theorem.
-% operate classification by the  of each segment , but it .   
-Our insight is that if two ciphertext segments have a large fraction of identical ciphertexts, then  they correspond to the same minimum chunk hash with a high probability.
-The reason is that deterministic encryption preserves the cardinalities of union and intersection of plaintext segments, based on which we can use Broder's theorem to learn the equivalence of their minimum chunk hashes.
-% the fraction of identical plaintexts, based on  Thus, we  apply a clustering algorithm, and aggregate similar ciphertext segments into the same cluster.
-
-In this work, we define the {\em clustering distance} $d(S_\mathbf{C}, S_\mathbf{C}')$ of any two ciphertext segments $S_\mathbf{C}$ and $S_\mathbf{C}'$ by one minus the fraction of their identical ciphertexts:
-\begin{eqnarray}
-d(S_\mathbf{C}, S_\mathbf{C}') = 1 - \frac{|S_\mathbf{C} \cap S_\mathbf{C}'|}{|S_\mathbf{C} \cup S_\mathbf{C}'|}. \nonumber
-\end{eqnarray}
-Note that identical ciphertexts may repeat in $S_\mathbf{C}$ or $S_\mathbf{C}'$, and $|S_\mathbf{C} \cap S_\mathbf{C}'|$ and $|S_\mathbf{C} \cup S_\mathbf{C}'|$ return the number of {\em unique} ciphertexts in their  intersection and union, respectively.
-Clearly,  the smaller $d(S_\mathbf{C}, S_\mathbf{C}')$ is, the more likely are $S_\mathbf{C}$ and $S_\mathbf{C}'$ to correspond to the same minimum chunk hash.
-Then, we adopt the {\em agglomerative hierarchical clustering (AHC)} \cite{johnson67} to aggregate similar ciphertext segments based on their distance information.
-Specifically, we start with eash ciphertext segment in its own singleton cluster, and iteratively combine the two closest clusters based on the maximum distance of their ciphertext segments.
-We configure a parameter $k$,
-% to indicate the upper bound distance in combination, 
-and stop the iterated combination when the maximum distance of ciphertext segments in the two cloest
-clusters is greater than $k$.
-
-% finally stop combination when       
-% Specifically, the clustering scheme is configured by a minimum intercluster distance $d$.   
-% We combine nearby segments into clusters based on the distance metric, and stop the combination when 
-% the maximum distance between any segment in two clusters is less than $d$.
-% the first cluster and any single data point in the second cluster.
-% Based on the distance definition, 
-% we implement the clustering algorithm via {\em ALGLIB} \cite{alglib}, which is a programming library for extensive data analysis.
-While ALGLIB supports multiple clustering algorithms, we choose the , because we  only have the distance information of  segments (rather than their coordinates).
-% Specifically, we configure a desired minimum intercluster distance $d$ (e.g., 0.8 by default) via ${\tt clusterizerseparatedbydist()}$, and generate multiple ciphertext clusters via ${\tt clusterizerrunahc()}$.
-
-For each aggregated ciphertext cluster $\mathcal{C}_\mathbf{C}$, we relate it to some plaintext cluster $\mathcal{C}_\mathbf{A}$ with frequency analysis, while taking frequency distribution into account.
-This is based on the observation that identical ciphertexts (resp.
-plaintexts) may  repeat in the same or different ciphertext (resp.
-plaintext) segments and identical ciphertext (resp.
-plaintext) segments may also repeat in the same ciphertext (resp.
-plaintext) cluster.
-We propose to examine the frequency distribution of the logical ciphertexts or plaintexts in each cluster, and perceive that the frequency distributions for similar clusters (i.e., correspond to the same minimum chunk hash) are also likely to be similar.
-% {\bf Our rationale is changes to backups only apply on limited regions, and do not modify the spatiality of majority chunks.}
-
-% We proceed the frequency analysis scheme as follows.
-First, we  sort available ciphertext and plaintext clusters by the total number of logical  ciphertexts and plaintexts they include, respectively.
-Then, we count the entropy of each cluster based on the frequency distribution of its logical ciphertexts or plaintexts.
-Like the distribution-based attack (see Section~\ref{sec:distribution-attack-description}), we configure the frequency analysis scheme with the parameters $(u, r, t)$, and infer the ciphertext cluster $\mathcal{C}_\mathbf{C}$ is similar to a plaintext cluster $\mathcal{C}_\mathbf{A}$, if they satisfy the following requirements:
-We proceed the frequency analysis scheme as follows.
-First, we  sort available ciphertext and plaintext clusters by the total number of logical  ciphertexts and plaintexts they include, respectively.
-Then, we count an associative array $\mathbf{F}$ that stores the frequency of each unique ciphertext or plaintext in  corresponding cluster.
-Based on $\mathbf{F}$, we compute the probability that a  ciphertext $C$ exists in a ciphertext cluster $\mathcal{C}_\mathbf{C}$ and further the
-entropy of $\mathcal{C}_\mathbf{C}$:      
-% entropy of each ciphertext cluster $\mathcal{C}_\mathbf{C}$:    
-\begin{eqnarray*}
-    \Pr[C \in \mathcal{C}_\mathbf{C}] = \frac{\mathbf{F}[\mathcal{C}_\mathbf{C}][C]}{\sum_{C' \in \mathcal{C}_\mathbf{C}} \mathbf{F}[\mathcal{C}_\mathbf{C}][C']}, \\
-    e(\mathcal{C}_\mathbf{C}) = \sum_{C \in \mathcal{C}_\mathbf{C}} \log_2 \frac{1}{\Pr[C \in \mathcal{C}_\mathbf{C}]},  
-    % e(\mathcal{C}_\mathbf{M}) = \sum_{M \in \mathbf{F}[\mathcal{C}_\mathbf{M}]} \log_2 \frac{\mathbf{F}[\mathcal{C}_\mathbf{M}][M]}{a} 
-\end{eqnarray*}
-where   
-$\mathbf{F}[\mathcal{C}_\mathbf{C}][C]$  stores the frequency of $C$ in $\mathcal{C}_\mathbf{C}$.
-Similarly, we  compute the entropy $e(\mathcal{C}_\mathbf{A})$ for the plaintext cluster $\mathcal{C}_\mathbf{A}$.
-Like the distribution-based attack (see Section~\ref{sec:distribution-attack-description}), we configure the frequency analysis scheme with the parameters $(u, r, t)$, and infer that the ciphertext cluster $\mathcal{C}_\mathbf{C}$ is similar to a plaintext cluster $\mathcal{C}_\mathbf{A}$, if they satisfy the following requirements:
-% the entropy of each cluster based on the frequency distribution of its logical ciphertexts or plaintexts.
-Like the distribution-based attack (see Section~\ref{sec:distribution-attack-description}), we configure the frequency analysis scheme with the parameters $(u, r, t)$, and infer the ciphertext cluster $\mathcal{C}_\mathbf{C}$ is similar to a plaintext cluster $\mathcal{C}_\mathbf{A}$, if they satisfy the following requirements:
-\begin{itemize}[leftmargin=*]
-    \item  The rank of $\mathcal{C}_\mathbf{C}$ is not larger than $u$.
-    \item  The rank difference of $\mathcal{C}_\mathbf{C}$ and $\mathcal{C}_\mathbf{A}$ is not larger than $r$.  
-    \item  The difference of $e(\mathcal{C}_\mathbf{C})$ and $e(\mathcal{C}_\mathbf{A})$ is the smallest and also not larger than $t$.
-\end{itemize}
-
-% Thus, the ciphertexts or plaintexts in each cluster may follow a non-uniform frequency distribution, and such frequency distributions are further correlated for the similar clusters  in different backups.
-% We expect  ciphertexts or plaintexts in most of clusters follow a non-uniform frequency distribution, and such frequency distributions are {\em correlated} for  similar clusters (i.e., correspond to the same minimum chunk hash) in different backups.
-% Our rationale is .   
-% Thus, we apply a  scheme like the distribution-based frequency analysis (see Section~\ref{sec:distribution-attack-description}), in order to find similar clusters.
-
-Then, for each pair $(\mathcal{C}_\mathbf{C}, \mathcal{C}_\mathbf{A})$ of similar clusters, we infer ciphertext-plaintext pairs in two levels. 
-\begin{itemize}[leftmargin=*]
-    \item {\bf Segment-level inference:}
-        If $\mathcal{C}_\mathbf{C}$ and $\mathcal{C}_\mathbf{A}$ have the same number of logical chunks (i.e., ciphertexts or plaintexts), as well as an identical entropy, this implies that $\mathcal{C}_\mathbf{C}$ is exactly mapped from $\mathcal{C}_\mathbf{A}$ with a high probability.
-In this case, we operate attack on the coarse-grained {\em segment} level.
-Specifically, we first compute the entropies of each ciphertext segment $S_\mathbf{C}$ in $\mathcal{C}_\mathbf{C}$ and each plaintext segment $S_\mathbf{A}$ in $\mathcal{C}_\mathbf{A}$, based on the frequency distributions of their ciphertexts and plaintexts, respectively.
-        % (recall identical chunks may have duplicate copies in the same segment). 
-         We infer that $S_\mathbf{C}$ is mapped from  $S_\mathbf{A}$, if the total numbers of logical chunks, as well as the entropies, of $S_\mathbf{C}$ and $S_\mathbf{A}$ are identical.
-Our evaluation shows that the segment-level inference contributes most of the correctly inferred contents in the
-        clustering-based attack (see
-        Section~\ref{sec:experiment-clustering}). It is also possible to further recover each plaintext in these inferred segments with additional adversarial knowledge (e.g., ordering).
-
-    \item {\bf Chunk-level inference:}
-        If $\mathcal{C}_\mathbf{C}$ and $\mathcal{C}_\mathbf{A}$ have different numbers of logical chunks or entropies, we apply frequency analysis to operate attack on the fine-grained {\em chunk} level.
-Specifically, we sort all unique ciphertexts and plaintexts by their frequencies in $\mathcal{C}_\mathbf{C}$ and $\mathcal{C}_\mathbf{A}$, respectively, and infer ciphertext-plaintext pairs based on frequency ranks.
-        However, we find the chunk-level inference does not perform well in our experimental dataset.
-The possible reason is each cluster includes a large number of logical chunks, which degrades the effectiveness of  frequency analysis.
-Even so, we expect the chunk-level inference can recover more ciphertext-plaintext pairs in practice, especially when the number of logical chunks in some clusters is limited.
-        % there are many tied chunks in the similar classes of the VM dataset
-        % Even so, we still expect it can recover even more information in practice, especially when each cluster is of .  
-\end{itemize}
-
-% Figure~\ref{fig:clustering-attack} puts all design primitives together, and show the workflow of the clustering-based attack.
-
-\paragraph{Summary:}
-To summarize, the clustering-based attack exploits similarity, and launches frequency analysis in similar clusters to infer ciphertext-plaintext pairs.
-In addition to  $u$, $r$ and $t$, it is configured by the parameter $k$, which specifies the upper bound distance in combining the closest clusters.
-
-Although possibly affected by the boundary shift of fixed-size segments, we argue that the clustering-based attack is severe against VM disk images. 
-Specifically, a flat VM image file is allocated of a fixed size at the time it is created, and such size cannot be changed during its lifetime.
-All unused regions in a VM image are initially filled with  zero chunks, which can be further re-written for storing additional data in the image.
-% The clustering-based attack does not suffer from boundary shift in this case, since VM images do not need to insert or remove chunks. 
-In Section \ref{sec:experiment-clustering}, we examine the effectiveness of the clustering-based attack against VM images.
-
-% One limitation of the clustering-based attack is it suffers from the {\em boundary shift} of segment.
-Specifically, since we apply fixed-size segmentation, the insertion of one or more chunks will shift the boundaries of all segments that come after the insertion point.
-This changes the frequency distribution of chunks in some segments, and affects the precision of the identified similar clusters.
-This also leads to a reduced number of identical segments, and degrades the amount of original contents inferred by the segment-level inference.
-% % Our evaluation shows that the clustering-based attack can only infer about 1\% original content in a long-term backup dataset. 
-% We argue that the clustering-based attack is still severe for {\em VM disk images}.
-
-% After allocation, all unused regions in the image are filled by , and   
-% which of {\em fixed} sizes during their lifetime.  
-% .
-Specifically, a flat image file is allocated of a {\em fixed} size at the time it is created, and all unused regions of the image file are initially filled with {\em zero chunks}.
-The image file can store additional data by re-writing zero chunks
-%  Flat images are fixed-size files, with one block for each block in the guest’s disk.
-Initially, unused blocks are zero-filled; thus, flat disk images tend to have a lot of zero-filled blocks, particularly if they are rela- tively large to allow the guest operating system space into which to store additional data.
-Sparse images, unlike flat im- ages, only contain virtual disk blocks that have been written at least once.
-Thus, sparse images can occupy relatively lit- tle space when created, and only grow as the guest operating system uses more and more of its virtual disk.
-Note, how- ever, that sparse images can
-% contain zero-filled blocks, since the guest operating system may write a block containing all zeros; such a block would be stored by the virtual machine in the disk image file.
-While there is no global standard for virtual machine disk images, specifications for one file format is available from VMware
-
-% the clustering-based attack has low effectiveness (about 1% inference rate) against the FSL dataset.
-
-% Even so, we argue that the clustering-based attack is severe for some workloads, which store data {\em aligned} with disk block boundaries and do not have the problem of  \cite{jin09}.
-In \S\ref{sec:experiment-clustering}, we will examine the effectiveness of the clustering-based attack against VM workloads,
-
-% The main limitation of the clustering-based attack is the {\em boundary shift} of segment.
-This changes the chunk distributions of some segments, and  affects the precision of identifying similar classes in Step 2.
-The boundary shift also decreases the effectiveness of the segment-level attack in Step 3, since it leads to fewer common segments in the auxiliary data and target data.
-On the other hand, we cannot address the boundary-shift problem by existing approaches (e.g., the content-defined segmentation \cite{lillibridge09}), which depend on the knowledge of the underlying content pattern of ciphertext chunks.
-
-%% In \S\ref{sec:clustering-experiment}, we justify the barrier of the boundary shift in the clustering-based attack.       
-% % between $\mathbf{M}_{\rm a}$ and $\mathbf{M}_{\rm t}$,  
-%%We adapt the similarity-based approach to inference attack.
-Specifically, we apply segmentation, yet on ciphertext chunks, and generate the segments that include adjacent ciphertext chunks under the scrambled order in $\widetilde{\mathcal{L}}_{\rm order}$.
-
-%If $\mathcal{C}_i$ and $\mathcal{M}_j$ have different numbers of logical chunks or entropies, we apply operate classical frequency analysis to operate attack on {\em chunk level}.
-This can infer more ciphertext-plaintext chunk pairs, yet degrading inference precision.
-
-%% over $\mathcal{C}_i$ and $\mathcal{M}_j$ . 
-%% for each ciphertext segment in $\mathcal{C}_i$, we find the plaintext segment that has the same  
-%% Specifically, for each ciphertext segment $S_{\rm t}$ in $\mathcal{C}_i$, we find the plaintext segment $S_{\rm a}$ in $\mathcal{S}_j$ such that   
-%% Then, we adopt the idea of distribution-based ranking (\S\ref{sec:distribution-attack-description}) to identify the ciphertext and plaintext classes that are identified by the same MinHash.  
-%%In the following, we first propose the {\em similarity-based clustering} approach, which aims to classify ciphertext segments by their underlying MinHash.
-Then, we elaborate how to relate a class of ciphertext segments with that of plaintext segments.
-%%\paragraph{Similarity-based clustering:}
-%%works on ciphertext segments and classify them by their underlying MinHash. Then,
-
-% \paragraph{Step 3: (Launch attack through similar classes):} For each identified similar classes $(\mathcal{C}_i, \mathcal{M}_j)$, we launch attack for two cases.
-If $\mathcal{C}_i$ and $\mathcal{M}_j$ have the same number of logical chunks and entropy, our attack operates on {\em segment level}.
-For each ciphertext segment $S_{\rm t}$ in $\mathcal{C}_i$, we examine each available plaintext segment $S_{\rm a}$ in $\mathcal{S}_j$, and infer $(S_{\rm t}, S_{\rm a})$ as a ciphertext-plaintext segment pair if $S_{\rm a}$ has the same number of logical chunks and entropy (via Equation~\ref{eq:clustering-entropy} but computed for segment) with $S_{\rm t}$.
-We stop the attack at segment level in this case, because there is not enough information to further extracting chunk content; otherwise it sacrifices inference precision.
-We argue that the segment-level attack is severe, since each segment represents a continues region of data.
-The adversary can learn significant information if it successfully extracts the underlying data of some segment.
-
-%% Through experimental analysis, the segment-level attack contributes the most component of correct inferences.     
-%% has the same number of logical chunks and entropy as $S_{\rm t}$. We infer that $S_{\rm a}$ is the original segment of $S_{\rm t}$.
-
-%If $\mathcal{C}_i$ and $\mathcal{M}_j$ have different numbers of logical chunks or entropies, we apply operate classical frequency analysis to operate attack on {\em chunk level}.
-This can infer more ciphertext-plaintext chunk pairs, yet degrading inference precision.
-
-%% over $\mathcal{C}_i$ and $\mathcal{M}_j$ . 
-%% for each ciphertext segment in $\mathcal{C}_i$, we find the plaintext segment that has the same  
-%% Specifically, for each ciphertext segment $S_{\rm t}$ in $\mathcal{C}_i$, we find the plaintext segment $S_{\rm a}$ in $\mathcal{S}_j$ such that   
-%% Then, we adopt the idea of distribution-based ranking (\S\ref{sec:distribution-attack-description}) to identify the ciphertext and plaintext classes that are identified by the same MinHash.  
-%%In the following, we first propose the {\em similarity-based clustering} approach, which aims to classify ciphertext segments by their underlying MinHash.
-Then, we elaborate how to relate a class of ciphertext segments with that of plaintext segments.
-%%\paragraph{Similarity-based clustering:}
-%%works on ciphertext segments and classify them by their underlying MinHash. Then,
-
-% Based on the configuration parameters of $u$, $r$ and $t$ (see \S\ref{sec:distribution-attack-description}), we pick the ciphertext class $\mathcal{C}_i$ that has the $i$-th most number of logical chunks ($1 \leq i \leq u$), and examine each plaintext class $\mathcal{M}_j$ that ranks from $i-r$ to $i+r$.
-We identify that $\mathcal{C}_i$ and $\mathcal{M}_j$ have the same MinHash, if the difference of their entropies is (i) minimum across all $i-r \leq j \leq i+r$ and (ii) smaller than $t$.
-
-% while the rest data preserve the same characteristics.   
-% Due to backup redundancies, .   . 
-% Our rationale is that the chunk distributions in similar classes are likely to be correlated due to deterministic encryption.
-
-%We build on the idea of the distribution-based ranking (see \S\ref{sec:distribution-attack-description}) to identify the ciphertext and plaintext classes that correspond to the same MinHash.
-Specifically, for each ciphertext class with an underlying MinHash of $h$, our aim is to find the plaintext class identified by the same MinHash of $h$.
-Note that we cannot measure relative frequency distributions for ranking, since we do not have enough knowledge about neighboring chunks.
-Instead, we count the entropy of a class by the {\em occurrences of different chunks} in the class.
-Specifically, for a plaintext class $\mathcal{M}$, we compute its entropy:  \begin{eqnarray}
-%        e_{\mathcal{M}} = \sum_{M \in \mathcal{M}} {\sf log}_2 \frac{{\sf cnt}_\mathcal{M}(M)}{|\mathcal{M}|},
-%        \label{eq:clustering-entropy}
-%\end{eqnarray}
-%where $|\mathcal{M}|$ is the total number of logical chunks in $\mathcal{M}$ and ${\sf cnt}_\mathcal{M}(M)$ returns the number of copies of the chunk $M$ in $\mathcal{M}$.
-We derive similar entropy $e_\mathcal{C}$ for a ciphertext class $\mathcal{C}$, and consider $\mathcal{M}$ and $\mathcal{C}$ are {\em similar classes} (i.e., having the same MinHash), if the difference of their entropies is minimum.
-Our rationale is that the chunk distributions in similar classes are likely to be correlated due to deterministic encryption.
-
-%In more details, we first sort the available ciphertext and plaintext classes separately by the number of logical chunks they include.
-Based on the configuration parameters of $u$, $r$ and $t$ (see \S\ref{sec:distribution-attack-description}), we pick the ciphertext class $\mathcal{C}_i$ that has the $i$-th most number of logical chunks ($1 \leq i \leq u$), and examine each plaintext class $\mathcal{M}_j$ that ranks from $i-r$ to $i+r$.
-We identify that $\mathcal{C}_i$ and $\mathcal{M}_j$ have the same MinHash, if the difference of their entropies is (i) minimum across all $i-r \leq j \leq i+r$ and (ii) smaller than $t$.
-
-%% However, it is hard to classify ciphertext segments, since there still exists a challenge on identifying the underlying MinHash of ciphertext segments. Recall that  
-%% By our assumption (\S\ref{sec:clustering-attack}), all ciphertext segments must have the same size.
-Thus, to be compatible, we also partition the original stream of plaintext chunks $\mathbf{M}_{\rm a}$ into fixed-size {\em plaintext segments}, each of which comprises a sequence of plaintext chunks.
-
-%% We adapt the similarity-based approach to inference attack. Specifically, to capture the notion of similarity,  
-%% for inferring ciphertext-plaintext chunk pairs through similar segments. Specifically, we
-
-% We proceed our similarity-based clustering scheme as follows.
-It defines the {\em clustering distance} of The smaller the distance ${\sf Dist}(S_{\rm t}, S_{\rm t}')$ is, the more likely are $S_{\rm t}$ and $S_{\rm t}'$ to have the same underlying MinHash.
-Then, it uses the agglomerative hierarchical clustering algorithm (via the function  in ) for clustering, and generates the ciphertext classes based on a desired minimum intercluster distance of $d$ (via the function  in ALGLIB \cite{alglib}).
-By default, we configure $d$ by 0.8.
-
-% we can apply Broder's theorem  on ciphertexts due to the deterministic nature of encryption.  
-% This is because encryption preserves the deduplication capability of elements.
-% .
-Thus, we can compute the overlaps between any two ciphertext segments, and cluster them into several {\em ciphertext classes}, such that each cluster includes the ciphertext segments that possibly have the same underlying MinHash.
-
-%We propose the {\em similarity-based clustering} approach, which aims to classify the ciphertext segments by their underlying MinHash while not compromising confidentiality.
-The key insight is that if two ciphertext segments have a large fraction of common (ciphertext) chunks, then they are likely to have the same underlying MinHash (due to Equation (\ref{eq:broder})).
-Thus, we can compute the overlaps between any two ciphertext segments, and cluster them into several {\em ciphertext classes}, such that each cluster includes the ciphertext segments that possibly have the same underlying MinHash.
-
-% identify  This raises a challenge on how to group   
-% the minimum element hash $h$  
-% it is impossible to the original plaintext and identify the minimum element hash corresponding to a ciphertext segment.  
-% recover its original plaintext segment and extract the minimum element hash.    
-% the original plaintexts of the ciphertext segment, and further learn the      
-% The challenge is  Since each ciphertext segment is mapped by symmetric encryption, it is impossible to learn their original content and identify the minimum element hash from corresponding plaintexts.
-% Since each ciphertext in $S_\mathbf{C}$ is mapped by symmetric encryption, it is impossible to learn their original plaintexts or identify the minimum element hash (based on these plaintexts).
-In other words, the main challenge
-% which chunk leads to the minimum element hash, and further the exact hash value.
-In other words, there exists a challenge on collecting similar $\{ S_\mathbf{C} \}$ (i.e., they share the same original minimum element hash) and map them to $\mathcal{C}_\mathbf{A}$.
-
-%Thus, instead of inferring ciphertext-plaintext pairs (from $\mathbf{C}$ and $\mathbf{A}$) directly,
-
-%One challenge behind the clustering-based attack is how to identify the original minimum element hash $h$ of each $S_\mathbf{C}$. Since
-
-%The clustering-based attack proceeds as follows. First, we
-
-%We classify plaintext segments into a set of {\em plaintext classes} by their MinHash.
-On the other hand, we cannot perform similar classification over ciphertext segments, since their underlying contents are protected by symmetric encryption (see \S\ref{sec:threat}).
-
-%% , each of which includes the plaintext segments that have the same MinHash. 
-%% it is impossible to access or compare the underlying contents of ciphertext chunks for classification, since their original contents are protected by symmetric encryption
-
-%% split the original space () of frequency analysis into multiple subspaces, and
-%% eliminates     
-%% identify the minimum element hash of each $S_\mathbf{C}$, and then apply frequency analysis with some $S_\mathbf{A}$ that shares the same minimum element hash. This      
-%% This inspires us to    
-% % $S_\mathbf{M}$ has a large fraction of overlaps with the original plaintexts of $S_{\rm t}$    
-%% Our insight is  if the {\em underlying MinHash} (that is computed from the plaintext of each ciphertext chunk element) of a ciphertext segment $S_{\rm t}$ is identified the same as that of some plaintext segment $S_{\rm a}$, then the chunks in $S_{\rm a}$ are likely to be the original plaintexts of the ciphertexts in $S_{\rm t}$.
-The rationale is that $S_{\rm a}$ has a large fraction of overlaps with the original plaintexts of $S_{\rm t}$  (due to Equation~(\ref{eq:broder})).
-In other words, we collect all ciphertext segments that have a common underlying MinHash (see Step 1), say $h$, and infer their original chunks from the plaintext segments that have the same MinHash of $h$ (see Step 2 and Step 3).
-By repeating the inference for each available MinHash, we can avoid some of ties incurred by classical frequency analysis, since the tied chunks may have different frequencies for the same MinHash.
-%% Similarly, we apply fixed-size segmentation to generate each segment $S_\mathbf{A}$ that consists of plaintexts of $\mathbf{A}$.
-%% knowledge of the underlying content pattern of ciphertext chunks. 
-%% that we need the order of each ciphertext in $\mathbf{C}$ for segmentation, while not requiring such order reflects that of corresponding plaintext. 
-%% We use  and  that is generated from $\mathbf{C}$ and that is mapped from, respectively.
-%% generated from $\mathbf{C}$ and its corresponding plaintext, respectively.
-%% denote a segment from $\mathbf{C}$ by  
-%% Note that we need the ordering of $\mathbf{C}$ to ensure each segment includes the continue content, while not requiring such ordering reflects that of corresponding plaintext.  
-%% {\em fixed-size} data units,   
-%%In this work, we implement fixed-size segmentation scheme to generate ciphertext segments.
-More sophisticated segmentation schemes (e.g., variable-size segmentation \cite{lillibridge09, qin17}) can be applied to address content shifting, yet they depend on the knowledge of the underlying content pattern of ciphertext chunks.
-For clustering, we define the distance of two ciphertext segments $S_{\rm tar}$ and $S_{\rm tar}'$ by one minus their Jaccard similarity coefficient:
-%%
-%% Given $\mathbf{C}$, we partition   
-%% The clustering-based attack builds on {\em similarity-based approach} \cite{li17,qin17,xia11,bhagwat09}.
-Specifically, the similarity-based approach groups multiple adjacent chunks into a coarse-grained unit called {\em segment}, and considers that two segments are {\em similar} if they have the same minimum hash value (i.e., {\em MinHash}) over their chunk elements.
-By Broder's theorem \cite{broder97}, the probability that two segments $S$ and $S'$ are similar is the same as their Jaccard similarity coefficient:
-%% \subsection{Attack Description}
-%% {\color{blue}
-%% {\bf --- not good enough ---}
-%% To capture similarity in inference attack, we partition the auxiliary stream $\mathbf{M}_{\rm a}$ of plaintext chunks into {\em plaintext segments}, which comprises sequences of plaintext chunks.
-Correspondingly, we construct {\em ciphertext segments}, each of which is composed of the ciphertext chunks whose original plaintexts are in the same plaintext segment.
-For compatibility, we ensure that both  plaintext and ciphertext segments have the same size.
-%% {\bf --- not good enough ---}
-%% }
-%% (recall that we can access the time windows of original chunks from $\widetilde{\mathcal{L}}_{\rm order}$). 
-%% We propose to launch inference attack through similar segments.
-
-%\begin{figure}
-%	\includegraphics[width=.48\textwidth]{pic/clustering-attack.pdf}
-%	\caption{Overview of the clustering-based attack.}
-%	\label{fig:clustering-attack}
-%\end{figure}
-
-%Figure~\ref{fig:clustering-attack} highlights the main steps of the clustering-based attack. We elaborate the details as follows.
-
-%\paragraph{Step 2: (Identify similar classes):}
-%We build on the idea of the distribution-based ranking (see \S\ref{sec:distribution-attack-description}) to identify the ciphertext and plaintext classes that correspond to the same MinHash.
-Specifically, for each ciphertext class with an underlying MinHash of $h$, our aim is to find the plaintext class identified by the same MinHash of $h$.
-Note that we cannot measure relative frequency distributions for ranking, since we do not have enough knowledge about neighboring chunks.
-Instead, we count the entropy of a class by the {\em occurrences of different chunks} in the class.
-Specifically, for a plaintext class $\mathcal{M}$, we compute its entropy:  \begin{eqnarray}
-%        e_{\mathcal{M}} = \sum_{M \in \mathcal{M}} {\sf log}_2 \frac{{\sf cnt}_\mathcal{M}(M)}{|\mathcal{M}|},
-%        \label{eq:clustering-entropy}
-%\end{eqnarray}
-%where $|\mathcal{M}|$ is the total number of logical chunks in $\mathcal{M}$ and ${\sf cnt}_\mathcal{M}(M)$ returns the number of copies of the chunk $M$ in $\mathcal{M}$.
-We derive similar entropy $e_\mathcal{C}$ for a ciphertext class $\mathcal{C}$, and consider $\mathcal{M}$ and $\mathcal{C}$ are {\em similar classes} (i.e., having the same MinHash), if the difference of their entropies is minimum.
-Our rationale is that the chunk distributions in similar classes are likely to be correlated due to deterministic encryption.
-
-%In more details, we first sort the available ciphertext and plaintext classes separately by the number of logical chunks they include.
-Based on the configuration parameters of $u$, $r$ and $t$ (see \S\ref{sec:distribution-attack-description}), we pick the ciphertext class $\mathcal{C}_i$ that has the $i$-th most number of logical chunks ($1 \leq i \leq u$), and examine each plaintext class $\mathcal{M}_j$ that ranks from $i-r$ to $i+r$.
-We identify that $\mathcal{C}_i$ and $\mathcal{M}_j$ have the same MinHash, if the difference of their entropies is (i) minimum across all $i-r \leq j \leq i+r$ and (ii) smaller than $t$.
-
-%% However, it is hard to classify ciphertext segments, since there still exists a challenge on identifying the underlying MinHash of ciphertext segments. Recall that  
-%% By our assumption (\S\ref{sec:clustering-attack}), all ciphertext segments must have the same size.
-Thus, to be compatible, we also partition the original stream of plaintext chunks $\mathbf{M}_{\rm a}$ into fixed-size {\em plaintext segments}, each of which comprises a sequence of plaintext chunks.
-
-%% We adapt the similarity-based approach to inference attack. Specifically, to capture the notion of similarity,  
-%% for inferring ciphertext-plaintext chunk pairs through similar segments. Specifically, we
-
-%\paragraph{Step 3: (Launch attack through similar classes):} For each identified similar classes $(\mathcal{C}_i, \mathcal{M}_j)$, we launch attack for two cases.
-If $\mathcal{C}_i$ and $\mathcal{M}_j$ have the same number of logical chunks and entropy, our attack operates on {\em segment level}.
-For each ciphertext segment $S_{\rm t}$ in $\mathcal{C}_i$, we examine each available plaintext segment $S_{\rm a}$ in $\mathcal{S}_j$, and infer $(S_{\rm t}, S_{\rm a})$ as a ciphertext-plaintext segment pair if $S_{\rm a}$ has the same number of logical chunks and entropy (via Equation~\ref{eq:clustering-entropy} but computed for segment) with $S_{\rm t}$.
-We stop the attack at segment level in this case, because there is not enough information to further extracting chunk content; otherwise it sacrifices inference precision.
-We argue that the segment-level attack is severe, since each segment represents a continues region of data.
-The adversary can learn significant information if it successfully extracts the underlying data of some segment.
-
-%% Through experimental analysis, the segment-level attack contributes the most component of correct inferences.     
-%% has the same number of logical chunks and entropy as $S_{\rm t}$. We infer that $S_{\rm a}$ is the original segment of $S_{\rm t}$.
-
-%If $\mathcal{C}_i$ and $\mathcal{M}_j$ have different numbers of logical chunks or entropies, we apply operate classical frequency analysis to operate attack on {\em chunk level}.
-This can infer more ciphertext-plaintext chunk pairs, yet degrading inference precision.
-
-%% over $\mathcal{C}_i$ and $\mathcal{M}_j$ . 
-%% for each ciphertext segment in $\mathcal{C}_i$, we find the plaintext segment that has the same  
-%% Specifically, for each ciphertext segment $S_{\rm t}$ in $\mathcal{C}_i$, we find the plaintext segment $S_{\rm a}$ in $\mathcal{S}_j$ such that   
-%% Then, we adopt the idea of distribution-based ranking (\S\ref{sec:distribution-attack-description}) to identify the ciphertext and plaintext classes that are identified by the same MinHash.  
-%%In the following, we first propose the {\em similarity-based clustering} approach, which aims to classify ciphertext segments by their underlying MinHash.
-Then, we elaborate how to relate a class of ciphertext segments with that of plaintext segments.
-%%\paragraph{Similarity-based clustering:}
-%%works on ciphertext segments and classify them by their underlying MinHash. Then,
-
-%\subsection{Discussion}
-%\label{sec:clustering-attack-discussion}
-
-%The main limitation of the clustering-based attack is the {\em boundary shift} of segment.
-The insertion of one or more chunks will shift the boundaries of all segments that come after the insertion point.
-This changes the chunk distributions of some segments, and  affects the precision of identifying similar classes in Step 2.
-The boundary shift also decreases the effectiveness of the segment-level attack in Step 3, since it leads to fewer common segments in the auxiliary data and target data.
-On the other hand, we cannot address the boundary-shift problem by existing approaches (e.g., the content-defined segmentation \cite{lillibridge09}), which depend on the knowledge of the underlying content pattern of ciphertext chunks.
-
-%Even so, we argue that the clustering-based attack is severe for the virtual machine (VM) images, which store data {\em aligned} with disk block boundaries  \cite{jin09}.
-In \S\ref{sec:experiment-clustering}, we will examine the effectiveness of the clustering-based attack against VM workloads.
-
-%% In \S\ref{sec:clustering-experiment}, we justify the barrier of the boundary shift in the clustering-based attack.       
-% % between $\mathbf{M}_{\rm a}$ and $\mathbf{M}_{\rm t}$,  
-%%We adapt the similarity-based approach to inference attack.
-Specifically, we apply segmentation, yet on ciphertext chunks, and generate the segments that include adjacent ciphertext chunks under the scrambled order in $\widetilde{\mathcal{L}}_{\rm order}$.
-
-%%In this work, we implement fixed-size segmentation scheme to generate ciphertext segments.
-More sophisticated segmentation schemes (e.g., variable-size segmentation \cite{lillibridge09, qin17}) can be applied to address content shifting, yet they depend on the knowledge of the underlying content pattern of ciphertext chunks.
-For clustering, we define the distance of two ciphertext segments $S_{\rm tar}$ and $S_{\rm tar}'$ by one minus their Jaccard similarity coefficient:
-%%$${\sf Sim}(S_{\rm tar}, S_{\rm tar}') = 1 - \frac{|S_{\rm tar} \cap S_{\rm tar}'|}{|S_{\rm tar} \cup S_{\rm tar}'|}.$$
-%%The smaller ${\sf Sim}(S_{\rm tar}, S_{\rm tar}')$ is, the more likely that they have the same underlying MinHash.
-Then, we use agglomerative hierarchical clustering algorithm (via the function {\tt clusterizerrunahc} in ALGLIB \cite{alglib}) to generate the slices.
-
-%%% For any two ciphertext segments $S_{\rm tar}$ and $S_{\rm tar}'$, we define their similarity distance by one minus their Jaccard similarity coefficient:
-%%% $${\sf Sim}(S_{\rm tar}, S_{\rm tar}') = 1 - \frac{|S_{\rm tar} \cap S_{\rm tar}'|}{|S_{\rm tar} \cup S_{\rm tar}'|}.$$
-
-%%In addition, we partition $\mathbf{M}_{\rm aux}$ to form plaintext segments, each of which is a region of logically adjacent chunks in $\mathbf{M}_{\rm aux}$.
-For compatibility, we require that the plaintext segment has the same (fixed) size with ciphertext segment.
-Then, we classify plaintext segments by their MinHash (note that we have full access to the MinHash of each plaintext segment), and obtain several plaintext slices.
-
-%%To launch attack, we apply frequency analysis to the ciphertext and plaintext slices that are identified by the same MinHash.
-This is for two reasons.
-First, tied chunks may have different frequencies in some slices, and these ties can be break.
-Second, the original chunks are likely to be in the
-
-%%each of which includes the segments that have the same MinHash (note that we have fully access to the MinHash of each plaintext segment).
-
-%%Like prior works \cite{li17,qin17,xia11,bhagwat09}, we
-
-%%Specifically, we  We also generate ciphertext segments, which include adjacent ciphertext chunks yet under the scrambled order in $\widetilde{\mathcal{L}}_{\rm order}$.
-
-%%The clustering-based attack uses {\em ``divide-and-conquer''} strategy to improve the inference accuracy of tied chunks.
-At a high level, it partitions $\mathbf{M}_{\rm aux}$ into {\em plaintext slices}, and each slice includes a number of plaintext chunks.
-It generates similar {\em ciphertext slices} from $\widetilde{\mathcal{L}}_{\rm order}$, and pairs each ciphertext slice with some plaintext slice of $\mathbf{M}_{\rm aux}$.
-It finally applies frequency analysis to infer original chunks from each slice pair.
-The rationale is that tied chunks may have different frequencies in some slices.
-
-%%% To generate slices, we build on the {\em similarity-based approach} \cite{li17,qin17,xia11,bhagwat09}.
-Specifically, it defines a coarse-grained unit called {\em segment}, which comprises multiple adjacent chunks.
-Two segments are said {\em similar}, if they have the same minimum hash (i.e., MinHash) over their chunk elements.
-By Broder's theorem \cite{broder97}, the probability that two segments $S_i, S_j$ are similar is the same as their Jaccard similarity coefficient:
-%%% $${\sf Pr}[{\sf MinHash}(S_i) = {\sf MinHash}(S_j)] = \frac{|S_i \cap S_j|}{|S_i \cup S_j|},$$
-%%% where ${\sf MinHash}(S)$ is the minimum hash of chunk element in $S$.
-Thus, prior works \cite{li17,qin17,xia11,bhagwat09} can apply the similarity-based approach to improve the effectiveness of near-exact deduplication.
-
-%%To form a plaintext slice, we collect all
-
-%%===
-
-%%Specifically, we add the segments that have the same MinHash into an identical slice, and pair a ciphertext slice with a plaintext slice if they have the same chunk. Thus,
-
-%%each slice includes the segments that have the same MinHash. Since
-
-%%the original chunk of ciphertext chunk is likely to be in
-
-%%Our insight is that if two ciphertext segments have a large fraction of common chunks, they are likely to have the same underlying MinHash.
-
-%%By Broder's theorem, similar segments are likely to have a large fraction of common chunks.
-
-%%Our insight is to generate slices
-
-%%A plaintext segment is a region of logically adjacent chunks in $\mathbf{M}_{\rm aux}$, while a ciphertext segment includes several adjacent ciphertext chunks defined in the scrambled order in $\widetilde{\mathcal{L}}_{\rm order}$.
-We measure the {\em similarity} of two segments (e.g., $S_i$ and $S_j$) by their Jaccard similarity coefficient (e.g., $|S_i \cap S_j|/|S_i \cup S_j|$).
-
-%%Our insight is to generate the slices that include all segments identified by the same MinHash.
-
-%%We propose a new inference attack, the {\em clustering-based attack}, which uses {\em ``divide-and-conquer''} strategy to improve the severity of frequency analysis.
-
-%%The clustering-based attack builds on
-
-%%The key technique underlying the attack is {\em similarity-based approach} to generate slices.
-
-%%To generate slices, the clustering-based attack uses a {\em similarity-based approach}, which builds on a coarse-grained unit, called {\em segment}, of chunks.
-A plaintext segment is a region of logically adjacent chunks in $\mathbf{M}_{\rm aux}$.
-We also extract ciphertext segments, which include adjacent ciphertext chunks defined in the scrambled order in $\widetilde{\mathcal{L}}_{\rm order}$.
-
-%%It can  based
-
-%%We generate a plaintext segment as a region of  On the other hand, we form ciphertext segments directly based on the scrambled order of each ciphertext chunk.
-
-%%Specifically,
-
-%%   which can infer original chunk content with coarse-grained order information.
-
-%%In the following, we present the attack details step by step.
-
-%%% We propose the {\em clustering-based attack}.
-At a high level, it partitions $\mathbf{M}_{\rm aux}$ into {\em plaintext slices}, which include a number of plaintext chunks.
-It generates similar {\em ciphertext slices} from $\widetilde{\mathcal{L}}_{\rm order}$, and pairs each ciphertext slice with some plaintext slice of $\mathbf{M}_{\rm aux}$.
-It finally applies frequency analysis to infer original chunks from each ciphertext-plaintext slice pair.
-In the following, we present the attack step by step.
-
-%%\paragraph{Step 1: Group chunks into segments.}
-%%The clustering-based attack defines a coarse-grained unit, called {\em segment}, of chunks.
-We generate a plaintext segment as a region of logically adjacent chunks in $\mathbf{M}_{\rm aux}$.
-On the other hand, we form ciphertext segments directly based on the scrambled order of each ciphertext chunk.
-
-%%By segmentation, we expect we can limit order scrambling within each segment.
-
-%%Note that since we cannot identify the underlying content of ciphertext chunks, our segmentation scheme is with a fixed size rather than content based.
-
-%%it can only form ciphertext segment based on the scrambled orders of ciphertext chunks. Even so, we expect the order scrambling can be located within each segment.
-
-%%By segmentation, we expect the order
-
-%%For $\mathbf{M}_{\rm aux}$, a (plaintext) segment includes a fixed-size region of logically adjacent chunks.
-On the other hand, we cannot identify the accurate order of each ciphertext chunk.
-Thus, we elaborate segment as based on the scrambled orders in $\widetilde{\mathcal{L}}_{\rm order}$.
-
-%%\paragraph{Step 2: Classify plaintext segments by MinHash.}
-
-%%\paragraph{Step 3: Cluster ciphertext segments by similarity.}
-
-%%% The rationale is that tied chunks may have different frequencies in some slices.
-
-%%The clustering-based attack builds on a {\em similarity-based approach} to generate slices of chunks. First, it groups chunks into a coarse-grained unit, called {\em segment}.
-
-%%After segmentation, we expect the order scrambling only appears within each segment.
-
-%%\paragraph{Step 3: Slice pairing.}
-
-%%\paragraph{Step 4: Chunk inference.}
-
-%%We start with a na\"{i}ve slicing approach. Specifically, we partition $\mathbf{M}_{\rm aux}$ into fixed-size regions of
-
-%%To realize slicing, we propose a  
-%%generates plaintext and ciphertext slices from $\mathbf{M}_{\rm aux}$ and $\widetilde{\mathcal{L}}_{\rm order}$, respectively. Each slice includes a number of plaintext or ciphertext chunks.
-
-%%To generate slices, the attack builds on the similarity characteristics of workloads.
-
-%%The attack apply to pair ciphertext-plaintext slices,
-
-%%First, the adversary
-
-%%We start with a na\"ive frequency analysis.
-
-%%builds on similarity.
-
-%%\paragraph{Similarity-based clustering:}
-
-%%\paragraph{Distribution-based pairing:}
-
-%%At a high level, the clustering-based attack partitions $\mathbf{M}_{\rm aux}$ into {\em plaintext slices}, and each slice includes a number of plaintext chunks.
-It also generates ciphertext slices from $\widetilde{\mathcal{L}}_{\rm order}$, and pairs each ciphertext slice with some plaintext slice of $\mathbf{M}_{\rm aux}$.
-Then, it applies frequency analysis on all paired ciphertext-plaintext slices to infer chunks.
-
-%%The similarity-based clustering builds on Broder's theorem, which states that the probability that the two sets $S_1$ and $S_2$ have the same minimum hash element is the same as their Jaccard similarity coefficient.
-
-%%\subsection{Attack Description}
-
-%%Our idea is to group all chunks
-
-%%We first overview how the clustering-based attack works.
-First, the adversary partitions $\mathbf{M}_{\rm aux}$ into {\em plaintext slices}, and each slice includes a number of plaintext chunks.
-It also generates ciphertext slices from $\widetilde{\mathcal{L}}_{\rm order}$.
-Then, the adversary pairs each ciphertext slice with some plaintext slice, and applies frequency analysis on all paired slices to infer chunks.
-This mitigates the chunk tiles in some extent, since the globally tied chunks may not have the same frequency in all paired slices.
-
-%%at high level. Generally, the clustering-based attack builds on the  It partitions
-
-%%The clustering-based attack builds on the  strategy. Specifically, it cuts $\mathbf{M}_{\rm aux}$ into several {\em plaintext slices}, and each slice includes a number of plaintext chunks.
-
-%%A naive slicing solution is to
-
-%%Based on the auxiliary information, it
-
-%%Instead of attacking with $\mathbf{M}_{\rm aux}$ and $\widetilde{\mathcal{L}}_{\rm order}$ in their entirety, it divides the adversarial knowledge into plaintext and ciphertext slices, and uses frequency analysis to identify the ciphertext-plaintext chunks in each slice.
-
-%%Specifically, it first generates plaintext slices $\mathbf{M}_{\rm aux}$. Each slice includes a number of continuous chunks.
-
-%%\paragraph{Attack details:}
-
-%%\subsection{Discussion}
-
-%%%in which the known chunk orders are {\em permuted} from the original order of corresponding chunks.
-
-%%%We first re-define our model to adapt the setting of the two-stage attack.
-
-%%%   which requires {\em minimum} knowledge about order information. Specifically, in the two-stage attack, the  instead, it just need to access
-
-%%%can work with
-
-%%%only needs {\em minimum} knowledge about order information. Specifically, it can build on
-
-%%%We suppose that the target victim file $\mathbf{M}_{\rm tar}$ includes $n$ chunks (including duplicates), and $\pi$ is a permutation by randomizing the logical orders of every $k$ chunks.
-
-%%%over their order set $\{1,\ldots,n\}$.
-
-%%%%We define $\widetilde{\mathcal{L}}_{\rm order} = \{(C, \pi({\sf ord}(M))): (M, *) \in \mathbf{M}_{\rm tar} \wedge C = \mathcal{E}_K(M)\}$.
-
-%%%{\bf TO DO}
-%%%% suppose the target victim file includes $n$ logical chunks, and $\pi$ is a permutation on the set $\{1,\ldots,n\}$. }
-
-%%%\paragraph{Attack Overview:}
-
-%%%\subsection{Attack Overview}
-
-%%%The two-stage attack follows the {\em divide and conquer} principle. Figure \ref{fig:overview} outlines the overview of the two-stage attack.
-
-%%\subsection{Similarity-based Clustering}
-
-%%\subsection{Attack Description}
-
-%%\subsection{Attack Example}
-
-\chapter{Experiments}
-\label{sec:experiment}
-
-In this section, we present the trace-driven evaluation results to demonstrate
-the severity of our proposed frequency analysis attacks against encrypted
-deduplication.
-
-\section{Methodology}
-\label{sec:dataset}
-
-\begin{table}[!t]
-    \caption{Characteristics of experimental datasets.}
-\small
-\label{tab:dataset}
-\renewcommand{\arraystretch}{1.2}
-\vspace{-3pt}
-\centering
-\begin{tabular}{|c|c|c|c|}
-\hline
- \multirow{2}{*}{\bf Dataset} & \multirow{2}{*}{\bf Category} & \multicolumn{2}{c|}{\bf Characteristics in Each Snapshot} \\
-\cline{3-4}
-    & &  \#Logical (Million) & \#Unique (Million) \\
-\hline
-    \multirow{6}{*}{FSL} & User004  & 1.0-1.3 & 0.7-0.9\\
- \cline{2-4}
-              & User007 &  3.5-5.2 & 2.3-3.6 \\
- \cline{2-4}
-              & User012 &  25.0-26.4 & 8.9-9.7 \\
-\cline{2-4}
-              & User013 &  1.8-5.7 & 1.2-4.2 \\
-\cline{2-4}
-              & User015 &  13.4-20.5 & 9.0-11.0 \\
-\cline{2-4}
-              & User028 &  6.0-10.3 & 3.5-6.8 \\
-\hline
-\hline
-    \multirow{4}{*}{MS} & Win7  & 61.6-61.8 & 61.1-61.3\\
-\cline{2-4}
-              & Serv-03 & 10.6-10.7 & 8.4-8.5\\
-\cline{2-4}
-              & Serv-08 & $\sim$6.5 & $\sim$3.8 \\
-\cline{2-4}
-              & Vista-B &  $\sim$7.6 & $\sim$2.0\\
-\cline{2-4}
-              & Vista-U &  $\sim$21.0 & $\sim$10.4 \\
-\hline
-\hline
-
-    \multirow{6}{*}{VM} & User1  &  \multirow{6}{*}{2.6} & $\sim$0.9 \\
-\cline{2-2}
-\cline{4-4}
-              & User2 &  & 1.1-1.3 \\
-\cline{2-2}
-\cline{4-4}
-              & User3 &  & 0.9-1.1 \\
-\cline{2-2}
-\cline{4-4}
-              & User4 &  & $\sim$0.9 \\
-\cline{2-2}
-\cline{4-4}
-              & User5 &  & 0.9-1.0 \\
-\cline{2-2}
-\cline{4-4}
-              & User6 &  & 0.9-1.1 \\
-\hline
-\end{tabular}
-\medskip
-
-\raggedright
-    The notations \#Logical and \#Unique denote the total number of logical and unique chunks in each experimental snapshot, respectively. 
-    % All VM images have a fixed size of 10GB and hence the same number of logical chunks.
-\end{table}
-
-%\begin{table}[!t]
-%\small
-%\caption{Experimental datasets.}
-%\label{tab:dataset}
-%\renewcommand{\arraystretch}{1.2}
-%\vspace{-3pt}
-%\centering
-%\begin{tabular}{|c|c|c|}
-%\hline
-%{\bf Dataset} & {\bf Category} & {\bf Approximate Logical Size} \\
-%\hline
-%\hline
-%%\multirow{2}{*}{FSL} & Physical  & 431.9GB  & 659.3GB & 584.3GB \\
-%	\multirow{6}{*}{FSL} & User004  & 10GB/backup $\times$ 14 backups \\
-%\cline{2-3}
-%			  & User007 & 39GB/backup $\times$ 14 backups \\
-%\cline{2-3}
-%			  & User012 & 244GB/backup $\times$ 14 backups \\
-%\cline{2-3}
-%			  & User013 & 22GB/backup $\times$ 14 backups\\
-%\cline{2-3}
-%			  & User015 & 158GB/backup $\times$ 14 backups\\
-%\cline{2-3}
-%			  & User028 & 77GB/backup $\times$ 14 backups\\
-%\hline
-%\hline
-%\multirow{4}{*}{MS} & WIN7  & 425GB/snapshot $\times$ 4 snapshots \\
-%\cline{2-3}
-%			  & Serv-03 & 78GB/snapshot $\times$ 4 snapshots \\
-%\cline{2-3}
-%			  & Serv-08 & 48GB/snapshot $\times$ 4 snapshots \\
-%\cline{2-3}
-%			  & Vista-B & 55GB/snapshot $\times$ 4 snapshots \\
-%\cline{2-3}
-%			  & Vista-U & 159GB/snapshot $\times$ 4 snapshots \\
-
-%\hline
-%\hline
-
-%\multirow{6}{*}{VM} & User1  & 25GB/backup $\times$ 13 backups \\
-%\cline{2-3}
-%			  & User2 & 28GB/backup $\times$ 13 backups \\
-%\cline{2-3}
-%			  & User3 & 26GB/backup $\times$ 13 backups \\
-%\cline{2-3}
-%			  & User4 & 25GB/backup $\times$ 13 backups\\
-%\cline{2-3}
-%			  & User5 & 25GB/backup $\times$ 13 backups\\
-%\cline{2-3}
-%			  & User6 & 27GB/backup $\times$ 13 backups\\
-
-%% \multicolumn{2}{|c|}{\bf Storage saving} & 98.6\% & 98.3\% \\
-%\hline
-%\end{tabular}
-%\end{table}
-We evaluate our attacks using the following real-world datasets, whose
-characteristics are summarized in Table~\ref{tab:dataset}. 
-% Table~\ref{tab:dataset} summarizes the characteristics of the experimental datasets used in our experiments. 
-% We evaluate our attacks using the following datasets. 
-% investigate the security implications of the leakages (see \S\ref{sec:background}) by means of simulated attacks,
-
-\begin{itemize}[leftmargin=*]
-\item 
-\textbf{FSL:} This dataset is collected by the File systems and
-        Storage Lab (FSL) at Stony Brook University \cite{sun16,FSL14,sun18}. We focus on
-the {\em fslhomes} snapshots, each of which includes an ordered list of 48-bit
-chunk hashes that are produced by variable-size chunking under an average size
-of 8KB, as well as the corresponding metadata information (e.g., chunk size,
-file name extension, etc). We pick the snapshots from January 22 to May 21 in
-2013, and select six users (i.e., User004, User007, User012, User013, User015,
-and User028) that have the complete daily snapshots over the whole duration.
-We collect these snapshots on a weekly basis, and hence form 14 weekly full
-backups for each user.  
-\item 
-\textbf{MS:} This dataset is collected by Microsoft
-\cite{meyer11} and publicized on SNIA \cite{ms}. The original dataset contains
-the Windows file system snapshots that span from September 5 to October 31,
-2009. Each snapshot is represented by the 40-bit chunk hashes under different
-average sizes obtained from Rabin fingerprinting \cite{rabin81}.  We focus on
-the snapshots that have been installed with the operating systems in the
-following categories: Windows 7 (Win7), Microsoft Windows Server 2003
-(Serv-03), Microsoft Windows Server 2008 (Serv-08), Microsoft Windows Vista
-Business Edition (Vista-B), and Microsoft Windows Vista Ultimate Edition
-(Vista-U). In each category, we pick four snapshots, each of which is
-configured with the average chunk size of 8KB.   
-\item 
-\textbf{VM:} This dataset is collected from a university programming course in
-Spring 2014. The original dataset includes a number of VM image snapshots for
-the students enrolled in the course, and each snapshot has a fixed size of
-10GB and is represented by the ordered list of SHA-1 hashes of 4KB fixed-size
-chunks. We focus on 6 users (i.e., User1-User6) and extract their snapshots
-into 13 weekly backups.  
-%Prior studies \cite{qin17, li15} have used some variants of the dataset for
-%different evaluation purposes, and we aim to validate the severity of the
-%clustering-based attack against VM disk images.   
-\end{itemize}
-
-Our datasets do not contain actual content, so we mimic the adversarial
-knowledge based on chunk hashes. Specifically, we use the ordered lists of
-chunk hashes in some snapshots as the auxiliary information $\mathbf{A}$ and
-the ground truth $\mathbf{M}$, respectively. To simulate encryption, we apply
-an additional hash function over each original chunk hash (that represents a
-plaintext) in $\mathbf{M}$, and truncate the result into an agreed number of
-bits specific to the used dataset. The truncated result mimics a ciphertext in
-$\mathbf{C}$. For each inferred ciphertext-plaintext pair $(C, M)$, we verify
-its correctness by applying the same simulated encryption on $M$ and comparing
-the result with $C$. Note that the clustering-based attack can operate at the
-segment level, and infer the ciphertext-plaintext segment pair $(S_\mathbf{C},
-S_\mathbf{A})$.  In this case, we check $(S_\mathbf{C}, S_\mathbf{A})$ by
-examining each ciphertext in $S_\mathbf{C}$ is exactly mapped from each
-plaintext in $S_\mathbf{A}$.
-
-% , although we cannot recover each chunk in the real attack.   
-% We count the leakage (see \S\ref{sec:threat}) of each ciphertext chunk, and use it for our inference attacks.  
-% MD5 on each hash (that represents a plaintext) in $\mathbf{M}$, and truncate the resulting hash into an agreed number of bits (e.g., 48-bit for FSL, 40-bit for MS, and 160-bit for VM).
-
-We measure the severity of the attacks by the inference rate and the inference
-precision (see Section~\ref{sec:threat}).
-
-\section{Results of Distribution-based Attack}
-\label{sec:experiment-distribution}
-
-\begin{figure*}[t]
-    \centering
-    \begin{tabular}{p{.31\textwidth}p{.31\textwidth}p{.31\textwidth}}
-        \multicolumn{3}{c}{\includegraphics[width=.7\textwidth]{pic/legend-fsl-line.pdf}} \smallskip \\
-        \includegraphics[width=.3\textwidth]{pic/distribution-impact-u.pdf} &
-        \includegraphics[width=.3\textwidth]{pic/distribution-impact-r.pdf} &
-	    \includegraphics[width=.3\textwidth]{pic/distribution-impact-t.pdf} \medskip \\
-        {\footnotesize 
-        \centering
-        (a) Impact of $u$: $r$ = 0; $t \rightarrow \infty$
-        } &
-        {\footnotesize
-        (b) Impact of $r$: $u$ = 128 for User004, User013 and User015, and $u$ = 256 for User007, User012 and User028; $t \rightarrow \infty$
-        } &
-        {\footnotesize
-        (c) Impact of $t$: $u$ = 128 for User004, User013 and User015, and $u$ = 256 for User007, User012 and User028; $r$ = 10
-        } \\
-    \end{tabular}
-    \caption{Experiment 1 (Impact of parameters): impact of $(u, r, t)$ in distribution-based attack.}
-    \label{fig:distribution-impact}
-\end{figure*}
-
-\paragraph{Experiment 1 (Impact of parameters):}
-We evaluate the impact of the parameters $(u, r, t)$ in the distribution-based
-attack. We drive our evaluation using the FSL dataset, and use the 12th weekly
-backup of each user as the auxiliary information to infer original plaintexts
-in corresponding 14th weekly backup.  We configure $t \rightarrow \infty$ and $r$ = 0 to
-evaluate the impact of $u$ (in this case, the distribution-based attack
-reduces to the locality-based attack \cite{li17}). Our rationale is to avoid
-the disturbances by other parameters.
-
-Figure~\ref{fig:distribution-impact}(a) shows the impact of $u$,
-when we vary $u$ from 2 to 512. Regarding inference rate, we have the same
-observation as the prior work \cite{li17}. Specifically, the inference rates
-first increase with $u$, since the attack can infer more ciphertext-plaintext
-pairs. After hitting the maximum values (e.g., 13.9\% for User004, 13.6\% for
-User007, 1.4\% for User012, 0.5\% for User013, 0.7\% for User015, and 6.1\%
-for User028), they decrease.  The reason is that the underlying frequency
-analysis introduces a large number of false positives that compromise the
-inferences over corresponding neighbors.
-
-The prior work \cite{li17} does not report the inference precision about the
-attack. We observe that the inference precisions for all users are at a
-fairly low level (e.g., less than 40\%), except the case of $u = 2$ for
-User028 that does not introduce any false positives. On the other hand, the
-inference rate in the special case is about 0.0001\%, meaning that the attack
-only infers a few ciphertext-plaintext pairs. In addition, as $u$ increases,
-the inference precisions decrease slightly. For example, when $u$ increases
-from 2 to 512, the inference precision of User004 drops from 30.7\% to 12.8\%.
-
-{\bf Observation (1) --} {\em A relatively larger $u$ increases the inference
-rate, yet it decreases the inference precision (i.e., more false positives are
-introduced). }
-
-Informed by the impact of $u$, we set $u$ at 128 for User004, User013 and
-User015, and at 256 for User007, User012 and User028, respectively, in order
-to evaluate the impact of $r$ and $t$. 
-% {\bf Note that the configuration
-% exceeds the best one that leads to the highest inference rate. PC: I don't
-% quite understand???} 
-Our rationale is to increase the coverage of inferred ciphertext-plaintext
-pairs, while we use $r$ and $t$ to filter possibly false positives.
-
-We first configure $t \rightarrow \infty$ and evaluate the impact of $r$. Figure~\ref{fig:distribution-impact}(b) shows the results. We observe that the
-inference rates of majority users increase with $r$. For example, when we vary
-$r$ from 0 to 16, the inference rates grow from 9.5\% to 16.0\%, from 10.0\%
-to 13.0\%, from 0.5\% to 0.7\%, and from 4.7\% to 5.6\% for User004, User007,
-User013, and User028, respectively. The reason is that the distribution-based
-attack addresses disturbances to frequency ranking, and infer more correct
-ciphertext-plaintext  pairs. On the other hand, the inference rates decrease
-slightly from 1.3\% to 0.8\% and from 0.6\% to 0.4\% for User012 and User015,
-respectively. The reason is that they examine a large range of plaintexts and
-may introduce more false positives. In addition, the inference precisions for
-all users are  at a low level (e.g., less than 45\%), and have similar
-tendencies with corresponding inference rates.
-
-{\bf Observation (2) --} {\em A larger $r$ provides more opportunities of
-identifying correct ciphertext-plaintext pairs, yet it also increases the
-probability of having false positives.}
-
-Then, we fix $r$ = 10 and evaluate the impact of $t$. 
-Figure~\ref{fig:distribution-impact}(c) shows the results. When $t$ is small
-(e.g., less than 0.5), we observe that the attack misjudges and filters a
-significant number of ciphertext-plaintext pairs, even they are correct. This
-introduces {\em false negatives} that reduce the inference rate. As $t$
-increases, the number of false negatives decreases.  When $t$ = 1.5, the
-inference rates hit the maximum values at 21.2\%, 18.2\%, 10.4\%, 1.2\%,
-1.2\%, and 13.5\% for User004, User007, User012, User013, User015, and
-User028, respectively. When $t$ further increases to 2, the corresponding
-inference rates drop to 20.5\%, 17.1\%, 8.3\%, 1.2\%, 1.0\%, and 11.2\%,
-respectively. The reason is that if $t$ is too large, it cannot filter false
-positives effectively. For the same reason, the inference precisions for all
-users decrease with $t$.  
-% The inference rates first  increase with $t$, since the number of false negatives (i.e., misjudge some correctly inferred ciphertext-plaintext pairs in filtering) are reduced.
-
-% implies that the distribution-based attack  returns more incorrect ciphertext-plaintext chunk pairs, which affects attack severity.
-
-{\bf Observation (3) --} {\em A smaller $t$ filters a large fraction of false
-positives, yet it introduces more false negatives.}
-
-\paragraph{Experiment 2 (Comparison with prior attack):}
-We compare the severity of the distribution-based attack with that of the
-locality-based attack \cite{li17}. In addition to using the FSL dataset like
-Experiment~1, we include the MS dataset for cross-dataset validation.
-Specifically, for each MS category, we choose two snapshots at a time, use one
-to infer the other, and evaluate the average inference rate and precision.
-
-We consider the following attack instances for comparison. 
-%
-\begin{itemize}[leftmargin=*]
-\item 
-$\tt Baseline$: We re-implement the locality-based attack based on the
-parameter configuration suggested in \cite{li17}. Specifically, it infers 5
-most frequent ciphertext-plaintext pairs in the first invocation (i.e., to
-initialize a set of ciphertext-plaintext pairs for iteration) of frequency
-analysis, and 30 in each following invocation (i.e., to iteratively infer ciphertext-plaintext pairs from 
- neighbors).  
-\item 
-$\tt Distribution$ and $\tt Distribution^S$: We consider two attack instances
-of the distribution-based attack, denoted by $\tt Distribution^S$ and ${\tt
-Distribution}$, which operate with and without size information,
-        respectively (i.e., the superscript $\tt S$ indicates that the attack instance operates with size information). 
-        We configure $\tt Distribution^S$ and ${\tt Distribution}$
-under the same configuration of  ${\tt Baseline}$. In addition, we choose
-$r$ and $t$ in both  $\tt Distribution^S$ and ${\tt Distribution}$ in the following way: for the FSL dataset, we fix $r$ = 10 for
-all users, and individually set $t$ = 1.5, 1.2, 1, 1, 0.7, and 0.9 for
-User004, User007, User012, User013, User015, and User028, respectively; for
-the MS dataset, we also fix $r$ = 10 for all categories, and set $t$ = 2 for
-Win7 and Serv-08, and $t$ = 1.6 for Vista-U, Serv-03, and Vista-B, respectively.
-This is informed by our tests for optimal configurations of the datasets.   
-\item 
-$\tt Distribution$-$\tt o$ and $\tt Distribution^S$-$\tt o$:
-We consider two additional distribution-based attack instances, denoted by $\tt Distribution$-$\tt o$
-and $\tt Distribution^S$-$\tt o$, which apply the same configurations for $r$ and $t$ as with $\tt Distribution$ and $\tt
-Distribution^S$, and further use larger $u$ to increase the
-coverage of inferred ciphertext-plaintext pairs.  
-        Specifically, we configure $u$ in $\tt Distribution$-$\tt o$
-and $\tt Distribution^S$-$\tt o$ in the following way:  
-        for the FSL
-dataset, we apply the same configuration of $u$ in Experiment~1; for the MS
-dataset, we set $u$ = 128 for Win7, and $u$ = 30 for Serv-03, Serv-08,
-Vista-B, and Vista-U. 
-        % Our rationale is to increase
-% the inference rate, while we expect  this only leads to a slight
-% degradation of the inference precision since the distribution-based attack
-% filters a large fraction of false positives. 
-\end{itemize}
-
-\begin{figure*}[t]
-    \centering
-    \begin{tabular}{c@{\hskip 2em}c}
-        \multicolumn{2}{c}{\includegraphics[width=.7\textwidth]{pic/legend-fsl-bar.pdf}} \smallskip \\
-        \includegraphics[height=2.1in]{pic/distribution-comparison-fsl.pdf} &
-        \includegraphics[height=2.1in]{pic/distribution-comparison-ms.pdf} \medskip \\
-        {\footnotesize 
-        (a) FSL dataset 
-        } &
-        {\footnotesize
-        (b) MS dataset 
-        } \\
-    \end{tabular}
-    \caption{Experiment 2 (Comparison with prior attack): comparison of attack severity for distribution-based attack and locality-based attack.}
-    \label{fig:distribution-comparison}
-\end{figure*}
-
-% \begin{itemize}[leftmargin=*]
-	% \item {\em Distribution-I:} We configure our proposed distribution-based attack with the {\em same} configuration of the baseline above.
-Informed by Experiment 3, we further choose the distribution-based ranking parameters in the following way: for the FSL dataset, we fix $r$ = 10 for all users, and individually set $t$ = 1.5, 1.2, 1, 1, 0.7, and 0.9 for User004, User007, User012, User013, User015, and User028; for the MS dataset, we fix $r$ = 10 for all categories, and configure $t$ as 2 for Win7 and Serv-08 and as 1.6 for Vista-U, Serv-03, and Vista-B, respectively.
-
-	% \item {\em Distribution-II:} We configure our proposed distribution-based attack with the same ranking configuration of distribution-I, while building on a larger $u$ to infer more chunk pairs.
-The rationale is to increase inference rate, while we expect the inference precision is degraded slightly as the attack can filter out unreasonable inferences.
-Specifically, for the FSL dataset, we set $u$ = 128 for User004, User013 and User015, and $u$ = 256 for User007, User012 and User028, respectively; for the MS dataset, we set $u$ = 128 for Win7, and $u$ = 30 for Serv-03, Serv-08, Vista-B, and Vista-U, respectively.
-% \end{itemize}
-
-Figure~\ref{fig:distribution-comparison}(a) shows the
-comparison results of the FSL dataset. We observe that different instances of
-the distribution-based attack outperform the locality-based attack in almost
-all cases. For example, regarding User028, the lowest inference rate of the
-distribution-based attack is 11.4\%, with the precision of 84.1\% (due to $\tt
-Distribution$), while the corresponding inference rate and precision of
-$\tt Baseline$ are only 1.2\% and 1.7\%, respectively; this implies that the distribution-based attack reduces the number of false postives by 82.4\% in this case.
-
-{\bf Observation (4) --} {\em The distribution-based attack significantly
-increases the inference precision, while achieving a higher inference rate than
-the locality-based attack.}
-
-$\tt Distribution^S$ and $\tt Distribution^S$-$\tt o$ have higher inference
-precisions than $\tt Distribution$ and $\tt Distribution$-$\tt o$,
-respectively, since they further filter false positives by size information.
-For example, for User004, $\tt Distribution^S$ and $\tt Distribution^S$-$\tt o$  reduce the fraction of false positives in  $\tt Distribution$ and $\tt Distribution$-$\tt o$ from 35.2\% to 1.7\% and from 35.3\% to 2.2\%, respectively.
-However, in the same case,
- we observe that the inference rates of $\tt Distribution$ and $\tt Distribution$-$\tt o$ are 20.0\% and 21.2\%, slightly higher than those of  
-$\tt Distribution^S$ and
-$\tt Distribution^S$-$\tt o$ by 2.0\% and
-0.4\%, respectively. The reason is that $\tt Distribution$ and $\tt
-Distribution$-$\tt o$ infer a small number of correct results from the
-neighbors of incorrect ciphertext-plaintext pairs. In other words,  although
-$(C, M)$ is an incorrect ciphertext-plaintext pair, the neighbors of $C$ may
-correspond to those of $M$ with a small probability.
-Even in this case, all distribution-based attack instances are more severe than the locality-based attack instance.
-Specifically, the inference rate of $\tt Baseline$ is only 15.2\%, lower than those of the best and the worst distribution-based attack instances by 6.0\% and 2.8\%, respectively.
-
-% For the same reason, $\tt Baseline$ has higher inference rate than $\tt Distribution^S$ in User013.
-
-{\bf Observation (5) --} {\em Filtering incorrect inference results improves
-the inference precision, yet it degrades the coverage of inferred
-ciphertext-plaintext pairs and possibly decreases the inference rate.
-}
-
-We further observe that although $\tt Distribution$-$\tt o$ and $\tt
-Distribution^S$-$\tt o$ build on larger $u$, their inference rates are just
-slightly higher than those of $\tt Distribution$ and $\tt Distribution^S$ by
-0.4\% and 0.9\%, respectively. The reason is that the distribution-based
-attack iterates inference just through neighbors, and has a bounded coverage
-of inferred ciphertext-plaintext pairs. The further increase of $u$ only adds
-a small number of new correct  ciphertext-plaintext pairs into results.
-
-Figure~\ref{fig:distribution-comparison}(b) shows the
-results of the MS dataset. Both locality-based and distribution-based attacks
-have high inference rates and precisions in most MS categories (except Win7).
-The possible reason is that MS snapshots are highly correlated (e.g., the
-variance of the total number of chunks is small, as shown in
-Table~\ref{tab:dataset}).  We observe that the distribution-based attack still
-outperforms the locality-based attack. For example, in Vista-U, the inference
-rates and precisions of all inferences of the distribution-based attack are
-above 24.1\% and 96.4\%, while those of $\tt Baseline$ are 21.7\% and 87.1\%,
-respectively.
-
-Note that both  distribution-based and  locality-based attacks have low
-inference rates (e.g., less than 0.01\%) in the Win7 category. The reason is
- that Win7 includes a large fraction (e.g., more than 98.8\%, as shown in
-Table~\ref{tab:dataset}) of unique chunks, which cannot be correctly
-inferred by the frequency analysis attacks.
-
-% We do not include Win7  in the comparison, since all attack instances have low effectiveness. We observe all attacks have higher severity than those in the FSL dataset.
-
-\begin{figure*}[t]
-     \centering
-    \centering
-    \begin{tabular}{c@{\hskip 2em}c}
-        \multicolumn{2}{c}{\includegraphics[width=.25\textwidth]{pic/legend-effectiveness.pdf}} \smallskip \\
-        \includegraphics[height=2.2in]{pic/distribution-effectiveness-wo-size.pdf} &
-	\includegraphics[height=2.2in]{pic/distribution-effectiveness-w-size.pdf} \medskip \\
-        {\footnotesize 
-        (a) Distribution-based attack without size information  
-        } &
-        {\footnotesize
-        (b) Distribution-based attack with size information 
-        } \\
-    \end{tabular}
-	\caption{Experiment 3 (Attack effectiveness): severity of distribution-based attack in FSL dataset.}
-	\label{fig:experiment-distribution-effectiveness}
-\end{figure*}
-
-\paragraph{Experiment 3 (Attack effectiveness):} We consider a long-term
-backup scenario and examine the effectiveness of the distribution-based attack
-with the FSL dataset. Specifically, we choose the $i$th FSL weekly backup of
-each user as the auxiliary information to infer original plaintexts in the corresponding $(i+w)$th FSL
-weekly backup. Clearly, the smaller $w$ is, the higher correlation between the
-auxiliary information and the target backup will be.  We configure the two  
-distribution-based attack instances $\tt Distribution$-$\tt o$ and $\tt Distribution^S$-$\tt o$
-like Experiment~2, and evaluate their inference rates and inference precisions that
-are averaged for all available $i$ for each user.
-
-Figure~\ref{fig:experiment-distribution-effectiveness}(a) shows the results. The
-distribution-based attack has varying inference rate and precision  across
-users. For example, in the favorable case like User004, it achieves the
-highest inference rates of 24.8\%, 24.5\%, and 24.0\% with the precisions of
-67.3\%, 67.0\%, and 66.5\% for $w$ = 1, 2, and 3, respectively; in the
-non-favorable case like User015, the inference rate of the distribution-based
-attack is only around 0.3\%. The possible reason is that the backup data from
-User015 has low chunk locality.
-
-In addition, we observe that the correlation (i.e., $w$) of the auxiliary
-information has low impact on the effectiveness of the distribution-based
-attack.  For example, when $w$ increases from 1 to 3, it only leads to limited
-degradations on inference rate (e.g., less than 1.4\%) and precision (e.g.,
-less than 5.6\%). The reason is that the distribution-based attack addresses
-disturbances to frequency ranking and preserves attack effectiveness.
-
-{\bf Observation (6) --} {\em The distribution-based attack can limit the
-degradation of attack effectiveness in the presence of loosely correlated
-auxiliary information.}
-
-% We also use the instance in Experiment 2 to evaluate the effectiveness of the distribution-based attack that operates with
- % size information. 
- Figure~\ref{fig:experiment-distribution-effectiveness}(b) shows the results of $\tt Distribution^S$-$\tt o$. We observe that it has similar inference rate with $\tt Distribution$-$\tt o$,  
- while achieving much higher precision. For example, the average inference precision of all users are 93.1\%, 92.8\%, and 92.4\% for $w$ = 1, 2, and 3, respectively.
-
-% Figure~\ref{fig:experiment-distribution-severity-ms} shows the attack results of the MS dataset.
-The distribution-based attack achieves high severity.
-For example, it can infer 24.0\% of unique chunks in Vista-U with a precision of 96.2\%.
-
-% Although there is l
-
-\section{Results of Clustering-based Attack}
-\label{sec:experiment-clustering}
-
-\paragraph{Experiment 4 (Impact of parameter):} We first evaluate the impact
-of the parameter $k$, which defines the upper bound distance
-in combining the closest clusters.  We use both the FSL and the VM datasets to
-study how $k$ affects the underlying clustering scheme in the attack.
-Specifically, we apply segmentation on the last backup of each considered FSL
-and VM user, respectively, and generate the segments that have a fixed size of
-4MB.
-
-The clustering scheme aims to aggregate similar ciphertext segments into the
-same cluster, without compromising the confidentiality of chunks in each
-ciphertext segment.  To quantify its effect, we compare the results of
-clustering with those of a {\em real} classification approach, which directly
-classifies segments by their minimum chunk hash.  Suppose we generate $m$ real
-classes of segments by classification, and $\widetilde{m}$ clusters by the
-clustering scheme, respectively.  We consider {\em clustering closeness},
-evaluated by $\frac{{\sf abs}(m-\widetilde{m})}{m}$ (where 
-${\sf abs}(m-\widetilde{m})$ returns the absolute value of $m-\widetilde{m}$),
-which quantifies how the  number of clusters approximates that of real
-classes. In addition, let $\hat{m}$ be the number of clusters, in which all
-segments are similar (i.e., have the same minimum chunk hash). We also
-consider {\em clustering correctness}, evaluated by
-$\frac{\hat{m}}{\widetilde{m}}$, which quantifies how precisely the clustering
-scheme groups similar segments.
-
-Figure~7(a) shows the results of the FSL dataset, where we
-consider four FSL users (e.g., User004, User007, User015 and User028) for
-saving evaluation time. The clustering closeness first increases with $k$,
-since the number (i.e., $\widetilde{m}$) of clusters decreases and
-approximates $m$. When $k$ increases further, the number of clusters drops
-away from $m$, and leads to the increase of clustering closeness.  In
-addition, we observe that the clustering correctness gradually decreases with
-$k$, because some of non-similar segments (i.e., their minimum chunk hashes are
-different) are aggregated into the same cluster. Both results suggest that we
-can configure an appropriate $k$ to balance the closeness and correctness of
-clustering. For example, when we set $k$ = 0.65 for User015, the corresponding
-closeness and correctness are 1.0\% and 94.2\%, respectively. This implies
-that the results of the clustering scheme  highly approximates
-those of real classification.
-
-{\bf Observation (7) --} {\em By configuring an appropriate $k$ for
-clustering, we  approximate the results of  classifying segments, without the knowledge of  minimum chunk hash in each
-segment.}
-
-Figure~7(b) shows the results of the VM dataset. We observe
-that the clustering closeness and correctness of all VM users have  similar
-tendencies with those of FSL users. When we configure $k$ = 0.8, the average
-clustering closeness of all VM users is only 3.0\%, while the corresponding
-clustering correctness is as high as 93.1\%.
-
-\begin{figure*}[t]
-\centering
-    \begin{tabular}{cc@{\hspace{0.3in}}p{.32\textwidth}}
-    \includegraphics[width=.3\textwidth]{pic/clustering-impact-d-fsl.pdf} &
-    \includegraphics[width=.3\textwidth]{pic/clustering-impact-d-vm.pdf} & 
-    \includegraphics[width=.3\textwidth]{pic/clustering-effectiveness.pdf} \medskip \\
-{\footnotesize 
-        (a) FSL dataset } 
-&
-{\footnotesize 
-        (a) VM dataset } 
-        &  ~~~ \medskip \\
-        \multicolumn{2}{p{.64\textwidth}}{
-            \footnotesize Fig.~7\quad Experiment 4 (Impact of parameter): impact of $k$ in the clustering scheme; for clustering closeness, the smaller the better; for clustering correctness, the larger the better.
-} &
-        % \multicolumn{2}{c}{\footnotesize Fig.~6\quad Experiment 4 (Impact of parameter): show impact of $d$ with clustering closeness and correctness; for clustering closeness, the smaller the better; for clustering correctness, the larger the better.} &
-        {\footnotesize
-Fig.~8\quad Experiment 5 (Attack effectiveness):  severity of clustering-based attack in VM dataset.
-        }
-\end{tabular}
-    \hspace{-1in}
-\end{figure*}
-
-% \begin{figure}
-% 	\includegraphics[width=.48\textwidth]{pic/clustering-impact-d.pdf}
-% 	\caption{Experiment 6 (Impact of parameter).}
-% 	\label{fig:experiment-clustering-impact}
-% \end{figure}
-
-\begin{table*}[!t]
-\small
-    \caption{Experiment 6 (Security implications)}
-\renewcommand{\arraystretch}{1.2}
-\vspace{-3pt}
- \begin{minipage}[t]{0.7\textwidth}
-\centering
-        (a) Distribution-based attacks \medskip \\
-\begin{tabular}{|c|c|c|c|c|c|}
-\hline
-
-    \multirow{2}{*}{\bf Type} & \multirow{2}{*}{\bf Extension Name} & \multirow{2}{*}{\bf \centering Range of File Size}  & \multicolumn{2}{c|}{\bf Raw Inference Rate} \\ \cline{4-5} 
-    & & &  $\sf Distribution$-$\sf o$ & $\sf Distribution^S$-$\sf o$ \\ \hline
-\hline
-    Office & doc(x), ppt(x), xls(x) & 10KB-1MB   & 4.9\% & 5.3\%\\
-\hline
-    Picture & jpg, png &10-100KB  & 7.7\% & 6.7\% \\
-\hline
-    Source & c, h, cpp, java, py & 10-20KB   & 17.1\% & 15.0\%\\
-% \hline
-	% Library & .a, .dll, .so \\
-% \hline
-	% Compression & .bz2, .gz, tar, rar, zip, 7z \\
-\hline
-    Database & db, po & 20-700KB   & 2.6\% & 2.4\%\\
-\hline
-    Disk & vmdk, img & 200MB-1GB  & 15.8\% & 16.7\%\\
-\hline
-\end{tabular}
-\label{tab:file}
- \end{minipage}
-\hfill
-    \begin{minipage}[t]{0.3\textwidth}
-    \centering
-        (b) Clustering-based attack \medskip \\
-    \begin{tabular}{|c|c|}
-    \hline
-        {\bf Users} & {\bf Raw Inference Rate} \\
-    \hline
-    \hline
-        1 & 13.2\% \\ 
-    \hline
-        2 & 22.4\% \\ 
-    \hline
-        3 & 25.7\% \\ 
-    \hline
-        4 & 28.4\% \\ 
-    \hline
-        5 & 18.5\% \\ 
-    \hline
-        6 & 30.8\% \\ 
-    \hline
-    \end{tabular}
-\label{tab:user}
-    \end{minipage}
-
-\end{table*}
-
-\paragraph{Experiment 5 (Attack effectiveness):} We now study the
-effectiveness of the clustering-based attack. Due to the boundary shift of
-fixed-size segment, it has low effectiveness
-(about 1\% inference rate in our test) against the FSL dataset.  Thus, we use
-the VM dataset to examine its severity. To configure the attack, we set $k$ =
-0.8 for clustering, and $(u, r, t)$ = (5000, 100, 0.5) for relating ciphertext
-clusters to corresponding plaintext clusters.
-
-In our micro-benchmarking, we find that the chunk-level inference in the
-clustering-based attack only infers thousands of chunks correctly, which
-contributes to a negligible inference rate (e.g., less than 0.01\%).  
-% The
-% reason is that each cluster includes a large number of chunks, and frequency
-% analysis is ineffective in this case. 
-Thus, we focus on the
-segment-level inference, which presents the bottom line of severity in the
-clustering-based attack. To be consistent with the chunk-level measurements, we count inference rate and precision based
-on the unique chunks in each correctly inferred segment.
-
-We use the same evaluation methodology of Experiment~3, and report the results
-in Figure~8. Specifically, the x-axis describes the index $i$ (where 1 $\leq i \leq$
-12) of the VM backup that is used as the auxiliary information for attack,
-while the y-axis presents the average inference rate or precision of all VM
-users against the $(i+w)$th backup (where $w$ = 1, 2, and 3). We observe that both the inference rate and the inference
-precision fluctuate significantly. For example, when using the 3rd backup as
-the auxiliary information, the attack achieves the highest inference rates at
-18.1\%, 17.1\% and 16.3\%, with the precisions of 76.8\%, 75.0\% and 73.0\%
-for $w$ = 1, 2, and 3, respectively. 
-On the other hand, when using the 7th
-backup as the auxiliary information, the corresponding inference rates and
-precisions drop down to 9.6\% and 65.9\%, 6.8\% and 71.2\%, and 6.9\% and
-75.6\%, respectively. The reason is that the VM users have heavy updates after
-the 7th week, and this reduces the correlation  of adjacent backups. 
-On
-average, for $w$ = 1, 2 and 3, the clustering-based attack infers 15.8\%,
-14.0\%, and 12.6\% ciphertext-plaintext pairs, with the precisions of 71.1\%,
-69.1\%, and 68.9\%, respectively. 
-% This demonstrates high severity against
-% the VM disk images.
-
-\section{Results of Security Implications}
-\label{sec:case}
-We thus far have examined the severity of inference attacks by quantifying the
-correctly inferred ciphertext-plaintext pairs.  However, it remains an open
-issue that what are the security implications informed by these results and
-how the frequency analysis attacks bring actual damage. In the following
-experiment, we evaluate the security implications of our attacks based on the
-{\em raw inference rate}, defined as the percentage of raw data content
-affected by correctly inferred chunks.
-
-\paragraph{Experiment 6 (Security implications):}
-We first consider the distribution-based attack, and evaluate its raw
-inference rate against {\em different types} of files. We drive the evaluation
-using the FSL dataset, since only the FSL dataset includes file metadata (that
-includes the extension names of files) in plaintext. Specifically, we focus on
-five types of files that have specific extension names (see
-Table~\ref{tab:file}(a)): office files ({\em Office}), picture files 
-({\em Picture}), programming source files ({\em Source}), database files 
-({\em Database}), and disk image files ({\em Disk}). These files occupy more
-than 60\% of raw content of FSL snapshots.
-
-We apply the methodology of Experiment~2, and evaluate the raw inference
-rates of $\sf Distribution^S$-$\sf o$ and $\sf Distribution$-$\sf o$. 
-Table~\ref{tab:file}(a) shows the results. Both attack instances have high raw
-inference rates against {\em Disk} (e.g., 15.8\% for 
-$\sf Distribution$-$\sf o$ and 16.7\% for $\sf Distribution^S$-$\sf o$),
-because each disk file includes a large number of rarely updated chunks that
-form high locality within the same file. Interestingly, we observe that 
-{\em Source}, although each file is of a small size, also incurs high raw
-inference rates by the distribution-based attacks (e.g., 17.1\% for 
-$\sf Distribution$-$\sf o$ and 15.0\% for $\sf Distribution^S$-$\sf o$). The
-reason is that programming source files are often stored together in file system
-(e.g., the source files that belong to the same project locate in an identical
-directory) and form a large stretch of correlated chunks, which present high
-locality across files. For small and scattered files (e.g., {\em Office}, 
-{\em Picture}, and {\em Database}), the distribution-based attacks have
-relative low raw inference rates.
-
-{\bf Observation (8) --} {\em The severity of the distribution-based attack depends on the update frequencies, sizes, and spatiality of target files. }
-
-We examine the security implication of the clustering-based attack using the
-VM dataset. Specifically, we use the 11th  backup of each VM user  to infer original content in corresponding 13th VM
-backup. Since the VM dataset does not contain any metadata, we count the raw
-inference rate based on the  whole data content in each VM snapshot.
-Note that we filter all zero chunks in the count of raw inference rate,
-because they occupy a large fraction in VM disk images \cite{jin09}.
-
-% switch to the clustering-based attack, and infer the content of the last (i.e., the 13th) VM backup based on the corresponding 11th backup.
-Since the VM dataset does not contain metadata, we evaluate the raw inference rate across different users.
-Specifically, like Experiment 7, we only consider segment-level attack for high precision, and count the raw inference rate based on the correctly inferred segments.
-Note that since VM images commonly contain a large fraction of zero chunks ,  we filter out the zero segments in our inferred raw content.
-
-We use the same configuration of Experiment~5, and evaluate raw inference rate
-based on segment-level inference.  Table~\ref{tab:user}(b) shows the results
-for different users.  We observe that the clustering-based attack achieves high
-severity against the VM dataset. For example, it infers up to 30.8\% raw
-content of User6's VM backup. On average, the raw inference rate of all users
-is as high as 23.2\%.  
-% a relatively high raw inference rate.  On average, the raw inference rate is 23.2\% for all users.
-
-{\bf Observation (9) --} {\em The clustering-based attack threatens the
-confidentiality of VM disk images. }
-
-\chapter{Countermeasure Discussion}
-\label{sec:countermeasure}
-
-In this section, we discuss the advantages and disadvantages of possible countermeasures against the leakage channels exploited in this paper.
-Note that the countermeasures against size leakage are not enough for preventing our attacks, in which the size information is just optional.
-
-\paragraph{Against frequency leakage:}
-MinHash encryption \cite{qin17, li17} encrypts each plaintext with a key derived from the minimum chunk hash over a set of its adjacent chunks, and possibly maps identical plaintexts into  different ciphertexts.
-The rationale for defense is that MinHash encryption changes frequencies, and disturbs frequency ranking.
- Note that MinHash encryption also prevents the frequency analysis attacks in this paper, because  we target deterministic encryption (e.g., MLE \cite{bellare13a}), while MinHash encryption is non-deterministic and changes the  frequency distribution of chunks.
-The disadvantage is that MinHash encryption degrades the storage saving by deduplication, since it breaks the one-to-one mapping between plaintexts and ciphertexts.
-In addition, MinHash encryption is not an active countermeasure, since its randomness essentially depends on the minimum chunk hashes in the target workloads.
-
-% (rather than the chunk itself \cite{bellare13a}) over its adjacent chunks, so that some identical plaintext chunks can be encrypted into different ciphertext chunks.
-The rationale of defense is MinHash encryption {\em changes the frequencies of chunks} and leads to rank disturbances in classical frequency analysis.
-In addition, the nature of MinHash encryption is {\em non-deterministic}, and prevents the distribution-based ranking (see \S\ref{sec:distribution-attack-description}) that targets deterministic encryption.
-On the other hand, MinHash encryption is not an {\em active} countermeasure, since its defense effectiveness is dominated by workload characteristics (i.e., depending on the diversity of MinHash).
-It also degrades deduplication effectiveness due to breaking the one-to-one mapping between plaintexts and ciphertexts.
-
-A recent work \cite{zuo18} suggests intentionally adding duplicate chunks to prevent traffic analysis against client-side deduplication.
-The approach \cite{zuo18} can be applied to address the frequency analysis attacks, since it changes the frequencies of chunks.
-Compared with MinHash encryption, the countermeasure \cite{zuo18} does not degrade storage efficiency, since only duplicate chunks are added.
-On the other hand, it  requires the priori knowledge that if particular chunks are duplicate, and only suits the client-side deduplication, which possibly introduces additional leakage channels (see Section~\ref{sec:related}).
-
-Several extended MLE instantiations build on strong cryptographic primitives to defend against the frequency leakage of encrypted deduplication, such as randomized encryption that supports equality testing \cite{abadi13}, hybrid encryption \cite{stanek14}, and interactions with fully homomorphic encryption \cite{bellare15}.
-They provide provable security, yet how they can be implemented and deployed in practice remains unexplored.
-
-% yet how they are implemented and deployed in practice remains unexplored. 
-% some random encryption schemes \cite{stanek14,bellare15,abadi13,lacharite18a}  address the frequency leakage of deterministic encryption.
-Other than the practical approaches \cite{qin17, li17, zuo18}, they provide provable security, yet building on computationally expensive primitives.
-% % (see Section~\ref{sec:related}).
-
-% are proposed to address frequency leakage from cryptography aspect, yet they are not readily implemented in practice .
-
-% Some studies \cite{stanek14,abadi13,bellare15} aim to achieve stronger security than the more practical schemes focused above.
-Stanek {\em et al.} \cite{stanek14} design a hybrid encryption scheme where unpopular messages are protected by semantically secure encryption for high security guarantee, while popular messages are protected by CE to enable deduplication.
-On the other hand, the scheme \cite{stanek14} builds on public-key primitive which is inefficient for encrypting large-size messages.
-Abadi {\em et al.} \cite{abadi13} construct two schemes for the messages whose distributions are publicly available.
-Their first scheme generates  random tags and ciphertexts to prevent frequency leakage, yet incurring expensive {\em equality test} for checking duplicates.
-Their second scheme produces deterministic ciphertexts, and exposes the frequencies of corresponding plaintexts.
-Interactive MLE \cite{bellare15} introduces interactions into encrypted deduplication, and strengthens the security of both correlated and parameter-dependent messages, yet it is impractical for the use of fully homomorphic encryption.
-On the contrary to these theoretical contributions \cite{stanek14, abadi13, bellare15}, this paper focuses on the applied aspect, and investigates the security vulnerabilities in practical deduplication.
-
-\paragraph{Against order leakage:}
-A simple countermeasure is to disturb the deduplication processing sequence of chunks.
-For example, we can operate an additional order-scrambling process on the stream of plaintexts before encryption, so as to hide the actual logical order of each plaintext.
-This prevents the distribution-based attack, because the adversary cannot identify neighboring information correctly.
-On the other hand, it is not always effective against the clustering-based attack.
-If scrambling  operates on just a small basis (e.g., the orders of plaintexts in each segment are scrambled), the clustering-based attack still works.
-The disadvantage of the order-scrambling countermeasure is that it breaks chunk locality and leads to performance drop in large-scale deduplication \cite{xia11,zhu08,lillibridge09}.
-
-% On the other hand, if we operate scrambling        
-% {\em scrambling}, which intentionally disturbs the deduplication processing sequence of chunks. 
-% operates the stream  before deduplication and disturbs the order of each plaintext. 
-% disturbs the orders of plaintexts before deduplication 
-% to scramble the orders of plaintexts. Specifically, the scrambling approach , and randomly changes the order of each plaintext.   
-% A countermeasure is to scramble the orders of chunks, so as to prevent adversary from learning the actual order of each chunk.
-One note is the scrambling countermeasure should be applied by taking similarity into account; otherwise, the adversary can exploit the property for inference attack (see \S\ref{sec:clustering-attack}).
-For example, applying scrambling in a small basis (e.g., within a segment) is not enough for preventing the clustering-based attack.
-On the other hand, large-scale scrambling breaks chunk locality completely, and leads to significant degradation of deduplication performance .
-
-\paragraph{Against size leakage:}
-As suggested by prior work \cite{ritzdorf16}, we can pad each plaintext with additional data to obfuscate the actual size of this plaintext.
-However, we note that the padding scheme is not straightforward, since it requires to add identical redundancies to the same plaintexts; otherwise the storage system cannot detect duplicates for deduplication.
-One possible solution is to build on the paradigm of MLE \cite{bellare13b,bellare13a}.
-We compute the cryptographic hash of each plaintext as a seed, and use it to generate variable-size pseudorandom data to be padded with the  plaintext.
-Like MLE, this solution comes at the expense of server-aided approach \cite{bellare13b} to defend against brute-force attack (see Section~\ref{sec:related}).
-
-% A countermeasure is to sacrifice storage efficiency and {\em pad each chunk with additional data}, which can obfuscate the original size of this chunk.
-The padding scheme is not straightforward, as it is required to {\em add identical redundant data to the same chunks}; otherwise, the server cannot detect duplicates for deduplication.
-One possible solution is based on the spirit of MLE \cite{bellare13b,bellare13a}.
-% Specifically, we compute the cryptographic hash of each chunk as a seed, and use the seed to generate variable-size pseudorandom data to be padded with the corresponding chunk.
-Like MLE, this solution comes at the expense of server-aided approach \cite{bellare13b} to defend against brute-force attack (see \S\ref{sec:related}).
-
-  Instead of variable-size chunking, we can use fixed-size chunking to 
- generate equal-size chunks for deduplication.
-Since all chunks have the same size, the adversary cannot exploit size information to differentiate them.
-Although fixed-size chunking suffers from boundary shift, it achieves almost the same storage saving of deduplication as variable-size chunking in VM disk images \cite{jin09}.
-Thus, we suggest applying fixed-size chunking in its favorable workloads to prevent size leakage.
-
-  % make the leaked size information hard to be exploited for inference attack.
-It suffers from the shift of chunk boundaries and is less effective for majority workloads, while prior work \cite{jin09} shows fixed-size chunking achieves almost the same storage efficiency as variable-size chunking for VM disk images.
-
-% , although does not address size leakage explicitly, can make the available size information hard to be exploited for inference attack.
-On the other hand, it sacrifices deduplication effectiveness in most of storage workloads due to the shift of chunk boundaries.
-
-\chapter{Related Work}
-\label{sec:related}
-
-\noindent
-{\bf MLE instantiations:}  
-Recall from Section~\ref{sec:background} that MLE \cite{bellare13a} formalizes the
-cryptographic foundation of encrypted deduplication.  The first published MLE
-instantiation is convergent encryption (CE) \cite{douceur02}, which uses the
-cryptographic hash of a plaintext and its corresponding ciphertext as the
-MLE key and the tag, respectively.  Other CE variants include: hash convergent
-encryption (HCE) \cite{bellare13a}, which derives the tag from the plaintext
-while still using the hash of the plaintext as the MLE key; random convergent
-encryption (RCE) \cite{bellare13a}, which encrypts a plaintext with a fresh
-random key to form a non-deterministic ciphertext, protects the random key by
-the MLE key derived from the hash of the plaintext, and attaches a
-deterministic tag derived from the plaintext for duplicate checks; and
-convergent dispersal (CD) \cite{li15}, which extends CE to secret sharing by
-using the cryptographic hash of a plaintext as the random seed of a secret
-sharing algorithm.  Since all the above instantiations derive MLE keys and/or
-tags from the plaintexts {\em only}, they are vulnerable to the offline
-brute-force attack \cite{bellare13b} if the plaintext is {\em predictable}
-(i.e., the number of all possible plaintexts is limited) , as an adversary can
-exhaustively derive the MLE keys and tags from all possible plaintexts and
-check if any plaintext is encrypted to a target ciphertext (in CE, HCE, and
-CD) or mapped to a target tag (in RCE).  The brute-force attack has been
-demonstrated to learn file information \cite{ce_attack}.
-
-%Suppose an adversary learns  that the underlying message of a target
-%ciphertext is drawn from a publicly available set. To recover the underlying
-%message, the adversary tries each possible message from the public set,
-%derives corresponding MLE key, and uses the derived key to decrypt the
-%target ciphertext. If the decryption result equals the tried message, the
-%adversary can deduce the underlying message.
-
-% {\em HCE1} and {\em HCE2} \cite{bellare13a} derive tag from client side, and
-% upload it along with ciphertext for deduplication. They offer better
-% performance for the storage system, which can simply read the tag from
-% uploads rather than computing it by hashing a possibly long ciphertext.
-% {\em Random convergent encryption (RCE)} \cite{bellare13a} encrypts a
-% message with a fresh random key, and protects the random key with the  MLE
-% key of the message. RCE is more efficient, since it can combine both
-% encryption and key generation into a single concerted pass over the message
-% \cite{bellare13a}. On the other hand, RCE needs to attach a deterministic
-% tag to the random ciphertext for checking duplicates. In addition to
-% improving performance, {\em convergent dispersal} \cite{li15} replaces the
-% random input of secret sharing by the cryptographic hash of message, so as
-% to  augment CE with fault-tolerate storage.
-
-% CE has been implemented in a wide variety of storage systems \cite{adya02, elephantdrive, mega, gnunet, freenet, cryptosphere, cox02, storer08, anderson10}.
-
-% compute the tag $T = {\sf H}({\sf H}(M))$ as a double hash over plaintext message, and require to upload $T$ along with ciphertext for efficient deduplication. 
-% A special note is RCE needs to places an appropriate tag along with ciphertext for deduplication, since its ciphertext is random. 
-% Like HCE1 and HCE2, RCE , and 
-% the message encryption and MLE key derivation of RCE can be combined into a single concerted pass over the possibly long message.
-
-To protect against the offline brute-force attack, DupLESS \cite{bellare13b}
-implements server-aided MLE by managing MLE keys in a standalone key server,
-which ensures that each MLE key cannot be derived from a message offline.
-DupLESS employs two mechanisms to achieve robust MLE key management: (i)
-oblivious key generation, in which a client always obtains a deterministic MLE
-key for a message from the key server without revealing the message content to
-the key server, and (ii) rate limiting, which limits the key generation
-requests from the client and prevents the online brute-force attack.  Other
-studies extend server-aided MLE to address various aspects, such as reliable
-key management \cite{duan14}, transparent pricing \cite{armknecht15},
-peer-to-peer key management \cite{liu15}, and rekeying \cite{qin17}.  However,
-server-aided MLE still builds on deterministic encryption.  To our
-knowledge, existing MLE instantiations (based on either CE or server-aided
-MLE) are all vulnerable to the inference attacks studied in this paper.
-
-%In addition, existing MLE instantiations lack active protection against the
-%size 
-%vulnerabilities explored in this paper, since they generate deterministic
-%ciphertexts or tags for deduplication. In addition, they lack active
-%protection against the size and order leakages, which can be exploited to
-%increase the severity of frequency analysis.
-
-%SS \cite{bellare13b}, follow-up studies (see \cite{shin17} for a complete
-%survey) address additional issues, including . Liu {\em et al.} \cite{liu15}
-%propose to encrypt each message with a random key, and share the key among
-%the clients that have the same message. This prevents brute-force attack due
-%to the use of random keys, while mitigating security dependence on a global
-%secret.
-
-% All above MLE instantiations transform identical message to the same ciphertext or tag, and hence incur the frequency leakage.
-They also lack of active protection against the size and order leakages.
-% via password-based key exchange. This addresses , and also prevents brute-force attack. 
-% Liu {\em et al.} \cite{liu15} propose to share encryption keys via a password-based key exchange protocol, so as to mitigate the dependence of the key manager.
-All above works apply deterministic encryption and are susceptible to frequency leakage.
-They also lack of active protection against the size and order leakages.
-
-\paragraph{Attacks against (encrypted) deduplication:} In addition to the
-offline brute-force attack, previous studies consider various attacks against
-deduplication storage, and such attacks generally apply to encrypted
-deduplication as well.  For example, the side-channel attack
-\cite{harnik10,halevi11} enables adversaries to exploit the deduplication
-pattern to infer the content of uploaded files from target users or gain
-unauthorized access in client-side deduplication; it is shown that the
-side-channel attack (and other related attacks) was successfully launched
-against Dropbox in 2010 \cite{mulazzani11}.  The duplicate-faking attack
-\cite{bellare13a} compromises message integrity via inconsistent tags.
-Ritzdorf {\em et al.} \cite{ritzdorf16} exploit the leakage of the chunk size
-to infer the existence of files.  The locality-based attack \cite{li17}
-exploits frequency analysis to infer ciphertext-plaintext pairs.  Our
-work follows the line of work on inference attacks \cite{ritzdorf16,li17}, yet
-provides a more in-depth study of inference attacks against encrypted
-deduplication via various types of leakage.
-
-%Our distribution-based attack inherently implies the prior attack \cite{li17}
-%(see \S\ref{sec:distribution-attack-description}). We also propose the
-%clustering-based attack that does not need the knowledge of fine-grained
-%chunk orders.  
-\paragraph{Defense mechanisms:} 
-Section~\ref{sec:countermeasure} discusses the countermeasures agasint the frequency, order and size leakage of encrypted deduplication. 
-Additional defense mechanisms are designed to protect against other types of attacks.  
-% Several countermeasures are designed to defend
-% against the attacks on encrypted deduplication.  
-As mentioned above,
-server-aided MLE \cite{bellare13b} can defend against the offline brute-force
-attack. Server-side deduplication \cite{li15,harnik10,armknecht17} and
-proof-of-ownership \cite{xu13,pietro12,halevi11} can defend against the
-side-channel attack.  Server-side tag generation \cite{douceur02,bellare13b}
-and guarded decryption \cite{bellare13a} can defend against the
-duplicate-checking attack.
-
-% MinHash encryption \cite{qin17} disturbs the
-% frequency ranking of ciphertexts and is shown to defend against the frequency
-% analysis based on the locality-based attack via trace analysis.  Several
-% extended MLE instantiations build on strong cryptographic primitives to defend
-% against the inference attacks, such as randomized encryption that supports
-% equality testing \cite{abadi13}, hybrid encryption \cite{stanek14}, and
-% interactions with fully homomorphic encryption \cite{bellare15}, yet how they
-% are implemented and deployed in practice remains unexplored.
-
-\paragraph{Inference attacks:}  Several inference attacks have been proposed
-against encrypted databases
-\cite{grubbs17,bindschaedler17,kellaris16,durak16,naveed15,lacharite18} and 
-keyword search \cite{zhang16b,grubbs16,pouliot16,cash15,islam12}.  They all
-exploit the deterministic encryption nature to identify different types of
-leakage.  Our work differs from them by specifically focusing on frequency analysis against encrypted
-deduplication.
-
-%construct inference attacks against encrypted databases. Naveed {\em et al.}
-%\cite{naveed15} propose attacks to recover the plaintext records of {\em
-%CryptDB} \cite{popa11a}. Kellaris {\em et al.} \cite{kellaris16} and
-%Lacharite {\em et al.} \cite{lacharite18} analyze the volumes of the data
-%returned by range queries, and present generic reconstruction attacks on
-%database entries. Grubbs {\em et al.} \cite{grubbs16}, Bindschaedler {\em
-%et al.} \cite{bindschaedler17}, and Durak {\em et al.} \cite{durak16}
-%show how to recover the plaintexts from the database column encrypted by
-%order-revealing encryption. 
-%
-%target keyword search.
-Islam {\em et al.} \cite{islam12} exploit the leakage of access pattern, and recover the plaintext keywords associated with files.
-Cash {\em et al.} \cite{cash15} and Pouliot \cite{pouliot16} examine the security of searchable encryption under different leakage profiles.
-Zhang {\em et al.} \cite{zhang16b} propose file-injection attacks to recover searchable keywords.
-Grubbs \cite{grubbs16} build attacks against {\em Mylar} \cite{popa14} that is a practical system with keyword search enabled.
-This paper differs from the above works \cite{grubbs17,bindschaedler17,kellaris16,durak16,naveed15,lacharite18,zhang16b,grubbs16,pouliot16,cash15,islam12} by launching inference attacks against encrypted deduplication.
-
-%Other studies \cite{zhang16b,grubbs16,pouliot16,cash15,islam12} target keyword search.
-Islam {\em et al.} \cite{islam12} exploit the leakage of access pattern, and recover the plaintext keywords associated with files.
-Cash {\em et al.} \cite{cash15} and Pouliot \cite{pouliot16} examine the security of searchable encryption under different leakage profiles.
-Zhang {\em et al.} \cite{zhang16b} propose file-injection attacks to recover searchable keywords.
-Grubbs \cite{grubbs16} build attacks against {\em Mylar} \cite{popa14} that is a practical system with keyword search enabled.
-This paper differs from the above works \cite{grubbs17,bindschaedler17,kellaris16,durak16,naveed15,lacharite18,zhang16b,grubbs16,pouliot16,cash15,islam12} by launching inference attacks against encrypted deduplication.
-
-%Client-side deduplication leaks the side channel information that if
-%particular messages have already been stored. Harnik {\em et al.}
-%\cite{harnik10} and Halevi {\em et al.} \cite{halevi11} show how to exploit
-%the side channel leakage for different purposes, including creating covert
-%channels between clients and gaining access to unauthorized information.
-
-%Some studies \cite{stanek14,abadi13,bellare15} aim to achieve stronger security than the more practical schemes focused above.
-Stanek {\em et al.} \cite{stanek14} design a hybrid encryption scheme where unpopular messages are protected by semantically secure encryption for high security guarantee, while popular messages are protected by CE to enable deduplication.
-On the other hand, the scheme \cite{stanek14} builds on public-key primitive which is inefficient for encrypting large-size messages.
-Abadi {\em et al.} \cite{abadi13} construct two schemes for the messages whose distributions are publicly available.
-Their first scheme generates  random tags and ciphertexts to prevent frequency leakage, yet incurring expensive {\em equality test} for checking duplicates.
-Their second scheme produces deterministic ciphertexts, and exposes the frequencies of corresponding plaintexts.
-Interactive MLE \cite{bellare15} introduces interactions into encrypted deduplication, and strengthens the security of both correlated and parameter-dependent messages, yet it is impractical for the use of fully homomorphic encryption.
-On the contrary to these theoretical contributions \cite{stanek14, abadi13, bellare15}, this paper focuses on the applied aspect, and investigates the security vulnerabilities in practical deduplication.
-
-% {\em Duplicate-faking attack} \cite{bellare13a} compromises the integrity of data by inconsistent tags.
-Specifically, an adversary can attach a maliciously-generated ciphertext to a faking tag $T$, so that the following legitimate messages that have the same tag of $T$ will be removed by deduplication.
-It can be addressed by server-side tag generation \cite{douceur02, bellare13b} or guarded decryption \cite{bellare13a}.
-
-% or introducing a random threshold to control client-side or server-side deduplication \cite{,harnik10}.
-
-% Our second attack augments the prior work \cite{li17} with distribution-based ranking and achieves high inference rate and accuracy. We   
-%Some studies \cite{bosman16,gruss15,xiao13} investigate the side channels of memory deduplication, and this paper differs from them in considering deduplication in outsourced storage (e.g., cloud storage).
-
-% \paragraph{Property-revealing encryption:}
-% Encrypted deduplication leaks the underlying equality of plaintext chunks for detecting duplicates.
-A generalized {\em property-revealing encryption} \cite{bindschaedler17} has been studied for securing database storage \cite{curtmola06,bellare07,bellare09,boldyreva09,boldyreva11,popa11}.
-This paper differs from these works as it targets unstructured workloads.
-
-% both theory \cite{curtmola06,bellare07,bellare09,boldyreva09,boldyreva11} and practice \cite{popa11}.
-
-% illustrate the weakness of searchable encryption.
-
-% present reconstruction attacks by analyzing ;
-
-% \cite{grubbs17,bindschaedler17,zhang16b,grubbs16,kellaris16,pouliot16,durak16,naveed15,cash15,islam12,lacharite18}  Regarding databases,    Regarding keyword search, ; further
-
-% under different leakage settings;
-
-% classical frequency analysis against cryptdb.
-
-% -specific cryptographic primitives of deterministic encryption.
-
-% applications.
-
-% structured relational data or
-
-% based on frequency analysis.
-
-% % Frequency analysis has been applied in prior works \cite{grubbs17,bindschaedler17,zhang16b,grubbs16,kellaris16,pouliot16,durak16,naveed15,cash15,islam12,lacharite18} to construct inference attacks.
-Some attacks target , by classical frequency analysis \cite{naveed15}, exploring correlations or orderings of table columns, .
-
-% while these approaches either target structured relational data \cite{grubbs17,bindschaedler17,kellaris16,durak16,naveed15,lacharite18} or aim to recover keywords of files \cite{zhang16b,grubbs16,pouliot16,cash15,islam12}, and cannot be applied to infer a huge number of chunks.
-% % Traditional MLE (e.g., CE) builds on a {\em public} function (e.g., the hash function) to derive encryption keys, and it is susceptible to brute-force attack \cite{bellare13a} that can be used to .
-The weakness can be addressed by server-aided MLE \cite{bellare13b}.
-%  % posted by the side-channel leakage in client-side and cross-user deduplication. 
-%  % This paper differs from these attacks in considering an adversary from the server side.
-
-\chapter{Conclusion}
-\label{sec:conclusion}
-
-Encrypted deduplication applies deterministic encryption, and leaks the frequencies of plaintexts.
-This paper revisits the security vulnerability  due to frequency analysis, and demonstrates that encrypted deduplication is even more vulnerable towards inference attacks.
-We propose two new frequency analysis attacks, both of which  achieve high inference rate and high inference precision, while under different assumptions of adversarial knowledge.
-We empirically evaluate our attacks with three real-world datasets, present a variety of new observations about their natures, and further analyze how they bring actual damages.
-We also discuss the advantages and disadvantages of possible countermeasures to advise practitioners for securely implementing and deploying encrypted deduplication storage systems.
-
-% types of files are especially insecure under these attacks.    
-% We propose two new inference attacks, which augment the prior attack \cite{li17} with high precision inference and relaxed adversarial knowledge, respectively.   
-% While prior work \cite{li17} has illustrated the vulnerability  via frequency analysis, this paper presents an in-depth study on the security of encrypted deduplication, and       
- We pose three directions for future work.
-First, we consider a complete old backup as the auxiliary information, and do not study how to launch attack if the adversary only has partial knowledge about the old backup.
-Possibly, we can still apply the frequency analysis attacks to extract characteristics from the available partial backup, and infer ciphertext-plaintext pairs by comparing the characteristics with those in the target backup.
-One direction is can we design advanced inference attacks, which  perform better than directly applying our attacks in this partial knowledge case?
-
- % The attack effectiveness depends on how the information in the partial backup correlates with the target backup.       
- Second, we adjust the parameters of the frequency analysis attacks based on their effectiveness, which can only be learnt after the attacks have happened.
-We do not study how to derive the optimal parameters from auxiliary information beforehand.
-Future work may do better.
-
- % We believe the parameter configurations depend on the characteristics of workloads, but do not see how to derive them efficiently.
-
- % the frequency analysis attacks are parameter sensitive.
-We adjust parameters based on the attack effectiveness (that can only be measured after the attack happens), and do not study how to identify the optimal parameter configuration  beforehand.
-We believe the parameter configurations depend on the characteristics of workloads, but do not see how to derive them efficiently.
-Future work may do better.
-
- % our proposed attacks are parameter sensitive.
-In evaluation, we adjust the parameters based on attack results, and report the security vulnerability of encrypted deduplication under some {\em specific} parameter settings of our attacks.
-We do not  study how to identify the optimal parameter setting of attack without the knowledge of attack results.
-We begin to consider that the attack configurations possibly depend on the characteristics of target workloads, but do not see how to derive them.
-Future work may do better.
-
-% help practitioners and researchers better understand the security issues in encrypted deduplication storage and motivate more research along this direction.
-% While 
-% of encrypted deduplication
-% Although it is vulnerable to frequency analysis, prior work \cite{li17} shows that classical frequency analysis can only infer a few original chunks in practice.
-This paper considers to increase the effectiveness of frequency analysis with additional leakages.
-Specifically, we present three new inference attacks by exploiting the size and order leakages that have been witnessed in deduplication systems \cite{xia11,lillibridge09,zhu08,douceur02, wilcox-ohearn08, bellare13b}.
-We evaluate the effectiveness of  our attacks with real-world datasets, and show that they can infer significant amount of original data under different types of workloads.
-We also discuss possible countermeasures to address the leakage channels exploited by our attacks.
-We pose the following future works.
-
-Third, we do not implement  attack prototypes against real-world encrypted deduplication storage systems. Another direction is to deploy our attack design and 
-report the vulnerability of encrypted deduplication in practice.
-
-% - Our attacks are parameter sensitive. One direction is to explore the relationship between configuration and workload characteristics.
-
-% - There seems a tradeoff between size-based attack and distribution-based attack.
-Throughout our experiment, size-based attack operates big chunks better, since they have more variances on chunk size.
-The distribution-based attack is expected to operate small chunks better, because there exists more chunk locality between small chunks.
-
-% - To defend our attacks, one approach is to obfuscate the chunk distributions.
-A recent work suggests to add redundant chunks to mix up network traffic.
-It works for changing chunk distribution, but depends on knowing if a chunk is duplicate before deduplication.
-
-% - This paper aims to report the vulnerabilities of encrypted deduplication, while not target on implementing a real attack against practical encrypted deduplication systems.
-Another direction is deploy our attack design in practice to alert the vulerabilities of encrypted deduplication.
-
-\thesisacknowledgement
-
-\thesisloadbibliography[nocite]{reference}
-
-%
-% Uncomment following codes to load bibliography database with native
-% \bibliography command.
-%
-% \nocite{*}
-% \bibliographystyle{thesis-uestc}
-% \bibliography{reference}
-%
+\nocite{*}
+\bibliographystyle{thesis-uestc}
+\bibliography{reference}
 

### 2018-12-12 code/InferenceAttacks/Bucket/src/countDB.cc

@@ -1,0 +1,51 @@
+#include <bits/stdc++.h>
+#include <openssl/bn.h>
+#include <openssl/md5.h>
+
+#include "leveldb/db.h"
+int FPSIZE = 6;
+#define FP_SIZE 12
+using namespace std;
+
+// store struct -----------------------------
+// fingerPrint-count pair
+
+// data counter--------------------
+
+uint64_t totalLogicChunkNumber = 0;
+uint64_t totalUniqueChunkNumber = 0;
+
+// store DBs-----------------------
+leveldb::DB *db; 
+
+//init leveldb======================================================
+int initDB(char *dbname){
+
+    leveldb::Options options;
+    options.create_if_missing = true;
+
+	leveldb::Status status = leveldb::DB::Open(options, dbname, &db);
+    assert(status.ok());
+    assert(db != NULL);
+}
+
+void MFC() {
+
+    freopen("MFC.txt", "w", stdout);
+    leveldb::Iterator* it = db->NewIterator(leveldb::ReadOptions());
+    for (it->SeekToFirst(); it->Valid(); it->Next()){
+        totalUniqueChunkNumber++;
+		string countStr = it->value().ToString();
+        totalLogicChunkNumber += atoi((const char*)countStr.c_str());
+    }
+    assert(it->status().ok());
+    delete it;
+}
+int main (int argc, char *argv[]){
+
+    initDB(argv[1]);
+    MFC();
+	cout<<"totalLogicChunkNumber "<<totalLogicChunkNumber<<endl;
+    cout<<"totalUniqueChunkNumber "<<totalUniqueChunkNumber<<endl;
+	return 0;
+}

### 2018-12-12 code/InferenceAttacks/Bucket/src/readInChunkToDBsFileType.cc

@@ -1,0 +1,206 @@
+#include <bits/stdc++.h>
+#include <openssl/bn.h>
+#include <openssl/md5.h>
+#include <fstream>
+#include "leveldb/db.h"
+
+int FPSIZE = 6;
+ 
+using namespace std;
+int insertTypeDB_Pair(string typeName, string typeHash);
+int insertTypeDB(string typeName, uint64_t chunkNum);
+int insertSFDB(string size, string chunkHash);
+int insertFCDB(string chunkHash);
+
+
+// data counter--------------------
+
+uint64_t totalLogicChunkNumber = 0;
+
+// store DBs-----------------------
+leveldb::DB *FCdb; //C chunk
+leveldb::DB *SFdb; //M chunk
+leveldb::DB *Tdb; //type 
+leveldb::DB *TPdb;
+
+//init leveldb======================================================
+int initDB(char *db1, char *db2, char *db3) {
+
+    leveldb::Options options;
+    options.create_if_missing = true;
+
+	leveldb::Status status = leveldb::DB::Open(options, db1, &FCdb);
+    assert(status.ok());
+    assert(FCdb != NULL);
+
+	status = leveldb::DB::Open(options, db2, &SFdb);
+    assert(status.ok());
+    assert(SFdb != NULL);
+
+	status = leveldb::DB::Open(options, db3, &Tdb);
+    assert(status.ok());
+    assert(Tdb != NULL);
+	
+	status = leveldb::DB::Open(options, "./TP", &TPdb);
+    assert(status.ok());
+    assert(TPdb != NULL);
+}
+
+int readInChunks(FILE *fp, FILE *typeFp) {
+
+	char read_buffer[256];
+    char typeBuffer[50];
+    char typeNumBuffer[256];
+    
+	fgets(read_buffer, 256, fp);// skip title line
+
+    //int cnt = 2000;
+    while (fgets(typeBuffer,256,typeFp)) {
+
+		//cnt++;
+        //cout<<cnt<<endl;
+		char *itemN = strtok(typeBuffer,":\t\n");
+		string typeName(itemN); 
+
+        fgets(typeNumBuffer, 256, typeFp);
+        char *tmp;
+        tmp = strtok(typeNumBuffer, ":\t\n");
+        uint64_t chunkNumber = atoi((const char*)tmp);
+        
+        char typeHash[FPSIZE];
[…]

### 2018-12-12 code/InferenceAttacks/CaseStudy/outPutFileData.py

@@ -1,0 +1,31 @@
+import sys
+import re
+
+file = open(sys.argv[1]);
+
+sum = 0;
+while 1:
+    line = file.readline()
+    if not line:
+        break
+    strTmp = "Chunks";
+    strTmp2 = "File path:";
+    if not cmp(line[:10], strTmp2[:10]):
+        #print line;
+        if line.find('.') == -1:
+            print 'NaNType';
+        else:
+            fileType = line.split('.');
+            if not re.search(r"(\d{4}-\d{1,2}-\d{1,2})", fileType[len(fileType)-1]):
+                print fileType[len(fileType)-1].replace('\n', '');
+            else:
+                print 'date'
+    if not cmp(line[:6], strTmp[:6]):
+        #print line;
+        line = re.sub("\D", "", line);
+        #print line;
+        num = int(line);
+        print num;
+        sum = sum + num;
+
+file.close()

### 2018-12-12 code/InferenceAttacks/multistream/src/similarity/cslice.cc

@@ -1,0 +1,452 @@
+/* c/c++ */
+#include <stdio.h>
+#include <stdlib.h>
+#include <assert.h>
+
+/* clustering */
+#include "../alglib/stdafx.h"
+#include <math.h>
+#include "../alglib/dataanalysis.h"
+
+/* timing */
+#include <sys/time.h>
+
+/* leveldb */
+#include "leveldb/db.h"
+
+/* stl */
+#include <vector>
+#include <queue>
+#include <map>
+#include <string>
+
+/* crypto */
+#include <openssl/bn.h>
+#include <openssl/sha.h>
+#include <openssl/md5.h>
+
+/* uint64_t */
+#include <inttypes.h>
+
+/* fingerprint size */
+#define FP_SIZE 6
+
+/* fixed-size segmentation, 1MB by default */
+#define SEG_SIZE ((1<<23)) 
+
+/* number of segments */
+uint64_t seg_count = 0;
+
+/* distance matrix */
+double *dist = NULL;
+
+/* segment (slice) db */
+leveldb::DB *seg_db;
+leveldb::DB *slice_db;
+leveldb::DB *chunksize;
+/* chunk information */
+struct node
+{
+	char key[FP_SIZE];
+	uint64_t size;
+};
+
+
+struct cmp
+{
+	bool operator()(node a, node b)
+	{
+		return memcmp(b.key, a.key, FP_SIZE); // b > a return 1
+	}
+};
+#define K_MINHASH 1
+
+/* clustering report */	
+alglib::ahcreport rep;
+
+
+void init_dbs(const char *seg_name, unsigned char *slice_name); 
+void read_hashes(FILE *fp, std::map<uint64_t, std::map<std::string, uint64_t>> &count_map);
+void process_seg(std::map<uint64_t, std::map<std::string, uint64_t>> &count_map, std::queue<node> sq);
+alglib::ae_int_t port2slice(std::map<uint64_t, std::map<std::string, uint64_t>> count_map, double r); 
+void port2cluster(std::map<uint64_t, std::map<std::string, uint64_t>> count_map);
+void clustering(); 
+void print_test();
+
+alglib::ae_int_t port2slice(std::map<uint64_t, std::map<std::string, uint64_t>> count_map, double r) {
+	alglib::integer_1d_array cidx;
+    alglib::integer_1d_array cz;
+	alglib::ae_int_t k;
+	/* generate clustering report */
+	alglib::clusterizerseparatedbydist(rep, r, k, cidx, cz);
+
[…]

### 2018-12-12 code/InferenceAttacks/multistream/src/similarity/pslice.cc

@@ -1,0 +1,290 @@
+/* c/c++ */
+#include <assert.h>
+#include <stdio.h>
+#include <stdlib.h>
+#include <inttypes.h>
+#include <iostream>
+
+/* stl */
+#include <queue>
+#include <string.h>
+#include <vector>
+
+/* timing */
+#include <time.h>
+
+/* leveldb */
+#include "leveldb/db.h"
+
+/* MinHash */
+#define K_MINHASH 1
+
+/* fingerprint size */
+#define FP_SIZE 6
+
+/* fixed-size segmentation, 1MB by default */
+#define SEG_SIZE ((1<<23)) 
+
+struct node
+{
+	char key[FP_SIZE];
+	uint64_t size;
+};
+
+struct cmp
+{
+	bool operator()(node a, node b)
+	{
+		return memcmp(b.key, a.key, FP_SIZE); // b > a return 1
+	}
+};
+
+leveldb::DB *seg_db;
+leveldb::DB *slice_db;
+leveldb::DB *chunk_size;
+/* number of segments */
+uint64_t seg_count = 0;
+/* number of slices */
+uint64_t slice_count = 0;
+
+/* minimum fingerprint in segment */
+/* priority_queue<node, vector<node>, cmp > pq; */
+
+
+void init_dbs(const char *seg_name, unsigned char *slice_name); 
+void process_seg(std::priority_queue<node, std::vector<node>, cmp > pq, std::queue<node> sq);
+void read_hashes(FILE *fp);
+void print_test();
+
+void init_dbs(const char *seg_name, const char *slice_name, const char* chunk_size_name) {
+      leveldb::Options options;
+      options.create_if_missing = true;
+	  leveldb::Status status;
+
+	  /* init segment db */
+      status = leveldb::DB::Open(options, seg_name, &seg_db);
+      assert(status.ok());
+      assert(seg_db != NULL);
+
+	  /* init slice db */
+      status = leveldb::DB::Open(options, slice_name, &slice_db);
+      assert(status.ok());
+      assert(slice_db != NULL);
+	
+      status = leveldb::DB::Open(options, chunk_size_name, &chunk_size);
+      assert(status.ok());
+      assert(chunk_size != NULL);
+}
+
+
+
+
+
+void process_seg(std::priority_queue<node, std::vector<node>, cmp > pq, std::queue<node> sq)
+{
[…]

### 2018-12-12 code/InferenceAttacks/single_stream/locality_script_fsl.sh

@@ -1,0 +1,49 @@
+#!/bin/bash
+
+# path of fsl trace
+fsl='/dataset/fsl/2013'
+
+# users considered in backups
+users=('004' '007' '012' '013' '015' '028')
+# auxiliary information
+date_of_aux=('2013-01-22' '2013-02-22' '2013-03-22' '2013-04-21')
+# target latest backup 
+date_of_latest='2013-05-21'
+
+# parameters
+u=5
+v=30
+w=200000
+leakage_rate=0
+
+# count latest backup
+for user in ${users[@]}; do
+	snapshot="fslhomes-user${user}-${date_of_latest}"
+	if [ -f "${fsl}"/${snapshot}.tar.gz ]; then
+		tar zxf "${fsl}"/${snapshot}.tar.gz  
+		fs-hasher/hf-stat -h ${snapshot}/${snapshot}.8kb.hash.anon > tmp/${snapshot} 
+		./count tmp/${snapshot} "dbs/F_${date_of_latest}/" "dbs/L_${date_of_latest}/" "dbs/R_${date_of_latest}/"  
+		rm -rf ${snapshot}
+#		rm -rf tmp/${snapshot}
+	fi
+done
+
+# count prior backups (as auxiliary information) and launch frequency analysis
+for aux in ${date_of_aux[@]}; do
+	for user in ${users[@]}; do
+		snapshot="fslhomes-user${user}-${aux}"
+		if [ -f "${fsl}"/${snapshot}.tar.gz ]; then
+			tar zxf "${fsl}"/${snapshot}.tar.gz  
+			fs-hasher/hf-stat -h ${snapshot}/${snapshot}.8kb.hash.anon > tmp/${snapshot} 
+			./count tmp/${snapshot} "dbs/F_${aux}" "dbs/L_${aux}" "dbs/R_${aux}"  
+			rm -rf ${snapshot}
+#			rm -rf tmp/${snapshot}
+		fi
+	done
+	echo "===================Attack==================="
+	echo "Auxiliary information: ${aux};  Target backup: ${date_of_latest}" 
+	echo "Parameters: (u, v, w) = (${u}, ${v}, ${w})"
+	# launch frequency analysis
+	./attack ${u} ${v} ${w} ${leakage_rate} "dbs/F_${aux}" "dbs/L_${aux}" "dbs/R_${aux}" "dbs/F_${date_of_latest}" "dbs/L_${date_of_latest}" "dbs/R_${date_of_latest}"
+	rm -rf inference-db/
+done

### 2018-12-12 code/SDFS/src/fuse/SDFS/SDFSCmds.java

@@ -1,0 +1,330 @@
+package fuse.SDFS;
+
+import java.io.File;
+
+import java.util.HashMap;
+import java.util.LinkedHashMap;
+import java.util.Map;
+
+import org.apache.commons.logging.Log;
+import org.apache.commons.logging.LogFactory;
+import org.opendedup.hashing.HashFunctionPool;
+import org.opendedup.logging.SDFSLogger;
+import org.opendedup.sdfs.Main;
+import org.opendedup.sdfs.filestore.DedupFileStore;
+import org.opendedup.sdfs.filestore.MetaFileStore;
+import org.opendedup.sdfs.filestore.gc.ManualGC;
+import org.opendedup.sdfs.io.MetaDataDedupFile;
+import org.opendedup.sdfs.notification.SDFSEvent;
+import org.opendedup.sdfs.servers.HCServiceProxy;
+import org.opendedup.util.RandomGUID;
+
+import fuse.Errno;
+import fuse.FuseException;
+import fuse.XattrLister;
+
+public class SDFSCmds {
+	private static final Log log = LogFactory.getLog(SDFSCmds.class);
+	public String mountedVolume;
+	public String mountPoint;
+
+	static long tbc = 1099511627776L;
+	static long gbc = 1024 * 1024 * 1024;
+	static int mbc = 1024 * 1024;
+	static int kbc = 1024;
+
+	public static final String[] cmds = { "user.cmd.cleanstore",
+			"user.cmd.dedupAll", "user.cmd.optimize", "user.cmd.snapshot",
+			"user.cmd.vmdk.make", "user.cmd.ids.clearstatus",
+			"user.cmd.ids.status", "user.cmd.file.flush", "user.cmd.flush.all",
+			"user.sdfs.file.isopen", "user.sdfs.ActualBytesWritten",
+			"user.sdfs.VirtualBytesWritten", "user.sdfs.BytesRead",
+			"user.sdfs.DuplicateData", "user.sdfs.fileGUID",
+			"user.sdfs.dfGUID", "user.sdfs.dedupAll", "user.dse.size",
+			"user.dse.maxsize" };
+
+	public static final String[] cmdDes = { "", "", "", "", "", "", "", "", "",
+			"", "", "", "", "", "", "", "", "", "" };
+
+	/*
+	 * public static final String[] cmdDes = {
+	 * "\"Collect all the unused chunks older than <minutes>\" e.g. setfattr -n user.cmd.cleanstore -v 6777:<minutes> ./"
+	 * ,
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/buse/sdfsdev/SDFSVolMgr.java

@@ -1,0 +1,249 @@
+/*******************************************************************************
+ * Copyright (C) 2016 Sam Silverberg sam.silverberg@gmail.com	
+ *
+ * This file is part of OpenDedupe SDFS.
+ *
+ * OpenDedupe SDFS is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * OpenDedupe SDFS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with Foobar.  If not, see <http://www.gnu.org/licenses/>.
+ *******************************************************************************/
+package org.opendedup.buse.sdfsdev;
+
+import java.io.File;
+import java.util.ArrayList;
+import java.util.Properties;
+import java.util.StringTokenizer;
+
+import org.apache.commons.cli.CommandLine;
+import org.apache.commons.cli.CommandLineParser;
+import org.apache.commons.cli.HelpFormatter;
+import org.apache.commons.cli.Options;
+import org.apache.commons.cli.ParseException;
+import org.apache.commons.cli.PosixParser;
+import org.apache.commons.daemon.Daemon;
+import org.apache.commons.daemon.DaemonContext;
+import org.apache.commons.daemon.DaemonInitException;
+import org.opendedup.buse.driver.BUSEMkDev;
+import org.opendedup.logging.SDFSLogger;
+import org.opendedup.sdfs.Main;
+import org.opendedup.sdfs.servers.SDFSService;
+import org.opendedup.util.OSValidator;
+
+public class SDFSVolMgr implements Daemon {
+	private static SDFSService sdfsService = null;
+	private static int port;
+	private static boolean useSSL;
+	private static String password = null;
+
+	public static Options buildOptions() {
+		Options options = new Options();
+		options.addOption("d", false, "verbose debug output");
+		options.addOption("v", true, "sdfs volume to mount \ne.g. dedup");
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/buse/sdfsdev/VolumeShutdownHook.java

@@ -1,0 +1,60 @@
+/*******************************************************************************
+ * Copyright (C) 2016 Sam Silverberg sam.silverberg@gmail.com	
+ *
+ * This file is part of OpenDedupe SDFS.
+ *
+ * OpenDedupe SDFS is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * OpenDedupe SDFS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with Foobar.  If not, see <http://www.gnu.org/licenses/>.
+ *******************************************************************************/
+package org.opendedup.buse.sdfsdev;
+
+import org.opendedup.buse.driver.BUSEMkDev;
+import org.opendedup.logging.SDFSLogger;
+import org.opendedup.sdfs.Main;
+import org.opendedup.sdfs.servers.SDFSService;
+
+public class VolumeShutdownHook extends Thread {
+	public static SDFSService service;
+	private static boolean stopped;
+
+	public VolumeShutdownHook() {
+	}
+
+	@Override
+	public void run() {
+
+		shutdown();
+	}
+
+	public static synchronized void shutdown() {
+		if (!stopped) {
+			stopped = true;
+			SDFSLogger.getLog().info("Please Wait while shutting down SDFS");
+			SDFSLogger.getLog().info("Data Can be lost if this is interrupted");
+			try {
+				Main.volume.closeAllDevices();
+				Thread.sleep(1000);
+				try {
+					BUSEMkDev.release();
+				}catch(Exception e) {
+					
+				}
+				service.stop();
+			} catch (Throwable e) {
+				e.printStackTrace();
+			}
+			SDFSLogger.getLog().info("SDFS Shut Down Cleanly");
+		}
+	}
+
+}

### 2018-12-12 code/SDFS/src/org/opendedup/cassandra/IgniteLongLongDBPersistence.java

@@ -1,0 +1,156 @@
+package org.opendedup.cassandra;
+
+import java.net.InetSocketAddress;
+import java.util.Collection;
+import java.util.Iterator;
+import java.util.Map;
+import java.util.concurrent.atomic.AtomicLong;
+
+import javax.cache.Cache.Entry;
+import javax.cache.configuration.FactoryBuilder;
+import javax.cache.integration.CacheLoaderException;
+import javax.cache.integration.CacheWriterException;
+
+import org.apache.ignite.Ignite;
+import org.apache.ignite.IgniteCache;
+import org.apache.ignite.Ignition;
+import org.apache.ignite.cache.CacheMode;
+import org.apache.ignite.configuration.CacheConfiguration;
+import org.apache.ignite.configuration.IgniteConfiguration;
+import org.apache.ignite.lang.IgniteBiInClosure;
+import org.apache.ignite.spi.discovery.tcp.TcpDiscoverySpi;
+import org.opendedup.logging.SDFSLogger;
+
+import com.datastax.driver.core.Row;
+
+public class IgniteLongLongDBPersistence implements org.apache.ignite.cache.store.CacheStore<Long, Long> {
+
+	CassandraDedupeDB db = null;
+
+	public IgniteLongLongDBPersistence() {
+		super();
+
+	}
+
+	@Override
+	public void loadCache(IgniteBiInClosure<Long, Long> clo, Object... args) {
+		this.db = (CassandraDedupeDB) args[0];
+		if (args.length > 1 ) {
+			Iterator<Row> iter = db._getAllRmrf();
+			AtomicLong k = (AtomicLong) args[1];
+			while (iter.hasNext()) {
+				Row r = iter.next();
+				clo.apply(r.getLong(0), r.getLong(1));
+				k.incrementAndGet();
+			}
+		}
+	}
+
+	@Override
+	public Long load(Long key) throws CacheLoaderException {
+		try {
+			return db.getRMRef(key);
+		} catch (Exception e) {
+			SDFSLogger.getLog().warn("unable to load hash", e);
+			throw new CacheLoaderException(e);
+		}
+
+	}
+
+	@Override
+	public void delete(Object key) throws CacheWriterException {
+		try {
+			Long bw = (Long) key;
+			this.db._delRMRef(bw);
+		} catch (Exception e) {
+			throw new CacheWriterException(e);
+		}
+
+	}
+
+	@Override
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/collections/CassandraDBMap.java

@@ -1,0 +1,1156 @@
+/*******************************************************************************
+ * Copyright (C) 2016 Sam Silverberg sam.silverberg@gmail.com	
+ *
+ * This file is part of OpenDedupe SDFS.
+ *
+ * OpenDedupe SDFS is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * OpenDedupe SDFS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with Foobar.  If not, see <http://www.gnu.org/licenses/>.
+ *******************************************************************************/
+package org.opendedup.collections;
+
+import java.io.File;
+
+import java.io.FileNotFoundException;
+import java.io.IOException;
+import java.net.InetSocketAddress;
+import java.nio.ByteBuffer;
+import java.nio.ByteOrder;
+import java.util.ArrayList;
+import java.util.Iterator;
+import java.util.List;
+import java.util.concurrent.ArrayBlockingQueue;
+import java.util.concurrent.BlockingQueue;
+import java.util.concurrent.ConcurrentHashMap;
+import java.util.concurrent.RejectedExecutionHandler;
+import java.util.concurrent.ThreadFactory;
+import java.util.concurrent.ThreadPoolExecutor;
+import java.util.concurrent.TimeUnit;
+import java.util.concurrent.atomic.AtomicInteger;
+import java.util.concurrent.atomic.AtomicLong;
+import java.util.concurrent.locks.Lock;
+import java.util.concurrent.locks.ReentrantLock;
+import java.util.concurrent.locks.ReentrantReadWriteLock;
+
+import javax.cache.Cache.Entry;
+
+import org.apache.commons.io.FileUtils;
+import org.opendedup.cassandra.CassandraDedupeDB;
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/collections/DataMapInterface.java

@@ -1,0 +1,82 @@
+/*******************************************************************************
+ * Copyright (C) 2016 Sam Silverberg sam.silverberg@gmail.com	
+ *
+ * This file is part of OpenDedupe SDFS.
+ *
+ * OpenDedupe SDFS is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * OpenDedupe SDFS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with Foobar.  If not, see <http://www.gnu.org/licenses/>.
+ *******************************************************************************/
+package org.opendedup.collections;
+
+import java.io.IOException;
+
+import org.opendedup.sdfs.io.FileClosedException;
+
+public interface DataMapInterface {
+
+	public abstract void iterInit() throws IOException;
+
+	public abstract long getIterPos();
+
+	public abstract long nextKey() throws IOException, FileClosedException;
+
+	public abstract SparseDataChunk nextValue(boolean refcount) throws IOException, FileClosedException;
+
+	public abstract boolean isClosed();
+
+	public abstract void put(long pos, SparseDataChunk data) throws IOException,
+			FileClosedException;
+
+	public abstract void put(long pos, SparseDataChunk data, int length)
+			throws IOException, FileClosedException;
+
+	public abstract void putIfNull(long pos, SparseDataChunk data) throws IOException,
+			FileClosedException;
+
+	public abstract void trim(long pos, int len) throws IOException,
+			FileClosedException;
+
+	public abstract void truncate(long length) throws IOException,
+			FileClosedException;
+
+	public abstract byte getVersion();
+
+	public abstract byte[] getFree();
+
+	/*
+	 * (non-Javadoc)
+	 * 
+	 * @see com.annesam.collections.AbstractMap#remove(long)
+	 */
+	public abstract void remove(long pos) throws IOException,
+			FileClosedException;
+
+	/*
+	 * (non-Javadoc)
+	 * 
+	 * @see com.annesam.collections.AbstractMap#get(long)
+	 */
+	public abstract SparseDataChunk get(long pos) throws IOException,
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/collections/HashExistsException.java

@@ -1,0 +1,42 @@
+/*******************************************************************************
+ * Copyright (C) 2016 Sam Silverberg sam.silverberg@gmail.com	
+ *
+ * This file is part of OpenDedupe SDFS.
+ *
+ * OpenDedupe SDFS is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * OpenDedupe SDFS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with Foobar.  If not, see <http://www.gnu.org/licenses/>.
+ *******************************************************************************/
+package org.opendedup.collections;
+
+import java.io.IOException;
+
+public class HashExistsException extends IOException {
+
+	private static final long serialVersionUID = 2207515169199626140L;
+	private long pos;
+	private byte[] hash;
+
+	public HashExistsException(long pos, byte[] hash) {
+		this.pos = pos;
+		this.hash = hash;
+	}
+
+	public long getPos() {
+		return this.pos;
+	}
+
+	public byte[] getHash() {
+		return this.hash;
+	}
+
+}

### 2018-12-12 code/SDFS/src/org/opendedup/collections/HashtableFullException.java

@@ -1,0 +1,32 @@
+/*******************************************************************************
+ * Copyright (C) 2016 Sam Silverberg sam.silverberg@gmail.com	
+ *
+ * This file is part of OpenDedupe SDFS.
+ *
+ * OpenDedupe SDFS is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * OpenDedupe SDFS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with Foobar.  If not, see <http://www.gnu.org/licenses/>.
+ *******************************************************************************/
+package org.opendedup.collections;
+
+public class HashtableFullException extends Exception {
+
+	/**
+	 * 
+	 */
+	private static final long serialVersionUID = 1L;
+
+	public HashtableFullException(String msg) {
+		super(msg);
+	}
+
+}

### 2018-12-12 code/SDFS/src/org/opendedup/collections/KeyNotFoundException.java

@@ -1,0 +1,38 @@
+/*******************************************************************************
+ * Copyright (C) 2016 Sam Silverberg sam.silverberg@gmail.com	
+ *
+ * This file is part of OpenDedupe SDFS.
+ *
+ * OpenDedupe SDFS is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * OpenDedupe SDFS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with Foobar.  If not, see <http://www.gnu.org/licenses/>.
+ *******************************************************************************/
+package org.opendedup.collections;
+
+import org.opendedup.util.StringUtils;
+
+public class KeyNotFoundException extends Exception {
+
+	/**
+	 * 
+	 */
+	private static final long serialVersionUID = 3838655007053133611L;
+
+	public KeyNotFoundException() {
+		super();
+	}
+
+	public KeyNotFoundException(byte[] key) {
+		super("Key [" + StringUtils.getHexString(key) + "] not found");
+	}
+
+}

### 2018-12-12 code/SDFS/src/org/opendedup/collections/ProgressiveFileBasedCSMap.java

@@ -1,0 +1,944 @@
+package org.opendedup.collections;
+
+/*******************************************************************************
+ * Copyright (C) 2016 Sam Silverberg sam.silverberg@gmail.com	
+ *
+ * This file is part of OpenDedupe SDFS.
+ *
+ * OpenDedupe SDFS is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * OpenDedupe SDFS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with Foobar.  If not, see <http://www.gnu.org/licenses/>.
+ *******************************************************************************/
+
+import java.io.File;
+
+import java.io.FileFilter;
+import java.io.FileNotFoundException;
+import java.io.IOException;
+import java.util.ArrayList;
+import java.util.Iterator;
+import java.util.concurrent.ArrayBlockingQueue;
+import java.util.concurrent.BlockingQueue;
+import java.util.concurrent.RejectedExecutionHandler;
+import java.util.concurrent.ThreadFactory;
+import java.util.concurrent.ThreadPoolExecutor;
+import java.util.concurrent.TimeUnit;
+import java.util.concurrent.atomic.AtomicLong;
+import java.util.concurrent.locks.Lock;
+import java.util.concurrent.locks.ReentrantLock;
+import java.util.concurrent.locks.ReentrantReadWriteLock;
+
+import org.apache.commons.io.FileUtils;
+import org.opendedup.collections.AbstractHashesMap;
+import org.opendedup.collections.AbstractMap;
+import org.opendedup.collections.AbstractShard;
+import org.opendedup.collections.DataArchivedException;
+import org.opendedup.collections.HashtableFullException;
+import org.opendedup.collections.KeyNotFoundException;
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/collections/ProgressiveFileByteArrayLongMap.java

@@ -1,0 +1,1497 @@
+/*******************************************************************************
+ * Copyright (C) 2016 Sam Silverberg sam.silverberg@gmail.com	
+ *
+ * This file is part of OpenDedupe SDFS.
+ *
+ * OpenDedupe SDFS is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * OpenDedupe SDFS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with Foobar.  If not, see <http://www.gnu.org/licenses/>.
+ *******************************************************************************/
+package org.opendedup.collections;
+
+import java.io.File;
+
+
+
+
+import java.io.FileInputStream;
+import java.io.FileOutputStream;
+import java.io.IOException;
+import java.io.ObjectInputStream;
+import java.io.ObjectOutputStream;
+import java.io.RandomAccessFile;
+import java.io.Serializable;
+import java.io.SyncFailedException;
+import java.nio.ByteBuffer;
+import java.nio.MappedByteBuffer;
+import java.nio.channels.FileChannel.MapMode;
+import java.util.Arrays;
+import java.util.BitSet;
+import java.util.concurrent.BlockingQueue;
+import java.util.concurrent.SynchronousQueue;
+import java.util.concurrent.ThreadPoolExecutor;
+import java.util.concurrent.TimeUnit;
+import java.util.concurrent.atomic.AtomicInteger;
+import java.util.concurrent.locks.Lock;
+import java.util.concurrent.locks.ReentrantReadWriteLock;
+
+import org.opendedup.collections.AbstractShard;
+import org.opendedup.collections.HashtableFullException;
+import org.opendedup.collections.KeyNotFoundException;
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/collections/QuickList.java

@@ -1,0 +1,228 @@
+/*******************************************************************************
+ * Copyright (C) 2016 Sam Silverberg sam.silverberg@gmail.com	
+ *
+ * This file is part of OpenDedupe SDFS.
+ *
+ * OpenDedupe SDFS is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * OpenDedupe SDFS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with Foobar.  If not, see <http://www.gnu.org/licenses/>.
+ *******************************************************************************/
+package org.opendedup.collections;
+
+import java.io.Externalizable;
+
+
+
+import java.io.IOException;
+import java.io.ObjectInput;
+import java.io.ObjectOutput;
+import java.util.Collection;
+import java.util.Iterator;
+import java.util.List;
+import java.util.ListIterator;
+
+import org.opendedup.hashing.HashFunctionPool;
+
+public class QuickList<E> implements java.util.List<E>, Externalizable {
+
+	private int size = 0;
+	private int arraySize = 0;
+	private transient E[] array;
+
+	public static byte[] FREE = new byte[HashFunctionPool.hashLength];
+	public static byte[] REMOVED = new byte[HashFunctionPool.hashLength];
+
+	public QuickList(int size) {
+		this.arraySize = size;
+		array = this.newElementArray(this.arraySize);
+	}
+
+	public QuickList() {
+
+	}
+
+	@SuppressWarnings("unchecked")
+	private E[] newElementArray(int size) {
+		return (E[]) new Object[size];
+	}
+
+	@Override
+	public int size() {
+		// TODO Auto-generated method stub
+		return this.size;
+	}
+
+	@Override
+	public boolean isEmpty() {
+		// TODO Auto-generated method stub
+		return (size == 0);
+	}
+
+	@Override
+	public boolean contains(Object o) {
+		// TODO Auto-generated method stub
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/collections/ShardedFileByteArrayLongMap.java

@@ -1,0 +1,1872 @@
+package org.opendedup.collections;
+
+import java.io.File;
+
+
+import java.io.FileInputStream;
+import java.io.FileOutputStream;
+import java.io.IOException;
+import java.io.ObjectInputStream;
+import java.io.ObjectOutputStream;
+import java.io.RandomAccessFile;
+import java.io.Serializable;
+import java.io.SyncFailedException;
+import java.nio.ByteBuffer;
+import java.nio.MappedByteBuffer;
+import java.nio.channels.FileChannel;
+import java.util.ArrayList;
+import java.util.Arrays;
+import java.util.BitSet;
+import java.util.Iterator;
+import java.util.concurrent.atomic.AtomicInteger;
+import java.util.concurrent.atomic.AtomicLong;
+import java.util.concurrent.locks.Lock;
+import java.util.concurrent.locks.ReentrantReadWriteLock;
+
+import org.opendedup.collections.AbstractShard;
+import org.opendedup.collections.HashtableFullException;
+import org.opendedup.collections.KeyNotFoundException;
+import org.opendedup.hashing.HashFunctionPool;
+import org.opendedup.hashing.LargeBloomFilter;
+import org.opendedup.logging.SDFSLogger;
+import org.opendedup.sdfs.filestore.ChunkData;
+import org.opendedup.util.NextPrime;
+import com.google.common.hash.Funnel;
+import com.google.common.hash.PrimitiveSink;
+
+import sun.nio.ch.DirectBuffer;
+
+@SuppressWarnings("restriction")
+public class ShardedFileByteArrayLongMap
+		implements Runnable, AbstractShard, Serializable, Comparable<ShardedFileByteArrayLongMap> {
+	/**
+	 * 
+	 */
+	private static final long serialVersionUID = 1L;
+	// transient MappedByteBuffer keys = null;
+	transient private int size = 0;
+	transient private int maxSz = 0;
+	transient private double loadFactor = .75;
+	transient private String path = null;
+	transient private FileChannel kFC = null;
+	transient private FileChannel rFC = null;
+	transient private RandomAccessFile rRaf = null;
+	transient protected static final int EL = HashFunctionPool.hashLength + 8;
+	transient protected static final int RL = 8;
+	transient private static final int VP = HashFunctionPool.hashLength;
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/collections/ShardedProgressiveFileBasedCSMap.java

@@ -1,0 +1,1281 @@
+/*******************************************************************************
+ * Copyright (C) 2016 Sam Silverberg sam.silverberg@gmail.com	
+ *
+ * This file is part of OpenDedupe SDFS.
+ *
+ * OpenDedupe SDFS is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * OpenDedupe SDFS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with Foobar.  If not, see <http://www.gnu.org/licenses/>.
+ *******************************************************************************/
+package org.opendedup.collections;
+
+import java.io.File;
+
+
+import java.io.FileFilter;
+import java.io.FileNotFoundException;
+import java.io.IOException;
+import java.util.ArrayList;
+import java.util.Iterator;
+import java.util.Random;
+import java.util.concurrent.ArrayBlockingQueue;
+import java.util.concurrent.BlockingQueue;
+import java.util.concurrent.RejectedExecutionHandler;
+import java.util.concurrent.ThreadFactory;
+import java.util.concurrent.ThreadLocalRandom;
+import java.util.concurrent.ThreadPoolExecutor;
+import java.util.concurrent.TimeUnit;
+import java.util.concurrent.atomic.AtomicLong;
+import java.util.concurrent.locks.Lock;
+import java.util.concurrent.locks.ReentrantLock;
+import java.util.concurrent.locks.ReentrantReadWriteLock;
+
+import org.apache.commons.io.FileUtils;
+import org.opendedup.collections.AbstractHashesMap;
+import org.opendedup.collections.AbstractMap;
+import org.opendedup.collections.AbstractShard;
+import org.opendedup.collections.DataArchivedException;
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/collections/ShardedProgressiveFileBasedCSMap2.java

@@ -1,0 +1,1319 @@
+/*******************************************************************************
+ * Copyright (C) 2016 Sam Silverberg sam.silverberg@gmail.com	
+ *
+ * This file is part of OpenDedupe SDFS.
+ *
+ * OpenDedupe SDFS is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * OpenDedupe SDFS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with Foobar.  If not, see <http://www.gnu.org/licenses/>.
+ *******************************************************************************/
+package org.opendedup.collections;
+
+import java.io.File;
+
+
+
+import java.io.FileFilter;
+import java.io.FileNotFoundException;
+import java.io.IOException;
+import java.util.ArrayList;
+import java.util.Iterator;
+import java.util.Random;
+import java.util.concurrent.ArrayBlockingQueue;
+import java.util.concurrent.BlockingQueue;
+import java.util.concurrent.RejectedExecutionHandler;
+import java.util.concurrent.ThreadFactory;
+import java.util.concurrent.ThreadLocalRandom;
+import java.util.concurrent.ThreadPoolExecutor;
+import java.util.concurrent.TimeUnit;
+import java.util.concurrent.atomic.AtomicLong;
+import java.util.concurrent.locks.Lock;
+import java.util.concurrent.locks.ReentrantLock;
+import java.util.concurrent.locks.ReentrantReadWriteLock;
+
+import org.apache.commons.io.FileUtils;
+import org.opendedup.collections.AbstractHashesMap;
+import org.opendedup.collections.AbstractMap;
+import org.opendedup.collections.AbstractShard;
+import org.opendedup.collections.DataArchivedException;
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/hashing/FLBF.java

@@ -1,0 +1,187 @@
+/*******************************************************************************
+ * Copyright (C) 2016 Sam Silverberg sam.silverberg@gmail.com	
+ *
+ * This file is part of OpenDedupe SDFS.
+ *
+ * OpenDedupe SDFS is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * OpenDedupe SDFS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with Foobar.  If not, see <http://www.gnu.org/licenses/>.
+ *******************************************************************************/
+package org.opendedup.hashing;
+
+import java.io.ByteArrayOutputStream;
+
+
+
+
+import java.io.File;
+import java.io.FileInputStream;
+import java.io.FileOutputStream;
+import java.io.IOException;
+import java.io.ObjectInputStream;
+import java.io.ObjectOutputStream;
+import java.io.Serializable;
+import java.util.concurrent.locks.ReentrantReadWriteLock;
+
+import org.opendedup.collections.ShardedFileByteArrayLongMap.KeyBlob;
+import org.opendedup.utils.hashing.FileBasedBloomFilter;
+
+import com.duprasville.guava.probably.CuckooFilter;
+import com.google.common.hash.Funnel;
+import com.google.common.hash.PrimitiveSink;
+
+
+public class FLBF implements Serializable {
+	private static final long serialVersionUID = 1L;
+	public transient FileBasedBloomFilter<KeyBlob> bfs = null;
+	public transient ReentrantReadWriteLock l = new ReentrantReadWriteLock();
+	boolean counting = false;
+	File path = null;
+	CuckooFilter filter = null;
+	private static Funnel<KeyBlob> kbFunnel = new Funnel<KeyBlob>() {
+		/**
+		 * 
+		 */
+		private static final long serialVersionUID = 1L;
+
+		/**
+		 * 
+		 */
+
+		@Override
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/hashing/Finger.java

@@ -1,0 +1,98 @@
+/*******************************************************************************
+ * Copyright (C) 2016 Sam Silverberg sam.silverberg@gmail.com	
+ *
+ * This file is part of OpenDedupe SDFS.
+ *
+ * OpenDedupe SDFS is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * OpenDedupe SDFS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with Foobar.  If not, see <http://www.gnu.org/licenses/>.
+ *******************************************************************************/
+package org.opendedup.hashing;
+
+import java.io.IOException;
+
+import java.util.Arrays;
+import java.util.List;
+
+import org.opendedup.collections.HashtableFullException;
+import org.opendedup.collections.InsertRecord;
+import org.opendedup.sdfs.io.AsyncChunkWriteActionListener;
+import org.opendedup.sdfs.io.WritableCacheBuffer;
+import org.opendedup.sdfs.servers.HCServiceProxy;
+
+public class Finger implements Runnable {
+	private static final byte[] k = new byte[HashFunctionPool.hashLength];
+	public byte[] chunk;
+	public byte[] hash;
+	public InsertRecord hl;
+	public int start;
+	public int len;
+	public int ap;
+	public boolean noPersist;
+	public AsyncChunkWriteActionListener l;
+	public int claims = -1;
+	public String lookupFilter = null;
+	public String uuid = null;
+
+	public Finger(String lookupFilter, String uuid) {
+		this.lookupFilter = lookupFilter;
+		this.uuid = uuid;
+	}
+
+	public void run() {
+		try {
+			if (Arrays.equals(this.hash, k))
+				this.hl = new InsertRecord(false, 1);
+			this.hl = HCServiceProxy.writeChunk(this.hash, this.chunk, claims, this.lookupFilter, this.uuid);
+
+			l.commandResponse(this);
+
+		} catch (Throwable e) {
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/hashing/Murmur3HashEngine.java

@@ -1,0 +1,84 @@
+/*******************************************************************************
+ * Copyright (C) 2016 Sam Silverberg sam.silverberg@gmail.com	
+ *
+ * This file is part of OpenDedupe SDFS.
+ *
+ * OpenDedupe SDFS is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * OpenDedupe SDFS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with Foobar.  If not, see <http://www.gnu.org/licenses/>.
+ *******************************************************************************/
+package org.opendedup.hashing;
+
+import java.io.IOException;
+import java.util.List;
+
+import org.opendedup.sdfs.Main;
+
+import com.google.common.hash.HashFunction;
+import com.google.common.hash.Hashing;
+
+public class Murmur3HashEngine implements AbstractHashEngine {
+
+	public static int defaultSeed = 6442;
+	private int seed;
+	HashFunction hf = null;
+
+	public Murmur3HashEngine() {
+		this.seed = defaultSeed;
+		hf = Hashing.murmur3_128(seed);
+	}
+
+	@Override
+	public byte[] getHash(byte[] data) {
+		byte[] hash = hf.hashBytes(data).asBytes();
+		return hash;
+	}
+
+	public static int getHashLenth() {
+		// TODO Auto-generated method stub
+		return 16;
+	}
+
+	@Override
+	public void destroy() {
+	}
+
+	@Override
+	public boolean isVariableLength() {
+		// TODO Auto-generated method stub
+		return false;
+	}
+
+	@Override
+	public int getMaxLen() {
+		// TODO Auto-generated method stub
+		return Main.CHUNK_LENGTH;
+	}
+
+	@Override
+	public int getMinLen() {
+		// TODO Auto-generated method stub
+		return Main.CHUNK_LENGTH;
+	}
+
+	@Override
+	public void setSeed(int seed) {
+		this.seed = seed;
+		hf = Hashing.murmur3_128(seed);
+		
+	}
+
+	@Override
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/hashing/VariableHighwayHashEngine.java

@@ -1,0 +1,131 @@
+/*******************************************************************************
+ * Copyright (C) 2016 Sam Silverberg sam.silverberg@gmail.com	
+ *
+ * This file is part of OpenDedupe SDFS.
+ *
+ * OpenDedupe SDFS is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * OpenDedupe SDFS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with Foobar.  If not, see <http://www.gnu.org/licenses/>.
+ *******************************************************************************/
+package org.opendedup.hashing;
+
+import java.io.IOException;
+
+import java.nio.ByteBuffer;
+import java.security.NoSuchAlgorithmException;
+import java.util.ArrayList;
+import java.util.List;
+
+import org.opendedup.logging.SDFSLogger;
+import org.opendedup.sdfs.Main;
+import org.rabinfingerprint.handprint.BoundaryDetectors;
+import org.rabinfingerprint.handprint.FingerFactory.ChunkBoundaryDetector;
+import org.rabinfingerprint.handprint.EnhancedFingerFactory;
+import org.rabinfingerprint.handprint.EnhancedFingerFactory.EnhancedChunkVisitor;
+import org.rabinfingerprint.polynomial.Polynomial;
+
+import org.opendedup.rabin.hashing.HighwayHash;
+
+public class VariableHighwayHashEngine implements AbstractHashEngine {
+	
+	static Polynomial p = Polynomial.createFromLong(10923124345206883L);
+	ChunkBoundaryDetector boundaryDetector = BoundaryDetectors.DEFAULT_BOUNDARY_DETECTOR;
+	
+	private EnhancedFingerFactory ff = null;
+	public static enum HASHTYPE {HASH128,HASH160,HASH256};
+	private HASHTYPE ht;
+
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/hashing/VariableSha256HashEngine.java

@@ -1,0 +1,125 @@
+/*******************************************************************************
+ * Copyright (C) 2016 Sam Silverberg sam.silverberg@gmail.com	
+ *
+ * This file is part of OpenDedupe SDFS.
+ *
+ * OpenDedupe SDFS is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * OpenDedupe SDFS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with Foobar.  If not, see <http://www.gnu.org/licenses/>.
+ *******************************************************************************/
+package org.opendedup.hashing;
+
+import java.io.IOException;
+
+import java.nio.ByteBuffer;
+import java.security.NoSuchAlgorithmException;
+import java.util.ArrayList;
+import java.util.List;
+
+import org.opendedup.logging.SDFSLogger;
+import org.opendedup.sdfs.Main;
+import org.rabinfingerprint.handprint.BoundaryDetectors;
+import org.rabinfingerprint.handprint.FingerFactory.ChunkBoundaryDetector;
+import org.rabinfingerprint.handprint.EnhancedFingerFactory;
+import org.rabinfingerprint.handprint.EnhancedFingerFactory.EnhancedChunkVisitor;
+import org.rabinfingerprint.polynomial.Polynomial;
+
+import com.google.common.hash.HashFunction;
+import com.google.common.hash.Hashing;
+
+public class VariableSha256HashEngine implements AbstractHashEngine {
+
+	static Polynomial p = Polynomial.createFromLong(10923124345206883L);
+	ChunkBoundaryDetector boundaryDetector = BoundaryDetectors.DEFAULT_BOUNDARY_DETECTOR;
+	public static enum HASHTYPE {HASH160,HASH256};
+	private EnhancedFingerFactory ff = null;
+	HashFunction hf = Hashing.sha256();
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/io/benchmarks/ReadTest.java

@@ -1,0 +1,223 @@
+/*******************************************************************************
+ * Copyright (C) 2016 Sam Silverberg sam.silverberg@gmail.com	
+ *
+ * This file is part of OpenDedupe SDFS.
+ *
+ * OpenDedupe SDFS is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * OpenDedupe SDFS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with Foobar.  If not, see <http://www.gnu.org/licenses/>.
+ *******************************************************************************/
+package org.opendedup.io.benchmarks;
+
+import java.io.File;
+import java.io.IOException;
+import java.nio.ByteBuffer;
+import java.nio.channels.FileChannel;
+import java.nio.file.Files;
+import java.nio.file.Path;
+import java.nio.file.Paths;
+import java.nio.file.StandardOpenOption;
+import java.util.Arrays;
+import java.util.Date;
+
+public class ReadTest implements Runnable {
+	String path;
+	int bs = 1048576;
+	public long duration = 0;
+	boolean finished = false;
+
+	public ReadTest(String path) {
+		this.path = path;
+		Thread th = new Thread(this);
+		th.start();
+	}
+
+	@Override
+	public void run() {
+		try {
+			long len = new File(path).length();
+			long sz = 0;
+			Path ps = Paths.get(path);
+			FileChannel fc = (FileChannel) Files.newByteChannel(ps,
+					StandardOpenOption.CREATE, StandardOpenOption.WRITE,
+					StandardOpenOption.READ);
+			ByteBuffer buf = ByteBuffer.allocateDirect(bs);
+			long time = System.currentTimeMillis();
+
+			while (sz < len) {
+				buf.position(0);
+				int read = fc.read(buf, sz);
+				sz = sz + read;
+			}
+
+			duration = (System.currentTimeMillis() - time);
+			System.out.println("read=" + path + " len=" + len + " tm="
+					+ duration);
+			fc.close();
+
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/logging/SDFSLogger.java

@@ -1,0 +1,138 @@
+/*******************************************************************************
+ * Copyright (C) 2016 Sam Silverberg sam.silverberg@gmail.com	
+ *
+ * This file is part of OpenDedupe SDFS.
+ *
+ * OpenDedupe SDFS is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * OpenDedupe SDFS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with Foobar.  If not, see <http://www.gnu.org/licenses/>.
+ *******************************************************************************/
+package org.opendedup.logging;
+
+import java.io.IOException;
+
+import org.apache.log4j.ConsoleAppender;
+import org.apache.log4j.Level;
+import org.apache.log4j.Logger;
+import org.apache.log4j.PatternLayout;
+import org.apache.log4j.RollingFileAppender;
+import org.opendedup.sdfs.Main;
+
+public class SDFSLogger {
+
+	private static Logger log = Logger.getLogger("sdfs");
+	private static Logger awslog = Logger.getLogger("com.amazonaws");
+	private static Logger quartzLog = Logger.getLogger("org.quartz");
+	private static Logger fslog = Logger.getLogger("fs");
+	private static Logger basicLog = Logger.getLogger("bsdfs");
+	private static boolean debug = false;
+	private static boolean fsdebug = false;
+	static RollingFileAppender app = null;
+	static {
+
+		ConsoleAppender bapp = new ConsoleAppender(new PatternLayout("%m%n"));
+		basicLog.addAppender(bapp);
+
+		basicLog.setLevel(Level.WARN);
+		try {
+
+			app = new RollingFileAppender(new PatternLayout(
+					"%d [%p] [%c] [%C] [%L] [%t] %x - %m%n"), Main.logPath, true);
+			app.setMaxBackupIndex(2);
+			app.setMaxFileSize(Main.logSize);
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/mtools/RestoreArchive.java

@@ -1,0 +1,189 @@
+/*******************************************************************************
+ * Copyright (C) 2016 Sam Silverberg sam.silverberg@gmail.com	
+ *
+ * This file is part of OpenDedupe SDFS.
+ *
+ * OpenDedupe SDFS is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * OpenDedupe SDFS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with Foobar.  If not, see <http://www.gnu.org/licenses/>.
+ *******************************************************************************/
+package org.opendedup.mtools;
+
+import java.io.File;
+import java.io.IOException;
+import java.util.ArrayList;
+import java.util.HashMap;
+import java.util.Map.Entry;
+import java.util.TreeMap;
+import java.util.concurrent.atomic.AtomicLong;
+
+import org.opendedup.collections.LongByteArrayMap;
+import org.opendedup.collections.LongKeyValue;
+import org.opendedup.collections.SparseDataChunk;
+import org.opendedup.logging.SDFSLogger;
+import org.opendedup.sdfs.Main;
+import org.opendedup.sdfs.io.HashLocPair;
+import org.opendedup.sdfs.io.MetaDataDedupFile;
+import org.opendedup.sdfs.notification.SDFSEvent;
+import org.opendedup.sdfs.servers.HCServiceProxy;
+import org.opendedup.util.FileCounts;
+
+import com.google.common.primitives.Longs;
+
+public class RestoreArchive implements Runnable {
+	private AtomicLong totalArchives = new AtomicLong(0);
+	private AtomicLong importedArchives = new AtomicLong(0);
+	public SDFSEvent fEvt = null;
+	private MetaDataDedupFile f = null;
+	private HashMap<String, String> restoreRequests = new HashMap<String, String>();
+
+	public RestoreArchive(MetaDataDedupFile f,long id) throws IOException {
+		
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/sdfs/DSEConfigWriter.java

@@ -1,0 +1,573 @@
+package org.opendedup.sdfs;
+
+import java.io.File;
+import java.io.IOException;
+import java.net.InetAddress;
+
+import javax.xml.parsers.DocumentBuilder;
+import javax.xml.parsers.DocumentBuilderFactory;
+import javax.xml.parsers.ParserConfigurationException;
+import javax.xml.transform.OutputKeys;
+import javax.xml.transform.Result;
+import javax.xml.transform.Source;
+import javax.xml.transform.Transformer;
+import javax.xml.transform.TransformerConfigurationException;
+import javax.xml.transform.TransformerException;
+import javax.xml.transform.TransformerFactory;
+import javax.xml.transform.dom.DOMSource;
+import javax.xml.transform.stream.StreamResult;
+
+import org.apache.commons.cli.CommandLine;
+import org.apache.commons.cli.CommandLineParser;
+import org.apache.commons.cli.HelpFormatter;
+import org.apache.commons.cli.OptionBuilder;
+import org.apache.commons.cli.Options;
+import org.apache.commons.cli.PosixParser;
+import org.apache.commons.cli.UnrecognizedOptionException;
+import org.opendedup.hashing.HashFunctionPool;
+import org.opendedup.hashing.HashFunctions;
+import org.opendedup.sdfs.filestore.S3ChunkStore;
+import org.opendedup.util.OSValidator;
+import org.opendedup.util.PassPhrase;
+import org.opendedup.util.StringUtils;
+import org.w3c.dom.DOMImplementation;
+import org.w3c.dom.Document;
+import org.w3c.dom.Element;
+
+public class DSEConfigWriter {
+	/**
+	 * write the client side config file
+	 * 
+	 * @param fileName
+	 * @throws Exception
+	 */
+
+	static long tbc = 1099511627776L;
+	static long gbc = 1024 * 1024 * 1024;
+	static int mbc = 1024 * 1024;
+	static int kbc = 1024;
+
+	String dse_name = null;
+	String base_path = OSValidator.getProgramBasePath() + File.separator
+			+ "dse" + File.separator + dse_name;
+	boolean chunk_store_local = true;
+	String chunk_store_data_location = null;
+	String chunk_store_hashdb_location = null;
+	int network_port = 2222;
+	String list_ip = "0.0.0.0";
+	long chunk_store_allocation_size = 0;
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/sdfs/Main.java

@@ -1,0 +1,373 @@
+package org.opendedup.sdfs;
+
+import java.io.File;
+
+import org.opendedup.hashing.HashFunctionPool;
+import org.opendedup.sdfs.filestore.gc.StandAloneGCScheduler;
+import org.opendedup.sdfs.io.AbstractStreamMatcher;
+import org.opendedup.sdfs.io.Volume;
+import org.opendedup.sdfs.notification.SDFSEvent;
+import org.opendedup.util.OSValidator;
+import org.w3c.dom.Element;
+
+/**
+ *
+ * @author Sam Silverberg Global constants used for SDFS classes.
+ *
+ */
+public class Main {
+	static {
+		if (OSValidator.isWindows()) {
+			Main.chunkStore = System.getenv("programfiles") + File.separator
+					+ "sdfs" + File.separator;
+		}
+
+	}
+
+	public static int hlVersion = 0;
+	public static boolean checkArchiveOnOpen = false;
+	public static boolean checkArchiveOnRead = true;
+	public static int hashSeed=6442;
+	public static double fpp = .01;
+	public static String logSize="10MB";
+	public static boolean ignoreDSEHTSize = true;
+	public static boolean CUCKOO =false;
+	public static long GLOBAL_CACHE_SIZE=512*1024L*1024L;
+	public static int readAheadThreads = 16;
+	public static boolean refCount = true;
+
+	public static int parallelDBCount = 4;
+	public static int writeTimeoutSeconds = -1; // 1 hour timeout
+	public static int readTimeoutSeconds = -1; // 1 hour timeout
+	// public static VolumeConfigWriterThread wth = null;
+	public static boolean runConsistancyCheck = false;
+	public static boolean blockDev = false;
+	public static AbstractStreamMatcher matcher = null;
+
+	public static boolean firstRun = true;
+	public static boolean disableGC = false;
+	public static boolean logToConsole = false;
+	public static boolean LOWMEM = false;
+	public static boolean REFRESH_BLOBS=false;
+	public static int MAX_TBLS=0;
+	public static int REPLICATION_THREADS=8;
+
+	public static boolean COMPRESS_METADATA = false;
+	public static boolean syncDL = false;
+
+	public static StandAloneGCScheduler pFullSched = null;
+
+	public static String logPath = "/var/log/sdfs/sdfs.log";
+	public static byte MAPVERSION = 0;
+
+	public static String sdfsPassword = "";
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/sdfs/VolumeConfigWriter.java

@@ -1,0 +1,1347 @@
+package org.opendedup.sdfs;
+
+import java.io.File;
+
+
+
+
+
+import java.io.IOException;
+import java.nio.file.Files;
+import java.nio.file.Path;
+import java.nio.file.Paths;
+import java.util.Random;
+
+import javax.xml.parsers.DocumentBuilder;
+import javax.xml.parsers.DocumentBuilderFactory;
+import javax.xml.parsers.ParserConfigurationException;
+import javax.xml.transform.OutputKeys;
+import javax.xml.transform.Result;
+import javax.xml.transform.Source;
+import javax.xml.transform.Transformer;
+import javax.xml.transform.TransformerFactory;
+import javax.xml.transform.dom.DOMSource;
+import javax.xml.transform.stream.StreamResult;
+
+import org.apache.commons.cli.CommandLine;
+import org.apache.commons.cli.CommandLineParser;
+import org.apache.commons.cli.HelpFormatter;
+import org.apache.commons.cli.OptionBuilder;
+import org.apache.commons.cli.Options;
+import org.apache.commons.cli.PosixParser;
+import org.opendedup.hashing.HashFunctionPool;
+import org.opendedup.hashing.HashFunctions;
+import org.opendedup.util.EncryptUtils;
+import org.opendedup.util.OSValidator;
+import org.opendedup.util.PassPhrase;
+import org.opendedup.util.StringUtils;
+import org.w3c.dom.DOMImplementation;
+import org.w3c.dom.Document;
+import org.w3c.dom.Element;
+
+import com.google.common.io.BaseEncoding;
+
+public class VolumeConfigWriter {
+	/**
+	 * write the client side config file
+	 * 
+	 * @param fileName
+	 * @throws Exception
+	 */
+	String volume_name = null;
+	String base_path = OSValidator.getProgramBasePath() + File.separator + "volumes" + File.separator + volume_name;
+	String dedup_db_store = base_path + File.separator + "ddb";
+	String io_log = base_path + File.separator + "io.log";
+	boolean safe_close = true;
+	boolean vrts_appliance = false;
+	boolean safe_sync = true;
+	int write_threads = (short) (Runtime.getRuntime().availableProcessors());
+	boolean dedup_files = true;
+	int chunk_size = 256;
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/sdfs/filestore/ChunkData.java

@@ -1,0 +1,240 @@
+package org.opendedup.sdfs.filestore;
+
+import java.io.IOException;
+import java.nio.ByteBuffer;
+
+import org.opendedup.collections.DataArchivedException;
+import org.opendedup.logging.SDFSLogger;
+import org.opendedup.sdfs.Main;
+import org.opendedup.sdfs.servers.HCServiceProxy;
+import org.opendedup.util.StringUtils;
+
+/**
+ * 
+ * @author sam silverberg Chunk block meta data is as follows: [mark of deletion
+ *         (1 byte)|hash lenth(2 bytes)|hash(32 bytes)|date added (8 bytes)|date
+ *         last claimed (8 bytes)| number of times claimed (8 bytes)|chunk len
+ *         (4 bytes)|chunk position (8 bytes)]
+ * 
+ */
+
+public class ChunkData {
+	public static final int RAWDL = 1 + 2 + 32 + 8 + 8 + 8 + 4 + 8;
+	public static final int CLAIMED_OFFSET = 1 + 2 + 32 + 8;
+	private boolean mDelete = false;
+	private short hashLen = 0;
+	private byte[] hash = null;
+	private long added = 0;
+	private long lastClaimed = 0;
+	private long numClaimed = 0;
+	public int cLen = 0;
+	private long cPos = 0;
+	private byte[] chunk = null;
+	private AbstractChunkStore writeStore = null;
+	public boolean recoverd = false;
+	public boolean blank;
+	public long references =-1;
+	public String uuid;
+	
+	public ChunkData() {
+		this.blank = true;
+	}
+
+	public ChunkData(long cPos, byte[] hash) {
+		this.cPos = cPos;
+		this.hash = hash;
+	}
+
+	public ChunkData(byte[] rawData) {
+		ByteBuffer buf = ByteBuffer.wrap(rawData);
+		byte del = buf.get();
+		if (del == 0)
+			this.mDelete = false;
+		else
+			this.mDelete = true;
+		this.hashLen = buf.getShort();
+		this.hash = new byte[hashLen];
+		buf.get(hash);
+		buf.get(new byte[32 - hashLen]);
+		added = buf.getLong();
+		lastClaimed = buf.getLong();
+		this.numClaimed = buf.getLong();
+		cLen = buf.getInt();
+		cPos = buf.getLong();
+	}
+
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/sdfs/filestore/HashBlobArchive.java

@@ -1,0 +1,2434 @@
+package org.opendedup.sdfs.filestore;
+
+import static java.lang.Math.toIntExact;
+
+import java.io.File;
+import java.io.IOException;
+import java.io.RandomAccessFile;
+import java.io.Serializable;
+import java.io.SyncFailedException;
+import java.nio.ByteBuffer;
+import java.nio.channels.ClosedChannelException;
+import java.nio.channels.FileChannel;
+import java.nio.file.Files;
+import java.nio.file.Path;
+import java.nio.file.Paths;
+import java.nio.file.StandardCopyOption;
+import java.nio.file.StandardOpenOption;
+import java.util.ArrayList;
+import java.util.Arrays;
+import java.util.Collection;
+import java.util.HashMap;
+import java.util.HashSet;
+import java.util.Map;
+import java.util.Random;
+import java.util.Set;
+import java.util.concurrent.BlockingQueue;
+import java.util.concurrent.Callable;
+import java.util.concurrent.ConcurrentHashMap;
+import java.util.concurrent.ExecutionException;
+import java.util.concurrent.LinkedBlockingQueue;
+import java.util.concurrent.RejectedExecutionHandler;
+import java.util.concurrent.SynchronousQueue;
+import java.util.concurrent.ThreadPoolExecutor;
+import java.util.concurrent.TimeUnit;
+import java.util.concurrent.atomic.AtomicInteger;
+import java.util.concurrent.atomic.AtomicLong;
+import java.util.concurrent.locks.Lock;
+import java.util.concurrent.locks.ReentrantLock;
+import java.util.concurrent.locks.ReentrantReadWriteLock;
+
+import javax.crypto.spec.IvParameterSpec;
+
+//import objectexplorer.MemoryMeasurer;
+
+import org.apache.commons.io.FileUtils;
+import org.opendedup.collections.DataArchivedException;
+import org.opendedup.collections.HashExistsException;
+import org.opendedup.collections.MapClosedException;
+import org.opendedup.collections.SimpleByteArrayLongMap;
+import org.opendedup.collections.SimpleByteArrayLongMap.KeyValuePair;
+import org.opendedup.hashing.AbstractHashEngine;
+import org.opendedup.hashing.HashFunctionPool;
+import org.opendedup.logging.SDFSLogger;
+import org.opendedup.sdfs.Main;
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/sdfs/filestore/MAzureServicePool.java

@@ -1,0 +1,122 @@
+package org.opendedup.sdfs.filestore;
+
+import java.io.IOException;
+
+import java.net.URISyntaxException;
+import java.util.ArrayList;
+import java.util.concurrent.LinkedBlockingQueue;
+import java.util.concurrent.locks.ReentrantLock;
+
+import org.opendedup.logging.SDFSLogger;
+import org.opendedup.sdfs.Main;
+
+import com.microsoft.azure.storage.*;
+import com.microsoft.azure.storage.blob.*;
+
+public class MAzureServicePool {
+
+	private int poolSize;
+	private LinkedBlockingQueue<CloudBlobContainer> passiveObjects = null;
+	private ArrayList<CloudBlobContainer> activeObjects = new ArrayList<CloudBlobContainer>();
+	private ReentrantLock alock = new ReentrantLock();
+	private CloudStorageAccount account;
+	private String bucket;
+
+	public MAzureServicePool(CloudStorageAccount account, int size,
+			String bucket) throws IOException {
+		System.setProperty("http.keepalive", "true");
+		System.setProperty("http.maxConnections", Integer.toString(size));
+		this.bucket = bucket;
+		this.account = account;
+		this.poolSize = size;
+		passiveObjects = new LinkedBlockingQueue<CloudBlobContainer>(
+				this.poolSize);
+		this.populatePool();
+	}
+
+	public void populatePool() throws IOException {
+		for (int i = 0; i < poolSize; i++) {
+			try {
+				this.passiveObjects.add(this.makeObject());
+			} catch (Exception e) {
+				SDFSLogger.getLog().error("Unable to get object out of pool ",
+						e);
+				throw new IOException(e.toString());
+
+			} finally {
+			}
+		}
+	}
+
+	public CloudBlobContainer borrowObject() throws IOException,
+			InterruptedException {
+		CloudBlobContainer hc = this.passiveObjects.take();
+		this.alock.lock();
+		this.activeObjects.add(hc);
+		this.alock.unlock();
+		return hc;
+	}
+
+	public void returnObject(CloudBlobContainer hc) throws IOException {
+		alock.lock();
+		try {
+
+			this.activeObjects.remove(hc);
+		} catch (Exception e) {
+			SDFSLogger.getLog().error("Unable to get object out of pool ", e);
+			throw new IOException(e.toString());
+
+		} finally {
+			alock.unlock();
+		}
+		try {
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/sdfs/filestore/OpenFileMonitor.java

@@ -1,0 +1,149 @@
+package org.opendedup.sdfs.filestore;
+
+import java.io.IOException;
+import java.nio.file.NoSuchFileException;
+
+import org.opendedup.logging.SDFSLogger;
+import org.opendedup.sdfs.Main;
+import org.opendedup.sdfs.io.DedupFile;
+
+/**
+ * 
+ * @author Sam Silverberg
+ * 
+ *         This class initiates a thread that is used to monitor open files
+ *         within the DedupFileStore. It will close them if left open and
+ *         untouched for longer than the @see
+ *         com.annesam.sdfs.Main#maxInactiveFileTime .
+ * 
+ */
+public class OpenFileMonitor implements Runnable {
+
+	int interval = 5000;
+	int maxInactive = 900000;
+	boolean closed = false;
+	boolean done = false;
+	Thread th = null;
+
+	/**
+	 * Instantiates the OpenFileMonitor
+	 * 
+	 * @param interval
+	 *            the interval to check for inactive files
+	 * @param maxInactive
+	 *            the maximum time allowed for a file to be inactive. Inactivity
+	 *            is determined by last accessed time.
+	 */
+	public OpenFileMonitor(int interval, int maxInactive) {
+		this.interval = interval;
+		this.maxInactive = maxInactive;
+		th = new Thread(this);
+		th.start();
+	}
+
+	@Override
+	public void run() {
+		try {
+			while (!closed) {
+				try {
+					Thread.sleep(this.interval);
+				} catch (InterruptedException e) {
+					if (this.closed)
+						break;
+				}
+				try {
+					DedupFile[] files = DedupFileStore.getArray();
+					for (int i = 0; i < files.length; i++) {
+						DedupFile df = null;
+						try {
+							df = files[i];
+							if (!Main.safeClose && this.isFileStale(df)
+									&& !df.hasOpenChannels()) {
+								try {
+									if (df != null) {
+										DedupFileStore.getDedupFile(
+												df.getMetaFile()).forceClose();
+										if (SDFSLogger.isDebug())
+											SDFSLogger
+													.getLog()
+													.debug("Closing ["
+															+ df.getMetaFile()
+																	.getPath()
+															+ "] because its stale");
+									}
+								} catch (Exception e) {
+									SDFSLogger.getLog().warn(
+											"Unable close file for "
+													+ df.getMetaFile()
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/sdfs/filestore/S3ChunkStore.java

@@ -1,0 +1,625 @@
+package org.opendedup.sdfs.filestore;
+
+import java.io.ByteArrayInputStream;
+import java.io.DataInputStream;
+import java.io.IOException;
+import java.util.concurrent.ExecutionException;
+import java.util.concurrent.atomic.AtomicLong;
+
+import org.bouncycastle.util.Arrays;
+import org.jets3t.service.S3Service;
+import org.jets3t.service.ServiceException;
+import org.jets3t.service.StorageObjectsChunk;
+import org.jets3t.service.impl.rest.httpclient.RestS3Service;
+import org.jets3t.service.model.S3Bucket;
+import org.jets3t.service.model.S3Object;
+import org.jets3t.service.model.StorageObject;
+import org.jets3t.service.security.AWSCredentials;
+import org.jets3t.service.security.AWSEC2IAMSessionCredentials;
+import org.opendedup.collections.DataArchivedException;
+import org.opendedup.logging.SDFSLogger;
+import org.opendedup.sdfs.Main;
+import org.opendedup.util.CompressionUtils;
+import org.opendedup.util.EncryptUtils;
+import org.opendedup.util.StringUtils;
+import org.w3c.dom.Element;
+
+import com.google.common.cache.CacheBuilder;
+import com.google.common.cache.CacheLoader;
+import com.google.common.cache.LoadingCache;
+
+/**
+ * 
+ * @author Sam Silverberg The S3 chunk store implements the AbstractChunkStore
+ *         and is used to store deduped chunks to AWS S3 data storage. It is
+ *         used if the aws tag is used within the chunk store config file. It is
+ *         important to make the chunk size very large on the client when using
+ *         this chunk store since S3 charges per http request.
+ * 
+ */
+public class S3ChunkStore implements AbstractChunkStore {
+	private static AWSCredentials awsCredentials = null;
+	private String name;
+	private S3ServicePool pool = null;
+	private AtomicLong currentLength = new AtomicLong(0);
+	private AtomicLong compressedLength = new AtomicLong(0);
+	private int cacheSize = 10485760 / Main.CHUNK_LENGTH;
+
+	LoadingCache<String, byte[]> chunks = CacheBuilder.newBuilder()
+			.maximumSize(cacheSize).concurrencyLevel(72)
+			.build(new CacheLoader<String, byte[]>() {
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/sdfs/filestore/S3ChunkStoreUtils.java

@@ -1,0 +1,95 @@
+package org.opendedup.sdfs.filestore;
+
+import org.apache.commons.cli.CommandLine;
+
+import org.apache.commons.cli.CommandLineParser;
+import org.apache.commons.cli.HelpFormatter;
+import org.apache.commons.cli.OptionBuilder;
+import org.apache.commons.cli.Options;
+import org.apache.commons.cli.PosixParser;
+import org.jets3t.service.S3Service;
+import org.jets3t.service.ServiceException;
+import org.jets3t.service.impl.rest.httpclient.RestS3Service;
+import org.jets3t.service.model.S3Object;
+import org.jets3t.service.security.AWSCredentials;
+import org.opendedup.logging.SDFSLogger;
+
+public class S3ChunkStoreUtils {
+	@SuppressWarnings("static-access")
+	public static Options buildOptions() {
+		Options options = new Options();
+		options.addOption(OptionBuilder.withLongOpt("help")
+				.withDescription("Display these options.").hasArg(false)
+				.create());
+		options.addOption(OptionBuilder.withLongOpt("delete-bucket")
+				.withDescription("Delete a  non-empty S3 bucket").hasArg()
+				.withArgName("PATH").create());
+		options.addOption(OptionBuilder
+				.withLongOpt("aws-secret-key")
+				.withDescription(
+						"Set to the value of Amazon S3 Cloud Storage secret key. aws-enabled, aws-access-key, and aws-bucket-name will also need to be set. ")
+				.hasArg().withArgName("S3 Secret Key").create());
+		options.addOption(OptionBuilder
+				.withLongOpt("aws-access-key")
+				.withDescription(
+						"Set to the value of Amazon S3 Cloud Storage access key. aws-enabled, aws-secret-key, and aws-bucket-name will also need to be set. ")
+				.hasArg().withArgName("S3 Access Key").create());
+		options.addOption(OptionBuilder
+				.withLongOpt("aws-bucket-name")
+				.withDescription(
+						"Set to the value of Amazon S3 Cloud Storage bucket name. This will need to be unique and a could be set the the access key if all else fails. aws-enabled, aws-secret-key, and aws-secret-key will also need to be set. ")
+				.hasArg().withArgName("Unique S3 Bucket Name").create());
+		return options;
+	}
+
+	private static void printHelp(Options options) {
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/sdfs/filestore/cloud/BatchAliChunkStore.java

@@ -1,0 +1,2623 @@
+/*******************************************************************************
+ * Copyright (C) 2016 Sam Silverberg sam.silverberg@gmail.com
+ *
+ * This file is part of OpenDedupe SDFS.
+ *
+ * OpenDedupe SDFS is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * OpenDedupe SDFS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with Foobar.  If not, see <http://www.gnu.org/licenses/>.
+ *******************************************************************************/
+package org.opendedup.sdfs.filestore.cloud;
+
+import static java.lang.Math.toIntExact;
+
+
+
+import java.io.BufferedInputStream;
+import java.io.BufferedOutputStream;
+import java.io.ByteArrayInputStream;
+import java.io.ByteArrayOutputStream;
+import java.io.DataInputStream;
+import java.io.File;
+import java.io.FileInputStream;
+import java.io.FileOutputStream;
+import java.io.IOException;
+import java.io.InputStream;
+import java.io.ObjectInputStream;
+import java.io.ObjectOutputStream;
+import java.net.InetAddress;
+import java.nio.ByteBuffer;
+import java.nio.file.Files;
+import java.nio.file.LinkOption;
+import java.nio.file.Path;
+import java.nio.file.Paths;
+import java.nio.file.StandardCopyOption;
+import java.nio.file.attribute.PosixFileAttributes;
+import java.security.NoSuchAlgorithmException;
+import java.security.SecureRandom;
+import java.util.ArrayList;
+import java.util.Arrays;
+import java.util.HashMap;
+import java.util.HashSet;
+import java.util.Iterator;
+import java.util.List;
+import java.util.Map;
+import java.util.Properties;
+import java.util.Set;
+import java.util.StringTokenizer;
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/sdfs/filestore/cloud/BatchAwsS3ChunkStore.java

@@ -1,0 +1,3272 @@
+/*******************************************************************************
+ * Copyright (C) 2016 Sam Silverberg sam.silverberg@gmail.com
+ *
+ * This file is part of OpenDedupe SDFS.
+ *
+ * OpenDedupe SDFS is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * OpenDedupe SDFS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with Foobar.  If not, see <http://www.gnu.org/licenses/>.
+ *******************************************************************************/
+package org.opendedup.sdfs.filestore.cloud;
+
+import java.io.BufferedInputStream;
+
+import java.io.BufferedOutputStream;
+import java.io.ByteArrayInputStream;
+import java.io.ByteArrayOutputStream;
+import java.io.DataInputStream;
+import java.io.File;
+import java.io.FileInputStream;
+import java.io.FileOutputStream;
+import java.io.IOException;
+import java.io.InputStream;
+import java.io.ObjectInputStream;
+import java.io.ObjectOutputStream;
+import java.net.InetAddress;
+import java.nio.ByteBuffer;
+import java.nio.file.Files;
+import java.nio.file.LinkOption;
+import java.nio.file.Path;
+import java.nio.file.Paths;
+import java.nio.file.StandardCopyOption;
+import java.nio.file.attribute.PosixFileAttributes;
+import java.security.NoSuchAlgorithmException;
+import java.security.SecureRandom;
+import java.security.cert.X509Certificate;
+import java.util.ArrayList;
+import java.util.Arrays;
+import java.util.HashMap;
+import java.util.HashSet;
+import java.util.Iterator;
+import java.util.List;
+import java.util.Map;
+import java.util.Properties;
+import java.util.Set;
+import java.util.StringTokenizer;
+import java.util.WeakHashMap;
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/sdfs/filestore/cloud/utils/EncyptUtils.java

@@ -1,0 +1,168 @@
+/*******************************************************************************
+ * Copyright (C) 2016 Sam Silverberg sam.silverberg@gmail.com	
+ *
+ * This file is part of OpenDedupe SDFS.
+ *
+ * OpenDedupe SDFS is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * OpenDedupe SDFS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with Foobar.  If not, see <http://www.gnu.org/licenses/>.
+ *******************************************************************************/
+package org.opendedup.sdfs.filestore.cloud.utils;
+
+import java.io.IOException;
+
+import org.opendedup.util.EncryptUtils;
+
+import com.google.common.io.BaseEncoding;
+
+public class EncyptUtils {
+	public static boolean baseEncode = false;
+
+	public static String encString(String hashes, boolean enc)
+			throws IOException {
+		if (baseEncode)
+			return hashes;
+		if (enc) {
+			byte[] encH = EncryptUtils.encryptCBC(hashes.getBytes());
+			if (baseEncode)
+				return BaseEncoding.base64().encode(encH);
+			else
+				return BaseEncoding.base64Url().encode(encH);
+
+		} else {
+			return BaseEncoding.base64Url().encode(hashes.getBytes());
+
+		}
+	}
+
+	public static String decString(String fname, boolean enc)
+			throws IOException {
+		if (baseEncode)
+			return fname;
+		if (enc) {
+			byte[] encH;
+			if (baseEncode)
+				encH = BaseEncoding.base64().decode(fname);
+			else
+				encH = BaseEncoding.base64Url().decode(fname);
+			String st = new String(EncryptUtils.decryptCBC(encH));
+			return st;
+		} else {
+
+			byte[] encH;
+			encH = BaseEncoding.base64Url().decode(fname);
+			return new String(encH);
+		}
+	}
+
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/sdfs/filestore/cloud/utils/FileUtils.java

@@ -1,0 +1,154 @@
+/*******************************************************************************
+ * Copyright (C) 2016 Sam Silverberg sam.silverberg@gmail.com	
+ *
+ * This file is part of OpenDedupe SDFS.
+ *
+ * OpenDedupe SDFS is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * OpenDedupe SDFS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with Foobar.  If not, see <http://www.gnu.org/licenses/>.
+ *******************************************************************************/
+package org.opendedup.sdfs.filestore.cloud.utils;
+
+import java.io.File;
+
+import java.io.FileInputStream;
+import java.io.IOException;
+import java.nio.ByteBuffer;
+import java.nio.file.Files;
+import java.nio.file.LinkOption;
+import java.nio.file.Path;
+import java.nio.file.attribute.UserDefinedFileAttributeView;
+import java.security.MessageDigest;
+import java.util.Arrays;
+import java.util.HashMap;
+import java.util.List;
+import java.util.Map;
+import java.util.Set;
+
+import org.opendedup.util.OSValidator;
+
+import org.opendedup.sdfs.filestore.cloud.utils.EncyptUtils;
+
+public class FileUtils {
+	// private static final String STATTR="DSHSTR";
+	private static final String BATTR = "DSHBAR";
+	private static final String IATTR = "DSHINT";
+	private static final String LATTR = "DSHLNG";
+
+	public static HashMap<String, String> getFileMetaData(File file,
+			boolean encrypt) throws IOException {
+		HashMap<String, String> md = new HashMap<String, String>();
+		if (OSValidator.isUnix()) {
+			boolean isSymbolicLink = Files.isSymbolicLink(file.toPath());
+			if (isSymbolicLink)
+				return md;
+			else {
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/sdfs/filestore/gc/GCMain.java

@@ -1,0 +1,28 @@
+/*******************************************************************************
+ * Copyright (C) 2016 Sam Silverberg sam.silverberg@gmail.com	
+ *
+ * This file is part of OpenDedupe SDFS.
+ *
+ * OpenDedupe SDFS is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * OpenDedupe SDFS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with Foobar.  If not, see <http://www.gnu.org/licenses/>.
+ *******************************************************************************/
+package org.opendedup.sdfs.filestore.gc;
+
+import java.util.concurrent.locks.ReentrantLock;
+import java.util.concurrent.locks.ReentrantReadWriteLock;
+
+public class GCMain {
+	public static final ReentrantReadWriteLock gclock = new ReentrantReadWriteLock();
+	public static final ReentrantLock gcRunningLock = new ReentrantLock();
+
+}

### 2018-12-12 code/SDFS/src/org/opendedup/sdfs/filestore/gc/ManualGC.java

@@ -1,0 +1,158 @@
+/*******************************************************************************
+ * Copyright (C) 2016 Sam Silverberg sam.silverberg@gmail.com	
+ *
+ * This file is part of OpenDedupe SDFS.
+ *
+ * OpenDedupe SDFS is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * OpenDedupe SDFS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with Foobar.  If not, see <http://www.gnu.org/licenses/>.
+ *******************************************************************************/
+package org.opendedup.sdfs.filestore.gc;
+
+import java.io.IOException;
+
+
+import java.util.concurrent.locks.Lock;
+
+import org.opendedup.logging.SDFSLogger;
+import org.opendedup.sdfs.Main;
+import org.opendedup.sdfs.filestore.DedupFileStore;
+import org.opendedup.sdfs.notification.SDFSEvent;
+import org.opendedup.sdfs.servers.HCServiceProxy;
+
+public class ManualGC {
+
+	
+	public static SDFSEvent evt = null;
+	private static long lastGC = 0;
+	//private static long MINGCTIME = 60*1000*60;
+	private static long MINGCTIME = 1;
+	public static long clearChunks(boolean compact) throws InterruptedException, IOException {
+		return clearChunksMills(compact);
+	}
+
+	public static synchronized long clearChunksMills(boolean compact)
+			throws InterruptedException, IOException {
+		Lock l = null;
+			l = GCMain.gclock.writeLock();
+
+		
+		l.lock();
+		try {
+			
+			long rm = 0;
+			long dur = System.currentTimeMillis()- lastGC;
+			if (Main.disableGC) {
+				evt = SDFSEvent
+						.gcInfoEvent("SDFS Volume Cleanup not enabled for this volume "
+								+ Main.volume.getName());
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/sdfs/filestore/gc/StandAloneGCScheduler.java

@@ -1,0 +1,71 @@
+/*******************************************************************************
+ * Copyright (C) 2016 Sam Silverberg sam.silverberg@gmail.com	
+ *
+ * This file is part of OpenDedupe SDFS.
+ *
+ * OpenDedupe SDFS is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * OpenDedupe SDFS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with Foobar.  If not, see <http://www.gnu.org/licenses/>.
+ *******************************************************************************/
+package org.opendedup.sdfs.filestore.gc;
+
+import org.opendedup.logging.SDFSLogger;
+
+import org.opendedup.sdfs.Main;
+
+public class StandAloneGCScheduler implements Runnable {
+	private GCControllerImpl gcController = null;
+	private boolean closed = false;
+	Thread th = null;
+	public SDFSGCScheduler gcSched = null;
+
+	public void recalcScheduler() {
+		gcController.reCalc();
+	}
+
+	public StandAloneGCScheduler() throws InstantiationException,
+			IllegalAccessException, ClassNotFoundException {
+		gcController = (GCControllerImpl) Class.forName(Main.gcClass)
+				.newInstance();
+		SDFSLogger.getLog().info(
+				"Using " + Main.gcClass + " for DSE Garbage Collection");
+		th = new Thread(this);
+		try {
+			th.setPriority(Thread.MAX_PRIORITY);
+		} catch (Throwable e) {
+			SDFSLogger.getLog().info(
+					"unable to set priority for Standalone GC Sceduler ");
+		}
+		SDFSLogger.getLog().info("GC Thread priority is " + th.getPriority());
+		th.start();
+		gcSched = new SDFSGCScheduler();
+	}
+
+	@Override
+	public void run() {
+		while (!closed) {
+			gcController.runGC();
+			try {
+				Thread.sleep(30 * 1000);
+			} catch (InterruptedException e) {
+				closed = true;
+			}
+		}
+	}
+
+	public void close() {
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/sdfs/io/AsyncChunkWriteActionListener.java

@@ -1,0 +1,62 @@
+/*******************************************************************************
+ * Copyright (C) 2016 Sam Silverberg sam.silverberg@gmail.com	
+ *
+ * This file is part of OpenDedupe SDFS.
+ *
+ * OpenDedupe SDFS is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * OpenDedupe SDFS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with Foobar.  If not, see <http://www.gnu.org/licenses/>.
+ *******************************************************************************/
+package org.opendedup.sdfs.io;
+
+import java.util.concurrent.atomic.AtomicInteger;
+
+import org.opendedup.collections.DataArchivedException;
+import org.opendedup.hashing.Finger;
+
+public abstract class AsyncChunkWriteActionListener {
+	AtomicInteger dn = new AtomicInteger(0);
+	AtomicInteger exdn = new AtomicInteger(0);
+	DataArchivedException dar = null;
+	int sz = 0;
+
+	public abstract void commandException(Finger result, Throwable e);
+
+	public abstract void commandResponse(Finger result);
+
+	public abstract void commandArchiveException(DataArchivedException e);
+
+	public int incrementandGetDN() {
+		return dn.incrementAndGet();
+	}
+
+	public int getDN() {
+		return dn.get();
+	}
+
+	public int incrementAndGetDNEX() {
+		return exdn.incrementAndGet();
+	}
+
+	public int getDNEX() {
+		return exdn.get();
+	}
+
+	public int getMaxSz() {
+		return this.sz;
+	}
+
+	public void setMaxSize(int sz) {
+		this.sz = sz;
+	}
+
+}

### 2018-12-12 code/SDFS/src/org/opendedup/sdfs/io/BufferClosedException.java

@@ -1,0 +1,34 @@
+/*******************************************************************************
+ * Copyright (C) 2016 Sam Silverberg sam.silverberg@gmail.com	
+ *
+ * This file is part of OpenDedupe SDFS.
+ *
+ * OpenDedupe SDFS is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * OpenDedupe SDFS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with Foobar.  If not, see <http://www.gnu.org/licenses/>.
+ *******************************************************************************/
+package org.opendedup.sdfs.io;
+
+/**
+ * 
+ * @author Sam Silverberg This exception is thrown if a WritableCacheBuffer has
+ *         already been closed for writing to a chunk store.
+ */
+public class BufferClosedException extends Exception {
+
+	private static final long serialVersionUID = 1L;
+
+	public BufferClosedException(String msg) {
+		super(msg);
+	}
+
+}

### 2018-12-12 code/SDFS/src/org/opendedup/sdfs/io/DedupChunkInterface.java

@@ -1,0 +1,150 @@
+/*******************************************************************************
+ * Copyright (C) 2016 Sam Silverberg sam.silverberg@gmail.com	
+ *
+ * This file is part of OpenDedupe SDFS.
+ *
+ * OpenDedupe SDFS is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * OpenDedupe SDFS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with Foobar.  If not, see <http://www.gnu.org/licenses/>.
+ *******************************************************************************/
+package org.opendedup.sdfs.io;
+
+import java.io.IOException;
+
+
+
+import java.util.TreeMap;
+
+import org.opendedup.collections.DataArchivedException;
+
+public interface DedupChunkInterface {
+
+	/**
+	 * 
+	 * @return gets the lenth of the DedupChunk
+	 */
+	public abstract int getLength();
+
+	public boolean getReconstructed();
+
+	public void setReconstructed(boolean re);
+
+	/**
+	 * 
+	 * @return the file position within the DedupFile
+	 */
+	public abstract long getFilePosition();
+
+	public abstract byte[] getReadChunk(int start, int end) throws IOException,
+			BufferClosedException, DataArchivedException;
+
+	public TreeMap<Integer,HashLocPair> getFingers();
+
+	/**
+	 * 
+	 * @param length
+	 *            the length of the dedup chunk
+	 */
+	public abstract void setLength(int length);
+
+	/**
+	 * 
+	 * @return if this is a new chunk or one retrieved from the chunk store
+	 *         service
+	 */
+	public abstract boolean isNewChunk();
+
+	/**
+	 * 
+	 * @param newChunk
+	 *            sets the chunk as new
+	 */
+	public abstract void setNewChunk(boolean newChunk);
+
+	/**
+	 * sets the chunk as writable
+	 * 
+	 * @param writable
+	 *            true if writable
+	 */
+	public abstract void setWritable(boolean writable);
+
+	/**
+	 * 
+	 * @return true if the chunk is writable
+	 */
+
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/sdfs/io/DedupFileListener.java

@@ -1,0 +1,47 @@
+/*******************************************************************************
+ * Copyright (C) 2016 Sam Silverberg sam.silverberg@gmail.com	
+ *
+ * This file is part of OpenDedupe SDFS.
+ *
+ * OpenDedupe SDFS is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * OpenDedupe SDFS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with Foobar.  If not, see <http://www.gnu.org/licenses/>.
+ *******************************************************************************/
+package org.opendedup.sdfs.io;
+
+public interface DedupFileListener {
+	void onCreate(DedupFile file);
+
+	void onCopyTo(String dst, DedupFile file);
+
+	void onAddLock(long position, long len, boolean shared, DedupFileLock lock,
+			DedupFile file);
+
+	void onCreateBlankFile(long size, DedupFile file);
+
+	void onDelete(DedupFile file);
+
+	void onForceClose(DedupFile file);
+
+	void onRemoveHash(long position, DedupFile file);
+
+	void onRemoveLock(DedupFileLock lock, DedupFile file);
+
+	void onSnapShot(MetaDataDedupFile mf, DedupFile file);
+
+	void onSync(DedupFile file);
+
+	void onTruncate(long length, DedupFile file);
+
+	void onUpdateMap(DedupChunkInterface writeBuffer, byte[] hash,
+			boolean doop, DedupFile file);
+}

### 2018-12-12 code/SDFS/src/org/opendedup/sdfs/io/MetaDataDedupFile.java

@@ -1,0 +1,1811 @@
+/*******************************************************************************
+ * Copyright (C) 2016 Sam Silverberg sam.silverberg@gmail.com	
+ *
+ * This file is part of OpenDedupe SDFS.
+ *
+ * OpenDedupe SDFS is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * OpenDedupe SDFS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with Foobar.  If not, see <http://www.gnu.org/licenses/>.
+ *******************************************************************************/
+package org.opendedup.sdfs.io;
+
+import java.io.File;
+
+import java.io.FileInputStream;
+import java.io.FileOutputStream;
+import java.io.IOException;
+import java.io.ObjectInput;
+import java.io.ObjectInputStream;
+import java.io.ObjectOutput;
+import java.io.ObjectOutputStream;
+import java.net.URLEncoder;
+import java.nio.file.Files;
+import java.nio.file.LinkOption;
+import java.nio.file.Path;
+import java.nio.file.Paths;
+import java.nio.file.StandardCopyOption;
+import java.nio.file.attribute.BasicFileAttributes;
+import java.time.Instant;
+import java.time.format.DateTimeFormatter;
+import java.util.HashMap;
+import java.util.Iterator;
+import java.util.Map;
+import java.util.Map.Entry;
+import java.util.UUID;
+import java.util.concurrent.atomic.AtomicLong;
+import java.util.concurrent.locks.ReentrantLock;
+
+import javax.xml.parsers.ParserConfigurationException;
+
+import org.apache.commons.io.FileUtils;
+import org.apache.commons.lang3.StringEscapeUtils;
+import org.apache.commons.lang3.StringUtils;
+import org.opendedup.collections.HashtableFullException;
+import org.opendedup.logging.SDFSLogger;
+import org.opendedup.sdfs.Main;
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/sdfs/io/SparseDedupFile.java

@@ -1,0 +1,1386 @@
+/*******************************************************************************
+ * Copyright (C) 2016 Sam Silverberg sam.silverberg@gmail.com	
+ *
+ * This file is part of OpenDedupe SDFS.
+ *
+ * OpenDedupe SDFS is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * OpenDedupe SDFS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with Foobar.  If not, see <http://www.gnu.org/licenses/>.
+ *******************************************************************************/
+package org.opendedup.sdfs.io;
+
+import java.io.BufferedReader;
+import java.io.BufferedWriter;
+import java.io.FileReader;
+import java.io.FileWriter;
+import java.io.IOException;
+import java.text.SimpleDateFormat;
+import java.util.*;
+import java.io.File;
+import java.io.IOException;
+import java.security.MessageDigest;
+import java.util.concurrent.BlockingQueue;
+import java.util.concurrent.ConcurrentHashMap;
+import java.util.concurrent.ExecutionException;
+import java.util.concurrent.SynchronousQueue;
+import java.util.concurrent.ThreadPoolExecutor;
+import java.util.concurrent.TimeUnit;
+import java.util.concurrent.locks.Lock;
+import java.util.concurrent.locks.ReentrantLock;
+import java.util.concurrent.locks.ReentrantReadWriteLock;
+
+import com.google.common.primitives.Longs;
+import org.opendedup.collections.ByteArrayWrapper;
+import org.opendedup.collections.DataArchivedException;
+import org.opendedup.collections.DataMapInterface;
+import org.opendedup.collections.HashtableFullException;
+import org.opendedup.collections.LongByteArrayMap;
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/sdfs/io/Volume.java

@@ -1,0 +1,859 @@
+/*******************************************************************************
+ * Copyright (C) 2016 Sam Silverberg sam.silverberg@gmail.com	
+ *
+ * This file is part of OpenDedupe SDFS.
+ *
+ * OpenDedupe SDFS is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * OpenDedupe SDFS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with Foobar.  If not, see <http://www.gnu.org/licenses/>.
+ *******************************************************************************/
+package org.opendedup.sdfs.io;
+
+import java.io.File;
+import java.io.IOException;
+import java.net.InetSocketAddress;
+import java.nio.file.Paths;
+import java.util.ArrayList;
+import java.util.Random;
+import java.util.concurrent.atomic.AtomicLong;
+import java.util.concurrent.locks.ReentrantLock;
+
+import javax.xml.parsers.ParserConfigurationException;
+
+import org.apache.ignite.Ignite;
+import org.opendedup.hashing.HashFunctionPool;
+import org.opendedup.logging.SDFSLogger;
+import org.opendedup.sdfs.Main;
+import org.opendedup.sdfs.filestore.DedupFileStore;
+import org.opendedup.sdfs.monitor.VolumeIOMeter;
+import org.opendedup.sdfs.notification.SDFSEvent;
+import org.opendedup.sdfs.servers.HCServiceProxy;
+import org.opendedup.util.FileCounts;
+import org.opendedup.util.RandomGUID;
+import org.opendedup.util.StorageUnit;
+import org.opendedup.util.StringUtils;
+import org.opendedup.util.XMLUtils;
+import org.w3c.dom.Document;
+import org.w3c.dom.Element;
+import org.w3c.dom.NodeList;
+
+import com.google.common.util.concurrent.AtomicDouble;
+
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/sdfs/io/events/MFileRenamed.java

@@ -1,0 +1,60 @@
+/*******************************************************************************
+ * Copyright (C) 2016 Sam Silverberg sam.silverberg@gmail.com	
+ *
+ * This file is part of OpenDedupe SDFS.
+ *
+ * OpenDedupe SDFS is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * OpenDedupe SDFS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with Foobar.  If not, see <http://www.gnu.org/licenses/>.
+ *******************************************************************************/
+package org.opendedup.sdfs.io.events;
+
+import org.opendedup.sdfs.Main;
+import org.opendedup.sdfs.io.MetaDataDedupFile;
+
+import com.google.gson.FieldNamingPolicy;
+import com.google.gson.Gson;
+import com.google.gson.GsonBuilder;
+import com.google.gson.JsonObject;
+
+public class MFileRenamed extends GenericEvent {
+
+	public MetaDataDedupFile mf;
+	public String from;
+	public String to;
+	private static final int pl = Main.volume.getPath().length();
+
+	public MFileRenamed(MetaDataDedupFile f, String from, String to) {
+		super();
+		this.mf = f;
+		this.from = from;
+		this.to = to;
+	}
+
+	public String toJSON() {
+		JsonObject dataset = this.toJSONObject();
+		dataset.addProperty("actionType", "mfileRename");
+		dataset.addProperty("object", mf.getPath().substring(pl));
+		dataset.addProperty("from", this.from.substring(pl));
+		dataset.addProperty("to", this.to.substring(pl));
+		if (mf.isSymlink())
+			dataset.addProperty("fileType", "symlink");
+		else if (mf.isDirectory())
+			dataset.addProperty("fileType", "dir");
+		else
+			dataset.addProperty("fileType", "file");
+		Gson gson = new GsonBuilder().setPrettyPrinting().serializeNulls()
+				.setFieldNamingPolicy(FieldNamingPolicy.UPPER_CAMEL_CASE)
+				.create();
+		return gson.toJson(dataset);
+	}
+}

### 2018-12-12 code/SDFS/src/org/opendedup/sdfs/io/events/MFileWritten.java

@@ -1,0 +1,62 @@
+/*******************************************************************************
+ * Copyright (C) 2016 Sam Silverberg sam.silverberg@gmail.com	
+ *
+ * This file is part of OpenDedupe SDFS.
+ *
+ * OpenDedupe SDFS is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * OpenDedupe SDFS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with Foobar.  If not, see <http://www.gnu.org/licenses/>.
+ *******************************************************************************/
+package org.opendedup.sdfs.io.events;
+
+import java.io.File;
+
+import org.opendedup.sdfs.Main;
+import org.opendedup.sdfs.io.MetaDataDedupFile;
+
+import com.google.gson.FieldNamingPolicy;
+import com.google.gson.Gson;
+import com.google.gson.GsonBuilder;
+import com.google.gson.JsonObject;
+
+public class MFileWritten extends GenericEvent {
+	public MetaDataDedupFile mf;
+	public boolean dirty;
+
+	public MFileWritten(MetaDataDedupFile f,boolean dirty) {
+		super();
+		this.mf = f;
+		this.dirty = dirty;
+	}
+
+	public String toJSON() {
+		String fl = new File(mf.getPath()).getPath().substring(Main.volume.getPath().length());
+		while(fl.startsWith("/") || fl.startsWith("\\"))
+			fl =fl.substring(1, fl.length());
+		JsonObject dataset = this.toJSONObject();
+		dataset.addProperty("actionType", "mfileWritten");
+		dataset.addProperty("object", fl);
+		
+		if (mf.isSymlink())
+			dataset.addProperty("fileType", "symlink");
+		else if (mf.isDirectory())
+			dataset.addProperty("fileType", "dir");
+		else {
+			dataset.addProperty("fileType", "file");
+			dataset.addProperty("size", mf.length());
+		}
+			Gson gson = new GsonBuilder().setPrettyPrinting().serializeNulls()
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/sdfs/io/events/SFileDeleted.java

@@ -1,0 +1,52 @@
+/*******************************************************************************
+ * Copyright (C) 2016 Sam Silverberg sam.silverberg@gmail.com	
+ *
+ * This file is part of OpenDedupe SDFS.
+ *
+ * OpenDedupe SDFS is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * OpenDedupe SDFS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with Foobar.  If not, see <http://www.gnu.org/licenses/>.
+ *******************************************************************************/
+package org.opendedup.sdfs.io.events;
+
+import java.io.File;
+
+import org.opendedup.sdfs.Main;
+import org.opendedup.sdfs.io.SparseDedupFile;
+
+import com.google.gson.FieldNamingPolicy;
+import com.google.gson.Gson;
+import com.google.gson.GsonBuilder;
+import com.google.gson.JsonObject;
+
+public class SFileDeleted extends GenericEvent{
+	public SparseDedupFile sf = null;
+	public String sfp = null;
+
+	public SFileDeleted(SparseDedupFile sf) {
+		this.sf = sf;
+		sfp = Main.dedupDBStore + File.separator
+				+ this.sf.getGUID().substring(0, 2) + File.separator
+				+ this.sf.getGUID()+ File.separator + this.sf.getGUID()+".map";
+	}
+
+	public String toJSON() {
+		JsonObject dataset = this.toJSONObject();
+		dataset.addProperty("actionType", "sfileDeleted");
+		dataset.addProperty("object", this.sf.getGUID());
+		Gson gson = new GsonBuilder().setPrettyPrinting().serializeNulls()
+				.setFieldNamingPolicy(FieldNamingPolicy.UPPER_CAMEL_CASE)
+				.create();
+		return gson.toJson(dataset);
+	}
+
+}

### 2018-12-12 code/SDFS/src/org/opendedup/sdfs/io/events/SFileSync.java

@@ -1,0 +1,30 @@
+/*******************************************************************************
+ * Copyright (C) 2016 Sam Silverberg sam.silverberg@gmail.com	
+ *
+ * This file is part of OpenDedupe SDFS.
+ *
+ * OpenDedupe SDFS is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * OpenDedupe SDFS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with Foobar.  If not, see <http://www.gnu.org/licenses/>.
+ *******************************************************************************/
+package org.opendedup.sdfs.io.events;
+
+import java.io.File;
+
+public class SFileSync {
+	public File sf = null;
+
+	public SFileSync(File f) {
+		this.sf = f;
+	}
+
+}

### 2018-12-12 code/SDFS/src/org/opendedup/sdfs/mgmt/CloseFile.java

@@ -1,0 +1,50 @@
+package org.opendedup.sdfs.mgmt;
+
+import java.io.File;
+import java.io.IOException;
+
+import org.opendedup.logging.SDFSLogger;
+import org.opendedup.sdfs.Main;
+import org.opendedup.sdfs.filestore.MetaFileStore;
+import org.opendedup.sdfs.io.DedupFileChannel;
+import org.opendedup.sdfs.io.MetaDataDedupFile;
+import org.opendedup.util.XMLUtils;
+import org.w3c.dom.Document;
+import org.w3c.dom.Element;
+
+public class CloseFile {
+
+	public static MetaDataDedupFile lastClosedFile = null;
+
+	public Element getResult(String cmd, boolean written, String file, long fd) throws IOException {
+		try {
+			if (fd != -1) {
+				DedupFileChannel ch = OpenFile.OpenChannels.remove(fd);
+				ch.getDedupFile().unRegisterChannel(ch, -33);
+			}
+			Document doc = XMLUtils.getXMLDoc("close-file");
+			Element root = doc.getDocumentElement();
+			File f = new File(Main.volume.getPath() + File.separator + file);
+			CopyExtents.writeChannels.invalidate(f.getPath());
+			MetaDataDedupFile mf = MetaFileStore.getMF(f);
+			close(mf, written);
+			return (Element) root.cloneNode(true);
+		} catch (Exception e) {
+			SDFSLogger.getLog().error("unable to fulfill request on file " + file, e);
+			throw new IOException("request to fetch attributes failed because " + e.toString());
+		}
+	}
+
+	public static void close(MetaDataDedupFile mf, boolean written) throws IOException {
+
+		if (written) {
+			mf.setRetentionLock();
+			mf.setDirty(true);
+			mf.unmarshal();
+			if (mf.exists() && (mf.getName().endsWith("F1.img") || mf.getName().startsWith("BEOST_"))) {
+				lastClosedFile = mf;
+			}
+		}
+	}
+
+}

### 2018-12-12 code/SDFS/src/org/opendedup/sdfs/mgmt/GetConnectedVolumes.java

@@ -1,0 +1,49 @@
+package org.opendedup.sdfs.mgmt;
+
+import java.io.IOException;
+
+
+
+import org.opendedup.logging.SDFSLogger;
+import org.opendedup.sdfs.Main;
+import org.opendedup.sdfs.filestore.cloud.FileReplicationService;
+import org.opendedup.sdfs.filestore.cloud.RemoteVolumeInfo;
+import org.opendedup.util.XMLUtils;
+import org.w3c.dom.Document;
+import org.w3c.dom.Element;
+
+public class GetConnectedVolumes {
+
+	public Element getResult() throws IOException {
+		try {
+			Document doc = XMLUtils.getXMLDoc("volumes");
+			Element root = doc.getDocumentElement();
+			RemoteVolumeInfo [] l = FileReplicationService.getConnectedVolumes();
+			if(l != null) {
+				for(RemoteVolumeInfo vl : l) {
+					Element el = doc.createElement("volume");
+					el.setAttribute("id", Long.toString(vl.id));
+					if(vl.id == Main.DSEID)
+						el.setAttribute("local", "true");
+					else
+						el.setAttribute("local", "false");
+					el.setAttribute("hostname", vl.hostname);
+					el.setAttribute("port", Integer.toString(vl.port));
+					el.setAttribute("size", Long.toString(vl.data));
+					el.setAttribute("compressed-size", Long.toString(vl.compressed));
+					el.setAttribute("sdfsversion", vl.sdfsversion);
+					el.setAttribute("version",Integer.toString(vl.version));
+					el.setAttribute("lastupdated", Long.toString(vl.lastupdated));
+					root.appendChild(el);
+				}
+			}
+			return (Element) root.cloneNode(true);
+		} catch (Exception e) {
+			SDFSLogger.getLog().error(
+					"unable to fulfill request", e);
+			throw new IOException("request to fetch attributes failed because "
+					+ e.toString());
+		}
+	}
+
+}

### 2018-12-12 code/SDFS/src/org/opendedup/sdfs/mgmt/GetDSE.java

@@ -1,0 +1,63 @@
+package org.opendedup.sdfs.mgmt;
+
+import java.io.IOException;
+
+import org.opendedup.hashing.HashFunctionPool;
+import org.opendedup.sdfs.Main;
+import org.opendedup.sdfs.servers.HCServiceProxy;
+import org.opendedup.util.XMLUtils;
+import org.w3c.dom.Document;
+import org.w3c.dom.Element;
+
+public class GetDSE {
+
+	public Element getResult(String cmd, String file) throws IOException {
+		try {
+			Document doc = XMLUtils.getXMLDoc("dse");
+			Element root = doc.getDocumentElement();
+			if (HashFunctionPool.max_hash_cluster == 1)
+				root.setAttribute(
+						"max-size",
+						Long.toString(HCServiceProxy.getMaxSize()
+								* HCServiceProxy.getPageSize()));
+			else
+				root.setAttribute(
+						"max-size",
+						Long.toString(HCServiceProxy.getMaxSize()
+								* HashFunctionPool.avg_page_size));
+			root.setAttribute("current-size",
+					Long.toString(HCServiceProxy.getChunkStore().size()));
+			root.setAttribute("entries", Long.toString(HCServiceProxy.getSize()));
+			root.setAttribute("compressed-size", Long.toString(HCServiceProxy
+					.getChunkStore().compressedSize()));
+			root.setAttribute("free-blocks",
+					Long.toString(HCServiceProxy.getFreeBlocks()));
+			root.setAttribute("page-size",
+					Long.toString(HCServiceProxy.getPageSize()));
+			root.setAttribute("storage-type", Main.chunkStoreClass);
+			root.setAttribute("listen-port", Integer.toString(Main.sdfsCliPort));
+			root.setAttribute("listen-hostname", Main.sdfsCliListenAddr);
+			root.setAttribute("read-speed",
+					Integer.toString(HCServiceProxy.getReadSpeed()));
+			root.setAttribute("write-speed",
+					Integer.toString(HCServiceProxy.getWriteSpeed()));
+			root.setAttribute("cache-size",
+					Long.toString(HCServiceProxy.getCacheSize()));
+			root.setAttribute("max-cache-size",
+					Long.toString(HCServiceProxy.getMaxCacheSize()));
+			root.setAttribute("listen-encrypted",
+					Boolean.toString(Main.sdfsCliSSL));
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/sdfs/mgmt/GetDebug.java

@@ -1,0 +1,61 @@
+package org.opendedup.sdfs.mgmt;
+
+import java.io.File;
+
+import java.io.IOException;
+import java.lang.management.ManagementFactory;
+
+import org.opendedup.logging.SDFSLogger;
+import org.opendedup.sdfs.Main;
+import org.opendedup.sdfs.servers.HCServiceProxy;
+import org.opendedup.util.OSValidator;
+import org.opendedup.util.XMLUtils;
+import org.w3c.dom.Document;
+import org.w3c.dom.Element;
+
+import com.sun.management.UnixOperatingSystemMXBean;
+
+@SuppressWarnings("restriction")
+public class GetDebug {
+
+	public Element getResult(String cmd, String file) throws IOException {
+		try {
+			Document doc = XMLUtils.getXMLDoc("debug");
+			Element root = doc.getDocumentElement();
+			root.setAttribute("active-threads",
+					Integer.toString(Thread.activeCount()));
+			root.setAttribute(
+					"blocks-stored",
+					Long.toString(HCServiceProxy.getSize()
+							/ HCServiceProxy.getPageSize()));
+			root.setAttribute(
+					"max-blocks-stored",
+					Long.toString(HCServiceProxy.getMaxSize()
+							/ HCServiceProxy.getPageSize()));
+
+			File f = new File(Main.chunkStore);
+			root.setAttribute("total-space", Long.toString(f.getTotalSpace()));
+			root.setAttribute("free-space", Long.toString(f.getFreeSpace()));
+			if (OSValidator.isUnix()) {
+				UnixOperatingSystemMXBean perf = (UnixOperatingSystemMXBean) ManagementFactory
+						.getOperatingSystemMXBean();
+				root.setAttribute("total-cpu-load",
+						Double.toString(perf.getSystemLoadAverage()));
+				root.setAttribute("sdfs-cpu-load",
+						Double.toString(perf.getProcessCpuLoad()));
+				root.setAttribute("total-memory",
+						Long.toString(Runtime.getRuntime().maxMemory()));
+				root.setAttribute("free-memory",
+						Long.toString(Runtime.getRuntime().freeMemory()));
+			}
+
+			return (Element) root.cloneNode(true);
+		} catch (Exception e) {
+			SDFSLogger.getLog().error(
+					"unable to fulfill request on file " + file, e);
+			throw new IOException("request to fetch attributes failed because "
+					+ e.toString());
+		}
+	}
+
+}

### 2018-12-12 code/SDFS/src/org/opendedup/sdfs/mgmt/ImportArchiveCmd.java

@@ -1,0 +1,73 @@
+package org.opendedup.sdfs.mgmt;
+
+import java.io.IOException;
+
+import javax.xml.parsers.ParserConfigurationException;
+
+import org.opendedup.logging.SDFSLogger;
+import org.opendedup.sdfs.notification.SDFSEvent;
+import org.opendedup.sdfs.replication.ArchiveImporter;
+import org.w3c.dom.Element;
+
+public class ImportArchiveCmd implements Runnable {
+	String archive;
+	String dest;
+	String server;
+	String password;
+	int port;
+	int maxSz;
+	boolean useSSL;
+	boolean useLz4;
+	SDFSEvent evt;
+
+	public Element getResult(String archive, String dest, String server,
+			String password, int port, int maxSz, boolean useSSL,boolean lz4)
+			throws IOException {
+		this.useSSL = useSSL;
+		return importArchive(archive, dest, server, password, port, maxSz,lz4);
+	}
+
+	private Element importArchive(String archive, String dest, String server,
+			String password, int port, int maxSz,boolean lz4) throws IOException {
+		this.archive = archive;
+		this.dest = dest;
+		this.server = server;
+		this.password = password;
+		this.port = port;
+		this.maxSz = maxSz;
+		this.useLz4 = lz4;
+
+		evt = SDFSEvent.importEvent("Importing " + archive + " from " + server
+				+ ":" + port + " to " + dest);
+		evt.curCt = 0;
+		evt.maxCt = 2;
+		Thread th = new Thread(this);
+		th.start();
+		try {
+			return evt.toXML();
+		} catch (ParserConfigurationException e) {
+			throw new IOException(e);
+		}
+	}
+
+	@Override
+	public void run() {
+		String sc = " not successful";
+		try {
+
+			new ArchiveImporter().importArchive(archive, dest, server,
+					password, port, maxSz, evt, useSSL,useLz4);
+			sc = "successful";
+		} catch (Throwable e) {
+			SDFSLogger.getLog().error(
+					"Unable to import archive [" + archive + "] "
+							+ "Destination [" + dest + "] because :"
+							+ e.toString(), e);
+
+		} finally {
+			SDFSLogger.getLog().info("Exited Replication task [" + sc + "]");
+		}
+
+	}
+
+}

### 2018-12-12 code/SDFS/src/org/opendedup/sdfs/mgmt/ImportFileCmd.java

@@ -1,0 +1,206 @@
+package org.opendedup.sdfs.mgmt;
+
+import java.io.BufferedInputStream;
+import java.io.BufferedOutputStream;
+import java.io.File;
+import java.io.FileOutputStream;
+import java.io.IOException;
+import java.net.URI;
+import java.net.URISyntaxException;
+import java.net.URL;
+import java.net.URLEncoder;
+import java.util.HashMap;
+import java.util.List;
+import java.util.Map;
+import java.util.UUID;
+
+import javax.xml.parsers.ParserConfigurationException;
+
+import org.apache.commons.httpclient.methods.GetMethod;
+import org.apache.commons.io.IOUtils;
+import org.apache.http.NameValuePair;
+import org.apache.http.client.utils.URLEncodedUtils;
+import org.opendedup.logging.SDFSLogger;
+import org.opendedup.sdfs.Main;
+import org.opendedup.sdfs.filestore.MetaFileStore;
+import org.opendedup.sdfs.io.MetaDataDedupFile;
+import org.opendedup.sdfs.mgmt.cli.MgmtServerConnection;
+import org.opendedup.sdfs.notification.SDFSEvent;
+import org.opendedup.sdfs.replication.MetaFileImport;
+import org.w3c.dom.Element;
+
+public class ImportFileCmd implements Runnable {
+	String srcFile;
+	String destFile;
+	String server;
+	String password;
+	int port;
+	int maxSz = 0;
+	boolean useSSL = false;
+	boolean hmac = false;
+	SDFSEvent evt;
+
+	public Element getResult(String srcFile, String destFile, String serverURL, int maxSz)
+			throws IOException, URISyntaxException {
+		URL url = new URL(serverURL);
+		server = url.getHost();
+		port = url.getPort();
+		if (url.getProtocol().equalsIgnoreCase("https"))
+			this.useSSL = true;
+		this.srcFile = srcFile;
+		this.destFile = destFile;
+		this.maxSz = maxSz;
+		SDFSLogger.getLog().info("connecting to " +serverURL + " srcfile=" + srcFile + " destFile=" + destFile);
+		@SuppressWarnings("deprecation")
+		List<NameValuePair> params = URLEncodedUtils.parse(new URI(serverURL), "UTF-8");
+		for (NameValuePair param : params) {
+			if (param.getName().equalsIgnoreCase("hmac")) {
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/sdfs/mgmt/MgmtWebServer.java

@@ -1,0 +1,1309 @@
+package org.opendedup.sdfs.mgmt;
+
+import java.io.File;
+
+
+import java.io.FileInputStream;
+import java.io.IOException;
+import java.io.InputStream;
+import java.io.OutputStream;
+import java.io.PrintStream;
+import java.net.InetSocketAddress;
+import java.net.SocketAddress;
+import java.net.URLDecoder;
+import java.nio.ByteBuffer;
+import java.security.InvalidKeyException;
+import java.security.KeyManagementException;
+import java.security.KeyStore;
+import java.security.KeyStoreException;
+import java.security.NoSuchAlgorithmException;
+import java.security.NoSuchProviderException;
+import java.security.SignatureException;
+import java.security.UnrecoverableKeyException;
+import java.security.cert.CertificateException;
+import java.util.HashMap;
+import java.util.LinkedHashMap;
+import java.util.List;
+import java.util.Map;
+import java.util.concurrent.TimeUnit;
+
+import javax.net.ssl.KeyManagerFactory;
+import javax.net.ssl.SSLContext;
+import javax.xml.parsers.DocumentBuilder;
+import javax.xml.parsers.DocumentBuilderFactory;
+
+import org.opendedup.hashing.HashFunctions;
+import org.opendedup.logging.SDFSLogger;
+import org.opendedup.rabin.utils.StringUtils;
+import org.opendedup.sdfs.Main;
+import org.opendedup.sdfs.filestore.MetaFileStore;
+import org.opendedup.sdfs.mgmt.websocket.DDBUpdate;
+import org.opendedup.sdfs.mgmt.websocket.MetaDataUpdate;
+import org.opendedup.sdfs.mgmt.websocket.MetaDataUpload;
+import org.opendedup.sdfs.mgmt.websocket.PingService;
+import org.opendedup.sdfs.servers.HCServiceProxy;
+import org.opendedup.util.FindOpenPort;
+import org.opendedup.util.KeyGenerator;
+import org.opendedup.util.XMLUtils;
+import org.simpleframework.common.buffer.FileAllocator;
+import org.simpleframework.http.Path;
+import org.simpleframework.http.Request;
+import org.simpleframework.http.Response;
+import org.simpleframework.http.core.Container;
+import org.simpleframework.http.core.ContainerSocketProcessor;
+import org.simpleframework.http.socket.service.PathRouter;
+import org.simpleframework.http.socket.service.Router;
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/sdfs/mgmt/OpenFile.java

@@ -1,0 +1,42 @@
+package org.opendedup.sdfs.mgmt;
+
+import java.io.File;
+import java.io.IOException;
+import java.util.HashMap;
+import java.util.concurrent.atomic.AtomicLong;
+
+import org.opendedup.sdfs.io.DedupFileChannel;
+import org.opendedup.logging.SDFSLogger;
+import org.opendedup.sdfs.Main;
+import org.opendedup.sdfs.filestore.MetaFileStore;
+import org.opendedup.sdfs.io.MetaDataDedupFile;
+import org.opendedup.util.XMLUtils;
+import org.w3c.dom.Document;
+import org.w3c.dom.Element;
+
+public class OpenFile {
+
+	public static HashMap<Long, DedupFileChannel> OpenChannels = new HashMap<Long, DedupFileChannel>();
+	AtomicLong fds = new AtomicLong();
+
+	public Element getResult(String cmd, String file) throws IOException {
+		try {
+			Document doc = XMLUtils.getXMLDoc("open-file");
+			Element root = doc.getDocumentElement();
+			File f = new File(Main.volume.getPath(), file);
+			MetaDataDedupFile mf = MetaFileStore.getMF(f);
+			DedupFileChannel ch = mf.getDedupFile(true).getChannel(-33);
+			long fd = fds.incrementAndGet();
+			root.setAttribute("fd", Long.toString(fd));
+			
+			OpenChannels.put(fd, ch);
+			return (Element) root.cloneNode(true);
+		} catch (Exception e) {
+			SDFSLogger.getLog().error(
+					"unable to fulfill request on file " + file, e);
+			throw new IOException("request to fetch attributes failed because "
+					+ e.toString());
+		}
+	}
+
+}

### 2018-12-12 code/SDFS/src/org/opendedup/sdfs/mgmt/SetCacheSize.java

@@ -1,0 +1,40 @@
+package org.opendedup.sdfs.mgmt;
+import java.io.IOException;
+
+import javax.xml.parsers.ParserConfigurationException;
+import org.opendedup.logging.SDFSLogger;
+import org.opendedup.sdfs.Main;
+import org.opendedup.sdfs.notification.SDFSEvent;
+import org.opendedup.sdfs.servers.HCServiceProxy;
+import org.w3c.dom.Element;
+
+public class SetCacheSize implements Runnable {
+	SDFSEvent evt = null;
+	String sz = null;
+
+	public Element getResult(String sz) throws IOException,
+			ParserConfigurationException, Exception {
+		evt = SDFSEvent.cszEvent("Setting Cache Size");
+		this.sz = sz;
+		Thread th = new Thread(this);
+		th.start();
+		long csz = Long.parseLong(sz);
+		HCServiceProxy.setCacheSize(csz);
+		Main.volume.writeUpdate();
+		return evt.toXML();
+
+	}
+
+	@Override
+	public void run() {
+		try {
+			long csz = Long.parseLong(sz);
+			evt.endEvent("Set Cache Size to " + csz + " bytes");
+		} catch (Exception e) {
+			evt.endEvent("unable to fulfill request because " + e.getMessage(),
+					SDFSEvent.ERROR);
+			SDFSLogger.getLog().error("unable to fulfill request ", e);
+		}
+	}
+
+}

### 2018-12-12 code/SDFS/src/org/opendedup/sdfs/mgmt/SyncFSCmd.java

@@ -1,0 +1,39 @@
+package org.opendedup.sdfs.mgmt;
+
+import java.io.IOException;
+
+import org.opendedup.logging.SDFSLogger;
+import org.opendedup.mtools.SyncFS;
+import org.w3c.dom.Element;
+
+public class SyncFSCmd implements Runnable {
+	int minutes = 0;
+	SyncFS fd = null;
+
+	public Element getResult() throws IOException {
+		// minutes = Integer.parseInt(cmd);
+		fd = new SyncFS("now");
+		Thread th = new Thread(this);
+		th.start();
+		try {
+			return fd.getEvt().toXML();
+		} catch (Exception e) {
+			throw new IOException(e);
+		}
+	}
+
+	@Override
+	public void run() {
+		try {
+			fd.init();
+		} catch (Exception e) {
+			SDFSLogger
+					.getLog()
+					.error("ERROR Clean Store: unable to cleand dedup storage engine of data not claimed in  ["
+							+ minutes + "] because :" + e.toString(), e);
+
+		}
+
+	}
+
+}

### 2018-12-12 code/SDFS/src/org/opendedup/sdfs/mgmt/SyncFromConnectedVolume.java

@@ -1,0 +1,29 @@
+package org.opendedup.sdfs.mgmt;
+
+import java.io.IOException;
+
+import org.opendedup.logging.SDFSLogger;
+import org.opendedup.sdfs.filestore.cloud.FileReplicationService;
+import org.opendedup.sdfs.filestore.cloud.RemoteVolumeInfo;
+import org.opendedup.sdfs.servers.HCServiceProxy;
+
+public class SyncFromConnectedVolume {
+
+	public void getResult(long id) throws IOException {
+		try {
+			RemoteVolumeInfo[] l = FileReplicationService.getConnectedVolumes();
+			for (RemoteVolumeInfo lv : l) {
+				if (lv.id == id) {
+					HCServiceProxy.syncVolume(id,true);
+					return;
+				}
+			}
+			throw new Exception("volume [" + id + "] not found");
+		} catch (Exception e) {
+			SDFSLogger.getLog().error("unable to fulfill request", e);
+			throw new IOException("request to fetch attributes failed because "
+					+ e.toString());
+		}
+	}
+
+}

### 2018-12-12 code/SDFS/src/org/opendedup/sdfs/mgmt/cli/ProcessBatchGetBlocks.java

@@ -1,0 +1,152 @@
+package org.opendedup.sdfs.mgmt.cli;
+
+import java.io.ByteArrayInputStream;
+
+
+import java.io.ByteArrayOutputStream;
+import java.io.IOException;
+import java.io.InputStream;
+import java.io.ObjectInputStream;
+import java.io.ObjectOutputStream;
+import java.util.ArrayList;
+import java.util.Formatter;
+import java.util.List;
+import java.util.concurrent.BlockingQueue;
+import java.util.concurrent.SynchronousQueue;
+import java.util.concurrent.ThreadPoolExecutor;
+import java.util.concurrent.TimeUnit;
+import java.util.concurrent.atomic.AtomicLong;
+
+import org.apache.commons.httpclient.methods.PostMethod;
+import org.apache.commons.io.IOUtils;
+import org.opendedup.collections.HashtableFullException;
+import org.opendedup.logging.SDFSLogger;
+import org.opendedup.sdfs.Main;
+import org.opendedup.sdfs.filestore.HashChunk;
+import org.opendedup.sdfs.servers.HCServiceProxy;
+import org.opendedup.util.CompressionUtils;
+
+
+public class ProcessBatchGetBlocks {
+	private static BlockingQueue<Runnable> worksQueue = new SynchronousQueue<Runnable>();
+	private static ThreadPoolExecutor executor = new ThreadPoolExecutor(1, Main.writeThreads, 15, TimeUnit.MINUTES, worksQueue,
+			new ThreadPoolExecutor.CallerRunsPolicy());
+	public static long runCmd(ArrayList<byte[]> hashes, String server,
+			int port, String password, boolean useSSL) throws Exception,
+			ClassNotFoundException, HashtableFullException {
+		Exception he = null;
+		for(int t = 0; t <10;t++) {
+		InputStream in = null;
+		PostMethod method = null;
+		try {
+			SDFSLogger.getLog().debug("getting hashes [" + hashes.size() + "]");
+			ByteArrayOutputStream bos = new ByteArrayOutputStream();
+			ObjectOutputStream obj_out = new ObjectOutputStream(bos);
+			obj_out.writeObject(hashes);
+			String file = com.google.common.io.BaseEncoding.base64Url().encode(
+					CompressionUtils.compressSnappy(bos.toByteArray()));
+			StringBuilder sb = new StringBuilder();
+			Formatter formatter = new Formatter(sb);
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/sdfs/mgmt/cli/ProcessClusterVolumesList.java

@@ -1,0 +1,112 @@
+package org.opendedup.sdfs.mgmt.cli;
+
+import java.text.DecimalFormat;
+import java.text.NumberFormat;
+import java.util.Formatter;
+import java.util.Locale;
+
+import org.opendedup.util.StorageUnit;
+import org.opendedup.util.StringUtils;
+import org.w3c.dom.Document;
+import org.w3c.dom.Element;
+import org.w3c.dom.NodeList;
+
+import com.bethecoder.ascii_table.ASCIITable;
+import com.bethecoder.ascii_table.ASCIITableHeader;
+
+public class ProcessClusterVolumesList {
+	public static void runCmd() {
+		try {
+			StringBuilder sb = new StringBuilder();
+			Formatter formatter = new Formatter(sb);
+			formatter.format("file=%s&cmd=cluster-volumes", "null");
+			Document doc = MgmtServerConnection.getResponse(sb.toString());
+			Element root = doc.getDocumentElement();
+			formatter.close();
+			if (root.getAttribute("status").equals("failed"))
+				System.out.println(root.getAttribute("msg"));
+			else {
+				ASCIITableHeader[] headerObjs = {
+						new ASCIITableHeader("Volume Name",
+								ASCIITable.ALIGN_LEFT),
+						new ASCIITableHeader("Mounted", ASCIITable.ALIGN_LEFT),
+						new ASCIITableHeader("Host", ASCIITable.ALIGN_LEFT),
+						new ASCIITableHeader("Current Size (GB)",
+								ASCIITable.ALIGN_RIGHT),
+						new ASCIITableHeader("Max Size (GB)",
+								ASCIITable.ALIGN_RIGHT),
+						new ASCIITableHeader("Percent Full",
+								ASCIITable.ALIGN_RIGHT),
+						new ASCIITableHeader("Unique Data (GB)",
+								ASCIITable.ALIGN_RIGHT),
+
+						new ASCIITableHeader("Duplicate (GB)",
+								ASCIITable.ALIGN_RIGHT),
+						new ASCIITableHeader("Read (GB)",
+								ASCIITable.ALIGN_RIGHT),
+						new ASCIITableHeader("Redundancy",
+								ASCIITable.ALIGN_RIGHT),
+						new ASCIITableHeader("Rack Aware",
+								ASCIITable.ALIGN_RIGHT),
+						new ASCIITableHeader("DSE as Cap",
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/sdfs/mgmt/cli/ProcessConnectedVolumes.java

@@ -1,0 +1,61 @@
+package org.opendedup.sdfs.mgmt.cli;
+
+import java.util.Formatter;
+
+
+import org.w3c.dom.Document;
+import org.w3c.dom.Element;
+import org.w3c.dom.NodeList;
+
+import com.bethecoder.ascii_table.ASCIITable;
+import com.bethecoder.ascii_table.ASCIITableHeader;
+
+public class ProcessConnectedVolumes {
+	public static void runCmd() {
+		try {
+
+			StringBuilder sb = new StringBuilder();
+			Formatter formatter = new Formatter(sb);
+			formatter.format("file=%s&cmd=connectedvolumes", "null");
+			Document doc = MgmtServerConnection.getResponse(sb.toString());
+			Element root = doc.getDocumentElement();
+			//System.out.println(XMLUtils.toXMLString(doc));
+			formatter.close();
+			if (root.getAttribute("status").equals("failed"))
+				System.out.println(root.getAttribute("msg"));
+			else {
+				ASCIITableHeader[] headerObjs = {
+						new ASCIITableHeader("Host Name", ASCIITable.ALIGN_LEFT),
+						new ASCIITableHeader("ID", ASCIITable.ALIGN_LEFT),
+						new ASCIITableHeader("Size"),
+						new ASCIITableHeader("Compressed Size"),
+						new ASCIITableHeader("cli port"),
+						new ASCIITableHeader("local volume",
+								ASCIITable.ALIGN_CENTER)
+
+				};
+				
+				Element volumes = (Element) root.getElementsByTagName("volumes")
+						.item(0);
+				NodeList nl = volumes.getElementsByTagName("volume");
+				String[][] data = new String[nl.getLength()][headerObjs.length];
+				for(int i = 0; i< nl.getLength();i++) {
+					Element el = (Element)nl.item(i);
+					String[] row = {el.getAttribute("hostname"),el.getAttribute("id"),el.getAttribute("size"),el.getAttribute("compressed-size"),el.getAttribute("port"),el.getAttribute("local")};
+					data[i] = row;
+				}
+				ASCIITable.getInstance().printTable(headerObjs, data);
+			}
+
+		} catch (Exception e) {
+			// TODO Auto-generated catch block
+			e.printStackTrace();
+		}
+
+	}
+
+	public static void main(String[] args) {
+		runCmd();
+	}
+
+}

### 2018-12-12 code/SDFS/src/org/opendedup/sdfs/mgmt/cli/ProcessCopyExtents.java

@@ -1,0 +1,51 @@
+package org.opendedup.sdfs.mgmt.cli;
+
+import java.net.URLEncoder;
+
+import java.util.Formatter;
+
+import org.w3c.dom.Document;
+import org.w3c.dom.Element;
+
+public class ProcessCopyExtents {
+	public static void runCmd(String srcfile, String dstfile, long sstart,
+			long len, long dstart) {
+		try {
+
+			StringBuilder sb = new StringBuilder();
+			Formatter formatter = new Formatter(sb);
+			formatter
+					.format("file=%s&cmd=copyextents&srcfile=%s&dstfile=%s&sstart=%d&len=%s&dstart=%d",
+							"null", URLEncoder.encode(srcfile, "UTF-8"),
+							URLEncoder.encode(dstfile, "UTF-8"), sstart, len,
+							dstart);
+			Document doc = MgmtServerConnection.getResponse(sb.toString());
+			Element root = doc.getDocumentElement();
+			formatter.close();
+			if (root.getAttribute("status").equals("failed"))
+				System.out.println(root.getAttribute("msg"));
+			else {
+				Element cpx = (Element) root
+						.getElementsByTagName("copy-extent").item(0);
+				System.out.printf("Copied Source : %s\n",
+						cpx.getAttribute("srcfile"));
+				System.out.printf("Copied Destination : %s\n",
+						cpx.getAttribute("dstfile"));
+				System.out.printf("Source Start : %s\n",
+						cpx.getAttribute("requested-source-start"));
+				System.out.printf("Destination Start : %s\n",
+						cpx.getAttribute("requested-dest-start"));
+				System.out.printf("Requested Bytes Copied : %s\n",
+						cpx.getAttribute("lenth"));
+				System.out.printf("Actual Bytes Copied : %s\n",
+						cpx.getAttribute("written"));
+			}
+
+		} catch (Exception e) {
+			// TODO Auto-generated catch block
+			e.printStackTrace();
+		}
+
+	}
+
+}

### 2018-12-12 code/SDFS/src/org/opendedup/sdfs/mgmt/cli/ProcessDSEInfo.java

@@ -1,0 +1,94 @@
+package org.opendedup.sdfs.mgmt.cli;
+
+import java.text.DecimalFormat;
+import java.text.NumberFormat;
+import java.util.Formatter;
+import java.util.Locale;
+
+import org.opendedup.util.StorageUnit;
+import org.w3c.dom.Document;
+import org.w3c.dom.Element;
+
+public class ProcessDSEInfo {
+	public static void runCmd() {
+		try {
+			StringBuilder sb = new StringBuilder();
+			Formatter formatter = new Formatter(sb);
+			formatter.format("file=%s&cmd=dse-info", "null");
+			Document doc = MgmtServerConnection.getResponse(sb.toString());
+			Element root = doc.getDocumentElement();
+			formatter.close();
+			if (root.getAttribute("status").equals("failed"))
+				System.out.println(root.getAttribute("msg"));
+			else {
+				Element dse = (Element) root.getElementsByTagName("dse")
+						.item(0);
+				long entries = -1;
+				if(dse.hasAttribute("entries"))
+					entries = Long.parseLong(dse.getAttribute("entries"));
+				long maxSz = Long.parseLong(dse.getAttribute("max-size"));
+				long maxCacheSz = Long.parseLong(dse
+						.getAttribute("max-cache-size"));
+				long cacheSz = Long.parseLong(dse.getAttribute("cache-size"));
+				long rsp = Long.parseLong(dse.getAttribute("read-speed")) * 1024;
+				long wsp = Long.parseLong(dse.getAttribute("write-speed")) * 1024;
+				long currentSz = Long.parseLong(dse
+						.getAttribute("current-size"));
+				long compressedSz = Long.parseLong(dse
+						.getAttribute("compressed-size"));
+				long freeBlocks = Long.parseLong(dse
+						.getAttribute("free-blocks"));
+				int pageSize = Integer.parseInt(dse.getAttribute("page-size"));
+				double pFull = 0.00;
+				if (currentSz > 0) {
+					pFull = (((double) currentSz / (double) maxSz) * 100);
+					DecimalFormat twoDForm = (DecimalFormat) NumberFormat
+							.getNumberInstance(Locale.US);
+					twoDForm.applyPattern("#.##");
+					pFull = Double.valueOf(twoDForm.format(pFull));
+				}
+				System.out.printf("DSE Max Size : %s\n", StorageUnit.of(maxSz)
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/sdfs/mgmt/cli/ProcessDeleteFileCmd.java

@@ -1,0 +1,36 @@
+package org.opendedup.sdfs.mgmt.cli;
+
+import java.net.URLEncoder;
+import java.util.Formatter;
+
+import org.opendedup.logging.SDFSLogger;
+import org.w3c.dom.Document;
+import org.w3c.dom.Element;
+
+public class ProcessDeleteFileCmd {
+	public String status;
+	public String msg;
+
+	public static ProcessDeleteFileCmd execute(String file,boolean rmlock) {
+		ProcessDeleteFileCmd store = new ProcessDeleteFileCmd();
+		try {
+			file = URLEncoder.encode(file, "UTF-8");
+			StringBuilder sb = new StringBuilder();
+			Formatter formatter = new Formatter(sb);
+			SDFSLogger.getLog().debug("Deleting File [" + file + "] ");
+			formatter.format("file=%s&cmd=%s&options=%s&retentionlock=%s", file, "deletefile",
+					"",Boolean.toString(rmlock));
+			Document doc = MgmtServerConnection.getResponse(sb.toString());
+			formatter.close();
+			Element root = doc.getDocumentElement();
+			store.status = root.getAttribute("status");
+			store.msg = root.getAttribute("msg");
+
+		} catch (Exception e) {
+			store.status = "failed";
+			store.msg = e.getMessage();
+		}
+		return store;
+	}
+
+}

### 2018-12-12 code/SDFS/src/org/opendedup/sdfs/mgmt/cli/ProcessSetWriteSpeed.java

@@ -1,0 +1,38 @@
+package org.opendedup.sdfs.mgmt.cli;
+
+import java.util.Formatter;
+
+import org.w3c.dom.Document;
+import org.w3c.dom.Element;
+
+public class ProcessSetWriteSpeed {
+	public static void runCmd(String ssz) {
+		try {
+			StringBuilder sb = new StringBuilder();
+			Formatter formatter = new Formatter(sb);
+			int sz = Integer.parseInt(ssz);
+			formatter.format("file=%s&cmd=setwritespeed&sp=%d", "null", sz);
+			Document doc = MgmtServerConnection.getResponse(sb.toString());
+			Element root = doc.getDocumentElement();
+			formatter.close();
+			if (root.getAttribute("status").equals("failed"))
+				System.out.println(root.getAttribute("msg"));
+			else {
+				if (root.getAttribute("status").equals("failed")) {
+					System.out.println(root.getAttribute("msg"));
+					System.exit(-1);
+				}
+				String status = root.getAttribute("status");
+				String msg = root.getAttribute("msg");
+				System.out.printf("Set Write Speed [%s] returned [%s]\n",
+						status, msg);
+			}
+
+		} catch (Exception e) {
+			// TODO Auto-generated catch block
+			e.printStackTrace();
+		}
+
+	}
+
+}

### 2018-12-12 code/SDFS/src/org/opendedup/sdfs/mgmt/cli/SDFSCmdline.java

@@ -1,0 +1,687 @@
+package org.opendedup.sdfs.mgmt.cli;
+
+import java.net.ConnectException;
+
+import org.apache.commons.cli.CommandLine;
+import org.apache.commons.cli.HelpFormatter;
+import org.apache.commons.cli.OptionBuilder;
+import org.apache.commons.cli.Options;
+import org.apache.commons.cli.PosixParser;
+import org.apache.log4j.BasicConfigurator;
+import org.apache.log4j.Level;
+import org.apache.log4j.LogManager;
+import org.opendedup.logging.SDFSLogger;
+
+public class SDFSCmdline {
+	public static void parseCmdLine(String[] args) throws Exception {
+		PosixParser parser = new PosixParser();
+		Options options = buildOptions();
+		CommandLine cmd = parser.parse(options, args);
+		try {
+
+			if (cmd.hasOption("help") || args.length == 0) {
+				printHelp(options);
+				System.exit(1);
+			}
+			boolean quiet = false;
+			if (cmd.hasOption("debug"))
+				SDFSLogger.setLevel(0);
+			if (cmd.hasOption("nossl"))
+				MgmtServerConnection.useSSL = false;
+			if (cmd.hasOption("server"))
+				MgmtServerConnection.server = cmd.getOptionValue("server");
+			
+			
+			if (cmd.hasOption("port"))
+				MgmtServerConnection.port = Integer.parseInt(cmd
+						.getOptionValue("port"));
+			
+			if (cmd.hasOption("password"))
+				MgmtServerConnection.baseHmac = MgmtServerConnection.initAuth(cmd.getOptionValue("password"),MgmtServerConnection.server,MgmtServerConnection.port,MgmtServerConnection.useSSL);
+			else
+				MgmtServerConnection.baseHmac = MgmtServerConnection.initAuth("admin",MgmtServerConnection.server,MgmtServerConnection.port,MgmtServerConnection.useSSL);
+			
+			if (cmd.hasOption("file-info")) {
+				if (cmd.hasOption("file-path")) {
+					ProcessFileInfo.runCmd(cmd.getOptionValue("file-path"));
+					System.exit(0);
+				} else {
+					SDFSLogger
+							.getBasicLog()
+							.warn("file info request failed. --file-path option is required");
+					System.exit(1);
+				}
+			}
+			if (cmd.hasOption("file-cache-info")) {
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/sdfs/mgmt/websocket/PingService.java

@@ -1,0 +1,175 @@
+/*******************************************************************************
+ * Copyright (C) 2016 Sam Silverberg sam.silverberg@gmail.com	
+ *
+ * This file is part of OpenDedupe SDFS.
+ *
+ * OpenDedupe SDFS is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * OpenDedupe SDFS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with Foobar.  If not, see <http://www.gnu.org/licenses/>.
+ *******************************************************************************/
+package org.opendedup.sdfs.mgmt.websocket;
+
+import java.io.IOException;
+import java.io.UnsupportedEncodingException;
+import java.security.NoSuchAlgorithmException;
+import java.security.NoSuchProviderException;
+import java.util.Map;
+import java.util.Set;
+import java.util.concurrent.ConcurrentHashMap;
+import java.util.concurrent.CopyOnWriteArraySet;
+
+import org.opendedup.hashing.HashFunctions;
+import org.opendedup.logging.SDFSLogger;
+import org.opendedup.sdfs.Main;
+import org.opendedup.util.RandomGUID;
+import org.simpleframework.http.Request;
+import org.simpleframework.http.socket.DataFrame;
+import org.simpleframework.http.socket.Frame;
+import org.simpleframework.http.socket.FrameChannel;
+import org.simpleframework.http.socket.FrameListener;
+import org.simpleframework.http.socket.FrameType;
+import org.simpleframework.http.socket.Reason;
+import org.simpleframework.http.socket.Session;
+import org.simpleframework.http.socket.service.Service;
+
+public class PingService implements Service, Runnable {
+	private final PingListener listener;
+	private final Map<String, FrameChannel> sockets;
+	private final Set<String> users;
+
+	public PingService() {
+		sockets = new ConcurrentHashMap<String, FrameChannel>();
+		listener = new PingListener(this);
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/sdfs/notification/SDFSEvent.java

@@ -1,0 +1,645 @@
+/*******************************************************************************
+ * Copyright (C) 2016 Sam Silverberg sam.silverberg@gmail.com	
+ *
+ * This file is part of OpenDedupe SDFS.
+ *
+ * OpenDedupe SDFS is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * OpenDedupe SDFS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with Foobar.  If not, see <http://www.gnu.org/licenses/>.
+ *******************************************************************************/
+package org.opendedup.sdfs.notification;
+
+import java.io.File;
+import java.io.IOException;
+import java.text.SimpleDateFormat;
+import java.util.ArrayList;
+import java.util.Date;
+import java.util.Iterator;
+import java.util.LinkedHashMap;
+import java.util.Map;
+
+import javax.xml.parsers.ParserConfigurationException;
+
+import org.opendedup.logging.SDFSEventLogger;
+import org.opendedup.sdfs.Main;
+import org.opendedup.sdfs.io.MetaDataDedupFile;
+import org.opendedup.util.FileCounts;
+import org.opendedup.util.RandomGUID;
+import org.opendedup.util.XMLUtils;
+import org.w3c.dom.Document;
+import org.w3c.dom.Element;
+
+public class SDFSEvent implements java.io.Serializable {
+	/**
+	 * 
+	 */
+	private static final long serialVersionUID = -7418485011806466368L;
+	public Type type = null;
+	public Level level;
+	public String shortMsg = null;
+	public String longMsg = "";
+	public String target = null;
+	public long maxCt = 1;
+	public long curCt = 1;
+	public long startTime;
+	public long endTime = -1;
+	public long actionCount = 0;
+	public boolean success = true;
+	public String uid = null;
+	public String extendedInfo = "";
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/sdfs/replication/ReplicationCanceledException.java

@@ -1,0 +1,32 @@
+/*******************************************************************************
+ * Copyright (C) 2016 Sam Silverberg sam.silverberg@gmail.com	
+ *
+ * This file is part of OpenDedupe SDFS.
+ *
+ * OpenDedupe SDFS is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * OpenDedupe SDFS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with Foobar.  If not, see <http://www.gnu.org/licenses/>.
+ *******************************************************************************/
+package org.opendedup.sdfs.replication;
+
+public class ReplicationCanceledException extends Exception {
+
+	public ReplicationCanceledException(String string) {
+		super(string);
+	}
+
+	/**
+	 * 
+	 */
+	private static final long serialVersionUID = -7687536462730018028L;
+
+}

### 2018-12-12 code/SDFS/src/org/opendedup/sdfs/replication/ReplicationScheduler.java

@@ -1,0 +1,69 @@
+/*******************************************************************************
+ * Copyright (C) 2016 Sam Silverberg sam.silverberg@gmail.com	
+ *
+ * This file is part of OpenDedupe SDFS.
+ *
+ * OpenDedupe SDFS is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * OpenDedupe SDFS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with Foobar.  If not, see <http://www.gnu.org/licenses/>.
+ *******************************************************************************/
+package org.opendedup.sdfs.replication;
+
+import java.util.Properties;
+
+import org.opendedup.logging.SDFSLogger;
+import org.quartz.CronTrigger;
+import org.quartz.JobDataMap;
+import org.quartz.JobDetail;
+import org.quartz.Scheduler;
+import org.quartz.SchedulerFactory;
+import org.quartz.impl.StdSchedulerFactory;
+
+public class ReplicationScheduler {
+	Scheduler sched = null;
+
+	public ReplicationScheduler(String schedule, ReplicationService service) {
+		try {
+			Properties props = new Properties();
+			props.setProperty("org.quartz.scheduler.skipUpdateCheck", "true");
+			props.setProperty("org.quartz.threadPool.class",
+					"org.quartz.simpl.SimpleThreadPool");
+			props.setProperty("org.quartz.threadPool.threadCount", "1");
+			props.setProperty("org.quartz.threadPool.threadPriority",
+					Integer.toString(Thread.NORM_PRIORITY));
+			SDFSLogger.getLog().info("Scheduling Replication Job for SDFS");
+			SchedulerFactory schedFact = new StdSchedulerFactory(props);
+			sched = schedFact.getScheduler();
+			sched.start();
+			JobDataMap dataMap = new JobDataMap();
+			dataMap.put("service", service);
+			JobDetail ccjobDetail = new JobDetail("replication", null,
+					ReplicationJob.class);
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/sdfs/replication/ReplicationSnapShotManager.java

@@ -1,0 +1,29 @@
+/*******************************************************************************
+ * Copyright (C) 2016 Sam Silverberg sam.silverberg@gmail.com	
+ *
+ * This file is part of OpenDedupe SDFS.
+ *
+ * OpenDedupe SDFS is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * OpenDedupe SDFS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with Foobar.  If not, see <http://www.gnu.org/licenses/>.
+ *******************************************************************************/
+package org.opendedup.sdfs.replication;
+
+import java.util.concurrent.ConcurrentHashMap;
+
+public class ReplicationSnapShotManager {
+	public static ConcurrentHashMap<String, String> replicationSnapshots = new ConcurrentHashMap<String, String>();
+
+	public void addSnapshot() {
+	}
+
+}

### 2018-12-12 code/SDFS/src/org/opendedup/sdfs/servers/HCServiceProxy.java

@@ -1,0 +1,452 @@
+/*******************************************************************************
+ * Copyright (C) 2016 Sam Silverberg sam.silverberg@gmail.com	
+ *
+ * This file is part of OpenDedupe SDFS.
+ *
+ * OpenDedupe SDFS is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * OpenDedupe SDFS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with Foobar.  If not, see <http://www.gnu.org/licenses/>.
+ *******************************************************************************/
+package org.opendedup.sdfs.servers;
+
+import java.io.File;
+import java.io.FileWriter;
+import java.io.IOException;
+import java.nio.ByteBuffer;
+import java.io.FileOutputStream;
+import java.util.ArrayList;
+
+import org.opendedup.collections.AbstractHashesMap;
+import org.opendedup.collections.DataArchivedException;
+import org.opendedup.collections.HashtableFullException;
+import org.opendedup.collections.InsertRecord;
+import org.opendedup.collections.LocalLookupFilter;
+import org.opendedup.hashing.LargeBloomFilter;
+import org.opendedup.logging.SDFSLogger;
+import org.opendedup.mtools.FDisk;
+import org.opendedup.mtools.FDiskException;
+import org.opendedup.sdfs.Main;
+import org.opendedup.sdfs.filestore.AbstractChunkStore;
+import org.opendedup.sdfs.filestore.HashChunk;
+import org.opendedup.sdfs.io.events.CloudSyncDLRequest;
+import org.opendedup.sdfs.notification.FDiskEvent;
+import org.opendedup.sdfs.notification.SDFSEvent;
+
+import com.google.common.eventbus.EventBus;
+import com.google.common.primitives.Longs;
+
+public class HCServiceProxy {
+
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/sdfs/servers/HashChunkServiceInterface.java

@@ -1,0 +1,121 @@
+/*******************************************************************************
+ * Copyright (C) 2016 Sam Silverberg sam.silverberg@gmail.com	
+ *
+ * This file is part of OpenDedupe SDFS.
+ *
+ * OpenDedupe SDFS is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * OpenDedupe SDFS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with Foobar.  If not, see <http://www.gnu.org/licenses/>.
+ *******************************************************************************/
+package org.opendedup.sdfs.servers;
+
+import java.io.IOException;
+
+
+import org.opendedup.collections.AbstractHashesMap;
+import org.opendedup.collections.DataArchivedException;
+import org.opendedup.collections.HashtableFullException;
+import org.opendedup.collections.InsertRecord;
+import org.opendedup.hashing.LargeBloomFilter;
+import org.opendedup.sdfs.filestore.AbstractChunkStore;
+import org.opendedup.sdfs.filestore.HashChunk;
+import org.opendedup.sdfs.filestore.cloud.RemoteVolumeInfo;
+import org.opendedup.sdfs.notification.SDFSEvent;
+
+public interface HashChunkServiceInterface {
+
+	/**
+	 * @return the chunksFetched
+	 */
+	public abstract String restoreBlock(byte[] hash,long id) throws IOException;
+
+	public abstract boolean blockRestored(String id) throws IOException;
+	
+	public abstract boolean mightContainKey(byte [] key,long id);
+
+	public abstract long getChunksFetched();
+
+	public abstract AbstractChunkStore getChuckStore();
+	
+	public abstract boolean claimKey(byte [] key,long val,long ct) throws IOException;
+	
+
+	public abstract InsertRecord writeChunk(byte[] hash, byte[] aContents,
+			boolean compressed,long ct,String uuid) throws IOException, HashtableFullException;
+
+	
+
+	public abstract long hashExists(byte[] hash) throws IOException,
+			HashtableFullException;
+
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/sdfs/servers/HashEngine.java

@@ -1,0 +1,23 @@
+/*******************************************************************************
+ * Copyright (C) 2016 Sam Silverberg sam.silverberg@gmail.com	
+ *
+ * This file is part of OpenDedupe SDFS.
+ *
+ * OpenDedupe SDFS is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * OpenDedupe SDFS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with Foobar.  If not, see <http://www.gnu.org/licenses/>.
+ *******************************************************************************/
+package org.opendedup.sdfs.servers;
+
+public class HashEngine {
+
+}

### 2018-12-12 code/SDFS/src/org/opendedup/sdfs/servers/SDFSService.java

@@ -1,0 +1,175 @@
+/*******************************************************************************
+ * Copyright (C) 2016 Sam Silverberg sam.silverberg@gmail.com	
+ *
+ * This file is part of OpenDedupe SDFS.
+ *
+ * OpenDedupe SDFS is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * OpenDedupe SDFS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with Foobar.  If not, see <http://www.gnu.org/licenses/>.
+ *******************************************************************************/
+package org.opendedup.sdfs.servers;
+
+import java.util.ArrayList;
+
+import java.util.Properties;
+
+import org.opendedup.hashing.HashFunctionPool;
+import org.opendedup.logging.SDFSLogger;
+import org.opendedup.sdfs.Config;
+import org.opendedup.sdfs.Main;
+import org.opendedup.sdfs.filestore.DedupFileStore;
+import org.opendedup.sdfs.filestore.MetaFileStore;
+import org.opendedup.sdfs.filestore.gc.StandAloneGCScheduler;
+import org.opendedup.sdfs.mgmt.MgmtWebServer;
+import org.opendedup.sdfs.notification.SDFSEvent;
+import org.opendedup.util.OSValidator;
+
+public class SDFSService {
+	String configFile;
+
+	private ArrayList<String> volumes;
+	private static boolean stopped = false;
+
+	public static boolean isStopped() {
+		return stopped;
+	}
+
+	public SDFSService(String configFile, ArrayList<String> volumes) {
+
+		this.configFile = configFile;
+		this.volumes = volumes;
+		String ts = "";
+		Properties props = new Properties();
+		try {
+			props.load(this.getClass().getResourceAsStream("/version.properties"));
+			Main.version = props.getProperty("version");
+			ts = props.getProperty("timestamp");
+
+		} catch (Exception e) {
+			e.printStackTrace();
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/sdfs/windows/fs/MetaDataFileInfo.java

@@ -1,0 +1,117 @@
+
+
+package org.opendedup.sdfs.windows.fs;
+
+import java.io.IOException;
+import java.nio.file.Files;
+import java.nio.file.Path;
+import java.nio.file.Paths;
+import java.nio.file.attribute.DosFileAttributes;
+
+import net.decasdev.dokan.ByHandleFileInformation;
+import net.decasdev.dokan.FileAttribute.FileAttributeFlags;
+import net.decasdev.dokan.Win32FindData;
+
+import org.apache.commons.io.FilenameUtils;
+import org.opendedup.logging.SDFSLogger;
+import org.opendedup.sdfs.Main;
+import org.opendedup.sdfs.io.MetaDataDedupFile;
+
+public class MetaDataFileInfo {
+	static long nextFileIndex = 2;
+
+	String fileName;
+	final boolean isDirectory;
+	private int fileAttribute = 0;
+	long creationTime = 0;
+	long lastAccessTime = 0;
+	long lastWriteTime = 0;
+	final long fileIndex;
+	final long fileSize;
+	MetaDataDedupFile mf = null;
+
+	MetaDataFileInfo(String fileName, MetaDataDedupFile mf) {
+		this.fileName = fileName;
+		this.mf = mf;
+		this.isDirectory = mf.isDirectory();
+		fileIndex = getNextFileIndex();
+		Path file = Paths.get(mf.getPath());
+		try {
+			DosFileAttributes attr = Files.readAttributes(file,
+					DosFileAttributes.class);
+			if (attr.isArchive())
+				fileAttribute |= FileAttributeFlags.FILE_ATTRIBUTE_ARCHIVE
+						.getValue();
+			if (attr.isDirectory())
+				fileAttribute |= FileAttributeFlags.FILE_ATTRIBUTE_DIRECTORY
+						.getValue();
+			if (attr.isHidden())
+				fileAttribute |= FileAttributeFlags.FILE_ATTRIBUTE_HIDDEN
+						.getValue();
+			if (attr.isReadOnly())
+				fileAttribute |= FileAttributeFlags.FILE_ATTRIBUTE_READONLY
+						.getValue();
+			if (attr.isRegularFile())
+				fileAttribute |= FileAttributeFlags.FILE_ATTRIBUTE_NORMAL
+						.getValue();
+			if (attr.isSymbolicLink())
+				fileAttribute |= FileAttributeFlags.FILE_ATTRIBUTE_REPARSE_POINT
+						.getValue();
+			if (attr.isSystem())
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/sdfs/windows/fs/ShutdownHook.java

@@ -1,0 +1,58 @@
+/*******************************************************************************
+ * Copyright (C) 2016 Sam Silverberg sam.silverberg@gmail.com	
+ *
+ * This file is part of OpenDedupe SDFS.
+ *
+ * OpenDedupe SDFS is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * OpenDedupe SDFS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with Foobar.  If not, see <http://www.gnu.org/licenses/>.
+ *******************************************************************************/
+package org.opendedup.sdfs.windows.fs;
+
+import net.decasdev.dokan.Dokan;
+
+import org.opendedup.sdfs.servers.SDFSService;
+import org.opendedup.sdfs.windows.utils.DriveIcon;
+
+class ShutdownHook extends Thread {
+	private SDFSService service;
+	private String driveLetter;
+
+	public ShutdownHook(SDFSService service, String driveLetter) {
+		this.service = service;
+		this.driveLetter = driveLetter;
+	}
+
+	@Override
+	public void run() {
+
+		System.out.println("Please Wait while shutting down SDFS");
+		System.out.println("Data Can be lost if this is interrupted");
+		service.stop();
+		System.out.println("All Data Flushed");
+		try {
+			System.out.println("Unmounting " + this.driveLetter);
+			Dokan.removeMountPoint(driveLetter);
+		} catch (Exception e) {
+			e.printStackTrace();
+		} finally {
+			try {
+				DriveIcon.deleteIcon(driveLetter);
+			} catch (Exception e) {
+				// TODO Auto-generated catch block
+				e.printStackTrace();
+			}
+		}
+		System.out.println("SDFS Shut Down Cleanly");
+
+	}
+}

### 2018-12-12 code/SDFS/src/org/opendedup/sdfs/windows/fs/UnmountFS.java

@@ -1,0 +1,35 @@
+/*
+The MIT License
+
+Copyright (C) 2008, 2011 Yu Kobayashi http://yukoba.accelart.jp/
+
+Permission is hereby granted, free of charge, to any person obtaining a copy
+of this software and associated documentation files (the "Software"), to deal
+in the Software without restriction, including without limitation the rights
+to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
+copies of the Software, and to permit persons to whom the Software is
+furnished to do so, subject to the following conditions:
+
+The above copyright notice and this permission notice shall be included in
+all copies or substantial portions of the Software.
+
+THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
+IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
+FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
+AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
+LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
+OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
+THE SOFTWARE.
+ */
+
+package org.opendedup.sdfs.windows.fs;
+
+import net.decasdev.dokan.Dokan;
+
+public class UnmountFS {
+	public static void main(String[] args) {
+		String driveLetter = (args.length == 0) ? "S" : args[0];
+		Dokan.removeMountPoint(driveLetter);
+		System.exit(0);
+	}
+}

### 2018-12-12 code/SDFS/src/org/opendedup/util/AsyncChunkWriteActionListener.java

@@ -1,0 +1,27 @@
+/*******************************************************************************
+ * Copyright (C) 2016 Sam Silverberg sam.silverberg@gmail.com	
+ *
+ * This file is part of OpenDedupe SDFS.
+ *
+ * OpenDedupe SDFS is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * OpenDedupe SDFS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with Foobar.  If not, see <http://www.gnu.org/licenses/>.
+ *******************************************************************************/
+package org.opendedup.util;
+
+public abstract class AsyncChunkWriteActionListener {
+
+	public abstract void commandException(Throwable e);
+
+	public abstract void commandResponse();
+
+}

### 2018-12-12 code/SDFS/src/org/opendedup/util/CompressionUtils.java

@@ -1,0 +1,180 @@
+/*******************************************************************************
+ * Copyright (C) 2016 Sam Silverberg sam.silverberg@gmail.com	
+ *
+ * This file is part of OpenDedupe SDFS.
+ *
+ * OpenDedupe SDFS is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * OpenDedupe SDFS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with Foobar.  If not, see <http://www.gnu.org/licenses/>.
+ *******************************************************************************/
+package org.opendedup.util;
+
+import java.io.ByteArrayOutputStream;
+
+import java.io.File;
+import java.io.FileInputStream;
+import java.io.FileOutputStream;
+import java.io.IOException;
+import java.util.zip.DataFormatException;
+import java.util.zip.Deflater;
+import java.util.zip.Inflater;
+
+import net.jpountz.lz4.LZ4BlockInputStream;
+import net.jpountz.lz4.LZ4BlockOutputStream;
+import net.jpountz.lz4.LZ4Compressor;
+import net.jpountz.lz4.LZ4FastDecompressor;
+import net.jpountz.lz4.LZ4Factory;
+
+import org.apache.commons.compress.utils.IOUtils;
+import org.opendedup.logging.SDFSLogger;
+import org.xerial.snappy.Snappy;
+import org.xerial.snappy.SnappyInputStream;
+import org.xerial.snappy.SnappyOutputStream;
+
+//import org.h2.compress.LZFInputStream;
+//import org.h2.compress.LZFOutputStream;
+
+public class CompressionUtils {
+
+	static LZ4Compressor lz4Compressor;
+	static LZ4FastDecompressor lz4Decompressor;
+	static {
+		try {
+			lz4Compressor = LZ4Factory.nativeInstance()
+					.fastCompressor();
+			lz4Decompressor = LZ4Factory
+					.nativeInstance().fastDecompressor();
+		} catch(Throwable e) {
+			SDFSLogger.getLog().warn("Falling back to basic compressor");
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/util/DirectBufPool.java

@@ -1,0 +1,92 @@
+/*******************************************************************************
+ * Copyright (C) 2016 Sam Silverberg sam.silverberg@gmail.com	
+ *
+ * This file is part of OpenDedupe SDFS.
+ *
+ * OpenDedupe SDFS is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * OpenDedupe SDFS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with Foobar.  If not, see <http://www.gnu.org/licenses/>.
+ *******************************************************************************/
+package org.opendedup.util;
+
+import java.io.IOException;
+import java.nio.ByteBuffer;
+import java.util.concurrent.ConcurrentLinkedQueue;
+
+import org.opendedup.logging.SDFSLogger;
+
+public class DirectBufPool {
+
+	private int poolSize = 1;
+
+	private ConcurrentLinkedQueue<ByteBuffer> passiveObjects = new ConcurrentLinkedQueue<ByteBuffer>();
+	private int size = 0;
+	private boolean closed = false;
+
+	public DirectBufPool(int sz) {
+		this.size = sz;
+		this.populatePool();
+	}
+
+	public void populatePool() {
+		for (int i = 0; i < poolSize; i++) {
+			try {
+				this.passiveObjects.add(this.makeObject());
+			} catch (Exception e) {
+				e.printStackTrace();
+				SDFSLogger.getLog().fatal(
+						"unable to instancial Hash Function pool", e);
+
+			} finally {
+
+			}
+		}
+	}
+
+	public ByteBuffer borrowObject() throws IOException {
+		if (this.closed)
+			throw new IOException("Buf Pool closed");
+		ByteBuffer hc = null;
+		hc = this.passiveObjects.poll();
+		if (hc == null) {
+			hc = makeObject();
+		}
+		return hc;
+	}
+
+	public void returnObject(ByteBuffer buf) {
+		if (!this.closed) {
+			buf.position(0);
+			this.passiveObjects.add(buf);
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/util/FactorTest.java

@@ -1,0 +1,80 @@
+/*******************************************************************************
+ * Copyright (C) 2016 Sam Silverberg sam.silverberg@gmail.com	
+ *
+ * This file is part of OpenDedupe SDFS.
+ *
+ * OpenDedupe SDFS is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * OpenDedupe SDFS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with Foobar.  If not, see <http://www.gnu.org/licenses/>.
+ *******************************************************************************/
+package org.opendedup.util;
+
+import java.util.ArrayList;
+
+public class FactorTest {
+	public static void main(String[] args) {
+		int val = 128 * 1024;
+
+		System.out.println("\nThe factors of " + val + " are:");
+		int[] result = factorsOf(val);
+		for (int i = 0; i < result.length && result[i] != 0; i++) {
+			System.out.println(result[i]);
+		}
+		System.out.println("closest=" + result[closest2Pos(3122, result)]);
+	}
+
+	public static int[] factorsOf(double val) {
+		ArrayList<Integer> al = new ArrayList<Integer>();
+		double prev = val;
+		al.add((int) val);
+		while (val >= 512) {
+			if ((prev - val) >= 512) {
+				al.add((int) val);
+				prev = val;
+			}
+			val = val / 1.2;
+		}
+		int[] z = new int[al.size()];
+		for (int i = 0; i < al.size(); i++) {
+			z[i] = al.get(i);
+		}
+		return z;
+	}
+
+	public static int closest2(int find, int[] values) {
+		int distance = Integer.MAX_VALUE;
+		int closest = -1;
+		for (int i : values) {
+			int distanceI = i - find;
+			if (distanceI > -1 && distance >= distanceI) {
+				distance = distanceI;
+				closest = i;
+			}
+		}
+		return closest;
+	}
+
+	public static int closest2Pos(int find, int[] values) {
+		int distance = Integer.MAX_VALUE;
+		int closest = -1;
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/util/HashFunctions.java

@@ -1,0 +1,318 @@
+package org.opendedup.util;
+
+import java.io.File;
+
+import java.io.FileInputStream;
+import java.io.IOException;
+import java.io.UnsupportedEncodingException;
+import java.nio.ByteBuffer;
+import java.nio.channels.ReadableByteChannel;
+import java.security.MessageDigest;
+import java.security.NoSuchAlgorithmException;
+import java.security.NoSuchProviderException;
+import java.security.SecureRandom;
+import java.security.Security;
+import java.util.Date;
+import java.util.zip.Adler32;
+
+import org.bouncycastle.jce.provider.BouncyCastleProvider;
+
+/**
+ * Licensed to the Apache Software Foundation (ASF) under one
+ * or more contributor license agreements.  See the NOTICE file
+ * distributed with this work for additional information
+ * regarding copyright ownership.  The ASF licenses this file
+ * to you under the Apache License, Version 2.0 (the
+ * "License"); you may not use this file except in compliance
+ * with the License.  You may obtain a copy of the License at
+ *
+ *     http://www.apache.org/licenses/LICENSE-2.0
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS,
+ * WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+ * See the License for the specific language governing permissions and
+ * limitations under the License.
+ */
+
+/**
+ * This is a very fast, non-cryptographic hash suitable for general hash-based
+ * lookup. See http://murmurhash.googlepages.com/ for more details.
+ * 
+ * <p>
+ * The C version of MurmurHash 2.0 found at that site was ported to Java by
+ * Andrzej Bialecki (ab at getopt org).
+ * </p>
+ */
+public class HashFunctions {
+
+	static MessageDigest algorithm;
+
+	static {
+
+		try {
+			Security.addProvider(new BouncyCastleProvider());
+			algorithm = MessageDigest.getInstance("Tiger", "BC");
+		} catch (NoSuchAlgorithmException e) {
+			// TODO Auto-generated catch block
+			e.printStackTrace();
+		} catch (Exception e) {
+			// TODO Auto-generated catch block
+			e.printStackTrace();
+		}
+	}
+
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/util/LargFile.java

@@ -1,0 +1,77 @@
+/*******************************************************************************
+ * Copyright (C) 2016 Sam Silverberg sam.silverberg@gmail.com	
+ *
+ * This file is part of OpenDedupe SDFS.
+ *
+ * OpenDedupe SDFS is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * OpenDedupe SDFS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with Foobar.  If not, see <http://www.gnu.org/licenses/>.
+ *******************************************************************************/
+package org.opendedup.util;
+
+import java.io.File;
+import java.io.FileOutputStream;
+import java.io.FileWriter;
+import java.io.IOException;
+import java.nio.ByteBuffer;
+import java.util.Random;
+
+public class LargFile {
+	public static void writeFile(String path, int size, int bs, boolean unique)
+			throws IOException {
+		long len = 1024L * 1024L * 1024L * size;
+		long sz = 0;
+		File log = new File(path + "log");
+		File f = new File(path);
+		java.io.FileWriter writer = new FileWriter(log);
+		System.out.println("unique data=" + unique);
+		FileOutputStream str = new FileOutputStream(f, true);
+		Random rnd = new Random();
+		byte[] b = new byte[bs];
+		if (!unique)
+			rnd.nextBytes(b);
+		System.out.println("1:" + len);
+		long time = System.currentTimeMillis();
+		int writes = 0;
+		int interval = (32768 * 10000) / bs;
+		while (sz < len) {
+			if (unique) {
+				rnd.nextBytes(b);
+			}
+			ByteBuffer buf = ByteBuffer.wrap(b);
+			str.getChannel().write(buf);
+			sz = sz + b.length;
+			if (writes > interval) {
+
+				float mb = (float) (writes * bs) / (1024 * 1024);
+				float duration = (float) (System.currentTimeMillis() - time) / 1000;
+				float mbps = mb / duration;
+				System.out.println(mbps + " (mb/s)");
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/util/MapDBTest.java

@@ -1,0 +1,78 @@
+package org.opendedup.util;
+
+import java.io.File;
+
+import java.nio.ByteBuffer;
+import java.util.Random;
+
+import org.mapdb.BTreeMap;
+import org.mapdb.DB;
+import org.mapdb.DBMaker;
+import org.opendedup.collections.LongLongValueSerializer;
+import org.opendedup.collections.SerializerKey;
+
+public class MapDBTest {
+	static BTreeMap<byte[], byte[]> indexMap = null;
+	static DB hashDB = null;
+
+	public static void main(String[] args) {
+		hashDB = DBMaker.fileDB("c:\\temp\\watchhashes.db").closeOnJvmShutdown().fileMmapEnable()
+				.allocateIncrement(1024 * 1024 * 5)
+				// TODO memory mapped files enable here
+				.make();
+		File f  = new File("c:\\temp\\watchhashes.db");
+		indexMap = hashDB.treeMap("map", new SerializerKey(),new LongLongValueSerializer() ).createOrOpen();
+		byte[] k = new byte[16];
+		byte[] v = new byte[16];
+		long tm = System.currentTimeMillis();
+		int it = 0;
+		ByteBuffer bf = ByteBuffer.wrap(v);
+		for (int i = 0; i < 100_000_000; i++) {
+			//rnd.nextBytes(k);
+			bf.position(0);
+			bf.putInt(i);
+			if(!indexMap.containsKey(k))
+				indexMap.put(k, v);
+			
+			if (it == 1_000_000) {
+				long ct = (System.currentTimeMillis() - tm) / 1000;
+				long fl = f.length();
+				System.out.println( ct + "," + i + "," +fl);
+				it = 0;
+				tm = System.currentTimeMillis();
+			}
+			it++;
+		}
+		
+		Random r = new Random();
+		int ki = -1;
+		it=0;
+		tm = System.currentTimeMillis();
+		for (int i = 0; i < 20_000_000; i++) {
+			
+			while(ki < 0)
+				ki = r.nextInt(10_000_000);
+			
+			bf.position(0);
+			bf.putInt(ki);
+			
+			byte [] z = indexMap.get(v);
+			if(z == null)
+				System.out.println(ki);
+				
+			ki = -1;
+			if (it == 1_000_000) {
+				long ct = (System.currentTimeMillis() - tm);
+				System.out.println( ct + "," + i);
+				it = 0;
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/util/MappedByteBufferBitSet.java

@@ -1,0 +1,750 @@
+/*******************************************************************************
+ * Copyright (C) 2016 Sam Silverberg sam.silverberg@gmail.com	
+ *
+ * This file is part of OpenDedupe SDFS.
+ *
+ * OpenDedupe SDFS is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * OpenDedupe SDFS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with Foobar.  If not, see <http://www.gnu.org/licenses/>.
+ *******************************************************************************/
+package org.opendedup.util;
+
+import java.io.File;
+import java.io.IOException;
+import java.io.ObjectStreamField;
+import java.nio.ByteBuffer;
+import java.nio.ByteOrder;
+import java.nio.MappedByteBuffer;
+import java.nio.channels.FileChannel;
+import java.nio.channels.FileChannel.MapMode;
+import java.nio.file.Files;
+import java.nio.file.Path;
+import java.nio.file.Paths;
+import java.nio.file.StandardOpenOption;
+
+/**
+ * This class implements a vector of bits that grows as needed. Each component
+ * of the bit set has a {@code boolean} value. The bits of a {@code BitSet} are
+ * indexed by nonnegative integers. Individual indexed bits can be examined,
+ * set, or cleared. One {@code BitSet} may be used to modify the contents of
+ * another {@code BitSet} through logical AND, logical inclusive OR, and logical
+ * exclusive OR operations.
+ * 
+ * <p>
+ * By default, all bits in the set initially have the value {@code false}.
+ * 
+ * <p>
+ * Every bit set has a current size, which is the number of bits of space
+ * currently in use by the bit set. Note that the size is related to the
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/util/NextPrime.java

@@ -1,0 +1,90 @@
+/*******************************************************************************
+ * Copyright (C) 2016 Sam Silverberg sam.silverberg@gmail.com	
+ *
+ * This file is part of OpenDedupe SDFS.
+ *
+ * OpenDedupe SDFS is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * OpenDedupe SDFS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with Foobar.  If not, see <http://www.gnu.org/licenses/>.
+ *******************************************************************************/
+package org.opendedup.util;
+
+import java.io.IOException;
+
+public class NextPrime {
+
+	public static long getNextPrimeL(long input) {
+		long root;
+		boolean isPrime = false;
+		if (input <= 2) {
+			return 2;
+		}
+		for (int k = 3; k < 9; k += 2) {
+			if (input <= k) {
+				return k;
+			}
+		}
+		if (input == ((input >> 1) << 1)) {
+			input += 1;
+		}
+		for (long i = input;; i += 2) {
+			root = (long) Math.sqrt(i);
+			for (long j = 3; j <= root; j++) {
+				if (i == (i / j) * j) {
+					isPrime = false;
+					break;
+				}
+				if (j == root) {
+					isPrime = true;
+				}
+			}
+			if (isPrime == true) {
+				return i;
+			}
+		}
+	}
+
+	public static int getNextPrimeI(long input) throws IOException {
+		long root;
+		boolean isPrime = false;
+		if (input <= 2) {
+			return 2;
+		}
+		for (int k = 3; k < 9; k += 2) {
+			if (input <= k) {
+				return k;
+			}
+		}
+		if (input == ((input >> 1) << 1)) {
+			input += 1;
+		}
+		for (long i = input;; i += 2) {
+			root = (long) Math.sqrt(i);
+			for (long j = 3; j <= root; j++) {
+				if (i == (i / j) * j) {
+					isPrime = false;
+					break;
+				}
+				if (j == root) {
+					isPrime = true;
+				}
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/util/RandomGUID.java

@@ -1,0 +1,231 @@
+/*******************************************************************************
+ * Copyright (C) 2016 Sam Silverberg sam.silverberg@gmail.com	
+ *
+ * This file is part of OpenDedupe SDFS.
+ *
+ * OpenDedupe SDFS is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * OpenDedupe SDFS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with Foobar.  If not, see <http://www.gnu.org/licenses/>.
+ *******************************************************************************/
+package org.opendedup.util;
+
+import java.io.IOException;
+import java.net.InetAddress;
+import java.net.UnknownHostException;
+import java.security.SecureRandom;
+import java.util.Random;
+
+import org.opendedup.hashing.HashFunctions;
+
+/**
+ * Used to generate random GUID(s) with SDFS. GUIDS are generated off of the
+ * SecureRandom function within java @see java.security.SecureRandom .
+ */
+public class RandomGUID extends Object {
+
+	public String valueBeforeMD5 = "";
+	public String valueAfterMD5 = "";
+	private static Random myRand;
+	private static SecureRandom mySecureRand;
+
+	private static String s_id;
+
+	/**
+	 * Static block to take care of one time secureRandom seed. It takes a few
+	 * seconds to initialize SecureRandom. You might want to consider removing
+	 * this static block or replacing it with a "time since first loaded" seed
+	 * to reduce this time. This block will run only once per JVM instance.
+	 */
+
+	static {
+		mySecureRand = new SecureRandom();
+		long secureInitializer = mySecureRand.nextLong();
+		myRand = new Random(secureInitializer);
+		try {
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/util/SDFSVolumeTLogger.java

@@ -1,0 +1,32 @@
+/*******************************************************************************
+ * Copyright (C) 2016 Sam Silverberg sam.silverberg@gmail.com	
+ *
+ * This file is part of OpenDedupe SDFS.
+ *
+ * OpenDedupe SDFS is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * OpenDedupe SDFS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with Foobar.  If not, see <http://www.gnu.org/licenses/>.
+ *******************************************************************************/
+package org.opendedup.util;
+
+import org.apache.commons.logging.Log;
+import org.apache.commons.logging.LogFactory;
+
+public class SDFSVolumeTLogger {
+
+	private static Log log = LogFactory.getLog("sdfs");
+
+	public static Log getLog() {
+		return log;
+	}
+
+}

### 2018-12-12 code/SDFS/src/org/opendedup/util/ShardDBTest.java

@@ -1,0 +1,72 @@
+package org.opendedup.util;
+
+import java.io.File;
+import java.io.IOException;
+import java.nio.ByteBuffer;
+import java.util.Random;
+
+import org.opendedup.collections.HashtableFullException;
+import org.opendedup.collections.ShardedProgressiveFileBasedCSMap2;
+import org.opendedup.sdfs.filestore.ChunkData;
+
+import com.google.common.hash.HashFunction;
+import com.google.common.hash.Hashing;
+
+public class ShardDBTest {
+	static ShardedProgressiveFileBasedCSMap2 hashDB = null;
+	
+	public static void main(String[] args) throws IOException, HashtableFullException {
+		hashDB = new ShardedProgressiveFileBasedCSMap2();
+		
+		
+		File f  = new File("c:\\temp\\shards\\shard3");
+		hashDB.init(150_000_000, f.getPath(), .001);
+		byte[] v = new byte[16];
+		ByteBuffer bf = ByteBuffer.wrap(v);
+		long tm = System.currentTimeMillis();
+		int it = 0;
+		HashFunction hf = Hashing.murmur3_128(6442);
+		for (int i = 0; i < 100_000_000; i++) {
+			bf.position(0);
+			bf.putInt(i);
+			byte [] k = hf.hashBytes(v).asBytes();
+			if(!hashDB.containsKey(k)) {
+				ChunkData cm = new ChunkData(k,i);
+				hashDB.put(cm,false);
+			}
+			if (it == 1_000_000) {
+				long ct = (System.currentTimeMillis() - tm);
+				long fl = f.length();
+				System.out.println( ct + "," + i + "," +fl);
+				it = 0;
+				tm = System.currentTimeMillis();
+			}
+			it++;
+		}Random r = new Random();
+		int ki = -1;
+		it=0;
+		tm = System.currentTimeMillis();
+		for (int i = 0; i < 10_000_000; i++) {
+			while(ki < 0)
+				ki = r.nextInt(10_000_000);
+			bf.position(0);
+			bf.putInt(ki);
+			byte [] k = hf.hashBytes(v).asBytes();
+			if(hashDB.get(k) == -1) {
+				System.out.println("no hit" + ki);
+			}
+			ki =-1;
+			if (it == 1_000_000) {
+				long ct = (System.currentTimeMillis() - tm);
+				long fl = f.length();
+				System.out.println( ct + "," + i + "," +fl);
[…]

### 2018-12-12 code/SDFS/src/org/opendedup/util/StringUtils.java

@@ -1,0 +1,145 @@
+/*******************************************************************************
+ * Copyright (C) 2016 Sam Silverberg sam.silverberg@gmail.com	
+ *
+ * This file is part of OpenDedupe SDFS.
+ *
+ * OpenDedupe SDFS is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * OpenDedupe SDFS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with Foobar.  If not, see <http://www.gnu.org/licenses/>.
+ *******************************************************************************/
+package org.opendedup.util;
+
+import java.io.IOException;
+
+import java.io.ObjectInput;
+import java.io.ObjectOutput;
+import java.io.UnsupportedEncodingException;
+import java.util.Random;
+import java.util.regex.Pattern;
+
+public class StringUtils {
+	final static long pbc = 1125899906842624L;
+	final static long tbc = 1099511627776L;
+	final static long gbc = 1024 * 1024 * 1024;
+	final static int mbc = 1024 * 1024;
+	final static int kbc = 1024;
+
+	public static void writeString(ObjectOutput out, String string)
+			throws IOException {
+		byte[] b = string.getBytes();
+		out.writeShort((short) b.length);
+		out.write(b);
+	}
+
+	public static String readString(ObjectInput in) throws IOException {
+		short l = in.readShort();
+		byte[] b = new byte[l];
+		in.readFully(b);
+		return new String(b);
+	}
+	
+	static Pattern utfp = Pattern.compile("\\A(\n" +
+			    "  [\\x09\\x0A\\x0D\\x20-\\x7E]             # ASCII\\n" +
[…]

### 2018-12-13 paper/introduction.tex
ING | add other part title into main.tex

@@
 
-本课题通过引入加密重复数据删除方案/系统的相关特性来设计新型频率分析攻击方法，针对性提高频率分析攻击方法的有效性。该研究问题具有很高的实际价值且在面向加密重复数据删除的攻击中，已有工作提出了基于数据块局部性（chunk locality）\citing{zhu2008avoiding,lillibridge2009sparse,xia2011silo}的频率分析攻击\citing{li2017information}，在此基础上改进攻击方案具有明确的可行性。
+本课题通过引入加密重复数据删除方案/系统的相关特性来设计新型频率分析攻击方法，针对性提高频率分析攻击方法的有效性。该研究问题具有很高的实际价值且在面向加密重复数据删除的攻击中，已有工作提出了基于数据块局部性（chunk locality）\citing{zhu2008avoiding,lillibridge2009sparse,xia2011silo}的频率分析攻击\citing{li2017information}，在此基础上改进攻击方案以提高频率分析攻击实际效果具有明确的可行性。
 
@@
 \end{enumerate}
+
+\section{论文结构及安排}

### 2018-12-13 paper/Conclusion.tex
ING | background done with all cite insetered

\chapter{结论}
\label{sec:Conclusion}

Encrypted deduplication applies deterministic encryption, and leaks the frequencies of plaintexts. This paper revisits the security vulnerability  due to frequency analysis, and demonstrates that encrypted deduplication is even more vulnerable towards inference attacks. We propose two new frequency analysis attacks, both of which  achieve high inference rate and high inference precision, while under different assumptions of adversarial knowledge. We empirically evaluate our attacks with three real-world datasets, present a variety of new observations about their natures, and further analyze how they bring actual damages. We also discuss the advantages and disadvantages of possible countermeasures to advise practitioners for securely implementing and deploying encrypted deduplication storage systems.

% types of files are especially insecure under these attacks.    
% We propose two new inference attacks, which augment the prior attack \cite{li17} with high precision inference and relaxed adversarial knowledge, respectively.   
% While prior work \cite{li17} has illustrated the vulnerability  via frequency analysis, this paper presents an in-depth study on the security of encrypted deduplication, and       
 We pose three directions for future work. First, we consider a complete old backup as the auxiliary information, and do not study how to launch attack if the adversary only has partial knowledge about the old backup. Possibly, we can still apply the frequency analysis attacks to extract characteristics from the available partial backup, and infer ciphertext-plaintext pairs by comparing the characteristics with those in the target backup. One direction is can we design advanced inference attacks, which  perform better than directly applying our attacks in this partial knowledge case?

 % The attack effectiveness depends on how the information in the partial backup correlates with the target backup.       
 Second, we adjust the parameters of the frequency analysis attacks based on their effectiveness, which can only be learnt after the attacks have happened. We do not study how to derive the optimal parameters from auxiliary information beforehand. Future work may do better.

 % We believe the parameter configurations depend on the characteristics of workloads, but do not see how to derive them efficiently.

 % the frequency analysis attacks are parameter sensitive. We adjust parameters based on the attack effectiveness (that can only be measured after the attack happens), and do not study how to identify the optimal parameter configuration  beforehand. We believe the parameter configurations depend on the characteristics of workloads, but do not see how to derive them efficiently. Future work may do better.

 % our proposed attacks are parameter sensitive. In evaluation, we adjust the parameters based on attack results, and report the security vulnerability of encrypted deduplication under some {\em specific} parameter settings of our attacks. We do not  study how to identify the optimal parameter setting of attack without the knowledge of attack results. We begin to consider that the attack configurations possibly depend on the characteristics of target workloads, but do not see how to derive them. Future work may do better.

% help practitioners and researchers better understand the security issues in encrypted deduplication storage and motivate more research along this direction.
% While 
% of encrypted deduplication
% Although it is vulnerable to frequency analysis, prior work \cite{li17} shows that classical frequency analysis can only infer a few original chunks in practice. This paper considers to increase the effectiveness of frequency analysis with additional leakages. Specifically, we present three new inference attacks by exploiting the size and order leakages that have been witnessed in deduplication systems \cite{xia11,lillibridge09,zhu08,douceur02, wilcox-ohearn08, bellare13b}. We evaluate the effectiveness of  our attacks with real-world datasets, and show that they can infer significant amount of original data under different types of workloads. We also discuss possible countermeasures to address the leakage channels exploited by our attacks. We pose the following future works.

Third, we do not implement  attack prototypes against real-world encrypted deduplication storage systems. Another direction is to deploy our attack design and 
report the vulnerability of encrypted deduplication in practice.

% - Our attacks are parameter sensitive. One direction is to explore the relationship between configuration and workload characteristics.

% - There seems a tradeoff between size-based attack and distribution-based attack. Throughout our experiment, size-based attack operates big chunks better, since they have more variances on chunk size. The distribution-based attack is expected to operate small chunks better, because there exists more chunk locality between small chunks.

% - To defend our attacks, one approach is to obfuscate the chunk distributions. A recent work suggests to add redundant chunks to mix up network traffic. It works for changing chunk distribution, but depends on knowing if a chunk is duplicate before deduplication.

% - This paper aims to report the vulnerabilities of encrypted deduplication, while not target on implementing a real attack against practical encrypted deduplication systems. Another direction is deploy our attack design in practice to alert the vulerabilities of encrypted deduplication.

### 2018-12-13 paper/Countermeasure.tex
ING | background done with all cite insetered

\chapter{应对频率分析攻击的对策讨论}
\label{sec:Countermeasure}

In this section, we discuss the advantages and disadvantages of possible countermeasures against the leakage channels exploited in this paper. Note that the countermeasures against size leakage are not enough for preventing our attacks, in which the size information is just optional.

\section{Against frequency leakage:}
MinHash encryption \cite{qin17, li17} encrypts each plaintext with a key derived from the minimum chunk hash over a set of its adjacent chunks, and possibly maps identical plaintexts into  different ciphertexts. The rationale for defense is that MinHash encryption changes frequencies, and disturbs frequency ranking. 
 Note that MinHash encryption also prevents the frequency analysis attacks in this paper, because  we target deterministic encryption (e.g., MLE \cite{bellare13a}), while MinHash encryption is non-deterministic and changes the  frequency distribution of chunks. The disadvantage is that MinHash encryption degrades the storage saving by deduplication, since it breaks the one-to-one mapping between plaintexts and ciphertexts. In addition, MinHash encryption is not an active countermeasure, since its randomness essentially depends on the minimum chunk hashes in the target workloads.

% (rather than the chunk itself \cite{bellare13a}) over its adjacent chunks, so that some identical plaintext chunks can be encrypted into different ciphertext chunks. The rationale of defense is MinHash encryption {\em changes the frequencies of chunks} and leads to rank disturbances in classical frequency analysis. In addition, the nature of MinHash encryption is {\em non-deterministic}, and prevents the distribution-based ranking (see \S\ref{sec:distribution-attack-description}) that targets deterministic encryption. On the other hand, MinHash encryption is not an {\em active} countermeasure, since its defense effectiveness is dominated by workload characteristics (i.e., depending on the diversity of MinHash). It also degrades deduplication effectiveness due to breaking the one-to-one mapping between plaintexts and ciphertexts.

A recent work \cite{zuo18} suggests intentionally adding duplicate chunks to prevent traffic analysis against client-side deduplication. The approach \cite{zuo18} can be applied to address the frequency analysis attacks, since it changes the frequencies of chunks. Compared with MinHash encryption, the countermeasure \cite{zuo18} does not degrade storage efficiency, since only duplicate chunks are added. On the other hand, it  requires the priori knowledge that if particular chunks are duplicate, and only suits the client-side deduplication, which possibly introduces additional leakage channels (see Section~\ref{sec:related}).

Several extended MLE instantiations build on strong cryptographic primitives to defend against the frequency leakage of encrypted deduplication, such as randomized encryption that supports equality testing \cite{abadi13}, hybrid encryption \cite{stanek14}, and interactions with fully homomorphic encryption \cite{bellare15}. They provide provable security, yet how they can be implemented and deployed in practice remains unexplored.

% yet how they are implemented and deployed in practice remains unexplored. 
% some random encryption schemes \cite{stanek14,bellare15,abadi13,lacharite18a}  address the frequency leakage of deterministic encryption. Other than the practical approaches \cite{qin17, li17, zuo18}, they provide provable security, yet building on computationally expensive primitives. 
% % (see Section~\ref{sec:related}).

% are proposed to address frequency leakage from cryptography aspect, yet they are not readily implemented in practice .

% Some studies \cite{stanek14,abadi13,bellare15} aim to achieve stronger security than the more practical schemes focused above. Stanek {\em et al.} \cite{stanek14} design a hybrid encryption scheme where unpopular messages are protected by semantically secure encryption for high security guarantee, while popular messages are protected by CE to enable deduplication. On the other hand, the scheme \cite{stanek14} builds on public-key primitive which is inefficient for encrypting large-size messages. Abadi {\em et al.} \cite{abadi13} construct two schemes for the messages whose distributions are publicly available. Their first scheme generates  random tags and ciphertexts to prevent frequency leakage, yet incurring expensive {\em equality test} for checking duplicates. Their second scheme produces deterministic ciphertexts, and exposes the frequencies of corresponding plaintexts. Interactive MLE \cite{bellare15} introduces interactions into encrypted deduplication, and strengthens the security of both correlated and parameter-dependent messages, yet it is impractical for the use of fully homomorphic encryption. On the contrary to these theoretical contributions \cite{stanek14, abadi13, bellare15}, this paper focuses on the applied aspect, and investigates the security vulnerabilities in practical deduplication.

\section{Against order leakage:}
A simple countermeasure is to disturb the deduplication processing sequence of chunks. For example, we can operate an additional order-scrambling process on the stream of plaintexts before encryption, so as to hide the actual logical order of each plaintext. This prevents the distribution-based attack, because the adversary cannot identify neighboring information correctly. On the other hand, it is not always effective against the clustering-based attack. If scrambling  operates on just a small basis (e.g., the orders of plaintexts in each segment are scrambled), the clustering-based attack still works. 
The disadvantage of the order-scrambling countermeasure is that it breaks chunk locality and leads to performance drop in large-scale deduplication \cite{xia11,zhu08,lillibridge09}.

% On the other hand, if we operate scrambling        
% {\em scrambling}, which intentionally disturbs the deduplication processing sequence of chunks. 
% operates the stream  before deduplication and disturbs the order of each plaintext. 
% disturbs the orders of plaintexts before deduplication 
% to scramble the orders of plaintexts. Specifically, the scrambling approach , and randomly changes the order of each plaintext.   
% A countermeasure is to scramble the orders of chunks, so as to prevent adversary from learning the actual order of each chunk. One note is the scrambling countermeasure should be applied by taking similarity into account; otherwise, the adversary can exploit the property for inference attack (see \S\ref{sec:clustering-attack}). For example, applying scrambling in a small basis (e.g., within a segment) is not enough for preventing the clustering-based attack. On the other hand, large-scale scrambling breaks chunk locality completely, and leads to significant degradation of deduplication performance .

\section{Against size leakage:}
As suggested by prior work \cite{ritzdorf16}, we can pad each plaintext with additional data to obfuscate the actual size of this plaintext. However, we note that the padding scheme is not straightforward, since it requires to add identical redundancies to the same plaintexts; otherwise the storage system cannot detect duplicates for deduplication. One possible solution is to build on the paradigm of MLE \cite{bellare13b,bellare13a}. We compute the cryptographic hash of each plaintext as a seed, and use it to generate variable-size pseudorandom data to be padded with the  plaintext. Like MLE, this solution comes at the expense of server-aided approach \cite{bellare13b} to defend against brute-force attack (see Section~\ref{sec:related}).

% A countermeasure is to sacrifice storage efficiency and {\em pad each chunk with additional data}, which can obfuscate the original size of this chunk. The padding scheme is not straightforward, as it is required to {\em add identical redundant data to the same chunks}; otherwise, the server cannot detect duplicates for deduplication. One possible solution is based on the spirit of MLE \cite{bellare13b,bellare13a}. 
% Specifically, we compute the cryptographic hash of each chunk as a seed, and use the seed to generate variable-size pseudorandom data to be padded with the corresponding chunk. Like MLE, this solution comes at the expense of server-aided approach \cite{bellare13b} to defend against brute-force attack (see \S\ref{sec:related}).

  Instead of variable-size chunking, we can use fixed-size chunking to 
 generate equal-size chunks for deduplication. Since all chunks have the same size, the adversary cannot exploit size information to differentiate them.  Although fixed-size chunking suffers from boundary shift, it achieves almost the same storage saving of deduplication as variable-size chunking in VM disk images \cite{jin09}. Thus, we suggest applying fixed-size chunking in its favorable workloads to prevent size leakage.

  % make the leaked size information hard to be exploited for inference attack. It suffers from the shift of chunk boundaries and is less effective for majority workloads, while prior work \cite{jin09} shows fixed-size chunking achieves almost the same storage efficiency as variable-size chunking for VM disk images.

% , although does not address size leakage explicitly, can make the available size information hard to be exploited for inference attack. On the other hand, it sacrifices deduplication effectiveness in most of storage workloads due to the shift of chunk boundaries.

### 2018-12-13 paper/Experiments.tex
ING | background done with all cite insetered

\chapter{实验测试与分析}
\label{sec:Experiment}

In this section, we present the trace-driven evaluation results to demonstrate
the severity of our proposed frequency analysis attacks against encrypted
deduplication.

\section{Methodology}
\label{sec:dataset}

\begin{table}[!t]
    \caption{Characteristics of experimental datasets.}
\small
\label{tab:dataset}
\renewcommand{\arraystretch}{1.2}
\vspace{-3pt}
\centering
\begin{tabular}{|c|c|c|c|}
\hline
 \multirow{2}{*}{\bf Dataset} & \multirow{2}{*}{\bf Category} & \multicolumn{2}{c|}{\bf Characteristics in Each Snapshot} \\
\cline{3-4}
    & &  \#Logical (Million) & \#Unique (Million) \\
\hline
    \multirow{6}{*}{FSL} & User004  & 1.0-1.3 & 0.7-0.9\\
 \cline{2-4}
              & User007 &  3.5-5.2 & 2.3-3.6 \\
 \cline{2-4}
              & User012 &  25.0-26.4 & 8.9-9.7 \\
\cline{2-4}
              & User013 &  1.8-5.7 & 1.2-4.2 \\
\cline{2-4}
              & User015 &  13.4-20.5 & 9.0-11.0 \\
\cline{2-4}
              & User028 &  6.0-10.3 & 3.5-6.8 \\
\hline
\hline
    \multirow{4}{*}{MS} & Win7  & 61.6-61.8 & 61.1-61.3\\
\cline{2-4}
              & Serv-03 & 10.6-10.7 & 8.4-8.5\\
\cline{2-4}
              & Serv-08 & $\sim$6.5 & $\sim$3.8 \\
\cline{2-4}
              & Vista-B &  $\sim$7.6 & $\sim$2.0\\
\cline{2-4}
              & Vista-U &  $\sim$21.0 & $\sim$10.4 \\
\hline
\hline

    \multirow{6}{*}{VM} & User1  &  \multirow{6}{*}{2.6} & $\sim$0.9 \\
\cline{2-2}
\cline{4-4}
              & User2 &  & 1.1-1.3 \\
\cline{2-2}
\cline{4-4}
              & User3 &  & 0.9-1.1 \\
\cline{2-2}
\cline{4-4}
              & User4 &  & $\sim$0.9 \\
\cline{2-2}
\cline{4-4}
              & User5 &  & 0.9-1.0 \\
\cline{2-2}
\cline{4-4}
              & User6 &  & 0.9-1.1 \\
\hline
\end{tabular}
\medskip

\raggedright
    The notations \#Logical and \#Unique denote the total number of logical and unique chunks in each experimental snapshot, respectively. 
    % All VM images have a fixed size of 10GB and hence the same number of logical chunks.
\end{table}

%\begin{table}[!t]
%\small
%\caption{Experimental datasets.}
%\label{tab:dataset}
%\renewcommand{\arraystretch}{1.2}
%\vspace{-3pt}
%\centering
%\begin{tabular}{|c|c|c|}
%\hline
%{\bf Dataset} & {\bf Category} & {\bf Approximate Logical Size} \\
%\hline
%\hline
%%\multirow{2}{*}{FSL} & Physical  & 431.9GB  & 659.3GB & 584.3GB \\
%	\multirow{6}{*}{FSL} & User004  & 10GB/backup $\times$ 14 backups \\
%\cline{2-3}
%			  & User007 & 39GB/backup $\times$ 14 backups \\
%\cline{2-3}
%			  & User012 & 244GB/backup $\times$ 14 backups \\
%\cline{2-3}
%			  & User013 & 22GB/backup $\times$ 14 backups\\
%\cline{2-3}
%			  & User015 & 158GB/backup $\times$ 14 backups\\
%\cline{2-3}
%			  & User028 & 77GB/backup $\times$ 14 backups\\
%\hline
%\hline
%\multirow{4}{*}{MS} & WIN7  & 425GB/snapshot $\times$ 4 snapshots \\
%\cline{2-3}
%			  & Serv-03 & 78GB/snapshot $\times$ 4 snapshots \\
%\cline{2-3}
%			  & Serv-08 & 48GB/snapshot $\times$ 4 snapshots \\
%\cline{2-3}
%			  & Vista-B & 55GB/snapshot $\times$ 4 snapshots \\
%\cline{2-3}
%			  & Vista-U & 159GB/snapshot $\times$ 4 snapshots \\

%\hline
%\hline

%\multirow{6}{*}{VM} & User1  & 25GB/backup $\times$ 13 backups \\
%\cline{2-3}
%			  & User2 & 28GB/backup $\times$ 13 backups \\
%\cline{2-3}
%			  & User3 & 26GB/backup $\times$ 13 backups \\
%\cline{2-3}
%			  & User4 & 25GB/backup $\times$ 13 backups\\
%\cline{2-3}
%			  & User5 & 25GB/backup $\times$ 13 backups\\
%\cline{2-3}
%			  & User6 & 27GB/backup $\times$ 13 backups\\

%% \multicolumn{2}{|c|}{\bf Storage saving} & 98.6\% & 98.3\% \\
%\hline
%\end{tabular}
%\end{table}
We evaluate our attacks using the following real-world datasets, whose
characteristics are summarized in Table~\ref{tab:dataset}. 
% Table~\ref{tab:dataset} summarizes the characteristics of the experimental datasets used in our experiments. 
% We evaluate our attacks using the following datasets. 
% investigate the security implications of the leakages (see \S\ref{sec:background}) by means of simulated attacks,

\begin{itemize}[leftmargin=*]
\item 
\textbf{FSL:} This dataset is collected by the File systems and
        Storage Lab (FSL) at Stony Brook University \cite{sun16,FSL14,sun18}. We focus on
the {\em fslhomes} snapshots, each of which includes an ordered list of 48-bit
chunk hashes that are produced by variable-size chunking under an average size
of 8KB, as well as the corresponding metadata information (e.g., chunk size,
file name extension, etc). We pick the snapshots from January 22 to May 21 in
2013, and select six users (i.e., User004, User007, User012, User013, User015,
and User028) that have the complete daily snapshots over the whole duration.
We collect these snapshots on a weekly basis, and hence form 14 weekly full
backups for each user.  
\item 
\textbf{MS:} This dataset is collected by Microsoft
\cite{meyer11} and publicized on SNIA \cite{ms}. The original dataset contains
the Windows file system snapshots that span from September 5 to October 31,
2009. Each snapshot is represented by the 40-bit chunk hashes under different
average sizes obtained from Rabin fingerprinting \cite{rabin81}.  We focus on
the snapshots that have been installed with the operating systems in the
following categories: Windows 7 (Win7), Microsoft Windows Server 2003
(Serv-03), Microsoft Windows Server 2008 (Serv-08), Microsoft Windows Vista
Business Edition (Vista-B), and Microsoft Windows Vista Ultimate Edition
(Vista-U). In each category, we pick four snapshots, each of which is
configured with the average chunk size of 8KB.   
\item 
\textbf{VM:} This dataset is collected from a university programming course in
Spring 2014. The original dataset includes a number of VM image snapshots for
the students enrolled in the course, and each snapshot has a fixed size of
10GB and is represented by the ordered list of SHA-1 hashes of 4KB fixed-size
chunks. We focus on 6 users (i.e., User1-User6) and extract their snapshots
into 13 weekly backups.  
%Prior studies \cite{qin17, li15} have used some variants of the dataset for
%different evaluation purposes, and we aim to validate the severity of the
%clustering-based attack against VM disk images.   
\end{itemize}

Our datasets do not contain actual content, so we mimic the adversarial
knowledge based on chunk hashes. Specifically, we use the ordered lists of
chunk hashes in some snapshots as the auxiliary information $\mathbf{A}$ and
the ground truth $\mathbf{M}$, respectively. To simulate encryption, we apply
an additional hash function over each original chunk hash (that represents a
plaintext) in $\mathbf{M}$, and truncate the result into an agreed number of
bits specific to the used dataset. The truncated result mimics a ciphertext in
$\mathbf{C}$. For each inferred ciphertext-plaintext pair $(C, M)$, we verify
its correctness by applying the same simulated encryption on $M$ and comparing
the result with $C$. Note that the clustering-based attack can operate at the
segment level, and infer the ciphertext-plaintext segment pair $(S_\mathbf{C},
S_\mathbf{A})$.  In this case, we check $(S_\mathbf{C}, S_\mathbf{A})$ by
examining each ciphertext in $S_\mathbf{C}$ is exactly mapped from each
plaintext in $S_\mathbf{A}$.

% , although we cannot recover each chunk in the real attack.   
% We count the leakage (see \S\ref{sec:threat}) of each ciphertext chunk, and use it for our inference attacks.  
% MD5 on each hash (that represents a plaintext) in $\mathbf{M}$, and truncate the resulting hash into an agreed number of bits (e.g., 48-bit for FSL, 40-bit for MS, and 160-bit for VM).

We measure the severity of the attacks by the inference rate and the inference
precision (see Section~\ref{sec:threat}).

\section{Results of Distribution-based Attack}
\label{sec:experiment-distribution}

\begin{figure*}[t]
    \centering
    \begin{tabular}{p{.31\textwidth}p{.31\textwidth}p{.31\textwidth}}
        \multicolumn{3}{c}{\includegraphics[width=.7\textwidth]{pic/legend-fsl-line.pdf}} \smallskip \\
        \includegraphics[width=.3\textwidth]{pic/distribution-impact-u.pdf} &
        \includegraphics[width=.3\textwidth]{pic/distribution-impact-r.pdf} &
	    \includegraphics[width=.3\textwidth]{pic/distribution-impact-t.pdf} \medskip \\
        {\footnotesize 
        \centering
        (a) Impact of $u$: $r$ = 0; $t \rightarrow \infty$
        } &
        {\footnotesize
        (b) Impact of $r$: $u$ = 128 for User004, User013 and User015, and $u$ = 256 for User007, User012 and User028; $t \rightarrow \infty$
        } &
        {\footnotesize
        (c) Impact of $t$: $u$ = 128 for User004, User013 and User015, and $u$ = 256 for User007, User012 and User028; $r$ = 10
        } \\
    \end{tabular}
    \caption{Experiment 1 (Impact of parameters): impact of $(u, r, t)$ in distribution-based attack.}
    \label{fig:distribution-impact}
\end{figure*}

\subsection{Experiment 1 (Impact of parameters):}
We evaluate the impact of the parameters $(u, r, t)$ in the distribution-based
attack. We drive our evaluation using the FSL dataset, and use the 12th weekly
backup of each user as the auxiliary information to infer original plaintexts
in corresponding 14th weekly backup.  We configure $t \rightarrow \infty$ and $r$ = 0 to
evaluate the impact of $u$ (in this case, the distribution-based attack
reduces to the locality-based attack \cite{li17}). Our rationale is to avoid
the disturbances by other parameters.

Figure~\ref{fig:distribution-impact}(a) shows the impact of $u$,
when we vary $u$ from 2 to 512. Regarding inference rate, we have the same
observation as the prior work \cite{li17}. Specifically, the inference rates
first increase with $u$, since the attack can infer more ciphertext-plaintext
pairs. After hitting the maximum values (e.g., 13.9\% for User004, 13.6\% for
User007, 1.4\% for User012, 0.5\% for User013, 0.7\% for User015, and 6.1\%
for User028), they decrease.  The reason is that the underlying frequency
analysis introduces a large number of false positives that compromise the
inferences over corresponding neighbors.

The prior work \cite{li17} does not report the inference precision about the
attack. We observe that the inference precisions for all users are at a
fairly low level (e.g., less than 40\%), except the case of $u = 2$ for
User028 that does not introduce any false positives. On the other hand, the
inference rate in the special case is about 0.0001\%, meaning that the attack
only infers a few ciphertext-plaintext pairs. In addition, as $u$ increases,
the inference precisions decrease slightly. For example, when $u$ increases
from 2 to 512, the inference precision of User004 drops from 30.7\% to 12.8\%.

{\bf Observation (1) --} {\em A relatively larger $u$ increases the inference
rate, yet it decreases the inference precision (i.e., more false positives are
introduced). }

Informed by the impact of $u$, we set $u$ at 128 for User004, User013 and
User015, and at 256 for User007, User012 and User028, respectively, in order
to evaluate the impact of $r$ and $t$. 
% {\bf Note that the configuration
% exceeds the best one that leads to the highest inference rate. PC: I don't
% quite understand???} 
Our rationale is to increase the coverage of inferred ciphertext-plaintext
pairs, while we use $r$ and $t$ to filter possibly false positives.

We first configure $t \rightarrow \infty$ and evaluate the impact of $r$. Figure~\ref{fig:distribution-impact}(b) shows the results. We observe that the
inference rates of majority users increase with $r$. For example, when we vary
$r$ from 0 to 16, the inference rates grow from 9.5\% to 16.0\%, from 10.0\%
to 13.0\%, from 0.5\% to 0.7\%, and from 4.7\% to 5.6\% for User004, User007,
User013, and User028, respectively. The reason is that the distribution-based
attack addresses disturbances to frequency ranking, and infer more correct
ciphertext-plaintext  pairs. On the other hand, the inference rates decrease
slightly from 1.3\% to 0.8\% and from 0.6\% to 0.4\% for User012 and User015,
respectively. The reason is that they examine a large range of plaintexts and
may introduce more false positives. In addition, the inference precisions for
all users are  at a low level (e.g., less than 45\%), and have similar
tendencies with corresponding inference rates.

{\bf Observation (2) --} {\em A larger $r$ provides more opportunities of
identifying correct ciphertext-plaintext pairs, yet it also increases the
probability of having false positives.}

Then, we fix $r$ = 10 and evaluate the impact of $t$. 
Figure~\ref{fig:distribution-impact}(c) shows the results. When $t$ is small
(e.g., less than 0.5), we observe that the attack misjudges and filters a
significant number of ciphertext-plaintext pairs, even they are correct. This
introduces {\em false negatives} that reduce the inference rate. As $t$
increases, the number of false negatives decreases.  When $t$ = 1.5, the
inference rates hit the maximum values at 21.2\%, 18.2\%, 10.4\%, 1.2\%,
1.2\%, and 13.5\% for User004, User007, User012, User013, User015, and
User028, respectively. When $t$ further increases to 2, the corresponding
inference rates drop to 20.5\%, 17.1\%, 8.3\%, 1.2\%, 1.0\%, and 11.2\%,
respectively. The reason is that if $t$ is too large, it cannot filter false
positives effectively. For the same reason, the inference precisions for all
users decrease with $t$.  
% The inference rates first  increase with $t$, since the number of false negatives (i.e., misjudge some correctly inferred ciphertext-plaintext pairs in filtering) are reduced.

% implies that the distribution-based attack  returns more incorrect ciphertext-plaintext chunk pairs, which affects attack severity.

{\bf Observation (3) --} {\em A smaller $t$ filters a large fraction of false
positives, yet it introduces more false negatives.}

\subsection{Experiment 2 (Comparison with prior attack):}
We compare the severity of the distribution-based attack with that of the
locality-based attack \cite{li17}. In addition to using the FSL dataset like
Experiment~1, we include the MS dataset for cross-dataset validation.
Specifically, for each MS category, we choose two snapshots at a time, use one
to infer the other, and evaluate the average inference rate and precision.

We consider the following attack instances for comparison. 
%
\begin{itemize}[leftmargin=*]
\item 
$\tt Baseline$: We re-implement the locality-based attack based on the
parameter configuration suggested in \cite{li17}. Specifically, it infers 5
most frequent ciphertext-plaintext pairs in the first invocation (i.e., to
initialize a set of ciphertext-plaintext pairs for iteration) of frequency
analysis, and 30 in each following invocation (i.e., to iteratively infer ciphertext-plaintext pairs from 
 neighbors).  
\item 
$\tt Distribution$ and $\tt Distribution^S$: We consider two attack instances
of the distribution-based attack, denoted by $\tt Distribution^S$ and ${\tt
Distribution}$, which operate with and without size information,
        respectively (i.e., the superscript $\tt S$ indicates that the attack instance operates with size information). 
        We configure $\tt Distribution^S$ and ${\tt Distribution}$
under the same configuration of  ${\tt Baseline}$. In addition, we choose
$r$ and $t$ in both  $\tt Distribution^S$ and ${\tt Distribution}$ in the following way: for the FSL dataset, we fix $r$ = 10 for
all users, and individually set $t$ = 1.5, 1.2, 1, 1, 0.7, and 0.9 for
User004, User007, User012, User013, User015, and User028, respectively; for
the MS dataset, we also fix $r$ = 10 for all categories, and set $t$ = 2 for
Win7 and Serv-08, and $t$ = 1.6 for Vista-U, Serv-03, and Vista-B, respectively.
This is informed by our tests for optimal configurations of the datasets.   
\item 
$\tt Distribution$-$\tt o$ and $\tt Distribution^S$-$\tt o$:
We consider two additional distribution-based attack instances, denoted by $\tt Distribution$-$\tt o$
and $\tt Distribution^S$-$\tt o$, which apply the same configurations for $r$ and $t$ as with $\tt Distribution$ and $\tt
Distribution^S$, and further use larger $u$ to increase the
coverage of inferred ciphertext-plaintext pairs.  
        Specifically, we configure $u$ in $\tt Distribution$-$\tt o$
and $\tt Distribution^S$-$\tt o$ in the following way:  
        for the FSL
dataset, we apply the same configuration of $u$ in Experiment~1; for the MS
dataset, we set $u$ = 128 for Win7, and $u$ = 30 for Serv-03, Serv-08,
Vista-B, and Vista-U. 
        % Our rationale is to increase
% the inference rate, while we expect  this only leads to a slight
% degradation of the inference precision since the distribution-based attack
% filters a large fraction of false positives. 
\end{itemize}

\begin{figure*}[t]
    \centering
    \begin{tabular}{c@{\hskip 2em}c}
        \multicolumn{2}{c}{\includegraphics[width=.7\textwidth]{pic/legend-fsl-bar.pdf}} \smallskip \\
        \includegraphics[height=2.1in]{pic/distribution-comparison-fsl.pdf} &
        \includegraphics[height=2.1in]{pic/distribution-comparison-ms.pdf} \medskip \\
        {\footnotesize 
        (a) FSL dataset 
        } &
        {\footnotesize
        (b) MS dataset 
        } \\
    \end{tabular}
    \caption{Experiment 2 (Comparison with prior attack): comparison of attack severity for distribution-based attack and locality-based attack.}
    \label{fig:distribution-comparison}
\end{figure*}

% \begin{itemize}[leftmargin=*]
	% \item {\em Distribution-I:} We configure our proposed distribution-based attack with the {\em same} configuration of the baseline above. Informed by Experiment 3, we further choose the distribution-based ranking parameters in the following way: for the FSL dataset, we fix $r$ = 10 for all users, and individually set $t$ = 1.5, 1.2, 1, 1, 0.7, and 0.9 for User004, User007, User012, User013, User015, and User028; for the MS dataset, we fix $r$ = 10 for all categories, and configure $t$ as 2 for Win7 and Serv-08 and as 1.6 for Vista-U, Serv-03, and Vista-B, respectively.

	% \item {\em Distribution-II:} We configure our proposed distribution-based attack with the same ranking configuration of distribution-I, while building on a larger $u$ to infer more chunk pairs. The rationale is to increase inference rate, while we expect the inference precision is degraded slightly as the attack can filter out unreasonable inferences. Specifically, for the FSL dataset, we set $u$ = 128 for User004, User013 and User015, and $u$ = 256 for User007, User012 and User028, respectively; for the MS dataset, we set $u$ = 128 for Win7, and $u$ = 30 for Serv-03, Serv-08, Vista-B, and Vista-U, respectively.
% \end{itemize}

Figure~\ref{fig:distribution-comparison}(a) shows the
comparison results of the FSL dataset. We observe that different instances of
the distribution-based attack outperform the locality-based attack in almost
all cases. For example, regarding User028, the lowest inference rate of the
distribution-based attack is 11.4\%, with the precision of 84.1\% (due to $\tt
Distribution$), while the corresponding inference rate and precision of
$\tt Baseline$ are only 1.2\% and 1.7\%, respectively; this implies that the distribution-based attack reduces the number of false postives by 82.4\% in this case.

{\bf Observation (4) --} {\em The distribution-based attack significantly
increases the inference precision, while achieving a higher inference rate than
the locality-based attack.}

$\tt Distribution^S$ and $\tt Distribution^S$-$\tt o$ have higher inference
precisions than $\tt Distribution$ and $\tt Distribution$-$\tt o$,
respectively, since they further filter false positives by size information.
For example, for User004, $\tt Distribution^S$ and $\tt Distribution^S$-$\tt o$  reduce the fraction of false positives in  $\tt Distribution$ and $\tt Distribution$-$\tt o$ from 35.2\% to 1.7\% and from 35.3\% to 2.2\%, respectively. However, in the same case,    
 we observe that the inference rates of $\tt Distribution$ and $\tt Distribution$-$\tt o$ are 20.0\% and 21.2\%, slightly higher than those of  
$\tt Distribution^S$ and
$\tt Distribution^S$-$\tt o$ by 2.0\% and
0.4\%, respectively. The reason is that $\tt Distribution$ and $\tt
Distribution$-$\tt o$ infer a small number of correct results from the
neighbors of incorrect ciphertext-plaintext pairs. In other words,  although
$(C, M)$ is an incorrect ciphertext-plaintext pair, the neighbors of $C$ may
correspond to those of $M$ with a small probability. Even in this case, all distribution-based attack instances are more severe than the locality-based attack instance. Specifically, the inference rate of $\tt Baseline$ is only 15.2\%, lower than those of the best and the worst distribution-based attack instances by 6.0\% and 2.8\%, respectively.

% For the same reason, $\tt Baseline$ has higher inference rate than $\tt Distribution^S$ in User013.

{\bf Observation (5) --} {\em Filtering incorrect inference results improves
the inference precision, yet it degrades the coverage of inferred
ciphertext-plaintext pairs and possibly decreases the inference rate.
}

We further observe that although $\tt Distribution$-$\tt o$ and $\tt
Distribution^S$-$\tt o$ build on larger $u$, their inference rates are just
slightly higher than those of $\tt Distribution$ and $\tt Distribution^S$ by
0.4\% and 0.9\%, respectively. The reason is that the distribution-based
attack iterates inference just through neighbors, and has a bounded coverage
of inferred ciphertext-plaintext pairs. The further increase of $u$ only adds
a small number of new correct  ciphertext-plaintext pairs into results.

Figure~\ref{fig:distribution-comparison}(b) shows the
results of the MS dataset. Both locality-based and distribution-based attacks
have high inference rates and precisions in most MS categories (except Win7).
The possible reason is that MS snapshots are highly correlated (e.g., the
variance of the total number of chunks is small, as shown in
Table~\ref{tab:dataset}).  We observe that the distribution-based attack still
outperforms the locality-based attack. For example, in Vista-U, the inference
rates and precisions of all inferences of the distribution-based attack are
above 24.1\% and 96.4\%, while those of $\tt Baseline$ are 21.7\% and 87.1\%,
respectively.

Note that both  distribution-based and  locality-based attacks have low
inference rates (e.g., less than 0.01\%) in the Win7 category. The reason is
 that Win7 includes a large fraction (e.g., more than 98.8\%, as shown in
Table~\ref{tab:dataset}) of unique chunks, which cannot be correctly
inferred by the frequency analysis attacks.

% We do not include Win7  in the comparison, since all attack instances have low effectiveness. We observe all attacks have higher severity than those in the FSL dataset.

\begin{figure*}[t]
     \centering
    \centering
    \begin{tabular}{c@{\hskip 2em}c}
        \multicolumn{2}{c}{\includegraphics[width=.25\textwidth]{pic/legend-effectiveness.pdf}} \smallskip \\
        \includegraphics[height=2.2in]{pic/distribution-effectiveness-wo-size.pdf} &
	\includegraphics[height=2.2in]{pic/distribution-effectiveness-w-size.pdf} \medskip \\
        {\footnotesize 
        (a) Distribution-based attack without size information  
        } &
        {\footnotesize
        (b) Distribution-based attack with size information 
        } \\
    \end{tabular}
	\caption{Experiment 3 (Attack effectiveness): severity of distribution-based attack in FSL dataset.}
	\label{fig:experiment-distribution-effectiveness}
\end{figure*}

\subsection{Experiment 3 (Attack effectiveness):} We consider a long-term
backup scenario and examine the effectiveness of the distribution-based attack
with the FSL dataset. Specifically, we choose the $i$th FSL weekly backup of
each user as the auxiliary information to infer original plaintexts in the corresponding $(i+w)$th FSL
weekly backup. Clearly, the smaller $w$ is, the higher correlation between the
auxiliary information and the target backup will be.  We configure the two  
distribution-based attack instances $\tt Distribution$-$\tt o$ and $\tt Distribution^S$-$\tt o$
like Experiment~2, and evaluate their inference rates and inference precisions that
are averaged for all available $i$ for each user.

Figure~\ref{fig:experiment-distribution-effectiveness}(a) shows the results. The
distribution-based attack has varying inference rate and precision  across
users. For example, in the favorable case like User004, it achieves the
highest inference rates of 24.8\%, 24.5\%, and 24.0\% with the precisions of
67.3\%, 67.0\%, and 66.5\% for $w$ = 1, 2, and 3, respectively; in the
non-favorable case like User015, the inference rate of the distribution-based
attack is only around 0.3\%. The possible reason is that the backup data from
User015 has low chunk locality.

In addition, we observe that the correlation (i.e., $w$) of the auxiliary
information has low impact on the effectiveness of the distribution-based
attack.  For example, when $w$ increases from 1 to 3, it only leads to limited
degradations on inference rate (e.g., less than 1.4\%) and precision (e.g.,
less than 5.6\%). The reason is that the distribution-based attack addresses
disturbances to frequency ranking and preserves attack effectiveness.

{\bf Observation (6) --} {\em The distribution-based attack can limit the
degradation of attack effectiveness in the presence of loosely correlated
auxiliary information.}

% We also use the instance in Experiment 2 to evaluate the effectiveness of the distribution-based attack that operates with
 % size information. 
 Figure~\ref{fig:experiment-distribution-effectiveness}(b) shows the results of $\tt Distribution^S$-$\tt o$. We observe that it has similar inference rate with $\tt Distribution$-$\tt o$,  
 while achieving much higher precision. For example, the average inference precision of all users are 93.1\%, 92.8\%, and 92.4\% for $w$ = 1, 2, and 3, respectively.

% Figure~\ref{fig:experiment-distribution-severity-ms} shows the attack results of the MS dataset. The distribution-based attack achieves high severity. For example, it can infer 24.0\% of unique chunks in Vista-U with a precision of 96.2\%.

% Although there is l

\section{Results of Clustering-based Attack}
\label{sec:experiment-clustering}

\subsection{Experiment 4 (Impact of parameter):} We first evaluate the impact
of the parameter $k$, which defines the upper bound distance
in combining the closest clusters.  We use both the FSL and the VM datasets to
study how $k$ affects the underlying clustering scheme in the attack.
Specifically, we apply segmentation on the last backup of each considered FSL
and VM user, respectively, and generate the segments that have a fixed size of
4MB.

The clustering scheme aims to aggregate similar ciphertext segments into the
same cluster, without compromising the confidentiality of chunks in each
ciphertext segment.  To quantify its effect, we compare the results of
clustering with those of a {\em real} classification approach, which directly
classifies segments by their minimum chunk hash.  Suppose we generate $m$ real
classes of segments by classification, and $\widetilde{m}$ clusters by the
clustering scheme, respectively.  We consider {\em clustering closeness},
evaluated by $\frac{{\sf abs}(m-\widetilde{m})}{m}$ (where 
${\sf abs}(m-\widetilde{m})$ returns the absolute value of $m-\widetilde{m}$),
which quantifies how the  number of clusters approximates that of real
classes. In addition, let $\hat{m}$ be the number of clusters, in which all
segments are similar (i.e., have the same minimum chunk hash). We also
consider {\em clustering correctness}, evaluated by
$\frac{\hat{m}}{\widetilde{m}}$, which quantifies how precisely the clustering
scheme groups similar segments.

Figure~7(a) shows the results of the FSL dataset, where we
consider four FSL users (e.g., User004, User007, User015 and User028) for
saving evaluation time. The clustering closeness first increases with $k$,
since the number (i.e., $\widetilde{m}$) of clusters decreases and
approximates $m$. When $k$ increases further, the number of clusters drops
away from $m$, and leads to the increase of clustering closeness.  In
addition, we observe that the clustering correctness gradually decreases with
$k$, because some of non-similar segments (i.e., their minimum chunk hashes are
different) are aggregated into the same cluster. Both results suggest that we
can configure an appropriate $k$ to balance the closeness and correctness of
clustering. For example, when we set $k$ = 0.65 for User015, the corresponding
closeness and correctness are 1.0\% and 94.2\%, respectively. This implies
that the results of the clustering scheme  highly approximates
those of real classification.

{\bf Observation (7) --} {\em By configuring an appropriate $k$ for
clustering, we  approximate the results of  classifying segments, without the knowledge of  minimum chunk hash in each
segment.}

Figure~7(b) shows the results of the VM dataset. We observe
that the clustering closeness and correctness of all VM users have  similar
tendencies with those of FSL users. When we configure $k$ = 0.8, the average
clustering closeness of all VM users is only 3.0\%, while the corresponding
clustering correctness is as high as 93.1\%.

\begin{figure*}[t]
\centering
    \begin{tabular}{cc@{\hspace{0.3in}}p{.32\textwidth}}
    \includegraphics[width=.3\textwidth]{pic/clustering-impact-d-fsl.pdf} &
    \includegraphics[width=.3\textwidth]{pic/clustering-impact-d-vm.pdf} & 
    \includegraphics[width=.3\textwidth]{pic/clustering-effectiveness.pdf} \medskip \\
{\footnotesize 
        (a) FSL dataset } 
&
{\footnotesize 
        (a) VM dataset } 
        &  ~~~ \medskip \\
        \multicolumn{2}{p{.64\textwidth}}{
            \footnotesize Fig.~7\quad Experiment 4 (Impact of parameter): impact of $k$ in the clustering scheme; for clustering closeness, the smaller the better; for clustering correctness, the larger the better. } &
        % \multicolumn{2}{c}{\footnotesize Fig.~6\quad Experiment 4 (Impact of parameter): show impact of $d$ with clustering closeness and correctness; for clustering closeness, the smaller the better; for clustering correctness, the larger the better.} &
        {\footnotesize
Fig.~8\quad Experiment 5 (Attack effectiveness):  severity of clustering-based attack in VM dataset.
        }
\end{tabular}
    \hspace{-1in}
\end{figure*}

% \begin{figure}
% 	\includegraphics[width=.48\textwidth]{pic/clustering-impact-d.pdf}
% 	\caption{Experiment 6 (Impact of parameter).}
% 	\label{fig:experiment-clustering-impact}
% \end{figure}

\begin{table*}[!t]
\small
    \caption{Experiment 6 (Security implications)}
\renewcommand{\arraystretch}{1.2}
\vspace{-3pt}
 \begin{minipage}[t]{0.7\textwidth}
\centering
        (a) Distribution-based attacks \medskip \\
\begin{tabular}{|c|c|c|c|c|c|}
\hline

    \multirow{2}{*}{\bf Type} & \multirow{2}{*}{\bf Extension Name} & \multirow{2}{*}{\bf \centering Range of File Size}  & \multicolumn{2}{c|}{\bf Raw Inference Rate} \\ \cline{4-5} 
    & & &  $\sf Distribution$-$\sf o$ & $\sf Distribution^S$-$\sf o$ \\ \hline
\hline
    Office & doc(x), ppt(x), xls(x) & 10KB-1MB   & 4.9\% & 5.3\%\\
\hline
    Picture & jpg, png &10-100KB  & 7.7\% & 6.7\% \\
\hline
    Source & c, h, cpp, java, py & 10-20KB   & 17.1\% & 15.0\%\\
% \hline
	% Library & .a, .dll, .so \\
% \hline
	% Compression & .bz2, .gz, tar, rar, zip, 7z \\
\hline
    Database & db, po & 20-700KB   & 2.6\% & 2.4\%\\
\hline
    Disk & vmdk, img & 200MB-1GB  & 15.8\% & 16.7\%\\
\hline
\end{tabular}
\label{tab:file}
 \end{minipage}
\hfill
    \begin{minipage}[t]{0.3\textwidth}
    \centering
        (b) Clustering-based attack \medskip \\
    \begin{tabular}{|c|c|}
    \hline
        {\bf Users} & {\bf Raw Inference Rate} \\
    \hline
    \hline
        1 & 13.2\% \\ 
    \hline
        2 & 22.4\% \\ 
    \hline
        3 & 25.7\% \\ 
    \hline
        4 & 28.4\% \\ 
    \hline
        5 & 18.5\% \\ 
    \hline
        6 & 30.8\% \\ 
    \hline
    \end{tabular}
\label{tab:user}
    \end{minipage}

\end{table*}

\subsection{Experiment 5 (Attack effectiveness):} We now study the
effectiveness of the clustering-based attack. Due to the boundary shift of
fixed-size segment, it has low effectiveness
(about 1\% inference rate in our test) against the FSL dataset.  Thus, we use
the VM dataset to examine its severity. To configure the attack, we set $k$ =
0.8 for clustering, and $(u, r, t)$ = (5000, 100, 0.5) for relating ciphertext
clusters to corresponding plaintext clusters.

In our micro-benchmarking, we find that the chunk-level inference in the
clustering-based attack only infers thousands of chunks correctly, which
contributes to a negligible inference rate (e.g., less than 0.01\%).  
% The
% reason is that each cluster includes a large number of chunks, and frequency
% analysis is ineffective in this case. 
Thus, we focus on the
segment-level inference, which presents the bottom line of severity in the
clustering-based attack. To be consistent with the chunk-level measurements, we count inference rate and precision based
on the unique chunks in each correctly inferred segment.

We use the same evaluation methodology of Experiment~3, and report the results
in Figure~8. Specifically, the x-axis describes the index $i$ (where 1 $\leq i \leq$
12) of the VM backup that is used as the auxiliary information for attack,
while the y-axis presents the average inference rate or precision of all VM
users against the $(i+w)$th backup (where $w$ = 1, 2, and 3). We observe that both the inference rate and the inference
precision fluctuate significantly. For example, when using the 3rd backup as
the auxiliary information, the attack achieves the highest inference rates at
18.1\%, 17.1\% and 16.3\%, with the precisions of 76.8\%, 75.0\% and 73.0\%
for $w$ = 1, 2, and 3, respectively. 
On the other hand, when using the 7th
backup as the auxiliary information, the corresponding inference rates and
precisions drop down to 9.6\% and 65.9\%, 6.8\% and 71.2\%, and 6.9\% and
75.6\%, respectively. The reason is that the VM users have heavy updates after
the 7th week, and this reduces the correlation  of adjacent backups. 
On
average, for $w$ = 1, 2 and 3, the clustering-based attack infers 15.8\%,
14.0\%, and 12.6\% ciphertext-plaintext pairs, with the precisions of 71.1\%,
69.1\%, and 68.9\%, respectively. 
% This demonstrates high severity against
% the VM disk images.

\section{Results of Security Implications}
\label{sec:case}
We thus far have examined the severity of inference attacks by quantifying the
correctly inferred ciphertext-plaintext pairs.  However, it remains an open
issue that what are the security implications informed by these results and
how the frequency analysis attacks bring actual damage. In the following
experiment, we evaluate the security implications of our attacks based on the
{\em raw inference rate}, defined as the percentage of raw data content
affected by correctly inferred chunks.

\subsection{Experiment 6 (Security implications):}
We first consider the distribution-based attack, and evaluate its raw
inference rate against {\em different types} of files. We drive the evaluation
using the FSL dataset, since only the FSL dataset includes file metadata (that
includes the extension names of files) in plaintext. Specifically, we focus on
five types of files that have specific extension names (see
Table~\ref{tab:file}(a)): office files ({\em Office}), picture files 
({\em Picture}), programming source files ({\em Source}), database files 
({\em Database}), and disk image files ({\em Disk}). These files occupy more
than 60\% of raw content of FSL snapshots.

We apply the methodology of Experiment~2, and evaluate the raw inference
rates of $\sf Distribution^S$-$\sf o$ and $\sf Distribution$-$\sf o$. 
Table~\ref{tab:file}(a) shows the results. Both attack instances have high raw
inference rates against {\em Disk} (e.g., 15.8\% for 
$\sf Distribution$-$\sf o$ and 16.7\% for $\sf Distribution^S$-$\sf o$),
because each disk file includes a large number of rarely updated chunks that
form high locality within the same file. Interestingly, we observe that 
{\em Source}, although each file is of a small size, also incurs high raw
inference rates by the distribution-based attacks (e.g., 17.1\% for 
$\sf Distribution$-$\sf o$ and 15.0\% for $\sf Distribution^S$-$\sf o$). The
reason is that programming source files are often stored together in file system
(e.g., the source files that belong to the same project locate in an identical
directory) and form a large stretch of correlated chunks, which present high
locality across files. For small and scattered files (e.g., {\em Office}, 
{\em Picture}, and {\em Database}), the distribution-based attacks have
relative low raw inference rates.

{\bf Observation (8) --} {\em The severity of the distribution-based attack depends on the update frequencies, sizes, and spatiality of target files. }

We examine the security implication of the clustering-based attack using the
VM dataset. Specifically, we use the 11th  backup of each VM user  to infer original content in corresponding 13th VM
backup. Since the VM dataset does not contain any metadata, we count the raw
inference rate based on the  whole data content in each VM snapshot.
Note that we filter all zero chunks in the count of raw inference rate,
because they occupy a large fraction in VM disk images \cite{jin09}.

% switch to the clustering-based attack, and infer the content of the last (i.e., the 13th) VM backup based on the corresponding 11th backup. Since the VM dataset does not contain metadata, we evaluate the raw inference rate across different users. Specifically, like Experiment 7, we only consider segment-level attack for high precision, and count the raw inference rate based on the correctly inferred segments. Note that since VM images commonly contain a large fraction of zero chunks ,  we filter out the zero segments in our inferred raw content.

We use the same configuration of Experiment~5, and evaluate raw inference rate
based on segment-level inference.  Table~\ref{tab:user}(b) shows the results
for different users.  We observe that the clustering-based attack achieves high
severity against the VM dataset. For example, it infers up to 30.8\% raw
content of User6's VM backup. On average, the raw inference rate of all users
is as high as 23.2\%.  
% a relatively high raw inference rate.  On average, the raw inference rate is 23.2\% for all users.

{\bf Observation (9) --} {\em The clustering-based attack threatens the
confidentiality of VM disk images. }

### 2018-12-13 paper/RelatedWork.tex
ING | background done with all cite insetered

\chapter{相关工作}
\label{sec:RelatedWork}

\noindent
{\bf MLE instantiations:}  
Recall from Section~\ref{sec:background} that MLE \cite{bellare13a} formalizes the
cryptographic foundation of encrypted deduplication.  The first published MLE
instantiation is convergent encryption (CE) \cite{douceur02}, which uses the
cryptographic hash of a plaintext and its corresponding ciphertext as the
MLE key and the tag, respectively.  Other CE variants include: hash convergent
encryption (HCE) \cite{bellare13a}, which derives the tag from the plaintext
while still using the hash of the plaintext as the MLE key; random convergent
encryption (RCE) \cite{bellare13a}, which encrypts a plaintext with a fresh
random key to form a non-deterministic ciphertext, protects the random key by
the MLE key derived from the hash of the plaintext, and attaches a
deterministic tag derived from the plaintext for duplicate checks; and
convergent dispersal (CD) \cite{li15}, which extends CE to secret sharing by
using the cryptographic hash of a plaintext as the random seed of a secret
sharing algorithm.  Since all the above instantiations derive MLE keys and/or
tags from the plaintexts {\em only}, they are vulnerable to the offline
brute-force attack \cite{bellare13b} if the plaintext is {\em predictable}
(i.e., the number of all possible plaintexts is limited) , as an adversary can
exhaustively derive the MLE keys and tags from all possible plaintexts and
check if any plaintext is encrypted to a target ciphertext (in CE, HCE, and
CD) or mapped to a target tag (in RCE).  The brute-force attack has been
demonstrated to learn file information \cite{ce_attack}.

%Suppose an adversary learns  that the underlying message of a target
%ciphertext is drawn from a publicly available set. To recover the underlying
%message, the adversary tries each possible message from the public set,
%derives corresponding MLE key, and uses the derived key to decrypt the
%target ciphertext. If the decryption result equals the tried message, the
%adversary can deduce the underlying message.

% {\em HCE1} and {\em HCE2} \cite{bellare13a} derive tag from client side, and
% upload it along with ciphertext for deduplication. They offer better
% performance for the storage system, which can simply read the tag from
% uploads rather than computing it by hashing a possibly long ciphertext.
% {\em Random convergent encryption (RCE)} \cite{bellare13a} encrypts a
% message with a fresh random key, and protects the random key with the  MLE
% key of the message. RCE is more efficient, since it can combine both
% encryption and key generation into a single concerted pass over the message
% \cite{bellare13a}. On the other hand, RCE needs to attach a deterministic
% tag to the random ciphertext for checking duplicates. In addition to
% improving performance, {\em convergent dispersal} \cite{li15} replaces the
% random input of secret sharing by the cryptographic hash of message, so as
% to  augment CE with fault-tolerate storage.

% CE has been implemented in a wide variety of storage systems \cite{adya02, elephantdrive, mega, gnunet, freenet, cryptosphere, cox02, storer08, anderson10}.

% compute the tag $T = {\sf H}({\sf H}(M))$ as a double hash over plaintext message, and require to upload $T$ along with ciphertext for efficient deduplication. 
% A special note is RCE needs to places an appropriate tag along with ciphertext for deduplication, since its ciphertext is random. 
% Like HCE1 and HCE2, RCE , and 
% the message encryption and MLE key derivation of RCE can be combined into a single concerted pass over the possibly long message.

To protect against the offline brute-force attack, DupLESS \cite{bellare13b}
implements server-aided MLE by managing MLE keys in a standalone key server,
which ensures that each MLE key cannot be derived from a message offline.
DupLESS employs two mechanisms to achieve robust MLE key management: (i)
oblivious key generation, in which a client always obtains a deterministic MLE
key for a message from the key server without revealing the message content to
the key server, and (ii) rate limiting, which limits the key generation
requests from the client and prevents the online brute-force attack.  Other
studies extend server-aided MLE to address various aspects, such as reliable
key management \cite{duan14}, transparent pricing \cite{armknecht15},
peer-to-peer key management \cite{liu15}, and rekeying \cite{qin17}.  However,
server-aided MLE still builds on deterministic encryption.  To our
knowledge, existing MLE instantiations (based on either CE or server-aided
MLE) are all vulnerable to the inference attacks studied in this paper.

%In addition, existing MLE instantiations lack active protection against the
%size 
%vulnerabilities explored in this paper, since they generate deterministic
%ciphertexts or tags for deduplication. In addition, they lack active
%protection against the size and order leakages, which can be exploited to
%increase the severity of frequency analysis.

%SS \cite{bellare13b}, follow-up studies (see \cite{shin17} for a complete
%survey) address additional issues, including . Liu {\em et al.} \cite{liu15}
%propose to encrypt each message with a random key, and share the key among
%the clients that have the same message. This prevents brute-force attack due
%to the use of random keys, while mitigating security dependence on a global
%secret.

% All above MLE instantiations transform identical message to the same ciphertext or tag, and hence incur the frequency leakage. They also lack of active protection against the size and order leakages. 
% via password-based key exchange. This addresses , and also prevents brute-force attack. 
% Liu {\em et al.} \cite{liu15} propose to share encryption keys via a password-based key exchange protocol, so as to mitigate the dependence of the key manager. All above works apply deterministic encryption and are susceptible to frequency leakage. They also lack of active protection against the size and order leakages.

\section{Attacks against (encrypted) deduplication:} In addition to the
offline brute-force attack, previous studies consider various attacks against
deduplication storage, and such attacks generally apply to encrypted
deduplication as well.  For example, the side-channel attack
\cite{harnik10,halevi11} enables adversaries to exploit the deduplication
pattern to infer the content of uploaded files from target users or gain
unauthorized access in client-side deduplication; it is shown that the
side-channel attack (and other related attacks) was successfully launched
against Dropbox in 2010 \cite{mulazzani11}.  The duplicate-faking attack
\cite{bellare13a} compromises message integrity via inconsistent tags.
Ritzdorf {\em et al.} \cite{ritzdorf16} exploit the leakage of the chunk size
to infer the existence of files.  The locality-based attack \cite{li17}
exploits frequency analysis to infer ciphertext-plaintext pairs.  Our
work follows the line of work on inference attacks \cite{ritzdorf16,li17}, yet
provides a more in-depth study of inference attacks against encrypted
deduplication via various types of leakage.

%Our distribution-based attack inherently implies the prior attack \cite{li17}
%(see \S\ref{sec:distribution-attack-description}). We also propose the
%clustering-based attack that does not need the knowledge of fine-grained
%chunk orders.  
\section{Defense mechanisms:} 
Section~\ref{sec:countermeasure} discusses the countermeasures agasint the frequency, order and size leakage of encrypted deduplication. 
Additional defense mechanisms are designed to protect against other types of attacks.  
% Several countermeasures are designed to defend
% against the attacks on encrypted deduplication.  
As mentioned above,
server-aided MLE \cite{bellare13b} can defend against the offline brute-force
attack. Server-side deduplication \cite{li15,harnik10,armknecht17} and
proof-of-ownership \cite{xu13,pietro12,halevi11} can defend against the
side-channel attack.  Server-side tag generation \cite{douceur02,bellare13b}
and guarded decryption \cite{bellare13a} can defend against the
duplicate-checking attack.

% MinHash encryption \cite{qin17} disturbs the
% frequency ranking of ciphertexts and is shown to defend against the frequency
% analysis based on the locality-based attack via trace analysis.  Several
% extended MLE instantiations build on strong cryptographic primitives to defend
% against the inference attacks, such as randomized encryption that supports
% equality testing \cite{abadi13}, hybrid encryption \cite{stanek14}, and
% interactions with fully homomorphic encryption \cite{bellare15}, yet how they
% are implemented and deployed in practice remains unexplored.

\section{Inference attacks:}  Several inference attacks have been proposed
against encrypted databases
\cite{grubbs17,bindschaedler17,kellaris16,durak16,naveed15,lacharite18} and 
keyword search \cite{zhang16b,grubbs16,pouliot16,cash15,islam12}.  They all
exploit the deterministic encryption nature to identify different types of
leakage.  Our work differs from them by specifically focusing on frequency analysis against encrypted
deduplication.

%construct inference attacks against encrypted databases. Naveed {\em et al.}
%\cite{naveed15} propose attacks to recover the plaintext records of {\em
%CryptDB} \cite{popa11a}. Kellaris {\em et al.} \cite{kellaris16} and
%Lacharite {\em et al.} \cite{lacharite18} analyze the volumes of the data
%returned by range queries, and present generic reconstruction attacks on
%database entries. Grubbs {\em et al.} \cite{grubbs16}, Bindschaedler {\em
%et al.} \cite{bindschaedler17}, and Durak {\em et al.} \cite{durak16}
%show how to recover the plaintexts from the database column encrypted by
%order-revealing encryption. 
%
%target keyword search. Islam {\em et al.} \cite{islam12} exploit the leakage of access pattern, and recover the plaintext keywords associated with files. Cash {\em et al.} \cite{cash15} and Pouliot \cite{pouliot16} examine the security of searchable encryption under different leakage profiles. Zhang {\em et al.} \cite{zhang16b} propose file-injection attacks to recover searchable keywords. Grubbs \cite{grubbs16} build attacks against {\em Mylar} \cite{popa14} that is a practical system with keyword search enabled.    This paper differs from the above works \cite{grubbs17,bindschaedler17,kellaris16,durak16,naveed15,lacharite18,zhang16b,grubbs16,pouliot16,cash15,islam12} by launching inference attacks against encrypted deduplication.

%Other studies \cite{zhang16b,grubbs16,pouliot16,cash15,islam12} target keyword search. Islam {\em et al.} \cite{islam12} exploit the leakage of access pattern, and recover the plaintext keywords associated with files. Cash {\em et al.} \cite{cash15} and Pouliot \cite{pouliot16} examine the security of searchable encryption under different leakage profiles. Zhang {\em et al.} \cite{zhang16b} propose file-injection attacks to recover searchable keywords. Grubbs \cite{grubbs16} build attacks against {\em Mylar} \cite{popa14} that is a practical system with keyword search enabled.    This paper differs from the above works \cite{grubbs17,bindschaedler17,kellaris16,durak16,naveed15,lacharite18,zhang16b,grubbs16,pouliot16,cash15,islam12} by launching inference attacks against encrypted deduplication.

%Client-side deduplication leaks the side channel information that if
%particular messages have already been stored. Harnik {\em et al.}
%\cite{harnik10} and Halevi {\em et al.} \cite{halevi11} show how to exploit
%the side channel leakage for different purposes, including creating covert
%channels between clients and gaining access to unauthorized information.

%Some studies \cite{stanek14,abadi13,bellare15} aim to achieve stronger security than the more practical schemes focused above. Stanek {\em et al.} \cite{stanek14} design a hybrid encryption scheme where unpopular messages are protected by semantically secure encryption for high security guarantee, while popular messages are protected by CE to enable deduplication. On the other hand, the scheme \cite{stanek14} builds on public-key primitive which is inefficient for encrypting large-size messages. Abadi {\em et al.} \cite{abadi13} construct two schemes for the messages whose distributions are publicly available. Their first scheme generates  random tags and ciphertexts to prevent frequency leakage, yet incurring expensive {\em equality test} for checking duplicates. Their second scheme produces deterministic ciphertexts, and exposes the frequencies of corresponding plaintexts. Interactive MLE \cite{bellare15} introduces interactions into encrypted deduplication, and strengthens the security of both correlated and parameter-dependent messages, yet it is impractical for the use of fully homomorphic encryption. On the contrary to these theoretical contributions \cite{stanek14, abadi13, bellare15}, this paper focuses on the applied aspect, and investigates the security vulnerabilities in practical deduplication.

% {\em Duplicate-faking attack} \cite{bellare13a} compromises the integrity of data by inconsistent tags. Specifically, an adversary can attach a maliciously-generated ciphertext to a faking tag $T$, so that the following legitimate messages that have the same tag of $T$ will be removed by deduplication. It can be addressed by server-side tag generation \cite{douceur02, bellare13b} or guarded decryption \cite{bellare13a}.

% or introducing a random threshold to control client-side or server-side deduplication \cite{,harnik10}.

% Our second attack augments the prior work \cite{li17} with distribution-based ranking and achieves high inference rate and accuracy. We   
%Some studies \cite{bosman16,gruss15,xiao13} investigate the side channels of memory deduplication, and this paper differs from them in considering deduplication in outsourced storage (e.g., cloud storage).

% \paragraph{Property-revealing encryption:}
% Encrypted deduplication leaks the underlying equality of plaintext chunks for detecting duplicates. A generalized {\em property-revealing encryption} \cite{bindschaedler17} has been studied for securing database storage \cite{curtmola06,bellare07,bellare09,boldyreva09,boldyreva11,popa11}. This paper differs from these works as it targets unstructured workloads.

% both theory \cite{curtmola06,bellare07,bellare09,boldyreva09,boldyreva11} and practice \cite{popa11}.

% illustrate the weakness of searchable encryption.

% present reconstruction attacks by analyzing ;

% \cite{grubbs17,bindschaedler17,zhang16b,grubbs16,kellaris16,pouliot16,durak16,naveed15,cash15,islam12,lacharite18}  Regarding databases,    Regarding keyword search, ; further

% under different leakage settings;

% classical frequency analysis against cryptdb.

% -specific cryptographic primitives of deterministic encryption.

% applications.

% structured relational data or

% based on frequency analysis.

% % Frequency analysis has been applied in prior works \cite{grubbs17,bindschaedler17,zhang16b,grubbs16,kellaris16,pouliot16,durak16,naveed15,cash15,islam12,lacharite18} to construct inference attacks. Some attacks target , by classical frequency analysis \cite{naveed15}, exploring correlations or orderings of table columns, .

% while these approaches either target structured relational data \cite{grubbs17,bindschaedler17,kellaris16,durak16,naveed15,lacharite18} or aim to recover keywords of files \cite{zhang16b,grubbs16,pouliot16,cash15,islam12}, and cannot be applied to infer a huge number of chunks.  
% % Traditional MLE (e.g., CE) builds on a {\em public} function (e.g., the hash function) to derive encryption keys, and it is susceptible to brute-force attack \cite{bellare13a} that can be used to . The weakness can be addressed by server-aided MLE \cite{bellare13b}.  
%  % posted by the side-channel leakage in client-side and cross-user deduplication. 
%  % This paper differs from these attacks in considering an adversary from the server side.

### 2018-12-13 paper/background.tex
ING | background done with all cite insetered

\chapter{预备知识}

\label{sec:background}
在本章中，将介绍普通和加密重复数据删除方法的基础知识，以及加密重复数据删除仍然容易受到攻击的原因。

\section{重复数据删除}

\begin{figure}[!htb]
    \small
    \centering
    \includegraphics[width=14cm]{DedupSystemView.eps}
    \caption{重复数据删除的工作流程概览} 
    \label{fig:重复数据删除的工作流程概览}
\end{figure}

本文专注于基于块的重复数据删除，它以称为数据块的小型数据单元为粒度运行。图\ref{fig:重复数据删除的工作流程概览}总结了重复数据删除工作流程。

具体地，重复数据删除系统首先通过文件切块过程将客户端的文件（例如，备份文件）分割成逻辑数据块，根据每一个逻辑数据块的内容使用HASH算法（散列算法）计算得到其对应的唯一标签（又成为指纹）。如果两个数据块具有相同的标签，那么认为两个数据块相同（不同逻辑数据块计算得到相同的标志的概率忽略不计\citing{black2006compare}），即数据块内容和其标志完全一致；若两个逻辑数据块标签不一致，显然两逻辑数据块不同。重复数据删除系统的存储系统仅存储相同逻辑数据块的副本（称为物理数据块），并且每个相同的逻辑数据块通过一个较小空间开销的索引引用相同的物理数据块。

基于块的重复数据删除比基于文件的重复数据删除更精细，因此通常具有更高的存储效率（节省更多的存储空间）。基于块的重复数据删除有两种基本的数据块分块方法：固定大小的数据分块方法和可变大小的数据分块方法。固定大小的数据分块方法将数据分割为大小相同的逻辑数据块，而可变大小的数据分块方法（也称为内容定义的数据块分块方法）通常以内容相关的方式指定数据块的边界（例如，通过Rabin指纹识别\citing{rabin1981fingerprinting}）将文件数据分区为可变大小的数据块。固定大小的分块方法简单而快速，而可变大小的分块方法可以在内容发生变换时保持存储效率，因为即使文件添加或删除了某些内容，大多数数据块仍保持不变。可变大小的分块通常用在备份系统中（例如，\citing{zhu2008avoiding,lillibridge2009sparse}），但固定大小的分块显然对某些工作负载更加有效（例如，VM备份数据集\citing{jin2009effectiveness}）。本文的工作同时涉及固定大小和可变大小的分块方法产生的数据块。

加密的重复数据删除解决了外包环境（例如，云存储）中的数据块机密性，同时保持了重复数据删除的有效性。出于安全考虑，用户希望在将自己的数据外包之前对其数据进行加密，以确保个人数据的隐私性。传统的对称加密要求多个客户端通过其（不同的）密钥加密其文件数据，即使相同的明文数据块也会被加密为不同的密文数据块，服务器无法感知到这些密文数据块所对应的的原始明文数据块内容是否相同。消息锁定加密（MLE）\citing{bellare2013message}给加密重复数据删除提供了新的处理方法。最基本的MLE实例化是基于每个明文的内容（例如，基于块的重复数据删除中的逻辑数据块）导出其对称密钥（称为MLE密钥），并使用MLE密钥加密明文以形成对应的密文（例如，加密的逻辑数据块）。因此，MLE可以确保将相同的明文加密为相同的密文。最后，存储系统从每个密文中导出其对应的标签并执行重复数据删除。

\section{重复数据删除中存在的威胁}

\subsection{MLE加密具有确定性}

MLE可以实现为不同的实例化（参见章节：\ref{sec:RelatedWork}）。其中最受欢迎的是融合加密（CE）\citing{douceur2002reclaiming}，它已经在各种存储系统中实现\citing{adya2002farsite,ElephantDrive,MEGA,GNUP2P,Freenet,Cryptosphere,cox2002pastiche,storer2008secure,anderson2010fast}。 CE的主要思想是根据每个明文数据块的内容通过HASH函数（散列函数）导出其对应的MLE密钥。这种方法可以确保具有相同内容的逻辑数据块加密得到的密文数据块始终一致，即可使用密文数据块的标签进行重复数据删除。但也存在部分MLE实例\citing{bellare2013message}允许将相同的明文加密成不同的密文。当然，他们确保用于重复数据删除的标签仍然来自明文，因此他们依然可以通过检查标签的相同性来执行重复数据删除。

现有的MLE实例都建立在确定性加密这一概念的基础之上，确定性加密可以确保密文（或标签）从明文确定性地导出，与传统的对称加密相比，可以保留重复数据删除的有效性。虽然确定性加密提供了机密性保证，但是本文认为攻击者可以利用这种确定性来推断给定密文的原始明文。

\subsection{理论上加密重复数据删除存在信息泄漏}

实际的加密重复数据删除系统会暴露一些关于原始块的信息，称为泄漏。最基本的泄漏是数据块的频率，这一点已在先前的工作中得到承认\citing{abadi2013message,bellare2015interactive,ritzdorf2016information,li2017information}。具体地说，MLE会将相同的明文数据块加密成相同的密文数据块，这一过程泄漏了每个原始明文数据块出现在输入数据中的次数。本文认为频率泄漏难以避免，因为这会破坏明文和密文数据块的一对一映射关系，进而降低重复数据删除系统的性能\citing{abadi2013message}或存储效率\citing{li2017information}。

已有的研究工作已经探索了实际加密重复数据删除系统存在的的其他类型的泄漏\citing{ritzdorf2016information,li2017information}。首先，一些重复数据删除系统\citing{zhu2008avoiding,xia2011silo}   为了实现更高的性能，需要按照数据块在原始文件中出现的顺序来操作数据块；这暴露了铭文数据块的逻辑顺序，基于该逻辑顺序可以识别输入文件中每个数据块的位置。其次，一些工作\citing{douceur2002reclaiming,wilcox2008tahoe,keelveedhi2013dupless}为了降低存储开销，不会填充任何冗余的密文数据块，这暴露了原始明文数据块的数量信息，因为密文数据块应该与原始明文数据块具有相同的数量。

在已有工作\citing{ritzdorf2016information,li2017information} 中，通过构建攻击原语来推断原始明文数据块\citing{li2017information} 或根据特定文件的存在\citing{ritzdorf2016information}来攻击加密重复数据删除方案。但现有的其他关于加密重复数据删除的工作仍未探索过如何基于推断得到的信息发起实际攻击。本文对加密重复数据删除的泄漏问题进行了全面研究，以求回答以下两个问题：
%TODO: primitives如何翻译
\begin{enumerate}
    \item 如何在各种泄漏中通过启用基元来推断原始内容？
    \item 以推断内容为基础的实际攻击的具体含义是什么？
\end{enumerate}

\subsection{观察得到的实际系统中的泄漏}

下面将讨论在最先进的加密重复数据删除方案/系统中观察到的各种泄漏。

\begin{itemize}
    \item \textbf{频率泄漏}

    加密的重复数据删除方案应用了确定性加密（例如，MLE），其中相同的明文数据块将被加密成相同的密文数据块。 这泄漏了每个数据块的频率信息（即原始数据块出现在输入数据中的次数）。频率泄漏是MLE难以解决的问题，因为它很难被预防（否则，将导致重复数据删除性能显着下降\citing{abadi2013message}或存储空间开销大幅提高\citing{li2017information}）。
    \item \textbf{数据块长度信息泄漏}

    为了减轻存储开销，建议从业者在没有填充方案\citing{ritzdorf2016information}的情况下实现块加密。 例如，Farsite\citing{douceur2002reclaiming}，Tahoe-LAFS\citing{wilcox2008tahoe}和DupLESS\citing{keelveedhi2013dupless}在计数器模式下使用AES加密，但它们不会使用任何其他数据填充密文数据块。因为密文数据块应该与原始明文数据块具有相同的大小，这会泄漏原始数据块大小信息\citing{ritzdorf2016information}。

    对于可变大小的数据块，这种泄漏更加严重，由于数据块边界通过匹配特定内容的方法来识别（例如，通过Rabin指纹识别\citing{rabin1981fingerprinting}）。具有不同大小的两个密文数据块进一步暴露了它们来自于不同明文数据块的信息。

    \item \textbf{数据块逻辑顺序泄漏}

    在部署加密重复数据删除时无意中发生泄漏，使得数据块逻辑顺序被外部所获的。
\end{itemize}

\section{频率分析攻击}

频率分析已在一些已有的工作\citing{grubbs2016breaking,bindschaedler2018tao,zhang2016all,grubbs2016breaking,kellaris2016generic,pouliot2016shadow,durak2016else,naveed2015inference,cash2015leakage,islam2012access,lacharite2018improved}中用来构建攻击。例如针对数据库中的结构化关系数据的攻击，通过经典频率分析\citing{naveed2015inference}，探索表列的相关性或排序。

本文旨在应用频率分析来探索加密重复数据删除的漏洞。 我们的重点不是解决如何获得用于推理攻击的相关明文。在统频率分析模式下，攻击者能够访问明文逻辑数据块集合M和密文逻辑数据块集合$C$（$M$和$C$包含重复的明文和密文数据块）。攻击者根据出现频率分别对$M$和$C$中的数据块进行排序，然后将$C$中的密文数据块映射为$M$中与其具有相同排名的明文数据块。

\section{本章小结}

本章介绍了普通与加密重复数据删除，现有加密重复数据删除中存在的信息泄漏，以及频率分析攻击的典型应用和其在加密重复数据删除中的基本运用方式。

### 2018-12-13 paper/threatModel.tex
ING | background done with all cite insetered

\chapter{威胁模型分析}
\label{sec:ThreatModel}

In this section, we formulate the threat model for our proposed frequency
analysis attacks against encrypted deduplication.

\section{Definitions}
\label{sec:ThreatModel-Definitions}

We first provide the definitions for our threat model. We model a plain file
as an ordered list of $n$ {\em logical plaintexts} (i.e., logical chunks
before deduplication), denoted by $\mathbf{M} = \langle \hat{M}^{(1)},
\hat{M}^{(2)}, \ldots, \hat{M}^{(n)}\rangle$.  Each logical plaintext
$\hat{M}^{(i)}$ (where $1\le i\le n$) is encrypted via MLE into the
corresponding ciphertext $\hat{C}^{(i)}$, and all encrypted results of
$\mathbf{M}$ form a stream of $n$ {\em logical ciphertexts} $\mathbf{C} =
\langle \hat{C}^{(1)}, \hat{C}^{(2)}, \ldots, \hat{C}^{(n)} \rangle$.  Note
that the logical ciphertexts in $\mathbf{C}$ are also ordered to reflect the
deduplication processing sequence of an encrypted deduplication storage
system.

Identical logical plaintexts and ciphertexts may appear at different positions
of $\mathbf{M}$ and $\mathbf{C}$, respectively.  We denote a unique plaintext
as $M$ (uniquely identified by its tag), which is encrypted via MLE to the
corresponding unique ciphertext $C$.  Each $M$ (resp. $C$) corresponds to one
or multiple identical copies of $\hat{M}^{(i)}$ (resp. $\hat{C}^{(i)}$).

% of $\mathbf{M}$ is
% independently encrypted into corresponding ciphertext $C$ via MLE, and all encrypted results

% A unique plaintext (or plaintext for short) $M$ has one or more copies in $\mathbf{M}$  
% Identical plaintexts may have multiple copies in $\mathbf{M}$, and we introduce unique plaintext  
% We define a unique plaintext as the plaintext that has unique content among other plaintexts of $\mathbf{M}$    
% Let $M$ and $C$ be a
% plaintext and its corresponding ciphertext, respectively; both of them are in
% units of chunks defined by deduplication.  We model a plain file before
% deduplication as an {\em ordered} list of $n$ plaintexts, denoted by
% $\mathbf{M} = \langle M^{(1)},  M^{(2)}, \ldots, M^{(n)}\rangle$.  Identical
% plaintexts may appear at different positions of $\mathbf{M}$, say $M^{(i)} =
% M^{(j)}$ for some $1\le i \neq j\le n$.   
% % Also, each plaintext can have the
% same or different chunk sizes due to fixed-size or variable-size chunking,
% respectively, and let $|M|$ denote the size of a plaintext $M$.  
% Let $M$ and $C$ denote a
% plaintext (i.e., a logical chunk before encryption) and its corresponding
% ciphertext (i.e., a logical chunk after encryption).  We model a plain file

\section{Adversarial Goals and Assumptions}
\label{sec:ThreatModel-Assumptions}

We consider an adversary that aims to infer a set of ciphertext-plaintext
pairs, denoted by \{$(C, M)$\}, with two specific goals:
\begin{itemize}[leftmargin=*]
\item
{\bf High inference rate:} A large fraction of correct ciphertext-plaintext pairs
are inferred, among all correct ciphertext-plaintext pairs (i.e., high recall or
low false negative rates in statistical terms).
\item
{\bf High inference precision:} A large fraction of ciphertext-plaintext pairs
are correct, among all inferred ciphertext-plaintext pairs (i.e., high precision
or low false positive rates in statistical terms).
\end{itemize}

We assume that the adversary is {\em honest-but-curious}, such that it can
passively monitor the stream of ciphertexts $\mathbf{C}$ being written to the
storage system and exploit different types of leakage information from
$\mathbf{C}$ (see Section~\ref{sec:leakage}).  Given the available leakage
information, the adversary aims to infer the original plaintext of each
ciphertext in $\mathbf{C}$ via a {\em ciphertext-only} attack.  It is possible
that the adversary knows a limited subset of ciphertext-plaintext pairs to
launch a known-plaintext attack, which further strengthens attack severity
\cite{li17}.  We do not consider the known-plaintext attack in this paper.

%We treat $\mathbf{C}$ as the {\em view} by the
%adversary and model different properties of the view

We assume that the adversary does not have access to any {\em metadata} that
contains the information about how chunks are operated and stored, as we do
not apply deduplication to the metadata and hence it can be protected by
traditional symmetric encryption.  Also, we assume that the adversary does not
have {\em active} capabilities, which can be independently prevented by
existing approaches. One example is that a malicious client may claim the
ownership of unauthorized files in client-side deduplication
\cite{harnik10,halevi11,mulazzani11}; it can be addressed by
proof-of-ownership \cite{halevi11,xu13,pietro12} or server-side deduplication
\cite{harnik10,li15}.  Another example is that a malicious storage system may
modify stored data; it can be detected by remote integrity checking
\cite{juels07,ateniese07}.

% In addition, $\mathcal{A}$ does not aim to infer if
% particular files have been stored \cite{harnik10, ritzdorf16}. Instead, we
% study the security implication based on the inferred contents over different
% types of files (see \S\ref{sec:case}).. 
% Intuitively, we want to guarantee that what $\mathcal{A}$ can learn is some
% well defined leakage $\mathcal{L}$, which includes the frequency, logical
% order and/or chunk size (\S\ref{sec:leakage}). 
% Note that $\mathcal{A}$ is specific to a {\em passive} adversary with content
% inference in mind. We do not assume $\mathcal{A}$ has {\em active}
% capabilities,

\section{Leakage Channels}
\label{sec:ThreatModel-Leakage}

We consider three types of leakage channels in encrypted deduplication storage
that enable an adversary to infer information:
\begin{itemize}[leftmargin=*]
\item
{\bf Frequency:}  Due to the deterministic nature of encrypted deduplication,
the frequency of each ciphertext in $\mathbf{C}$ before deduplication (i.e., 
the number of duplicate copies) can be mapped to that of its corresponding
plaintext in $\mathbf{M}$. 
% the size of each ciphertext in
% $\mathbf{C}$ is approximately equal to that of its corresponding plaintext in
% $\mathbf{M}$. In other words, the exact number of blocks (e.g., that are of size 16 bytes) in ciphertexts   
% the exact number of blocks in the plaintext equals the number of blocks in the ciphertext
% {\bf PC: if block cipher is used, it's not necessary that the
% plaintext has the same size as its ciphertext}.
%(e.g., \cite{douceur02, wilcox-ohearn08, bellare13b}) do not pad ciphertexts
%with additional data to avoid storage overhead, 
\item
{\bf Order:}  Some storage systems (e.g., \cite{xia11,lillibridge09,zhu08})
apply deduplication to the chunks in the same order as they appear in the
original file.  Thus, the order of ciphertexts in $\mathbf{C}$ can be mapped
to that of plaintexts in $\mathbf{M}$. 
\item
{\bf Size:}  Variable-size chunking (see Section~\ref{sec:background}) leads
to different chunk sizes of the ciphertexts.  If such ciphertexts are not
padded (to avoid storage overhead \cite{ritzdorf16}), the size of a ciphertext
in $\mathbf{C}$ can be mapped to that of its corresponding plaintext in
$\mathbf{M}$.    
\end{itemize}

%We also consider other leakage channels that are specific to real-world
%deduplication storage systems. First, {\em order leakage} exposes the logical
%order of each plaintext, and it is available for the systems
%\cite{xia11,lillibridge09,zhu08} that aim for high performance and operate
%the deduplication of chunks in the same order as these chunks appear in
%original files; this implies that the logical order of ciphertext in
%$\mathbf{C}$ exactly reflects that of its corresponding plaintext. Second,
%{\em size leakage} exposes the chunk size of each plaintext, since some
%systems \cite{douceur02, wilcox-ohearn08, bellare13b} avoid storage
%overhead and do not pad ciphertexts with any additional data; this
%implies that the size of ciphertext in $\mathbf{C}$ exactly equals that
%of its corresponding plaintext.

In addition, the adversary has access to some {\em auxiliary information} that
presents the ground truth about the data characteristics correlated with
$\mathbf{M}$. Note that the availability of auxiliary information is necessary
for any inference attack \cite{kumar07,li17,grubbs17,zhang16b,kellaris16,ritzdorf16,naveed15,cash15,islam12}.
In this work, we consider the auxiliary information as an ordered list of
previously known plaintexts (e.g., old user backups or VM disk images),
denoted by $\mathbf{A}$.  Clearly, the attack severity depends on the
correlation between $\mathbf{A}$ (i.e., the previously known plaintexts) and
$\mathbf{M}$ (i.e., the plaintexts that are to be inferred).  Our focus is not
to address how an adversary can obtain auxiliary information, possibly due to
careless data release \cite{careless-release}, stolen storage devices
\cite{stolen-device}, and cloud leakage \cite{cloud-leakage}. Instead, given
such information, we investigate how the available auxiliary information,
combined with the leakage channels, bring information leakage from encrypted
deduplication.

We focus on frequency analysis \cite{alkadit92} as the attack methodology.
Classical frequency analysis sorts the unique ciphertexts in $\mathbf{C}$ and
the unique plaintexts in $\mathbf{A}$ by {\em frequency} (i.e., the number of
identical copies corresponding to each unique ciphertext or unique plaintext). 
It then relates each unique ciphertext in $\mathbf{C}$ with the unique
plaintext in $\mathbf{A}$ that has the same frequency rank. In the following
sections, we design sophisticated frequency analysis attacks against encrypted
deduplication.

% Frequency analysis is a cryptanalysis primitive to relate the ciphertexts in $\mathbf{C}$  with the plaintexts in $\mathbf{M}$. Specifically, it sorts ciphertexts and plaintexts by their frequencies in $\mathbf{C}$ and $\mathbf{A}$, respectively, and maps each ciphertext to the plaintext that has the same frequency rank. Building on the classical version of frequency analysis, we show how to exploit leakage channels to strengthen its severity against encrypted deduplication.

% infer ciphertext-plaintext pairs from $\mathbf{C}$ and $\mathbf{A}$. 
 % Specifically, the adversary

% It performs well, only when the frequency of ciphertext is correlated with that of the corresponding plaintext. 
% The more correlated to $\mathbf{M}$,

% Our focus is not to address its availability, which is due to careless data release \cite{careless-release}, stolen storage devices \cite{stolen-device}, and cloud leakage \cite{cloud-leakage}. Instead, we show how an adversary can launch inference attacks based on the available auxiliary information $\mathbf{A}$.

% Our focus is not to address how to obtain accurate auxiliary information, which we pose as future work; instead, given the available auxiliary information, we study how an adversary can design a severe attack based on frequency analysis and how we can defend against the attack
% Some available auxiliary information has been demonstrated to be necessary for inference attacks  and we consider the auxiliary information $\mathbf{M}$ as a complete user backup, file system snapshot or VM disk image in plaintext. The rationale of its availability is that the adversary can obtain the original data from  We emphasize that the auxiliary information $\mathbf{M}$ does not need to be identical with the original file of $\mathbf{C}$. In other words, $\mathbf{M}$ may not have the
% same number of chunks with $\mathbf{C}$, or its $i$-th chunk $M^{\langle i \rangle}$ may not be the plaintext of $C^{\langle i \rangle}$ or even not mapped into $\mathbf{C}$. 
% {\bf PC: give the background on frequency analysis.}

% We assume that the adversary can take advantage of some   for attacks. The auxiliary information , and it has been demonstrated for necessity in inference attacks . In this work,

% In addition, the adversary can exploit other deduplication-specific leakage channels.

% effectiveness of inference attacks. First, we consider {\em size leakage}, meaning that the adversary can derive the size of a plaintext directly based on the corresponding ciphertext: ${\sf s}(C) = |M|$, where $C$ is the encryption of $M$.

% deduplication-specific leakage channels.

% We target inference attacks against {\em backup workloads}, which refer to the copies of primary data (e.g., application states, file systems, and virtual disk images) over time. The recent technology trend \cite{douglis17} suggests to create full backups (that store the complete data of the primary source) over traditional incremental backups (that only store the changes of data since the last full backup), so as to mitigate the overhead in restoring earlier (full) backups. Thus, we focus on inferring information from different versions of full backups (or backups for short) that are created based on the same primary data source at different times.

% They can be created as either weekly full backups (that store the complete data of the primary source) or daily incremental backups (that only store the changes of data since the prior full backup). Informed by the technology trend , we focus on full backups (or {\em backups} for short). Specifically, we aim to infer information from different versions of backups that are created based on the same primary data source yet at different times.

% To launch attacks, we assume that $\mathcal{A}$ is an ``{\em honest-but-curious}'' adversary that can compromise the server hosting deduplication service, while it cannot establish a long-term presence for attack. Intuitively, we want to guarantee that what $\mathcal{A}$ can learn is some well defined leakage $\mathcal{L}$, which includes the frequency, logical order and/or chunk size (\S\ref{sec:leakage}). Formally, we define these leakage channels based on a target victim file $\mathbf{M}_{\rm t}$:

% \begin{itemize}[leftmargin=*]
% 	\item  {\bf Frequency leakage}: $\mathcal{L}_{\rm freq} = \{(C, {\sf freq}(M)): M \in \mathbf{M}_{\rm t}$ and $C = {\sf E}_{K_M}(M) \}$ is a set of chunk-frequency pairs, where $C$ is the encryption of some plaintext chunk $M$ in $\mathbf{M}_{\rm t}$, and each pair $(C, {\sf freq}(M))$ leaks the corresponding frequency of $M$.

% 	\item  {\bf Order leakage}: $\mathcal{L}_{\rm order} = \{(C, {\sf ord}(M)): M\in\mathbf{M}_{\rm t}$ and $C = {\sf E}_{K_M}(M) \}$ associates each ciphertext chunk $C$ with a set ${\sf ord}(M)$ of logical orders, at which the copies of its original chunk $M$ appear in $\mathbf{M}_{\rm t}$. Note that order leakage {\em implies} frequency leakage, since the logical orders of each chunk copy inherently includes the number of times the corresponding chunk appears.

% 	\item  {\bf Size leakage}: $\mathcal{L}_{\rm size} = \{(C, {\sf size}(M)): M \in \mathbf{M}_{\rm t}$ and $C = {\sf E}_{K_M}(M) \}$ is a set of chunk-size pairs, where each pair leaks the size of the original chunk of $C$.
% \end{itemize}

% In addition, $\mathcal{A}$ can take advantage of the {\em auxiliary information} $\mathbf{M}_{\rm a}$ that presents the ground truth about the frequency, size and order information about plaintext chunks. Some available auxiliary information is necessary for inference attacks , and we focus on validating our attacks with the auxiliary information obtained from different types of storage workloads (see \S\ref{sec:dataset}).

% Acquiring the above capabilities, $\mathcal{A}$'s primary goal is to recover the plaintext chunks in the target file $\mathbf{M}_{\rm t}$. More formally, given the leakage $\mathcal{L}$ (that can be some combination of $\mathcal{L}_{\rm freq}$, $\mathcal{L}_{\rm order}$ and $\mathcal{L}_{\rm size}$) and the auxiliary information $\mathbf{M}_{\rm a}$, $\mathcal{A}$ outputs a collection of ciphertext-plaintext chunk pairs $\mathcal{R} = \{ (C, M) \}$: $\mathcal{A}(\mathcal{L}, \mathbf{M}_{\rm a}) \rightarrow \mathcal{R}.$ Each output pair $(C, M)$ indicates $\mathcal{A}$'s guess that relates a ciphertext chunk $C$ with a plaintext chunk $M$.

% identify the ciphertext-plaintext chunk pairs about $\mathbf{M}_{\rm tar}$. More formally, given the leakage $\mathcal{L}$ (that can be some combinations of $\mathcal{L}_{\rm freq}$, $\mathcal{L}_{\rm order}$ and $\mathcal{L}_{\rm size}$), and auxiliary information $\mathbf{M}_{\rm aux}$, $\mathcal{A}$ outputs a collection of ciphertext-plaintext chunk pairs $\mathcal{R} = \{ (C, M) \}$: $\mathcal{A}(\mathcal{L}, \mathbf{M}_{\rm aux}) \rightarrow \mathcal{R}.$ Each pair $(C, M)$ indicates $\mathcal{A}$'s guess that relates a ciphertext chunk $C$ with a plaintext chunk $M$.

% a malicious server may corrupt stored chunks, yet it can be detected by integrity checking mechanisms \cite{juels07,ateniese07};

% and it is a correct inference by $\mathcal{A}$ if $C$ is the actual encryption of $M$, i.e., $(M, C) \in \mathcal{E}$.

% We measure the success of attacks in several ways. The {\em raw inference rate} is the percentage of ciphertext chunks (including duplicates) that are inferred correctly over the total number of ciphertext chunks in the target information. For example, if the adversary correctly infers a ciphertext-plaintext chunk pair $(C, M)$ and the ciphertext chunk $C$ accounts for a fraction of 10\% in the target information, then the raw inference rate will be at least 10\%.

% We assume the adversary can eavesdrop the deduplication processing (e.g., comparison operation of fingerprints) of all ciphertext chunks in a victim file (called {\em target information}); on the other hand, it cannot access related metadata that can be protected by traditional encryption \cite{li17}. 
% the same and different private sources, as well as some public source .

% Note that $\mathcal{A}$ is specific to a passive adversary with content recovery in mind. We do not abstract $\mathcal{A}$ with active capabilities, since these threats can be protected by existing approaches. For example, a malicious server may corrupt stored chunks, yet it can be detected by integrity checking mechanisms \cite{juels07,ateniese07}; a malicious client may cheat owning a particular file \cite{harnik10,halevi11,mulazzani11}, yet it can be addressed by proof of ownership \cite{halevi11} or enforcing server-side deduplication \cite{li15}.

### 2018-12-15 paper/DataSetandSystemReport.tex
ING | add threat model and begining of dis-attack

\chapter{数据集与实际系统调研}
\section{数据集}
\subsection{FSL数据集}
\subsection{VM数据集}
\subsection{MS数据集}

\section{实际系统}
\subsection{SDFS}

\subsection{Destor}

### 2018-12-15 paper/threatModel.tex
ING | add threat model and begining of dis-attack

@@
-\chapter{威胁模型分析}
+\chapter{威胁模型}
 \label{sec:ThreatModel}
+本章为针对加密重复数据删除的频率分析攻击制定了威胁模型。
 
-In this section, we formulate the threat model for our proposed frequency
-analysis attacks against encrypted deduplication.
-
-\section{Definitions}
+\section{威胁模型定义}
 \label{sec:ThreatModel-Definitions}
 
-We first provide the definitions for our threat model. We model a plain file
-as an ordered list of $n$ {\em logical plaintexts} (i.e., logical chunks
-before deduplication), denoted by $\mathbf{M} = \langle \hat{M}^{(1)},
-\hat{M}^{(2)}, \ldots, \hat{M}^{(n)}\rangle$.  Each logical plaintext
-$\hat{M}^{(i)}$ (where $1\le i\le n$) is encrypted via MLE into the
-corresponding ciphertext $\hat{C}^{(i)}$, and all encrypted results of
-$\mathbf{M}$ form a stream of $n$ {\em logical ciphertexts} $\mathbf{C} =
-\langle \hat{C}^{(1)}, \hat{C}^{(2)}, \ldots, \hat{C}^{(n)} \rangle$.  Note
-that the logical ciphertexts in $\mathbf{C}$ are also ordered to reflect the
-deduplication processing sequence of an encrypted deduplication storage
-system.
+本文分别使用$M$和$C$来表示明文数据块（即加密前的逻辑数据块）及其对应的密文数据块（即加密后的逻辑数据块）；$|M|$和$|C|$来表示明文数据块（即加密前的逻辑数据块）的大小及其对应的密文数据块（即加密后的逻辑数据块）的大小。
 
-Identical logical plaintexts and ciphertexts may appear at different positions
-of $\mathbf{M}$ and $\mathbf{C}$, respectively.  We denote a unique plaintext
-as $M$ (uniquely identified by its tag), which is encrypted via MLE to the
-corresponding unique ciphertext $C$.  Each $M$ (resp. $C$) corresponds to one
-or multiple identical copies of $\hat{M}^{(i)}$ (resp. $\hat{C}^{(i)}$).
+首先将普通文件建模为由$n$个逻辑明文数据块构成的有序列表（即重复数据删除之前的逻辑块），该列表记为$\mathbf{M} = \langle \hat{M}^{(1)}, \hat{M}^{(2)}, \ldots, \hat{M}^{(n)}\rangle$。 每个逻辑明文数据块$\hat{M}^{(i)}$（其中$1\le i\le n$）通过MLE加密得到相应的密文数据块$\hat{C}^{(i)}$。由$\mathbf{M}$的所有加密结果形成由$n$个逻辑密文数据块组成的有序列表记为$\mathbf{C} = \langle \hat{C}^{(1)}, \hat{C}^{(2)}, \ldots, \hat{C}^{(n)} \rangle$。在$\mathbf{C}$中的逻辑密文数据块也会被排序以反映加密重复数据删除存储系统中重复数据删除处理过程的顺序。
 
-% of $\mathbf{M}$ is
-% independently encrypted into corresponding ciphertext $C$ via MLE, and all encrypted results
+相同的逻辑明文和密文可能分别出现在$\mathbf{M}$和$\mathbf{C}$中的不同位置。 本文将一个唯一的明文数据块表示为$M$（通过其指纹的唯一性确定），通过MLE加密得到相应的唯一密文数据块$C$。每个$M$对应于$\hat{M}^{(i)}$的一个或多个相同副本，同理，每个$C$对应于$\hat{C}^{(i)}$的一个或多个相同副本。
 
-% A unique plaintext (or plaintext for short) $M$ has one or more copies in $\mathbf{M}$  
-% Identical plaintexts may have multiple copies in $\mathbf{M}$, and we introduce unique plaintext  
-% We define a unique plaintext as the plaintext that has unique content among other plaintexts of $\mathbf{M}$    
-% Let $M$ and $C$ be a
-% plaintext and its corresponding ciphertext, respectively; both of them are in
-% units of chunks defined by deduplication.  We model a plain file before
-% deduplication as an {\em ordered} list of $n$ plaintexts, denoted by
-% $\mathbf{M} = \langle M^{(1)},  M^{(2)}, \ldots, M^{(n)}\rangle$.  Identical
-% plaintexts may appear at different positions of $\mathbf{M}$, say $M^{(i)} =
-% M^{(j)}$ for some $1\le i \neq j\le n$.   
-% % Also, each plaintext can have the
-% same or different chunk sizes due to fixed-size or variable-size chunking,
-% respectively, and let $|M|$ denote the size of a plaintext $M$.  
-% Let $M$ and $C$ denote a
-% plaintext (i.e., a logical chunk before encryption) and its corresponding
-% ciphertext (i.e., a logical chunk after encryption).  We model a plain file
-
-\section{Adversarial Goals and Assumptions}
+\section{对手的目标和相关假设}
 \label{sec:ThreatModel-Assumptions}
 
-We consider an adversary that aims to infer a set of ciphertext-plaintext
-pairs, denoted by \{$(C, M)$\}, with two specific goals:
-\begin{itemize}[leftmargin=*]
-\item
-{\bf High inference rate:} A large fraction of correct ciphertext-plaintext pairs
-are inferred, among all correct ciphertext-plaintext pairs (i.e., high recall or
-low false negative rates in statistical terms).
-\item
-{\bf High inference precision:} A large fraction of ciphertext-plaintext pairs
-are correct, among all inferred ciphertext-plaintext pairs (i.e., high precision
-or low false positive rates in statistical terms).
+本文考虑存在一个对手，它准备以以下两个明确的目标为基准推断一组密文数据块-明文数据块对（用\{$(C, M)$\}表示）。
+
+\begin{itemize}
+    \item \textbf{推理率高:}
+
+    在所有的正确密文数据块-明文数据块对中，推断出大部分正确的密文数据块-明文数据块对（即统计学上的高召回率或低阴性率）。
+
+    \item \textbf{推理精度高:}
+
+    在所有推断得到的密文数据块-明文数据块对中大部分的密文数据块-明文数据块对的配对是正确的（即统计术语中的高精度或低误报率）。
 \end{itemize}
 
-We assume that the adversary is {\em honest-but-curious}, such that it can
-passively monitor the stream of ciphertexts $\mathbf{C}$ being written to the
-storage system and exploit different types of leakage information from
-$\mathbf{C}$ (see Section~\ref{sec:leakage}).  Given the available leakage
-information, the adversary aims to infer the original plaintext of each
-ciphertext in $\mathbf{C}$ via a {\em ciphertext-only} attack.  It is possible
-that the adversary knows a limited subset of ciphertext-plaintext pairs to
-launch a known-plaintext attack, which further strengthens attack severity
-\cite{li17}.  We do not consider the known-plaintext attack in this paper.
+本文假设该对手是诚实但好奇的，它可以被动地监视密文数据块流$\mathbf{C}$被写入存储系统中的过程，并利用来自$\mathbf{C}$的不同类型的泄漏信息（参见章节：\ref{sec:ThreatModel-Leakage}）。鉴于可用的泄漏信息种类，对手仅可通过唯密文攻击的方法推断$\mathbf{C}$中每个密文数据块对应的原始明文数据块。当然，对手也有可能知道有限的密文数据块-明文数据块对的集合来发起已知明文攻击，这种情况进一步加深了攻击的严重性\citing{li2017information}。但在本文中不会考虑前述的已知明文攻击方式。因此，本文将$\mathbf{C}$视为对手所能观察到的的视图，并为该视图的不同属性建模。
 
-%We treat $\mathbf{C}$ as the {\em view} by the
-%adversary and model different properties of the view
+本文假设对手无法访问任何包含有关如何操作和存储数据块的信息的元数据（由于不对元数据应用重复数据删除，因此可以通过传统的对称加密来保护这些元数据，这种操作可使得对手无法获知该类型的信息）。此外，本文假设对手没有主动对重复数据删除系统进行攻击的能力，因为这种问题可以通过现有方法予以阻止。例如是恶意客户端可以在客户端重复数据删除中声明对未授权文件拥有所有权\citing{harnik2010side,halevi2011proofs,mulazzani2011dark}； 该问题可以通过所有权证明\citing{halevi2011proofs,xu2013weak,di2012boosting}或服务器端重复数据删除\citing{harnik2010side,li2015cdstore}予以解决。另一个例子是恶意存储系统可以修其改存储的数据；该问题可以通过远程完整性检查来进行检测和解决\citing{juels2007pors,ateniese2007provable}。
 
-We assume that the adversary does not have access to any {\em metadata} that
-contains the information about how chunks are operated and stored, as we do
-not apply deduplication to the metadata and hence it can be protected by
-traditional symmetric encryption.  Also, we assume that the adversary does not
-have {\em active} capabilities, which can be independently prevented by
-existing approaches. One example is that a malicious client may claim the
-ownership of unauthorized files in client-side deduplication
-\cite{harnik10,halevi11,mulazzani11}; it can be addressed by
-proof-of-ownership \cite{halevi11,xu13,pietro12} or server-side deduplication
-\cite{harnik10,li15}.  Another example is that a malicious storage system may
-modify stored data; it can be detected by remote integrity checking
-\cite{juels07,ateniese07}.
-
-% In addition, $\mathcal{A}$ does not aim to infer if
-% particular files have been stored \cite{harnik10, ritzdorf16}. Instead, we
-% study the security implication based on the inferred contents over different
-% types of files (see \S\ref{sec:case}).. 
-% Intuitively, we want to guarantee that what $\mathcal{A}$ can learn is some
-% well defined leakage $\mathcal{L}$, which includes the frequency, logical
-% order and/or chunk size (\S\ref{sec:leakage}). 
-% Note that $\mathcal{A}$ is specific to a {\em passive} adversary with content
-% inference in mind. We do not assume $\mathcal{A}$ has {\em active}
-% capabilities,
-
-\section{Leakage Channels}
+\section{三种信息的泄漏}
 \label{sec:ThreatModel-Leakage}
 
-We consider three types of leakage channels in encrypted deduplication storage
-that enable an adversary to infer information:
-\begin{itemize}[leftmargin=*]
-\item
-{\bf Frequency:}  Due to the deterministic nature of encrypted deduplication,
-the frequency of each ciphertext in $\mathbf{C}$ before deduplication (i.e., 
-the number of duplicate copies) can be mapped to that of its corresponding
-plaintext in $\mathbf{M}$. 
-% the size of each ciphertext in
-% $\mathbf{C}$ is approximately equal to that of its corresponding plaintext in
-% $\mathbf{M}$. In other words, the exact number of blocks (e.g., that are of size 16 bytes) in ciphertexts   
-% the exact number of blocks in the plaintext equals the number of blocks in the ciphertext
-% {\bf PC: if block cipher is used, it's not necessary that the
-% plaintext has the same size as its ciphertext}.
-%(e.g., \cite{douceur02, wilcox-ohearn08, bellare13b}) do not pad ciphertexts
-%with additional data to avoid storage overhead, 
-\item
-{\bf Order:}  Some storage systems (e.g., \cite{xia11,lillibridge09,zhu08})
-apply deduplication to the chunks in the same order as they appear in the
-original file.  Thus, the order of ciphertexts in $\mathbf{C}$ can be mapped
-to that of plaintexts in $\mathbf{M}$. 
-\item
-{\bf Size:}  Variable-size chunking (see Section~\ref{sec:background}) leads
-to different chunk sizes of the ciphertexts.  If such ciphertexts are not
-padded (to avoid storage overhead \cite{ritzdorf16}), the size of a ciphertext
-in $\mathbf{C}$ can be mapped to that of its corresponding plaintext in
-$\mathbf{M}$.    
+本文在加密重复数据删除存储中考虑三种类型的泄漏方式，这些泄漏使得对手能够基于它们推断信息：
+
+\begin{itemize}
+    \item \textbf{频率：}
+
+    由于加密重复数据删除的加密过程的确定性，重复数据删除前$\mathbf{C}$中每个密文数据块的频率（即重复副本数量）可以映射得到$\mathbf{M}$中相应明文数据块的频率。
+
+    \item \textbf{顺序：}
+
+    某些加密重复数据删除存储系统\cite{xia2011silo,lillibridge2009sparse,zhu2008avoiding}为了更高的运行性能，在存储密文数据块是保持了其对应的明文数据块的原始顺序。因此，$\mathbf{C}$中的密文的顺序可以映射到$\mathbf{M}$中的明文的顺序。
+
+    \item \textbf{大小：}
+
+    可变大小的数据块分块方法（参见章节：\ref{sec:background}）产生会产生各种不同大小的明文数据块，如果在对明文数据块进行加密前没有进行数据填充（为了避免增大存储开销\citing{ritzdorf2016information,douceur2002reclaiming,wilcox2008tahoe,keelveedhi2013dupless}），则产生的密文数据块大小与其对应的原始明文数据块大小一致（$\mathbf{C}$中的密文大小可以映射到$\mathbf{M}$中相应明文的大小）且密文数据块集合中的密文数据块也具有众多不同的大小。当然，该泄漏可以通过使用块密码算法使得明密文数据块大小不一致来避免。
 \end{itemize}
 
-%We also consider other leakage channels that are specific to real-world
-%deduplication storage systems. First, {\em order leakage} exposes the logical
-%order of each plaintext, and it is available for the systems
-%\cite{xia11,lillibridge09,zhu08} that aim for high performance and operate
-%the deduplication of chunks in the same order as these chunks appear in
-%original files; this implies that the logical order of ciphertext in
-%$\mathbf{C}$ exactly reflects that of its corresponding plaintext. Second,
-%{\em size leakage} exposes the chunk size of each plaintext, since some
-%systems \cite{douceur02, wilcox-ohearn08, bellare13b} avoid storage
-%overhead and do not pad ciphertexts with any additional data; this
-%implies that the size of ciphertext in $\mathbf{C}$ exactly equals that
-%of its corresponding plaintext.
+除上述三种泄漏以外，对手还可以获得一些辅助信息，这些信息提供了与$\mathbf{M}$相关的数据特征的基本情况（任何推理攻击都必须提供辅助信息\citing{kumar2007anonymizing,li2017information,grubbs2016breaking,zhang2016all,kellaris2016generic,ritzdorf2016information,naveed2015inference,cash2015leakage,islam2012access}）。在这项工作中，将辅助信息视为先前已知的明文数据块（例如，通过旧用户备份或VM磁盘映像得到）构成的有序列表，由$\mathbf{A}$表示。显然，攻击有效性与严重性取决于$\mathbf{A}$（即先前已知的明文数据块）和$\mathbf{M}$（即要推断的明文数据块）之间的相关性。本文的重点不是解决对手如何获取辅助信息的问题。例如，可能是由于粗心的数据发布\citing{careless-release}、被的盗存储设备\citing{stolen-device}和云存储泄漏\citing{cloud-leakage}。相反，根据这些信息，本文研究了可以获得的的辅助信息如何与各种泄漏渠道相结合，给加密重复数据删除带来信息泄漏。
 
-In addition, the adversary has access to some {\em auxiliary information} that
-presents the ground truth about the data characteristics correlated with
-$\mathbf{M}$. Note that the availability of auxiliary information is necessary
-for any inference attack \cite{kumar07,li17,grubbs17,zhang16b,kellaris16,ritzdorf16,naveed15,cash15,islam12}.
-In this work, we consider the auxiliary information as an ordered list of
-previously known plaintexts (e.g., old user backups or VM disk images),
-denoted by $\mathbf{A}$.  Clearly, the attack severity depends on the
-correlation between $\mathbf{A}$ (i.e., the previously known plaintexts) and
-$\mathbf{M}$ (i.e., the plaintexts that are to be inferred).  Our focus is not
-to address how an adversary can obtain auxiliary information, possibly due to
-careless data release \cite{careless-release}, stolen storage devices
-\cite{stolen-device}, and cloud leakage \cite{cloud-leakage}. Instead, given
-such information, we investigate how the available auxiliary information,
-combined with the leakage channels, bring information leakage from encrypted
-deduplication.
+本文将频率分析\citing{al1992origins}作为攻击方法。经典频率分析对$\mathbf{C}$中的唯一密文数据块和$\mathbf{A}$中的唯一明文数据块按频率（即对应于每个唯一密文数据块或唯一明文数据块的相同副本的数量）进行排序。然后，简单的将$\mathbf{C}$中的每个唯一密文数据块与$\mathbf{A}$中具有相同频率等级的唯一明文数据块相关联。基本的频率分析攻击实际效果非常糟糕，在接下来的章节中，本文针对加密重复数据删除设计了较为复杂同时效性极高的频率分析攻击。
 
-We focus on frequency analysis \cite{alkadit92} as the attack methodology.
-Classical frequency analysis sorts the unique ciphertexts in $\mathbf{C}$ and
-the unique plaintexts in $\mathbf{A}$ by {\em frequency} (i.e., the number of
-identical copies corresponding to each unique ciphertext or unique plaintext). 
-It then relates each unique ciphertext in $\mathbf{C}$ with the unique
-plaintext in $\mathbf{A}$ that has the same frequency rank. In the following
-sections, we design sophisticated frequency analysis attacks against encrypted
-deduplication.
+\section{本章小结}
 
-% Frequency analysis is a cryptanalysis primitive to relate the ciphertexts in $\mathbf{C}$  with the plaintexts in $\mathbf{M}$.
-Specifically, it sorts ciphertexts and plaintexts by their frequencies in $\mathbf{C}$ and $\mathbf{A}$, respectively, and maps each ciphertext to the plaintext that has the same frequency rank.
-Building on the classical version of frequency analysis, we show how to exploit leakage channels to strengthen its severity against encrypted deduplication.
-
-% infer ciphertext-plaintext pairs from $\mathbf{C}$ and $\mathbf{A}$. 
- % Specifically, the adversary
-
-% It performs well, only when the frequency of ciphertext is correlated with that of the corresponding plaintext. 
-% The more correlated to $\mathbf{M}$,
-
-% Our focus is not to address its availability, which is due to careless data release \cite{careless-release}, stolen storage devices \cite{stolen-device}, and cloud leakage \cite{cloud-leakage}.
-Instead, we show how an adversary can launch inference attacks based on the available auxiliary information $\mathbf{A}$.
-
-% Our focus is not to address how to obtain accurate auxiliary information, which we pose as future work; instead, given the available auxiliary information, we study how an adversary can design a severe attack based on frequency analysis and how we can defend against the attack
-% Some available auxiliary information has been demonstrated to be necessary for inference attacks  and we consider the auxiliary information $\mathbf{M}$ as a complete user backup, file system snapshot or VM disk image in plaintext.
-The rationale of its availability is that the adversary can obtain the original data from  We emphasize that the auxiliary information $\mathbf{M}$ does not need to be identical with the original file of $\mathbf{C}$.
-In other words, $\mathbf{M}$ may not have the
-% same number of chunks with $\mathbf{C}$, or its $i$-th chunk $M^{\langle i \rangle}$ may not be the plaintext of $C^{\langle i \rangle}$ or even not mapped into $\mathbf{C}$. 
-% {\bf PC: give the background on frequency analysis.}
-
-% We assume that the adversary can take advantage of some   for attacks. The auxiliary information , and it has been demonstrated for necessity in inference attacks . In this work,
-
-% In addition, the adversary can exploit other deduplication-specific leakage channels.
-
-% effectiveness of inference attacks.
-First, we consider {\em size leakage}, meaning that the adversary can derive the size of a plaintext directly based on the corresponding ciphertext: ${\sf s}(C) = |M|$, where $C$ is the encryption of $M$.
-
-% deduplication-specific leakage channels.
-
-% We target inference attacks against {\em backup workloads}, which refer to the copies of primary data (e.g., application states, file systems, and virtual disk images) over time.
-The recent technology trend \cite{douglis17} suggests to create full backups (that store the complete data of the primary source) over traditional incremental backups (that only store the changes of data since the last full backup), so as to mitigate the overhead in restoring earlier (full) backups.
-Thus, we focus on inferring information from different versions of full backups (or backups for short) that are created based on the same primary data source at different times.
-
-% They can be created as either weekly full backups (that store the complete data of the primary source) or daily incremental backups (that only store the changes of data since the prior full backup).
-Informed by the technology trend , we focus on full backups (or {\em backups} for short).
-Specifically, we aim to infer information from different versions of backups that are created based on the same primary data source yet at different times.
-
-% To launch attacks, we assume that $\mathcal{A}$ is an ``{\em honest-but-curious}'' adversary that can compromise the server hosting deduplication service, while it cannot establish a long-term presence for attack.
-Intuitively, we want to guarantee that what $\mathcal{A}$ can learn is some well defined leakage $\mathcal{L}$, which includes the frequency, logical order and/or chunk size (\S\ref{sec:leakage}).
-Formally, we define these leakage channels based on a target victim file $\mathbf{M}_{\rm t}$:
-
-% \begin{itemize}[leftmargin=*]
-% 	\item  {\bf Frequency leakage}: $\mathcal{L}_{\rm freq} = \{(C, {\sf freq}(M)): M \in \mathbf{M}_{\rm t}$ and $C = {\sf E}_{K_M}(M) \}$ is a set of chunk-frequency pairs, where $C$ is the encryption of some plaintext chunk $M$ in $\mathbf{M}_{\rm t}$, and each pair $(C, {\sf freq}(M))$ leaks the corresponding frequency of $M$.
-
-% 	\item  {\bf Order leakage}: $\mathcal{L}_{\rm order} = \{(C, {\sf ord}(M)): M\in\mathbf{M}_{\rm t}$ and $C = {\sf E}_{K_M}(M) \}$ associates each ciphertext chunk $C$ with a set ${\sf ord}(M)$ of logical orders, at which the copies of its original chunk $M$ appear in $\mathbf{M}_{\rm t}$.
-Note that order leakage {\em implies} frequency leakage, since the logical orders of each chunk copy inherently includes the number of times the corresponding chunk appears.
-
-% 	\item  {\bf Size leakage}: $\mathcal{L}_{\rm size} = \{(C, {\sf size}(M)): M \in \mathbf{M}_{\rm t}$ and $C = {\sf E}_{K_M}(M) \}$ is a set of chunk-size pairs, where each pair leaks the size of the original chunk of $C$.
-% \end{itemize}
-
-% In addition, $\mathcal{A}$ can take advantage of the {\em auxiliary information} $\mathbf{M}_{\rm a}$ that presents the ground truth about the frequency, size and order information about plaintext chunks.
-Some available auxiliary information is necessary for inference attacks , and we focus on validating our attacks with the auxiliary information obtained from different types of storage workloads (see \S\ref{sec:dataset}).
-
-% Acquiring the above capabilities, $\mathcal{A}$'s primary goal is to recover the plaintext chunks in the target file $\mathbf{M}_{\rm t}$.
-More formally, given the leakage $\mathcal{L}$ (that can be some combination of $\mathcal{L}_{\rm freq}$, $\mathcal{L}_{\rm order}$ and $\mathcal{L}_{\rm size}$) and the auxiliary information $\mathbf{M}_{\rm a}$, $\mathcal{A}$ outputs a collection of ciphertext-plaintext chunk pairs $\mathcal{R} = \{ (C, M) \}$: $\mathcal{A}(\mathcal{L}, \mathbf{M}_{\rm a}) \rightarrow \mathcal{R}.$ Each output pair $(C, M)$ indicates $\mathcal{A}$'s guess that relates a ciphertext chunk $C$ with a plaintext chunk $M$.
-
-% identify the ciphertext-plaintext chunk pairs about $\mathbf{M}_{\rm tar}$.
-More formally, given the leakage $\mathcal{L}$ (that can be some combinations of $\mathcal{L}_{\rm freq}$, $\mathcal{L}_{\rm order}$ and $\mathcal{L}_{\rm size}$), and auxiliary information $\mathbf{M}_{\rm aux}$, $\mathcal{A}$ outputs a collection of ciphertext-plaintext chunk pairs $\mathcal{R} = \{ (C, M) \}$: $\mathcal{A}(\mathcal{L}, \mathbf{M}_{\rm aux}) \rightarrow \mathcal{R}.$ Each pair $(C, M)$ indicates $\mathcal{A}$'s guess that relates a ciphertext chunk $C$ with a plaintext chunk $M$.
-
-% a malicious server may corrupt stored chunks, yet it can be detected by integrity checking mechanisms \cite{juels07,ateniese07};
-
-% and it is a correct inference by $\mathcal{A}$ if $C$ is the actual encryption of $M$, i.e., $(M, C) \in \mathcal{E}$.
-
-% We measure the success of attacks in several ways.
-The {\em raw inference rate} is the percentage of ciphertext chunks (including duplicates) that are inferred correctly over the total number of ciphertext chunks in the target information.
-For example, if the adversary correctly infers a ciphertext-plaintext chunk pair $(C, M)$ and the ciphertext chunk $C$ accounts for a fraction of 10\% in the target information, then the raw inference rate will be at least 10\%.
-
-% We assume the adversary can eavesdrop the deduplication processing (e.g., comparison operation of fingerprints) of all ciphertext chunks in a victim file (called {\em target information}); on the other hand, it cannot access related metadata that can be protected by traditional encryption \cite{li17}.
-% the same and different private sources, as well as some public source .
-
-% Note that $\mathcal{A}$ is specific to a passive adversary with content recovery in mind.
-We do not abstract $\mathcal{A}$ with active capabilities, since these threats can be protected by existing approaches.
-For example, a malicious server may corrupt stored chunks, yet it can be detected by integrity checking mechanisms \cite{juels07,ateniese07}; a malicious client may cheat owning a particular file \cite{harnik10,halevi11,mulazzani11}, yet it can be addressed by proof of ownership \cite{halevi11} or enforcing server-side deduplication \cite{li15}.
+本章介绍了针对重复数据删除的威胁模型的定义、本课题研究中将要用到的各种信息来源，以及本文攻击方案的假设的相关说明。

### 2018-12-15 paper/background.tex
ING | add part of dis-attack before dis-summary

@@
 
-本文旨在应用频率分析来探索加密重复数据删除的漏洞。 我们的重点不是解决如何获得用于推理攻击的相关明文。在统频率分析模式下，攻击者能够访问明文逻辑数据块集合M和密文逻辑数据块集合$C$（$M$和$C$包含重复的明文和密文数据块）。攻击者根据出现频率分别对$M$和$C$中的数据块进行排序，然后将$C$中的密文数据块映射为$M$中与其具有相同排名的明文数据块。
+本文旨在应用频率分析来探索加密重复数据删除的漏洞。 我们的重点不是解决如何获得用于推断攻击的相关明文。在统频率分析模式下，攻击者能够访问明文逻辑数据块集合M和密文逻辑数据块集合$C$（$M$和$C$包含重复的明文和密文数据块）。攻击者根据出现频率分别对$M$和$C$中的数据块进行排序，然后将$C$中的密文数据块映射为$M$中与其具有相同排名的明文数据块。
 

### 2018-12-15 paper/threatModel.tex
ING | add part of dis-attack before dis-summary

@@
 \begin{itemize}
-    \item \textbf{推理率高:}
+    \item \textbf{推断率高:}
 
@@
 
-    \item \textbf{推理精度高:}
+    \item \textbf{推断精度高:}
 
@@
 
-除上述三种泄漏以外，对手还可以获得一些辅助信息，这些信息提供了与$\mathbf{M}$相关的数据特征的基本情况（任何推理攻击都必须提供辅助信息\citing{kumar2007anonymizing,li2017information,grubbs2016breaking,zhang2016all,kellaris2016generic,ritzdorf2016information,naveed2015inference,cash2015leakage,islam2012access}）。在这项工作中，将辅助信息视为先前已知的明文数据块（例如，通过旧用户备份或VM磁盘映像得到）构成的有序列表，由$\mathbf{A}$表示。显然，攻击有效性与严重性取决于$\mathbf{A}$（即先前已知的明文数据块）和$\mathbf{M}$（即要推断的明文数据块）之间的相关性。本文的重点不是解决对手如何获取辅助信息的问题。例如，可能是由于粗心的数据发布\citing{careless-release}、被的盗存储设备\citing{stolen-device}和云存储泄漏\citing{cloud-leakage}。相反，根据这些信息，本文研究了可以获得的的辅助信息如何与各种泄漏渠道相结合，给加密重复数据删除带来信息泄漏。
+除上述三种泄漏以外，对手还可以获得一些辅助信息，这些信息提供了与$\mathbf{M}$相关的数据特征的基本情况（任何推断攻击都必须提供辅助信息\citing{kumar2007anonymizing,li2017information,grubbs2016breaking,zhang2016all,kellaris2016generic,ritzdorf2016information,naveed2015inference,cash2015leakage,islam2012access}）。在这项工作中，将辅助信息视为先前已知的明文数据块（例如，通过旧用户备份或VM磁盘映像得到）构成的有序列表，由$\mathbf{A}$表示。显然，攻击有效性与严重性取决于$\mathbf{A}$（即先前已知的明文数据块）和$\mathbf{M}$（即要推断的明文数据块）之间的相关性。本文的重点不是解决对手如何获取辅助信息的问题。例如，可能是由于粗心的数据发布\citing{careless-release}、被的盗存储设备\citing{stolen-device}和云存储泄漏\citing{cloud-leakage}。相反，根据这些信息，本文研究了可以获得的的辅助信息如何与各种泄漏渠道相结合，给加密重复数据删除带来信息泄漏。
 

### 2018-12-28 paper/Conclusion.tex
ING | complete chapter 4 and begin chapter 5 before workflow

@@
 \label{sec:Conclusion}
+
+加密重复数据删除应用确定性加密，并由此泄漏了明文的频率。本文重新审视了频率分析引起的安全漏洞，并证明加密重复数据删除更容易受到推理攻击。本文提出了两种新的频率分析攻击方法，它们在攻击者所具有的条件的不同假设下都能实现高推理率和高推理精度。本文用三个真实世界的数据集来验证评估这两种攻击方法，提出关于其性质的各种新观察，并进一步分析它们如何带来实际损害。本文还讨论了可能的对策的优缺点，以建议从业者安全地实施和部署加密的重复数据删除存储系统。
 
@@
 
-% types of files are especially insecure under these attacks.    
-% We propose two new inference attacks, which augment the prior attack \cite{li17} with high precision inference and relaxed adversarial knowledge, respectively.   
-% While prior work \cite{li17} has illustrated the vulnerability  via frequency analysis, this paper presents an in-depth study on the security of encrypted deduplication, and       
+\section{后续工作}
+
+我们为未来的工作提出三个方向。
+ 
+ 首先，我们将完整的旧备份视为辅助信息，如果攻击者仅对旧备份有部分了解，则不研究如何发起攻击。可能的是，我们仍然可以应用频率分析攻击从可用的部分备份中提取特征，并通过比较特征与目标备份中的特征来推断密文 - 明文对。一个方向是我们可以设计先进的推理攻击，这比在这个部分知识案例中直接应用我们的攻击更好吗？
+      
+ 其次，我们根据频率分析攻击的有效性调整频率分析攻击的参数，只有在攻击发生后才能学习。我们不研究如何预先从辅助信息中推导出最佳参数。未来的工作可能会做得更好
+
+第三，我们不对实际加密的重复数据删除存储系统实施攻击原型。另一个方向是部署我们的攻击设计和报告加密重复数据删除在实践中的漏洞。
+
  We pose three directions for future work.
+
  First, we consider a complete old backup as the auxiliary information, and do not study how to launch attack if the adversary only has partial knowledge about the old backup.
@@
 
- % The attack effectiveness depends on how the information in the partial backup correlates with the target backup.       
  Second, we adjust the parameters of the frequency analysis attacks based on their effectiveness, which can only be learnt after the attacks have happened.
@@
 
- % We believe the parameter configurations depend on the characteristics of workloads, but do not see how to derive them efficiently.
-
- % the frequency analysis attacks are parameter sensitive.
-We adjust parameters based on the attack effectiveness (that can only be measured after the attack happens), and do not study how to identify the optimal parameter configuration  beforehand.
-We believe the parameter configurations depend on the characteristics of workloads, but do not see how to derive them efficiently.
-Future work may do better.
-
- % our proposed attacks are parameter sensitive.
-In evaluation, we adjust the parameters based on attack results, and report the security vulnerability of encrypted deduplication under some {\em specific} parameter settings of our attacks.
-We do not  study how to identify the optimal parameter setting of attack without the knowledge of attack results.
-We begin to consider that the attack configurations possibly depend on the characteristics of target workloads, but do not see how to derive them.
-Future work may do better.
-
-% help practitioners and researchers better understand the security issues in encrypted deduplication storage and motivate more research along this direction.
-% While 
-% of encrypted deduplication
-% Although it is vulnerable to frequency analysis, prior work \cite{li17} shows that classical frequency analysis can only infer a few original chunks in practice.
-This paper considers to increase the effectiveness of frequency analysis with additional leakages.
-Specifically, we present three new inference attacks by exploiting the size and order leakages that have been witnessed in deduplication systems \cite{xia11,lillibridge09,zhu08,douceur02, wilcox-ohearn08, bellare13b}.
-We evaluate the effectiveness of  our attacks with real-world datasets, and show that they can infer significant amount of original data under different types of workloads.
-We also discuss possible countermeasures to address the leakage channels exploited by our attacks.
-We pose the following future works.
-
 Third, we do not implement  attack prototypes against real-world encrypted deduplication storage systems. Another direction is to deploy our attack design and 
 report the vulnerability of encrypted deduplication in practice.
-
-% - Our attacks are parameter sensitive. One direction is to explore the relationship between configuration and workload characteristics.
-
-% - There seems a tradeoff between size-based attack and distribution-based attack.
-Throughout our experiment, size-based attack operates big chunks better, since they have more variances on chunk size.
-The distribution-based attack is expected to operate small chunks better, because there exists more chunk locality between small chunks.
-
-% - To defend our attacks, one approach is to obfuscate the chunk distributions.
-A recent work suggests to add redundant chunks to mix up network traffic.
-It works for changing chunk distribution, but depends on knowing if a chunk is duplicate before deduplication.
-
-% - This paper aims to report the vulnerabilities of encrypted deduplication, while not target on implementing a real attack against practical encrypted deduplication systems.
-Another direction is deploy our attack design in practice to alert the vulerabilities of encrypted deduplication.

### 2018-12-28 paper/background.tex
ING | complete chapter 4 and begin chapter 5 before workflow

@@
 
-具体地，重复数据删除系统首先通过文件切块过程将客户端的文件（例如，备份文件）分割成逻辑数据块，根据每一个逻辑数据块的内容使用HASH算法（散列算法）计算得到其对应的唯一标签（又成为指纹）。如果两个数据块具有相同的标签，那么认为两个数据块相同（不同逻辑数据块计算得到相同的标志的概率忽略不计\citing{black2006compare}），即数据块内容和其标志完全一致；若两个逻辑数据块标签不一致，显然两逻辑数据块不同。重复数据删除系统的存储系统仅存储相同逻辑数据块的副本（称为物理数据块），并且每个相同的逻辑数据块通过一个较小空间开销的索引引用相同的物理数据块。
+具体地，重复数据删除系统首先通过文件切块过程将客户端的文件（例如，备份文件）分割成逻辑数据块，根据每一个逻辑数据块的内容使用HASH算法（哈希算法）计算得到其对应的唯一标签（又成为指纹）。如果两个数据块具有相同的标签，那么认为两个数据块相同（不同逻辑数据块计算得到相同的标志的概率忽略不计\citing{black2006compare}），即数据块内容和其标志完全一致；若两个逻辑数据块标签不一致，显然两逻辑数据块不同。重复数据删除系统的存储系统仅存储相同逻辑数据块的副本（称为物理数据块），并且每个相同的逻辑数据块通过一个较小空间开销的索引引用相同的物理数据块。
 
@@
 
-MLE可以实现为不同的实例化（参见章节：\ref{sec:RelatedWork}）。其中最受欢迎的是融合加密（CE）\citing{douceur2002reclaiming}，它已经在各种存储系统中实现\citing{adya2002farsite,ElephantDrive,MEGA,GNUP2P,Freenet,Cryptosphere,cox2002pastiche,storer2008secure,anderson2010fast}。 CE的主要思想是根据每个明文数据块的内容通过HASH函数（散列函数）导出其对应的MLE密钥。这种方法可以确保具有相同内容的逻辑数据块加密得到的密文数据块始终一致，即可使用密文数据块的标签进行重复数据删除。但也存在部分MLE实例\citing{bellare2013message}允许将相同的明文加密成不同的密文。当然，他们确保用于重复数据删除的标签仍然来自明文，因此他们依然可以通过检查标签的相同性来执行重复数据删除。
+MLE可以实现为不同的实例化（参见章节：\ref{sec:RelatedWork}）。其中最受欢迎的是融合加密（CE）\citing{douceur2002reclaiming}，它已经在各种存储系统中实现\citing{adya2002farsite,ElephantDrive,MEGA,GNUP2P,Freenet,Cryptosphere,cox2002pastiche,storer2008secure,anderson2010fast}。 CE的主要思想是根据每个明文数据块的内容通过HASH函数（哈希函数）导出其对应的MLE密钥。这种方法可以确保具有相同内容的逻辑数据块加密得到的密文数据块始终一致，即可使用密文数据块的标签进行重复数据删除。但也存在部分MLE实例\citing{bellare2013message}允许将相同的明文加密成不同的密文。当然，他们确保用于重复数据删除的标签仍然来自明文，因此他们依然可以通过检查标签的相同性来执行重复数据删除。
 

### 2018-12-28 paper/introduction.tex
ING | complete chapter 4 and begin chapter 5 before workflow

@@
 
-为了保护数据隐私，加密重复数据删除（encrypted deduplication）增加了一层作用于逻辑数据块的加密操作。如图\ref{fig:加密重复数据删除系统逻辑视图}所示，该加密层基于数据内容来产生加密密钥\citing{bellare2013message}（例如将数据块的散列值作为密钥\citing{douceur2002reclaiming}），从而将相同的明文数据块加密为相同的密文数据块。系统计算每个密文数据块的散列值(称为指纹，fingerprint)，查询指纹索引（fingerprint index）确定该数据块是否已经存储，最后保存仅具有唯一指纹的密文数据块。需要指出的是，部分加密重复数据删除方案\citing{bellare2013message}采用随机加密算法，但基于明文数据块产生指纹，因此仍然可以通过检查指纹来识别重复数据。
+为了保护数据隐私，加密重复数据删除（encrypted deduplication）增加了一层作用于逻辑数据块的加密操作。如图\ref{fig:加密重复数据删除系统逻辑视图}所示，该加密层基于数据内容来产生加密密钥\citing{bellare2013message}（例如将数据块的哈希值作为密钥\citing{douceur2002reclaiming}），从而将相同的明文数据块加密为相同的密文数据块。系统计算每个密文数据块的哈希值(称为指纹，fingerprint)，查询指纹索引（fingerprint index）确定该数据块是否已经存储，最后保存仅具有唯一指纹的密文数据块。需要指出的是，部分加密重复数据删除方案\citing{bellare2013message}采用随机加密算法，但基于明文数据块产生指纹，因此仍然可以通过检查指纹来识别重复数据。
 
@@
 
-消息锁定加密（message-locked encryption，MLE）确立了加密重复数据删除的密码学基础\citing{bellare2013message}:基于数据内容产生密钥(称为 MLE 密钥)，从而将相同明文加密为相同密文。最流行的MLE实例是收敛加密（convergent encryption，CE）\citing{douceur2002reclaiming}，它使用明文的散列值作为MLE密钥，并基于密文散列值计算指纹，以识别重复数据（如图\ref{fig:加密重复数据删除系统逻辑视图}）。基于CE的加密重复数据删除方案还包括:
+消息锁定加密（message-locked encryption，MLE）确立了加密重复数据删除的密码学基础\citing{bellare2013message}:基于数据内容产生密钥(称为 MLE 密钥)，从而将相同明文加密为相同密文。最流行的MLE实例是收敛加密（convergent encryption，CE）\citing{douceur2002reclaiming}，它使用明文的哈希值作为MLE密钥，并基于密文哈希值计算指纹，以识别重复数据（如图\ref{fig:加密重复数据删除系统逻辑视图}）。基于CE的加密重复数据删除方案还包括:
 
 \begin{enumerate}
-    \item 散列收敛加密（hash convergent encryption，HCE）\citing{douceur2002reclaiming}与CE具有相同的MLE密钥产生规则，但基于明文散列值计算指纹。
-    \item 随机收敛加密（random convergent encryption，RCE）\citing{douceur2002reclaiming}使用随机密钥加密以产生非确定的密文，同时也基于明文散列值来进行重复检查。
-    \item 收敛扩散（convergent dispersal，CD）\citing{li2016cdstore}使用明文散列值作为秘密共享（secret sharing）的输入种子，在兼容重复数据删除的基础上 提高了密文存储的可靠性。
+    \item 哈希收敛加密（hash convergent encryption，HCE）\citing{douceur2002reclaiming}与CE具有相同的MLE密钥产生规则，但基于明文哈希值计算指纹。
+    \item 随机收敛加密（random convergent encryption，RCE）\citing{douceur2002reclaiming}使用随机密钥加密以产生非确定的密文，同时也基于明文哈希值来进行重复检查。
+    \item 收敛扩散（convergent dispersal，CD）\citing{li2016cdstore}使用明文哈希值作为秘密共享（secret sharing）的输入种子，在兼容重复数据删除的基础上 提高了密文存储的可靠性。
 \end{enumerate}

### 2019-01-03 paper/Conclusion.tex
ING | last part - exp - figure fix

@@
-\chapter{结论}
+\chapter{结束语}
 \label{sec:Conclusion}
 
-加密重复数据删除应用确定性加密，并由此泄漏了明文的频率。本文重新审视了频率分析引起的安全漏洞，并证明加密重复数据删除更容易受到推理攻击。本文提出了两种新的频率分析攻击方法，它们在攻击者所具有的条件的不同假设下都能实现高推理率和高推理精度。本文用三个真实世界的数据集来验证评估这两种攻击方法，提出关于其性质的各种新观察，并进一步分析它们如何带来实际损害。本文还讨论了可能的对策的优缺点，以建议从业者安全地实施和部署加密的重复数据删除存储系统。
+\section{本文总结}
 
-Encrypted deduplication applies deterministic encryption, and leaks the frequencies of plaintexts.
-This paper revisits the security vulnerability  due to frequency analysis, and demonstrates that encrypted deduplication is even more vulnerable towards inference attacks.
-We propose two new frequency analysis attacks, both of which  achieve high inference rate and high inference precision, while under different assumptions of adversarial knowledge.
-We empirically evaluate our attacks with three real-world datasets, present a variety of new observations about their natures, and further analyze how they bring actual damages.
-We also discuss the advantages and disadvantages of possible countermeasures to advise practitioners for securely implementing and deploying encrypted deduplication storage systems.
+加密重复数据删除应用确定性加密，并由此泄漏了明文的频率。本文重新审视了频率分析引起的安全漏洞，并证明加密重复数据删除更容易受到推理攻击。本文提出了两种新的频率分析攻击方法，它们在攻击者所具有的条件的不同假设下都能实现高推理率和高推理精度。本文用三个真实世界的数据集来验证评估这两种攻击方法，提出关于其性质的各种新观察，并进一步分析它们如何带来实际性的损害。本文还讨论了加密重复数据删除应对频率分析攻击的可能的对策及其相应的优缺点，以建议从业者安全地实现和部署加密重复数据删除存储系统。
 
-\section{后续工作}
+\section{下一步学习工作方向}
 
-我们为未来的工作提出三个方向。
+本文为未来的工作提出三个方向。
 
- 首先，我们将完整的旧备份视为辅助信息，如果攻击者仅对旧备份有部分了解，则不研究如何发起攻击。可能的是，我们仍然可以应用频率分析攻击从可用的部分备份中提取特征，并通过比较特征与目标备份中的特征来推断密文 - 明文对。一个方向是我们可以设计先进的推理攻击，这比在这个部分知识案例中直接应用我们的攻击更好吗？
+首先，本文将完整的旧备份视为辅助信息，如果攻击者仅对旧备份的部分有了解（没有完整的旧备份用作辅助信息），则不研究攻击者如何发起攻击。可能的是，攻击者仍然可以应用频率分析攻击从可用的部分备份中提取特征，并通过比较特征与目标备份中的特征来推断密文数据块-明文数据块对。未来研究的第一个方向是设计更高级的推理攻击方法，并比较在前述的部分知识案例中新方法是否比直接应用本文提出的两种攻击更好。
       
- 其次，我们根据频率分析攻击的有效性调整频率分析攻击的参数，只有在攻击发生后才能学习。我们不研究如何预先从辅助信息中推导出最佳参数。未来的工作可能会做得更好
       
-第三，我们不对实际加密的重复数据删除存储系统实施攻击原型。另一个方向是部署我们的攻击设计和报告加密重复数据删除在实践中的漏洞。
+\par 其次，本文根据频率分析攻击的有效性调整频率分析攻击的参数，这种调整只有在攻击发生后才能学习。本文没有研究如何预先从辅助信息中推导出最佳参数。未来研究的第二个方向是在预先通过辅助信息推导最佳攻击参数方面尝试作出改进。
 
- We pose three directions for future work.
-
- First, we consider a complete old backup as the auxiliary information, and do not study how to launch attack if the adversary only has partial knowledge about the old backup.
-Possibly, we can still apply the frequency analysis attacks to extract characteristics from the available partial backup, and infer ciphertext-plaintext pairs by comparing the characteristics with those in the target backup.
-One direction is can we design advanced inference attacks, which  perform better than directly applying our attacks in this partial knowledge case?
-
- Second, we adjust the parameters of the frequency analysis attacks based on their effectiveness, which can only be learnt after the attacks have happened.
-We do not study how to derive the optimal parameters from auxiliary information beforehand.
-Future work may do better.
-
-Third, we do not implement  attack prototypes against real-world encrypted deduplication storage systems. Another direction is to deploy our attack design and 
-report the vulnerability of encrypted deduplication in practice.
+第三，本文不对实际的加密重复数据删除存储系统实现攻击原型。未来研究的第三个方向是在实际系统中部署本文提出的攻击设计以及报告加密重复数据删除在实践中存在的漏洞。

### 2019-01-03 paper/Countermeasure.tex
ING | last part - exp - figure fix

@@
 
-In this section, we discuss the advantages and disadvantages of possible countermeasures against the leakage channels exploited in this paper.
-Note that the countermeasures against size leakage are not enough for preventing our attacks, in which the size information is just optional.
+在本章中，将讨论应对本文攻击方案使用的三种泄漏的对策及其优缺点。但在三中泄漏中，单纯的防范数据块大小信息泄漏并不足以使本文提出的攻击手段失效（大小信息的利用只是攻击用于进一步提高推理攻击准确性的可选条件）。
 
-\section{Against frequency leakage:}
-MinHash encryption \cite{qin17, li17} encrypts each plaintext with a key derived from the minimum chunk hash over a set of its adjacent chunks, and possibly maps identical plaintexts into  different ciphertexts.
-The rationale for defense is that MinHash encryption changes frequencies, and disturbs frequency ranking.
- Note that MinHash encryption also prevents the frequency analysis attacks in this paper, because  we target deterministic encryption (e.g., MLE \cite{bellare13a}), while MinHash encryption is non-deterministic and changes the  frequency distribution of chunks.
-The disadvantage is that MinHash encryption degrades the storage saving by deduplication, since it breaks the one-to-one mapping between plaintexts and ciphertexts.
-In addition, MinHash encryption is not an active countermeasure, since its randomness essentially depends on the minimum chunk hashes in the target workloads.
+\section{防止频率泄漏}
 
-% (rather than the chunk itself \cite{bellare13a}) over its adjacent chunks, so that some identical plaintext chunks can be encrypted into different ciphertext chunks.
-The rationale of defense is MinHash encryption {\em changes the frequencies of chunks} and leads to rank disturbances in classical frequency analysis.
-In addition, the nature of MinHash encryption is {\em non-deterministic}, and prevents the distribution-based ranking (see \S\ref{sec:distribution-attack-description}) that targets deterministic encryption.
-On the other hand, MinHash encryption is not an {\em active} countermeasure, since its defense effectiveness is dominated by workload characteristics (i.e., depending on the diversity of MinHash).
-It also degrades deduplication effectiveness due to breaking the one-to-one mapping between plaintexts and ciphertexts.
+MinHash加密\citing{qin2017design,li2017information}使用从一组相邻数据块上的最小块哈希导出的密钥加密该组内每个明文数据块，因此可能将相同的明文数据块加密映射到不同的密文数据块。防御频率信息泄漏的基本原理是通过MinHash加密改变各个密文数据块的频率，并由此扰乱不同数据块的频率排名。
 
-A recent work \cite{zuo18} suggests intentionally adding duplicate chunks to prevent traffic analysis against client-side deduplication.
-The approach \cite{zuo18} can be applied to address the frequency analysis attacks, since it changes the frequencies of chunks.
-Compared with MinHash encryption, the countermeasure \cite{zuo18} does not degrade storage efficiency, since only duplicate chunks are added.
-On the other hand, it  requires the priori knowledge that if particular chunks are duplicate, and only suits the client-side deduplication, which possibly introduces additional leakage channels (see Section~\ref{sec:related}).
+与此同时，MinHash加密还可以用于防止本文中的频率分析攻击。MinHash加密是非确定性的加密方法，使用该方法会改变数据块的频率分布，因此本文的的攻击目标是确定性加密（例如，MLE\citing{bellare2013message}）。但MinHash加密因为打破了明文数据块-密文数据块之间的一一映射关系，所以在加密重复数据删除中导致了存储效率的下降（重复数据删除所能节省的存储空间变小）。此外，因为MinHash加密的随机性主要取决于目标工作负载中的最小块哈希，所以其不是一种扰乱数据块频率的主动对策，在不同的工作负载中能实现的扰乱效果具有较大的差异。
 
-Several extended MLE instantiations build on strong cryptographic primitives to defend against the frequency leakage of encrypted deduplication, such as randomized encryption that supports equality testing \cite{abadi13}, hybrid encryption \cite{stanek14}, and interactions with fully homomorphic encryption \cite{bellare15}.
-They provide provable security, yet how they can be implemented and deployed in practice remains unexplored.
+最近的一项工作\citing{zuo2018mitigating}提出通过有计划的添加冗余（重复）的数据块来防止针对客户端加密重复数据删除的流量分析攻击。该方法\citing{zuo2018mitigating}在运作中会改变数据块的频率，因此可以用于防止频率分析攻击。与MinHash加密相比，该方法\citing{zuo2018mitigating}只是添加了重复的数据块，因此不会降低存储效率。但另一方面，它需要使用在特定的假设之下。首先它要求特定的数据块是重复的，其次它只适用于客户端重复数据删除。因此使用这种方法可能会引入额外的泄漏通道（参见\ref{sec:RelatedWork}）。
 
-% yet how they are implemented and deployed in practice remains unexplored. 
-% some random encryption schemes \cite{stanek14,bellare15,abadi13,lacharite18a}  address the frequency leakage of deterministic encryption.
-Other than the practical approaches \cite{qin17, li17, zuo18}, they provide provable security, yet building on computationally expensive primitives.
-% % (see Section~\ref{sec:related}).
+现有工作提出了几个扩展的MLE实例基于强加密原语构建，以防止加密重复数据删除的频率泄漏，例如支持等式测试的随机加密\citing{abadi2013message}，混合加密\citing{stanek2014secure}，以及与完全同态加密的交互\citing{bellare2015interactive}。它们都提供了可证明的安全性，但它们如何在实践中实施和部署仍未有进一步的研究。
 
-% are proposed to address frequency leakage from cryptography aspect, yet they are not readily implemented in practice .
+\section{防止顺序泄漏}
 
-% Some studies \cite{stanek14,abadi13,bellare15} aim to achieve stronger security than the more practical schemes focused above.
-Stanek {\em et al.} \cite{stanek14} design a hybrid encryption scheme where unpopular messages are protected by semantically secure encryption for high security guarantee, while popular messages are protected by CE to enable deduplication.
-On the other hand, the scheme \cite{stanek14} builds on public-key primitive which is inefficient for encrypting large-size messages.
-Abadi {\em et al.} \cite{abadi13} construct two schemes for the messages whose distributions are publicly available.
-Their first scheme generates  random tags and ciphertexts to prevent frequency leakage, yet incurring expensive {\em equality test} for checking duplicates.
-Their second scheme produces deterministic ciphertexts, and exposes the frequencies of corresponding plaintexts.
-Interactive MLE \cite{bellare15} introduces interactions into encrypted deduplication, and strengthens the security of both correlated and parameter-dependent messages, yet it is impractical for the use of fully homomorphic encryption.
-On the contrary to these theoretical contributions \cite{stanek14, abadi13, bellare15}, this paper focuses on the applied aspect, and investigates the security vulnerabilities in practical deduplication.
+一个简单的对策是干扰数据块在重复数据删除处理中顺序。例如，加密重复数据删除可以在加密之前对明文数据块流进行额外的顺序扰动添加处理，以隐藏每个明文数据块的真实逻辑顺序。这种方法可以有效的防止基于分布的频率分析攻击（参见\ref{sec:DistributionAttack}），因为攻击者无法正确识别到数据块邻居信息。但它对于基于聚类的频率分析攻击（参见\ref{sec:ClusteringAttack}）并不是完全有效的。如果添加扰动仅在很小的范围内进行（例如，每个数据段中的明文数据块的顺序被添加扰动），则基于聚类的频率分析攻击方法仍然有效。
 
-\section{Against order leakage:}
-A simple countermeasure is to disturb the deduplication processing sequence of chunks.
-For example, we can operate an additional order-scrambling process on the stream of plaintexts before encryption, so as to hide the actual logical order of each plaintext.
-This prevents the distribution-based attack, because the adversary cannot identify neighboring information correctly.
-On the other hand, it is not always effective against the clustering-based attack.
-If scrambling  operates on just a small basis (e.g., the orders of plaintexts in each segment are scrambled), the clustering-based attack still works.
-The disadvantage of the order-scrambling countermeasure is that it breaks chunk locality and leads to performance drop in large-scale deduplication \cite{xia11,zhu08,lillibridge09}.
+顺序扰乱策略的最大缺陷在于它破坏了数据块的局部性并且在大规模的重复数据删除中会导致性能的严重下降\citing{xia2011silo,zhu2008avoiding,lillibridge2009sparse}。
 
-% On the other hand, if we operate scrambling        
-% {\em scrambling}, which intentionally disturbs the deduplication processing sequence of chunks. 
-% operates the stream  before deduplication and disturbs the order of each plaintext. 
-% disturbs the orders of plaintexts before deduplication 
-% to scramble the orders of plaintexts. Specifically, the scrambling approach , and randomly changes the order of each plaintext.   
-% A countermeasure is to scramble the orders of chunks, so as to prevent adversary from learning the actual order of each chunk.
-One note is the scrambling countermeasure should be applied by taking similarity into account; otherwise, the adversary can exploit the property for inference attack (see \S\ref{sec:clustering-attack}).
-For example, applying scrambling in a small basis (e.g., within a segment) is not enough for preventing the clustering-based attack.
-On the other hand, large-scale scrambling breaks chunk locality completely, and leads to significant degradation of deduplication performance .
+\section{防止大小泄漏}
 
-\section{Against size leakage:}
-As suggested by prior work \cite{ritzdorf16}, we can pad each plaintext with additional data to obfuscate the actual size of this plaintext.
-However, we note that the padding scheme is not straightforward, since it requires to add identical redundancies to the same plaintexts; otherwise the storage system cannot detect duplicates for deduplication.
-One possible solution is to build on the paradigm of MLE \cite{bellare13b,bellare13a}.
-We compute the cryptographic hash of each plaintext as a seed, and use it to generate variable-size pseudorandom data to be padded with the  plaintext.
-Like MLE, this solution comes at the expense of server-aided approach \cite{bellare13b} to defend against brute-force attack (see Section~\ref{sec:related}).
+正如已有的工作\citing{ritzdorf2016information}所建议的那样，加密重复数据删除可以在每个明文数据块种填充额外的数据来混淆这个明文数据块的实际大小。但是，这种填充方案的实现存在很大的难度，因为它需要在相同的明文数据块中添加相同的冗余数据；否则加密重复数据删除存储系统无法正常检测数据块是否重复。一种可能的解决方案建立在MLE\citing{keelveedhi2013dupless,bellare2013message}的范例之上，考虑将每个明文数据块的加密哈希作为计算种子，并使用它来生成可变大小的伪随机数据用于明文数据块的填充。与MLE一样，这种解决方案的代价是需要使用服务器辅助方法\citing{keelveedhi2013dupless}来抵御暴力攻击（参见\ref{sec:RelatedWork}）。
 
-% A countermeasure is to sacrifice storage efficiency and {\em pad each chunk with additional data}, which can obfuscate the original size of this chunk.
-The padding scheme is not straightforward, as it is required to {\em add identical redundant data to the same chunks}; otherwise, the server cannot detect duplicates for deduplication.
-One possible solution is based on the spirit of MLE \cite{bellare13b,bellare13a}.
-% Specifically, we compute the cryptographic hash of each chunk as a seed, and use the seed to generate variable-size pseudorandom data to be padded with the corresponding chunk.
-Like MLE, this solution comes at the expense of server-aided approach \cite{bellare13b} to defend against brute-force attack (see \S\ref{sec:related}).
-
-  Instead of variable-size chunking, we can use fixed-size chunking to 
- generate equal-size chunks for deduplication.
-Since all chunks have the same size, the adversary cannot exploit size information to differentiate them.
-Although fixed-size chunking suffers from boundary shift, it achieves almost the same storage saving of deduplication as variable-size chunking in VM disk images \cite{jin09}.
-Thus, we suggest applying fixed-size chunking in its favorable workloads to prevent size leakage.
-
-  % make the leaked size information hard to be exploited for inference attack.
-It suffers from the shift of chunk boundaries and is less effective for majority workloads, while prior work \cite{jin09} shows fixed-size chunking achieves almost the same storage efficiency as variable-size chunking for VM disk images.
-
-% , although does not address size leakage explicitly, can make the available size information hard to be exploited for inference attack.
-On the other hand, it sacrifices deduplication effectiveness in most of storage workloads due to the shift of chunk boundaries.
+另一种思路是使用固定大小的数据块分块方法来取代可变大小的数据块分块方法。在这种情况下，由于所有的数据块都具有相同的大小，因此攻击者无法利用大小信息来区分它们。虽然固定大小的分块会受到边界偏移的影响，但它在VM磁盘映像这一特定数据类型中实现了与可变大小数据块分块方案几乎相同的重复数据删除存储空间节省效果\citing{jin2009effectiveness}。 因此，本文建议在某些特定的加密重复数据删除工作负载（例如，VM磁盘映像）中应用固定大小的数据块分块方法，以防止数据块大小信息泄漏。

### 2019-01-03 paper/DataSetandSystemReport.tex
ING | last part - exp - figure fix

@@
 \chapter{数据集与实际系统调研}
-\section{数据集}
+\section{数据集调研}
+
+本文调研与使用以下数据集用于评估提出的两种攻击方法的效果，通过模拟攻击评估重复数据删除中信息泄漏带来的安全隐患（参见\ref{sec:background}）。
+
 \subsection{FSL数据集}
+
+\begin{table}[!hbt]
+    \caption{FSL数据集特征}
+\small
+\label{tab:FSL-dataset}
+\centering
+\begin{tabular}{|c|c|c|c|}
+\hline
+\multirow{2}{*}{\bf 类别} & \multicolumn{3}{c|}{\bf 备份中的特征} \\
+\cline{2-4}
+    & \#逻辑数据块数（百万） & \#唯一数据块数（百万） & 近似逻辑大小（GB）\\
+\hline
+User004  & 1.0-1.3 & 0.7-0.9 & 10GB/备份$\times$ 14个\\
+\cline{1-4}
+User007 &  3.5-5.2 & 2.3-3.6 & 39GB/备份 $\times$ 14个\\
+\cline{1-4}
+User012 &  25.0-26.4 & 8.9-9.7 & 244GB/备份 $\times$ 14个\\
+\cline{1-4}
+User013 &  1.8-5.7 & 1.2-4.2 & 22GB/备份 $\times$ 14个\\
+\cline{1-4}
+User015 &  13.4-20.5 & 9.0-11.0 & 158GB/备份 $\times$ 14个\\
+\cline{1-4}
+User028 &  6.0-10.3 & 3.5-6.8 & 77GB/备份 $\times$ 14个\\
+\hline
+\end{tabular}
+\end{table}
+
+表\ref{tab:FSL-dataset}总结了FSL实验数据集的相关特征信息，其中\#逻辑数据块数 和 \#唯一数据块数表示每个实验快照中逻辑数据块数量和具有唯一性的数据块数量。
+
+此数据集由Stony Brook大学的文件系统和存储实验室（FSL）收集\cite{sun16，FSL14，sun18}。本文使用fslhomes快照进行实验，每个快照包括48位数据块哈希的有序列表，这些哈希是由平均大小为8KB的可变大小分块生成的，以及相应的元数据信息（例如，数据块大小、文件名、扩展名等）。本文从2013年1月22日到5月21日选择快照，并选择在整个持续时间内具有完整每日快照的六个用户（即User004，User007，User012，User013，User015和User028）用于后续实验分析。本文以周为单位选取备份数据，因此为每个用户选出14个每周完整备份。
+
 \subsection{VM数据集}
+
+\begin{table}[!hbt]
+    \caption{VM数据集特征}
+\small
+\label{tab:VM-dataset}
+\renewcommand{\arraystretch}{1.2}
+\vspace{-3pt}
+\centering
+\begin{tabular}{|c|c|c|c|}
+\hline
+\multirow{2}{*}{\bf 类别} & \multicolumn{3}{c|}{\bf 备份中的特征} \\
+\cline{2-4}
+    & \#逻辑数据块数（百万） & \#唯一数据块数（百万） & 近似逻辑大小（GB）\\
+
+\hline
+User1  &  \multirow{6}{*}{2.6} & $\sim$0.9 & 25GB/备份 $\times$ 13 个 \\
+\cline{1-1}
+\cline{3-4}
+User2 &  & 1.1-1.3 & 28GB/备份 $\times$ 13 个\\
+\cline{1-1}
+\cline{3-4}
+User3 &  & 0.9-1.1 & 26GB/备份 $\times$ 13 个\\
+\cline{1-1}
+\cline{3-4}
+User4 &  & $\sim$0.9 & 25GB/备份 $\times$ 13 个\\
+\cline{1-1}
+\cline{3-4}
+User5 &  & 0.9-1.0 & 25GB/备份 $\times$ 13 个\\
+\cline{1-1}
+\cline{3-4}
+User6 &  & 0.9-1.1 & 27GB/备份 $\times$ 13 个\\
+\hline
+\end{tabular} 
+\end{table}
+
+表\ref{tab:VM-dataset}总结了VM实验数据集的相关特征信息，其中\#逻辑数据块数 和 \#唯一数据块数表示每个实验快照中逻辑数据块数量和具有唯一性的数据块数量。由于所有的VM映像都具有10GB的固定大小，因此其具有相同数量的逻辑块。。
+
+此数据集是从某大学2014年春季的编程课程中收集的。原始数据集包括为课程中注册的学生提供的大量VM镜像快照，每个快照的大小固定为10GB，每个快照中的数据用固定大小为4KB的数据块通过SHA-1算法计算得到的哈希的列表表示。本文使用6个用户（即User1-User6）的数据，每个用户的数据由13个每周备份组成。
+
 \subsection{MS数据集}
 
-\section{实际系统}
+\begin{table}[!hbt]
+    \caption{MS数据集特征}
+\small
+\label{tab:MS-dataset}
+\renewcommand{\arraystretch}{1.2}
+\vspace{-3pt}
+\centering
+\begin{tabular}{|c|c|c|c|}
+\hline
+\multirow{2}{*}{\bf 类别} & \multicolumn{3}{c|}{\bf 备份中的特征} \\
+\cline{2-4}
+    & \#逻辑数据块数（百万） & \#唯一数据块数（百万） & 近似逻辑大小（GB）\\
+
+\hline
+Win7  & 61.6-61.8 & 61.1-61.3 & 425GB/备份 $\times$ 4 个\\
+\cline{1-4}
+Serv-03 & 10.6-10.7 & 8.4-8.5 & 78GB/备份 $\times$ 4 个\\
+\cline{1-4}
+Serv-08 & $\sim$6.5 & $\sim$3.8 & 48GB/备份 $\times$ 4 个\\
+\cline{1-4}
+Vista-B &  $\sim$7.6 & $\sim$2.0 & 55GB/备份 $\times$ 4 个\\
+\cline{1-4}
+Vista-U &  $\sim$21.0 & $\sim$10.4 & 159GB/备份 $\times$ 4 个\\
+\hline
+\end{tabular}
+\end{table}
+
+表\ref{tab:MS-dataset}总结了MS实验数据集的相关特征信息，其中\#逻辑数据块数 和 \#唯一数据块数表示每个实验快照中逻辑数据块数量和具有唯一性的数据块数量。
+
+此数据集由Microsoft\cite{meyer2012study}收集，并在SNIA\cite{ms}上公布。 原始数据集包含2009年9月5日至10月31日的Windows文件系统快照。每个快照由通过Rabin Fingerprinting\cite{rabin1981fingerprinting}获得的不同平均大小的40位数据块哈希表示。 本文使用以下类别的操作系统快照用于试验：Windows 7（Win7），Microsoft Windows Server 2003（Serv-03），Microsoft Windows Server 2008（Serv-08），Microsoft Windows Vista Business Edition（ Vista-B）和Microsoft Windows Vista Ultimate Edition（Vista-U）。在每个类别中，选择四个快照（这些快照的平均数据块大小为8KB。
+
+\section{实际系统调研}
 \subsection{SDFS}
 
+SDFS\cite{SDFS}是一种分布式、可扩展的文件系统，旨在为应用程序提供具有较强灵活性的内联重复数据删除。该系统有两种部署方法：
+
+\begin{itemize}
+    \item \textbf{单节点配置}：实际运行时将数据存储在本地文件系统中。
+    \item \textbf{多节点配置}：实际运行中将数据存储在远端存储服务商/服务器中。
+\end{itemize}
+
+\subsubsection{系统的整体结构}
+
+\par SDFS系统的整体结构如下所示：
+
+\begin{figure}[!htb]
+    \small
+    \centering
+    \includegraphics[width=11cm]{SDFS-Workflow}
+    \caption{SDFS文件系统的运作流程} 
+    \label{fig:SDFS-Workflow}
+\end{figure}
+
+该系统主要由以下四部分组成，其中Dedup File Engine和Dedup Storage Engine是SDFS系统的主要组件：
+
+\begin{itemize}
+    \item \textbf{Fuse Based File System (Fuse-J)}
+    \item \textbf{Dedup File Engine}
+    \item \textbf{Dedup Storage Engine}
+    \item \textbf{Logic Data Store}
+\end{itemize}
+
+\subsubsection{Dedup File Engine}
+本节将说明Dedup File Engine的工作原理以及相关的系统实现。Dedup File Engine的工作流程如下所示：
+
+\begin{figure}[!htb]
+    \small
+    \centering
+    \includegraphics[width=11cm]{SDFS-DedupFileEngine.eps}
+    \caption{SDFS文件系统的Dedup File Engine运作流程} 
+    \label{fig:SDFS-DedupFileEngine}
+\end{figure}
+
+SDFS将Dedup File Engine通过Java Native Interface（JNI）连接到由FUSE-J驱动的实际文件系统的的卷，使得Dedup File Engine可以通过系统文件系统直接进行文件操作。
+
+\textbf{Fuse-J Java Native Interface}
+
+\begin{itemize}
+    \item 文件统计和高级文件操作是通过获取和设置扩展文件属性（getfattr setfattr）来完成的。
+    \item 每个挂载到SFDS的卷都拥有其独立的的Fuse-J接口和Dedup File Engine实例。
+\end{itemize}
+
+\textbf{Dedup File Channel}
+
+本模块Fuse-J和DedupFile之间用于I/O命令的接口。该接口提供了一些方法（例如获取文件元数据/读取或写入文件）用于获取将进行重复数据删除的文件。
+
+\textbf{Meta Data Store}
+
+在SDFS文件系统中，文件通过两个不同的元数据进行表示，并将两种不同的元数据保存在两个不同的文件中。这两个文件分别为：
+
+\begin{itemize}
+    \item Meta Data Dedup File
+
+    该文件用于存储进行重复数据删除的原始文件的文件属性元数据，包括文件大小、atime、ctime、acls以及指向关联映射文件的链接等。
+
+    \item Mapping File
+
+该文件包含用于重复数据删除的文件的数据块记录列表，其存储了文件中每个数据块在原始文件中的位置、数据块是否具有唯一性、数据块的哈希值以及该数据块是否存储在远程服务器中。
+\end{itemize}
+
+\textbf{DedupFile}
+
+该文件用于存储将要进行重复数据删除的文件的记录，其中的内容是挂载到SDFS文件系统的券中各个文件的哈希与完整文件路径与文件名的映射关系表。
+
+\textbf{WritableCacheBuffer}
+
+本数据结构包含一系列正在读取或写入的数据信息。在I/O活动期间，DedupFile会缓存其中的许多内容。在这部分中，SDFS使用SparseDedupFile类来处理writableCacheBuffer中的数据（即进行文件分块以获得获取逻辑数据块）。
+
+SDFS支持两种数据块分块方法：固定大小的分块方法和Rabin可变大小数据块分块方法。
+
+\textbf{HCService Proxy (HC == HashChunk)}
+
+HCServiceProxy根据哈希的第一个字节（如果设置了多个Dedup Storage Engine）为当前数据块查找到适当的重复数据删除存储引擎。HCServiceProxy通过查询相应的Dedup File Engine以确定当前哈希所对应的数据块是否已存入存储系统（是否是重复的数据块），如果该数据块是重复的，则不进行任何操作，如果当前数据块是具有唯一性的，则将其加入存储系统中进行持久化存储。
+
+\subsubsection{Dedup Storage Engine}
+
+Dedup Storage Engine（DSE）存储、检索和删除所有SDFS分割形成的数据块。重复数据删除存储引擎可以作为SDFS卷（单节点模式）的一部分运行，或在云端单独运行（多节点模式）。Dedup Storage Engine的运作流程如下所示：
+
+\begin{figure}[!htb]
+    \small
+    \centering
+    \includegraphics[width=\textwidth]{SDFS-DedupStorageEngine}
+    \caption{SDFS文件系统的Dedup Storage Engine运作流程} 
+    \label{fig:SDFS-DedupStorageEngine}
+\end{figure}
+
+\begin{enumerate}
+    \item 客户端线程接收$WRITE\_HASH\_CMD$或$WRITE\_COMPRESSED\_CMD$信号并读取哈希和数据。
+    \item 客户端线程将哈希传递给HashChunkService。
+    \item HashChunkService将哈希和数据传递给适当的HashStore。
+    \item HashStore存储哈希并将数据发送到指定的ChunkStore。
+    \item ChunkStore存储数据。
+\end{enumerate}
+
+DES由2个基本组件组成：
+
+\textbf{HashStore}
+
+HashStore用于存储所有数据块的哈希与其对应的逻辑数据的存储位置。
+
+\textbf{ChunkStore}
+
+ChunkStore负责存储和检索与特定哈希相匹配的数据块原始逻辑数据。
+
+\begin{itemize}
+    \item 本地数据块存储
+    \begin{itemize}
+        \item 单文件数据块存储：将所有数据块写入一个文件中（文件大小与数据块总量有关）。
+        \item 基于文件的数据块存储：将所有数据块依次写入固定大小的文件中。
+    \end{itemize}
+    \item 远程数据块存储
+    \begin{itemize}
+        \item Amazon S3
+        \item Microsoft Azure
+        \item Google Cloud
+    \end{itemize}
+\end{itemize}
+
+\subsubsection{SDFS文件系统调研总结}
+
+SDFS文件系统提供了商业使用级别的（加密）重复数据删除，但其中重复数据删除工作均先进行文件内的重复数据删除，再进行文件间的重复数据删除。其中的数据块处理顺序随机，不会发生数据块逻辑顺序信息的泄漏，因此可以防范本文提出的第一种攻击方法（基于分布的频率分析攻击方法）。但本文提出的第二种攻击手段在SDFS中仍然可以发挥作用。
+
 \subsection{Destor}
+
+Destor\cite{fu2015design}是重复数据删除的评估平台，其包含了大量重复数据删除中常用的方法，可以用于常用重复数据删除的方法测试与应用效果模拟评估。系统原型中包含的主要特征有：
+
+\begin{itemize}
+    \item 基于容器的数据块存储。
+    \item 数据块级的管道通信。
+    \item 三种重复数据删除方案：
+    \begin{itemize}
+        \item 基于固定大小的数据块分块的重复数据删除。
+        \item 基于内容定义数据块分块方法的重复数据删除。
+        \item 近似的文件级重复数据删除。
+    \end{itemize}
+    \item 多种文件重写算法：CFL、CBR、CAP和HAR等。
+    \item 多种文件还原算法：LRU、最优替换算法和前滚组装。
+\end{itemize}
+
+\subsubsection{Destor系统原型调研总结}
+
+Destor不同与商业化的SDFS文件系统，该系统原型是重复数据删除领域中著名的重复数据删除工具集合与样例。系统中的数据块处理是按照原有逻辑明文数据块的逻辑顺序进行的，因此会受到本文提出的两种攻击方法的威胁。
+
+\section{本章小结}
+本章介绍了本文用于评估攻击效果的三种真实世界数据集的来源和基本信息，以及两种现有重复数据删除系统的相关调研工作。

### 2019-01-03 paper/Experiments.tex
ING | complete chapter 4 and begin chapter 5 before workflow
ING | Clustering Attack
ING | last part - exp - figure fix

@@
 
-In this section, we present the trace-driven evaluation results to demonstrate
-the severity of our proposed frequency analysis attacks against encrypted
-deduplication.
+在本章中，将给出基于真实世界数据集的评估结果，以证明本文针对加密重复数据删除提出的频率分析攻击方法的严重性与有效性。
 
@@
 
-\begin{table}[!t]
-    \caption{Characteristics of experimental datasets.}
-\small
-\label{tab:dataset}
-\renewcommand{\arraystretch}{1.2}
-\vspace{-3pt}
-\centering
-\begin{tabular}{|c|c|c|c|}
-\hline
- \multirow{2}{*}{\bf Dataset} & \multirow{2}{*}{\bf Category} & \multicolumn{2}{c|}{\bf Characteristics in Each Snapshot} \\
-\cline{3-4}
-    & &  \#Logical (Million) & \#Unique (Million) \\
-\hline
-    \multirow{6}{*}{FSL} & User004  & 1.0-1.3 & 0.7-0.9\\
- \cline{2-4}
-              & User007 &  3.5-5.2 & 2.3-3.6 \\
- \cline{2-4}
-              & User012 &  25.0-26.4 & 8.9-9.7 \\
-\cline{2-4}
-              & User013 &  1.8-5.7 & 1.2-4.2 \\
-\cline{2-4}
-              & User015 &  13.4-20.5 & 9.0-11.0 \\
-\cline{2-4}
-              & User028 &  6.0-10.3 & 3.5-6.8 \\
-\hline
-\hline
-    \multirow{4}{*}{MS} & Win7  & 61.6-61.8 & 61.1-61.3\\
-\cline{2-4}
-              & Serv-03 & 10.6-10.7 & 8.4-8.5\\
-\cline{2-4}
-              & Serv-08 & $\sim$6.5 & $\sim$3.8 \\
-\cline{2-4}
-              & Vista-B &  $\sim$7.6 & $\sim$2.0\\
-\cline{2-4}
-              & Vista-U &  $\sim$21.0 & $\sim$10.4 \\
-\hline
-\hline
+本文所使用的真实世界数据集不包数据的实际内容，因此我们模仿基于块哈希的对抗性知识。具体来说，我们在一些快照中使用有序的数据块哈希列表作为辅助信息$\mathbf{A}$和基本事实$\mathbf{M}$。为了模拟加密，我们在$\mathbf{M}$中的每个原始块散列（表示明文）上应用额外的散列函数，并将结果截断为特定于已使用数据集的约定位数。截断的结果模仿$\mathbf{C}$中的密文。对于每个推断的密文 - 明文对$(C,M)$，我们通过在$M$上应用相同的模拟加密并将结果与​​$C$进行比较来验证其正确性。请注意，基于聚类的攻击可以在段级别操作，并推断出密文 - 明文段对$(S_\mathbf{C},S_\mathbf {A})$。在这种情况下，我们检查$(S_\mathbf {C},S_\mathbf{A})$，检查$S_\mathbf{C}$中的每个密文是否完全映射到$S_\mathbf{A}$中的每个明文。
 
-    \multirow{6}{*}{VM} & User1  &  \multirow{6}{*}{2.6} & $\sim$0.9 \\
-\cline{2-2}
-\cline{4-4}
-              & User2 &  & 1.1-1.3 \\
-\cline{2-2}
-\cline{4-4}
-              & User3 &  & 0.9-1.1 \\
-\cline{2-2}
-\cline{4-4}
-              & User4 &  & $\sim$0.9 \\
-\cline{2-2}
-\cline{4-4}
-              & User5 &  & 0.9-1.0 \\
-\cline{2-2}
-\cline{4-4}
-              & User6 &  & 0.9-1.1 \\
-\hline
-\end{tabular}
-\medskip
+Our datasets do not contain actual content, so we mimic the adversarial knowledge based on chunk hashes.
+Specifically, we use the ordered lists of chunk hashes in some snapshots as the auxiliary information $\mathbf{A}$ and the ground truth $\mathbf{M}$, respectively.
+To simulate encryption, we apply an additional hash function over each original chunk hash (that represents a plaintext) in $\mathbf{M}$, and truncate the result into an agreed number of bits specific to the used dataset.
+The truncated result mimics a ciphertext in $\mathbf{C}$.
+For each inferred ciphertext-plaintext pair $(C, M)$, we verify its correctness by applying the same simulated encryption on $M$ and comparing the result with $C$.
+Note that the clustering-based attack can operate at the segment level, and infer the ciphertext-plaintext segment pair $(S_\mathbf{C}, S_\mathbf{A})$.
+In this case, we check $(S_\mathbf{C}, S_\mathbf{A})$ by examining each ciphertext in $S_\mathbf{C}$ is exactly mapped from each plaintext in $S_\mathbf{A}$.
 
-\raggedright
-    The notations \#Logical and \#Unique denote the total number of logical and unique chunks in each experimental snapshot, respectively. 
-    % All VM images have a fixed size of 10GB and hence the same number of logical chunks.
-\end{table}
-
-%\begin{table}[!t]
-%\small
-%\caption{Experimental datasets.}
-%\label{tab:dataset}
-%\renewcommand{\arraystretch}{1.2}
-%\vspace{-3pt}
-%\centering
-%\begin{tabular}{|c|c|c|}
-%\hline
-%{\bf Dataset} & {\bf Category} & {\bf Approximate Logical Size} \\
-%\hline
-%\hline
-%%\multirow{2}{*}{FSL} & Physical  & 431.9GB  & 659.3GB & 584.3GB \\
-%	\multirow{6}{*}{FSL} & User004  & 10GB/backup $\times$ 14 backups \\
-%\cline{2-3}
-%			  & User007 & 39GB/backup $\times$ 14 backups \\
-%\cline{2-3}
-%			  & User012 & 244GB/backup $\times$ 14 backups \\
-%\cline{2-3}
-%			  & User013 & 22GB/backup $\times$ 14 backups\\
-%\cline{2-3}
-%			  & User015 & 158GB/backup $\times$ 14 backups\\
-%\cline{2-3}
-%			  & User028 & 77GB/backup $\times$ 14 backups\\
-%\hline
-%\hline
-%\multirow{4}{*}{MS} & WIN7  & 425GB/snapshot $\times$ 4 snapshots \\
-%\cline{2-3}
-%			  & Serv-03 & 78GB/snapshot $\times$ 4 snapshots \\
-%\cline{2-3}
-%			  & Serv-08 & 48GB/snapshot $\times$ 4 snapshots \\
-%\cline{2-3}
-%			  & Vista-B & 55GB/snapshot $\times$ 4 snapshots \\
-%\cline{2-3}
-%			  & Vista-U & 159GB/snapshot $\times$ 4 snapshots \\
-
-%\hline
-%\hline
-
-%\multirow{6}{*}{VM} & User1  & 25GB/backup $\times$ 13 backups \\
-%\cline{2-3}
-%			  & User2 & 28GB/backup $\times$ 13 backups \\
-%\cline{2-3}
-%			  & User3 & 26GB/backup $\times$ 13 backups \\
-%\cline{2-3}
-%			  & User4 & 25GB/backup $\times$ 13 backups\\
-%\cline{2-3}
-%			  & User5 & 25GB/backup $\times$ 13 backups\\
-%\cline{2-3}
-%			  & User6 & 27GB/backup $\times$ 13 backups\\
-
-%% \multicolumn{2}{|c|}{\bf Storage saving} & 98.6\% & 98.3\% \\
-%\hline
-%\end{tabular}
-%\end{table}
-We evaluate our attacks using the following real-world datasets, whose
-characteristics are summarized in Table~\ref{tab:dataset}. 
-% Table~\ref{tab:dataset} summarizes the characteristics of the experimental datasets used in our experiments. 
-% We evaluate our attacks using the following datasets. 
-% investigate the security implications of the leakages (see \S\ref{sec:background}) by means of simulated attacks,
-
-\begin{itemize}[leftmargin=*]
-\item 
-\textbf{FSL:} This dataset is collected by the File systems and
-        Storage Lab (FSL) at Stony Brook University \cite{sun16,FSL14,sun18}. We focus on
-the {\em fslhomes} snapshots, each of which includes an ordered list of 48-bit
-chunk hashes that are produced by variable-size chunking under an average size
-of 8KB, as well as the corresponding metadata information (e.g., chunk size,
-file name extension, etc). We pick the snapshots from January 22 to May 21 in
-2013, and select six users (i.e., User004, User007, User012, User013, User015,
-and User028) that have the complete daily snapshots over the whole duration.
-We collect these snapshots on a weekly basis, and hence form 14 weekly full
-backups for each user.  
-\item 
-\textbf{MS:} This dataset is collected by Microsoft
-\cite{meyer11} and publicized on SNIA \cite{ms}. The original dataset contains
-the Windows file system snapshots that span from September 5 to October 31,
-2009. Each snapshot is represented by the 40-bit chunk hashes under different
-average sizes obtained from Rabin fingerprinting \cite{rabin81}.  We focus on
-the snapshots that have been installed with the operating systems in the
-following categories: Windows 7 (Win7), Microsoft Windows Server 2003
-(Serv-03), Microsoft Windows Server 2008 (Serv-08), Microsoft Windows Vista
-Business Edition (Vista-B), and Microsoft Windows Vista Ultimate Edition
-(Vista-U). In each category, we pick four snapshots, each of which is
-configured with the average chunk size of 8KB.   
-\item 
-\textbf{VM:} This dataset is collected from a university programming course in
-Spring 2014. The original dataset includes a number of VM image snapshots for
-the students enrolled in the course, and each snapshot has a fixed size of
-10GB and is represented by the ordered list of SHA-1 hashes of 4KB fixed-size
-chunks. We focus on 6 users (i.e., User1-User6) and extract their snapshots
-into 13 weekly backups.  
-%Prior studies \cite{qin17, li15} have used some variants of the dataset for
-%different evaluation purposes, and we aim to validate the severity of the
-%clustering-based attack against VM disk images.   
-\end{itemize}
-
-Our datasets do not contain actual content, so we mimic the adversarial
-knowledge based on chunk hashes. Specifically, we use the ordered lists of
-chunk hashes in some snapshots as the auxiliary information $\mathbf{A}$ and
-the ground truth $\mathbf{M}$, respectively. To simulate encryption, we apply
-an additional hash function over each original chunk hash (that represents a
-plaintext) in $\mathbf{M}$, and truncate the result into an agreed number of
-bits specific to the used dataset. The truncated result mimics a ciphertext in
-$\mathbf{C}$. For each inferred ciphertext-plaintext pair $(C, M)$, we verify
-its correctness by applying the same simulated encryption on $M$ and comparing
-the result with $C$. Note that the clustering-based attack can operate at the
-segment level, and infer the ciphertext-plaintext segment pair $(S_\mathbf{C},
-S_\mathbf{A})$.  In this case, we check $(S_\mathbf{C}, S_\mathbf{A})$ by
-examining each ciphertext in $S_\mathbf{C}$ is exactly mapped from each
-plaintext in $S_\mathbf{A}$.
-
-% , although we cannot recover each chunk in the real attack.   
-% We count the leakage (see \S\ref{sec:threat}) of each ciphertext chunk, and use it for our inference attacks.  
-% MD5 on each hash (that represents a plaintext) in $\mathbf{M}$, and truncate the resulting hash into an agreed number of bits (e.g., 48-bit for FSL, 40-bit for MS, and 160-bit for VM).
-
-We measure the severity of the attacks by the inference rate and the inference
-precision (see Section~\ref{sec:threat}).
+We measure the severity of the attacks by the inference rate and the inference precision (see Section~\ref{sec:threat}).
 
@@
 
-\begin{figure*}[t]
+\begin{figure}[!htbp]
     \centering
-    \begin{tabular}{p{.31\textwidth}p{.31\textwidth}p{.31\textwidth}}
-        \multicolumn{3}{c}{\includegraphics[width=.7\textwidth]{pic/legend-fsl-line.pdf}} \smallskip \\
-        \includegraphics[width=.3\textwidth]{pic/distribution-impact-u.pdf} &
-        \includegraphics[width=.3\textwidth]{pic/distribution-impact-r.pdf} &
-	    \includegraphics[width=.3\textwidth]{pic/distribution-impact-t.pdf} \medskip \\
-        {\footnotesize 
+    \begin{tabular}{p{.48\linewidth}p{.48\linewidth}}
+        \multicolumn{2}{c}{\includegraphics[width=.7\textwidth]{legend-fsl-line.pdf}}  \\
+        \includegraphics[width=\linewidth]{dis-impact-u-rate.pdf} &
+        \includegraphics[width=\linewidth]{dis-impact-u-accuracy.pdf}\\
+    \end{tabular}
+    \caption{基于分布的攻击实验1-参数$u$的变化对推理结果的影响（$r = 0$；$t \rightarrow \infty$）}
+    \label{fig:distribution-impact-u}
+\end{figure}
+
+\begin{figure}[!htbp]
     \centering
-        (a) Impact of $u$: $r$ = 0; $t \rightarrow \infty$
-        } &
-        {\footnotesize
-        (b) Impact of $r$: $u$ = 128 for User004, User013 and User015, and $u$ = 256 for User007, User012 and User028; $t \rightarrow \infty$
-        } &
-        {\footnotesize
-        (c) Impact of $t$: $u$ = 128 for User004, User013 and User015, and $u$ = 256 for User007, User012 and User028; $r$ = 10
-        } \\
+    \begin{tabular}{p{.48\linewidth}p{.48\linewidth}}
+        \multicolumn{2}{c}{\includegraphics[width=.7\textwidth]{legend-fsl-line.pdf}}  \\
+        \includegraphics[width=\linewidth]{dis-impact-r-rate.pdf} &
+        \includegraphics[width=\linewidth]{dis-impact-r-accuracy.pdf}\\
     \end{tabular}
-    \caption{Experiment 1 (Impact of parameters): impact of $(u, r, t)$ in distribution-based attack.}
-    \label{fig:distribution-impact}
-\end{figure*}
+    \caption{基于分布的攻击实验1-参数$r$的变化对推理结果的影响（User004、User013和User015中$u = 128$，User007、User012和User028中$u = 256$；$t \rightarrow \infty$）}
+    \label{fig:distribution-impact-r}
+\end{figure}
+
+\begin{figure}[!htbp]
+    \centering
+    \begin{tabular}{p{.48\linewidth}p{.48\linewidth}}
+        \multicolumn{2}{c}{\includegraphics[width=.7\textwidth]{legend-fsl-line.pdf}}  \\
+        \includegraphics[width=\linewidth]{dis-impact-t-rate.pdf} &
+        \includegraphics[width=\linewidth]{dis-impact-t-accuracy.pdf}\\
+    \end{tabular}
+    \caption{基于分布的攻击实验1-参数$t$的变化对推理结果的影响（User004、User013和User015中$u = 128$，User007、User012和User028中$u = 256$；$r = 10$）}
+    \label{fig:distribution-impact-t}
+\end{figure}
 
 \subsection{Experiment 1 (Impact of parameters):}
-We evaluate the impact of the parameters $(u, r, t)$ in the distribution-based
-attack. We drive our evaluation using the FSL dataset, and use the 12th weekly
-backup of each user as the auxiliary information to infer original plaintexts
-in corresponding 14th weekly backup.  We configure $t \rightarrow \infty$ and $r$ = 0 to
-evaluate the impact of $u$ (in this case, the distribution-based attack
-reduces to the locality-based attack \cite{li17}). Our rationale is to avoid
-the disturbances by other parameters.
+We evaluate the impact of the parameters $(u, r, t)$ in the distribution-based attack.
+We drive our evaluation using the FSL dataset, and use the 12th weekly backup of each user as the auxiliary information to infer original plaintexts in corresponding 14th weekly backup.
+We configure $t \rightarrow \infty$ and $r$ = 0 to evaluate the impact of $u$ (in this case, the distribution-based attack reduces to the locality-based attack \cite{li17}).
+Our rationale is to avoid the disturbances by other parameters.
 
-Figure~\ref{fig:distribution-impact}(a) shows the impact of $u$,
-when we vary $u$ from 2 to 512. Regarding inference rate, we have the same
-observation as the prior work \cite{li17}. Specifically, the inference rates
-first increase with $u$, since the attack can infer more ciphertext-plaintext
-pairs. After hitting the maximum values (e.g., 13.9\% for User004, 13.6\% for
-User007, 1.4\% for User012, 0.5\% for User013, 0.7\% for User015, and 6.1\%
-for User028), they decrease.  The reason is that the underlying frequency
-analysis introduces a large number of false positives that compromise the
-inferences over corresponding neighbors.
+Figure~\ref{fig:distribution-impact}(a) shows the impact of $u$, when we vary $u$ from 2 to 512.
+Regarding inference rate, we have the same observation as the prior work \cite{li17}.
+Specifically, the inference rates first increase with $u$, since the attack can infer more ciphertext-plaintext pairs.
+After hitting the maximum values (e.g., 13.9\% for User004, 13.6\% for User007, 1.4\% for User012, 0.5\% for User013, 0.7\% for User015, and 6.1\% for User028), they decrease.
+The reason is that the underlying frequency analysis introduces a large number of false positives that compromise the inferences over corresponding neighbors.
 
-The prior work \cite{li17} does not report the inference precision about the
-attack. We observe that the inference precisions for all users are at a
-fairly low level (e.g., less than 40\%), except the case of $u = 2$ for
-User028 that does not introduce any false positives. On the other hand, the
-inference rate in the special case is about 0.0001\%, meaning that the attack
-only infers a few ciphertext-plaintext pairs. In addition, as $u$ increases,
-the inference precisions decrease slightly. For example, when $u$ increases
-from 2 to 512, the inference precision of User004 drops from 30.7\% to 12.8\%.
+The prior work \cite{li17} does not report the inference precision about the attack.
+We observe that the inference precisions for all users are at a fairly low level (e.g., less than 40\%), except the case of $u = 2$ for User028 that does not introduce any false positives.
+On the other hand, the inference rate in the special case is about 0.0001\%, meaning that the attack only infers a few ciphertext-plaintext pairs.
+In addition, as $u$ increases,the inference precisions decrease slightly.
+For example, when $u$ increases from 2 to 512, the inference precision of User004 drops from 30.7\% to 12.8\%.
 
-{\bf Observation (1) --} {\em A relatively larger $u$ increases the inference
-rate, yet it decreases the inference precision (i.e., more false positives are
-introduced). }
+{\bf Observation (1) --} {\em A relatively larger $u$ increases the inference rate, yet it decreases the inference precision (i.e., more false positives are introduced). }
 
-Informed by the impact of $u$, we set $u$ at 128 for User004, User013 and
-User015, and at 256 for User007, User012 and User028, respectively, in order
-to evaluate the impact of $r$ and $t$. 
-% {\bf Note that the configuration
-% exceeds the best one that leads to the highest inference rate. PC: I don't
-% quite understand???} 
-Our rationale is to increase the coverage of inferred ciphertext-plaintext
-pairs, while we use $r$ and $t$ to filter possibly false positives.
+Informed by the impact of $u$, we set $u$ at 128 for User004, User013 and User015, and at 256 for User007, User012 and User028, respectively, in order to evaluate the impact of $r$ and $t$.
+Our rationale is to increase the coverage of inferred ciphertext-plaintext pairs, while we use $r$ and $t$ to filter possibly false positives.
 
-We first configure $t \rightarrow \infty$ and evaluate the impact of $r$. Figure~\ref{fig:distribution-impact}(b) shows the results. We observe that the
-inference rates of majority users increase with $r$. For example, when we vary
-$r$ from 0 to 16, the inference rates grow from 9.5\% to 16.0\%, from 10.0\%
-to 13.0\%, from 0.5\% to 0.7\%, and from 4.7\% to 5.6\% for User004, User007,
-User013, and User028, respectively. The reason is that the distribution-based
-attack addresses disturbances to frequency ranking, and infer more correct
-ciphertext-plaintext  pairs. On the other hand, the inference rates decrease
-slightly from 1.3\% to 0.8\% and from 0.6\% to 0.4\% for User012 and User015,
-respectively. The reason is that they examine a large range of plaintexts and
-may introduce more false positives. In addition, the inference precisions for
-all users are  at a low level (e.g., less than 45\%), and have similar
-tendencies with corresponding inference rates.
+We first configure $t \rightarrow \infty$ and evaluate the impact of $r$.
+Figure~\ref{fig:distribution-impact}(b) shows the results.
+We observe that the inference rates of majority users increase with $r$.
+For example, when we vary $r$ from 0 to 16, the inference rates grow from 9.5\% to 16.0\%, from 10.0\% to 13.0\%, from 0.5\% to 0.7\%, and from 4.7\% to 5.6\% for User004, User007, User013, and User028, respectively.
+The reason is that the distribution-based attack addresses disturbances to frequency ranking, and infer more correct ciphertext-plaintext  pairs.
+On the other hand, the inference rates decrease slightly from 1.3\% to 0.8\% and from 0.6\% to 0.4\% for User012 and User015, respectively.
+The reason is that they examine a large range of plaintexts and may introduce more false positives.
+In addition, the inference precisions for all users are  at a low level (e.g., less than 45\%), and have similar tendencies with corresponding inference rates.
 
-{\bf Observation (2) --} {\em A larger $r$ provides more opportunities of
-identifying correct ciphertext-plaintext pairs, yet it also increases the
-probability of having false positives.}
+{\bf Observation (2) --} {\em A larger $r$ provides more opportunities of identifying correct ciphertext-plaintext pairs, yet it also increases the probability of having false positives.}
 
 Then, we fix $r$ = 10 and evaluate the impact of $t$.
-Figure~\ref{fig:distribution-impact}(c) shows the results. When $t$ is small
-(e.g., less than 0.5), we observe that the attack misjudges and filters a
-significant number of ciphertext-plaintext pairs, even they are correct. This
-introduces {\em false negatives} that reduce the inference rate. As $t$
-increases, the number of false negatives decreases.  When $t$ = 1.5, the
-inference rates hit the maximum values at 21.2\%, 18.2\%, 10.4\%, 1.2\%,
-1.2\%, and 13.5\% for User004, User007, User012, User013, User015, and
-User028, respectively. When $t$ further increases to 2, the corresponding
-inference rates drop to 20.5\%, 17.1\%, 8.3\%, 1.2\%, 1.0\%, and 11.2\%,
-respectively. The reason is that if $t$ is too large, it cannot filter false
-positives effectively. For the same reason, the inference precisions for all
-users decrease with $t$.  
-% The inference rates first  increase with $t$, since the number of false negatives (i.e., misjudge some correctly inferred ciphertext-plaintext pairs in filtering) are reduced.
-
-% implies that the distribution-based attack  returns more incorrect ciphertext-plaintext chunk pairs, which affects attack severity.
+Figure~\ref{fig:distribution-impact}(c) shows the results.
+When $t$ is small (e.g., less than 0.5), we observe that the attack misjudges and filters a significant number of ciphertext-plaintext pairs, even they are correct.
+This introduces {\em false negatives} that reduce the inference rate.
+As $t$ increases, the number of false negatives decreases.
+When $t$ = 1.5, the inference rates hit the maximum values at 21.2\%, 18.2\%, 10.4\%, 1.2\%, 1.2\%, and 13.5\% for User004, User007, User012, User013, User015, and User028, respectively.
+When $t$ further increases to 2, the corresponding inference rates drop to 20.5\%, 17.1\%, 8.3\%, 1.2\%, 1.0\%, and 11.2\%, respectively.
+The reason is that if $t$ is too large, it cannot filter false positives effectively.
+For the same reason, the inference precisions for all users decrease with $t$.
 
@@
 \subsection{Experiment 2 (Comparison with prior attack):}
-We compare the severity of the distribution-based attack with that of the
-locality-based attack \cite{li17}. In addition to using the FSL dataset like
-Experiment~1, we include the MS dataset for cross-dataset validation.
-Specifically, for each MS category, we choose two snapshots at a time, use one
-to infer the other, and evaluate the average inference rate and precision.
+We compare the severity of the distribution-based attack with that of the locality-based attack \cite{li17}.
+In addition to using the FSL dataset like Experiment~1, we include the MS dataset for cross-dataset validation.
+Specifically, for each MS category, we choose two snapshots at a time, use one to infer the other, and evaluate the average inference rate and precision.
 
 We consider the following attack instances for comparison.
-%
+
 \begin{itemize}[leftmargin=*]
 \item 
-$\tt Baseline$: We re-implement the locality-based attack based on the
-parameter configuration suggested in \cite{li17}. Specifically, it infers 5
-most frequent ciphertext-plaintext pairs in the first invocation (i.e., to
-initialize a set of ciphertext-plaintext pairs for iteration) of frequency
-analysis, and 30 in each following invocation (i.e., to iteratively infer ciphertext-plaintext pairs from 
- neighbors).  
+$\tt Baseline$: We re-implement the locality-based attack based on the parameter configuration suggested in \cite{li17}.
+Specifically, it infers 5 most frequent ciphertext-plaintext pairs in the first invocation (i.e., to initialize a set of ciphertext-plaintext pairs for iteration) of frequency analysis, and 30 in each following invocation (i.e., to iteratively infer ciphertext-plaintext pairs from neighbors).
 \item 
-$\tt Distribution$ and $\tt Distribution^S$: We consider two attack instances
-of the distribution-based attack, denoted by $\tt Distribution^S$ and ${\tt
-Distribution}$, which operate with and without size information,
-        respectively (i.e., the superscript $\tt S$ indicates that the attack instance operates with size information). 
-        We configure $\tt Distribution^S$ and ${\tt Distribution}$
-under the same configuration of  ${\tt Baseline}$. In addition, we choose
-$r$ and $t$ in both  $\tt Distribution^S$ and ${\tt Distribution}$ in the following way: for the FSL dataset, we fix $r$ = 10 for
-all users, and individually set $t$ = 1.5, 1.2, 1, 1, 0.7, and 0.9 for
-User004, User007, User012, User013, User015, and User028, respectively; for
-the MS dataset, we also fix $r$ = 10 for all categories, and set $t$ = 2 for
-Win7 and Serv-08, and $t$ = 1.6 for Vista-U, Serv-03, and Vista-B, respectively.
+$\tt Distribution$ and $\tt Distribution^S$: We consider two attack instances of the distribution-based attack, denoted by $\tt Distribution^S$ and ${\tt Distribution}$, which operate with and without size information, respectively (i.e., the superscript $\tt S$ indicates that the attack instance operates with size information).
+We configure $\tt Distribution^S$ and ${\tt Distribution}$ under the same configuration of  ${\tt Baseline}$.
+In addition, we choose $r$ and $t$ in both  $\tt Distribution^S$ and ${\tt Distribution}$ in the following way: for the FSL dataset, we fix $r$ = 10 for all users, and individually set $t$ = 1.5, 1.2, 1, 1, 0.7, and 0.9 for User004, User007, User012, User013, User015, and User028, respectively; for the MS dataset, we also fix $r$ = 10 for all categories, and set $t$ = 2 for Win7 and Serv-08, and $t$ = 1.6 for Vista-U, Serv-03, and Vista-B, respectively.
 This is informed by our tests for optimal configurations of the datasets.
 \item 
-$\tt Distribution$-$\tt o$ and $\tt Distribution^S$-$\tt o$:
-We consider two additional distribution-based attack instances, denoted by $\tt Distribution$-$\tt o$
-and $\tt Distribution^S$-$\tt o$, which apply the same configurations for $r$ and $t$ as with $\tt Distribution$ and $\tt
-Distribution^S$, and further use larger $u$ to increase the
-coverage of inferred ciphertext-plaintext pairs.  
-        Specifically, we configure $u$ in $\tt Distribution$-$\tt o$
-and $\tt Distribution^S$-$\tt o$ in the following way:  
-        for the FSL
-dataset, we apply the same configuration of $u$ in Experiment~1; for the MS
-dataset, we set $u$ = 128 for Win7, and $u$ = 30 for Serv-03, Serv-08,
-Vista-B, and Vista-U. 
-        % Our rationale is to increase
-% the inference rate, while we expect  this only leads to a slight
-% degradation of the inference precision since the distribution-based attack
-% filters a large fraction of false positives. 
+$\tt Distribution$-$\tt o$ and $\tt Distribution^S$-$\tt o$: We consider two additional distribution-based attack instances, denoted by $\tt Distribution$-$\tt o$ and $\tt Distribution^S$-$\tt o$, which apply the same configurations for $r$ and $t$ as with $\tt Distribution$ and $\tt Distribution^S$, and further use larger $u$ to increase the coverage of inferred ciphertext-plaintext pairs.
+Specifically, we configure $u$ in $\tt Distribution$-$\tt o$ and $\tt Distribution^S$-$\tt o$ in the following way:  for the FSL dataset, we apply the same configuration of $u$ in Experiment~1; for the MS dataset, we set $u$ = 128 for Win7, and $u$ = 30 for Serv-03, Serv-08, Vista-B, and Vista-U.
+
 \end{itemize}
@@
     \centering
-    \begin{tabular}{c@{\hskip 2em}c}
-        \multicolumn{2}{c}{\includegraphics[width=.7\textwidth]{pic/legend-fsl-bar.pdf}} \smallskip \\
-        \includegraphics[height=2.1in]{pic/distribution-comparison-fsl.pdf} &
-        \includegraphics[height=2.1in]{pic/distribution-comparison-ms.pdf} \medskip \\
-        {\footnotesize 
-        (a) FSL dataset 
-        } &
-        {\footnotesize
-        (b) MS dataset 
-        } \\
+    \begin{tabular}{c}
+        \includegraphics[width=.7\textwidth]{pic/legend-fsl-bar.pdf}\\
+        \includegraphics[width=.7\textwidth]{pic/distribution-comparison-fsl.pdf} 
     \end{tabular}
-    \caption{Experiment 2 (Comparison with prior attack): comparison of attack severity for distribution-based attack and locality-based attack.}
+    \caption{Experiment 2 FSL dataset  (Comparison with prior attack): comparison of attack severity for distribution-based attack and locality-based attack.}
     \label{fig:distribution-comparison}
@@
 
-% \begin{itemize}[leftmargin=*]
-	% \item {\em Distribution-I:} We configure our proposed distribution-based attack with the {\em same} configuration of the baseline above.
-Informed by Experiment 3, we further choose the distribution-based ranking parameters in the following way: for the FSL dataset, we fix $r$ = 10 for all users, and individually set $t$ = 1.5, 1.2, 1, 1, 0.7, and 0.9 for User004, User007, User012, User013, User015, and User028; for the MS dataset, we fix $r$ = 10 for all categories, and configure $t$ as 2 for Win7 and Serv-08 and as 1.6 for Vista-U, Serv-03, and Vista-B, respectively.
-
-	% \item {\em Distribution-II:} We configure our proposed distribution-based attack with the same ranking configuration of distribution-I, while building on a larger $u$ to infer more chunk pairs.
-The rationale is to increase inference rate, while we expect the inference precision is degraded slightly as the attack can filter out unreasonable inferences.
-Specifically, for the FSL dataset, we set $u$ = 128 for User004, User013 and User015, and $u$ = 256 for User007, User012 and User028, respectively; for the MS dataset, we set $u$ = 128 for Win7, and $u$ = 30 for Serv-03, Serv-08, Vista-B, and Vista-U, respectively.
-% \end{itemize}
+\begin{figure*}[t]
+    \centering
+    \begin{tabular}{c}
+        \includegraphics[width=.7\textwidth]{pic/legend-fsl-bar.pdf}\\
+        \includegraphics[width=.7\textwidth]{pic/distribution-comparison-ms.pdf}\\
+    \end{tabular}
+    \caption{Experiment 2 MS dataset (Comparison with prior attack): comparison of attack severity for distribution-based attack and locality-based attack.}
+    \label{fig:distribution-comparison}
+\end{figure*}
 
@@
     \centering
-    \begin{tabular}{c@{\hskip 2em}c}
-        \multicolumn{2}{c}{\includegraphics[width=.25\textwidth]{pic/legend-effectiveness.pdf}} \smallskip \\
-        \includegraphics[height=2.2in]{pic/distribution-effectiveness-wo-size.pdf} &
-	\includegraphics[height=2.2in]{pic/distribution-effectiveness-w-size.pdf} \medskip \\
-        {\footnotesize 
-        (a) Distribution-based attack without size information  
-        } &
-        {\footnotesize
-        (b) Distribution-based attack with size information 
-        } \\
+    \begin{tabular}{c}
+        \includegraphics[width=.35\textwidth]{pic/legend-effectiveness.pdf}\\
+        \includegraphics[width=.7\textwidth]{pic/distribution-effectiveness-wo-size.pdf}
     \end{tabular}
-	\caption{Experiment 3 (Attack effectiveness): severity of distribution-based attack in FSL dataset.}
+	\caption{Experiment 3 Distribution-based attack without size information  (Attack effectiveness): severity of distribution-based attack in FSL dataset.}
+	\label{fig:experiment-distribution-effectiveness}
+\end{figure*}
+
+\begin{figure*}[t]
+     \centering
+    \centering
+    \begin{tabular}{c}
+        \includegraphics[width=.35\textwidth]{pic/legend-effectiveness.pdf}\\
+        \includegraphics[width=.7\textwidth]{pic/distribution-effectiveness-w-size.pdf}
+    \end{tabular}
+	\caption{Experiment 3 Distribution-based attack with size information (Attack effectiveness): severity of distribution-based attack in FSL dataset.}
 	\label{fig:experiment-distribution-effectiveness}
@@
 
-We examine the security implication of the clustering-based attack using the
-VM dataset. Specifically, we use the 11th  backup of each VM user  to infer original content in corresponding 13th VM
-backup. Since the VM dataset does not contain any metadata, we count the raw
-inference rate based on the  whole data content in each VM snapshot.
-Note that we filter all zero chunks in the count of raw inference rate,
-because they occupy a large fraction in VM disk images \cite{jin09}.
+We examine the security implication of the clustering-based attack using the VM dataset.
+Specifically, we use the 11th  backup of each VM user  to infer original content in corresponding 13th VM backup.
+Since the VM dataset does not contain any metadata, we count the raw inference rate based on the  whole data content in each VM snapshot.
+Note that we filter all zero chunks in the count of raw inference rate, because they occupy a large fraction in VM disk images \cite{jin09}.
 

### 2019-01-03 paper/RelatedWork.tex
ING | last part - exp - figure fix

@@
 
-\noindent
-{\bf MLE instantiations:}  
-Recall from Section~\ref{sec:background} that MLE \cite{bellare13a} formalizes the
-cryptographic foundation of encrypted deduplication.  The first published MLE
-instantiation is convergent encryption (CE) \cite{douceur02}, which uses the
-cryptographic hash of a plaintext and its corresponding ciphertext as the
-MLE key and the tag, respectively.  Other CE variants include: hash convergent
-encryption (HCE) \cite{bellare13a}, which derives the tag from the plaintext
-while still using the hash of the plaintext as the MLE key; random convergent
-encryption (RCE) \cite{bellare13a}, which encrypts a plaintext with a fresh
-random key to form a non-deterministic ciphertext, protects the random key by
-the MLE key derived from the hash of the plaintext, and attaches a
-deterministic tag derived from the plaintext for duplicate checks; and
-convergent dispersal (CD) \cite{li15}, which extends CE to secret sharing by
-using the cryptographic hash of a plaintext as the random seed of a secret
-sharing algorithm.  Since all the above instantiations derive MLE keys and/or
-tags from the plaintexts {\em only}, they are vulnerable to the offline
-brute-force attack \cite{bellare13b} if the plaintext is {\em predictable}
-(i.e., the number of all possible plaintexts is limited) , as an adversary can
-exhaustively derive the MLE keys and tags from all possible plaintexts and
-check if any plaintext is encrypted to a target ciphertext (in CE, HCE, and
-CD) or mapped to a target tag (in RCE).  The brute-force attack has been
-demonstrated to learn file information \cite{ce_attack}.
+\section{MLE的应用}
 
-%Suppose an adversary learns  that the underlying message of a target
-%ciphertext is drawn from a publicly available set. To recover the underlying
-%message, the adversary tries each possible message from the public set,
-%derives corresponding MLE key, and uses the derived key to decrypt the
-%target ciphertext. If the decryption result equals the tried message, the
-%adversary can deduce the underlying message.
+回顾\ref{sec:background}，MLE\citing{bellare2013message}正式确立了加密重复数据删除的加密方案基础。第一个发布的MLE实例是收敛加密（CE）\citing{douceur2002reclaiming}，它使用明文的加密哈希及其对应的密文作为MLE密钥和标签。其他CE的变体包括：散列收敛加密（HCE）\citing{bellare2013message}，它从明文中导出标记，同时仍然使用明文的哈希作为MLE密钥；随机收敛加密（RCE）\citing{bellare2013message}，用新的随机密钥加密明文以形成非确定性密文，通过从明文的哈希中导出的MLE密钥保护随机密钥，并附加来自明文的确定性标签以实现数据块重复性的检查；收敛扩散加密（CD）\citing{li2015cdstore}，它通过使用明文的加密哈希作为秘密共享算法的随机种子，将CE扩展到秘密共享。由于所有上述实例仅从明文中获取MLE密钥和（或）标签，如果明文是可预测的（即，所有可能的明文的总数量有限），它们很容易受到离线暴力攻击\citing{keelveedhi2013dupless}的影响，因为攻击者可以从所有可能的明文中穷举地导出MLE密钥和标签，并检查是否存在某种明文被加密到目标密文（在CE，HCE和CD中）或映射到目标标签（在RCE中）。
 
-% {\em HCE1} and {\em HCE2} \cite{bellare13a} derive tag from client side, and
-% upload it along with ciphertext for deduplication. They offer better
-% performance for the storage system, which can simply read the tag from
-% uploads rather than computing it by hashing a possibly long ciphertext.
-% {\em Random convergent encryption (RCE)} \cite{bellare13a} encrypts a
-% message with a fresh random key, and protects the random key with the  MLE
-% key of the message. RCE is more efficient, since it can combine both
-% encryption and key generation into a single concerted pass over the message
-% \cite{bellare13a}. On the other hand, RCE needs to attach a deterministic
-% tag to the random ciphertext for checking duplicates. In addition to
-% improving performance, {\em convergent dispersal} \cite{li15} replaces the
-% random input of secret sharing by the cryptographic hash of message, so as
-% to  augment CE with fault-tolerate storage.
+暴力攻击已经被证明可以用来获取文件信息\citing{wilcox2008drew}。为了防止离线暴力攻击，DupLESS\citing{keelveedhi2013dupless}通过在独立密钥服务器中管理MLE密钥来实现服务器辅助MLE，从而确保无法从离线消息中获得每个MLE密钥。DupLESS采用两种机制来实现强大的MLE密钥管理：
+\begin{enumerate}
+    \item \textbf{无关密钥生成：}
 
-% CE has been implemented in a wide variety of storage systems \cite{adya02, elephantdrive, mega, gnunet, freenet, cryptosphere, cox02, storer08, anderson10}.
+        DupLESS中客户端总是在不向密钥服务器显示消息内容的前提下从密钥服务器获得确定性MLE密钥。
+    \item \textbf{密钥生成频率限制：}
 
-% compute the tag $T = {\sf H}({\sf H}(M))$ as a double hash over plaintext message, and require to upload $T$ along with ciphertext for efficient deduplication. 
-% A special note is RCE needs to places an appropriate tag along with ciphertext for deduplication, since its ciphertext is random. 
-% Like HCE1 and HCE2, RCE , and 
-% the message encryption and MLE key derivation of RCE can be combined into a single concerted pass over the possibly long message.
+        DupLESS中的密钥服务器通过限制来自客户端的密钥生成请求频率，防止在线暴力攻击。
+\end{enumerate}
 
-To protect against the offline brute-force attack, DupLESS \cite{bellare13b}
-implements server-aided MLE by managing MLE keys in a standalone key server,
-which ensures that each MLE key cannot be derived from a message offline.
-DupLESS employs two mechanisms to achieve robust MLE key management: (i)
-oblivious key generation, in which a client always obtains a deterministic MLE
-key for a message from the key server without revealing the message content to
-the key server, and (ii) rate limiting, which limits the key generation
-requests from the client and prevents the online brute-force attack.  Other
-studies extend server-aided MLE to address various aspects, such as reliable
-key management \cite{duan14}, transparent pricing \cite{armknecht15},
-peer-to-peer key management \cite{liu15}, and rekeying \cite{qin17}.  However,
-server-aided MLE still builds on deterministic encryption.  To our
-knowledge, existing MLE instantiations (based on either CE or server-aided
-MLE) are all vulnerable to the inference attacks studied in this paper.
+其他研究扩展了服务器辅助MLE的各个方面，例如可靠的密钥管理\citing{duan2014distributed}，透明定价\citing{armknecht2015transparent}，点对点密钥管理\citing{liu2015secure}和密钥转换（所属权变更） \citing{qin2017design}。但是服务器辅助MLE仍然建立在确定性加密的基础之上，现有的MLE实例（基于CE或服务器辅助MLE）都容易受到本文研究的推理攻击方法的攻击。
 
-%In addition, existing MLE instantiations lack active protection against the
-%size 
-%vulnerabilities explored in this paper, since they generate deterministic
-%ciphertexts or tags for deduplication. In addition, they lack active
-%protection against the size and order leakages, which can be exploited to
-%increase the severity of frequency analysis.
+\section{对（加密）重复数据删除的攻击}
 
-%SS \cite{bellare13b}, follow-up studies (see \cite{shin17} for a complete
-%survey) address additional issues, including . Liu {\em et al.} \cite{liu15}
-%propose to encrypt each message with a random key, and share the key among
-%the clients that have the same message. This prevents brute-force attack due
-%to the use of random keys, while mitigating security dependence on a global
-%secret.
+除了离线暴力攻击之外，之前的研究还考虑了针对重复数据删除存储的各种攻击，此类攻击通常也适用于加密重复数据删除。例如，侧信道攻击\citing{harnik2010side,halevi2011proofs}使攻击者可以利用重复数据删除的运作模式来推断目标用户上传文件的具体内容，或者在客户端重复数据删除中获取未经授权的访问权限；例如，2010年针对“Dropbox”成功发起了侧通道攻击（以及其他相关攻击）\citing{mulazzani2011dark}。重复伪造攻击\citing{bellare2013message}通过利用不一致的标签破坏了消息的完整性。Ritzdorf等人在其工作中利用数据块大小的泄漏来推断文件的存在性\citing{ritzdorf2016information}。基于数据块局部性的攻击\citing{li2017information}利用频率分析来推断密文数据块-明文数据块对。本文的工作在推理攻击的已有工作\citing{ritzdorf2016information,li2017information}，通过利用各种类型的泄漏给出了针对加密重复数据删除的推理攻击的更深入研究。
 
-% All above MLE instantiations transform identical message to the same ciphertext or tag, and hence incur the frequency leakage.
-They also lack of active protection against the size and order leakages.
-% via password-based key exchange. This addresses , and also prevents brute-force attack. 
-% Liu {\em et al.} \cite{liu15} propose to share encryption keys via a password-based key exchange protocol, so as to mitigate the dependence of the key manager.
-All above works apply deterministic encryption and are susceptible to frequency leakage.
-They also lack of active protection against the size and order leakages.
+\section{防御机制}
 
-\section{Attacks against (encrypted) deduplication:} In addition to the
-offline brute-force attack, previous studies consider various attacks against
-deduplication storage, and such attacks generally apply to encrypted
-deduplication as well.  For example, the side-channel attack
-\cite{harnik10,halevi11} enables adversaries to exploit the deduplication
-pattern to infer the content of uploaded files from target users or gain
-unauthorized access in client-side deduplication; it is shown that the
-side-channel attack (and other related attacks) was successfully launched
-against Dropbox in 2010 \cite{mulazzani11}.  The duplicate-faking attack
-\cite{bellare13a} compromises message integrity via inconsistent tags.
-Ritzdorf {\em et al.} \cite{ritzdorf16} exploit the leakage of the chunk size
-to infer the existence of files.  The locality-based attack \cite{li17}
-exploits frequency analysis to infer ciphertext-plaintext pairs.  Our
-work follows the line of work on inference attacks \cite{ritzdorf16,li17}, yet
-provides a more in-depth study of inference attacks against encrypted
-deduplication via various types of leakage.
+ 在\ref{sec:Countermeasure}中讨论了针对加密重复数据删除的频率，顺序和大小泄漏的应对对策。而其他防御机制旨在防范其他类型的攻击。
 
-%Our distribution-based attack inherently implies the prior attack \cite{li17}
-%(see \S\ref{sec:distribution-attack-description}). We also propose the
-%clustering-based attack that does not need the knowledge of fine-grained
-%chunk orders.  
-\section{Defense mechanisms:} 
-Section~\ref{sec:countermeasure} discusses the countermeasures agasint the frequency, order and size leakage of encrypted deduplication. 
-Additional defense mechanisms are designed to protect against other types of attacks.  
-% Several countermeasures are designed to defend
-% against the attacks on encrypted deduplication.  
-As mentioned above,
-server-aided MLE \cite{bellare13b} can defend against the offline brute-force
-attack. Server-side deduplication \cite{li15,harnik10,armknecht17} and
-proof-of-ownership \cite{xu13,pietro12,halevi11} can defend against the
-side-channel attack.  Server-side tag generation \cite{douceur02,bellare13b}
-and guarded decryption \cite{bellare13a} can defend against the
-duplicate-checking attack.
+如上所述，服务器辅助的MLE\citing{keelveedhi2013dupless}可以抵御离线暴力攻击。服务器端重复数据删除\citing{li2015cdstore,harnik2010side,armknecht2017side}和所有权证明\citing{xu2013weak,di2012boosting,halevi2011proofs}可以抵御侧信道攻击。服务器端标签生成\citing{douceur2002reclaiming,keelveedhi2013dupless}和受保护的解密\citing{bellare2013message}可以抵御重复检查攻击。
 
-% MinHash encryption \cite{qin17} disturbs the
-% frequency ranking of ciphertexts and is shown to defend against the frequency
-% analysis based on the locality-based attack via trace analysis.  Several
-% extended MLE instantiations build on strong cryptographic primitives to defend
-% against the inference attacks, such as randomized encryption that supports
-% equality testing \cite{abadi13}, hybrid encryption \cite{stanek14}, and
-% interactions with fully homomorphic encryption \cite{bellare15}, yet how they
-% are implemented and deployed in practice remains unexplored.
+\section{推理攻击}
 
-\section{Inference attacks:}  Several inference attacks have been proposed
-against encrypted databases
-\cite{grubbs17,bindschaedler17,kellaris16,durak16,naveed15,lacharite18} and 
-keyword search \cite{zhang16b,grubbs16,pouliot16,cash15,islam12}.  They all
-exploit the deterministic encryption nature to identify different types of
-leakage.  Our work differs from them by specifically focusing on frequency analysis against encrypted
-deduplication.
-
-%construct inference attacks against encrypted databases. Naveed {\em et al.}
-%\cite{naveed15} propose attacks to recover the plaintext records of {\em
-%CryptDB} \cite{popa11a}. Kellaris {\em et al.} \cite{kellaris16} and
-%Lacharite {\em et al.} \cite{lacharite18} analyze the volumes of the data
-%returned by range queries, and present generic reconstruction attacks on
-%database entries. Grubbs {\em et al.} \cite{grubbs16}, Bindschaedler {\em
-%et al.} \cite{bindschaedler17}, and Durak {\em et al.} \cite{durak16}
-%show how to recover the plaintexts from the database column encrypted by
-%order-revealing encryption. 
-%
-%target keyword search.
-Islam {\em et al.} \cite{islam12} exploit the leakage of access pattern, and recover the plaintext keywords associated with files.
-Cash {\em et al.} \cite{cash15} and Pouliot \cite{pouliot16} examine the security of searchable encryption under different leakage profiles.
-Zhang {\em et al.} \cite{zhang16b} propose file-injection attacks to recover searchable keywords.
-Grubbs \cite{grubbs16} build attacks against {\em Mylar} \cite{popa14} that is a practical system with keyword search enabled.
-This paper differs from the above works \cite{grubbs17,bindschaedler17,kellaris16,durak16,naveed15,lacharite18,zhang16b,grubbs16,pouliot16,cash15,islam12} by launching inference attacks against encrypted deduplication.
-
-%Other studies \cite{zhang16b,grubbs16,pouliot16,cash15,islam12} target keyword search.
-Islam {\em et al.} \cite{islam12} exploit the leakage of access pattern, and recover the plaintext keywords associated with files.
-Cash {\em et al.} \cite{cash15} and Pouliot \cite{pouliot16} examine the security of searchable encryption under different leakage profiles.
-Zhang {\em et al.} \cite{zhang16b} propose file-injection attacks to recover searchable keywords.
-Grubbs \cite{grubbs16} build attacks against {\em Mylar} \cite{popa14} that is a practical system with keyword search enabled.
-This paper differs from the above works \cite{grubbs17,bindschaedler17,kellaris16,durak16,naveed15,lacharite18,zhang16b,grubbs16,pouliot16,cash15,islam12} by launching inference attacks against encrypted deduplication.
-
-%Client-side deduplication leaks the side channel information that if
-%particular messages have already been stored. Harnik {\em et al.}
-%\cite{harnik10} and Halevi {\em et al.} \cite{halevi11} show how to exploit
-%the side channel leakage for different purposes, including creating covert
-%channels between clients and gaining access to unauthorized information.
-
-%Some studies \cite{stanek14,abadi13,bellare15} aim to achieve stronger security than the more practical schemes focused above.
-Stanek {\em et al.} \cite{stanek14} design a hybrid encryption scheme where unpopular messages are protected by semantically secure encryption for high security guarantee, while popular messages are protected by CE to enable deduplication.
-On the other hand, the scheme \cite{stanek14} builds on public-key primitive which is inefficient for encrypting large-size messages.
-Abadi {\em et al.} \cite{abadi13} construct two schemes for the messages whose distributions are publicly available.
-Their first scheme generates  random tags and ciphertexts to prevent frequency leakage, yet incurring expensive {\em equality test} for checking duplicates.
-Their second scheme produces deterministic ciphertexts, and exposes the frequencies of corresponding plaintexts.
-Interactive MLE \cite{bellare15} introduces interactions into encrypted deduplication, and strengthens the security of both correlated and parameter-dependent messages, yet it is impractical for the use of fully homomorphic encryption.
-On the contrary to these theoretical contributions \cite{stanek14, abadi13, bellare15}, this paper focuses on the applied aspect, and investigates the security vulnerabilities in practical deduplication.
-
-% {\em Duplicate-faking attack} \cite{bellare13a} compromises the integrity of data by inconsistent tags.
-Specifically, an adversary can attach a maliciously-generated ciphertext to a faking tag $T$, so that the following legitimate messages that have the same tag of $T$ will be removed by deduplication.
-It can be addressed by server-side tag generation \cite{douceur02, bellare13b} or guarded decryption \cite{bellare13a}.
-
-% or introducing a random threshold to control client-side or server-side deduplication \cite{,harnik10}.
-
-% Our second attack augments the prior work \cite{li17} with distribution-based ranking and achieves high inference rate and accuracy. We   
-%Some studies \cite{bosman16,gruss15,xiao13} investigate the side channels of memory deduplication, and this paper differs from them in considering deduplication in outsourced storage (e.g., cloud storage).
-
-% \paragraph{Property-revealing encryption:}
-% Encrypted deduplication leaks the underlying equality of plaintext chunks for detecting duplicates.
-A generalized {\em property-revealing encryption} \cite{bindschaedler17} has been studied for securing database storage \cite{curtmola06,bellare07,bellare09,boldyreva09,boldyreva11,popa11}.
-This paper differs from these works as it targets unstructured workloads.
-
-% both theory \cite{curtmola06,bellare07,bellare09,boldyreva09,boldyreva11} and practice \cite{popa11}.
-
-% illustrate the weakness of searchable encryption.
-
-% present reconstruction attacks by analyzing ;
-
-% \cite{grubbs17,bindschaedler17,zhang16b,grubbs16,kellaris16,pouliot16,durak16,naveed15,cash15,islam12,lacharite18}  Regarding databases,    Regarding keyword search, ; further
-
-% under different leakage settings;
-
-% classical frequency analysis against cryptdb.
-
-% -specific cryptographic primitives of deterministic encryption.
-
-% applications.
-
-% structured relational data or
-
-% based on frequency analysis.
-
-% % Frequency analysis has been applied in prior works \cite{grubbs17,bindschaedler17,zhang16b,grubbs16,kellaris16,pouliot16,durak16,naveed15,cash15,islam12,lacharite18} to construct inference attacks.
-Some attacks target , by classical frequency analysis \cite{naveed15}, exploring correlations or orderings of table columns, .
-
-% while these approaches either target structured relational data \cite{grubbs17,bindschaedler17,kellaris16,durak16,naveed15,lacharite18} or aim to recover keywords of files \cite{zhang16b,grubbs16,pouliot16,cash15,islam12}, and cannot be applied to infer a huge number of chunks.
-% % Traditional MLE (e.g., CE) builds on a {\em public} function (e.g., the hash function) to derive encryption keys, and it is susceptible to brute-force attack \cite{bellare13a} that can be used to .
-The weakness can be addressed by server-aided MLE \cite{bellare13b}.
-%  % posted by the side-channel leakage in client-side and cross-user deduplication. 
-%  % This paper differs from these attacks in considering an adversary from the server side.
+已有工作已经提出了几种针对加密数据库\citing{grubbs2017leakage,bindschaedler2018tao,kellaris2016generic,durak2016else,naveed2015inference,lacharite2018improved}和关键字搜索\citing{zhang2016all,grubbs2016breaking,pouliot2016shadow,cash2015leakage,islam2012access}的推理攻击方案。它们都利用确定性加密的性质来识别不同类型的泄漏。本文的研究内容与它们的不同之处在于专门研究了针对加密重复数据删除的频率分析推理攻击。

### 2019-01-04 paper/Experiments.tex
ING | exp1

@@
 
-在本章中，将给出基于真实世界数据集的评估结果，以证明本文针对加密重复数据删除提出的频率分析攻击方法的严重性与有效性。
+在本章中，将给出基于真实世界数据集的评估结果，以证明本文针对加密重复数据删除提出的频率分析攻击方法的有效性（对加密重复数据删除的威胁的严重性）。
 
-\section{Methodology}
+\section{实验方法}
 \label{sec:dataset}
 
-本文所使用的真实世界数据集不包数据的实际内容，因此我们模仿基于块哈希的对抗性知识。具体来说，我们在一些快照中使用有序的数据块哈希列表作为辅助信息$\mathbf{A}$和基本事实$\mathbf{M}$。为了模拟加密，我们在$\mathbf{M}$中的每个原始块散列（表示明文）上应用额外的散列函数，并将结果截断为特定于已使用数据集的约定位数。截断的结果模仿$\mathbf{C}$中的密文。对于每个推断的密文 - 明文对$(C,M)$，我们通过在$M$上应用相同的模拟加密并将结果与​​$C$进行比较来验证其正确性。请注意，基于聚类的攻击可以在段级别操作，并推断出密文 - 明文段对$(S_\mathbf{C},S_\mathbf {A})$。在这种情况下，我们检查$(S_\mathbf {C},S_\mathbf{A})$，检查$S_\mathbf{C}$中的每个密文是否完全映射到$S_\mathbf{A}$中的每个明文。
+本文所使用的真实世界数据集不包数据的实际内容，因此基于数据块哈希模拟攻击者所拥有的的对抗性知识。具体来说，本文将一些快照中的有序的数据块哈希列表作为辅助信息$\mathbf{A}$和原始明文信息$\mathbf{M}$。为了模拟加密过程，在$\mathbf{M}$中的每个原始数据块哈希（表示明文）上应用额外的哈希函数，并将结果截断为当前使用的数据集中约定的哈希值的长度。截断的结果用于模仿$\mathbf{C}$中的密文。对于每个推断的密文数据块-明文数据块对$(C,M)$，本文通过在$M$上应用相同的模拟加密并将结果与​​$C$进行比较来验证其正确性。特别的，基于聚类的频率分析攻击可以在数据段级别进行操作，断出密文数据段-明文数据段对$(S_\mathbf{C},S_\mathbf {A})$。在这种情况下，本文通过检查$S_\mathbf{C}$中的每个密文是否完全映射到$S_\mathbf{A}$中的每个明文来评估$(S_\mathbf {C},S_\mathbf{A})$的正确性。
 
-Our datasets do not contain actual content, so we mimic the adversarial knowledge based on chunk hashes.
-Specifically, we use the ordered lists of chunk hashes in some snapshots as the auxiliary information $\mathbf{A}$ and the ground truth $\mathbf{M}$, respectively.
-To simulate encryption, we apply an additional hash function over each original chunk hash (that represents a plaintext) in $\mathbf{M}$, and truncate the result into an agreed number of bits specific to the used dataset.
-The truncated result mimics a ciphertext in $\mathbf{C}$.
-For each inferred ciphertext-plaintext pair $(C, M)$, we verify its correctness by applying the same simulated encryption on $M$ and comparing the result with $C$.
-Note that the clustering-based attack can operate at the segment level, and infer the ciphertext-plaintext segment pair $(S_\mathbf{C}, S_\mathbf{A})$.
-In this case, we check $(S_\mathbf{C}, S_\mathbf{A})$ by examining each ciphertext in $S_\mathbf{C}$ is exactly mapped from each plaintext in $S_\mathbf{A}$.
+本文通过推理率和推理精度两个标准来衡量攻击的有效性（参见\ref{sec:ThreatModel}）。
 
-We measure the severity of the attacks by the inference rate and the inference precision (see Section~\ref{sec:threat}).
+\section{基于分布的攻击的实验结果}
+\label{sec:experiment-distribution}
 
-\section{Results of Distribution-based Attack}
-\label{sec:experiment-distribution}
+\subsection{实验1（参数的影响）}
+
+本节将评估参数$(u, r, t)$的变化在基于分布的频率分析攻击中带来的影响。实验使用FSL数据集（参见\ref{sec:fsl}）来进行评估。在实验中使用每个用户的第12周备份作为辅助信息来推断该用户相应的第14周备份中的原始明文数据。出于控制变量的需求，实验将在固定另两个参数的前提下对三个参数中的一个的变化进行测试和分析。
+
+\subsubsection{参数$u$的影响}
+
+首先，配置参数$t \rightarrow \infty$和$r = 0$来评估参数$u$变化的影响（在这种情况下，基于分发的攻击将退化到基于数据块局部性的的攻击\cite{li2017information}）。
 
@@
 
+图\ref{fig:distribution-impact-u}显示了将参数$u$从2变为512时对推理率和推理精度带来的影响。对于推理率的结果，本实验的观察结果与已有的工作\cite{li2017information}相同。推理率首先随着$u$的增大而提高，这是因为频率分析攻击可以推断出更多的密文数据块-明文数据块对。推理率在达到最大值之后（例如，User004为13.9\%，User007为13.6\%，User012为1.4\%，User013为0.5\%，User015为0.7\%，User028为6.1\%）开始下降。其原因在于频率分析引入了大量的误报，这些误报会继续影响基于分布的攻击对每个数据块相邻邻居的推断。同时，部分特殊情况下的推理率约为0.0001\%，这意味着攻击只能推断出几个密文数据块-明文数据块对。
+
+已有的工作\cite{li2017information}不提供基于数据块局部性的攻击的推理精度信息，因此本文提出的两种推理攻击方法的实验的推理精度的部分不与其进行对比。实验中观察到除User028的数据在$u=2$的条件下没有引入任何误报外，针对所有用户备份数据的推理精度都处于相当低的水平（小于40\%）。随着$u$的增大，推理精度会略有下降。例如，当$u$从2增加到512时，User004的推理精度从30.7\%下降到12.8\%。
+
+{\bf Observation (1) --}
+
+A relatively larger $u$ increases the inference rate, yet it decreases the inference precision (i.e., more false positives are introduced).
+
+\subsubsection{参数$r$的影响}
+
+Informed by the impact of $u$, we set $u$ at 128 for User004, User013 and User015, and at 256 for User007, User012 and User028, respectively, in order to evaluate the impact of $r$ and $t$.
+Our rationale is to increase the coverage of inferred ciphertext-plaintext pairs, while we use $r$ and $t$ to filter possibly false positives.
+
 \begin{figure}[!htbp]
@@
 
-\begin{figure}[!htbp]
-    \centering
-    \begin{tabular}{p{.48\linewidth}p{.48\linewidth}}
-        \multicolumn{2}{c}{\includegraphics[width=.7\textwidth]{legend-fsl-line.pdf}}  \\
-        \includegraphics[width=\linewidth]{dis-impact-t-rate.pdf} &
-        \includegraphics[width=\linewidth]{dis-impact-t-accuracy.pdf}\\
-    \end{tabular}
-    \caption{基于分布的攻击实验1-参数$t$的变化对推理结果的影响（User004、User013和User015中$u = 128$，User007、User012和User028中$u = 256$；$r = 10$）}
-    \label{fig:distribution-impact-t}
-\end{figure}
-
-\subsection{Experiment 1 (Impact of parameters):}
-We evaluate the impact of the parameters $(u, r, t)$ in the distribution-based attack.
-We drive our evaluation using the FSL dataset, and use the 12th weekly backup of each user as the auxiliary information to infer original plaintexts in corresponding 14th weekly backup.
-We configure $t \rightarrow \infty$ and $r$ = 0 to evaluate the impact of $u$ (in this case, the distribution-based attack reduces to the locality-based attack \cite{li17}).
-Our rationale is to avoid the disturbances by other parameters.
-
-Figure~\ref{fig:distribution-impact}(a) shows the impact of $u$, when we vary $u$ from 2 to 512.
-Regarding inference rate, we have the same observation as the prior work \cite{li17}.
-Specifically, the inference rates first increase with $u$, since the attack can infer more ciphertext-plaintext pairs.
-After hitting the maximum values (e.g., 13.9\% for User004, 13.6\% for User007, 1.4\% for User012, 0.5\% for User013, 0.7\% for User015, and 6.1\% for User028), they decrease.
-The reason is that the underlying frequency analysis introduces a large number of false positives that compromise the inferences over corresponding neighbors.
-
-The prior work \cite{li17} does not report the inference precision about the attack.
-We observe that the inference precisions for all users are at a fairly low level (e.g., less than 40\%), except the case of $u = 2$ for User028 that does not introduce any false positives.
-On the other hand, the inference rate in the special case is about 0.0001\%, meaning that the attack only infers a few ciphertext-plaintext pairs.
-In addition, as $u$ increases,the inference precisions decrease slightly.
-For example, when $u$ increases from 2 to 512, the inference precision of User004 drops from 30.7\% to 12.8\%.
-
-{\bf Observation (1) --} {\em A relatively larger $u$ increases the inference rate, yet it decreases the inference precision (i.e., more false positives are introduced). }
-
-Informed by the impact of $u$, we set $u$ at 128 for User004, User013 and User015, and at 256 for User007, User012 and User028, respectively, in order to evaluate the impact of $r$ and $t$.
-Our rationale is to increase the coverage of inferred ciphertext-plaintext pairs, while we use $r$ and $t$ to filter possibly false positives.
-
 We first configure $t \rightarrow \infty$ and evaluate the impact of $r$.
@@
 {\bf Observation (2) --} {\em A larger $r$ provides more opportunities of identifying correct ciphertext-plaintext pairs, yet it also increases the probability of having false positives.}
+
+\subsubsection{参数$t$的影响}
+
+\begin{figure}[!ht]
+    \centering
+    \begin{tabular}{p{.48\linewidth}p{.48\linewidth}}
+        \multicolumn{2}{c}{\includegraphics[width=.7\textwidth]{legend-fsl-line.pdf}}  \\
+        \includegraphics[width=\linewidth]{dis-impact-t-rate.pdf} &
+        \includegraphics[width=\linewidth]{dis-impact-t-accuracy.pdf}\\
+    \end{tabular}
+    \caption{基于分布的攻击实验1-参数$t$的变化对推理结果的影响（User004、User013和User015中$u = 128$，User007、User012和User028中$u = 256$；$r = 10$）}
+    \label{fig:distribution-impact-t}
+\end{figure}
 

### 2019-01-04 paper/Experiments.tex
ING | exp4

@@
 \subsection{实验1（参数的影响）}
+\label{sec:exp1}
 
@@
     \end{tabular}
-    \caption{基于分布的攻击实验1-参数$u$的变化对推理结果的影响（$r = 0$；$t \rightarrow \infty$）}
+    \caption{基于分布的攻击实验1：参数$u$的变化对推理结果的影响（$r = 0$；$t \rightarrow \infty$）}
     \label{fig:distribution-impact-u}
@@
 
-{\bf Observation (1) --}
-
-A relatively larger $u$ increases the inference rate, yet it decreases the inference precision (i.e., more false positives are introduced).
+\textbf{结论（1）：}相对较大的$u$提高了推理率，但降低了推理精度（即，引入了更多的误报）
 
@@
 
-Informed by the impact of $u$, we set $u$ at 128 for User004, User013 and User015, and at 256 for User007, User012 and User028, respectively, in order to evaluate the impact of $r$ and $t$.
-Our rationale is to increase the coverage of inferred ciphertext-plaintext pairs, while we use $r$ and $t$ to filter possibly false positives.
+然后，通过$u$变化的影响分析，本文选择增加推断的密文数据块-明文数据块对的覆盖范围，同时使用$r$和$t$来过滤可能的误报。因此，本文将User004，User013和User015的$u$设置为128，User007，User012和User028的设置分别为256，以评估$r$和$t$变化的影响。
 
@@
     \end{tabular}
-    \caption{基于分布的攻击实验1-参数$r$的变化对推理结果的影响（User004、User013和User015中$u = 128$，User007、User012和User028中$u = 256$；$t \rightarrow \infty$）}
+    \caption{基于分布的攻击实验1：参数$r$的变化对推理结果的影响（User004、User013和User015中$u = 128$，User007、User012和User028中$u = 256$；$t \rightarrow \infty$）}
     \label{fig:distribution-impact-r}
@@
 
-We first configure $t \rightarrow \infty$ and evaluate the impact of $r$.
-Figure~\ref{fig:distribution-impact}(b) shows the results.
-We observe that the inference rates of majority users increase with $r$.
-For example, when we vary $r$ from 0 to 16, the inference rates grow from 9.5\% to 16.0\%, from 10.0\% to 13.0\%, from 0.5\% to 0.7\%, and from 4.7\% to 5.6\% for User004, User007, User013, and User028, respectively.
-The reason is that the distribution-based attack addresses disturbances to frequency ranking, and infer more correct ciphertext-plaintext  pairs.
-On the other hand, the inference rates decrease slightly from 1.3\% to 0.8\% and from 0.6\% to 0.4\% for User012 and User015, respectively.
-The reason is that they examine a large range of plaintexts and may introduce more false positives.
-In addition, the inference precisions for all users are  at a low level (e.g., less than 45\%), and have similar tendencies with corresponding inference rates.
+本实验中首先令$t\rightarrow \infty$，然后评估$r$变化带来的影响。图\ref{fig:distribution-impact-r}展示了参数$r$变化的实验结果。 实验观察到大多数用户的推理率随着$r$而增加。例如，当将$r$从0变为16时，User004推理率从9.5\%增加到16.0\%，User007从10.0\%增加到13.0\%，User013从0.5\%增加到0.7\%，User028从4.7\%增加到5.6\%。发生这种现象的原因是基于分布的攻击减少了直接频率排序的干扰，并推断出更多正确的密文数据块-明文数据块对。另一方面，对于User012和User015，推理率分别从1.3\%降至0.8\%，从0.6\%降至0.4\%。原因是随着检查的扩大，可能引入更多的误报。同时，所有用户的推断精度均处于低水平（小于45％），并且具有与其相应的推断率类似的变化趋势。
 
-{\bf Observation (2) --} {\em A larger $r$ provides more opportunities of identifying correct ciphertext-plaintext pairs, yet it also increases the probability of having false positives.}
-
+\textbf{结论（2）：}较大的$r$提供了识别正确的密文数据块-明文数据块对的更多机会，但也增加了发生误报的概率。
 \subsubsection{参数$t$的影响}
@@
     \end{tabular}
-    \caption{基于分布的攻击实验1-参数$t$的变化对推理结果的影响（User004、User013和User015中$u = 128$，User007、User012和User028中$u = 256$；$r = 10$）}
+    \caption{基于分布的攻击实验1：参数$t$的变化对推理结果的影响（User004、User013和User015中$u = 128$，User007、User012和User028中$u = 256$；$r = 10$）}
     \label{fig:distribution-impact-t}
@@
 
-Then, we fix $r$ = 10 and evaluate the impact of $t$.
-Figure~\ref{fig:distribution-impact}(c) shows the results.
-When $t$ is small (e.g., less than 0.5), we observe that the attack misjudges and filters a significant number of ciphertext-plaintext pairs, even they are correct.
-This introduces {\em false negatives} that reduce the inference rate.
-As $t$ increases, the number of false negatives decreases.
-When $t$ = 1.5, the inference rates hit the maximum values at 21.2\%, 18.2\%, 10.4\%, 1.2\%, 1.2\%, and 13.5\% for User004, User007, User012, User013, User015, and User028, respectively.
-When $t$ further increases to 2, the corresponding inference rates drop to 20.5\%, 17.1\%, 8.3\%, 1.2\%, 1.0\%, and 11.2\%, respectively.
-The reason is that if $t$ is too large, it cannot filter false positives effectively.
-For the same reason, the inference precisions for all users decrease with $t$.
+最后，设定$r=10$来评估参数$t$变化的影响。 图\ref{fig:distribution-impact-t}展示了参数$t$变化的实验结果果。当$t$很小（例如，小于0.5）时，实验观察到攻击误判并过滤了大量的密文数据块-明文数据块对，即使它们是正确的（即，引入了降低推理率的假阳性结果）。随着$t$的增加，假阳性的结果数量减少。当$t= 1.5$时，对于User004，User007，User012，User013，User015和User028，推理率分别达到最大值21.2\%，18.2\%，10.4\%，1.2\%，1.2\%和13.5\%。 当$t$进一步增大到2时，相应的推理率分别降至20.5\%，17.1\%，8.3\%，1.2\%，1.0\%和11.2\%。其原因是如果$t$过大，攻击就无法有效地过滤误报。因此，所有用户数据的推理精度都会随着$t$的增大而下降。
 
-{\bf Observation (3) --} {\em A smaller $t$ filters a large fraction of false
-positives, yet it introduces more false negatives.}
+\textbf{结论（3）：}较小的$t$过滤了大部分频率分析带来的误报，但它引入了更多的假阳性结果，导致了推理率的下降。
 
-\subsection{Experiment 2 (Comparison with prior attack):}
-We compare the severity of the distribution-based attack with that of the locality-based attack \cite{li17}.
-In addition to using the FSL dataset like Experiment~1, we include the MS dataset for cross-dataset validation.
-Specifically, for each MS category, we choose two snapshots at a time, use one to infer the other, and evaluate the average inference rate and precision.
+\subsection{实验2（与已有工作的对比）}
+\label{sec:exp2}
+本文将基于分布的攻击的有效性与基于数据块局部性的攻击的有效性进行比较\cite{li2017information}。除了使用实验1（参见\ref{sec:exp1}）中采用的FSL数据集之外，本文还加入MS数据集（参见\ref{sec:ubc-ms}）用于进行跨数据集的验证与评估。在MS数据集中，对于每个系统类别，一次选择两个快照，使用其中一个来推断另一个，以此评估平均的推理率和推理精度。
 
-We consider the following attack instances for comparison.
+本文考虑采用以下攻击实例来进行比较。
 
 \begin{itemize}[leftmargin=*]
-\item 
-$\tt Baseline$: We re-implement the locality-based attack based on the parameter configuration suggested in \cite{li17}.
-Specifically, it infers 5 most frequent ciphertext-plaintext pairs in the first invocation (i.e., to initialize a set of ciphertext-plaintext pairs for iteration) of frequency analysis, and 30 in each following invocation (i.e., to iteratively infer ciphertext-plaintext pairs from neighbors).
-\item 
-$\tt Distribution$ and $\tt Distribution^S$: We consider two attack instances of the distribution-based attack, denoted by $\tt Distribution^S$ and ${\tt Distribution}$, which operate with and without size information, respectively (i.e., the superscript $\tt S$ indicates that the attack instance operates with size information).
-We configure $\tt Distribution^S$ and ${\tt Distribution}$ under the same configuration of  ${\tt Baseline}$.
-In addition, we choose $r$ and $t$ in both  $\tt Distribution^S$ and ${\tt Distribution}$ in the following way: for the FSL dataset, we fix $r$ = 10 for all users, and individually set $t$ = 1.5, 1.2, 1, 1, 0.7, and 0.9 for User004, User007, User012, User013, User015, and User028, respectively; for the MS dataset, we also fix $r$ = 10 for all categories, and set $t$ = 2 for Win7 and Serv-08, and $t$ = 1.6 for Vista-U, Serv-03, and Vista-B, respectively.
-This is informed by our tests for optimal configurations of the datasets.
-\item 
-$\tt Distribution$-$\tt o$ and $\tt Distribution^S$-$\tt o$: We consider two additional distribution-based attack instances, denoted by $\tt Distribution$-$\tt o$ and $\tt Distribution^S$-$\tt o$, which apply the same configurations for $r$ and $t$ as with $\tt Distribution$ and $\tt Distribution^S$, and further use larger $u$ to increase the coverage of inferred ciphertext-plaintext pairs.
-Specifically, we configure $u$ in $\tt Distribution$-$\tt o$ and $\tt Distribution^S$-$\tt o$ in the following way:  for the FSL dataset, we apply the same configuration of $u$ in Experiment~1; for the MS dataset, we set $u$ = 128 for Win7, and $u$ = 30 for Serv-03, Serv-08, Vista-B, and Vista-U.
+\item \textbf{$\tt Baseline$：}
 
+实验根据已有工作\cite{li2017information}中建议的参数配置实现基于数据块局部性的攻击。具体来说，它在频率分析的第一次调用中推断出5个出现频率最高的的密文数据块-明文数据块对（即，初始化一组用于迭代的密文数据块-明文数据块对），并且在每次后续调用中根据已有数据块对的邻居推断30个新的数据块对（即，迭代地推断密文数据块-明文数据块对）。
+
+\item \textbf{$\tt Distribution$和$\tt Distribution^S$：}
+
+考虑两个基于分布的攻击的攻击实例，分别由$\tt Distribution$和$\tt Distribution^S$表示，它们分别使用和不使用大小信息作为辅助信息（即上标$\tt S$表示攻击实例使用大小信息进行操作）。实验在与${\tt Baseline}$相同参数的条件下配置$\tt Distribution^S$和${\tt Distribution}$。 此外，实验通过以下方式在$\tt Distribution^S$和${\tt Distribution}$中选择参数$r$和$t$的取值：对于FSL数据集，我们为所有用户设定$r = 10$，并分别为User004、User007、User012、User013、User015和User028设置参数$t$ = 1.5、1.2、1、1、0.7和0.9；对于MS数据集，实验继续为所有类别设置参数$r = 10$，为Win7和Serv-08设置参数$t = 2$，为Vista-U、Serv-03和Vista-B设置参数$t = 1.6$。以上数据是通过按照实验1（参见\ref{sec:exp1}）的方法对数据集的最佳配置的测试得出的。
+\item \textbf{$\tt Distribution$-$\tt o$和$\tt Distribution^S$-$\tt o$：}
+
+实验考虑另外两个基于分布的攻击的实例，用$\tt Distribution$-$\tt o$和$\tt Distribution^S$-$\tt o$表示，对于$r$和$t$应用与$\tt Distribution$和$\tt Distribution^S$相同的配置，但进一步使用更大的参数$u$增加推断的密文数据块-明文数据块对的覆盖范围。具体来说，实验通过以下方式在$\tt Distribution$-$\tt o$和$\tt Distribution^S$-$\tt o$中配置参数$u$：对于FSL数据集，参数$u$的选择与实验1（参见\ref{sec:exp1}）相同；对于MS数据集，实验为Win7数据设置$u = 128$，为Serv-03、Serv-08、Vista-B和Vista-U设置$u  = 30$。
 \end{itemize}
 
-\begin{figure*}[t]
+\begin{figure*}[!htbp]
     \centering
@@
     \end{tabular}
-    \caption{Experiment 2 FSL dataset  (Comparison with prior attack): comparison of attack severity for distribution-based attack and locality-based attack.}
-    \label{fig:distribution-comparison}
+    \caption{基于分布的攻击实验2（与已有工作的对比）：比较基于分布的攻击和基于数据块局部性的攻击的有效性（FSL数据集）。}
+    \label{fig:distribution-comparison-fsl}
 \end{figure*}
+
+图\ref{fig:distribution-comparison-fsl}给出了基于FSL数据集的上述5种实例的比较结果。实验观察到，在几乎所有情况下，基于分布的攻击的不同实例都优于基于数据块局部性的攻击。例如，对于User028，基于分布的攻击的最低推理率是11.4\%，推理精度为84.1\%（$\tt Distribution$）；此时$\tt Baseline$相应的推理率仅为1.2\%，推理精度仅为1.7\%。这意味着在这种情况下，基于分布的攻击可以将假阳性的数量减少82.4\%。
+
+\textbf{结论（4）：}基于分布的攻击显着提高了推理精度，同时实现了比基于数据块局部性的攻击更高的推理率。
+
+$\tt Distribution^S$和$\tt Distribution^S$-$\tt o$相较于$\tt Distribution$和$\tt Distribution$-$\tt o$拥有更高的推理精度，这因为它们进一步通过数据块大小信息过滤了误报。例如，对于User004，$\tt Distribution^S$和$\tt Distribution^S$-$\tt o$相较于$\tt Distribution$和$\tt Distribution$-$\tt o$将误报分别从35.2\%减少到1.7\%，从35.3\%减少到2.2\%。然而，在同样的情况下，实验观察到$\tt Distribution$ and $\tt Distribution$-$\tt o$的推理率分别为20.0\%和21.2\%，相较于$\tt Distribution^S$和$\tt Distribution^S$-$\tt o$分别高出2.0\%和0.4\%。其原因是$\tt Distribution$和$\tt Distribution$-$\tt o$推断出了来自不正确的密文数据块-明文数据块对的邻居中的少量正确结果。换句话说，虽然$(C, M)$是不正确的密文数据块-明文数据块对，但$C$的邻居可能以很小的概率对应于$M$的邻居。即使在这种情况下，所有基于分布的攻击实例都比基于数据块局部性的攻击实例效果更佳。具体来说，$\tt Baseline$的推理率仅为15.2\%，比基于分布的攻击的最佳情况低6.0\%，最差情况低2.8\%。
+
+\textbf{结论（5）：}过滤不正确的推理结果可以提高推理精度，但会降低推理的密文数据块-明文数据块对的覆盖范围，并可能降低推理率。
+
+我们进一步观察到，虽然$\tt Distribution$-$\tt o$和$\tt Distribution^S$-$\tt o$构建在更大的参数$u$上，但它们的推理率仅略高于$\tt Distribution$和$\tt Distribution^S$（分别高为0.4\%和0.9\%）。 原因是基于分布的攻击仅通过已推理出数据块对的邻居进行迭代推理。参数$u$的进一步增大只会在结果中添加少量新的正确密文数据块-明文数据块对。
 
@@
     \end{tabular}
-    \caption{Experiment 2 MS dataset (Comparison with prior attack): comparison of attack severity for distribution-based attack and locality-based attack.}
-    \label{fig:distribution-comparison}
+    \caption{基于分布的攻击实验2（与已有工作的对比）：比较基于分布的攻击和基于数据块局部性的攻击的有效性（MS数据集）。}
+    \label{fig:distribution-comparison-ms}
 \end{figure*}
 
-Figure~\ref{fig:distribution-comparison}(a) shows the
-comparison results of the FSL dataset. We observe that different instances of
-the distribution-based attack outperform the locality-based attack in almost
-all cases. For example, regarding User028, the lowest inference rate of the
-distribution-based attack is 11.4\%, with the precision of 84.1\% (due to $\tt
-Distribution$), while the corresponding inference rate and precision of
-$\tt Baseline$ are only 1.2\% and 1.7\%, respectively; this implies that the distribution-based attack reduces the number of false postives by 82.4\% in this case.
+图\ref{fig:distribution-comparison-ms}给出了基于MS数据集的上述5种实例的比较结果。基于数据块局部性的攻击和基于分布的攻击在大多数MS数据集的类别（Win7除外）中具有高推理率和精度。可能的原因是MS数据集中的快照高度相关（例如，数据块总数的方差很小，如表\ref{tab:MS-dataset}所示）。实验观察到基于分布的攻击仍然优于基于数据块局部性的攻击。例如，在Vista-U中，基于分布的攻击的所有推理的推理率和推理精度分别高于24.1\%和96.4\%，而$\tt Baseline$的推断率和分辨率分别为21.7\%和87.1\%。
 
-{\bf Observation (4) --} {\em The distribution-based attack significantly
-increases the inference precision, while achieving a higher inference rate than
-the locality-based attack.}
+实验中对于数据集中Win7类别，基于分布的攻击和基于数据块局部性的攻击的推断率都很低（小于0.01％）。其原因是Win7包含大量具有唯一性的数据块（大约超过98.8\%，如表\ref{tab:MS-dataset}所示），导致了攻击效果表现不佳。
 
-$\tt Distribution^S$ and $\tt Distribution^S$-$\tt o$ have higher inference
-precisions than $\tt Distribution$ and $\tt Distribution$-$\tt o$,
-respectively, since they further filter false positives by size information.
-For example, for User004, $\tt Distribution^S$ and $\tt Distribution^S$-$\tt o$  reduce the fraction of false positives in  $\tt Distribution$ and $\tt Distribution$-$\tt o$ from 35.2\% to 1.7\% and from 35.3\% to 2.2\%, respectively.
-However, in the same case,
- we observe that the inference rates of $\tt Distribution$ and $\tt Distribution$-$\tt o$ are 20.0\% and 21.2\%, slightly higher than those of  
-$\tt Distribution^S$ and
-$\tt Distribution^S$-$\tt o$ by 2.0\% and
-0.4\%, respectively. The reason is that $\tt Distribution$ and $\tt
-Distribution$-$\tt o$ infer a small number of correct results from the
-neighbors of incorrect ciphertext-plaintext pairs. In other words,  although
-$(C, M)$ is an incorrect ciphertext-plaintext pair, the neighbors of $C$ may
-correspond to those of $M$ with a small probability.
-Even in this case, all distribution-based attack instances are more severe than the locality-based attack instance.
-Specifically, the inference rate of $\tt Baseline$ is only 15.2\%, lower than those of the best and the worst distribution-based attack instances by 6.0\% and 2.8\%, respectively.
+\subsection{实验3（攻击效果）}
 
-% For the same reason, $\tt Baseline$ has higher inference rate than $\tt Distribution^S$ in User013.
+实验考虑长期备份模式，并使用FSL数据集检查基于分布的攻击的有效性。具体来说，实验选择每个用户的第$i$个FSL每周备份作为辅助信息，以推断相应的第$(i+w)$个FSL每周备份中的原始明文。显然，$w$越小，辅助信息和目标备份之间的相关性就越高。与实验2（参见\ref{sec:exp2}）配置两个基于分布的攻击实例$\tt Distribution$-$\tt o$和$\tt Distribution^S$-$\tt o$，并评估它们的推理率和推理精度（针对每个用户的所有可用的$i$）。
 
-{\bf Observation (5) --} {\em Filtering incorrect inference results improves
-the inference precision, yet it degrades the coverage of inferred
-ciphertext-plaintext pairs and possibly decreases the inference rate.
-}
-
-We further observe that although $\tt Distribution$-$\tt o$ and $\tt
-Distribution^S$-$\tt o$ build on larger $u$, their inference rates are just
-slightly higher than those of $\tt Distribution$ and $\tt Distribution^S$ by
-0.4\% and 0.9\%, respectively. The reason is that the distribution-based
-attack iterates inference just through neighbors, and has a bounded coverage
-of inferred ciphertext-plaintext pairs. The further increase of $u$ only adds
-a small number of new correct  ciphertext-plaintext pairs into results.
-
-Figure~\ref{fig:distribution-comparison}(b) shows the
-results of the MS dataset. Both locality-based and distribution-based attacks
-have high inference rates and precisions in most MS categories (except Win7).
-The possible reason is that MS snapshots are highly correlated (e.g., the
-variance of the total number of chunks is small, as shown in
-Table~\ref{tab:dataset}).  We observe that the distribution-based attack still
-outperforms the locality-based attack. For example, in Vista-U, the inference
-rates and precisions of all inferences of the distribution-based attack are
-above 24.1\% and 96.4\%, while those of $\tt Baseline$ are 21.7\% and 87.1\%,
-respectively.
-
-Note that both  distribution-based and  locality-based attacks have low
-inference rates (e.g., less than 0.01\%) in the Win7 category. The reason is
- that Win7 includes a large fraction (e.g., more than 98.8\%, as shown in
-Table~\ref{tab:dataset}) of unique chunks, which cannot be correctly
-inferred by the frequency analysis attacks.
-
-% We do not include Win7  in the comparison, since all attack instances have low effectiveness. We observe all attacks have higher severity than those in the FSL dataset.
-
-\begin{figure*}[t]
+\begin{figure*}[!htbp]
     \centering
@@
     \begin{tabular}{c}
-        \includegraphics[width=.35\textwidth]{pic/legend-effectiveness.pdf}\\
-        \includegraphics[width=.7\textwidth]{pic/distribution-effectiveness-wo-size.pdf}
+        \includegraphics[width=.35\textwidth]{legend-effectiveness.pdf}\\
+        \includegraphics[width=.7\textwidth]{distribution-effectiveness-wo-size.pdf}
     \end{tabular}
-	\caption{Experiment 3 Distribution-based attack without size information  (Attack effectiveness): severity of distribution-based attack in FSL dataset.}
-	\label{fig:experiment-distribution-effectiveness}
+	\caption{实验3（攻击效果）：没有大小信息辅助的基于分布的攻击在FSL数据集中的有效性。}
+	\label{fig:experiment-distribution-effectiveness-wo}
 \end{figure*}
 
-\begin{figure*}[t]
+图\ref{fig:experiment-distribution-effectiveness-wo}给出了$\tt Distribution$-$\tt o$的实验结果。基于分布的攻击在用户之间具有不同的推理率和推理精度。例如，在类似User004这样的有利情况下，它实现了推理率24.8\%、推理精度67.3\%（$w = 1$）；推理率24.5\%、推理精度67.0\%（$w = 2$）；推理率24.0\%、推理精度66.5\%（$w = 3$）。在类似User015这样的非有利情况下，基于分布的攻击的推理率仅有0.3\%。可能的原因是User015的备份数据具有较低的数据块局部性。
+
+此外，实验观察到辅助信息的相关性（即$w$）对基于分布的攻击的有效性影响较低。例如，当$w$从1增加到3时，它仅导致推理率（下降小于1.4\%）和精度（下降小于5.6\%）的有限下降。其原因是基于分布的攻击解决了频率排名中的干扰并保留了攻击的有效性。
+
+\textbf{结论（6）：}基于分布的攻击可以在存在松散相关的辅助信息的帮助下有效控制攻击有效性的下降程度。
+
+\begin{figure*}[!htbp]
     \centering
@@
     \end{tabular}
-	\caption{Experiment 3 Distribution-based attack with size information (Attack effectiveness): severity of distribution-based attack in FSL dataset.}
-	\label{fig:experiment-distribution-effectiveness}
+	\caption{实验3（攻击效果）：有大小信息辅助的基于分布的攻击在FSL数据集中的有效性。}
+	\label{fig:experiment-distribution-effectiveness-w}
 \end{figure*}
 
-\subsection{Experiment 3 (Attack effectiveness):} We consider a long-term
-backup scenario and examine the effectiveness of the distribution-based attack
-with the FSL dataset. Specifically, we choose the $i$th FSL weekly backup of
-each user as the auxiliary information to infer original plaintexts in the corresponding $(i+w)$th FSL
-weekly backup. Clearly, the smaller $w$ is, the higher correlation between the
-auxiliary information and the target backup will be.  We configure the two  
-distribution-based attack instances $\tt Distribution$-$\tt o$ and $\tt Distribution^S$-$\tt o$
-like Experiment~2, and evaluate their inference rates and inference precisions that
-are averaged for all available $i$ for each user.
+图\ref{fig:experiment-distribution-effectiveness-w}给出了$\tt Distribution^S$-$\tt o$的实验结果。实验观察到它具有与$\tt Distribution$-$\tt o$相似的推理率，同时拥有更高的推理精度。例如，对于所有用户的平均推断精度分别为93.1\%（$w = 1$）、92.8\%（$w = 2$）和92.4\%（$w = 3$）。
 
-Figure~\ref{fig:experiment-distribution-effectiveness}(a) shows the results. The
-distribution-based attack has varying inference rate and precision  across
-users. For example, in the favorable case like User004, it achieves the
-highest inference rates of 24.8\%, 24.5\%, and 24.0\% with the precisions of
-67.3\%, 67.0\%, and 66.5\% for $w$ = 1, 2, and 3, respectively; in the
-non-favorable case like User015, the inference rate of the distribution-based
-attack is only around 0.3\%. The possible reason is that the backup data from
-User015 has low chunk locality.
-
-In addition, we observe that the correlation (i.e., $w$) of the auxiliary
-information has low impact on the effectiveness of the distribution-based
-attack.  For example, when $w$ increases from 1 to 3, it only leads to limited
-degradations on inference rate (e.g., less than 1.4\%) and precision (e.g.,
-less than 5.6\%). The reason is that the distribution-based attack addresses
-disturbances to frequency ranking and preserves attack effectiveness.
-
-{\bf Observation (6) --} {\em The distribution-based attack can limit the
-degradation of attack effectiveness in the presence of loosely correlated
-auxiliary information.}
-
-% We also use the instance in Experiment 2 to evaluate the effectiveness of the distribution-based attack that operates with
- % size information. 
- Figure~\ref{fig:experiment-distribution-effectiveness}(b) shows the results of $\tt Distribution^S$-$\tt o$. We observe that it has similar inference rate with $\tt Distribution$-$\tt o$,  
- while achieving much higher precision. For example, the average inference precision of all users are 93.1\%, 92.8\%, and 92.4\% for $w$ = 1, 2, and 3, respectively.
-
-% Figure~\ref{fig:experiment-distribution-severity-ms} shows the attack results of the MS dataset.
-The distribution-based attack achieves high severity.
-For example, it can infer 24.0\% of unique chunks in Vista-U with a precision of 96.2\%.
-
-% Although there is l
-
-\section{Results of Clustering-based Attack}
+\section{基于聚类的攻击的实验结果}
 \label{sec:experiment-clustering}
 
-\subsection{Experiment 4 (Impact of parameter):} We first evaluate the impact
-of the parameter $k$, which defines the upper bound distance
-in combining the closest clusters.  We use both the FSL and the VM datasets to
-study how $k$ affects the underlying clustering scheme in the attack.
-Specifically, we apply segmentation on the last backup of each considered FSL
-and VM user, respectively, and generate the segments that have a fixed size of
-4MB.
+\subsection{实验4（参数的影响）}
 
-The clustering scheme aims to aggregate similar ciphertext segments into the
-same cluster, without compromising the confidentiality of chunks in each
-ciphertext segment.  To quantify its effect, we compare the results of
-clustering with those of a {\em real} classification approach, which directly
-classifies segments by their minimum chunk hash.  Suppose we generate $m$ real
-classes of segments by classification, and $\widetilde{m}$ clusters by the
-clustering scheme, respectively.  We consider {\em clustering closeness},
-evaluated by $\frac{{\sf abs}(m-\widetilde{m})}{m}$ (where 
-${\sf abs}(m-\widetilde{m})$ returns the absolute value of $m-\widetilde{m}$),
-which quantifies how the  number of clusters approximates that of real
-classes. In addition, let $\hat{m}$ be the number of clusters, in which all
-segments are similar (i.e., have the same minimum chunk hash). We also
-consider {\em clustering correctness}, evaluated by
-$\frac{\hat{m}}{\widetilde{m}}$, which quantifies how precisely the clustering
-scheme groups similar segments.
+实验首先评估参数$k$的影响，该参数定义了凝聚法层次聚类中组合两个最近聚类的距离上限。本实验使用FSL和VM数据集来研究$k$如何影响攻击中的基础聚类方案。具体来说，分别对每个选出的FSL和VM用户数据的最后一次备份应用分段方法，并生成固定大小为4MB的数据段。
 
-Figure~7(a) shows the results of the FSL dataset, where we
-consider four FSL users (e.g., User004, User007, User015 and User028) for
-saving evaluation time. The clustering closeness first increases with $k$,
-since the number (i.e., $\widetilde{m}$) of clusters decreases and
-approximates $m$. When $k$ increases further, the number of clusters drops
-away from $m$, and leads to the increase of clustering closeness.  In
-addition, we observe that the clustering correctness gradually decreases with
-$k$, because some of non-similar segments (i.e., their minimum chunk hashes are
-different) are aggregated into the same cluster. Both results suggest that we
-can configure an appropriate $k$ to balance the closeness and correctness of
-clustering. For example, when we set $k$ = 0.65 for User015, the corresponding
-closeness and correctness are 1.0\% and 94.2\%, respectively. This implies
-that the results of the clustering scheme  highly approximates
-those of real classification.
+聚类方案旨在将类似的密文数据段聚合到同一个聚类中，这一过程不会损害每个密文数据段中的数据块的机密性。为了量化其影响，将聚类的结果与实际分类方法的结果进行比较（实际分类方法通过最小数据块哈希直接对分段进行分类）。假设我们分别通过实际分类方法生成$m$个数据段的集合，并且通过聚类方案生成$\widetilde{m}$个数据段的集合。通过$\frac{{\sf abs}(m-\widetilde{m})}{m}$（其中${\sf abs}(m-\widetilde{m})$返回$m-\widetilde{m}$的绝对值）衡量聚类形成的集合与实际分类形成的集合的相似程度。记集合所有数据段都相同（具有相同的最小数据块哈希）的聚类的数量为$\hat{m}$。此外，实验还考虑了聚类正确性，由$\frac{\hat{m}}{\widetilde{m}}$进行评估，它量化了对相似数据段的聚类方案的精确程度。
 
-{\bf Observation (7) --} {\em By configuring an appropriate $k$ for
-clustering, we  approximate the results of  classifying segments, without the knowledge of  minimum chunk hash in each
-segment.}
+Figure~7(a) shows the results of the FSL dataset, where we consider four FSL users (e.g., User004, User007, User015 and User028) for saving evaluation time.
+The clustering closeness first increases with $k$, since the number (i.e., $\widetilde{m}$) of clusters decreases and approximates $m$.
+When $k$ increases further, the number of clusters drops away from $m$, and leads to the increase of clustering closeness.
+In addition, we observe that the clustering correctness gradually decreases with $k$, because some of non-similar segments (i.e., their minimum chunk hashes are different) are aggregated into the same cluster.
+Both results suggest that we can configure an appropriate $k$ to balance the closeness and correctness of clustering.
+For example, when we set $k$ = 0.65 for User015, the corresponding closeness and correctness are 1.0\% and 94.2\%, respectively.
+This implies that the results of the clustering scheme  highly approximates those of real classification.
 
-Figure~7(b) shows the results of the VM dataset. We observe
-that the clustering closeness and correctness of all VM users have  similar
-tendencies with those of FSL users. When we configure $k$ = 0.8, the average
-clustering closeness of all VM users is only 3.0\%, while the corresponding
-clustering correctness is as high as 93.1\%.
+{\bf Observation (7) --} {\em By configuring an appropriate $k$ for clustering, we  approximate the results of  classifying segments, without the knowledge of  minimum chunk hash in each segment.}
 
-\begin{figure*}[t]
+Figure~7(b) shows the results of the VM dataset.
+We observe that the clustering closeness and correctness of all VM users have  similar tendencies with those of FSL users.
+When we configure $k$ = 0.8, the average clustering closeness of all VM users is only 3.0\%, while the corresponding clustering correctness is as high as 93.1\%.
+
+\begin{figure*}[!htbp]
 \centering
@@
 } &
-        % \multicolumn{2}{c}{\footnotesize Fig.~6\quad Experiment 4 (Impact of parameter): show impact of $d$ with clustering closeness and correctness; for clustering closeness, the smaller the better; for clustering correctness, the larger the better.} &
         {\footnotesize
@@
 
-% \begin{figure}
-% 	\includegraphics[width=.48\textwidth]{pic/clustering-impact-d.pdf}
-% 	\caption{Experiment 6 (Impact of parameter).}
-% 	\label{fig:experiment-clustering-impact}
-% \end{figure}
-
-\begin{table*}[!t]
+\begin{table*}[!htbp]
 \small
@@
     Source & c, h, cpp, java, py & 10-20KB   & 17.1\% & 15.0\%\\
-% \hline
-	% Library & .a, .dll, .so \\
-% \hline
-	% Compression & .bz2, .gz, tar, rar, zip, 7z \\
 \hline
@@
 
-\subsection{Experiment 5 (Attack effectiveness):} We now study the
+\subsection{实验5（攻击效果）}
+
+We now study the
 effectiveness of the clustering-based attack. Due to the boundary shift of
@@
 
-\section{Results of Security Implications}
+\section{攻击对安全影响的结果}
 \label{sec:case}
-We thus far have examined the severity of inference attacks by quantifying the
-correctly inferred ciphertext-plaintext pairs.  However, it remains an open
-issue that what are the security implications informed by these results and
-how the frequency analysis attacks bring actual damage. In the following
-experiment, we evaluate the security implications of our attacks based on the
-{\em raw inference rate}, defined as the percentage of raw data content
-affected by correctly inferred chunks.
 
-\subsection{Experiment 6 (Security implications):}
+We thus far have examined the severity of inference attacks by quantifying the correctly inferred ciphertext-plaintext pairs.
+However, it remains an open issue that what are the security implications informed by these results and how the frequency analysis attacks bring actual damage.
+In the following experiment, we evaluate the security implications of our attacks based on the raw inference rate, defined as the percentage of raw data content affected by correctly inferred chunks.
+
+\subsection{实验6（安全隐患分析）}
+
 We first consider the distribution-based attack, and evaluate its raw
@@
 
-% switch to the clustering-based attack, and infer the content of the last (i.e., the 13th) VM backup based on the corresponding 11th backup.
-Since the VM dataset does not contain metadata, we evaluate the raw inference rate across different users.
-Specifically, like Experiment 7, we only consider segment-level attack for high precision, and count the raw inference rate based on the correctly inferred segments.
-Note that since VM images commonly contain a large fraction of zero chunks ,  we filter out the zero segments in our inferred raw content.
-
 We use the same configuration of Experiment~5, and evaluate raw inference rate
@@
 is as high as 23.2\%.
-% a relatively high raw inference rate.  On average, the raw inference rate is 23.2\% for all users.
 
@@
 confidentiality of VM disk images. }
+
+\section{本章小结}

### 2019-01-05 paper/Conclusion.tex
ING | body done

@@
 
-首先，本文将完整的旧备份视为辅助信息，如果攻击者仅对旧备份的部分有了解（没有完整的旧备份用作辅助信息），则不研究攻击者如何发起攻击。可能的是，攻击者仍然可以应用频率分析攻击从可用的部分备份中提取特征，并通过比较特征与目标备份中的特征来推断密文数据块-明文数据块对。未来研究的第一个方向是设计更高级的推理攻击方法，并比较在前述的部分知识案例中新方法是否比直接应用本文提出的两种攻击更好。
+首先，本文将完整的旧备份视为辅助信息，如果攻击者仅对旧备份的部分有了解（没有完整的旧备份用作辅助信息），则不研究攻击者如何发起攻击。可能的是，攻击者仍然可以应用频率分析攻击从可用的部分备份中提取特征，并通过比较特征与目标备份中的特征来推理密文数据块-明文数据块对。未来研究的第一个方向是设计更高级的推理攻击方法，并比较在前述的部分知识案例中新方法是否比直接应用本文提出的两种攻击更好。
       

### 2019-01-05 paper/DataSetandSystemReport.tex
ING | exp1
ING | body done

@@
 \chapter{数据集与实际系统调研}
+\label{sec:DataSetSystem}
 \section{数据集调研}
@@
 \subsection{FSL数据集}
-
+\label{sec:fsl}
 \begin{table}[!hbt]
@@
 
-此数据集由Stony Brook大学的文件系统和存储实验室（FSL）收集\cite{sun16，FSL14，sun18}。本文使用fslhomes快照进行实验，每个快照包括48位数据块哈希的有序列表，这些哈希是由平均大小为8KB的可变大小分块生成的，以及相应的元数据信息（例如，数据块大小、文件名、扩展名等）。本文从2013年1月22日到5月21日选择快照，并选择在整个持续时间内具有完整每日快照的六个用户（即User004，User007，User012，User013，User015和User028）用于后续实验分析。本文以周为单位选取备份数据，因此为每个用户选出14个每周完整备份。
+此数据集由Stony Brook大学的文件系统和存储实验室（FSL）收集\citing{sun2016long,FSL14,sun2018cluster}。本文使用fslhomes快照进行实验，每个快照包括48位数据块哈希的有序列表，这些哈希是由平均大小为8KB的可变大小分块生成的，以及相应的元数据信息（例如，数据块大小、文件名、扩展名等）。本文从2013年1月22日到5月21日选择快照，并选择在整个持续时间内具有完整每日快照的六个用户（即User004，User007，User012，User013，User015和User028）用于后续实验分析。本文以周为单位选取备份数据，因此为每个用户选出14个每周完整备份。
 
 \subsection{VM数据集}
-
+\label{sec:vm}
 \begin{table}[!hbt]
@@
 \subsection{MS数据集}
-
+\label{sec:ubc-ms}
 \begin{table}[!hbt]
@@
 
-此数据集由Microsoft\cite{meyer2012study}收集，并在SNIA\cite{ms}上公布。 原始数据集包含2009年9月5日至10月31日的Windows文件系统快照。每个快照由通过Rabin Fingerprinting\cite{rabin1981fingerprinting}获得的不同平均大小的40位数据块哈希表示。 本文使用以下类别的操作系统快照用于试验：Windows 7（Win7），Microsoft Windows Server 2003（Serv-03），Microsoft Windows Server 2008（Serv-08），Microsoft Windows Vista Business Edition（ Vista-B）和Microsoft Windows Vista Ultimate Edition（Vista-U）。在每个类别中，选择四个快照（这些快照的平均数据块大小为8KB。
+此数据集由Microsoft\citing{meyer2012study}收集，并在SNIA\citing{ms}上公布。 原始数据集包含2009年9月5日至10月31日的Windows文件系统快照。每个快照由通过Rabin Fingerprinting\citing{rabin1981fingerprinting}获得的不同平均大小的40位数据块哈希表示。 本文使用以下类别的操作系统快照用于试验：Windows 7（Win7），Microsoft Windows Server 2003（Serv-03），Microsoft Windows Server 2008（Serv-08），Microsoft Windows Vista Business Edition（ Vista-B）和Microsoft Windows Vista Ultimate Edition（Vista-U）。在每个类别中，选择四个快照（这些快照的平均数据块大小为8KB。
 
@@
 
-SDFS\cite{SDFS}是一种分布式、可扩展的文件系统，旨在为应用程序提供具有较强灵活性的内联重复数据删除。该系统有两种部署方法：
+SDFS\citing{SDFS}是一种分布式、可扩展的文件系统，旨在为应用程序提供具有较强灵活性的内联重复数据删除。该系统有两种部署方法：
 
@@
 
-Destor\cite{fu2015design}是重复数据删除的评估平台，其包含了大量重复数据删除中常用的方法，可以用于常用重复数据删除的方法测试与应用效果模拟评估。系统原型中包含的主要特征有：
+Destor\citing{fu2015design}是重复数据删除的评估平台，其包含了大量重复数据删除中常用的方法，可以用于常用重复数据删除的方法测试与应用效果模拟评估。系统原型中包含的主要特征有：
 

### 2019-01-05 paper/Experiments.tex
ING | body done

@@
 
-本文所使用的真实世界数据集不包数据的实际内容，因此基于数据块哈希模拟攻击者所拥有的的对抗性知识。具体来说，本文将一些快照中的有序的数据块哈希列表作为辅助信息$\mathbf{A}$和原始明文信息$\mathbf{M}$。为了模拟加密过程，在$\mathbf{M}$中的每个原始数据块哈希（表示明文）上应用额外的哈希函数，并将结果截断为当前使用的数据集中约定的哈希值的长度。截断的结果用于模仿$\mathbf{C}$中的密文。对于每个推断的密文数据块-明文数据块对$(C,M)$，本文通过在$M$上应用相同的模拟加密并将结果与​​$C$进行比较来验证其正确性。特别的，基于聚类的频率分析攻击可以在数据段级别进行操作，断出密文数据段-明文数据段对$(S_\mathbf{C},S_\mathbf {A})$。在这种情况下，本文通过检查$S_\mathbf{C}$中的每个密文是否完全映射到$S_\mathbf{A}$中的每个明文来评估$(S_\mathbf {C},S_\mathbf{A})$的正确性。
+本文所使用的真实世界数据集不包数据的实际内容，因此基于数据块哈希模拟攻击者所拥有的的对抗性知识。具体来说，本文将一些快照中的有序的数据块哈希列表作为辅助信息$\mathbf{A}$和原始明文信息$\mathbf{M}$。为了模拟加密过程，在$\mathbf{M}$中的每个原始数据块哈希（表示明文）上应用额外的哈希函数，并将结果截断为当前使用的数据集中约定的哈希值的长度。截断的结果用于模仿$\mathbf{C}$中的密文。对于每个推理的密文数据块-明文数据块对$(C,M)$，本文通过在$M$上应用相同的模拟加密并将结果与​​$C$进行比较来验证其正确性。特别的，基于聚类的频率分析攻击可以在数据段级别进行操作，断出密文数据段-明文数据段对$(S_\mathbf{C},S_\mathbf {A})$。在这种情况下，本文通过检查$S_\mathbf{C}$中的每个密文是否完全映射到$S_\mathbf{A}$中的每个明文来评估$(S_\mathbf {C},S_\mathbf{A})$的正确性。
 
@@
 
-本节将评估参数$(u, r, t)$的变化在基于分布的频率分析攻击中带来的影响。实验使用FSL数据集（参见\ref{sec:fsl}）来进行评估。在实验中使用每个用户的第12周备份作为辅助信息来推断该用户相应的第14周备份中的原始明文数据。出于控制变量的需求，实验将在固定另两个参数的前提下对三个参数中的一个的变化进行测试和分析。
+本节将评估参数$(u, r, t)$的变化在基于分布的频率分析攻击中带来的影响。实验使用FSL数据集（参见\ref{sec:fsl}）来进行评估。在实验中使用每个用户的第12周备份作为辅助信息来推理该用户相应的第14周备份中的原始明文数据。出于控制变量的需求，实验将在固定另两个参数的前提下对三个参数中的一个的变化进行测试和分析。
 
@@
 
-首先，配置参数$t \rightarrow \infty$和$r = 0$来评估参数$u$变化的影响（在这种情况下，基于分发的攻击将退化到基于数据块局部性的的攻击\cite{li2017information}）。
+首先，配置参数$t \rightarrow \infty$和$r = 0$来评估参数$u$变化的影响（在这种情况下，基于分发的攻击将退化到基于数据块局部性的的攻击\citing{li2017information}）。
 
@@
 
-图\ref{fig:distribution-impact-u}显示了将参数$u$从2变为512时对推理率和推理精度带来的影响。对于推理率的结果，本实验的观察结果与已有的工作\cite{li2017information}相同。推理率首先随着$u$的增大而提高，这是因为频率分析攻击可以推断出更多的密文数据块-明文数据块对。推理率在达到最大值之后（例如，User004为13.9\%，User007为13.6\%，User012为1.4\%，User013为0.5\%，User015为0.7\%，User028为6.1\%）开始下降。其原因在于频率分析引入了大量的误报，这些误报会继续影响基于分布的攻击对每个数据块相邻邻居的推断。同时，部分特殊情况下的推理率约为0.0001\%，这意味着攻击只能推断出几个密文数据块-明文数据块对。
+图\ref{fig:distribution-impact-u}显示了将参数$u$从2变为512时对推理率和推理精度带来的影响。对于推理率的结果，本实验的观察结果与已有的工作\citing{li2017information}相同。推理率首先随着$u$的增大而提高，这是因为频率分析攻击可以推理出更多的密文数据块-明文数据块对。推理率在达到最大值之后（例如，User004为13.9\%，User007为13.6\%，User012为1.4\%，User013为0.5\%，User015为0.7\%，User028为6.1\%）开始下降。其原因在于频率分析引入了大量的误报，这些误报会继续影响基于分布的攻击对每个数据块相邻邻居的推理。同时，部分特殊情况下的推理率约为0.0001\%，这意味着攻击只能推理出几个密文数据块-明文数据块对。
 
-已有的工作\cite{li2017information}不提供基于数据块局部性的攻击的推理精度信息，因此本文提出的两种推理攻击方法的实验的推理精度的部分不与其进行对比。实验中观察到除User028的数据在$u=2$的条件下没有引入任何误报外，针对所有用户备份数据的推理精度都处于相当低的水平（小于40\%）。随着$u$的增大，推理精度会略有下降。例如，当$u$从2增加到512时，User004的推理精度从30.7\%下降到12.8\%。
+已有的工作\citing{li2017information}不提供基于数据块局部性的攻击的推理精度信息，因此本文提出的两种推理攻击方法的实验的推理精度的部分不与其进行对比。实验中观察到除User028的数据在$u=2$的条件下没有引入任何误报外，针对所有用户备份数据的推理精度都处于相当低的水平（小于40\%）。随着$u$的增大，推理精度会略有下降。例如，当$u$从2增加到512时，User004的推理精度从30.7\%下降到12.8\%。
 
@@
 
-然后，通过$u$变化的影响分析，本文选择增加推断的密文数据块-明文数据块对的覆盖范围，同时使用$r$和$t$来过滤可能的误报。因此，本文将User004，User013和User015的$u$设置为128，User007，User012和User028的设置分别为256，以评估$r$和$t$变化的影响。
+然后，通过$u$变化的影响分析，本文选择增加推理的密文数据块-明文数据块对的覆盖范围，同时使用$r$和$t$来过滤可能的误报。因此，本文将User004，User013和User015的$u$设置为128，User007，User012和User028的设置分别为256，以评估$r$和$t$变化的影响。
 
@@
 
-本实验中首先令$t\rightarrow \infty$，然后评估$r$变化带来的影响。图\ref{fig:distribution-impact-r}展示了参数$r$变化的实验结果。 实验观察到大多数用户的推理率随着$r$而增加。例如，当将$r$从0变为16时，User004推理率从9.5\%增加到16.0\%，User007从10.0\%增加到13.0\%，User013从0.5\%增加到0.7\%，User028从4.7\%增加到5.6\%。发生这种现象的原因是基于分布的攻击减少了直接频率排序的干扰，并推断出更多正确的密文数据块-明文数据块对。另一方面，对于User012和User015，推理率分别从1.3\%降至0.8\%，从0.6\%降至0.4\%。原因是随着检查的扩大，可能引入更多的误报。同时，所有用户的推断精度均处于低水平（小于45％），并且具有与其相应的推断率类似的变化趋势。
+本实验中首先令$t\rightarrow \infty$，然后评估$r$变化带来的影响。图\ref{fig:distribution-impact-r}展示了参数$r$变化的实验结果。 实验观察到大多数用户的推理率随着$r$而增加。例如，当将$r$从0变为16时，User004推理率从9.5\%增加到16.0\%，User007从10.0\%增加到13.0\%，User013从0.5\%增加到0.7\%，User028从4.7\%增加到5.6\%。发生这种现象的原因是基于分布的攻击减少了直接频率排序的干扰，并推理出更多正确的密文数据块-明文数据块对。另一方面，对于User012和User015，推理率分别从1.3\%降至0.8\%，从0.6\%降至0.4\%。原因是随着检查的扩大，可能引入更多的误报。同时，所有用户的推理精度均处于低水平（小于45％），并且具有与其相应的推理率类似的变化趋势。
 
@@
 \label{sec:exp2}
-本文将基于分布的攻击的有效性与基于数据块局部性的攻击的有效性进行比较\cite{li2017information}。除了使用实验1（参见\ref{sec:exp1}）中采用的FSL数据集之外，本文还加入MS数据集（参见\ref{sec:ubc-ms}）用于进行跨数据集的验证与评估。在MS数据集中，对于每个系统类别，一次选择两个快照，使用其中一个来推断另一个，以此评估平均的推理率和推理精度。
+本文将基于分布的攻击的有效性与基于数据块局部性的攻击的有效性进行比较\citing{li2017information}。除了使用实验1（参见\ref{sec:exp1}）中采用的FSL数据集之外，本文还加入MS数据集（参见\ref{sec:ubc-ms}）用于进行跨数据集的验证与评估。在MS数据集中，对于每个系统类别，一次选择两个快照，使用其中一个来推理另一个，以此评估平均的推理率和推理精度。
 
@@
 
-实验根据已有工作\cite{li2017information}中建议的参数配置实现基于数据块局部性的攻击。具体来说，它在频率分析的第一次调用中推断出5个出现频率最高的的密文数据块-明文数据块对（即，初始化一组用于迭代的密文数据块-明文数据块对），并且在每次后续调用中根据已有数据块对的邻居推断30个新的数据块对（即，迭代地推断密文数据块-明文数据块对）。
+实验根据已有工作\citing{li2017information}中建议的参数配置实现基于数据块局部性的攻击。具体来说，它在频率分析的第一次调用中推理出5个出现频率最高的的密文数据块-明文数据块对（即，初始化一组用于迭代的密文数据块-明文数据块对），并且在每次后续调用中根据已有数据块对的邻居推理30个新的数据块对（即，迭代地推理密文数据块-明文数据块对）。
 
@@
 
-实验考虑另外两个基于分布的攻击的实例，用$\tt Distribution$-$\tt o$和$\tt Distribution^S$-$\tt o$表示，对于$r$和$t$应用与$\tt Distribution$和$\tt Distribution^S$相同的配置，但进一步使用更大的参数$u$增加推断的密文数据块-明文数据块对的覆盖范围。具体来说，实验通过以下方式在$\tt Distribution$-$\tt o$和$\tt Distribution^S$-$\tt o$中配置参数$u$：对于FSL数据集，参数$u$的选择与实验1（参见\ref{sec:exp1}）相同；对于MS数据集，实验为Win7数据设置$u = 128$，为Serv-03、Serv-08、Vista-B和Vista-U设置$u  = 30$。
+实验考虑另外两个基于分布的攻击的实例，用$\tt Distribution$-$\tt o$和$\tt Distribution^S$-$\tt o$表示，对于$r$和$t$应用与$\tt Distribution$和$\tt Distribution^S$相同的配置，但进一步使用更大的参数$u$增加推理的密文数据块-明文数据块对的覆盖范围。具体来说，实验通过以下方式在$\tt Distribution$-$\tt o$和$\tt Distribution^S$-$\tt o$中配置参数$u$：对于FSL数据集，参数$u$的选择与实验1（参见\ref{sec:exp1}）相同；对于MS数据集，实验为Win7数据设置$u = 128$，为Serv-03、Serv-08、Vista-B和Vista-U设置$u  = 30$。
 \end{itemize}
@@
 
-$\tt Distribution^S$和$\tt Distribution^S$-$\tt o$相较于$\tt Distribution$和$\tt Distribution$-$\tt o$拥有更高的推理精度，这因为它们进一步通过数据块大小信息过滤了误报。例如，对于User004，$\tt Distribution^S$和$\tt Distribution^S$-$\tt o$相较于$\tt Distribution$和$\tt Distribution$-$\tt o$将误报分别从35.2\%减少到1.7\%，从35.3\%减少到2.2\%。然而，在同样的情况下，实验观察到$\tt Distribution$ and $\tt Distribution$-$\tt o$的推理率分别为20.0\%和21.2\%，相较于$\tt Distribution^S$和$\tt Distribution^S$-$\tt o$分别高出2.0\%和0.4\%。其原因是$\tt Distribution$和$\tt Distribution$-$\tt o$推断出了来自不正确的密文数据块-明文数据块对的邻居中的少量正确结果。换句话说，虽然$(C, M)$是不正确的密文数据块-明文数据块对，但$C$的邻居可能以很小的概率对应于$M$的邻居。即使在这种情况下，所有基于分布的攻击实例都比基于数据块局部性的攻击实例效果更佳。具体来说，$\tt Baseline$的推理率仅为15.2\%，比基于分布的攻击的最佳情况低6.0\%，最差情况低2.8\%。
+$\tt Distribution^S$和$\tt Distribution^S$-$\tt o$相较于$\tt Distribution$和$\tt Distribution$-$\tt o$拥有更高的推理精度，这因为它们进一步通过数据块大小信息过滤了误报。例如，对于User004，$\tt Distribution^S$和$\tt Distribution^S$-$\tt o$相较于$\tt Distribution$和$\tt Distribution$-$\tt o$将误报分别从35.2\%减少到1.7\%，从35.3\%减少到2.2\%。然而，在同样的情况下，实验观察到$\tt Distribution$ and $\tt Distribution$-$\tt o$的推理率分别为20.0\%和21.2\%，相较于$\tt Distribution^S$和$\tt Distribution^S$-$\tt o$分别高出2.0\%和0.4\%。其原因是$\tt Distribution$和$\tt Distribution$-$\tt o$推理出了来自不正确的密文数据块-明文数据块对的邻居中的少量正确结果。换句话说，虽然$(C, M)$是不正确的密文数据块-明文数据块对，但$C$的邻居可能以很小的概率对应于$M$的邻居。即使在这种情况下，所有基于分布的攻击实例都比基于数据块局部性的攻击实例效果更佳。具体来说，$\tt Baseline$的推理率仅为15.2\%，比基于分布的攻击的最佳情况低6.0\%，最差情况低2.8\%。
 
@@
 
-图\ref{fig:distribution-comparison-ms}给出了基于MS数据集的上述5种实例的比较结果。基于数据块局部性的攻击和基于分布的攻击在大多数MS数据集的类别（Win7除外）中具有高推理率和精度。可能的原因是MS数据集中的快照高度相关（例如，数据块总数的方差很小，如表\ref{tab:MS-dataset}所示）。实验观察到基于分布的攻击仍然优于基于数据块局部性的攻击。例如，在Vista-U中，基于分布的攻击的所有推理的推理率和推理精度分别高于24.1\%和96.4\%，而$\tt Baseline$的推断率和分辨率分别为21.7\%和87.1\%。
+图\ref{fig:distribution-comparison-ms}给出了基于MS数据集的上述5种实例的比较结果。基于数据块局部性的攻击和基于分布的攻击在大多数MS数据集的类别（Win7除外）中具有高推理率和精度。可能的原因是MS数据集中的快照高度相关（例如，数据块总数的方差很小，如表\ref{tab:MS-dataset}所示）。实验观察到基于分布的攻击仍然优于基于数据块局部性的攻击。例如，在Vista-U中，基于分布的攻击的所有推理的推理率和推理精度分别高于24.1\%和96.4\%，而$\tt Baseline$的推理率和分辨率分别为21.7\%和87.1\%。
 
-实验中对于数据集中Win7类别，基于分布的攻击和基于数据块局部性的攻击的推断率都很低（小于0.01％）。其原因是Win7包含大量具有唯一性的数据块（大约超过98.8\%，如表\ref{tab:MS-dataset}所示），导致了攻击效果表现不佳。
+实验中对于数据集中Win7类别，基于分布的攻击和基于数据块局部性的攻击的推理率都很低（小于0.01％）。其原因是Win7包含大量具有唯一性的数据块（大约超过98.8\%，如表\ref{tab:MS-dataset}所示），导致了攻击效果表现不佳。
 
 \subsection{实验3（攻击效果）} 
-
-实验考虑长期备份模式，并使用FSL数据集检查基于分布的攻击的有效性。具体来说，实验选择每个用户的第$i$个FSL每周备份作为辅助信息，以推断相应的第$(i+w)$个FSL每周备份中的原始明文。显然，$w$越小，辅助信息和目标备份之间的相关性就越高。与实验2（参见\ref{sec:exp2}）配置两个基于分布的攻击实例$\tt Distribution$-$\tt o$和$\tt Distribution^S$-$\tt o$，并评估它们的推理率和推理精度（针对每个用户的所有可用的$i$）。
+\label{sec:exp3}
+实验考虑长期备份模式，并使用FSL数据集检查基于分布的攻击的有效性。具体来说，实验选择每个用户的第$i$个FSL每周备份作为辅助信息，以推理相应的第$(i+w)$个FSL每周备份中的原始明文。显然，$w$越小，辅助信息和目标备份之间的相关性就越高。与实验2（参见\ref{sec:exp2}）配置两个基于分布的攻击实例$\tt Distribution$-$\tt o$和$\tt Distribution^S$-$\tt o$，并评估它们的推理率和推理精度（针对每个用户的所有可用的$i$）。
 
@@
 
-图\ref{fig:experiment-distribution-effectiveness-w}给出了$\tt Distribution^S$-$\tt o$的实验结果。实验观察到它具有与$\tt Distribution$-$\tt o$相似的推理率，同时拥有更高的推理精度。例如，对于所有用户的平均推断精度分别为93.1\%（$w = 1$）、92.8\%（$w = 2$）和92.4\%（$w = 3$）。
+图\ref{fig:experiment-distribution-effectiveness-w}给出了$\tt Distribution^S$-$\tt o$的实验结果。实验观察到它具有与$\tt Distribution$-$\tt o$相似的推理率，同时拥有更高的推理精度。例如，对于所有用户的平均推理精度分别为93.1\%（$w = 1$）、92.8\%（$w = 2$）和92.4\%（$w = 3$）。
 
@@
 \subsection{实验4（参数的影响）} 
-
+\label{sec:exp4}
 实验首先评估参数$k$的影响，该参数定义了凝聚法层次聚类中组合两个最近聚类的距离上限。本实验使用FSL和VM数据集来研究$k$如何影响攻击中的基础聚类方案。具体来说，分别对每个选出的FSL和VM用户数据的最后一次备份应用分段方法，并生成固定大小为4MB的数据段。
 
-聚类方案旨在将类似的密文数据段聚合到同一个聚类中，这一过程不会损害每个密文数据段中的数据块的机密性。为了量化其影响，将聚类的结果与实际分类方法的结果进行比较（实际分类方法通过最小数据块哈希直接对分段进行分类）。假设我们分别通过实际分类方法生成$m$个数据段的集合，并且通过聚类方案生成$\widetilde{m}$个数据段的集合。通过$\frac{{\sf abs}(m-\widetilde{m})}{m}$（其中${\sf abs}(m-\widetilde{m})$返回$m-\widetilde{m}$的绝对值）衡量聚类形成的集合与实际分类形成的集合的相似程度。记集合所有数据段都相同（具有相同的最小数据块哈希）的聚类的数量为$\hat{m}$。此外，实验还考虑了聚类正确性，由$\frac{\hat{m}}{\widetilde{m}}$进行评估，它量化了对相似数据段的聚类方案的精确程度。
+聚类方案旨在将类似的密文数据段聚合到同一个聚类中，这一过程不会损害每个密文数据段中的数据块的机密性。本文使用聚类接近度量化其影响，将聚类的结果与实际分类方法的结果进行比较（实际分类方法通过最小数据块哈希直接对分段进行分类）。假设我们分别通过实际分类方法生成$m$个数据段的集合，并且通过聚类方案生成$\widetilde{m}$个数据段的集合。通过$\frac{{\sf abs}(m-\widetilde{m})}{m}$（其中${\sf abs}(m-\widetilde{m})$返回$m-\widetilde{m}$的绝对值）衡量聚类形成的集合与实际分类形成的集合的相似程度。记集合所有数据段都相同（具有相同的最小数据块哈希）的聚类的数量为$\hat{m}$。此外，实验还考虑了聚类正确性，通过$\frac{\hat{m}}{\widetilde{m}}$进行评估，它量化了对相似数据段的聚类方案的精确程度。
 
-Figure~7(a) shows the results of the FSL dataset, where we consider four FSL users (e.g., User004, User007, User015 and User028) for saving evaluation time.
-The clustering closeness first increases with $k$, since the number (i.e., $\widetilde{m}$) of clusters decreases and approximates $m$.
-When $k$ increases further, the number of clusters drops away from $m$, and leads to the increase of clustering closeness.
-In addition, we observe that the clustering correctness gradually decreases with $k$, because some of non-similar segments (i.e., their minimum chunk hashes are different) are aggregated into the same cluster.
-Both results suggest that we can configure an appropriate $k$ to balance the closeness and correctness of clustering.
-For example, when we set $k$ = 0.65 for User015, the corresponding closeness and correctness are 1.0\% and 94.2\%, respectively.
-This implies that the results of the clustering scheme  highly approximates those of real classification.
+\begin{figure}[!htbp]
+    \centering
+    \begin{tabular}{p{.48\linewidth}p{.48\linewidth}}
+        \multicolumn{2}{c}{\includegraphics[width=.5\textwidth]{clu-fsl-bar.pdf}}  \\
+        \includegraphics[width=\linewidth]{clu-impact-d-fsl-clo.pdf} &
+        \includegraphics[width=\linewidth]{clu-impact-d-fsl-cro.pdf}\\
+    \end{tabular}
+    \caption{实验4（参数的影响）：FSL数据集中参数$k$对基于聚类的攻击的影响（聚类接近度越小越好；聚类正确性越大越好）。}
+    \label{fig:cluster-impact-d-fsl}
+\end{figure}
 
-{\bf Observation (7) --} {\em By configuring an appropriate $k$ for clustering, we  approximate the results of  classifying segments, without the knowledge of  minimum chunk hash in each segment.}
+图\ref{fig:cluster-impact-d-fsl}给出了针对FSL数据集的实验结果，其中考虑了四个FSL用户的数据（User004，User007，User015和User028）以节省评估时间。 聚类接近度首先随$k$的增加而增加，这是因为聚类的数量（即$\widetilde{m}$）减少并接近$m$。当$k$进一步增加时，聚类数量会从$m$开始下降，并导致聚类间接近度的增加。此外，实验观察到聚类正确性随$k$的增大逐渐减小，这是因为一些非相似的数据段（即，它们的最小块散列不同）被聚合到同一聚类中。这两个结果都表明攻击者可以通过配置一个合适的$k$来平衡聚类的接近程度和正确性的关系。 例如，当我们为User015设置$k = 0.65$时，相应的聚类接近度和正确性分别为1.0\%和94.2\%。这意味着聚类方案的结果高度接近实际分类的结果。
 
-Figure~7(b) shows the results of the VM dataset.
-We observe that the clustering closeness and correctness of all VM users have  similar tendencies with those of FSL users.
-When we configure $k$ = 0.8, the average clustering closeness of all VM users is only 3.0\%, while the corresponding clustering correctness is as high as 93.1\%.
+\textbf{结论（7）：}通过为聚类方法配置适当的参数$k$，攻击可以在未知数据段的最小数据块哈希的前提下得到近似的分类效果。
 
-\begin{figure*}[!htbp]
+\begin{figure}[!htbp]
     \centering
-    \begin{tabular}{cc@{\hspace{0.3in}}p{.32\textwidth}}
-    \includegraphics[width=.3\textwidth]{pic/clustering-impact-d-fsl.pdf} &
-    \includegraphics[width=.3\textwidth]{pic/clustering-impact-d-vm.pdf} & 
-    \includegraphics[width=.3\textwidth]{pic/clustering-effectiveness.pdf} \medskip \\
-{\footnotesize 
-        (a) FSL dataset } 
-&
-{\footnotesize 
-        (a) VM dataset } 
-        &  ~~~ \medskip \\
-        \multicolumn{2}{p{.64\textwidth}}{
-            \footnotesize Fig.~7\quad Experiment 4 (Impact of parameter): impact of $k$ in the clustering scheme; for clustering closeness, the smaller the better; for clustering correctness, the larger the better.
-} &
-        {\footnotesize
-Fig.~8\quad Experiment 5 (Attack effectiveness):  severity of clustering-based attack in VM dataset.
-        }
+    \begin{tabular}{p{.48\linewidth}p{.48\linewidth}}
+        \multicolumn{2}{c}{\includegraphics[width=.7\textwidth]{clu-vm-bar.pdf}}  \\
+        \includegraphics[width=\linewidth]{clu-impact-d-vm-clo.pdf} &
+        \includegraphics[width=\linewidth]{clu-impact-d-vm-cro.pdf}\\
     \end{tabular}
-    \hspace{-1in}
-\end{figure*}
+    \caption{实验4（参数的影响）：VM数据集中参数$k$对基于聚类的攻击的影响（聚类接近度越小越好；聚类正确性越大越好）。}
+    \label{fig:cluster-impact-d-vm}
+\end{figure}
 
-\begin{table*}[!htbp]
-\small
-    \caption{Experiment 6 (Security implications)}
-\renewcommand{\arraystretch}{1.2}
-\vspace{-3pt}
- \begin{minipage}[t]{0.7\textwidth}
-\centering
-        (a) Distribution-based attacks \medskip \\
-\begin{tabular}{|c|c|c|c|c|c|}
-\hline
-
-    \multirow{2}{*}{\bf Type} & \multirow{2}{*}{\bf Extension Name} & \multirow{2}{*}{\bf \centering Range of File Size}  & \multicolumn{2}{c|}{\bf Raw Inference Rate} \\ \cline{4-5} 
-    & & &  $\sf Distribution$-$\sf o$ & $\sf Distribution^S$-$\sf o$ \\ \hline
-\hline
-    Office & doc(x), ppt(x), xls(x) & 10KB-1MB   & 4.9\% & 5.3\%\\
-\hline
-    Picture & jpg, png &10-100KB  & 7.7\% & 6.7\% \\
-\hline
-    Source & c, h, cpp, java, py & 10-20KB   & 17.1\% & 15.0\%\\
-\hline
-    Database & db, po & 20-700KB   & 2.6\% & 2.4\%\\
-\hline
-    Disk & vmdk, img & 200MB-1GB  & 15.8\% & 16.7\%\\
-\hline
-\end{tabular}
-\label{tab:file}
- \end{minipage}
-\hfill
-    \begin{minipage}[t]{0.3\textwidth}
-    \centering
-        (b) Clustering-based attack \medskip \\
-    \begin{tabular}{|c|c|}
-    \hline
-        {\bf Users} & {\bf Raw Inference Rate} \\
-    \hline
-    \hline
-        1 & 13.2\% \\ 
-    \hline
-        2 & 22.4\% \\ 
-    \hline
-        3 & 25.7\% \\ 
-    \hline
-        4 & 28.4\% \\ 
-    \hline
-        5 & 18.5\% \\ 
-    \hline
-        6 & 30.8\% \\ 
-    \hline
-    \end{tabular}
-\label{tab:user}
-    \end{minipage}
-
-\end{table*}
+图\ref{fig:cluster-impact-d-vm}给出了针对VM数据集的实验结果。实验观察到所有VM数据集中的用户数据的聚类接近度和正确性与FSL数据集中的用户数据具有相似的趋势。当配置参数$k = 0.8$时，所有VM数据集中的用户数据的平均聚类接近度为3.0\%，相应的聚类正确性高达93.1\%。
 
 \subsection{实验5（攻击效果）} 
+\label{sec:exp5}
+本实验研究基于聚类的攻击的有效性。由于固定大小的数据段的边界移位问题，它对FSL数据集的有效性很低（在本实验的测试中大约仅有1\%的推理率）。因此，本实验使用VM数据集来评估其有效性。在基于聚类的攻击中，为聚类方法设置参数$ k  = 0.8$，并配置$(u, r, t) = (5000, 100, 0.5）$用于将密文聚类与相应的明文聚类相关联。
 
-We now study the
-effectiveness of the clustering-based attack. Due to the boundary shift of
-fixed-size segment, it has low effectiveness
-(about 1\% inference rate in our test) against the FSL dataset.  Thus, we use
-the VM dataset to examine its severity. To configure the attack, we set $k$ =
-0.8 for clustering, and $(u, r, t)$ = (5000, 100, 0.5) for relating ciphertext
-clusters to corresponding plaintext clusters.
+在本实验的基准测试中，实验发现基于聚类的攻击中的数据块级推理仅正确地推理出数千个数据块（推理率过低，小于0.01\%）。因此，本文重点研究数据段级的推理，它给出了基于聚类的攻击的有效性的下限。为了与数据块级推理效果的测量保持一致，实验基于每个正确推理的数据段中的唯一性的数据块个数来计算推理率和推理精度。
 
-In our micro-benchmarking, we find that the chunk-level inference in the
-clustering-based attack only infers thousands of chunks correctly, which
-contributes to a negligible inference rate (e.g., less than 0.01\%).  
-% The
-% reason is that each cluster includes a large number of chunks, and frequency
-% analysis is ineffective in this case. 
-Thus, we focus on the
-segment-level inference, which presents the bottom line of severity in the
-clustering-based attack. To be consistent with the chunk-level measurements, we count inference rate and precision based
-on the unique chunks in each correctly inferred segment.
+\begin{figure}[!htbp]
+    \centering
+    \begin{tabular}{p{.48\linewidth}p{.48\linewidth}}
+        \multicolumn{2}{c}{\includegraphics[width=.35\textwidth]{clu-effect-bar.pdf}}  \\
+        \includegraphics[width=\linewidth]{clu-effect-rate.pdf} &
+        \includegraphics[width=\linewidth]{clu-effect-pre.pdf}\\
+    \end{tabular}
+    \caption{实验5（攻击有效性）：VM数据集中基于聚类的攻击的有效性。}
+    \label{fig:cluster-effect}
+\end{figure}
 
-We use the same evaluation methodology of Experiment~3, and report the results
-in Figure~8. Specifically, the x-axis describes the index $i$ (where 1 $\leq i \leq$
-12) of the VM backup that is used as the auxiliary information for attack,
-while the y-axis presents the average inference rate or precision of all VM
-users against the $(i+w)$th backup (where $w$ = 1, 2, and 3). We observe that both the inference rate and the inference
-precision fluctuate significantly. For example, when using the 3rd backup as
-the auxiliary information, the attack achieves the highest inference rates at
-18.1\%, 17.1\% and 16.3\%, with the precisions of 76.8\%, 75.0\% and 73.0\%
-for $w$ = 1, 2, and 3, respectively. 
-On the other hand, when using the 7th
-backup as the auxiliary information, the corresponding inference rates and
-precisions drop down to 9.6\% and 65.9\%, 6.8\% and 71.2\%, and 6.9\% and
-75.6\%, respectively. The reason is that the VM users have heavy updates after
-the 7th week, and this reduces the correlation  of adjacent backups. 
-On
-average, for $w$ = 1, 2 and 3, the clustering-based attack infers 15.8\%,
-14.0\%, and 12.6\% ciphertext-plaintext pairs, with the precisions of 71.1\%,
-69.1\%, and 68.9\%, respectively. 
-% This demonstrates high severity against
-% the VM disk images.
+本实验采取与实验3（参见\ref{sec:exp3}）相同的评估方法，实验结果如图\ref{fig:cluster-effect}所示。具体来说，X轴描述了VM备份数据集中的第$i$（其中1 $ \leq i \leq $ 12）个备份用作攻击的辅助信息，而y轴表示该辅助信息对VM数据集中第$(i + w)$（其中$w = 1,2,3$）个备份的平均推理效果。实验观察到推理率和推理精度都有显著波动。例如，当使用第3个备份作为辅助信息时，攻击的推理率为18.1\%，推理精度为76.8\%（$w = 1$）；推理率为17.1\%，推理精度为75.0\%（$w = 2$）；推理率为16.3\%，推理精度为73.0\%（$w = 3$）。但当使用第7个备份作为辅助信息时，相应的推理率和推理精度分别下降到9.6\%和65.9\%；6.8\%和71.2\%；以及6.9\%和75.6\%。原因是VM数据集中的备份在第7周之后有大量更新，显著减少了相邻备份间的相关性。平均而言，对于$w = 1,2,3$时，基于聚类的攻击推理出15.8\%，14.0\%和12.6\%密文数据块-明文数据块对，对应的推理精度为71.1\%，69.1\%，和68.9\%。
 
@@
 
-We thus far have examined the severity of inference attacks by quantifying the correctly inferred ciphertext-plaintext pairs.
-However, it remains an open issue that what are the security implications informed by these results and how the frequency analysis attacks bring actual damage.
-In the following experiment, we evaluate the security implications of our attacks based on the raw inference rate, defined as the percentage of raw data content affected by correctly inferred chunks.
+到目前为止，本文通过量化正确推理的密文数据块-明文数据块对来检查推理攻击的有效性。然而，这些结果所带来的安全隐患以及频率分析攻击如何带来实际损害仍然是一个悬而未决的问题。在下面的实验中，本文根据原始推理率评估攻击的安全隐患，原始推理率定义为受正确推理的数据块影响的原始数据块的百分比。
 
 \subsection{实验6（安全隐患分析）}
+\label{sec:exp6}
+实验首先考虑基于分布的攻击，并针对不同类型的文件评估其原始推理率。这一部分使用FSL数据集来进行评估，因为只有FSL数据集包含数据块所属的文件的文件元数据（包含文件的扩展名）。具体来说，本实验关注具有特定扩展名的五种类型的文件（参见表\ref{tab:exp-fsl-file-dis}）：office文件，图片文件，程序源代码文件，数据库文件和磁盘映像文件。这些文件占FSL数据集原始内容的60\%以上。
 
-We first consider the distribution-based attack, and evaluate its raw
-inference rate against {\em different types} of files. We drive the evaluation
-using the FSL dataset, since only the FSL dataset includes file metadata (that
-includes the extension names of files) in plaintext. Specifically, we focus on
-five types of files that have specific extension names (see
-Table~\ref{tab:file}(a)): office files ({\em Office}), picture files 
-({\em Picture}), programming source files ({\em Source}), database files 
-({\em Database}), and disk image files ({\em Disk}). These files occupy more
-than 60\% of raw content of FSL snapshots.
+\begin{table}[!htbp]
+\small
+\caption{实验6（安全隐患分析）：基于分布的攻击}
+\label{tab:exp-fsl-file-dis}
+\centering
+\begin{tabular}{|c|c|c|c|c|c|}
+\hline
 
-We apply the methodology of Experiment~2, and evaluate the raw inference
-rates of $\sf Distribution^S$-$\sf o$ and $\sf Distribution$-$\sf o$. 
-Table~\ref{tab:file}(a) shows the results. Both attack instances have high raw
-inference rates against {\em Disk} (e.g., 15.8\% for 
-$\sf Distribution$-$\sf o$ and 16.7\% for $\sf Distribution^S$-$\sf o$),
-because each disk file includes a large number of rarely updated chunks that
-form high locality within the same file. Interestingly, we observe that 
-{\em Source}, although each file is of a small size, also incurs high raw
-inference rates by the distribution-based attacks (e.g., 17.1\% for 
-$\sf Distribution$-$\sf o$ and 15.0\% for $\sf Distribution^S$-$\sf o$). The
-reason is that programming source files are often stored together in file system
-(e.g., the source files that belong to the same project locate in an identical
-directory) and form a large stretch of correlated chunks, which present high
-locality across files. For small and scattered files (e.g., {\em Office}, 
-{\em Picture}, and {\em Database}), the distribution-based attacks have
-relative low raw inference rates.
+    \multirow{2}{*}{\bf 文件类型} & \multirow{2}{*}{\bf 扩展名} & \multirow{2}{*}{\bf \centering 文件大小范围}  & \multicolumn{2}{c|}{\bf 原始推理率} \\ \cline{4-5} 
+    & & &  $\sf Distribution$-$\sf o$ & $\sf Distribution^S$-$\sf o$ \\ \hline
+    Office文件 & doc(x), ppt(x), xls(x) & 10KB-1MB   & 4.9\% & 5.3\%\\
+\hline
+    图片文件 & jpg, png &10-100KB  & 7.7\% & 6.7\% \\
+\hline
+    程序源代码 & c, h, cpp, java, py & 10-20KB   & 17.1\% & 15.0\%\\
+\hline
+    数据库文件 & db, po & 20-700KB   & 2.6\% & 2.4\%\\
+\hline
+    磁盘映像文件 & vmdk, img & 200MB-1GB  & 15.8\% & 16.7\%\\
+\hline
+\end{tabular}
+\end{table}
 
-{\bf Observation (8) --} {\em The severity of the distribution-based attack depends on the update frequencies, sizes, and spatiality of target files. }
+这一部分应用实验2（参见\ref{sec:exp2}）提出的方法的方法，用$\sf Distribution^S$-$\sf o$和$\sf Distribution$-$\sf o$来评估机遇分布的攻击的原始推理率。表\ref{tab:exp-fsl-file-dis}给出了实验结果。两种攻击实例针对磁盘映像文件都具有较高的原始推理率（例如，$\sf Distribution$-$\sf o$为15.8\%，$\sf Distribution^S$-$\sf o$为16.7\%），这因为每个磁盘文件中包含大量很少进行更新的数据块，这些数据块在同一文件中具有很强的数据块局部性。有趣的是，实验观察到程序源代码文件中，尽管每个文件都很小，但基于分布的攻击也具有很高的原始推理率（例如，$\sf Distribution$-$\sf o$为17.1\%，$\sf Distribution^S$-$\sf o$为15.0\%）。其原因是程序源代码文件通常一起存储在文件系统中（例如，属于同一项目的源文件位于相同的目录中）并形成大范围的相关数据块，在文件之间具有很强的数据块局部性。对于小型或分散的文件（例如，Office文件，图片文件和数据库文件），基于分布的攻击的原始推理率相对较低。
 
-We examine the security implication of the clustering-based attack using the VM dataset.
-Specifically, we use the 11th  backup of each VM user  to infer original content in corresponding 13th VM backup.
-Since the VM dataset does not contain any metadata, we count the raw inference rate based on the  whole data content in each VM snapshot.
-Note that we filter all zero chunks in the count of raw inference rate, because they occupy a large fraction in VM disk images \cite{jin09}.
+\textbf{结论（8）：}基于分布的攻击的有效性取决于目标文件的更新频率，文件大小和存储结构。
 
-We use the same configuration of Experiment~5, and evaluate raw inference rate
-based on segment-level inference.  Table~\ref{tab:user}(b) shows the results
-for different users.  We observe that the clustering-based attack achieves high
-severity against the VM dataset. For example, it infers up to 30.8\% raw
-content of User6's VM backup. On average, the raw inference rate of all users
-is as high as 23.2\%.
+这一部分使用VM数据集评估基于聚类的攻击带来的安全隐患。具体来说，本实验使用每个VM用户数据的第11个备份来推理该用户相应的第13个中的原始数据内容。由于VM数据集不包含任何元数据，因此本实验根据每个VM快照中的所有数据块计算原始推理率。请注意，本实验在原始推理率的计数中过滤所有全零数据块，因为它们在VM磁盘映像中占有很大比例\citing{jin2009effectiveness}，且会对评估的结果产生误导（导致原始推理率结果虚假偏高）。
 
-{\bf Observation (9) --} {\em The clustering-based attack threatens the
-confidentiality of VM disk images. }
+\begin{table}[!htbp]
+\small
+    \caption{实验6（安全隐患分析）：基于聚类的攻击}
+    \centering
+    \begin{tabular}{|c|c|c|c|}
+    \hline
+        {\bf 用户ID} & {\bf 原始推理率} & {\bf 用户ID} & {\bf 原始推理率}\\
+    \hline
+        1 & 13.2\% & 2 & 22.4\% \\ 
+    \hline
+        3 & 25.7\% & 4 & 28.4\% \\ 
+    \hline
+        5 & 18.5\% & 6 & 30.8\% \\ 
+    \hline
+    \end{tabular}
+\label{tab:exp-vm-user-cluster}
 
+\end{table}
+
+这一部分使用与实验5（参见\ref{sec:exp5}）相同的配置，并在通过数据段级推理来评估原始推理率。 表\ref{tab:exp-vm-user-cluster}给出了不同用户数据的原始推理率结果。实验观察到基于聚类的攻击对VM数据集实现了很高的安全威胁。例如，它可以推理出User6的VM备份中高达30.8\%的原始内容。所有用户的平均原始推理率高达23.2\%。
+
+\textbf{结论（9）：}基于聚类的攻击严重威胁到VM磁盘映像的机密性。
 \section{本章小结}
+本章通过6个实验对基于分布的攻击和基于聚类的攻击的相关参数的影响、攻击的有效性以及两种攻击手段对真实世界数据集的安全威胁进行了验证与分析，提出了9个根据实验观察得出的结论，证明了两种攻击手段的作用和价值。

### 2019-01-05 paper/background.tex
ING | body done

@@
 
-现有的MLE实例都建立在确定性加密这一概念的基础之上，确定性加密可以确保密文（或标签）从明文确定性地导出，与传统的对称加密相比，可以保留重复数据删除的有效性。虽然确定性加密提供了机密性保证，但是本文认为攻击者可以利用这种确定性来推断给定密文的原始明文。
+现有的MLE实例都建立在确定性加密这一概念的基础之上，确定性加密可以确保密文（或标签）从明文确定性地导出，与传统的对称加密相比，可以保留重复数据删除的有效性。虽然确定性加密提供了机密性保证，但是本文认为攻击者可以利用这种确定性来推理给定密文的原始明文。
 
@@
 
-在已有工作\citing{ritzdorf2016information,li2017information} 中，通过构建攻击原语来推断原始明文数据块\citing{li2017information} 或根据特定文件的存在\citing{ritzdorf2016information}来攻击加密重复数据删除方案。但现有的其他关于加密重复数据删除的工作仍未探索过如何基于推断得到的信息发起实际攻击。本文对加密重复数据删除的泄漏问题进行了全面研究，以求回答以下两个问题：
+在已有工作\citing{ritzdorf2016information,li2017information} 中，通过构建攻击原语来推理原始明文数据块\citing{li2017information} 或根据特定文件的存在\citing{ritzdorf2016information}来攻击加密重复数据删除方案。但现有的其他关于加密重复数据删除的工作仍未探索过如何基于推理得到的信息发起实际攻击。本文对加密重复数据删除的泄漏问题进行了全面研究，以求回答以下两个问题：
 %TODO: primitives如何翻译
 \begin{enumerate}
-    \item 如何在各种泄漏中通过启用基元来推断原始内容？
-    \item 以推断内容为基础的实际攻击的具体含义是什么？
+    \item 如何在各种泄漏中通过启用基元来推理原始内容？
+    \item 以推理内容为基础的实际攻击的具体含义是什么？
 \end{enumerate}
@@
 
-本文旨在应用频率分析来探索加密重复数据删除的漏洞。 我们的重点不是解决如何获得用于推断攻击的相关明文。在统频率分析模式下，攻击者能够访问明文逻辑数据块集合M和密文逻辑数据块集合$C$（$M$和$C$包含重复的明文和密文数据块）。攻击者根据出现频率分别对$M$和$C$中的数据块进行排序，然后将$C$中的密文数据块映射为$M$中与其具有相同排名的明文数据块。
+本文旨在应用频率分析来探索加密重复数据删除的漏洞。 我们的重点不是解决如何获得用于推理攻击的相关明文。在统频率分析模式下，攻击者能够访问明文逻辑数据块集合M和密文逻辑数据块集合$C$（$M$和$C$包含重复的明文和密文数据块）。攻击者根据出现频率分别对$M$和$C$中的数据块进行排序，然后将$C$中的密文数据块映射为$M$中与其具有相同排名的明文数据块。
 

### 2019-01-05 paper/introduction.tex
ING | last part - exp - figure fix
ING | body done

@@
+\chapter{绪\hspace{6pt}论}
+
 \section{研究工作的背景与意义}
@@
     \centering
-    \includegraphics[width=14cm]{DedupSystemStorageMode}
+    \includegraphics[width=10cm]{DedupSystemStorageMode}
     \caption{数据重删系统的存储模式} 
@@
 
-\section{拟采取的研究方案}
-\label{sec:技术路线}
-
-如图\ref{fig:技术路线图}所示，在支撑研究（基于数据块局部性的频率分析攻击方案\citing{li2017information}）的基础上，根据相对频率分布特性，设计抗排序干扰的攻击方法；在数据相似性的基础上，设计低依赖条件的攻击方法。最终设计出针对加密重复数据删除方案/系统的新型频率分析攻击方法及对应的原型软件工具。
-
-\begin{figure}[!htb]
-    \small
-    \centering
-    \includegraphics[width=15cm]{TechnicalRoute.eps}
-    \caption{技术路线图} 
-    \label{fig:技术路线图}
-\end{figure}
-
-\subsection{支撑研究}
-
-基于数据块局部性的频率分析攻击方案（locality-based attack）\citing{li2017information}作为支撑研究，该方案主要用于破译加密数据备份，即已知的明文数据块集合$M$和目标密文数据块集合$C$源于同一个系统在两个不同时间点的备份镜像。攻击利用了数据块的局部性特征：在不同备份之间，绝大多数数据块保持了相同的局部顺序；例如，每天备份工作项目的进度快照，若一天内的改动较小，则在两次备份之间未被改动的大部分数据块之间的相对顺序保持不变。因此，得出一个关键推论：如果明文数据块M是密文数据块$C$的原始明文，那么M左边和右边相邻的明文数据块有较大可能也是$C$左边和右边相邻密文数据块的原始明文。
-
-\begin{figure}[!htb]
-    \small
-    \centering
-    \includegraphics[width=14cm]{BaseFrequencyAttack}
-    \caption{基于数据块局部性的频率分析攻击} 
-    \label{fig:基于数据块局部性的频率分析攻击}
-\end{figure}
-
-基于此，攻击流程如图\ref{fig:基于数据块局部性的频率分析攻击}所示：首先，对$C$和$M$应用传统频率分析（\cref{sec:传统频率分析攻击}），将获得的若干组高频明密文对加入推测结果集合 $G$；然后，每次从$G$中选取一组明密文对$(M,C)$，分别对其左右相邻的明文和密文数据块集合$L_M[M]$和$L_C[C]$，以及$R_M[M]$和$R_C[C]$实施频率分析，并将获得的高频明密文对也加入$G$；继续对$G$中的明密文对进行基于相邻数据块的频率分析，直至所有明密文对都被处理。
-
-为了验证攻击效果，定义推测率为正确推测出原始明文的(不同)密文数据块个数与$C$中(不同)密文数据块总个数的比率。在基于真实数据集的实验验证中，攻击方案能够达到17.8\%推测率，远远高于传统频率分析方法的0.0001\%推测率。
-
-\subsection{技术突破}
-
-\subsubsection{基于分布的频率分析攻击方法}
-
-\par 基于分布的频率分析攻击利用密文和明文的相对顺序信息来增强频率分析的有效性。该攻击方法建立在数据块局部性\citing{xia2011silo,lillibridge2009sparse,zhu2008avoiding}的基础上。通过以下三个关键特性构造出基于分布的频率分析攻击方法。
-
-\begin{itemize}
-    \item 数据块局部性指出数据的原始排序可能会在各种备份文件中得以保留，因此可以用于在备份文件中推断出类似的与位置相关的密文-明文对。
-    \item 相邻数据的共现频率的相对频率分布可以通过分析得到。
-    \item 明文及其相应的密文具有相似的相对频率分布的特性。
-\end{itemize}
-
-\subsubsection{基于聚类的频率分析攻击方法}
-
-在基于分布的频率分析攻击方法的基础上，通过引入相似性\citing{bhagwat2009extreme}这一属性来消除基于分布的频率分析攻击方法对明文数据的细粒度顺序信息的需求。基于此提出基于聚类的频率分析攻击方法。
-
-\section{可行性分析}
-
-\subsection{研究方法可行}
-
-本课题通过引入加密重复数据删除方案/系统的相关特性来设计新型频率分析攻击方法，针对性提高频率分析攻击方法的有效性。该研究问题具有很高的实际价值且在面向加密重复数据删除的攻击中，已有工作提出了基于数据块局部性（chunk locality）\citing{zhu2008avoiding,lillibridge2009sparse,xia2011silo}的频率分析攻击\citing{li2017information}，在此基础上改进攻击方案以提高频率分析攻击实际效果具有明确的可行性。
-
-\subsection{研究条件可行}
-
-前期基于数据块局部性的频率分析攻击方案给出了本课题研究两种新型频率分析攻击方法的基本理论和工具基础。在原有方案上改进即可用于本课题研究。研究者在本科阶段深入钻研了CDStore、REED、SDFS等加密重复数据删除系统，以及前期基于数据块局部性的频率分析攻击方案的理论和工具实现。这些经验可以帮助设计新型频率分析方法以及其在真实系统中的实践。
-
-\section{本文特色与创新之处}
-
-本文的特色与创新之处有以下几点：
-
-\begin{enumerate}
-    \item 本文针对加密重复数据删除提出了两种新型的频率分析攻击方法。除了利用由于加密重复数据删除具有确定性导致的频率泄漏之外，两种攻击都利用重复数据删除工作负载的特性来增加频率分析攻击的有效性。
-    \item 本文使用多个真实数据集（包括长期备份\citing{sun2016long,FSL14}，Windows文件系统快照\citing{meyer2012study}和VM磁盘映像\citing{li2016cdstore,qin2017design}）以及开源重复数据删除系统SDFS\citing{SDFS}、Destor\citing{Destor}，评估两种新型频率分析攻击方法和基本频率分析攻击方法的实际效果。本文通过评估频率攻击方法的攻击结果，进一步分析本频率分析攻击方法对实际加密重复数据删除带来的安全性影响。
-    \item 本文讨论了减少加密重复数据删除中信息泄漏的可能方案。
-\end{enumerate}
+%\section{拟采取的研究方案}
+%\label{sec:技术路线}
+%
+%
+%
+%如图\ref{fig:技术路线图}所示，在支撑研究（基于数据块局部性的频率分析攻击方案\citing{li2017information}）的基础上，根据相对频率分布特性，设计抗排序干扰的攻击方法；在数据相似性的基础上，设计低依赖条件的攻击方法。最终设计出针对加密重复数据删除方案/系统的新型频率分析攻击方法及对应的原型软件工具。
+%
+%\begin{figure}[!htb]
+%    \small
+%    \centering
+%    \includegraphics[width=15cm]{TechnicalRoute.eps}
+%    \caption{技术路线图} 
+%    \label{fig:技术路线图}
+%\end{figure}
+%
+%\subsection{支撑研究}
+%
+%基于数据块局部性的频率分析攻击方案（locality-based attack）\citing{li2017information}作为支撑研究，该方案主要用于破译加密数据备份，即已知的明文数据块集合$M$和目标密文数据块集合$C$源于同一个系统在两个不同时间点的备份镜像。攻击利用了数据块的局部性特征：在不同备份之间，绝大多数数据块保持了相同的局部顺序；例如，每天备份工作项目的进度快照，若一天内的改动较小，则在两次备份之间未被改动的大部分数据块之间的相对顺序保持不变。因此，得出一个关键推论：如果明文数据块M是密文数据块$C$的原始明文，那么M左边和右边相邻的明文数据块有较大可能也是$C$左边和右边相邻密文数据块的原始明文。
+%
+%\begin{figure}[!htb]
+%    \small
+%    \centering
+%    \includegraphics[width=14cm]{BaseFrequencyAttack}
+%    \caption{基于数据块局部性的频率分析攻击} 
+%    \label{fig:基于数据块局部性的频率分析攻击}
+%\end{figure}
+%
+%
+%基于此，攻击流程如图\ref{fig:基于数据块局部性的频率分析攻击}所示：首先，对$C$和$M$应用传统频率分析（\cref{sec:传统频率分析攻击}），将获得的若干组高频明密文对加入推测结果集合 $G$；然后，每次从$G$中选取一组明密文对$(M,C)$，分别对其左右相邻的明文和密文数据块集合$L_M[M]$和$L_C[C]$，以及$R_M[M]$和$R_C[C]$实施频率分析，并将获得的高频明密文对也加入$G$；继续对$G$中的明密文对进行基于相邻数据块的频率分析，直至所有明密文对都被处理。
+%
+%为了验证攻击效果，定义推测率为正确推测出原始明文的(不同)密文数据块个数与$C$中(不同)密文数据块总个数的比率。在基于真实数据集的实验验证中，攻击方案能够达到17.8\%推测率，远远高于传统频率分析方法的0.0001\%推测率。
+%
+%
+%\subsection{技术突破}
+%
+%\subsubsection{基于分布的频率分析攻击方法}
+%
+%
+%\par 基于分布的频率分析攻击利用密文和明文的相对顺序信息来增强频率分析的有效性。该攻击方法建立在数据块局部性\citing{xia2011silo,lillibridge2009sparse,zhu2008avoiding}的基础上。通过以下三个关键特性构造出基于分布的频率分析攻击方法。
+%
+%\begin{itemize}
+%    \item 数据块局部性指出数据的原始排序可能会在各种备份文件中得以保留，因此可以用于在备份文件中推理出类似的与位置相关的密文-明文对。
+%    \item 相邻数据的共现频率的相对频率分布可以通过分析得到。
+%    \item 明文及其相应的密文具有相似的相对频率分布的特性。
+%\end{itemize}
+% 
+%\subsubsection{基于聚类的频率分析攻击方法}
+%
+%
+%在基于分布的频率分析攻击方法的基础上，通过引入相似性\citing{bhagwat2009extreme}这一属性来消除基于分布的频率分析攻击方法对明文数据的细粒度顺序信息的需求。基于此提出基于聚类的频率分析攻击方法。
+%
+%\section{可行性分析}
+%
+%\subsection{研究方法可行}
+%
+%本课题通过引入加密重复数据删除方案/系统的相关特性来设计新型频率分析攻击方法，针对性提高频率分析攻击方法的有效性。该研究问题具有很高的实际价值且在面向加密重复数据删除的攻击中，已有工作提出了基于数据块局部性（chunk locality）\citing{zhu2008avoiding,lillibridge2009sparse,xia2011silo}的频率分析攻击\citing{li2017information}，在此基础上改进攻击方案以提高频率分析攻击实际效果具有明确的可行性。
+%
+%\subsection{研究条件可行}
+%
+%前期基于数据块局部性的频率分析攻击方案给出了本课题研究两种新型频率分析攻击方法的基本理论和工具基础。在原有方案上改进即可用于本课题研究。研究者在本科阶段深入钻研了CDStore、REED、SDFS等加密重复数据删除系统，以及前期基于数据块局部性的频率分析攻击方案的理论和工具实现。这些经验可以帮助设计新型频率分析方法以及其在真实系统中的实践。
+%
+%\section{本文特色与创新之处}
+%
+%本文的特色与创新之处有以下几点：
+%
+%\begin{enumerate}
+%    \item 本文针对加密重复数据删除提出了两种新型的频率分析攻击方法。除了利用由于加密重复数据删除具有确定性导致的频率泄漏之外，两种攻击都利用重复数据删除工作负载的特性来增加频率分析攻击的有效性。
+%    \item 本文使用多个真实数据集（包括长期备份\citing{sun2016long,FSL14}，Windows文件系统快照\citing{meyer2012study}和VM磁盘映像\citing{li2016cdstore,qin2017design}）以及开源重复数据删除系统SDFS\citing{SDFS}、Destor\citing{Destor}，评估两种新型频率分析攻击方法和基本频率分析攻击方法的实际效果。本文通过评估频率攻击方法的攻击结果，进一步分析本频率分析攻击方法对实际加密重复数据删除带来的安全性影响。
+%    \item 本文讨论了减少加密重复数据删除中信息泄漏的可能方案。
+%\end{enumerate}
 
 \section{论文结构及安排}
+
+本文的其余部分安排如下：\ref{sec:background}将介绍本文中将使用的概念的背景知识，\ref{sec:ThreatModel}将介绍本文的威胁模型与假设，\ref{sec:DistributionAttack}将给出本文提出的第一种攻击方法（基于分布的攻击），\ref{sec:ClusteringAttack} 将给出本文提出的第二种攻击方法（基于聚类的攻击），\ref{sec:DataSetSystem}将给出本文实验采用的相关数据来源的介绍， \ref{sec:Experiment}将对两种攻击进行实验分析， \ref{sec:Countermeasure}将给出应对本文提出的攻击方法的一些讨论， \ref{sec:RelatedWork}将介绍重复数据删除与相应攻击的相关工作，最后\ref{sec:Conclusion}对本文进行总结。

### 2019-01-05 paper/main.tex
ING | add other part title into main.tex
ING | background done with all cite insetered
ING | add part of dis-attack before dis-summary
ING | last part - exp - figure fix
ING | body done

@@
 \crefname{section}{§}{§§}
+
+%\usepackage{algorithm,algpseudocode}
+%\usepackage{caption}
 %----------
 
-\title{密文重复数据删除机制的频率攻击方法}
+\title{密文重复数据删除机制的频率分析攻击}
 \author{任彦璟}
@@
 
-加密重复数据删除旨在解决大规模数据存储系统中的安全性和存储效率：它确保每个明文都由明文本身内容派生的对称密钥加密，从而为数据存储提供机密性保证，同时保留重复数据删除的存储节省效率。但是，加密重复数据删除的确定性特性也会泄漏明文的频率，从而使加密重复数据删除容易受到频率分析的影响。在本文中，我们重新审视了频率分析导致的加密重复数据删除的安全漏洞。我们认为加密重复数据删除可能更容易受到精心设计的频率分析攻击，因此攻击提供了高可信度，可确保每个推断的明文确实对应于目标密文的概率很高（即从统计角度来看，高精度） 。为此，我们提出了两种新的频率分析攻击，它们可以适应实际重复数据删除工作负载的特性，从而提高频率分析的准确性。我们根据实际情况评估针对实际存储工作负载的建议攻击，并提供有关如何带来实际损失的观察。
+加密重复数据删除旨在解决大规模数据存储系统中的安全性和存储效率：它确保每个明文都由明文本身内容派生的对称密钥加密，从而为数据存储提供机密性保证，同时保留重复数据删除的存储节省效率。但是，加密重复数据删除的确定性特性也会泄漏明文的频率，从而使加密重复数据删除容易受到频率分析的影响。在本文中，重新审视了频率分析导致的加密重复数据删除的安全漏洞。本文认为加密重复数据删除可能更容易受到精心设计的频率分析攻击，因此攻击提供了高可信度，可确保每个推理的明文确实对应于目标密文的概率很高（即从统计角度来看，高精度） 。为此，本文提出了两种新的频率分析攻击，它们可以适应实际重复数据删除工作负载的特性，从而提高频率分析的准确性。本文根据实际情况评估针对实际存储工作负载的建议攻击，并提供有关如何带来实际损失的观察。
 
@@
 
+%% body
 \input{introduction}
+\input{background}
+\input{threatModel}
+\input{DistributionAttack}
+\input{ClusteringAttack}
+\input{DataSetandSystemReport}
+\input{Experiments}
+\input{Countermeasure}
+\input{RelatedWork}
+\input{Conclusion}
 
-%\thesisacknowledgement
+\thesisacknowledgement
+
+本科阶段四年的求学生涯即将落下帷幕，在老师、同学的支持与帮助下，本科这四年收获颇丰。本研究及论文是在我的导师李经纬的亲切关怀和耐心的指导下完成的。在此，我谨向李经纬老师至以万分诚挚的谢意。
 
@@
 
-%\thesistranslationoriginal
-%\section{}
+\thesistranslationoriginal
+
+翻译的文献内容是2017年ASIA CCS会议上由Armknecht, F., Boyd, C., Davies, G. T., Gjsteen, K., \& Toorani, M.完成的Side Channels in Deduplication: Trade-offs between Leakage and Efficiency的引言部分，该部分的电子版原始内容截图如下
+
+\begin{figure}[!htb]
+    \small
+    \centering
+    \includegraphics[width=14.5cm]{translate-1.pdf} 
+    \label{fig:}
+\end{figure}
+\begin{figure}[!htb]
+    \small
+    \centering
+    \includegraphics[width=\linewidth]{translate-2.pdf} 
+    \label{fig:}
+\end{figure}
 %
 %
-%\thesistranslationchinese
+\thesistranslationchinese
 %
-%\section{}
+\input{Translate}
 

### 2019-01-05 paper/threatModel.tex
ING | body done

--- 2018-12-15 paper/threatModel.tex
@@
 
-本文考虑存在一个对手，它准备以以下两个明确的目标为基准推断一组密文数据块-明文数据块对（用\{$(C, M)$\}表示）。
+本文考虑存在一个对手，它准备以以下两个明确的目标为基准推理一组密文数据块-明文数据块对（用\{$(C, M)$\}表示）。
 
@@
 
-    在所有的正确密文数据块-明文数据块对中，推断出大部分正确的密文数据块-明文数据块对（即统计学上的高召回率或低阴性率）。
+    在所有的正确密文数据块-明文数据块对中，推理出大部分正确的密文数据块-明文数据块对（即统计学上的高召回率或低阴性率）。
 
@@
 
-    在所有推断得到的密文数据块-明文数据块对中大部分的密文数据块-明文数据块对的配对是正确的（即统计术语中的高精度或低误报率）。
+    在所有推理得到的密文数据块-明文数据块对中大部分的密文数据块-明文数据块对的配对是正确的（即统计术语中的高精度或低误报率）。
 \end{itemize}
 
-本文假设该对手是诚实但好奇的，它可以被动地监视密文数据块流$\mathbf{C}$被写入存储系统中的过程，并利用来自$\mathbf{C}$的不同类型的泄漏信息（参见章节：\ref{sec:ThreatModel-Leakage}）。鉴于可用的泄漏信息种类，对手仅可通过唯密文攻击的方法推断$\mathbf{C}$中每个密文数据块对应的原始明文数据块。当然，对手也有可能知道有限的密文数据块-明文数据块对的集合来发起已知明文攻击，这种情况进一步加深了攻击的严重性\citing{li2017information}。但在本文中不会考虑前述的已知明文攻击方式。因此，本文将$\mathbf{C}$视为对手所能观察到的的视图，并为该视图的不同属性建模。
+本文假设该对手是诚实但好奇的，它可以被动地监视密文数据块流$\mathbf{C}$被写入存储系统中的过程，并利用来自$\mathbf{C}$的不同类型的泄漏信息（参见章节：\ref{sec:ThreatModel-Leakage}）。鉴于可用的泄漏信息种类，对手仅可通过唯密文攻击的方法推理$\mathbf{C}$中每个密文数据块对应的原始明文数据块。当然，对手也有可能知道有限的密文数据块-明文数据块对的集合来发起已知明文攻击，这种情况进一步加深了攻击的严重性\citing{li2017information}。但在本文中不会考虑前述的已知明文攻击方式。因此，本文将$\mathbf{C}$视为对手所能观察到的的视图，并为该视图的不同属性建模。
 
@@
 
-本文在加密重复数据删除存储中考虑三种类型的泄漏方式，这些泄漏使得对手能够基于它们推断信息：
+本文在加密重复数据删除存储中考虑三种类型的泄漏方式，这些泄漏使得对手能够基于它们推理信息：
 
@@
 
-    某些加密重复数据删除存储系统\cite{xia2011silo,lillibridge2009sparse,zhu2008avoiding}为了更高的运行性能，在存储密文数据块是保持了其对应的明文数据块的原始顺序。因此，$\mathbf{C}$中的密文的顺序可以映射到$\mathbf{M}$中的明文的顺序。
+    某些加密重复数据删除存储系统\citing{xia2011silo,lillibridge2009sparse,zhu2008avoiding}为了更高的运行性能，在存储密文数据块是保持了其对应的明文数据块的原始顺序。因此，$\mathbf{C}$中的密文的顺序可以映射到$\mathbf{M}$中的明文的顺序。
 
@@
 
-除上述三种泄漏以外，对手还可以获得一些辅助信息，这些信息提供了与$\mathbf{M}$相关的数据特征的基本情况（任何推理攻击都必须提供辅助信息\citing{kumar2007anonymizing,li2017information,grubbs2016breaking,zhang2016all,kellaris2016generic,ritzdorf2016information,naveed2015inference,cash2015leakage,islam2012access}）。在这项工作中，将辅助信息视为先前已知的明文数据块（例如，通过旧用户备份或VM磁盘映像得到）构成的有序列表，由$\mathbf{A}$表示。显然，攻击有效性与严重性取决于$\mathbf{A}$（即先前已知的明文数据块）和$\mathbf{M}$（即要推断的明文数据块）之间的相关性。本文的重点不是解决对手如何获取辅助信息的问题。例如，可能是由于粗心的数据发布\citing{careless-release}、被的盗存储设备\citing{stolen-device}和云存储泄漏\citing{cloud-leakage}。相反，根据这些信息，本文研究了可以获得的的辅助信息如何与各种泄漏渠道相结合，给加密重复数据删除带来信息泄漏。
+除上述三种泄漏以外，对手还可以获得一些辅助信息，这些信息提供了与$\mathbf{M}$相关的数据特征的基本情况（任何推理攻击都必须提供辅助信息\citing{kumar2007anonymizing,li2017information,grubbs2016breaking,zhang2016all,kellaris2016generic,ritzdorf2016information,naveed2015inference,cash2015leakage,islam2012access}）。在这项工作中，将辅助信息视为先前已知的明文数据块（例如，通过旧用户备份或VM磁盘映像得到）构成的有序列表，由$\mathbf{A}$表示。显然，攻击有效性与严重性取决于$\mathbf{A}$（即先前已知的明文数据块）和$\mathbf{M}$（即要推理的明文数据块）之间的相关性。本文的重点不是解决对手如何获取辅助信息的问题。例如，可能是由于粗心的数据发布\citing{careless-release}、被的盗存储设备\citing{stolen-device}和云存储泄漏\citing{cloud-leakage}。相反，根据这些信息，本文研究了可以获得的的辅助信息如何与各种泄漏渠道相结合，给加密重复数据删除带来信息泄漏。
 

### 2019-01-05 开题报告/RelatedWork.tex
ING | add start report

--- 2019-01-03 paper/RelatedWork.tex
@@
 
-除了离线暴力攻击之外，之前的研究还考虑了针对重复数据删除存储的各种攻击，此类攻击通常也适用于加密重复数据删除。例如，侧信道攻击\citing{harnik2010side,halevi2011proofs}使攻击者可以利用重复数据删除的运作模式来推断目标用户上传文件的具体内容，或者在客户端重复数据删除中获取未经授权的访问权限；例如，2010年针对“Dropbox”成功发起了侧通道攻击（以及其他相关攻击）\citing{mulazzani2011dark}。重复伪造攻击\citing{bellare2013message}通过利用不一致的标签破坏了消息的完整性。Ritzdorf等人在其工作中利用数据块大小的泄漏来推断文件的存在性\citing{ritzdorf2016information}。基于数据块局部性的攻击\citing{li2017information}利用频率分析来推断密文数据块-明文数据块对。本文的工作在推理攻击的已有工作\citing{ritzdorf2016information,li2017information}，通过利用各种类型的泄漏给出了针对加密重复数据删除的推理攻击的更深入研究。
+除了离线暴力攻击之外，之前的研究还考虑了针对重复数据删除存储的各种攻击，此类攻击通常也适用于加密重复数据删除。例如，侧信道攻击\citing{harnik2010side,halevi2011proofs}使攻击者可以利用重复数据删除的运作模式来推理目标用户上传文件的具体内容，或者在客户端重复数据删除中获取未经授权的访问权限；例如，2010年针对“Dropbox”成功发起了侧通道攻击（以及其他相关攻击）\citing{mulazzani2011dark}。重复伪造攻击\citing{bellare2013message}通过利用不一致的标签破坏了消息的完整性。Ritzdorf等人在其工作中利用数据块大小的泄漏来推理文件的存在性\citing{ritzdorf2016information}。基于数据块局部性的攻击\citing{li2017information}利用频率分析来推理密文数据块-明文数据块对。本文的工作在推理攻击的已有工作\citing{ritzdorf2016information,li2017information}，通过利用各种类型的泄漏给出了针对加密重复数据删除的推理攻击的更深入研究。
 
@@
 已有工作已经提出了几种针对加密数据库\citing{grubbs2017leakage,bindschaedler2018tao,kellaris2016generic,durak2016else,naveed2015inference,lacharite2018improved}和关键字搜索\citing{zhang2016all,grubbs2016breaking,pouliot2016shadow,cash2015leakage,islam2012access}的推理攻击方案。它们都利用确定性加密的性质来识别不同类型的泄漏。本文的研究内容与它们的不同之处在于专门研究了针对加密重复数据删除的频率分析推理攻击。
+
+\section{本章小结}
+本章介绍了现有加密重复数据删除中的各种安全机制与攻击手段，并分析了本文的工作与已有工作的不同之处。

### 2019-01-05 开题报告/Translate.tex
ING | add start report

\section{引言}

重复数据删除是许多云存储提供商和服务使用的一个过程，用于删除存储在云中的冗余数据副本。已经显示[12,14]其在实践中大大降低了存储要求，因为个人和公司的用户通常存储相同或相似的内容。重复数据删除可以在服务器端或客户端进行。在服务器端重复数据删除中，服务器会检查客户端上载的文件是否已经存储。如果是这样，服务器不会再次存储它，而是由客户端记录文件所有权，并允许客当前户端使用合适的索引访问该共享文件。服务器端重复数据删除实现了减少存储空间占用的目的，但仍然要求客户端上载它希望存储的每个文件。在客户端重复数据删除中，希望首先上载文件的用户检查文件是否已经存储在云中，例如通过将文件的散列发送到服务器，该服务器检查其存储的文件散列列表。如果文件已经存储，则客户端不会发送文件，但服务器允许客户端像以前一样访问共享文件。因此，除了降低存储要求之外，客户端重复数据删除还可以大大降低云存储的带宽需求。由于与存储成本相比，通信成本可能很高，因此客户端重复数据删除通常优于服务器端重复数据删除，这是出于经济原因。重复数据删除可以针对文件或关于块进行，但我们不会关注这种差异，因为本文中考虑的许多攻击和对策都可以应用于任何一种方法。

\subsection{加密重复数据删除}

尽管存储和带宽节省了很多，但重复数据删除至少会导致两个主要的安全和隐私问题，这导致了最近在安全重复数据删除方面的广泛工作[14]。第一个问题是，如果部署了语义安全的端到端加密，则无法进行重复数据删除。在密文不可区分的情况下，不具有解密密钥的云服务提供商（CSP）将无法确定两个密文是否对应于相同的明文。为了解决这个问题[1,3,5,8,9,18]，已经提出了几种替代的加密形式，以各种方式从文件本身导出加密密钥。这些工作通常会对文件不可预测性或关键分布做出强有力的假设。第二个问题是客户端重复数据删除可以作为在不同攻击下泄露信息的辅助渠道[7]。本文重点介绍这些侧通道攻击。

哈尼克等人。 [7]确定了客户端重复数据删除中由于侧通道引起的三次攻击。这些攻击适用于跨用户方案，其中上载相同文件的不同用户将对其数据进行重复数据删除。所有攻击的基本思想是，一个用户可以通过接收显示文件是否先前上载的信号来获取有关另一个用户文件的信息。在一个例子中，有时称为工资攻击，对手试图在她与CSP存储的雇佣合同中学习Alice的私人数据（她的工资）。攻击者在模板文件上插入猜测并将其上传到Alice的相应文件所在的CSP。然后，重复数据删除信号的出现将允许对手推断出猜测的正确性。

确定了这些侧通道攻击后，Harnik等人。 [7]提出了一种对策，其中关于文件是否已经上传的信号被随机化隐藏。更具体地，对于每个文件，随机均匀地选择阈值，并且如果先前上载的数量满足或超过阈值，则仅通知用户不上载文件。与基本的客户端重复数据删除相比，这显然会增加所需的带宽。在服务器端重复数据删除中不会出现旁道，因为客户端总是上传文件并允许服务器决定是否进行重复数据删除。因此，随机阈值对策可视为客户端重复数据删除的效率与服务器端重复数据删除的安全性之间的折衷。

\subsection{主要贡献}

虽然Harnik等的缓解思路。 [7]已经在文献[10,17]中进行了讨论和开发，没有正式建模和分析基于阈值的解决方案来保护侧通道攻击。这预示着有机会正式比较不同解决方案的有效性。本文的目的是通过以下方式纠正这种情况：
\begin{itemize}
    \item 为旁道重复数据删除策略提供正式定义，包括对策的有效性的自然衡量标准;
    \item 确定优化带宽和安全性战略所需的条件;
    \item 描述所有战略所需的安全性和效率之间的权衡;
    \item 显示Harnik等人的原始提案。 [7]在一个自然安全措施中提供最佳防御。
\end{itemize}

在其他情况下，攻击者可以使用类似的旁道。在独立和同时的工作中，Ritzdorf等人。 [16]考虑在重复数据删除存储系统中泄漏给好奇的云提供商的信息，特别关注使用内容定义的分块作为分段机制引起的泄漏。他们凭经验证明，在目标文件的许多强烈假设下，即使加密密钥未知，云提供商也可以高概率地推断低熵文件的内容。这个攻击向量与本文讨论的问题相关，但它确实强调了在存在恶意客户端和服务器的情况下分析云存储安全性的严格要求。另一个密切相关的领域是缓存隐私攻击，例如A cs等人所考虑的那些。 [2]在命名数据网络中;我们相信我们的模型也可以应用于这种情况。

本文的其余部分安排如下。 第2节回顾了对云存储的侧通道攻击和一些现有的对策。第3节讨论了我们的安全模型和防御的最优性。第4节证明了我们关于安全性和效率的主要定理，同时描述了良好的解除策略 安全与效率之间的基本权衡。 在第5节中，我们将讨论我们的工作如何与其他对策和方法相关。

### 2019-01-05 开题报告/introduction.tex
ING | add start report

--- 2018-12-28 paper/introduction.tex
@@
+\chapter*{开题报告}
+
+\setcounter{chapter}{1}
+
 \section{研究工作的背景与意义}
@@
 %TODO:数据块信息引用
-由于基于数据块内容产生密钥，加密重复数据删除泄漏了数据块的频率信息，即如果一个明文数据块出现了n次，则它对应的密文数据块也将出现n次。另一方面，真实数据集中数据块的出现频率往往呈非均匀分布，本文调研了FSL和VM备份数据集(数据集信息见§3.2)的数据块频率分布特征，发现三种数据集有超过97\%的数据块的频率低于100次，而至多只有0.04\%的数据块的频率高于10,000次（图\ref{fig:两种真实数据集的数据块频率分布}），这种非均匀的分布特点使攻击者可以利用频率来确定相应数据块。
+由于基于数据块内容产生密钥，加密重复数据删除泄漏了数据块的频率信息，即如果一个明文数据块出现了n次，则它对应的密文数据块也将出现n次。另一方面，真实数据集中数据块的出现频率往往呈非均匀分布，调研了FSL和VM备份数据集的数据块频率分布特征，发现三种数据集有超过97\%的数据块的频率低于100次，而至多只有0.04\%的数据块的频率高于10,000次（图\ref{fig:两种真实数据集的数据块频率分布}），这种非均匀的分布特点使攻击者可以利用频率来确定相应数据块。
 
@@
 \begin{itemize}
-    \item 数据块局部性指出数据的原始排序可能会在各种备份文件中得以保留，因此可以用于在备份文件中推断出类似的与位置相关的密文-明文对。
+    \item 数据块局部性指出数据的原始排序可能会在各种备份文件中得以保留，因此可以用于在备份文件中推理出类似的与位置相关的密文-明文对。
     \item 相邻数据的共现频率的相对频率分布可以通过分析得到。
@@
 
-前期基于数据块局部性的频率分析攻击方案给出了本课题研究两种新型频率分析攻击方法的基本理论和工具基础。在原有方案上改进即可用于本课题研究。研究者在本科阶段深入钻研了CDStore、REED、SDFS等加密重复数据删除系统，以及前期基于数据块局部性的频率分析攻击方案的理论和工具实现。这些经验可以帮助设计新型频率分析方法以及其在真实系统中的实践。
-
-\section{本文特色与创新之处}
-
-本文的特色与创新之处有以下几点：
-
-\begin{enumerate}
-    \item 本文针对加密重复数据删除提出了两种新型的频率分析攻击方法。除了利用由于加密重复数据删除具有确定性导致的频率泄漏之外，两种攻击都利用重复数据删除工作负载的特性来增加频率分析攻击的有效性。
-    \item 本文使用多个真实数据集（包括长期备份\citing{sun2016long,FSL14}，Windows文件系统快照\citing{meyer2012study}和VM磁盘映像\citing{li2016cdstore,qin2017design}）以及开源重复数据删除系统SDFS\citing{SDFS}、Destor\citing{Destor}，评估两种新型频率分析攻击方法和基本频率分析攻击方法的实际效果。本文通过评估频率攻击方法的攻击结果，进一步分析本频率分析攻击方法对实际加密重复数据删除带来的安全性影响。
-    \item 本文讨论了减少加密重复数据删除中信息泄漏的可能方案。
-\end{enumerate}
-
-\section{论文结构及安排}
+前期基于数据块局部性的频率分析攻击方案给出了本课题研究两种新型频率分析攻击方法的基本理论和工具基础。

### 2019-01-05 paper/Translate.tex
ING | paper over

\section{引言}

重复数据删除是许多云存储提供商和服务使用的一个过程，用于删除存储在云中的冗余数据副本。因为个人和公司的用户通常存储相同或相似的内容，其在实践中大大降低了存储要求[12,14]。重复数据删除可以在服务器端或客户端进行。在服务器端重复数据删除中，服务器会检查客户端上载的文件是否已经存储。如果是这样，服务器不会再次存储它，而是由客户端记录文件所有权，并允许客当前户端使用合适的索引访问该共享文件。服务器端重复数据删除实现了减少存储空间占用的目的，但仍然要求客户端上载它希望存储的每个文件。在客户端重复数据删除中，希望首先上载文件的用户检查文件是否已经存储在云中，例如通过将文件的散列发送到服务器，该服务器检查其存储的文件散列列表。如果文件已经存储，则客户端不会发送文件，但服务器允许客户端像以前一样访问共享文件。因此，除了降低存储要求之外，客户端重复数据删除还可以大大降低云存储的带宽需求。由于与存储成本相比，通信成本可能更高。出于经济原因，客户端重复数据删除通常优于服务器端重复数据删除。重复数据删除可以针对文件或针对数据块进行，但我们不会关注这种差异，因为本文中考虑的许多攻击和对策都可以应用于其中任何一种方法。

\subsection{加密重复数据删除}

尽管重复数据删除中存储和带宽节省了很多，但其至少会导致两个主要的安全和隐私问题，这些问题在安全重复数据删除方面的有广泛的工作[14]。第一个问题是，如果部署了端到端加密方法，则无法进行重复数据删除。因为在密文不可区分的情况下，不具有解密密钥的云服务提供商（CSP）将无法确定两个密文是否对应于相同的明文。为了解决这个问题[1,3,5,8,9,18]，已经提出了几种替代的加密形式，以各种方式从文件本身导出加密密钥。这些工作通常会对文件的不可预测性或关键分布做出强有力的假设。第二个问题是客户端重复数据删除可以作为在不同攻击下泄露信息的辅助渠道[7]。本文重点介绍这些侧通道攻击。

Harnik等人[7]提出了客户端重复数据删除中由于侧通道引起的三种攻击。这些攻击适用于跨用户的重复数据删除方案（其中上载相同文件的不同用户将对其数据进行重复数据删除）。这些攻击的基本思想是，一个用户可以通过接收显示文件是否已经上载的信号来获取有关另一个用户文件的信息。在一个例子中（有时称为工资攻击），对手试图在Alice与CSP存储的雇佣合同中学习她的私人数据（她的工资）。攻击者在模板文件上插入猜测的数据并将其上传到Alice的相应文件所在的CSP。然后，对手通过重复数据删除信号的出现与否推断出猜测的正确性。

确定了这些侧通道攻击后，Harnik等人[7]提出了一种对策，其中关于文件是否已经上传的信号被随机化隐藏。更具体地，对于每个文件，随机均匀地选择阈值，如果先前上载的次数满足或超过阈值，则通知用户不上载文件。与基本的客户端重复数据删除相比，这显然会增加系统所需的带宽。同时，在服务器端重复数据删除中不会出现侧信道攻击，因为客户端总是上传文件并由服务器决定是否进行重复数据删除。因此，随机阈值对策可视为客户端重复数据删除的效率与服务器端重复数据删除的安全性之间的折衷选择。

\subsection{主要贡献}

虽然Harnik等的基于阈值的解决方案来保护侧通道攻击的对策[7]已经在文献[10,17]中进行了讨论和开发，但没有进行正式的建模和分析。本文正式的比较不同解决方案的有效性：

\begin{itemize}
    \item 为侧信道重复数据删除策略提供正式定义，包括对策的有效性的自然衡量标准。
    \item 确定优化带宽和安全性所需的条件。
    \item 描述所有策略所需的安全性和效率之间如何进行权衡。
    \item 证明Harnik等人的原始提案[7]在一个自然安全措施中可以提供最佳防御效果。
\end{itemize}

在其他情况下，攻击者可以使用类似的侧信道。在独立而同时的工作中，Ritzdorf等人[16]考虑在重复数据删除存储系统中泄漏给好奇的云提供商的信息，并且特别关注使用内容定义的分块作为数据块分块机制引起的泄漏。他们凭经验证明，在对目标文件的许多强假设下，即使加密密钥未知，云提供商也可以高概率地推断出低熵文件的内容。这个攻击向量与本文讨论的问题相关，它强调了在存在恶意客户端和服务器的情况下分析云存储安全性的严格要求。另一个密切相关的领域是缓存隐私攻击，例如Acs等人[2]所考虑的那些在命名数据网络中的攻击。我们相信我们的模型也可以应用于这种情况。

本文的其余部分安排如下。第2节回顾了对云存储的侧通道攻击和一些现有的对策。第3节讨论了我们的安全模型和防御的最优性。第4节证明了我们关于安全性和效率的主要定理，同时描述了良好的策略如何在安全与效率之间做基本权衡。 在第5节中，我们将讨论我们的工作与其他对策和方法的相关性。

### 2019-01-05 paper/introduction.tex
ING | paper over

@@
 
-面向加密重复数据删除，已有工作\citing{li2017information}提出了基于数据块局部性（chunk locality）\citing{zhu2008avoiding,lillibridge2009sparse,xia2011silo}的频率分析攻击。本课题的部分技术路线（\cref{sec:技术路线}）就是在该工作\citing{li2017information}的基础上提出来的，并进一步研究频率分析攻击的准确率和依赖条件，以及面向真实系统的攻击原型。除了频率分析和暴力破解（\cref{sec:加密重复数据删除}）之外，加密重复数据删除还可能遭受边信道攻击\citing{harnik2010side,halevi2011proofs,mulazzani2011dark}、副本伪造攻击\citing{bellare2013message}、基于数据块长度的攻击\citing{ritzdorf2016information}等威胁，但这些攻击可通过所有权证明\citing{halevi2011proofs}、守卫解密(guarded decryption)\citing{bellare2013message}、固定长度分块等措施进行防御，而本文所研究的频率分析攻击超出了现有保护措施的防御范畴。
+面向加密重复数据删除，已有工作\citing{li2017information}提出了基于数据块局部性（chunk locality）\citing{zhu2008avoiding,lillibridge2009sparse,xia2011silo}的频率分析攻击。本课题的部分技术路线（参见\ref{sec:技术路线}）就是在该工作\citing{li2017information}的基础上提出来的，并进一步研究频率分析攻击的准确率和依赖条件，以及面向真实系统的攻击原型。除了频率分析和暴力破解（参见\ref{sec:加密重复数据删除}）之外，加密重复数据删除还可能遭受边信道攻击\citing{harnik2010side,halevi2011proofs,mulazzani2011dark}、副本伪造攻击\citing{bellare2013message}、基于数据块长度的攻击\citing{ritzdorf2016information}等威胁，但这些攻击可通过所有权证明\citing{halevi2011proofs}、守卫解密(guarded decryption)\citing{bellare2013message}、固定长度分块等措施进行防御，而本文所研究的频率分析攻击超出了现有保护措施的防御范畴。
 
@@
 %
-%基于此，攻击流程如图\ref{fig:基于数据块局部性的频率分析攻击}所示：首先，对$C$和$M$应用传统频率分析（\cref{sec:传统频率分析攻击}），将获得的若干组高频明密文对加入推测结果集合 $G$；然后，每次从$G$中选取一组明密文对$(M,C)$，分别对其左右相邻的明文和密文数据块集合$L_M[M]$和$L_C[C]$，以及$R_M[M]$和$R_C[C]$实施频率分析，并将获得的高频明密文对也加入$G$；继续对$G$中的明密文对进行基于相邻数据块的频率分析，直至所有明密文对都被处理。
+%基于此，攻击流程如图\ref{fig:基于数据块局部性的频率分析攻击}所示：首先，对$C$和$M$应用传统频率分析（参见\ref{sec:传统频率分析攻击}），将获得的若干组高频明密文对加入推测结果集合 $G$；然后，每次从$G$中选取一组明密文对$(M,C)$，分别对其左右相邻的明文和密文数据块集合$L_M[M]$和$L_C[C]$，以及$R_M[M]$和$R_C[C]$实施频率分析，并将获得的高频明密文对也加入$G$；继续对$G$中的明密文对进行基于相邻数据块的频率分析，直至所有明密文对都被处理。
 %
@@
 %
-%\section{本文特色与创新之处}
-%
-%本文的特色与创新之处有以下几点：
-%
-%\begin{enumerate}
-%    \item 本文针对加密重复数据删除提出了两种新型的频率分析攻击方法。除了利用由于加密重复数据删除具有确定性导致的频率泄漏之外，两种攻击都利用重复数据删除工作负载的特性来增加频率分析攻击的有效性。
-%    \item 本文使用多个真实数据集（包括长期备份\citing{sun2016long,FSL14}，Windows文件系统快照\citing{meyer2012study}和VM磁盘映像\citing{li2016cdstore,qin2017design}）以及开源重复数据删除系统SDFS\citing{SDFS}、Destor\citing{Destor}，评估两种新型频率分析攻击方法和基本频率分析攻击方法的实际效果。本文通过评估频率攻击方法的攻击结果，进一步分析本频率分析攻击方法对实际加密重复数据删除带来的安全性影响。
-%    \item 本文讨论了减少加密重复数据删除中信息泄漏的可能方案。
-%\end{enumerate}
+\section{本文特色与创新之处}
+
+本文的特色与创新之处有以下几点：
+
+\begin{enumerate}
+    \item 本文针对加密重复数据删除提出了两种新型的频率分析攻击方法。除了利用由于加密重复数据删除具有确定性导致的频率泄漏之外，两种攻击都利用重复数据删除工作负载的特性来增加频率分析攻击的有效性。
+    \item 本文使用多个真实数据集（包括长期备份\citing{sun2016long,FSL14}，Windows文件系统快照\citing{meyer2012study}和VM磁盘映像\citing{li2016cdstore,qin2017design}）以及开源重复数据删除系统SDFS\citing{SDFS}、Destor\citing{Destor}，评估两种新型频率分析攻击方法和基本频率分析攻击方法的实际效果。本文通过评估频率攻击方法的攻击结果，进一步分析本频率分析攻击方法对实际加密重复数据删除带来的安全性影响。
+    \item 本文讨论了减少加密重复数据删除中信息泄漏的可能方案。
+\end{enumerate}
 

### 2019-01-05 slides/materialDesignExample.tex
ING | add slides

\documentclass[aspectratio=43]{beamer}
\usepackage[utf8]{inputenc}
\usepackage{multicol}
\usepackage{fontspec}
\setsansfont{Songti SC} % font name is case-sensitive

\title{密文重复数据删除机制的\\频率分析攻击}
\date{\today}
\author[Tinoryj]{任彦璟}

\usetheme{material}

\useLightTheme
\usePrimaryBlue
\useAccentOrange

\begin{document}

\begin{frame}
\titlepage
\end{frame}

\begin{frame}
\begin{card}
现有频率分析攻击在加密重复数据删除中效果不佳，\\[2mm]如何有针对性的提高攻击效果？
\end{card}
\end{frame}

\begin{frame}{目录}
\begin{card}
\tableofcontents
\end{card}
\end{frame}

\section{选题的意义及目的}
\begin{frame}{选题的意义及目的}
\begin{card}

\end{card}
\begin{card}

\end{card}
\end{frame}

\section{国内外研究现状}

\section{主要研究内容}

\section{攻击方案的设计}

\section{研究结果与分析}

\section{选题的意义及目的}

\section{总结建议与参考文献}

\begin{frame}{Setup}
\begin{card}
Setup is really easy: 
{\color{primary}\textbackslash usetheme\{material\}}
\end{card}
\begin{card}
Further you might want to customize the background with: \\[2mm]
{\color{primary}\textbackslash useLightTheme} or {\color{primary}\textbackslash useDarkTheme} \\[2mm]
and primary and accent colors.
\end{card}
\end{frame}

\begin{frame}{Setup -- colors}
\begin{card}
There are some colors from the Material Design guidelines coded in. You access those by: \\[2mm]
{\color{primary} \textbackslash usePrimary[Color]} and {\color{primary}\textbackslash useAccent[Color]}\\[2mm]
{\tiny {\color{primary}Color} $\in \{$ Red, Pink, Purple, Deep Purple, Indigo, Blue, Light Blue, Cyan, Teal, Green, Light Green, Lime, Yellow, Amber, Orange, Deep Orange, Brown, Grey, Blue Grey $\}$} \\[2mm]
or you can pick your own:\\[2mm]
{\color{primary} \textbackslash usePrimary\{primary color, darker primary color, text color\}}
{\color{primary} \textbackslash useAccent\{primary color, text color\}}\\[2mm]
{\color{primary} darker primary color} is just darker version of {\color{primary} primary color} and {\color{primary} text color} is color of text on {\color{primary} primary} or {\color{primary} accent colors}.
\end{card}
\end{frame}

\begin{frame}{Card}
\begin{card}
All content should only appear in cards. There are several variants:
\begin{itemize}
\item plain card
\item card with a title
\item card with an image
\item tiny card
\end{itemize}
\end{card}
\end{frame}

\begin{frame}{plain card}
\begin{card}
\end{card}

\begin{card}
{\color{primary} \textbackslash begin\{card\}\\[2mm]}
\null\qquad \textit{[your content here]}\\[2mm]
{\color{primary} \textbackslash end\{card\}}
\end{card}
\end{frame}

\begin{frame}{card with a title}
\begin{card}[Title]
\end{card}

\begin{card}
{\color{primary} \textbackslash begin\{card\}[Title]\\[2mm]}
\null\qquad \textit{[your content here]}\\[2mm]
{\color{primary} \textbackslash end\{card\}}
\end{card}
\end{frame}

\begin{frame}{card with an image}
\centering
\cardImg{img/rudolfinum.jpg}{0.5\textwidth}

\begin{card}
{\color{primary} \textbackslash cardImg\{file name\}\{width\}}
\end{card}
\end{frame}

\begin{frame}{tiny card}
\begin{cardTiny}
\end{cardTiny}

\begin{card}
{\color{primary} \textbackslash begin\{cardTiny\}\\[2mm]}
\null\qquad \textit{[your content here]}\\[2mm]
{\color{primary} \textbackslash end\{cardTiny\}}
\end{card}
\begin{card}
Tiny card is useful for labels where too much whitespace gets in the way. 
\end{card}
\end{frame}

\begin{frame}{Cards can be filled with anything you want}

\begin{card}
\centering$V(x) = \left\{ y \in \mathbb{R}^n \,|\, \forall z \in P, z\neq x:\, \|y-x\|\leq\|y-z\| \right\}$
\end{card}

\begin{card}
\centering
\begin{tabular}{lcr}
left & center & right \\
\hline
1 & 2 & 3 \\
\end{tabular}
\end{card}

\begin{card}
\begin{theorem}[Pythagorean]
The sum of the areas of the two squares on the legs equals the area of the square on the hypotenuse.
\end{theorem}
\end{card}
\end{frame}

\begin{frameImg}{img/rudolfinum.jpg}
\vspace*{60mm}
\begin{cardTiny}
Lastly it is possible to set image as a background for a frame:\\[2mm]
{\color{primary} \textbackslash begin\{frameImg\}["height"]\{file name\}\\[2mm]}
\null\qquad \textit{[your content here]}\\[2mm]
{\color{primary} \textbackslash end\{frameImg\}}
\end{cardTiny}
\end{frameImg}

\begin{frameImg}[height]{img/rudolfinum.jpg}
\vspace*{60mm}
\begin{cardTiny}
Parameter {\color{primary} ["height"]} determines the dimension that is stretched to cover the frame ({\color{primary} ["width"]} is default).
\end{cardTiny}
\end{frameImg}

\begin{frame}
\begin{multicols}{2}
[
\begin{cardTiny}
Two images side by side with columns.
\end{cardTiny}
]
\centering
\cardImg{img/rudolfinum.jpg}{0.48\textwidth}

\cardImg{img/rudolfinum.jpg}{0.48\textwidth}
\end{multicols}
\end{frame}

\begin{frame}
\begin{card}
That is all for now. Despite having successfully presented several project with this theme, it is still work in progress. If this manual is not clear enough, you can also review it's source, that may bring more clarity.
\end{card}
\begin{card}
Feel free to submit any issues you find on github: \\
{\footnotesize \url{https://github.com/edasubert/beamerMaterialDesign}}
\end{card}
\begin{card}
This theme is released under MIT license. Feel free to modify or improve or whatever. 
\end{card}
\end{frame}

\end{document}

### 2019-01-05 开题报告/report/introduction.tex
ING | report slides page 4

--- 2019-01-05 开题报告/introduction.tex
@@
 
-面向加密重复数据删除，已有工作\citing{li2017information}提出了基于数据块局部性（chunk locality）\citing{zhu2008avoiding,lillibridge2009sparse,xia2011silo}的频率分析攻击。本课题的部分技术路线（\cref{sec:技术路线}）就是在该工作\citing{li2017information}的基础上提出来的，并进一步研究频率分析攻击的准确率和依赖条件，以及面向真实系统的攻击原型。除了频率分析和暴力破解（\cref{sec:加密重复数据删除}）之外，加密重复数据删除还可能遭受边信道攻击\citing{harnik2010side,halevi2011proofs,mulazzani2011dark}、副本伪造攻击\citing{bellare2013message}、基于数据块长度的攻击\citing{ritzdorf2016information}等威胁，但这些攻击可通过所有权证明\citing{halevi2011proofs}、守卫解密(guarded decryption)\citing{bellare2013message}、固定长度分块等措施进行防御，而本文所研究的频率分析攻击超出了现有保护措施的防御范畴。
+面向加密重复数据删除，已有工作\citing{li2017information}提出了基于数据块局部性（chunk locality）\citing{zhu2008avoiding,lillibridge2009sparse,xia2011silo}的频率分析攻击。本课题的部分技术路线（\ref{sec:技术路线}）就是在该工作\citing{li2017information}的基础上提出来的，并进一步研究频率分析攻击的准确率和依赖条件，以及面向真实系统的攻击原型。除了频率分析和暴力破解（\ref{sec:加密重复数据删除}）之外，加密重复数据删除还可能遭受边信道攻击\citing{harnik2010side,halevi2011proofs,mulazzani2011dark}、副本伪造攻击\citing{bellare2013message}、基于数据块长度的攻击\citing{ritzdorf2016information}等威胁，但这些攻击可通过所有权证明\citing{halevi2011proofs}、守卫解密(guarded decryption)\citing{bellare2013message}、固定长度分块等措施进行防御，而本文所研究的频率分析攻击超出了现有保护措施的防御范畴。
 
@@
 
-基于此，攻击流程如图\ref{fig:基于数据块局部性的频率分析攻击}所示：首先，对$C$和$M$应用传统频率分析（\cref{sec:传统频率分析攻击}），将获得的若干组高频明密文对加入推测结果集合 $G$；然后，每次从$G$中选取一组明密文对$(M,C)$，分别对其左右相邻的明文和密文数据块集合$L_M[M]$和$L_C[C]$，以及$R_M[M]$和$R_C[C]$实施频率分析，并将获得的高频明密文对也加入$G$；继续对$G$中的明密文对进行基于相邻数据块的频率分析，直至所有明密文对都被处理。
+基于此，攻击流程如图\ref{fig:基于数据块局部性的频率分析攻击}所示：首先，对$C$和$M$应用传统频率分析（\ref{sec:传统频率分析攻击}），将获得的若干组高频明密文对加入推测结果集合 $G$；然后，每次从$G$中选取一组明密文对$(M,C)$，分别对其左右相邻的明文和密文数据块集合$L_M[M]$和$L_C[C]$，以及$R_M[M]$和$R_C[C]$实施频率分析，并将获得的高频明密文对也加入$G$；继续对$G$中的明密文对进行基于相邻数据块的频率分析，直至所有明密文对都被处理。
 
@@
 
-前期基于数据块局部性的频率分析攻击方案给出了本课题研究两种新型频率分析攻击方法的基本理论和工具基础。
+前期基于数据块局部性的频率分析攻击方案给出了本课题研究两种新型频率分析攻击方法的基本理论和工具基础。在原有方案上改进即可用于本课题研究。研究者在本科阶段深入钻研了CDStore、REED、SDFS等加密重复数据删除系统，以及前期基于数据块局部性的频率分析攻击方案的理论和工具实现。这些经验可以帮助设计新型频率分析方法以及其在真实系统中的实践。
+
+\section{本文特色与创新之处}
+
+本研究的特色与创新之处有以下几点：
+
+\begin{enumerate}
+    \item 研究针对加密重复数据删除提出了两种新型的频率分析攻击方法。除了利用由于加密重复数据删除具有确定性导致的频率泄漏之外，两种攻击都利用重复数据删除工作负载的特性来增加频率分析攻击的有效性。
+    \item 本文研究使用多个真实数据集（包括长期备份\citing{sun2016long,FSL14}，Windows文件系统快照\citing{meyer2012study}和VM磁盘映像\citing{li2016cdstore,qin2017design}）以及开源重复数据删除系统SDFS\citing{SDFS}、Destor\citing{Destor}，评估两种新型频率分析攻击方法和基本频率分析攻击方法的实际效果。通过评估频率攻击方法的攻击结果，进一步分析本频率分析攻击方法对实际加密重复数据删除带来的安全性影响。
+    \item 本研究讨论了减少加密重复数据删除中信息泄漏的可能方案。
+\end{enumerate}

### 2019-01-08 paper/introduction.tex
ING | report slides page 4
ING | slides without reference over

@@
 
-%TODO:数据块信息引用
 由于基于数据块内容产生密钥，加密重复数据删除泄漏了数据块的频率信息，即如果一个明文数据块出现了n次，则它对应的密文数据块也将出现n次。另一方面，真实数据集中数据块的出现频率往往呈非均匀分布，本文调研了FSL和VM备份数据集(数据集信息见§3.2)的数据块频率分布特征，发现三种数据集有超过97\%的数据块的频率低于100次，而至多只有0.04\%的数据块的频率高于10,000次（图\ref{fig:两种真实数据集的数据块频率分布}），这种非均匀的分布特点使攻击者可以利用频率来确定相应数据块。
@@
 
-消息锁定加密（message-locked encryption，MLE）确立了加密重复数据删除的密码学基础\citing{bellare2013message}:基于数据内容产生密钥(称为 MLE 密钥)，从而将相同明文加密为相同密文。最流行的MLE实例是收敛加密（convergent encryption，CE）\citing{douceur2002reclaiming}，它使用明文的哈希值作为MLE密钥，并基于密文哈希值计算指纹，以识别重复数据（如图\ref{fig:加密重复数据删除系统逻辑视图}）。基于CE的加密重复数据删除方案还包括:
+消息锁定加密（message-locked encryption，MLE）确立了加密重复数据删除的密码学基础\citing{bellare2013message}：基于数据内容产生密钥(称为 MLE 密钥)，从而将相同明文加密为相同密文。最流行的MLE实例是收敛加密（convergent encryption，CE）\citing{douceur2002reclaiming}，它使用明文的哈希值作为MLE密钥，并基于密文哈希值计算指纹，以识别重复数据（如图\ref{fig:加密重复数据删除系统逻辑视图}）。基于CE的加密重复数据删除方案还包括:
 
@@
 
-面向加密重复数据删除，已有工作\citing{li2017information}提出了基于数据块局部性（chunk locality）\citing{zhu2008avoiding,lillibridge2009sparse,xia2011silo}的频率分析攻击。本课题的部分技术路线（参见\ref{sec:技术路线}）就是在该工作\citing{li2017information}的基础上提出来的，并进一步研究频率分析攻击的准确率和依赖条件，以及面向真实系统的攻击原型。除了频率分析和暴力破解（参见\ref{sec:加密重复数据删除}）之外，加密重复数据删除还可能遭受边信道攻击\citing{harnik2010side,halevi2011proofs,mulazzani2011dark}、副本伪造攻击\citing{bellare2013message}、基于数据块长度的攻击\citing{ritzdorf2016information}等威胁，但这些攻击可通过所有权证明\citing{halevi2011proofs}、守卫解密(guarded decryption)\citing{bellare2013message}、固定长度分块等措施进行防御，而本文所研究的频率分析攻击超出了现有保护措施的防御范畴。
-
+面向加密重复数据删除，已有工作\citing{li2017information}提出了基于数据块局部性（chunk locality）\citing{zhu2008avoiding,lillibridge2009sparse,xia2011silo}的频率分析攻击。本课题的部分技术路线就是在该工作\citing{li2017information}的基础上提出来的，并进一步研究频率分析攻击的准确率和依赖条件，以及面向真实系统的攻击原型。除了频率分析和暴力破解（参见\ref{sec:加密重复数据删除}）之外，加密重复数据删除还可能遭受边信道攻击\citing{harnik2010side,halevi2011proofs,mulazzani2011dark}、副本伪造攻击\citing{bellare2013message}、基于数据块长度的攻击\citing{ritzdorf2016information}等威胁，但这些攻击可通过所有权证明\citing{halevi2011proofs}、守卫解密(guarded decryption)\citing{bellare2013message}、固定长度分块等措施进行防御，而本文所研究的频率分析攻击超出了现有保护措施的防御范畴。
+%（参见\ref{sec:技术路线}）
 \section{课题的研究内容、研究目标、以及拟解决的关键问题}
